### 2022-10-06 README.qmd
Add MPSA proposal

---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.retina = 3
)

library(emoji)

Title <- "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
Authors <- "Andrew Heiss and Meng Ye"
Year <- "2022"
```

# `r Title`

[Andrew Heiss](https://www.andrewheiss.com/) • Andrew Young School of Policy Studies • Georgia State University  
Meng Ye • Andrew Young School of Policy Studies • Georgia State University

---

## Abstract

China’s 2017 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international NGOs (INGOs). However, the effects of this global crackdown on INGOs have been difficult to measure since there is often divergence between the formal de jure regulations and the de facto implementation of these laws. The enforcement of these laws also depends on the services provided by these organizations. In particular, authoritarian regimes display conflicting attitudes towards claim-making (e.g. advocacy) INGOs versus service-providing (e.g. humanitarian assistance) INGOs. In this paper, we measure the effect of China’s ONGO law on INGO operations since 2017. We test how INGO operational flexibility under the ONGO law is influenced by organizations’ issue areas. We argue that service provision INGOs have greater flexibility and are allowed to work in a larger number of provinces than their claim-making counterparts. China provides an excellent setting for testing our claim—the 2017 ONGO law regulates both claim-making and service-providing NGOs, and ambiguity in the law gives ample room for arbitrary discretion by authorities. We test our argument using multilevel Bayesian models with administrative data from 635 registered representative offices of INGOs registered in China between 2017–2021. Our results speak to the broader literature on closing civic space and provide an empirical illustration of the practical effect of NGO restrictions on global civil society.

---

## `r emoji::emoji_glue(":hugs::oyster:")`: "Compassionate clam" project name

Because project titles change all the time with revisions, rewriting, and peer review, we used [**codename**](http://svmiller.com/codename/) to generate an [Ubuntu-style](https://wiki.ubuntu.com/DevelopmentCodeNames) internal-to-us project name that won't change.

```{r generate-code-name, eval=FALSE}
library(codename)
codename_message()
#> code name generated by {codename} v.0.4.0

codename(seed = "china ongo law", type = "ubuntu")
#> [1] "compassionate clam"
```

## Licenses

**Text and figures:** All prose and images are licensed under Creative Commons ([CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/))

**Code:** All code is licensed under the [MIT License](LICENSE.md).

## Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By participating in this project you agree to abide by its terms.

### 2022-10-06 manuscript/submissions/2023-mpsa.qmd
Add MPSA proposal

--- 2022-10-06 README.qmd
@@
 ---
-format: gfm
+title: "MPSA 2023 proposal" 
+date: "October 6, 2022"
+author:
+  - name: Andrew Heiss
+    email: aheiss@gsu.edu
+    orcid: 0000-0002-3948-3914
+    affiliations: 
+      - id: ays
+        name: Georgia State University
+        department: Andrew Young School of Policy Studies
+        city: Atlanta
+        region: GA
+    attributes:
+      corresponding: true
+  - name: Meng Ye
+    email: mye2@gsu.edu
+    affiliations:
+      - ref: ays
+format:
+  html: default
+  docx: default
+  pdf: default
 ---
 
-<!-- README.md is generated from README.qmd. Please edit that file -->
+# Title
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(
-  collapse = TRUE,
-  comment = "#>",
-  fig.path = "README-",
-  fig.retina = 3
-)
+*(102 characters; 250 limit)*
 
-library(emoji)
+The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society
 
-Title <- "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
-Authors <- "Andrew Heiss and Meng Ye"
-Year <- "2022"
-```
+# Brief Overview
 
-# `r Title`
+*(244 characters; 250 limit)*
 
-[Andrew Heiss](https://www.andrewheiss.com/) • Andrew Young School of Policy Studies • Georgia State University  
-Meng Ye • Andrew Young School of Policy Studies • Georgia State University
+To better understand the effect of closing space for global civil society, we use administrative data collected under China’s 2017 Overseas NGO law to explore how NGO issue areas influence their operational flexibility under strict regulations.
 
----
+# Keywords
 
-## Abstract
+*(49 characters; 250 limit)*
+
+China, international NGO, civil society, ONGO law
+
+# Abstract
+
+*(1,500 characters; 1,500 limit)*
 
@@
 Our results speak to the broader literature on closing civic space and provide an empirical illustration of the practical effect of NGO restrictions on global civil society.
-
----
-
-## `r emoji::emoji_glue(":hugs::oyster:")`: "Compassionate clam" project name
-
-Because project titles change all the time with revisions, rewriting, and peer review, we used [**codename**](http://svmiller.com/codename/) to generate an [Ubuntu-style](https://wiki.ubuntu.com/DevelopmentCodeNames) internal-to-us project name that won't change.
-
-```{r generate-code-name, eval=FALSE}
-library(codename)
-codename_message()
-#> code name generated by {codename} v.0.4.0
-
-codename(seed = "china ongo law", type = "ubuntu")
-#> [1] "compassionate clam"
-```
-
-## Licenses
-
-**Text and figures:** All prose and images are licensed under Creative Commons ([CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/))
-
-**Code:** All code is licensed under the [MIT License](LICENSE.md).
-
-## Contributions
-
-We welcome contributions from everyone.
-Before you get started, please see our [contributor guidelines](CONTRIBUTING.md).
-Please note that this project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html).
-By participating in this project you agree to abide by its terms.

### 2022-10-10 data-cleanning/data_cleaning_ongo.Rmd
add data cleaning rmd

---
title: "ongo data cleaning"
author: "Meng Ye"
date: "2022-10-07"
output: html_document
---

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(lubridate)
library(sf)
library(mapchina)
```

## Import Data

```{r import csv, message=FALSE, warning=FALSE}
# manually cleaned Chinese ONGO regulator administrative data
# ongo_manual_csv <- read_csv(here("data", "manual_data", "ongo-manual-clean.csv"))
```

```{r save rds}
# saveRDS(ongo_manual_csv, here("data", "manual_data", "ongo_manual.rds"))
```

```{r import data from rds}
ongo_manual <- readRDS(here("data", "manual_data", "ongo_manual.rds"))
```

Documentation of the pre-processing of scraped data

The inspected raw data is the version derived after inspecting the scraped csv file against the source website. The blank lines in the scraped csv file are from ROs that have been de-registered. The website (https://ngo.mps.gov.cn/ngo/portal/toInfogs.do) keep their names in the general list but their profiles are all blank now.

A couple of scraping errors have also been corrected in the process. That is cases where the RO is active but shown as blank rows in the scraped. I manually added those rows back.

For those that already been de-registered, I added back their `index`, `ro_name`, and `ro_id`, and generated a dichotomous indicator that they are no more "active" in the `still_active` column.

For the `still_active` variable, the values are manually input for the blank lines. After checking against the offical website, `FALSE` for those have indeed de-register and `TRUE` for those that turned out to be parsing errors. The rest NAs will be recoded to `TRUE` in data cleaning.

After the cross-checking process, the index number of ROs in our dataset is the same as the index in the official database as of 2022-10-4.

The following columns are also manually coded:

- `home`

home county or region of the ONGO. Not using the name "country" to be flexible enough to denote, Hong Kong, Macau and Taiwan

- `ro_count`

There are cases where ONGOs are not granted to operate across China, so they register multiple ROs to cover enough number of provinces where they need to work. We surely want to include this variable because it is directly correlated with `geo_scope_num`

A related `multiple_index` is a index number created to identify siblings, in the form of 100-1, 100-2...(starting from 100 to ensure all have three digits) `NA` for ONGOs only having one RO. Note there can be cases where one of the siblings has been de-registered, but only several.

- `work_field`

`work_field` is the original mission statement in Chinese. The name "field" is chosen for the moment, because it seems "area" is more easily to be confused with the geographical scope
`work_field_code1` is the main work field code
`work_field_code2` is an alternative code for the work field if the ONGO's works touch on overlapping fields

The field categories are (planed to be) decided based on Article 3 of the law.

*Overseas NGOs may, in accordance with the provisions of this Law, engage in undertakings of benefit to the public in the areas of the economy, education, science, culture, health, sports and environmental protection, as well as in the areas of poverty and disaster relief.*

Earlier fields used 
- Commerce and Trade Promotion
- Science and Technology
- Education
- Charity and Public Benefit
- Environment
- Industry Promotion and Self-regulation
- Public Health
- International Exchange
- Multiple Fields (usually grant-making foundations)

**to be discussed**
Some confusing one - plan to mark -> google translate -> discuss/decide together

- `local_aim`
There are cases where the aim/mission of the ONGO is attached to a locality. So I created this dummy to indicate such situation.

- `Index`

Index number larger than 700 are ROs that were active at time of data scraping (Jan. 2022) but have been deregistered as of Oct. 2022.

*Note: RO/ro = representative office of ONGOs

## Data Cleaning

```{r corret data format}
# get rid of extra spaces in the date column
ongo <- ongo_manual |>
  mutate(province_cn = str_sub(address, end = 2)) #province name from address
```

## Code Province Names

Extracting Province List to check the name format and prepare for translation tribble

```{r}
province_list <- ongo |> 
  group_by(province_cn) |> 
  summarise(province_cn = first(province_cn)) |>
  drop_na() |> #de-registered ones
  as.list()
province_list
```

There are totally 29 provinces (including provincial-level cities e.g. Beijing and Shanghai) that have ONGO rep offices.

The maximum number of provinces that a RO can possible operate in is 32.

## Translation Tribbles

```{r}
province_name <- tribble(
  ~province_cn, ~province_en,      ~province_code,
  "北京",      "Beijing",        "BJ",
  "上海",      "Shanghai",       "SH",
  "天津",      "Tianjin",        "TJ",
  "重庆",      "Chongqing",      "CQ",
  "河北",      "Hebei",          "HE",
  "山西",      "Beijing",        "SX",
  "内蒙",      "Inner Mongolia", "NM",
  "辽宁",      "Liaoning",       "LN",
  "吉林",      "Jilin",          "JL",
  "黑龙",      "Heilongjiang",   "HL",
  "江苏",      "Jiangsu",        "JS",
  "浙江",      "Zhejiang",       "ZJ",
  "安徽",      "Anhui",          "AH",
  "福建",      "Fujian",         "FJ",
  "江西",      "Jiangxi",        "JX",
  "山东",      "Shandong",       "SD",
  "河南",      "Henan",          "HA",
  "湖北",      "Hubei",          "HB",
  "湖南",      "Hunan",          "HN",
  "广东",      "Guangdong",      "GD",
  "广西",      "Guangxi",        "GX",
  "海南",      "Hainan",         "HI",
  "四川",      "Sichuan",        "SC",
  "贵州",      "Guizhou",        "GZ",
  "云南",      "Yunnan",         "YN",
  "西藏",      "Tibet",          "XZ",
  "陕西",      "Shaanxi",        "SN",
  "甘肃",      "Gansu",          "GS",
  "青海",      "Qinghai",        "QH",
  "宁夏",      "Ningxia",        "NX",
  "新疆",      "Xinjiang",       "XJ",
  "兵团",      "Bingtuan",       "BT"
)
```

## Adding English province name and clean other variables

```{r}
ongo <- ongo |>
  left_join(province_name, by = "province_cn") |>
  mutate(registration_date = ymd(registration_date), 
         still_active = ifelse(is.na(still_active), TRUE, still_active),
         geo_scope_num = str_count(geo_scope, ",") + 1) |>
  mutate(geo_scope_num = ifelse(geo_scope == "中国境内", # recode "all over China"
                                max(geo_scope_num, na.rm = TRUE), geo_scope_num))
```

```{r}
#a glance at current columns
summary(ongo)
```

## China sf data for fun

(https://github.com/xmc811/mapchina)

```{r}
#devtools::install_github("xmc811/mapchina", ref = "dev")
library(mapchina)
```

```{r message=FALSE, warning=FALSE}
sf_use_s2(FALSE) #https://github.com/xmc811/mapchina/issues/7#issuecomment-1028792066

sf_china <- china |>
        group_by(Name_Province) |>
        summarise(geometry = st_union(geometry)) |> 
        mutate(province_cn = str_sub(Name_Province, end = 2))
```

```{r }
# summerize by province
province_count <- ongo |>
  group_by(province_cn) |>
  summarise(ro_count = n())

mapdata <-sf_china |> 
  left_join(province_count, by = "province_cn") |> 
  mutate(ro_count = ifelse(is.na(ro_count), 0, ro_count))

labeldata <- mapdata |> 
  filter(ro_count>0)
```

```{r fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
plot_map <- ggplot() +
  geom_sf(data = mapdata,
          aes(fill = ro_count), color = "white") +
  scale_fill_viridis_c(option = "mako", begin = 0.1, end = 0.9, direction = -1) +
  geom_sf_label(data = labeldata, aes(label = ro_count), 
                nudge_y = - 0.8 , nudge_x = -0.1, size = 3, alpha = 0.7,) +
  theme_minimal()
plot_map
```

## Other notes

There should be year fixed/random effects because 2017 is the first year of implementation, had a big first wave. 2018-2019 are normal years that ROs could not registered/were not familiar with the new law got registered. 2020 and 2021 are years when international communication was largely impacted by COVID.

`home` and `province` of ROs are very unbalanced, I think that's another reason we want to use Bayesian

## Save data

```{r save cleaned rds}
saveRDS(ongo, here("data","derived_data", "ongo_cleaned.rds"))
```

### 2022-12-05 data-cleanning/data_cleaning_ongo.Rmd
Update data_cleaning_ongo.Rmd

@@
 
+- `psu_level`
+
+Dummy variable indicating whether the official sponsoring unit (for registration and annual audit) is at the national or local level. 
+It is clearly correlated with `geo_scope_num`, but should be a mediating factor for the relationship we are examine.
+
 - `ro_count`
@@
 
-`work_field` is the original mission statement in Chinese. The name "field" is chosen for the moment, because it seems "area" is more easily to be confused with the geographical scope
+`work_field` is the original mission statement in Chinese.
+The name "field" is chosen for the moment, because it seems "area" is more easily to be confused with the geographical scope.
+It is not called "mission" to differentiate from the mission of the mother organization which is not subject to approval of the authority.
+Also, the statement of the work field tends to be more concrete than missions.
+
 `work_field_code1` is the main work field code
@@
 - `local_aim`
-There are cases where the aim/mission of the ONGO is attached to a locality. So I created this dummy to indicate such situation.
+There are cases where the aim/mission of the ONGO is attached to a locality.
+So I created this dummy to indicate such situation.
+*However,* there seems to be some inconsistency in different ONGO's choices whether to use a location name in their work field.
+Also, it might be the case that the location limitation is added as requested by the authority.
+So probably should not use this variable.
 

### 2022-12-15 data-cleanning/data_cleaning_ongo.Rmd
Update data_cleaning_ongo.Rmd

@@
 
+Updated 12/15/2022
+
 ```{r message=FALSE, warning=FALSE}
@@
 library(here)
+library(rvest)
 library(lubridate)
@@
 # manually cleaned Chinese ONGO regulator administrative data
-# ongo_manual_csv <- read_csv(here("data", "manual_data", "ongo-manual-clean.csv"))
+ ongo_manual_csv <- read_csv(here("data", "manual_data", "ongo-manual-clean.csv"))
 ```
@@
 ```{r save rds}
-# saveRDS(ongo_manual_csv, here("data", "manual_data", "ongo_manual.rds"))
+ saveRDS(ongo_manual_csv, here("data", "manual_data", "ongo_manual.rds"))
 ```
@@
 ongo_manual <- readRDS(here("data", "manual_data", "ongo_manual.rds"))
+```
+
+```{r china file}
+# Chinafile data with English org names
+chinafile <- read_html("https://jessicachinafile.github.io/index_RO_table.html") |> 
+  html_element(css = "#filter") |>
+  html_table() |>
+  select(org_name_cn = `Organization Name (Chinese)`,
+         org_name_en = `Organization Name (English)`) |>
+  group_by(org_name_cn) |>
+  slice(1)
 ```
@@
 
+## Work Field Coding notes
+
+**Decided by how the work fields of registered NGOs cluster**
+
+- **[Economy and trade]**
+
+- **[Environment]** (including animal protection)
+
+- **[Education]** (including youth development and international cultural exchange)
+
+- **[Charity and humanitarian]** poverty alleviation, disaster relief, etc., including rural development and social work
+  If rural development is researched at the macroeconomics level, coded as science and technology, eg. #375
+
+- **[Science and technology]**
+
+- **[Industry association]**
+
+- **[Health]** public health and health care system support (professional training)
+
+- **[Arts and Culture]** including sports (noted as “sports” in `work_field_code2`) and international culture exchange
+
+- **[General]** usually grant-making organizations, Or working on general international communication, including among governments, Or working on multiple fields not overlapping
+
+(Chinese background) (ONGOs set up by Chinese communities abroad or by Chinese entities in foreign jurisdictions).
+Such ONGOs tend to have strong local connection with its origins.
+Not sure yet if should be kept as a separate variable.
+Now coded only in work_field_code2.
+(equality)
+Only in `work_field_code2`, aim to right-based Charity and humanitarian and non-right-based Charity and humanitarian orgs
+
+**Coding rules used and notes**
+
+1. Education vs. Charity
+If charitable activities are all education related, e.g. building schools, donating education facilities and books, coded as education
+If the aids provided include other community support, e.g. building bridges, roads, medical facilities, coded as charity
+
+2. Economy and trade vs. Industry association
+If the trade promoted is focused on a particular industry (poultry, grains etc.), coded as industry association
+
+3. Arts and culture vs. education
+Now includes sports organizations too. 
+4. Industry association vs. health, science and technology, arts and culture
+There are professional association on health providers and certain techniques.
+Coded as health, science & technology at the moment because they also conducting activities of promoting certain techniques .
+And their nature of work can be quite different from industry associations on grains, wines, pecans etc.
+The are more of a professional association with specialized expertise.
+Same as arts and culture organizations: e.g., ballet dancer association 
+Exception: specialized association coded as industry associations if only serving the member companies #91
+5. Health vs. Charity 
+If only providing medical aids to underprivileged communities, not building schools etc., coded as health 
+6. Charity vs. General 
+If multiple work, e.g., poverty alleviation, education, health can be encompassed by Charity and humanitarian, then former, or latter (e.g.)
+7. International exchange category is dropped because it is assimilated by other fields, i.e., international exchange in education, arts and culture, science and technology
+8. Limitations: The sample/population only covers those INGOs that got successfully registered
+9. Chinese background, equality and sports are coded in `work_field_code2`, we can derive separate variables for them if needed 
+10. Multiple ROs are coded based on the overall work area spans of the mother organization, not the specific RO, so ensure the work_area is consistent across ROs
+
 ## Data Cleaning
@@
 
-```{r}
+```{r province list}
 province_list <- ongo |> 
@@
 
-```{r}
+```{r province cn to en tribble}
 province_name <- tribble(
@@
 
-## Adding English province name and clean other variables
+### Adding English org name and clean other variables
 
-```{r}
+```{r add data cleanning 1}
 ongo <- ongo |>
@@
   mutate(geo_scope_num = ifelse(geo_scope == "中国境内", # recode "all over China"
-                                max(geo_scope_num, na.rm = TRUE), geo_scope_num))
+                                max(geo_scope_num, na.rm = TRUE), geo_scope_num)) |>
+# reformat ro_name to merge with Chinafile data
+  mutate(org_name_cn = ifelse(province_cn == "内蒙", str_sub(ro_name, end = -7), str_sub(ro_name, end = -6))) |>
+  mutate(org_name_cn = ifelse(home == "South Korea", org_name_cn, str_remove(org_name_cn, "\\（.*\\）"))) |>
+  left_join(chinafile, by = "org_name_cn")
+
+table(is.na(ongo$org_name_en))
+```
+
+### data cleaning 2
+```{r data cleanning 2}
+# Derive local connection variable
+ongo <- ongo |>
+  mutate(cn_background = case_when(work_field_code2 == "Chinese background" ~ 1, 
+                                   TRUE ~ 0),
+         local_aim = ifelse(!is.na(local_aim), 1, 0),
+         local_org_name = ifelse(!is.na(local_org_name), 1, 0),
+         local_connect = ifelse (cn_background + local_aim + local_org_name == 0, FALSE, TRUE))
 ```
@@
 ```
+
+## Toy models
+
+```{r}
+model_simple <- lm(geo_scope_num ~ work_field_code1, data = ongo)
+summary(model_simple)
+```
+
+```{r}
+model_control <- lm(geo_scope_num ~ work_field_code1 + local_connect + psu_level + province_code, data = ongo)
+summary(model_control)
+```
+
+```{r}
+table(ongo$work_field_code1)
+```

### 2023-03-25 index.qmd
Quarto-ify the project

---
title: "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
author:
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@student.gsu.edu
  orcid: 0000-0002-6552-8338
format:
  html:
    code-tools: false
    toc: false
---

## Abstract

Abstract goes here

## Code

All the raw code and data for this paper is available in a [GitHub repository](https://github.com/andrewheiss/compassionate-clam).

### 2023-03-25 manuscript/manuscript.qmd
Quarto-ify the project

---
title: "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
author:
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@student.gsu.edu
  orcid: 0000-0002-6552-8338
bibliography: references.bib
link-citations: true
format: 
  html:
    toc: true
  pdf: default
  docx: default
language: 
  title-block-published: "Latest version"
---

Lorem ipsum dolor sit amet, consectetur adipisicing elit [@Mayer:2010], sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

## References

### 2023-03-25 notebook/clean-data.qmd
Quarto-ify the project

---
title: "Data cleaning"
author: "Meng Ye"
date: "2022-10-07"
---

### 2023-03-25 notebook/manuscript.qmd
Quarto-ify the project

---
title: Manuscript
toc: false
page-layout: full
---

The final manuscript will be downloadable from here. ([See this for a similar example.](https://stats.andrewheiss.com/mountainous-mackerel/analysis/manuscript.html))

### 2023-03-25 presentations/2023-04-16_mpsa/index.qmd
Quarto-ify the project

--- 2022-10-06 manuscript/submissions/2023-mpsa.qmd
@@
 ---
-title: "MPSA 2023 proposal" 
-date: "October 6, 2022"
-author:
-  - name: Andrew Heiss
-    email: aheiss@gsu.edu
-    orcid: 0000-0002-3948-3914
-    affiliations: 
-      - id: ays
-        name: Georgia State University
-        department: Andrew Young School of Policy Studies
-        city: Atlanta
-        region: GA
-    attributes:
-      corresponding: true
-  - name: Meng Ye
-    email: mye2@gsu.edu
-    affiliations:
-      - ref: ays
-format:
-  html: default
-  docx: default
-  pdf: default
+title: "Midwest Political Science Association"
+date: 2023-04-16
+toc: true
+abstract: |
+  Annual conference of the Midwest Political Science Association (MPSA); Chicago
+abstract-title: "Location"
+published-title: "Presented"
+page-layout: full
 ---
 
-# Title
+## Presentation
+
+Slides will be embedded here.
+
+## Proposal
+
+### Title
 
@@
 
-# Brief Overview
+### Brief Overview
 
@@
 
-# Keywords
+### Keywords
 
@@
 
-# Abstract
+### Abstract
 

### 2023-03-25 index.qmd
woohoo got this working with {rbbt}

@@
 author:
+- name: Meng Ye
+  affiliation: Georgia State University
+  email: mye2@student.gsu.edu
+  orcid: 0000-0002-6552-8338
 - name: Andrew Heiss
@@
   orcid: 0000-0002-3948-3914
-- name: Meng Ye
-  affiliation: Georgia State University
-  email: mye2@student.gsu.edu
-  orcid: 0000-0002-6552-8338
 format:

### 2023-03-25 manuscript/manuscript.qmd
woohoo got this working with {rbbt}

@@
   orcid: 0000-0002-3948-3914
-- name: Meng Ye
-  affiliation: Georgia State University
-  email: mye2@student.gsu.edu
-  orcid: 0000-0002-6552-8338
 bibliography: references.bib
@@
 
-Lorem ipsum dolor sit amet, consectetur adipisicing elit [@Mayer:2010], sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Lorem ipsum dolor sit amet, consectetur adipisicing elit [@ChaudhryHeiss:2022], sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
 Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.

### 2023-03-25 data-cleanning/data_cleaning_ongo.Rmd
Update data_cleaning_ongo.Rmd

@@
 
+Kept the above chunks here, expecting there might be changes in the manual coding csv file, especially for the "need check" area coding
+
 ```{r import data from rds}
@@
 For the `still_active` variable, the values are manually input for the blank lines.
-After checking against the offical website, `FALSE` for those have indeed de-register and `TRUE` for those that turned out to be parsing errors.
+After checking against the official website, `FALSE` for those have indeed de-register and `TRUE` for those that turned out to be parsing errors.
 The rest NAs will be recoded to `TRUE` in data cleaning.
@@
 Dummy variable indicating whether the official sponsoring unit (for registration and annual audit) is at the national or local level. 
-It is clearly correlated with `geo_scope_num`, but should be a mediating factor for the relationship we are examine.
+It is clearly correlated with `geo_scope_num`, but should be a mediating factor for the relationship we are examining.
 
@@
 
-A related `multiple_index` is a index number created to identify siblings, in the form of 100-1, 100-2...(starting from 100 to ensure all have three digits) `NA` for ONGOs only having one RO.
+A related `multiple_index` is an index number created to identify siblings, in the form of 100-1, 100-2...(starting from 100 to ensure all have three digits) `NA` for ONGOs only having one RO.
 Note there can be cases where one of the siblings has been de-registered, but only several.
+
+- `local_aim`
+There are cases where the aim/mission of the ONGO is attached to a locality.
+So I created this dummy to indicate such situation.
+*However,* there seems to be some inconsistency in different ONGO's choices whether to use a location name in their work field.
+Also, it might be the case that the location limitation is added as requested by the authority.
+So probably should not use this variable.
+
+- `Index`
+
+Index number larger than 700 are ROs that were active at time of data scraping (Jan. 2022) but have been deregistered as of Oct. 2022.
+
+*Note: RO/ro = representative office of ONGOs
 
@@
 `work_field_code1` is the main work field code
-`work_field_code2` is an alternative code for the work field if the ONGO's works touch on overlapping fields
+`work_field_code2` is an alternative code for the work field if the ONGO's work touches on overlapping fields
 
-The field categories are (planed to be) decided based on Article 3 of the law.
+The field categories listed on Article 3 of the law.
 
@@
 
-**to be discussed**
-Some confusing one - plan to mark -> google translate -> discuss/decide together
-
-- `local_aim`
-There are cases where the aim/mission of the ONGO is attached to a locality.
-So I created this dummy to indicate such situation.
-*However,* there seems to be some inconsistency in different ONGO's choices whether to use a location name in their work field.
-Also, it might be the case that the location limitation is added as requested by the authority.
-So probably should not use this variable.
-
-- `Index`
-
-Index number larger than 700 are ROs that were active at time of data scraping (Jan. 2022) but have been deregistered as of Oct. 2022.
-
-*Note: RO/ro = representative office of ONGOs
+**Cross checking of ONGO work field coding**
+Google translation of the work field statements (disclosed in Chinese) are included.
+Researcher 1 is the main coder of the work field.
+When there is some ambiguity of the coding, Researcher 1 marks "TRUE" in the `coding_need_check` document and Researcher 2 cross check the coding of the work field.
 
@@
 
-**Decided by how the work fields of registered NGOs cluster**
+**Decided by how the work fields of registered NGO ROs cluster**
 
@@
 (equality)
+
 Only in `work_field_code2`, aim to right-based Charity and humanitarian and non-right-based Charity and humanitarian orgs

### 2023-03-28 notebook/clean-data.qmd
Targetify data cleaning

@@
 author: "Meng Ye"
-date: "2022-10-07"
+date: "2023-03-28"
+format:
+  html: 
+    code-fold: show
+language: 
+  title-block-published: "Last updated"
 ---
+
+```{r load-packages-data, message=FALSE, warning=FALSE}
+library(tidyverse)
+library(targets)
+library(here)
+library(lubridate)
+library(sf)
+library(mapchina)
+
+# Point to the _targets folder location since this qmd is in a subfolder
+tar_config_set(store = here::here('_targets'),
+               script = here::here('_targets.R'))
+
+# Load targets
+ongo <- tar_read(ongo)
+```
+
+# Documentation of the pre-processing of scraped data
+
+The inspected raw data is the version derived after inspecting the scraped csv file against the source website.
+The blank lines in the scraped csv file are from ROs^[RO/ro = representative office of ONGOs] that have been de-registered.
+[The website](https://ngo.mps.gov.cn/ngo/portal/toInfogs.do) keep their names in the general list but their profiles are all blank now.
+
+A couple of scraping errors have also been corrected in the process. That is cases where the RO is active but shown as blank rows in the scraped. I manually added those rows back.
+
+For those that already been de-registered, I added back their `index`, `ro_name`, and `ro_id`, and generated a dichotomous indicator that they are no more "active" in the `still_active` column.
+
+For the `still_active` variable, the values are manually input for the blank lines.
+After checking against the official website, `FALSE` for those have indeed de-register and `TRUE` for those that turned out to be parsing errors.
+The rest NAs will be recoded to `TRUE` in data cleaning.
+
+After the cross-checking process, the index number of ROs in our dataset is the same as the index in the official database as of 2022-10-04.
+
+The following columns are also manually coded:
+
+- `home`: home county or region of the ONGO. Not using the name "country" to be flexible enough to denote, Hong Kong, Macau and Taiwan
+
+- `psu_level`: dummy variable indicating whether the official sponsoring unit (for registration and annual audit) is at the national or local level.
+
+  It is clearly correlated with `geo_scope_num`, but should be a mediating factor for the relationship we are examining.
+
+- `ro_count`: There are cases where ONGOs are not granted to operate across China, so they register multiple ROs to cover enough number of provinces where they need to work.
+We surely want to include this variable because it is directly correlated with `geo_scope_num`
+
+  A related `multiple_index` is an index number created to identify siblings, in the form of 100-1, 100-2...(starting from 100 to ensure all have three digits) `NA` for ONGOs only having one RO.
+Note there can be cases where one of the siblings has been de-registered, but only several.
+
+- `local_aim`: There are cases where the aim/mission of the ONGO is attached to a locality.
+So I created this dummy to indicate such situation.
+*However,* there seems to be some inconsistency in different ONGO's choices whether to use a location name in their work field.
+Also, it might be the case that the location limitation is added as requested by the authority.
+So probably should not use this variable.
+
+- `Index`: Index number larger than 700 are ROs that were active at time of data scraping (Jan. 2022) but have been deregistered as of Oct. 2022.
+
+- `work_field`: original mission statement in Chinese.
+The name "field" is chosen for the moment, because it seems "area" is more easily to be confused with the geographical scope.
+It is not called "mission" to differentiate from the mission of the mother organization which is not subject to approval of the authority.
+Also, the statement of the work field tends to be more concrete than missions.
+
+  `work_field_code1` is the main work field code; `work_field_code2` is an alternative code for the work field if the ONGO's work touches on overlapping fields
+
+  The field categories listed on Article 3 of the law.
+
+  > Overseas NGOs may, in accordance with the provisions of this Law, engage in undertakings of benefit to the public in the areas of the economy, education, science, culture, health, sports and environmental protection, as well as in the areas of poverty and disaster relief.
+
+  Earlier fields used:
+
+  - Commerce and Trade Promotion
+  - Science and Technology
+  - Education
+  - Charity and Public Benefit
+  - Environment
+  - Industry Promotion and Self-regulation
+  - Public Health
+  - International Exchange
+  - Multiple Fields (usually grant-making foundations)
+
+# Cross checking of ONGO work field coding
+
+Google translation of the work field statements (disclosed in Chinese) are included.
+Researcher 1 is the main coder of the work field.
+When there is some ambiguity of the coding, Researcher 1 marks "TRUE" in the `coding_need_check` document and Researcher 2 cross check the coding of the work field.
+
+# Work Field coding notes
+
+**Decided by how the work fields of registered NGO ROs cluster**
+
+- **[Economy and trade]**
+
+- **[Environment]** (including animal protection)
+
+- **[Education]** (including youth development and international cultural exchange)
+
+- **[Charity and humanitarian]** poverty alleviation, disaster relief, etc., including rural development and social work
+  If rural development is researched at the macroeconomics level, coded as science and technology, eg. #375
+
+- **[Science and technology]**
+
+- **[Industry association]**
+
+- **[Health]** public health and health care system support (professional training)
+
+- **[Arts and Culture]** including sports (noted as “sports” in `work_field_code2`) and international culture exchange
+
+- **[General]** usually grant-making organizations, Or working on general international communication, including among governments, Or working on multiple fields not overlapping
+
+(Chinese background) (ONGOs set up by Chinese communities abroad or by Chinese entities in foreign jurisdictions).
+Such ONGOs tend to have strong local connection with its origins.
+Not sure yet if should be kept as a separate variable.
+Now coded only in work_field_code2.
+(equality)
+
+Only in `work_field_code2`, aim to right-based Charity and humanitarian and non-right-based Charity and humanitarian orgs
+
+# Coding rules used and notes
+
+1. Education vs. Charity
+
+   If charitable activities are all education related, e.g. building schools, donating education facilities and books, coded as education
+
+   If the aids provided include other community support, e.g. building bridges, roads, medical facilities, coded as charity
+
+2. Economy and trade vs. Industry association
+
+   If the trade promoted is focused on a particular industry (poultry, grains etc.), coded as industry association
+
+3. Arts and culture vs. education
+
+   Now includes sports organizations too.
+
+4. Industry association vs. health, science and technology, arts and culture
+
+   There are professional association on health providers and certain techniques.
+Coded as health, science & technology at the moment because they also conducting activities of promoting certain techniques .
+And their nature of work can be quite different from industry associations on grains, wines, pecans etc.
+The are more of a professional association with specialized expertise.
+
+   Same as arts and culture organizations: e.g., ballet dancer association
+
+   Exception: specialized association coded as industry associations if only serving the member companies #91
+
+5. Health vs. Charity
+
+   If only providing medical aids to underprivileged communities, not building schools etc., coded as health
+
+6. Charity vs. General
+
+   If multiple work, e.g., poverty alleviation, education, health can be encompassed by Charity and humanitarian, then former, or latter (e.g.)
+
+7. International exchange category is dropped because it is assimilated by other fields, i.e., international exchange in education, arts and culture, science and technology
+
+8. Limitations: The sample/population only covers those INGOs that got successfully registered
+
+9. Chinese background, equality and sports are coded in `work_field_code2`, we can derive separate variables for them if needed
+
+10. Multiple ROs are coded based on the overall work area spans of the mother organization, not the specific RO, so ensure the work_area is consistent across ROs
+
+# Clean data
+
+## Province names
+
+```{r province list}
+province_list <- ongo |> 
+  group_by(province_cn) |> 
+  summarise(province_cn = first(province_cn)) |>
+  drop_na() |> #de-registered ones
+  pull(province_cn)
+province_list
+```
+
+There are totally `r length(province_list)` provinces (including provincial-level cities e.g. Beijing and Shanghai) that have ONGO rep offices.
+
+The maximum number of provinces that a RO can possible operate in is 32.
+
+## English organization names
+
+```{r}
+table(is.na(ongo$org_name_en))
+```

### 2023-03-28 R/funs_data.R

@@ -1,0 +1,75 @@
+library(glue)
+library(rvest)
+suppressPackageStartupMessages(library(lubridate))
+
+load_clean_chinafile <- function() {
+  chinafile <- read_html(glue("https://web.archive.org/web/20220922181643/",
+                              "https://jessicachinafile.github.io/index_RO_table.html")) |> 
+    html_element(css = "#filter") |>
+    html_table() |>
+    select(org_name_cn = `Organization Name (Chinese)`,
+           org_name_en = `Organization Name (English)`) |>
+    group_by(org_name_cn) |>
+    slice(1)
+  
+  return(chinafile)
+}
+
+province_cn_to_en <- function() {
+  province_name <- tribble(
+    ~province_cn, ~province_en,      ~province_code,
+    "北京",      "Beijing",        "BJ",
+    "上海",      "Shanghai",       "SH",
+    "天津",      "Tianjin",        "TJ",
+    "重庆",      "Chongqing",      "CQ",
+    "河北",      "Hebei",          "HE",
+    "山西",      "Beijing",        "SX",
+    "内蒙",      "Inner Mongolia", "NM",
+    "辽宁",      "Liaoning",       "LN",
+    "吉林",      "Jilin",          "JL",
+    "黑龙",      "Heilongjiang",   "HL",
+    "江苏",      "Jiangsu",        "JS",
+    "浙江",      "Zhejiang",       "ZJ",
+    "安徽",      "Anhui",          "AH",
+    "福建",      "Fujian",         "FJ",
+    "江西",      "Jiangxi",        "JX",
+    "山东",      "Shandong",       "SD",
+    "河南",      "Henan",          "HA",
+    "湖北",      "Hubei",          "HB",
+    "湖南",      "Hunan",          "HN",
+    "广东",      "Guangdong",      "GD",
+    "广西",      "Guangxi",        "GX",
+    "海南",      "Hainan",         "HI",
+    "四川",      "Sichuan",        "SC",
+    "贵州",      "Guizhou",        "GZ",
+    "云南",      "Yunnan",         "YN",
+    "西藏",      "Tibet",          "XZ",
+    "陕西",      "Shaanxi",        "SN",
+    "甘肃",      "Gansu",          "GS",
+    "青海",      "Qinghai",        "QH",
+    "宁夏",      "Ningxia",        "NX",
+    "新疆",      "Xinjiang",       "XJ",
+    "兵团",      "Bingtuan",       "BT"
+  )
+  
+  return(province_name)
+}
+
+
[…]

### 2023-03-28 _targets.R

@@ -1,0 +1,50 @@
+# Packages required to define the pipeline:
+library(targets)
+library(tarchetypes)
+suppressPackageStartupMessages(library(dplyr))
+
+
+# General options
+options(tidyverse.quiet = TRUE,
+        dplyr.summarise.inform = FALSE)
+
+set.seed(58214)  # From random.org
+
+
+# Global target options
+tar_option_set(
+  packages = c("tibble"),  # Packages available to all targets
+  format = "qs",  # Storage format
+  workspace_on_error = TRUE  # Automatically create a debug workspace on errors
+)
+
+
+# here::here() returns an absolute path, which then gets stored in tar_meta and
+# becomes computer-specific (i.e. /Users/andrew/Research/blah/thing.Rmd).
+# There's no way to get a relative path directly out of here::here(), but
+# fs::path_rel() works fine with it (see
+# https://github.com/r-lib/here/issues/36#issuecomment-530894167)
+here_rel <- function(...) {fs::path_rel(here::here(...))}
+
+
+# Load all the scripts in the R/ folder that contain the functions to be used in
+# the pipeline
+tar_source()
+
+
+# Pipeline ----------------------------------------------------------------
+list(
+  ## Raw data files ----
+  tar_target(ongo_manual_file,
+             here_rel("data", "manual_data", "ongo-manual-clean.csv"),
+             format = "file"),
+  
+  ## Process and clean data ----
+  tar_target(chinafile_clean, load_clean_chinafile()),
+  tar_target(province_name, province_cn_to_en()),
+  tar_target(ongo,
+             clean_ongo_data(ongo_manual_file, chinafile_clean, province_name)),
+  
+  ## Analysis notebook ----
+  tar_quarto(website, path = ".", quiet = FALSE)
+)

### 2023-03-28 notebook/exploratory.qmd
Process map data with a target + make map

---
title: EDA
---

# Map!

```{r load-packages-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(here)
library(sf)

# Point to the _targets folder location since this qmd is in a subfolder
tar_config_set(store = here::here('_targets'),
               script = here::here('_targets.R'))

# Load targets
mapdata <- tar_read(ongo_mapdata)
```

```{r ongo-map, fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
labeldata <- mapdata |> 
  filter(ro_count > 0)

plot_map <- ggplot() +
  geom_sf(data = mapdata,
          aes(fill = ro_count), color = "white") +
  scale_fill_viridis_c(option = "mako", begin = 0.1, end = 0.9, direction = -1) +
  geom_sf_label(data = labeldata, aes(label = ro_count), 
                nudge_y = -0.8 , nudge_x = -0.1, size = 3, alpha = 0.7) +
  theme_void()
plot_map
```

### 2023-03-28 R/funs_data.R

@@ -56,6 +56,34 @@ province_cn_to_en <- function() {
 }
 
 
+clean_map_data <- function(ongo) {
+  suppressPackageStartupMessages(library(sf))
+  suppressPackageStartupMessages(library(mapchina))
+  
+  # Clean up the geographic data
+  suppressMessages({
+    sf_use_s2(FALSE)  # https://github.com/xmc811/mapchina/issues/7#issuecomment-1028792066
+    
+    sf_china <- china |>
+      group_by(Name_Province) |>
+      summarise(geometry = st_union(geometry)) |> 
+      mutate(province_cn = str_sub(Name_Province, end = 2))
+  })
+  
+  # Get a count of ONGOs per province
+  province_count <- ongo |>
+    group_by(province_cn) |>
+    summarise(ro_count = n())
+  
+  # Join ONGO count to map
+  mapdata <- sf_china |> 
+    left_join(province_count, by = "province_cn") |> 
+    mutate(ro_count = ifelse(is.na(ro_count), 0, ro_count))
+  
+  return(mapdata)
+}
+
+
 clean_ongo_data <- function(manual, chinafile, province_name) {
   ongo <- read_csv(manual, show_col_types = FALSE) |>
     mutate(province_cn = str_sub(address, end = 2)) |>   # Province name from address

### 2023-03-28 _targets.R

@@ -44,6 +44,8 @@ list(
   tar_target(province_name, province_cn_to_en()),
   tar_target(ongo,
              clean_ongo_data(ongo_manual_file, chinafile_clean, province_name)),
+  tar_target(ongo_mapdata,
+             clean_map_data(ongo)),
   
   ## Analysis notebook ----
   tar_quarto(website, path = ".", quiet = FALSE)

### 2023-03-28 R/funs_data.R
Add local connection stuff

@@ -96,7 +96,13 @@ clean_ongo_data <- function(manual, chinafile, province_name) {
     # reformat ro_name to merge with Chinafile data
     mutate(org_name_cn = ifelse(province_cn == "内蒙", str_sub(ro_name, end = -7), str_sub(ro_name, end = -6))) |>
     mutate(org_name_cn = ifelse(home == "South Korea", org_name_cn, str_remove(org_name_cn, "\\（.*\\）"))) |>
-    left_join(chinafile, by = "org_name_cn")
+    left_join(chinafile, by = "org_name_cn") |> 
+    # Derive local connection variable
+    mutate(cn_background = case_when(work_field_code2 == "Chinese background" ~ 1, 
+                                     TRUE ~ 0),
+           local_aim = ifelse(!is.na(local_aim), 1, 0),
+           local_org_name = ifelse(!is.na(local_org_name), 1, 0),
+           local_connect = ifelse(cn_background + local_aim + local_org_name == 0, FALSE, TRUE))
   
   return(ongo)
 }

### 2023-03-28 _targets.R

@@ -13,7 +13,7 @@ set.seed(58214)  # From random.org
 
 # Global target options
 tar_option_set(
-  packages = c("tibble"),  # Packages available to all targets
+  packages = c("tidyverse"),  # Packages available to all targets
   format = "qs",  # Storage format
   workspace_on_error = TRUE  # Automatically create a debug workspace on errors
 )

### 2023-04-05 manuscript/manuscript.qmd
Add super initial outline

@@
     toc: true
+    citeproc: false
+    filters: 
+      - "_extensions/andrewheiss/wordcount/citeproc.lua"
+      - "_extensions/andrewheiss/wordcount/wordcount.lua"
   pdf: default
@@
 
-## References
+# Introduction
+
+ONGO law, what has it meant for ONGOs—how are they responding?
+
+@FaridLi:2021
+
+Charity law + ONGO law happened at the same time - lots of discussion about what it would mean for ONGOs at the time - lots of people looked at the framework of the law, but we don't know what it has actually looked like
+Following up with the actual implementation of law
+
+# Context of the ONGO law
+
+How the law works, what it looked like pre-2016/7
+
+# Literature
+
+## Literature on global crackdown on NGOs
+
+Contentiousness, regime stability, other reasons
+
+## Literature on implementation - de jure vs. de facto differences
+
+## Literature on organizational flexibility
+
+# Theory / research questions
+
+- RQ1: Provinces and work field - connects to NGO contentiousness bc everything is noncontentious
+- RQ2: Provinces and PSUs - local vs. national - there's variance in local PSUs - flexibility, venue-seeking maybe
+- RQ3: Provinces and length of time in country / registration date/year - earlier organizations work in more?
+- flexibility bc more local knowledge, more interest, more support from government to get registered, etc.
+
+# Data and methods
+
+No control/pre-group - this is all descriptive about the "after" group of ONGOs that all selected themselves into the regulations
+
+multiple_id - either treat it as a random organization effect for the parent org, or weight it, so if there are 8, we weight by 1/8
+cn_background = Chinese NGOs
+
+Main assumption: We're interested in the potential to be in other provinces, even if an organization is small now, they want to someday spread out
+
+# Results
+
+TODO: Oxfam and World Vision as short case studies?
+
+# Discussion
+
+# References

### 2023-04-06 manuscript/manuscript.qmd
Update manuscript.qmd

@@
 
-Lorem ipsum dolor sit amet, consectetur adipisicing elit [@ChaudhryHeiss:2022], sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+# Abstract:
+
+China’s 2017 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international NGOs (INGOs).
+However, the effects of this global crackdown on INGOs have been difficult to measure since there is often divergence between the formal de jure regulations and the de facto implementation of these laws.
+Additionally, the severity and consistency of the enforcement of these laws often depends on the type of services provided by these organizations.
+In particular, authoritarian regimes display dual and conflicting attitudes towards claim-making (e.g.
+human rights & advocacy) INGOs versus service-providing (e.g.
+humanitarian assistance) INGOs.
+In this paper, we measure the effect of China’s ONGO law on INGO operations in the five years since the passage of the law.
+We test whether and how INGO operational space under the ONGO law is influenced by organizations’ issue areas.
+We argue that service provision INGOs have greater flexibility and are allowed to work in a larger number of provinces than their claim-making counterparts.
+China provides an excellent setting for testing our claim—the 2017 ONGO law regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities.
+We test our argument by analyzing administrative data from 635 registered representative offices of INGOs registered in China between 2017–2021 and test our hypothesis with multilevel Bayesian models.
+Our results speak to the broader literature on closing civic space and provide an empirical illustration of the practical effect of NGO restrictions on global civil society.
+
+# Key words: China ONGO Law, international NGO, civil society, Authoritarianism
 
@@
 
-ONGO law, what has it meant for ONGOs—how are they responding?
+In recent decades, there has been a global tend of “closing space” for civil society across jurisdictions such as Russia, India and Vietnam.(*to add citation*) The manifestation of such trend is rolling up laws that restrictive laws that regulate international NGOs (INGOs).
+[@ChaudhryHeiss:2022;DupuyPrakash:2020] China’s promulgation of the Law of the People’s Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China (the “ONGO Law”) on April 28, 2016 was considered part of a global wave of legal restrictions on INGOs.
+The purpose of this study is to empirically examine how the ONGO law has impacted INGO's presence as well as the operational space after the law took effect.
+By inquiring the de facto implementation of the law in addition to formal de jure regulations, we will be able to see a more comprehensive picture of the operational space for INGOs.
+It will also inform as the evolving theorization of the "closing space" and dual attitudes towards INGOs hold true for an Authoritarian jurisdiction such as China.
+
+ONGO law, what has it meant for ONGOs—how are they responding? [@ChaudhryHeiss:2022]
 
@@
 # Context of the ONGO law
+(to update citations)
 
-How the law works, what it looked like pre-2016/7
+In recent decades, ONGOs came to China after the Reform and Opening-up policy was adopted by the authority and have been playing pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China’s domestic nonprofit sector (Yin, 2009).
+Before the promulgation of the ONGO Law, most ONGOs in China operated outside formal legal rules (Schwartz, 2018).
+The only legal document relevant to ONGOs was a section of the Regulation on the Management of Foundations by the State Council that specifies the registration of representative offices (“ROs”) of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic NGOs.
+However, the actual application of the regulation was very limited.
+Up until the ONGO Law took effect on January 1, 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs according to the Regulation on the Management of Foundations, while some Chinese officials estimated in 2016 that there were roughly over 7000 ONGOs operating in China (Ye & Huang, 2018).
 
-# Literature
+Many ONGOs gained legal identity within mainland China using the vehicle of foreign-funded companies (Sidel, 2016), though there were no clear requirements for them to have a formal legal presence in China (Han, 2011).
+They choose to have a formal legal identity for the convenience such as signing labor contracts directly with employees.
+However, the legal form of foreign-funded company is not quite compatible with the nature of ONGOs.
+Under the Chinese legal system, enterprises should be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms for them — foundations, associations and social service organizations (Ye, 2020).
+As such ONGOs adopting the for-profit legal form of foreign-funded companies were not regulated for their non-profit nature, which can increase the risks of such issues as private benefits, mission drift and conflict of interest for the activities conducted within mainland China before the ONGO Law was passed.
 
-## Literature on global crackdown on NGOs
+The legal framework governing ONGOs was overhauled by the Chinese ONGO Law.
+The new law applies to all Overseas (including Hong Kong, Macau and Taiwan) non-governmental organizations that conduct not-for-profit activities in the fields of Economic Development, Education, Science, Technology, Culture, Public Health, Sports, Environment Protection, Poverty Alleviation, and Disaster Relief etc.
+(Article 3).
+In other words, after the Overseas NGOs became effective, any nonprofit activities conducted by those ONGOs that cannot successfully obtaining proper legal authorization according to the law will be deemed illegal.
+Specifically, the ONGO law stipulates two ways to lawfully conduct nonprofit activities in China for ONGOs: registering ROs and filing information for documentation of temporary activities (TAs) with the Ministry of Public Security (“MPS”) and Provincial-level Public Security bureaus, which are the registering and regulatory authorities designated by the law.
+
+Successfully registering ROs and filing TAs both require the support and participation by Chinese partners in the application process.
+In a sense, they are co-regulating and supervising the ONGOs with Public Security bureaus.
+And it turns out that obtaining the consent of a PSU to apply for registration became a key challenge for ONGOs, because potential PSUs do not have a legal obligation to assume such a demanding role (Jia, 2017; Shieh, 2018; Ye & Huang, 2018).
+The filing of TAs also requires having a Chinese partner organization, which can be one of the four types of entities according to the law – governmental agencies, peoples’ groups (considered by many as GONGOs), public institutions (quasi-governmental entities providing public services including public hospitals and public schools) and social organizations (Chinese official name for nonprofits) (Article 16).
+
+The ONGO Law also sets out various rules for daily operation once the registration of ROs or the filing of TAs is completed.
+Among these regulatory provisions there are some boundaries that ROs and TAs are obliged to abide by.
+For one thing, the registration document of an RO would specify the field of work and mission for the RO and list the range of provinces that the RO is authorized to conduct nonprofit activities in (Article 18).
+Some ROs are authorized to operate across mainland China, which is 32 provincial administrative regions in total, but there are also many that are authorized to operate in one to multiple provinces but not all.
+To compensate such limitation, ONGOs are allowed to register multiple ROs within mainland China at the meantime.
+Moreover, ONGOs that file TAs are also required to comply with the purpose, location and duration of the TA stated in their filing (Article), and the ONGO Law limits the duration of a TA within one year (Article 17).
+To monitor the activities conducted by ONGOs, ROs are required to submit their annual plans by Dec.
+31 in the previous year and their annual reports before Jan 31 of the following year, to PSU first for approval, and then to the Public Security Bureaus that they registered with.
+Also, the ONGOs that file TAs need to conduct the TA using the activity name which was filed with the Public Security Bureaus and are required to file a report with their Chinese partner organizations after the activity is completed (Article 30).
+ROs and TAs of ONGO are not allowed to fundraise within mainland China (Article 21) but can enjoy tax benefits according to relevant laws and regulations (Article 36).
+
+# Literature and Theoretical Background
+
+## Literature on Closing Space for INGOs
 
@@
 
+The promulgation of China’s ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down International NGOs (Chaudhry & Heiss, 2018; Toepler, Zimmer, Fröhlich, & Obuch, 2020).
+Studies on the law has been focused on discussing the historical and political impetus of passing the law (Shieh, 2018) or analyzing the regulatory regimes it that has established and potential implications for ONGOs operating in China (Feng, 2017; Hsu & Teets, 2016).
+However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs’ operations and projects have been affected by the law after successfully gaining legal registration and documentation.
+A couple of studies (Jia, 2017; Ye & Huang, 2018) conducted reflections on the first year’s implementation of China’s ONGO Law, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations.
+However, a more up-to-date and comprehensive understanding of the effects of the ONGO law is still lacking.
+
 ## Literature on implementation - de jure vs. de facto differences
 
-## Literature on organizational flexibility
+## Literature on differenciated attitudes towards INGOs (*maybe merge with literature on implementation*)
+
+"We discuss the role of civil society organizations (CSOs) as agents of democratization and note the emergence of dual, at times apparently conflicting policy postures within authoritarian regimes (restriction and repression for some CSOs vs.
+financial support and opportunities for collaboration for others)." [@ToeplerZimmerFrohlich:2020]
+
+Also, [@Plantan2022]
 
 # Theory / research questions
+
+This aims to examin how the "closing space" hypothesis plays out in China.
+China provides an excellent setting for testing our claim—the 2017 ONGO law regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities.
 
@@
 # Data and methods
+
+The data used in this paper was collected from ONGOs' public registration documents disclosed by MPS’s Overseas NGO Office on the online service platform for ONGOs .
+We also use ChinaFile's China ONGO data for complementary purpose, we merge in the English organization name in ChinaFile for the sake of transparenty of our analysis to broader communities.
 

### 2023-04-06 notebook/analysis-issue.qmd
Create targets for models + preliminary results

---
title: "Issue area"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
                      fig.width = 6, fig.height = (6 * 0.618),
                      out.width = "80%", collapse = TRUE,
                      dev = "png", dev.args = list(type = "cairo-png"))

options(digits = 3, width = 120,
        dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

```{r load-libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(brms)
library(marginaleffects)
library(tidybayes)
library(ggdist)
library(patchwork)
library(scales)

# Generated via random.org
set.seed(196491)

# Load targets
tar_load(ongo)
tar_load(m_full_ordbeta)
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))

prop_to_provinces <- function(x, lower = 1, upper = 32) {
  (x * (upper - lower)) + lower
}
```

```{r generate-preds}
preds <- m_full_ordbeta |> 
  predicted_draws(datagrid(model = m_full_ordbeta, work_field_code1 = unique), 
                  ndraws = 1000)

epreds <- m_full_ordbeta |> 
  epred_draws(datagrid(model = m_full_ordbeta, work_field_code1 = unique), 
              ndraws = 1000)
```

```{r plot-epred-issue}
epreds |> 
  ungroup() |> 
  mutate(work_field_code1 = fct_reorder(work_field_code1, .epred)) |> 
  ggplot(aes(x = .epred, y = work_field_code1)) +
  stat_halfeye(fill = clrs[5]) +
  scale_x_continuous(labels = label_percent(),
                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
                                         name = "Expected provinces",
                                         breaks = seq(8, 32, 4))) +
  guides(fill = "none") +
  labs(x = "Expected proportion of provinces", y = NULL) +
  theme_ongo() +
  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
```

TODO: Prop of 1s, 32s, and in-betweens

### 2023-04-06 notebook/analysis-local.qmd
Create targets for models + preliminary results

--- 2023-04-06 notebook/analysis-issue.qmd
@@
 ---
-title: "Issue area"
+title: "Local connections"
 ---
@@
 preds <- m_full_ordbeta |> 
-  predicted_draws(datagrid(model = m_full_ordbeta, work_field_code1 = unique), 
+  predicted_draws(datagrid(model = m_full_ordbeta, local_connect = unique), 
                   ndraws = 1000)
@@
 epreds <- m_full_ordbeta |> 
-  epred_draws(datagrid(model = m_full_ordbeta, work_field_code1 = unique), 
+  epred_draws(datagrid(model = m_full_ordbeta, local_connect = unique), 
               ndraws = 1000)
@@
 
-```{r plot-epred-issue}
+```{r plot-epred-local}
 epreds |> 
   ungroup() |> 
-  mutate(work_field_code1 = fct_reorder(work_field_code1, .epred)) |> 
-  ggplot(aes(x = .epred, y = work_field_code1)) +
-  stat_halfeye(fill = clrs[5]) +
+  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
+  ggplot(aes(x = .epred, y = local_connect)) +
+  stat_halfeye(fill = clrs[2]) +
   scale_x_continuous(labels = label_percent(),

### 2023-04-06 notebook/analysis-timing.qmd
Create targets for models + preliminary results

--- 2023-04-06 notebook/analysis-issue.qmd
@@
 ---
-title: "Issue area"
+title: "Registration timing"
 ---
@@
 preds <- m_full_ordbeta |> 
-  predicted_draws(datagrid(model = m_full_ordbeta, work_field_code1 = unique), 
+  predicted_draws(datagrid(model = m_full_ordbeta, years_since_law = 0:5), 
                   ndraws = 1000)
@@
 epreds <- m_full_ordbeta |> 
-  epred_draws(datagrid(model = m_full_ordbeta, work_field_code1 = unique), 
+  epred_draws(datagrid(model = m_full_ordbeta, years_since_law = 0:5), 
               ndraws = 1000)
@@
 
-```{r plot-epred-issue}
+```{r plot-epred-timing}
 epreds |> 
-  ungroup() |> 
-  mutate(work_field_code1 = fct_reorder(work_field_code1, .epred)) |> 
-  ggplot(aes(x = .epred, y = work_field_code1)) +
-  stat_halfeye(fill = clrs[5]) +
+  mutate(years_since_law = factor(years_since_law)) |> 
+  ggplot(aes(x = .epred, y = years_since_law)) +
+  stat_halfeye(fill = clrs[7]) +
   scale_x_continuous(labels = label_percent(),
@@
   guides(fill = "none") +
-  labs(x = "Expected proportion of provinces", y = NULL) +
+  labs(x = "Expected proportion of provinces", y = "Years since law took effect in 2017") +
   theme_ongo() +

### 2023-04-06 notebook/analysis.qmd
Create targets for models + preliminary results

---
title: "Questions and expectations"
---

- [**Expectation 1—issue area**](/notebook/analysis-issue.qmd): Because they are seen as less of a threat, ONGOs working on less contentious issues should be registered in more provinces

- [**Expectation 2—local connections**](/notebook/analysis-local.qmd): Because they are explicitly focused on local issues, ONGOs with local connections should be registered in fewer provinces

- [**Expectation 3—registration timing**](/notebook/analysis-timing.qmd): Because formal registration can take a long time and can involve many bureaucratic hurdles, ONGOs that registered soon after the law took effect should be be (1) less of a threat and (2) a higher priority for processing, and so should be registered in more provinces

### 2023-04-06 notebook/exploratory.qmd
Create targets for models + preliminary results

@@
 ---
-
-# Map!
 
@@
 library(sf)
+library(ggrepel)
 
@@
 mapdata <- tar_read(ongo_mapdata)
+invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+set_annotation_fonts()
 ```
 
-```{r ongo-map, fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
+# Timeline of registration
+
+TODO
+
+# Distribution of outcome
+
+TODO
+
+# Map of provinces and counts
+
+```{r ongo-map, fig.height=5, fig.width=7, message=FALSE, warning=FALSE}
+# Use aes(geometry) and stat = "sf_coordinates" to make geom_label_repel() work
+# with geom_sf(): https://github.com/slowkow/ggrepel/issues/111#issuecomment-416853013
 labeldata <- mapdata |> 
@@
           aes(fill = ro_count), color = "white") +
-  scale_fill_viridis_c(option = "mako", begin = 0.1, end = 0.9, direction = -1) +
-  geom_sf_label(data = labeldata, aes(label = ro_count), 
-                nudge_y = -0.8 , nudge_x = -0.1, size = 3, alpha = 0.7) +
+  scale_fill_viridis_c(option = "mako", begin = 0.1, end = 0.9, direction = -1,
+                       guide = "none") +
+  geom_label_repel(data = labeldata, 
+                   aes(label = ro_count, geometry = geometry),
+                   stat = "sf_coordinates",
+                   size = 3) +
   theme_void()

### 2023-04-06 notebook/model-details.qmd
Create targets for models + preliminary results

---
title: Model details
---

TODO: Formal definition and justification for ordered beta instead of ZOIB

TODO: MCMC diagnostics

TODO: Timing

### 2023-04-06 notebook/models.Rmd
Create targets for models + preliminary results

---
title: Models
---

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(brms)
library(tidybayes)
library(scales)
library(targets)

# Point to the _targets folder location since this qmd is in a subfolder
tar_config_set(store = here::here('_targets'),
               script = here::here('_targets.R'))

# Load targets
tar_load(ongo)
tar_load(c(m_basic_zoib, m_basic_ologit))
tar_load(m_full_zoib)

ongo <- ongo %>% 
  mutate(province0 = province_count - 1)

ggplot(ongo, aes(x = province_count)) +
  geom_bar()
```

```{r eval=FALSE}
library(ordbetareg)

m_basic_ordbeta <- ordbetareg(province_count ~ work_field_code1,
                              data = ongo)

m_full_ordbeta <- ordbetareg(
  bf(province_count ~ work_field_code1 + local_connect + local_aim + psu_level + (1 | province_code)),
  data = ongo,
  true_bounds = c(1, 32),
  extra_prior = priors,
  chains = 4
)

priors <- c(prior(student_t(3, 0, 1.5), class = b, coef = "*"))

priors <- set_prior("normal(0,5)",class="b") + 
  prior(constant(0),class="b",coef="Intercept") +
  prior_string("target += normal_lpdf((cutzero + exp(cutone)) - cutzero|0,3) + cutone",check=F) +
  set_prior("exponential(.1)",class="phi")

m_full_ordbeta1 <- brm(
  bf(province_count ~ 0 + Intercept + work_field_code1 + local_connect + local_aim + psu_level + (1 | province_code)),
  data = ongo,
  prior = priors,
  family = ord_beta_reg,
  stanvars=stanvars, backend = "cmdstanr")

prior_summary(m_full_ordbeta)

conditional_effects(m_full_zoib)
conditional_effects(m_full_ordbeta)

modelr::data_grid()

asdf <- m_full_ordbeta %>% 
  epred_draws(newdata = )

get_prior(
  bf(province_count ~ work_field_code1 + local_connect + local_aim + psu_level + (1 | province_code)),
  data = ongo,
  family = "ord_beta_reg"
)

plots <- pp_check_ordbeta(m_full_ordbeta,
                          ndraws = 100,
                          outcome_label = "Provinces")

plots$continuous

pp_check(m_basic_ordbeta, type = "bars")
```

```{r}
pp_check(m_basic_zoib)
pp_check(m_full_zoib)
```

```{r}
pp_check(m_basic_ologit, type = "bars")
```

```{r}
ongo |> 
  modelr::data_grid(work_field_code1 = unique(work_field_code1)) |> 
  add_epred_draws(m_basic_zoib, ndraws = 1000) |> 
  ungroup() |> 
  drop_na(work_field_code1) |> 
  mutate(work_field_code1 = fct_reorder(work_field_code1, .epred)) |> 
  ggplot(aes(y = work_field_code1, x = .epred, fill = work_field_code1)) +
  stat_halfeye() +
  scale_x_continuous(labels = label_percent()) +
  scale_fill_viridis_d(option = "rocket", end = 0.9) +
  guides(fill = "none") +
  labs(x = "Expected proportion of provinces", y = NULL) +
  theme_minimal()
```

### 2023-04-06 R/funs_data.R

@@ -76,7 +76,7 @@ clean_map_data <- function(ongo) {
     summarise(ro_count = n())
   
   # Join ONGO count to map
-  mapdata <- sf_china |> 
+  mapdata <- sf_china |>  
     left_join(province_count, by = "province_cn") |> 
     mutate(ro_count = ifelse(is.na(ro_count), 0, ro_count))
   
@@ -102,7 +102,23 @@ clean_ongo_data <- function(manual, chinafile, province_name) {
                                      TRUE ~ 0),
            local_aim = ifelse(!is.na(local_aim), 1, 0),
            local_org_name = ifelse(!is.na(local_org_name), 1, 0),
-           local_connect = ifelse(cn_background + local_aim + local_org_name == 0, FALSE, TRUE))
+           local_connect = ifelse(cn_background + local_aim + local_org_name == 0, FALSE, TRUE)) |> 
+    # Create different versions of the outcome variable
+    mutate(province_count = geo_scope_num,
+           province_pct = province_count / 32,
+           province_cat = case_when(
+             province_count == 1 ~ "Single province",
+             province_count > 1 & province_count < 32 ~ "Multiple provinces",
+             province_count == 32 ~ "All provinces"
+           )) |> 
+    mutate(province_cat = factor(province_cat, 
+                                 levels = c("Single province", "Multiple provinces", "All provinces"),
+                                 ordered = TRUE)) %>% 
+    mutate(time_since_law_passed = interval(ymd("2017-01-01"), registration_date),
+           days_since_law = time_since_law_passed / days(1),
+           months_since_law = time_since_law_passed / months(1),
+           years_since_law = time_since_law_passed / years(1)) |> 
+    mutate(year_registered = year(registration_date))
   
   return(ongo)
 }

### 2023-04-06 R/funs_graphics.R

@@ -1,0 +1,47 @@
+clrs <- MetBrewer::met.brewer("Tam")
+
+set_annotation_fonts <- function() {
+  ggplot2::update_geom_defaults("label", list(family = "IBM Plex Sans Condensed", face = "plain"))
+  ggplot2::update_geom_defaults("text", list(family = "IBM Plex Sans Condensed", face = "plain"))
+}
+
+theme_ongo <- function(base_size = 11, base_family = "IBM Plex Sans Condensed", prior = FALSE) {
+  ret <- theme_bw(base_size, base_family) +
+    theme(panel.background = element_rect(fill = "#ffffff", colour = NA),
+          title = element_text(size = rel(1), family = "IBM Plex Sans Condensed", face = "bold"),
+          plot.subtitle = element_text(size = rel(0.8),
+                                       family = "IBM Plex Sans Condensed", face = "plain"),
+          plot.caption = element_text(margin = margin(t = 10), size = rel(0.6),
+                                      family = "IBM Plex Sans Condensed", face = "plain"),
+          panel.border = element_rect(color = "grey50", fill = NA, linewidth = 0.15),
+          panel.spacing = unit(1, "lines"),
+          panel.grid.minor = element_blank(),
+          panel.grid.major = element_line(linewidth = 0.25, colour = "grey90"),
+          axis.line = element_blank(),
+          axis.ticks = element_blank(),
+          axis.title = element_text(size = rel(0.8),
+                                    family = "IBM Plex Sans Condensed", face = "bold"),
+          axis.title.x = element_text(hjust = 0, margin = margin(t = 10)),
+          axis.title.y = element_text(hjust = 1, margin = margin(r = 10)),
+          legend.position = "bottom",
+          legend.title = element_text(size = rel(0.7), vjust = 0.5,
+                                      family = "IBM Plex Sans Condensed", face = "plain"),
+          legend.key.size = unit(0.7, "line"),
+          legend.key = element_blank(),
+          legend.spacing = unit(0.1, "lines"),
+          legend.justification = "left",
+          legend.margin = margin(t = -5, b = 0, l = 0, r = 0),
+          strip.text = element_text(size = rel(0.9), hjust = 0,
+                                    family = "IBM Plex Sans Condensed", face = "bold"),
+          strip.background = element_rect(fill = "white", colour = NA))
+  
+  if (prior) {
+    ret <- ret +
+      theme(panel.grid.major = element_blank(),
[…]

### 2023-04-06 R/funs_models.R

@@ -1,0 +1,86 @@
+# Model definitions
+f_basic_zoib <- function(data) {
+  BAYES_SEED <- 102819  # From random.org
+  
+  zoib_priors <- c(prior(student_t(1, 0, 3), class = Intercept),
+                   prior(student_t(1, 0, 3), class = b),
+                   prior(student_t(1, 0, 3), class = b, dpar = zoi))
+  
+  model <- brm(
+    bf(
+      # mu: mean of the 0-1 values; logit scale
+      province_pct ~ work_field_code1,
+      # zoi: zero-or-one-inflated part; logit scale
+      zoi ~ work_field_code1,
+      # coi: one-inflated part, conditional on the 0s; logit scale
+      #   This is set to a fixed 1 because there are no zeros; this effectively
+      #   makes a one-inflated beta regression
+      coi = 1), 
+    data = data,
+    family = zero_one_inflated_beta(), 
+    prior = zoib_priors,
+    seed = BAYES_SEED)
+  
+  return(model)
+}
+
+f_basic_ologit <- function(data) {
+  BAYES_SEED <- 659022  # From random.org
+  
+  ologit_priors <- c(prior(student_t(1, 0, 3), class = Intercept),
+                     prior(student_t(1, 0, 3), class = b))
+  
+  model <- brm(
+    bf(
+      province_cat ~ work_field_code1
+    ), 
+    data = data,
+    family = cumulative(), 
+    prior = ologit_priors,
+    seed = BAYES_SEED)
+  
+  return(model)
+}
+
+
+f_full_zoib <- function(data) {
+  BAYES_SEED <- 102819  # From random.org
+  
+  zoib_priors <- c(prior(student_t(1, 0, 3), class = Intercept),
+                   prior(student_t(1, 0, 3), class = b),
+                   prior(student_t(1, 0, 3), class = b, dpar = zoi))
+  
+  model <- brm(
+    bf(
+      # mu: mean of the 0-1 values; logit scale
+      province_pct ~ work_field_code1 + local_connect + local_aim + psu_level + (1 | province_code),
+      # zoi: zero-or-one-inflated part; logit scale
+      zoi ~ work_field_code1 + local_connect + local_aim + psu_level + (1 | province_code),
+      # coi: one-inflated part, conditional on the 0s; logit scale
+      #   This is set to a fixed 1 because there are no zeros; this effectively
[…]

### 2023-04-06 _targets.R

@@ -8,6 +8,12 @@ suppressPackageStartupMessages(library(dplyr))
 options(tidyverse.quiet = TRUE,
         dplyr.summarise.inform = FALSE)
 
+# Bayes stuff
+suppressPackageStartupMessages(library(brms))
+options(mc.cores = 4,
+        brms.backend = "cmdstanr",
+        brms.threads = 2)
+
 set.seed(58214)  # From random.org
 
 
@@ -39,6 +45,9 @@ list(
              here_rel("data", "manual_data", "ongo-manual-clean.csv"),
              format = "file"),
   
+  ## Graphics ----
+  tar_target(graphic_functions, lst(theme_ongo, set_annotation_fonts, clrs)),
+
   ## Process and clean data ----
   tar_target(chinafile_clean, load_clean_chinafile()),
   tar_target(province_name, province_cn_to_en()),
@@ -46,6 +55,13 @@ list(
              clean_ongo_data(ongo_manual_file, chinafile_clean, province_name)),
   tar_target(ongo_mapdata,
              clean_map_data(ongo)),
+  
+  ## Models ----
+  tar_target(m_basic_zoib, f_basic_zoib(ongo)),
+  tar_target(m_basic_ologit, f_basic_ologit(ongo)),
+  
+  tar_target(m_full_zoib, f_full_zoib(ongo)),
+  tar_target(m_full_ordbeta, f_full_ordbeta(ongo)),
   
   ## Analysis notebook ----
   tar_quarto(website, path = ".", quiet = FALSE)

### 2023-04-06 notebook/exploratory.qmd
Add custom pp_check for ordbetareg

@@
 # Load targets
+tar_load(ongo)
 mapdata <- tar_read(ongo_mapdata)
@@
 
-TODO
+```{r province-count-distribution, warning=FALSE}
+ggplot(ongo, aes(x = province_count)) +
+  geom_histogram(binwidth = 1, color = "white", size = 0.1, boundary = 0) +
+  labs(x = "Number of provinces", y = "Count",
+       title = "Distribution of province counts") +
+  theme_ongo()
+```
 

### 2023-04-06 notebook/model-details.qmd
Add custom pp_check for ordbetareg

@@
 
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
+                      fig.width = 6, fig.height = (6 * 0.618),
+                      out.width = "80%", collapse = TRUE,
+                      dev = "png", dev.args = list(type = "cairo-png"))
+
+options(digits = 3, width = 120,
+        dplyr.summarise.inform = FALSE,
+        knitr.kable.NA = "")
+```
+
+```{r load-libraries, warning=FALSE, message=FALSE}
+library(tidyverse)
+library(targets)
+library(brms)
+library(marginaleffects)
+library(tidybayes)
+library(ggdist)
+library(patchwork)
+library(scales)
+
+# Generated via random.org
+set.seed(196491)
+
+# Load targets
+tar_load(ongo)
+tar_load(m_full_ordbeta)
+invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+
+prop_to_provinces <- function(x, lower = 1, upper = 32) {
+  (x * (upper - lower)) + lower
+}
+```
+
 TODO: Formal definition and justification for ordered beta instead of ZOIB
+
+```{r build-posterior-preds}
+full_posterior <- predicted_draws(m_full_ordbeta, 
+                                  newdata = m_full_ordbeta$data, 
+                                  ndraws = 100)
+
+posterior_categories <- full_posterior %>% 
+  ungroup() %>% 
+  mutate(outcome = case_when(
+    .prediction == 0 ~ "1",
+    .prediction > 0 & .prediction < 1 ~ "1–32",
+    .prediction == 1 ~ "32"
+  )) %>% 
+  group_by(outcome, .draw) %>% 
+  summarize(count = n()) %>% 
+  ungroup()
+
+actual_counts <- m_full_ordbeta$data |> 
+  mutate(outcome = case_when(
+    province_count == 0 ~ "1",
+    province_count > 0 & province_count < 1 ~ "1–32",
+    province_count == 1 ~ "32"
+  )) |> 
+  group_by(outcome) |> 
+  summarize(count = n())
+
+plot_categories <- posterior_categories %>% 
+  ggplot(aes(x = outcome, y = count)) +
+  geom_col(data = actual_counts, fill = "grey70") +
+  stat_pointinterval() +
+  labs(x = NULL, y = "Observed and predicted counts",
+       title = "Posterior predictions of discrete and continuous outcomes") +
+  coord_cartesian(ylim = c(0, 300)) +
+  theme_ongo()
+
+actual_middle <- m_full_ordbeta$data |> 
+  filter(province_count > 0 & province_count < 1) |> 
+  mutate(province_count = prop_to_provinces(province_count))
+
+plot_continuous <- full_posterior |> 
+  mutate(.prediction = prop_to_provinces(.prediction)) |> 
+  filter(.prediction > 1 & .prediction < 32) |> 
+  ggplot(aes(x = .prediction, group = .draw)) +
+  geom_density(linewidth = 0.05, bounds = c(1, 32)) +
+  geom_density(data = actual_middle, aes(x = province_count),
+               inherit.aes = FALSE, bounds = c(1, 32)) +
+  labs(x = "Discrete and continuous predicted outcomes",
+       y = "Probability density") +
+  theme_ongo()
+```
+
+```{r combined-posterior-preds, fig.width=6, fig.height=5}
+arrow_part <- ggplot() +
+  annotate(geom = "segment", x = 0.35, xend = 0.65, y = 0.9, yend = 0.9) +
+  annotate(geom = "segment", x = 0.5, xend = 0.5, y = 0.9, yend = 0.1,
+           arrow = arrow(angle = 30, type = "closed", length = unit(0.1, "inches"))) +
+  scale_x_continuous(limits = c(0, 1)) +
+  theme_void()
+
+plot_categories / arrow_part / plot_continuous +
+  plot_layout(heights = c(0.45, 0.1, 0.45))
+```
+
+```{r}
+# ordbetareg's built-in way, just to check
+# pp_check_ordbeta(m_full_ordbeta, ndraws = 100)
+```
 

### 2023-04-06 deploy.sh

@@ -1,0 +1,7 @@
+REMOTE_HOST="cloud"
+REMOTE_DIR="~/sites/stats/public_html/compassionate-clam"
+REMOTE_DEST=$REMOTE_HOST:$REMOTE_DIR
+
+echo "Uploading new changes to remote server..."
+echo
+rsync -crvP --exclude '*_cache' --delete _site/ $REMOTE_DEST

### 2023-04-07 data-cleanning/data_cleaning_ongo.Rmd
Update data_cleaning_ongo.Rmd
Plot discrete and continuous predictions across groups

@@
 
-Updated 12/15/2022
+Updated 03/24/2023
 
@@
 ```{r}
-model_control <- lm(geo_scope_num ~ work_field_code1 + local_connect + psu_level + province_code, data = ongo)
+model_control <- lm(geo_scope_num ~ work_field_code1 + local_connect + local_aim + psu_level + province_code, data = ongo)
 summary(model_control)

### 2023-04-07 notebook/analysis-local.qmd
Plot discrete and continuous predictions across groups

@@
 
-TODO: Prop of 1s, 32s, and in-betweens
+```{r plot-pred-discrete-continuous-local, message=FALSE}
+preds_local_plot <- preds %>% 
+  ungroup() %>% 
+  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
+  mutate(outcome = case_when(
+    .prediction == 0 ~ "1 province",
+    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
+    .prediction == 1 ~ "32 provinces"
+  )) %>% 
+  group_by(outcome, local_connect) %>% 
+  summarize(count = n()) |> 
+  group_by(local_connect) |> 
+  mutate(prop = count / sum(count))
+
+ggplot(preds_local_plot, aes(x = local_connect, y = prop)) +
+  geom_segment(aes(xend = local_connect, yend = 0), color = "grey50") +
+  geom_point(color = clrs[2], size = 2) +
+  expand_limits(y = 0) +
+  facet_wrap(vars(outcome)) +
+  scale_x_discrete(labels = label_wrap(10)) +
+  scale_y_continuous(labels = label_percent()) +
+  labs(x = NULL, y = "Proportion of predictions") +
+  theme_ongo()
+```

### 2023-04-07 manuscript/manuscript.qmd
Updated MS and BibTex

@@
 
-In recent decades, there has been a global tend of “closing space” for civil society across jurisdictions such as Russia, India and Vietnam.(*to add citation*) The manifestation of such trend is rolling up laws that restrictive laws that regulate international NGOs (INGOs).
-[@ChaudhryHeiss:2022;DupuyPrakash:2020] China’s promulgation of the Law of the People’s Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China (the “ONGO Law”) on April 28, 2016 was considered part of a global wave of legal restrictions on INGOs.
+In recent decades, there has been a global tend of “closing space” for civil society across jurisdictions such as Russia, India and Vietnam.[@DupuyPrakash:2020;@ChaudhryHeiss:] (*to add citation*) The manifestation of such trend is rolling up laws that restrictive laws that regulate international NGOs (INGOs).[@DupuyPrakash:2020; @ChaudhryHeiss:2022] China’s promulgation of the Law of the People’s Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China (the “ONGO Law”) on April 28, 2016 was considered part of a global wave of legal restrictions on INGOs.
 The purpose of this study is to empirically examine how the ONGO law has impacted INGO's presence as well as the operational space after the law took effect.
-By inquiring the de facto implementation of the law in addition to formal de jure regulations, we will be able to see a more comprehensive picture of the operational space for INGOs.
+By inquiring the *de facto* implementation of the law in addition to formal *de jure* regulations, we will be able to see a more comprehensive picture of the operational space for INGOs.
 It will also inform as the evolving theorization of the "closing space" and dual attitudes towards INGOs hold true for an Authoritarian jurisdiction such as China.
@@
 # Context of the ONGO law
-(to update citations)
 
-In recent decades, ONGOs came to China after the Reform and Opening-up policy was adopted by the authority and have been playing pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China’s domestic nonprofit sector (Yin, 2009).
-Before the promulgation of the ONGO Law, most ONGOs in China operated outside formal legal rules (Schwartz, 2018).
+In recent decades, ONGOs came to China after the Reform and Opening-up policy was adopted by the authority and have been playing pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China’s domestic nonprofit sector [@Yin:2009].
+Before the promulgation of the ONGO Law, the regulation of ONGOs in China was obscure [Shieh:2018].
 The only legal document relevant to ONGOs was a section of the Regulation on the Management of Foundations by the State Council that specifies the registration of representative offices (“ROs”) of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic NGOs.
 However, the actual application of the regulation was very limited.
-Up until the ONGO Law took effect on January 1, 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs according to the Regulation on the Management of Foundations, while some Chinese officials estimated in 2016 that there were roughly over 7000 ONGOs operating in China (Ye & Huang, 2018).
+Up until the ONGO Law took effect on January 1, 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs according to the Regulation on the Management of Foundations, while some Chinese officials estimated in 2016 that there were roughly over 7000 ONGOs operating in China [@YeHuang:2018].
 
-Many ONGOs gained legal identity within mainland China using the vehicle of foreign-funded companies (Sidel, 2016), though there were no clear requirements for them to have a formal legal presence in China (Han, 2011).
+Many ONGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [@sidel:2016], though there were no clear requirements for them to have a formal legal presence in China[@Han:2011].
 They choose to have a formal legal identity for the convenience such as signing labor contracts directly with employees.
 However, the legal form of foreign-funded company is not quite compatible with the nature of ONGOs.
-Under the Chinese legal system, enterprises should be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms for them — foundations, associations and social service organizations (Ye, 2020).
-As such ONGOs adopting the for-profit legal form of foreign-funded companies were not regulated for their non-profit nature, which can increase the risks of such issues as private benefits, mission drift and conflict of interest for the activities conducted within mainland China before the ONGO Law was passed.
+Under the Chinese legal system, enterprises should be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms for them — foundations, associations and social service organizations [@Ye:2021].
+Thus, ONGOs obtaining legal identity in this way have to navigate through a legal framework designed for the for-profit institutional logic, e.g, focusing on project investers' right to investment return.
 
@@
 In other words, after the Overseas NGOs became effective, any nonprofit activities conducted by those ONGOs that cannot successfully obtaining proper legal authorization according to the law will be deemed illegal.
-Specifically, the ONGO law stipulates two ways to lawfully conduct nonprofit activities in China for ONGOs: registering ROs and filing information for documentation of temporary activities (TAs) with the Ministry of Public Security (“MPS”) and Provincial-level Public Security bureaus, which are the registering and regulatory authorities designated by the law.
+Specifically, the ONGO law stipulates two ways to lawfully conduct nonprofit activities in China for ONGOs: registering ROs or filing information for documentation of temporary activities with the Ministry of Public Security (“MPS”) and Provincial-level Public Security bureaus, which are the registering and regulatory authority for ONGOs designated by the law.
+Registering an RO would be lawful identity gaining channel for INGOs seeking for on-going presence in China while temporary activities are suitable for INGOs that need to coduct one-off programs that last no longer than one year.
 
-Successfully registering ROs and filing TAs both require the support and participation by Chinese partners in the application process.
-In a sense, they are co-regulating and supervising the ONGOs with Public Security bureaus.
-And it turns out that obtaining the consent of a PSU to apply for registration became a key challenge for ONGOs, because potential PSUs do not have a legal obligation to assume such a demanding role (Jia, 2017; Shieh, 2018; Ye & Huang, 2018).
-The filing of TAs also requires having a Chinese partner organization, which can be one of the four types of entities according to the law – governmental agencies, peoples’ groups (considered by many as GONGOs), public institutions (quasi-governmental entities providing public services including public hospitals and public schools) and social organizations (Chinese official name for nonprofits) (Article 16).
+This paper will study the the empirical data of the registration of ROs in the years following the enactment of the ONGO Law to uncover the association between ONGO issue areas and the composition of successful RO registration and the operational space granted.
 
-The ONGO Law also sets out various rules for daily operation once the registration of ROs or the filing of TAs is completed.
-Among these regulatory provisions there are some boundaries that ROs and TAs are obliged to abide by.
-For one thing, the registration document of an RO would specify the field of work and mission for the RO and list the range of provinces that the RO is authorized to conduct nonprofit activities in (Article 18).
+Registering RO under the ONGO Law requiring the consent of a Chinese professional sponsoring unit (the "PSU"), which are governmental or quasi-governmental overseeing the INGO's issue area to co-supervise the INGOs with Public Security bureaus.
+And it turns out that obtaining the consent of a PSU to apply for registration became a key challenge for ONGOs, because potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018].
+Therefore, the composition of the successfully registered RO inform us whether ROs working on different issue areas have varied level of difficulty in obtaining legal status.
+Moreover, We measure the later with a proxy of the number of provinces that the ROs are authorized to operate.
+Specifically, the registration document of an RO would specify the field of work and mission for the RO and list the range of provinces that the RO is authorized to conduct nonprofit activities in (Article 18).
 Some ROs are authorized to operate across mainland China, which is 32 provincial administrative regions in total, but there are also many that are authorized to operate in one to multiple provinces but not all.
-To compensate such limitation, ONGOs are allowed to register multiple ROs within mainland China at the meantime.
-Moreover, ONGOs that file TAs are also required to comply with the purpose, location and duration of the TA stated in their filing (Article), and the ONGO Law limits the duration of a TA within one year (Article 17).
-To monitor the activities conducted by ONGOs, ROs are required to submit their annual plans by Dec.
-31 in the previous year and their annual reports before Jan 31 of the following year, to PSU first for approval, and then to the Public Security Bureaus that they registered with.
-Also, the ONGOs that file TAs need to conduct the TA using the activity name which was filed with the Public Security Bureaus and are required to file a report with their Chinese partner organizations after the activity is completed (Article 30).
-ROs and TAs of ONGO are not allowed to fundraise within mainland China (Article 21) but can enjoy tax benefits according to relevant laws and regulations (Article 36).
 
@@
 
-The data used in this paper was collected from ONGOs' public registration documents disclosed by MPS’s Overseas NGO Office on the online service platform for ONGOs .
-We also use ChinaFile's China ONGO data for complementary purpose, we merge in the English organization name in ChinaFile for the sake of transparenty of our analysis to broader communities.
+## Data
+
+The data used in this paper was collected from INGOs' public registration documents disclosed by MPS’s Overseas NGO Office on the online service platform for INGOs.
+We also use ChinaFile's China ONGO data for complementary purpose, we merge in the English organization name in ChinaFile for the sake of transparency of our analysis to broader communities.
+The data we collected spans from January 1, 2017, when the law took effect, to December 31, 2021, with data for 633 ROs in total.
+The filing document of ROs disclose the name, the registration date, the registration authority (which public security bureau regulates it), the PSU, the address and issue area or purposes of the RO and the specific provinces they can work in.
+We code the variables we use in the empirical analysis from the registration information.
+Most of the coding and data cleaning work is objective data wrangling process, such as parsing out the province each RO is in from the address, or calculating the total number provinces approved in the registration document.
+Meanwhile, the coding of issue areas are conducted by the authors based on the areas set out Article 3 (specified above) and clustering of the issue areas of the actually registered ROs.
+(to cross-validate among authors).
+
+## Measurement
+
+### Dependent Variables
+
+- `geo_scope_num`
+
+Count of the number of provinces each RO is authorized to operate in
+
+### Independent Variables
+
+- `work_field`
+
+`work_field` is the original mission statement in Chinese.
+The name "field" is chosen for the moment, because it seems "area" is more easily to be confused with the geographical scope.
+It is not called "mission" to differentiate from the mission of the mother organization which is not subject to approval of the authority.
+Also, the statement of the work field tends to be more concrete than missions.
+
+`work_field_code1` is the main work field code
+
+## Work Field Coding notes
+
+**Decided by how the work fields of registered NGO ROs cluster**
+
+- **[Economy and trade]**
+
+- **[Environment]** (including animal protection)
+
+- **[Education]** (including youth development and international cultural exchange)
+
+- **[Charity and humanitarian]** poverty alleviation, disaster relief, etc., including rural development and social work
+  If rural development is researched at the macroeconomics level, coded as science and technology, eg. #375
+
+- **[Science and technology]**
+
+- **[Industry association]**
+
+- **[Health]** public health and health care system support (professional training)
+
+- **[Arts and Culture]** including sports (noted as “sports” in `work_field_code2`) and international culture exchange
+
+- **[General]** usually grant-making organizations, Or working on general international communication, including among governments, Or working on multiple fields not overlapping
+
+- `time_elapsed`
+
+to add
+
+### Control Variables
+
+- `still_active`, `FALSE` for those have indeed de-register and `TRUE` otherwise.
+
+- `home`
+
+home county or region of the ONGO. Not using the name "country" to be flexible enough to denote, Hong Kong, Macau and Taiwan
+
+- `psu_level`
+
+Dummy variable indicating whether the official sponsoring unit (for registration and annual audit) is at the national or local level. 
+It is clearly correlated with `geo_scope_num`, but should be a mediating factor for the relationship we are examining.
+
+- `ro_count`
+
+There are cases where ONGOs are not granted to operate across China, so they register multiple ROs to cover enough number of provinces where they need to work.
+
+- `local_connect`
+There are cases where the aim/mission of the ONGO is attached to a locality, either having a county/city name in their RO name or purposes, or the INGO are actually set up by people in China and they RO to communicate between the "hometown" and the INGO
+
+*Notes to delete:*
 
@@
 cn_background = Chinese NGOs
+To compensate such limitation, ONGOs are allowed to register multiple ROs within mainland China at the meantime.
 
@@
 
+## Regression Model
+
+We use
+
 # Results
 
-TODO: Oxfam and World Vision as short case studies?
+## Descriptive Results
+
+## Regression Results
 

### 2023-04-07 notebook/analysis-issue.qmd

@@
   predicted_draws(datagrid(model = m_full_ordbeta, work_field_code1 = unique), 
-                  ndraws = 1000)
+                  ndraws = 4000)
 
@@
 
-TODO: Prop of 1s, 32s, and in-betweens
+```{r plot-pred-discrete-continuous-local, message=FALSE, fig.width=6, fig.height=6}
+preds_issue_plot <- preds %>% 
+  ungroup() %>% 
+  mutate(outcome = case_when(
+    .prediction == 0 ~ "1 province",
+    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
+    .prediction == 1 ~ "32 provinces"
+  )) %>% 
+  group_by(outcome, work_field_code1) %>% 
+  summarize(count = n()) |> 
+  group_by(work_field_code1) |> 
+  mutate(prop = count / sum(count))
+
+ggplot(preds_issue_plot, aes(x = work_field_code1, y = prop)) +
+  geom_segment(aes(xend = work_field_code1, yend = 0), color = "grey50") +
+  geom_point(color = clrs[5], size = 2) +
+  expand_limits(y = 0) +
+  facet_wrap(vars(outcome), ncol = 1) +
+  scale_x_discrete(labels = label_wrap(10)) +
+  scale_y_continuous(labels = label_percent()) +
+  labs(x = NULL, y = "Proportion of predictions") +
+  theme_ongo()
+```

### 2023-04-07 notebook/analysis-timing.qmd

@@
 
-TODO: Prop of 1s, 32s, and in-betweens
+```{r plot-epred-timing-lineribbon}
+epreds %>% 
+  ggplot(aes(x = years_since_law, y = .epred)) +
+  scale_x_reverse() +
+  scale_y_continuous(labels = label_percent(),
+                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
+                                         name = "Expected provinces")) +
+  labs(x = "Years since law took effect (2017)", 
+       y = "Expected proportion of provinces") +
+  stat_lineribbon(alpha = 0.35, fill = clrs[7], color = clrs[7]) +
+  theme_ongo() +
+  theme(axis.title.y.right = element_text(hjust = 1, margin = margin(l = 10), angle = 90))
+```
+
+```{r plot-pred-discrete-continuous-timing, message=FALSE}
+preds_timing_plot <- preds %>% 
+  ungroup() %>% 
+  mutate(outcome = case_when(
+    .prediction == 0 ~ "1 province",
+    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
+    .prediction == 1 ~ "32 provinces"
+  )) %>% 
+  group_by(outcome, years_since_law) %>% 
+  summarize(count = n()) |> 
+  group_by(years_since_law) |> 
+  mutate(prop = count / sum(count))
+
+ggplot(preds_timing_plot, aes(x = years_since_law, y = prop)) +
+  geom_point() +
+  geom_smooth(method = "lm", se = FALSE, color = clrs[7]) +
+  expand_limits(y = 0) +
+  facet_wrap(vars(outcome)) +
+  scale_x_reverse(breaks = c(0:5)) +
+  scale_y_continuous(labels = label_percent()) +
+  labs(x = "Years since law took effect (2017)", 
+       y = "Proportion of predictions") +
+  theme_ongo()
+```

### 2023-04-07 manuscript/manuscript.qmd
Move abstract and keywords to metadata

@@
 title: "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
+date: "2023-04-07"
 author:
@@
   orcid: 0000-0002-3948-3914
-bibliography: references.bib
-link-citations: true
-format: 
-  html:
-    toc: true
-    citeproc: false
-    filters: 
-      - "_extensions/andrewheiss/wordcount/citeproc.lua"
-      - "_extensions/andrewheiss/wordcount/wordcount.lua"
-  pdf: default
-  docx: default
-language: 
-  title-block-published: "Latest version"
----
-
-# Abstract:
-
+abstract: |
   China’s 2017 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international NGOs (INGOs).
@@
 Our results speak to the broader literature on closing civic space and provide an empirical illustration of the practical effect of NGO restrictions on global civil society.
-
-# Key words: China ONGO Law, international NGO, civil society, Authoritarianism
-
-# Introduction
+keywords:
+  - international NGOs
+  - civil society
+  - authoritarianism
+  - Chinese ONGO law
+bibliography: references.bib
+link-citations: true
+---
 

### 2023-04-07 notebook/manuscript.qmd
Add embedded manuscript to manuscript page

@@
 
-The final manuscript will be downloadable from here. ([See this for a similar example.](https://stats.andrewheiss.com/mountainous-mackerel/analysis/manuscript.html))
+```{r include=FALSE}
+# Add the manuscript target as a dependency to the overall website
+# targets::tar_load(c(manuscript_nice, manuscript_manuscripty))
+```
+
+```{=html}
+<p class="text-center">
+  <a class="btn btn-success btn-sm mb-1" href="/manuscript/output/manuscript.html" target="manuscript">
+  <i class="fa-solid fa-file-lines"></i> &ensp;HTML
+  </a>
+
+  <a class="btn btn-success btn-sm mb-1" href="/manuscript/output/manuscript.html" target="_blank">
+  <i class="fa-solid fa-arrow-up-right-from-square"></i>&ensp;HTML <small>(new window)</small>
+  </a>
+
+  <a class="btn btn-danger btn-sm mb-1" href="/manuscript/output/manuscript.pdf" target="manuscript">
+  <i class="fa-solid fa-file-pdf"></i>&ensp;PDF
+  </a>
+
+  <a class="btn btn-danger btn-sm mb-1" target="_blank" href="/manuscript/output/manuscript.pdf">
+  <i class="fa-solid fa-file-arrow-down"></i>&ensp;PDF <small>(download)</small>
+  </a>
+
+  <a class="btn btn-warning btn-sm mb-1" href="/manuscript/output-ms/manuscript-ms.pdf" target="manuscript">
+  <i class="fa-solid fa-file-pdf"></i>&ensp;Manuscripty PDF
+  </a>
+
+  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/manuscript/output-ms/manuscript-ms.pdf">
+  <i class="fa-solid fa-file-arrow-down"></i>&ensp;Manuscripty PDF <small>(download)</small>
+  </a>
+</p>
+
+<iframe src="/manuscript/output/manuscript.html" frameborder="0" style="overflow:hidden;height:90%;width:100%;border:2px solid #ccc;" height="90%" width="100%" name="manuscript"></iframe>
+```

### 2023-04-08 notebook/exploratory.qmd
Add more descriptive graphs

@@
 ---
-title: EDA
+title: Exploratory and descriptive analysis
 ---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
+                      fig.width = 6, fig.height = (6 * 0.618),
+                      out.width = "80%", collapse = TRUE,
+                      dev = "png", dev.args = list(type = "cairo-png"))
+
+options(digits = 3, width = 120,
+        dplyr.summarise.inform = FALSE,
+        knitr.kable.NA = "")
+```
 
@@
 
-# Timeline of registration
+# Timeline of ONGO registrations
 
-TODO
+```{r plot-registration-timeline}
+ggplot(ongo, aes(x = registration_date)) +
+  geom_histogram(binwidth = 365.25/4, boundary = ymd("2017-01-01"), 
+                 fill = clrs[6], color = "white") +
+  scale_x_date(date_breaks = "years", date_labels = "%Y") +
+  labs(x = NULL, y = "Count of new ONGO registrations") +
+  theme_ongo()
+```
 
@@
 ggplot(ongo, aes(x = province_count)) +
-  geom_histogram(binwidth = 1, color = "white", size = 0.1, boundary = 0) +
-  labs(x = "Number of provinces", y = "Count",
-       title = "Distribution of province counts") +
+  geom_histogram(binwidth = 1, size = 0.1, boundary = 0,
+                 fill = clrs[6], color = "white") +
+  labs(x = "Number of provinces ONGOs are registered in", y = "Count") +
+  theme_ongo()
+```
+
+# Issue areas
+
+```{r plot-ongo-issues}
+issue_count <- ongo |> 
+  drop_na(work_field_code1) |> 
+  group_by(work_field_code1) |>
+  summarize(n = n()) |> 
+  mutate(work_field_code1 = fct_reorder(work_field_code1, n))
+
+ggplot(issue_count, aes(y = work_field_code1, x = n)) +
+  geom_col(fill = clrs[5]) +
+  labs(x = "Count of ONGOs", y = NULL) +
   theme_ongo()
@@
 # with geom_sf(): https://github.com/slowkow/ggrepel/issues/111#issuecomment-416853013
-labeldata <- mapdata |> 
-  filter(ro_count > 0)
-
-plot_map <- ggplot() +
-  geom_sf(data = mapdata,
-          aes(fill = ro_count), color = "white") +
-  scale_fill_viridis_c(option = "mako", begin = 0.1, end = 0.9, direction = -1,
-                       guide = "none") +
-  geom_label_repel(data = labeldata, 
+ggplot() +
+  geom_sf(data = mapdata, aes(fill = ro_count), 
+          linewidth = 0.3, color = "white") +
+  scale_fill_distiller(palette = "Reds", direction = 1, guide = "none") +
+  geom_label_repel(data = filter(mapdata, ro_count > 0), 
                    aes(label = ro_count, geometry = geometry),
-                   stat = "sf_coordinates",
-                   size = 3) +
+                   stat = "sf_coordinates", seed = 1234, label.size = 0.1, size = 3,
+                   segment.color = "black", segment.size = 0.5, min.segment.length = 0) +
+  coord_sf(crs = st_crs("EPSG:4480")) +  # China Geodetic Coordinate System 2000
   theme_void()
-plot_map
 ```

### 2023-04-08 manuscript/manuscript.qmd
MS minor editting
I kept the notes you put - to delete later

@@
 
-In recent decades, there has been a global tend of “closing space” for civil society across jurisdictions such as Russia, India and Vietnam.[@DupuyPrakash:2020;@ChaudhryHeiss:] (*to add citation*) The manifestation of such trend is rolling up laws that restrictive laws that regulate international NGOs (INGOs).[@DupuyPrakash:2020; @ChaudhryHeiss:2022] China’s promulgation of the Law of the People’s Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China (the “ONGO Law”) on April 28, 2016 was considered part of a global wave of legal restrictions on INGOs.
+In recent decades, there has been a global tend of “closing space” for civil society across jurisdictions such as Russia, India and Vietnam.[@DupuyPrakash:2020;@ChaudhryHeiss:2020] (*to add citation*) The manifestation of such trend is rolling out restrictive laws that regulate international NGOs (INGOs).[@DupuyPrakash:2020; @ChaudhryHeiss:2022] China’s promulgation of the Law of the People’s Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China (the “ONGO Law”) on April 28, 2016 was considered part of a global wave of legal restrictions on INGOs.
 The purpose of this study is to empirically examine how the ONGO law has impacted INGO's presence as well as the operational space after the law took effect.
@@
 
-Many ONGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [@sidel:2016], though there were no clear requirements for them to have a formal legal presence in China[@Han:2011].
+Many ONGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [Sidel:2016], though there were no clear requirements for them to have a formal legal presence in China[@Han:2011].
 They choose to have a formal legal identity for the convenience such as signing labor contracts directly with employees.
@@
 
-The promulgation of China’s ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down International NGOs (Chaudhry & Heiss, 2018; Toepler, Zimmer, Fröhlich, & Obuch, 2020).
-Studies on the law has been focused on discussing the historical and political impetus of passing the law (Shieh, 2018) or analyzing the regulatory regimes it that has established and potential implications for ONGOs operating in China (Feng, 2017; Hsu & Teets, 2016).
+- on how Chinese ONGO Law is seen as part of this trend
+
+The promulgation of China’s ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down International NGOs [@ChaudhryHeiss2022; @Carothers:2016].
+(*to update*) Studies on the law has been focused on discussing the historical and political impetus of passing the law (Shieh, 2018) or analyzing the regulatory regimes it that has established and potential implications for ONGOs operating in China [@Feng:2017;@TeetsHsu:2016).
 However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs’ operations and projects have been affected by the law after successfully gaining legal registration and documentation.
-A couple of studies (Jia, 2017; Ye & Huang, 2018) conducted reflections on the first year’s implementation of China’s ONGO Law, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations.
+A couple of studies [@Jia2017; @YeHuang:2018)] conducted reflections on the first year’s implementation of China’s ONGO Law, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations.
 However, a more up-to-date and comprehensive understanding of the effects of the ONGO law is still lacking.
@@
 
-## Literature on differenciated attitudes towards INGOs (*maybe merge with literature on implementation*)
+## Literature on differenciated attitudes towards INGOs (*maybe merge with literature on implementation?*)
 
@@
 
-## Work Field Coding notes
-
-**Decided by how the work fields of registered NGO ROs cluster**
+Based on the issue areas listed by the ONGO Law and how the work fields of registered NGO ROs cluster**
 
@@
 
-to add
+This variable is derived the time difference between ROs' registration date and January 1, 2017 when the law took effect.
+The longer the time elapsed since registration should be achieved by INGOs, it indicates that it took longer time for them to seek the content of both the PSU and Public Security Bureaus to be their supervisions or regulators and grant them legal identity.
 
@@
 
-We use
+We use multilevel Bayesian modeling to analyze the empirical data.
 

### 2023-04-08 notebook/analysis-timing.qmd
Show posterior predicted proportions instead of single values

--- 2023-04-06 notebook/analysis-timing.qmd
@@
 tar_load(ongo)
-tar_load(m_full_ordbeta)
+tar_load(c(m_full_ordbeta, preds_timing))
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
@@
 
-```{r generate-preds}
-preds <- m_full_ordbeta |> 
-  predicted_draws(datagrid(model = m_full_ordbeta, years_since_law = 0:5), 
-                  ndraws = 1000)
-
+```{r plot-epred-timing}
 epreds <- m_full_ordbeta |> 
@@
               ndraws = 1000)
-```
 
-```{r plot-epred-timing}
 epreds |> 
@@
 
-TODO: Prop of 1s, 32s, and in-betweens
+```{r plot-epred-timing-lineribbon}
+epreds %>% 
+  ggplot(aes(x = years_since_law, y = .epred)) +
+  scale_x_reverse() +
+  scale_y_continuous(labels = label_percent(),
+                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
+                                         name = "Expected provinces")) +
+  labs(x = "Years since law took effect (2017)", 
+       y = "Expected proportion of provinces") +
+  stat_lineribbon(alpha = 0.35, fill = clrs[7], color = clrs[7]) +
+  theme_ongo() +
+  theme(axis.title.y.right = element_text(hjust = 1, margin = margin(l = 10), angle = 90))
+```
+
+```{r plot-pred-discrete-continuous-timing, message=FALSE, cache=TRUE}
+preds_timing_plot <- preds_timing |> 
+  unnest(preds) |> 
+  mutate(outcome = case_when(
+    .prediction == 0 ~ "1 province",
+    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
+    .prediction == 1 ~ "32 provinces"
+  )) %>% 
+  group_by(outcome, years_since_law, draw) %>% 
+  summarize(count = n()) |> 
+  group_by(years_since_law) |> 
+  mutate(prop = count / sum(count) * 100)
+
+ggplot(preds_timing_plot, aes(x = years_since_law, y = prop)) +
+  stat_lineribbon(alpha = 0.35, fill = clrs[7], color = clrs[7]) +
+  expand_limits(y = 0) +
+  facet_wrap(vars(outcome)) +
+  scale_x_reverse(breaks = c(0:5)) +
+  scale_y_continuous(labels = label_percent()) +
+  labs(x = "Years since law took effect (2017)", 
+       y = "Proportion of predictions") +
+  theme_ongo()
+```

### 2023-04-09 manuscript/manuscript.qmd
updated the abstract

@@
 Additionally, the severity and consistency of the enforcement of these laws often depends on the type of services provided by these organizations.
-In particular, authoritarian regimes display dual and conflicting attitudes towards claim-making (e.g.
-human rights & advocacy) INGOs versus service-providing (e.g.
-humanitarian assistance) INGOs.
 In this paper, we measure the effect of China’s ONGO law on INGO operations in the five years since the passage of the law.
 We test whether and how INGO operational space under the ONGO law is influenced by organizations’ issue areas.
-We argue that service provision INGOs have greater flexibility and are allowed to work in a larger number of provinces than their claim-making counterparts.
-China provides an excellent setting for testing our claim—the 2017 ONGO law regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities.
-We test our argument by analyzing administrative data from 635 registered representative offices of INGOs registered in China between 2017–2021 and test our hypothesis with multilevel Bayesian models.
+We argue that the less contensious the issue areas INGOs work in the more likely they are granted greater operational space, measured by thenumber of provinces they are allowed to work in by the registration documentation.
+China provides an excellent setting for testing the "closing space" and "changing space" theoretical understanding because the 2017 ONGO law hypothetically regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities.
+We test our argument by analyzing administrative data from 633 registered representative offices of INGOs registered in China between 2017–2021 and test our hypothesis with multilevel Bayesian models.
 Our results speak to the broader literature on closing civic space and provide an empirical illustration of the practical effect of NGO restrictions on global civil society.

### 2023-04-09 notebook/analysis-issue.qmd

--- 2023-04-06 notebook/analysis-issue.qmd
@@
 tar_load(ongo)
-tar_load(m_full_ordbeta)
+tar_load(c(m_full_ordbeta, preds_issue))
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
@@
 
-```{r generate-preds}
-preds <- m_full_ordbeta |> 
-  predicted_draws(datagrid(model = m_full_ordbeta, work_field_code1 = unique), 
-                  ndraws = 1000)
-
+```{r plot-epred-issue}
 epreds <- m_full_ordbeta |> 
@@
               ndraws = 1000)
-```
 
-```{r plot-epred-issue}
 epreds |> 
@@
 
-TODO: Prop of 1s, 32s, and in-betweens
+```{r plot-pred-discrete-continuous-local, message=FALSE, fig.width=6, fig.height=6}
+preds_issue_plot <- preds_issue |> 
+  unnest(preds) |> 
+  mutate(outcome = case_when(
+    .prediction == 0 ~ "1 province",
+    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
+    .prediction == 1 ~ "32 provinces"
+  )) %>% 
+  group_by(outcome, work_field_code1, draw) %>% 
+  summarize(count = n()) |> 
+  group_by(work_field_code1) |> 
+  mutate(prop = count / sum(count) * 100)
+
+ggplot(preds_issue_plot, aes(x = work_field_code1, y = prop)) +
+  stat_pointinterval(color = clrs[5], fatten_point = 1) +
+  expand_limits(y = 0) +
+  facet_wrap(vars(outcome), ncol = 1) +
+  scale_x_discrete(labels = label_wrap(10)) +
+  scale_y_continuous(labels = label_percent()) +
+  labs(x = NULL, y = "Proportion of predictions") +
+  theme_ongo()
+```

### 2023-04-09 notebook/analysis-local.qmd

--- 2023-04-06 notebook/analysis-local.qmd
@@
 tar_load(ongo)
-tar_load(m_full_ordbeta)
+tar_load(c(m_full_ordbeta, preds_local))
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
@@
 
-```{r generate-preds}
-preds <- m_full_ordbeta |> 
-  predicted_draws(datagrid(model = m_full_ordbeta, local_connect = unique), 
-                  ndraws = 1000)
-
+```{r plot-epred-local}
 epreds <- m_full_ordbeta |> 
@@
               ndraws = 1000)
-```
 
-```{r plot-epred-local}
 epreds |> 
@@
 
-TODO: Prop of 1s, 32s, and in-betweens
+```{r plot-pred-discrete-continuous-local, message=FALSE}
+preds_local_plot <- preds_local |> 
+  unnest(preds) |> 
+  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
+  mutate(outcome = case_when(
+    .prediction == 0 ~ "1 province",
+    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
+    .prediction == 1 ~ "32 provinces"
+  )) %>% 
+  group_by(outcome, local_connect, draw) %>% 
+  summarize(count = n()) |> 
+  group_by(local_connect) |> 
+  mutate(prop = count / sum(count) * 100)
+
+ggplot(preds_local_plot, aes(x = local_connect, y = prop)) +
+  stat_pointinterval(color = clrs[2]) +
+  expand_limits(y = 0) +
+  facet_wrap(vars(outcome)) +
+  scale_x_discrete(labels = label_wrap(10)) +
+  scale_y_continuous(labels = label_percent()) +
+  labs(x = NULL, y = "Proportion of predictions") +
+  theme_ongo()
+```

### 2023-04-09 R/funs_models.R
Use better range for posterior predictions

@@ -88,6 +88,20 @@ f_full_ordbeta <- function(data) {
   return(model)
 }
 
+# f_lotsa_preds <- function(model, column_name, ndraws = 100) {
+#   # This dynamically generates the grid, essentially building this command:
+#   #   datagrid(model = model, local_connect = unique)
+#   # but with any variable in place of "local_connect"
+#   args <- list(model = model)
+#   args[[column_name]] <- unique
+#   grid <- exec(datagrid, !!!args)
+#   # Or with do.call():
+#   #   grid <- do.call(datagrid, args)
+#   
+#   tibble(draw = 1:ndraws) |> 
+#     mutate(preds = map(draw, ~predicted_draws(model, grid, ndraws = 1000)))
+# }
+
 f_preds_issue <- function(model, ndraws = 500) {
   tibble(draw = 1:ndraws) |> 
     mutate(preds = map(draw, ~{
@@ -110,7 +124,7 @@ f_preds_timing <- function(model, ndraws = 100) {
   tibble(draw = 1:ndraws) |> 
     mutate(preds = map(draw, ~{
       model |> 
-        predicted_draws(datagrid(model = model, years_since_law = unique), 
+        predicted_draws(datagrid(model = model, years_since_law = 0:5), 
                         ndraws = 1000)
     }))
 }

### 2023-04-09 notebook/analysis-timing.qmd
stop caching now that I'm making the predictions right

@@
 
-```{r plot-pred-discrete-continuous-timing, message=FALSE, cache=TRUE}
+```{r plot-pred-discrete-continuous-timing, message=FALSE}
 preds_timing_plot <- preds_timing |> 

### 2023-04-09 notebook/exploratory.qmd
Add collapsed bar chart

@@
 library(ggrepel)
+library(scales)
 
@@
                  fill = clrs[6], color = "white") +
-  labs(x = "Number of provinces ONGOs are registered in", y = "Count") +
+  labs(x = "Number of provinces INGOs are authorized to work in", y = "Count") +
+  theme_ongo()
+```
+
+```{r province-count-collapsed}
+provinces_collapsed <- ongo |> 
+  drop_na(province_count) |> 
+  mutate(province_count = case_when(
+    province_count == 1 ~ "1 province",
+    province_count > 1 & province_count < 32 ~ "2–31 provinces",
+    province_count == 32 ~ "32 provinces"
+  ))
+
+ggplot(provinces_collapsed, aes(x = province_count)) + 
+  geom_bar(fill = clrs[6]) +
+  scale_y_continuous(sec.axis = sec_axis(trans = ~ . / nrow(provinces_collapsed),
+                                         labels = label_percent())) +
+  labs(x = "Number of provinces INGOs are authorized to work in", y = "Count") +
   theme_ongo()

### 2023-04-09 _targets.R
Add uploading script as a target

@@ -69,5 +69,13 @@ list(
   tar_target(preds_timing, f_preds_timing(m_full_ordbeta)),
   
   ## Analysis notebook ----
-  tar_quarto(website, path = ".", quiet = FALSE)
+  tar_quarto(website, path = ".", quiet = FALSE),
+  
+  tar_target(deploy_script, here_rel("deploy.sh"), format = "file"),
+  tar_target(deploy, {
+    # Force a dependency
+    website
+    # Run the deploy script, but only on Andrew's computer, which has SSH access to the server
+    if (Sys.getenv("UPLOAD_WEBSITES") == "TRUE") processx::run(paste0("./", deploy_script))
+  })
 )

### 2023-04-09 _targets.R
Make the manuscript a target

@@ -69,6 +69,7 @@ list(
   tar_target(preds_timing, f_preds_timing(m_full_ordbeta)),
   
   ## Analysis notebook ----
+  tar_quarto(manuscript_nice, path = "manuscript", quiet = FALSE),
   tar_quarto(website, path = ".", quiet = FALSE),
   
   tar_target(deploy_script, here_rel("deploy.sh"), format = "file"),

### 2023-04-09 manuscript/manuscript.qmd
Add initial model definition writeup

@@
 ---
+
+```{r setup, include=FALSE}
+if (is.null(knitr::pandoc_to())) {
+  fmt_out <- "interactive"
+} else {
+  fmt_out <- knitr::pandoc_to()
+}
+
+knitr::opts_chunk$set(echo = FALSE, include = FALSE, 
+                      warning = FALSE, message = FALSE)
+
+knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
+                      fig.width = 6, fig.height = (6 * 0.618),
+                      out.width = "80%", collapse = TRUE)
+
+options(digits = 3, width = 120,
+        dplyr.summarise.inform = FALSE,
+        knitr.kable.NA = "")
+```
+
+```{r libraries-data}
+library(tidyverse)
+library(scales)
+library(lubridate)
+library(tidybayes)
+library(marginaleffects)
+library(patchwork)
+library(kableExtra)
+library(gt)
+library(targets)
+
+tar_config_set(store = here::here('_targets'),
+               script = here::here('_targets.R'))
+
+# Generated via random.org
+set.seed(8511)
+
+# Load targets 
+tar_load(ongo)
+tar_load(ongo_mapdata)
+
+# Plotting and modelsummary functions
+invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+```
 
@@
 
+Our data provides us with rich descriptive detail of the types of INGOs allowed to register in China following the advent of the ONGO law, and we explore patterns in this data below.
+In addition to presenting descriptive summary statistics, we create a multilevel Bayesian regression model to examine the complex effects that issue area, local connections, and registration timing have on organizational flexibility.
+This approach allows us to hold specific variables constant and generate predictions for hypothetical new, not-yet-registered INGOs, providing us with stronger empirical implications.
+
 We use multilevel Bayesian modeling to analyze the empirical data.
+
+```{r fig-province-count-collapsed, fig.width=6, fig.height=3}
+#| include: true
+#| echo: false
+#| fig-cap: "Count of the number of provinces each INGO is authorized to operate in.
+The left panel shows the full distribution of INGOs registered in 2–31 provinces; the right panel collapses these in-between counts to a single category."
+provinces_collapsed <- ongo |> 
+  drop_na(province_count) |> 
+  mutate(province_count = case_when(
+    province_count == 1 ~ "1",
+    province_count > 1 & province_count < 32 ~ "2–31",
+    province_count == 32 ~ "32"
+  ))
+
+p1 <- ggplot(ongo, aes(x = province_count)) +
+  geom_histogram(binwidth = 1, size = 0.1, boundary = 0,
+                 fill = clrs[6], color = "white") +
+  scale_y_continuous(breaks = seq(0, 250, 50)) +
+  labs(x = "Provinces INGOs are authorized to work in", y = "Count") +
+  theme_ongo()
+
+p2 <- ggplot(provinces_collapsed, aes(x = province_count)) + 
+  geom_bar(fill = clrs[6]) +
+  scale_x_discrete(labels = label_wrap(10)) +
+  scale_y_continuous(sec.axis = sec_axis(trans = ~ . / nrow(provinces_collapsed),
+                                         labels = label_percent()),
+                     breaks = seq(0, 250, 50)) +
+  labs(x = NULL, y = NULL) +
+  theme_ongo()
+
+(p1 | p2) + 
+  plot_layout(nrow = 1, widths = c(0.7, 0.3))
+```
+
+Modeling the count of provinces each INGO is authorized to operate in presents a unique statistical challenge.
+As seen in @fig-province-count-collapsed, roughly 30% of INGOs are registered in only one province, 40% are registered nationwide, while the remaining 30% are registered in 2–31 provinces.
+Our main variable of interest is thus a mix of continuous outcomes (i.e.
+a range of provinces) bounded between two discrete outcomes (i.e.
+one province and all provinces).
+Standard modeling approaches like ordinary least squares regression (OLS) cannot accurately capture the unique features of the data and will generate predictions that fall outside allowable bounds (i.e.
+negative counts of provinces or more than 32 provinces).
+If we transform the count of provinces to a percentage, Beta regression would work well, as it is naturally limited outcomes within a 0–1 range.
+However, Beta regression cannot handle values that are exactly 0 or 1, making it inappropriate for our data with its inflated counts at 0 (1)  and 100% (32).
+To account for values at the bounds, we rely on ordered Beta regression [@Kubinec:2022], and extension of zero-and-one-inflated Beta regression that allows us to simultaneously model the continuous range of provinces (2–31) and the discrete outcomes (1 province and 32 provinces) without relying on percentages.
+We can thus explore the dynamics of each of our independent variables of interest in multiple ways—we can see (1) how each variable predicts that an organizations works in one province, nationwide, or somewhere in between, and (2) how each variable predicts the overall expected count of provinces.
+
+@eq-ordbeta provides a formal definition of our modeling choices.
+Since we are primarily interested in how an INGO's issue area, its local connections, and the timing of its registration after January 2017, we include these as explanatory variables.
+We also include province-specific random offsets for each intercept to account for between-region differences in how INGOs are regulated.
+We use weakly informative priors for all model parameters.
+
+::: {.column-page-inset-right}
+
+$$
+\begin{aligned}
+\text{Count of provinces}\ \sim&\ \operatorname{Ordered Beta}(\mu_{i_j}, \phi_y, k_{0_y}, k_{1_y}) & \text{Registered provinces for INGO $i$ in province $j$}\\[8pt]
+\mu_{i_j} =&\ (\beta_0 + b_{0_j}) + \beta_1\ \text{Issue area}\ + & \text{Average outcome}\\
+&\ \beta_2\ \text{Local connections}\ + \\
+&\ \beta_3\ \text{Years since law took effect} \\
+b_{0_j} =&\ \mathcal{N}(0, \sigma_0) & \text{Random province offsets} \\[8pt]
+\beta_0\ \sim&\ \operatorname{Student\,t}(\nu = 3, \mu = 0, \sigma = 2.5) & \text{Prior for global intercept} \\
+\beta_{1..3}\ \sim&\ \mathcal{N}(0, 5) & \text{Prior for global coefficients} \\
+\sigma_0\ \sim&\ \operatorname{Student\,t}(3, 0, 2.5) & \text{Prior for between-province variability} \\
+\phi_y\ \sim&\ \operatorname{Exponential}(1 / 100) & \text{Prior for within-province variability} \\
+k_{0_y}, k_{1_y}\ \sim&\ \operatorname{Dirichlet}(1, 1, 1) & \text{Prior for 0–continuous and continuous–1 cutpoints} \\
+\end{aligned}
+$$ {#eq-ordbeta}
+
+:::
 

### 2023-04-09 manuscript/manuscript.qmd
oof add space in family name

@@
 \begin{aligned}
-\text{Count of provinces}\ \sim&\ \operatorname{Ordered Beta}(\mu_{i_j}, \phi_y, k_{0_y}, k_{1_y}) & \text{Registered provinces for INGO $i$ in province $j$}\\[8pt]
+\text{Count of provinces}\ \sim&\ \operatorname{Ordered\ Beta}(\mu_{i_j}, \phi_y, k_{0_y}, k_{1_y}) & \text{Registered provinces for INGO $i$ in province $j$}\\[8pt]
 \mu_{i_j} =&\ (\beta_0 + b_{0_j}) + \beta_1\ \text{Issue area}\ + & \text{Average outcome}\\

### 2023-04-09 manuscript/manuscript.qmd
Add super preliminary stuff about local connections

@@
 This approach allows us to hold specific variables constant and generate predictions for hypothetical new, not-yet-registered INGOs, providing us with stronger empirical implications.
-
-We use multilevel Bayesian modeling to analyze the empirical data.
+Additionally, Bayesian modeling allows us to calculate the posterior distribution of our different estimands.
+Rather than report a single value for the proportion of registered INGOs worked on specific issues, we can estimate posterior credible intervals that represent the probability that the true proportion falls within a specific range.
+We report posterior medians and 95% credible intervals throughout our analysis.
+Importantly, these intervals do not behave like more traditional frequentist confidence intervals.
+Instead, they can be interpreted as the probability that a reported estimate falls within the range, given the data and modeling choices.
 
@@
 
+### Issue area
+
+### Local connections
+
+In our second empirical expectation, we posit that since INGOs that seek out local connections and that are focused on more local China-specific issues, those organizations should be registered in fewer provinces.
+The results from our model confirm this expectation.
+
+TODO 12ish expected provinces for INGOs with no local connections; 21ish for INGOs with local connections
+
+TODO We can take advantage of the continuous + discrete features of ordered beta and see BLAH BLAH.
+After simulating 1,000 hypothetical new INGOs, organizations without local connections are predicted to work nationally in all provinces nearly 50% of the time (ASDF-ASDF credible interval), and are predicted to work in 2 or more provinces 35% of the time.
+These organizations with no local connections or local programmatic focus are only predicted to work in a single province 15ish% of the time.
+In contrast, INGOs *with* local connections are far more likely to only work in one province (35%), or only work in a handful of provinces.
+These locally-focused organizations are only predicted to work nationally 25% of the time.
+
+TODO Graphs
+
+### Registration timing
+
 # Discussion

### 2023-04-09 manuscript/manuscript.qmd
Major updates
Start to look presentable

@@
 
-In recent decades, there has been a global tend of “closing space” for civil society across jurisdictions such as Russia, India and Vietnam.[@DupuyPrakash:2020;@ChaudhryHeiss:2020] (*to add citation*) The manifestation of such trend is rolling out restrictive laws that regulate international NGOs (INGOs).[@DupuyPrakash:2020; @ChaudhryHeiss:2022] China’s promulgation of the Law of the People’s Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China (the “ONGO Law”) on April 28, 2016 was considered part of a global wave of legal restrictions on INGOs.
-The purpose of this study is to empirically examine how the ONGO law has impacted INGO's presence as well as the operational space after the law took effect.
-By inquiring the *de facto* implementation of the law in addition to formal *de jure* regulations, we will be able to see a more comprehensive picture of the operational space for INGOs.
-It will also inform as the evolving theorization of the "closing space" and dual attitudes towards INGOs hold true for an Authoritarian jurisdiction such as China.
+# Introduction
 
-ONGO law, what has it meant for ONGOs—how are they responding? [@ChaudhryHeiss:2022]
+In recent decades, there has been a global tend of “closing space” for civil society across jurisdictions such as Russia, India and Vietnam.[@DupuyPrakash:2020; @ChaudhryHeiss:2020; @Heiss2017; @Sidel:2023; AtiaHerrold:2018] (*to update citation*).
+An ubiquitous manifestation of such trend is rolling out restrictive laws that regulate international NGOs (INGOs).[@DupuyPrakash:2020; @ChaudhryHeiss:2022a].
+China’s promulgation of the Law of the People’s Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China (the “ONGO Law”) on April 28, 2016 was considered part of a recent global wave of legal restrictions on INGOs.
+As an authoritarian jurisdiction with a growing nonprofit sector, the Chinese model of implementing restrictive laws for INGOs has great implications for scholarly understanding of the dynamics of how such laws are used as policy tools to harness INGOs in practice.
+The purpose of this study is to empirically examine how the ONGO Law has impacted INGO's presence as well as the operational space after the law took effect.
+By inquiring the *de facto* implementation of the law in addition to formal *de jure* regulations, we intent to inquire into a more comprehensive and data-based picture of the operational space for INGOs.
+It will also test out the evolving theory of the "closing space" or "changing space" for INGOs hold true in a representative empirical setting of the mainland China.
 
-@FaridLi:2021
-
-Charity law + ONGO law happened at the same time - lots of discussion about what it would mean for ONGOs at the time - lots of people looked at the framework of the law, but we don't know what it has actually looked like
-Following up with the actual implementation of law
-
-# Context of the ONGO law
-
-In recent decades, ONGOs came to China after the Reform and Opening-up policy was adopted by the authority and have been playing pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China’s domestic nonprofit sector [@Yin:2009].
-Before the promulgation of the ONGO Law, the regulation of ONGOs in China was obscure [Shieh:2018].
-The only legal document relevant to ONGOs was a section of the Regulation on the Management of Foundations by the State Council that specifies the registration of representative offices (“ROs”) of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic NGOs.
+INGOs came to China after the Reform and Opening-up policy was adopted by the authority and have been playing pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China’s domestic nonprofit sector [@Yin:2009].
+Before the promulgation of the ONGO Law, the regulation of INGOs in China was obscure [Shieh:2018; Spires:2022].
+The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations by the State Council that specifies the registration of representative offices (“ROs”) of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic NGOs.
 However, the actual application of the regulation was very limited.
@@
 
-Many ONGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [Sidel:2016], though there were no clear requirements for them to have a formal legal presence in China[@Han:2011].
+Many INGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [Sidel:2016], though there were no clear requirements for them to have a formal legal presence in China[@Han:2011].
 They choose to have a formal legal identity for the convenience such as signing labor contracts directly with employees.
@@
 Under the Chinese legal system, enterprises should be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms for them — foundations, associations and social service organizations [@Ye:2021].
-Thus, ONGOs obtaining legal identity in this way have to navigate through a legal framework designed for the for-profit institutional logic, e.g, focusing on project investers' right to investment return.
+Thus, ONGOs obtaining legal identity in this way have to navigate through a legal framework designed for the for-profit institutional logic, e.g, focusing on project investors' right to investment return.
 
@@
 Specifically, the ONGO law stipulates two ways to lawfully conduct nonprofit activities in China for ONGOs: registering ROs or filing information for documentation of temporary activities with the Ministry of Public Security (“MPS”) and Provincial-level Public Security bureaus, which are the registering and regulatory authority for ONGOs designated by the law.
-Registering an RO would be lawful identity gaining channel for INGOs seeking for on-going presence in China while temporary activities are suitable for INGOs that need to coduct one-off programs that last no longer than one year.
+Registering an RO would be lawful identity gaining channel for INGOs seeking for on-going presence in China while temporary activities are suitable for INGOs that need to conduct one-off programs that last no longer than one year.
 
-This paper will study the the empirical data of the registration of ROs in the years following the enactment of the ONGO Law to uncover the association between ONGO issue areas and the composition of successful RO registration and the operational space granted.
-
-Registering RO under the ONGO Law requiring the consent of a Chinese professional sponsoring unit (the "PSU"), which are governmental or quasi-governmental overseeing the INGO's issue area to co-supervise the INGOs with Public Security bureaus.
+This paper studies the the empirical data of the registration of ROs in the years following the enactment of the ONGO Law to uncover the association between INGO issue areas and the composition of successful RO registration and the operational space granted.
+Registering RO under the ONGO Law requiring the consent of a Chinese professional supervisory unit (the "PSU"), which are governmental or quasi-governmental overseeing the INGO's issue area to co-supervise the INGOs with Public Security bureaus.
 And it turns out that obtaining the consent of a PSU to apply for registration became a key challenge for ONGOs, because potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018].
@@
 Some ROs are authorized to operate across mainland China, which is 32 provincial administrative regions in total, but there are also many that are authorized to operate in one to multiple provinces but not all.
+We use the number of provinces that ROs are authorized to work in as a proxy to measure the operational space for INGOs in China based on the empirical understanding that INGOs need to or hope to have the approval to be able to carry out their programs in a geographical scope as larger as possible.
+[@Li:2020]
 
@@
 
-Contentiousness, regime stability, other reasons
+Contentiousness, regime stability, other reasons (to add studies on this construct globally)
 
-- on how Chinese ONGO Law is seen as part of this trend
+## Literature on differenciated attitudes towards INGOs (as reveal in implementation)
+
+"We discuss the role of civil society organizations (CSOs) as agents of democratization and note the emergence of dual, at times apparently conflicting policy postures within authoritarian regimes (restriction and repression for some CSOs vs.
+financial support and opportunities for collaboration for others)." [@ToeplerZimmerFrohlich:2020]
+
+Also, [@Plantan2022] finds "that I find" evidence of selective implementation that reveals which groups are seen as threatening or beneficial."
+
+*de jure* vs. *de facto* difference "represents a bureaucratic form of repression" [@ChaudhryHeiss:2022]
 
 The promulgation of China’s ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down International NGOs [@ChaudhryHeiss2022; @Carothers:2016].
-(*to update*) Studies on the law has been focused on discussing the historical and political impetus of passing the law (Shieh, 2018) or analyzing the regulatory regimes it that has established and potential implications for ONGOs operating in China [@Feng:2017;@TeetsHsu:2016).
+Studies on the law has been focused on discussing the historical and political impetus of passing the law (Shieh, 2018) or analyzing the regulatory regimes it that has established and potential implications for INGOs operating in China [@Feng:2017;@TeetsHsu:2016).
 However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs’ operations and projects have been affected by the law after successfully gaining legal registration and documentation.
@@
 
-## Literature on implementation - de jure vs. de facto differences
+This paper aims to fill these gaps by empirically examining how the "closing space" hypothesis applies to China in the years after the ONGO Law took effect.
+China provides an excellent setting for testing these theories because China's promulgation of restrictive INGO law as an authoritarian jurisdiction fits the observed global trends in recent years, thus can serve as an representative case to deepen scholarly understanding around these themes.
+Also, the level of ambiguity of the legal framework gives ample room for arbitrary discretion and conflicting attitudes by authorities, enabling us to analyze rules in form (*de jure*) as well as rules in use (*de facto*).
 
-## Literature on differenciated attitudes towards INGOs (*maybe merge with literature on implementation?*)
+Based on extant literature and theoretical understanding, we hypothesize that the operation space INGOs are granted is associated with the level of contentious their missions, i.e., the issue areas they work in.
+Since the level of contentious is also manifested by the level of difficulty they face while seeking lawful registration.
+We also hypothesize that large operational space of INGOs is negatively associated the time elapsed since the law took effect when they successfully got registered.
 
-"We discuss the role of civil society organizations (CSOs) as agents of democratization and note the emergence of dual, at times apparently conflicting policy postures within authoritarian regimes (restriction and repression for some CSOs vs.
-financial support and opportunities for collaboration for others)." [@ToeplerZimmerFrohlich:2020]
-
-Also, [@Plantan2022]
-
-# Theory / research questions
-
-This aims to examin how the "closing space" hypothesis plays out in China.
-China provides an excellent setting for testing our claim—the 2017 ONGO law regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities.
-
-- RQ1: Provinces and work field - connects to NGO contentiousness bc everything is noncontentious
-- RQ2: Provinces and PSUs - local vs. national - there's variance in local PSUs - flexibility, venue-seeking maybe
-- RQ3: Provinces and length of time in country / registration date/year - earlier organizations work in more?
-- flexibility bc more local knowledge, more interest, more support from government to get registered, etc.
+The follow section is structured as follow.
+In the data and methods section, we first report the data cleaning and coding process and measurements used in our empirical analysis.
+Then we explain the rationale for choosing ordered beta regression to fit our models.
+In the Results section, we report and interpret both descriptive analysis and regression analysis results.
+We conclude the paper by discussing the implications of our findings with respective to more general scholarly understanding of the closing space of international civil society.
 
@@
 
-- `geo_scope_num`
-
-Count of the number of provinces each RO is authorized to operate in
+Our dependent variable is "geo_scope_num", the count of the total number of provinces each RO is authorized to operate in.
+We derived this variable from the specific list of authorized provinces as recorded in the RO's registration documentation.
+As discussed above, we use this measurement as a proxy for operational space for INGOs, because any geographical constraints on the RO impacts on the flexibility of the INGO operations.
+For example, in circumstances where emergency like the COVID 19 pandemic hits, it would be extremely hard for INGOs to plan beforehand which areas would need their service.
+Thus, we assume INGOs that are not set up with any locally-bound purposes would need to or hope to (if there is not yet such needs) be able to operate in as broader geographical scope as possible.
 
@@
 
-- `work_field`
+Our first independent variable is "work_field_code1", the issue area we code from mission statement specified in the RO's registration documentation.
+Given there is certain level of subjectivity in the coding process, the coding of issue areas are cross-checked between the researchers (to do).
+The coding rules for overlapping issue areas can be found in the Appendix (to add).
+We decided to have 9 issue areas groups based on list of lawful fields of work specified by the Article 3 of the ONGO Law and how actual issue areas cluster for registered ROs.
 
-`work_field` is the original mission statement in Chinese.
-The name "field" is chosen for the moment, because it seems "area" is more easily to be confused with the geographical scope.
-It is not called "mission" to differentiate from the mission of the mother organization which is not subject to approval of the authority.
-Also, the statement of the work field tends to be more concrete than missions.
+Below is the list of issue areas INGOs' registered ROs are coded into.
 
-`work_field_code1` is the main work field code
+- **Economy and trade**
+- **Environment** (including animal protection)
+- **Education** (including youth development)
+- **Charity and humanitarian** poverty alleviation, disaster relief, etc., including rural development 
+- **Science and technology**
+- **Industry association**
+- **Health**, public health and health care system support (professional training)
+- **Arts and Culture** including sports and international culture exchange
+- **General**, usually grant-making organizations, Or working on general international communication, including among governments, or working on multiple fields not overlapping
 
-Based on the issue areas listed by the ONGO Law and how the work fields of registered NGO ROs cluster**
-
-- **[Economy and trade]**
-
-- **[Environment]** (including animal protection)
-
-- **[Education]** (including youth development and international cultural exchange)
-
-- **[Charity and humanitarian]** poverty alleviation, disaster relief, etc., including rural development and social work
-  If rural development is researched at the macroeconomics level, coded as science and technology, eg. #375
-
-- **[Science and technology]**
-
-- **[Industry association]**
-
-- **[Health]** public health and health care system support (professional training)
-
-- **[Arts and Culture]** including sports (noted as “sports” in `work_field_code2`) and international culture exchange
-
-- **[General]** usually grant-making organizations, Or working on general international communication, including among governments, Or working on multiple fields not overlapping
-
-- `time_elapsed`
-
+Our second variable is "time_elapsed".
 This variable is derived the time difference between ROs' registration date and January 1, 2017 when the law took effect.
@@
 
-- `still_active`, `FALSE` for those have indeed de-register and `TRUE` otherwise.
+Our first control variable is "local_connet".
+It is a dichotomous variable indicating whether operating locally is built into the RO's mission.
+There are cases where the aim or mission of the INGO attached to a locality, either having a county or city name in their RO name or purposes, or the INGO are actually set up by people in China and they registered the RO to communicate between the "hometown" and the INGO set up abroad.
+So we include this variable in our model to how having local connection is associated with the operational space of ROs as well as how the contentious level associates with operation space when we account for this factor.
 
-- `home`
-
-home county or region of the ONGO. Not using the name "country" to be flexible enough to denote, Hong Kong, Macau and Taiwan
-
-- `psu_level`
-
-Dummy variable indicating whether the official sponsoring unit (for registration and annual audit) is at the national or local level. 
-It is clearly correlated with `geo_scope_num`, but should be a mediating factor for the relationship we are examining.
-
-- `ro_count`
-
-There are cases where ONGOs are not granted to operate across China, so they register multiple ROs to cover enough number of provinces where they need to work.
-
-- `local_connect`
-There are cases where the aim/mission of the ONGO is attached to a locality, either having a county/city name in their RO name or purposes, or the INGO are actually set up by people in China and they RO to communicate between the "hometown" and the INGO
-
-*Notes to delete:*
-
-No control/pre-group - this is all descriptive about the "after" group of ONGOs that all selected themselves into the regulations
-
-multiple_id - either treat it as a random organization effect for the parent org, or weight it, so if there are 8, we weight by 1/8
-cn_background = Chinese NGOs
-To compensate such limitation, ONGOs are allowed to register multiple ROs within mainland China at the meantime.
-
-Main assumption: We're interested in the potential to be in other provinces, even if an organization is small now, they want to someday spread out
+We also cluster our 633 RO cases by the province where they are registered in our hierarchical Bayesian modeling.
+Thus, we account for any variance caused by the socioeconomic and institutional differences in various provinces of China.
+And the level province is the apporoiate level to cluster because all the ROs are registered at the provincial public security bureaus.
 

### 2023-04-09 manuscript/manuscript.qmd
fixed citation typo

@@
 
-In recent decades, there has been a global tend of “closing space” for civil society across jurisdictions such as Russia, India and Vietnam.[@DupuyPrakash:2020; @ChaudhryHeiss:2020; @Heiss2017; @Sidel:2023; AtiaHerrold:2018] (*to update citation*).
+In recent decades, there has been a global tend of “closing space” for civil society across jurisdictions such as Russia, India and Vietnam.[@DupuyPrakash:2020; @ChaudhryHeiss:2020; @Heiss:2017; @Sidel:2023; AtiaHerrold:2018] (*to update citation*).
 An ubiquitous manifestation of such trend is rolling out restrictive laws that regulate international NGOs (INGOs).[@DupuyPrakash:2020; @ChaudhryHeiss:2022a].
@@
 
-Also, [@Plantan2022] finds "that I find" evidence of selective implementation that reveals which groups are seen as threatening or beneficial."
+Also, [@Plantan:2022] finds "that I find" evidence of selective implementation that reveals which groups are seen as threatening or beneficial."
 
@@
 
-The promulgation of China’s ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down International NGOs [@ChaudhryHeiss2022; @Carothers:2016].
+The promulgation of China’s ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down International NGOs [@ChaudhryHeiss:2022; @Carothers:2016].
 Studies on the law has been focused on discussing the historical and political impetus of passing the law (Shieh, 2018) or analyzing the regulatory regimes it that has established and potential implications for INGOs operating in China [@Feng:2017;@TeetsHsu:2016).
 However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs’ operations and projects have been affected by the law after successfully gaining legal registration and documentation.
-A couple of studies [@Jia2017; @YeHuang:2018)] conducted reflections on the first year’s implementation of China’s ONGO Law, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations.
+A couple of studies [@Jia:2017; @YeHuang:2018)] conducted reflections on the first year’s implementation of China’s ONGO Law, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations.
 However, a more up-to-date and comprehensive understanding of the effects of the ONGO law is still lacking.

### 2023-04-09 manuscript/manuscript.tex
fixed citation typo

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
]{article}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{mathtools}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{sidenotes}{}{\usepackage{sidenotes}}
\@ifpackageloaded{marginnote}{}{\usepackage{marginnote}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={The Implementation of China's Overseas NGO Law and the Operating Space for International Civil Society},
  pdfauthor={Meng Ye; Andrew Heiss},
  pdfkeywords={international NGOs, civil
society, authoritarianism, Chinese ONGO law},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{The Implementation of China's Overseas NGO Law and the Operating
Space for International Civil Society}
\author{Meng Ye \and Andrew Heiss}
\date{2023-04-07}

\begin{document}
\maketitle
\begin{abstract}
China's 2017 Overseas NGO (ONGO) Law is part of a larger global trend of
legal restrictions on international NGOs (INGOs). However, the effects
of this global crackdown on INGOs have been difficult to measure since
there is often divergence between the formal de jure regulations and the
de facto implementation of these laws. Additionally, the severity and
consistency of the enforcement of these laws often depends on the type
of services provided by these organizations. In this paper, we measure
the effect of China's ONGO law on INGO operations in the five years
since the passage of the law. We test whether and how INGO operational
space under the ONGO law is influenced by organizations' issue areas. We
argue that the less contensious the issue areas INGOs work in the more
likely they are granted greater operational space, measured by thenumber
of provinces they are allowed to work in by the registration
documentation. China provides an excellent setting for testing the
``closing space'' and ``changing space'' theoretical understanding
because the 2017 ONGO law hypothetically regulates both claim-making and
service-providing NGOs, while the level of ambiguity of the law gives
ample room for arbitrary discretion and conflicting attitudes by
authorities. We test our argument by analyzing administrative data from
633 registered representative offices of INGOs registered in China
between 2017--2021 and test our hypothesis with multilevel Bayesian
models. Our results speak to the broader literature on closing civic
space and provide an empirical illustration of the practical effect of
NGO restrictions on global civil society.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, boxrule=0pt, sharp corners, frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

In recent decades, there has been a global tend of ``closing space'' for
civil society across jurisdictions such as Russia, India and
Vietnam.{[}Dupuy and Prakash
(\protect\hyperlink{ref-DupuyPrakash:2020}{2020}); Chaudhry and Heiss
(\protect\hyperlink{ref-ChaudhryHeiss:2020}{2020});
(\protect\hyperlink{ref-Heiss2017}{\textbf{Heiss2017?}}); Sidel
(\protect\hyperlink{ref-Sidel:2023}{2023}); AtiaHerrold:2018{]}
(\emph{to update citation}). An ubiquitous manifestation of such trend
is rolling out restrictive laws that regulate international NGOs
(INGOs).(\protect\hyperlink{ref-DupuyPrakash:2020}{Dupuy and Prakash
2020}; \protect\hyperlink{ref-ChaudhryHeiss:2022a}{Chaudhry and Heiss
2022a}). China's promulgation of the Law of the People's Republic of
China on Administration of Activities of Overseas Nongovernmental
Organizations in the Mainland of China (the ``ONGO Law'') on April 28,
2016 was considered part of a recent global wave of legal restrictions
on INGOs. As an authoritarian jurisdiction with a growing nonprofit
sector, the Chinese model of implementing restrictive laws for INGOs has
great implications for scholarly understanding of the dynamics of how
such laws are used as policy tools to harness INGOs in practice. The
purpose of this study is to empirically examine how the ONGO Law has
impacted INGO's presence as well as the operational space after the law
took effect. By inquiring the \emph{de facto} implementation of the law
in addition to formal \emph{de jure} regulations, we intent to inquire
into a more comprehensive and data-based picture of the operational
space for INGOs. It will also test out the evolving theory of the
``closing space'' or ``changing space'' for INGOs hold true in a
representative empirical setting of the mainland China.

INGOs came to China after the Reform and Opening-up policy was adopted
by the authority and have been playing pivotal roles in providing
funding, organizational and program management skills, as well as
catalytic support for the emergence of China's domestic nonprofit sector
(\protect\hyperlink{ref-Yin:2009}{Yin 2009}). Before the promulgation of
the ONGO Law, the regulation of INGOs in China was obscure
{[}Shieh:2018; Spires:2022{]}. The only legal document relevant to INGOs
was a section of the Regulation on the Management of Foundations by the
State Council that specifies the registration of representative offices
(``ROs'') of foreign foundations with the Ministry of Civil Affairs, the
regulator of Chinese domestic NGOs. However, the actual application of
the regulation was very limited. Up until the ONGO Law took effect on
January 1, 2017, there were fewer than 30 foreign foundation ROs
registered at the Ministry of Civil Affairs according to the Regulation
on the Management of Foundations, while some Chinese officials estimated
in 2016 that there were roughly over 7000 ONGOs operating in China
(\protect\hyperlink{ref-YeHuang:2018}{Ye and Huang 2018}).

Many INGOs gained legal identity within mainland China using the vehicle
of foreign-funded companies {[}Sidel:2016{]}, though there were no clear
requirements for them to have a formal legal presence in
China(\protect\hyperlink{ref-Han:2011}{Han 2011}). They choose to have a
formal legal identity for the convenience such as signing labor
contracts directly with employees. However, the legal form of
foreign-funded company is not quite compatible with the nature of ONGOs.
Under the Chinese legal system, enterprises should be for-profit
entities and nonprofit organizations are required to choose other
stand-alone legal forms for them --- foundations, associations and
social service organizations (\protect\hyperlink{ref-Ye:2021}{Ye 2021}).
Thus, ONGOs obtaining legal identity in this way have to navigate
through a legal framework designed for the for-profit institutional
logic, e.g, focusing on project investors' right to investment return.

The legal framework governing ONGOs was overhauled by the Chinese ONGO
Law. The new law applies to all Overseas (including Hong Kong, Macau and
Taiwan) non-governmental organizations that conduct not-for-profit
activities in the fields of Economic Development, Education, Science,
Technology, Culture, Public Health, Sports, Environment Protection,
Poverty Alleviation, and Disaster Relief etc. (Article 3). In other
words, after the Overseas NGOs became effective, any nonprofit
activities conducted by those ONGOs that cannot successfully obtaining
proper legal authorization according to the law will be deemed illegal.
Specifically, the ONGO law stipulates two ways to lawfully conduct
nonprofit activities in China for ONGOs: registering ROs or filing
information for documentation of temporary activities with the Ministry
of Public Security (``MPS'') and Provincial-level Public Security
bureaus, which are the registering and regulatory authority for ONGOs
designated by the law. Registering an RO would be lawful identity
gaining channel for INGOs seeking for on-going presence in China while
temporary activities are suitable for INGOs that need to conduct one-off
programs that last no longer than one year.

This paper studies the the empirical data of the registration of ROs in
the years following the enactment of the ONGO Law to uncover the
association between INGO issue areas and the composition of successful
RO registration and the operational space granted. Registering RO under
the ONGO Law requiring the consent of a Chinese professional supervisory
unit (the ``PSU''), which are governmental or quasi-governmental
overseeing the INGO's issue area to co-supervise the INGOs with Public
Security bureaus. And it turns out that obtaining the consent of a PSU
to apply for registration became a key challenge for ONGOs, because
potential PSUs do not have a legal obligation to assume such a demanding
role (\protect\hyperlink{ref-Jia:2017}{Jia 2017};
\protect\hyperlink{ref-Shieh:2018}{Shieh 2018};
\protect\hyperlink{ref-YeHuang:2018}{Ye and Huang 2018}). Therefore, the
composition of the successfully registered RO inform us whether ROs
working on different issue areas have varied level of difficulty in
obtaining legal status. Moreover, We measure the later with a proxy of
the number of provinces that the ROs are authorized to operate.
Specifically, the registration document of an RO would specify the field
of work and mission for the RO and list the range of provinces that the
RO is authorized to conduct nonprofit activities in (Article 18). Some
ROs are authorized to operate across mainland China, which is 32
provincial administrative regions in total, but there are also many that
are authorized to operate in one to multiple provinces but not all. We
use the number of provinces that ROs are authorized to work in as a
proxy to measure the operational space for INGOs in China based on the
empirical understanding that INGOs need to or hope to have the approval
to be able to carry out their programs in a geographical scope as larger
as possible. (\protect\hyperlink{ref-Li:2020}{Li 2020})

\hypertarget{literature-and-theoretical-background}{%
\section{Literature and Theoretical
Background}\label{literature-and-theoretical-background}}

\hypertarget{literature-on-closing-space-for-ingos}{%
\subsection{Literature on Closing Space for
INGOs}\label{literature-on-closing-space-for-ingos}}

Contentiousness, regime stability, other reasons (to add studies on this
construct globally)

\hypertarget{literature-on-differenciated-attitudes-towards-ingos-as-reveal-in-implementation}{%
\subsection{Literature on differenciated attitudes towards INGOs (as
reveal in
implementation)}\label{literature-on-differenciated-attitudes-towards-ingos-as-reveal-in-implementation}}

``We discuss the role of civil society organizations (CSOs) as agents of
democratization and note the emergence of dual, at times apparently
conflicting policy postures within authoritarian regimes (restriction
and repression for some CSOs vs.~financial support and opportunities for
collaboration for others).''
(\protect\hyperlink{ref-ToeplerZimmerFrohlich:2020}{Toepler et al.
2020})

Also, (\protect\hyperlink{ref-Plantan2022}{\textbf{Plantan2022?}}) finds
``that I find'' evidence of selective implementation that reveals which
groups are seen as threatening or beneficial.''

\emph{de jure} vs.~\emph{de facto} difference ``represents a
bureaucratic form of repression''
(\protect\hyperlink{ref-ChaudhryHeiss:2022}{Chaudhry and Heiss 2022b})

The promulgation of China's ONGO Law has been discussed by scholars
mostly as a part of a global trend of restricting and cracking down
International NGOs
(\protect\hyperlink{ref-ChaudhryHeiss2022}{\textbf{ChaudhryHeiss2022?}};
\protect\hyperlink{ref-Carothers:2016}{Carothers 2016}). Studies on the
law has been focused on discussing the historical and political impetus
of passing the law (Shieh, 2018) or analyzing the regulatory regimes it
that has established and potential implications for INGOs operating in
China {[}Feng (\protect\hyperlink{ref-Feng:2017}{2017});Teets and Hsu
(\protect\hyperlink{ref-TeetsHsu:2016}{2016})). However, little work has
been done to examine the actual implementation situation of this law,
and how the dynamics of ONGOs' operations and projects have been
affected by the law after successfully gaining legal registration and
documentation. A couple of studies
(\protect\hyperlink{ref-Jia2017}{\textbf{Jia2017?}};
\protect\hyperlink{ref-YeHuang:2018}{Ye and Huang 2018})) conducted
reflections on the first year's implementation of China's ONGO Law,
including the initial phase of drafting and refining implementing
regulations and promotion, as well as training sessions conducted by
Public Security Bureaus in different locations. However, a more
up-to-date and comprehensive understanding of the effects of the ONGO
law is still lacking.

This paper aims to fill these gaps by empirically examining how the
``closing space'' hypothesis applies to China in the years after the
ONGO Law took effect. China provides an excellent setting for testing
these theories because China's promulgation of restrictive INGO law as
an authoritarian jurisdiction fits the observed global trends in recent
years, thus can serve as an representative case to deepen scholarly
understanding around these themes. Also, the level of ambiguity of the
legal framework gives ample room for arbitrary discretion and
conflicting attitudes by authorities, enabling us to analyze rules in
form (\emph{de jure}) as well as rules in use (\emph{de facto}).

Based on extant literature and theoretical understanding, we hypothesize
that the operation space INGOs are granted is associated with the level
of contentious their missions, i.e., the issue areas they work in. Since
the level of contentious is also manifested by the level of difficulty
they face while seeking lawful registration. We also hypothesize that
large operational space of INGOs is negatively associated the time
elapsed since the law took effect when they successfully got registered.

The follow section is structured as follow. In the data and methods
section, we first report the data cleaning and coding process and
measurements used in our empirical analysis. Then we explain the
rationale for choosing ordered beta regression to fit our models. In the
Results section, we report and interpret both descriptive analysis and
regression analysis results. We conclude the paper by discussing the
implications of our findings with respective to more general scholarly
understanding of the closing space of international civil society.

\hypertarget{data-and-methods}{%
\section{Data and methods}\label{data-and-methods}}

\hypertarget{data}{%
\subsection{Data}\label{data}}

The data used in this paper was collected from INGOs' public
registration documents disclosed by MPS's Overseas NGO Office on the
online service platform for INGOs. We also use ChinaFile's China ONGO
data for complementary purpose, we merge in the English organization
name in ChinaFile for the sake of transparency of our analysis to
broader communities. The data we collected spans from January 1, 2017,
when the law took effect, to December 31, 2021, with data for 633 ROs in
total. The filing document of ROs disclose the name, the registration
date, the registration authority (which public security bureau regulates
it), the PSU, the address and issue area or purposes of the RO and the
specific provinces they can work in. We code the variables we use in the
empirical analysis from the registration information. Most of the coding
and data cleaning work is objective data wrangling process, such as
parsing out the province each RO is in from the address, or calculating
the total number provinces approved in the registration document.
Meanwhile, the coding of issue areas are conducted by the authors based
on the areas set out Article 3 (specified above) and clustering of the
issue areas of the actually registered ROs. (to cross-validate among
authors).

\hypertarget{measurement}{%
\subsection{Measurement}\label{measurement}}

\hypertarget{dependent-variables}{%
\subsubsection{Dependent Variables}\label{dependent-variables}}

Our dependent variable is ``geo\_scope\_num'', the count of the total
number of provinces each RO is authorized to operate in. We derived this
variable from the specific list of authorized provinces as recorded in
the RO's registration documentation. As discussed above, we use this
measurement as a proxy for operational space for INGOs, because any
geographical constraints on the RO impacts on the flexibility of the
INGO operations. For example, in circumstances where emergency like the
COVID 19 pandemic hits, it would be extremely hard for INGOs to plan
beforehand which areas would need their service. Thus, we assume INGOs
that are not set up with any locally-bound purposes would need to or
hope to (if there is not yet such needs) be able to operate in as
broader geographical scope as possible.

\hypertarget{independent-variables}{%
\subsubsection{Independent Variables}\label{independent-variables}}

Our first independent variable is ``work\_field\_code1'', the issue area
we code from mission statement specified in the RO's registration
documentation. Given there is certain level of subjectivity in the
coding process, the coding of issue areas are cross-checked between the
researchers (to do). The coding rules for overlapping issue areas can be
found in the Appendix (to add). We decided to have 9 issue areas groups
based on list of lawful fields of work specified by the Article 3 of the
ONGO Law and how actual issue areas cluster for registered ROs.

Below is the list of issue areas INGOs' registered ROs are coded into.

\begin{itemize}
\tightlist
\item
  \textbf{Economy and trade}
\item
  \textbf{Environment} (including animal protection)
\item
  \textbf{Education} (including youth development)
\item
  \textbf{Charity and humanitarian} poverty alleviation, disaster
  relief, etc., including rural development
\item
  \textbf{Science and technology}
\item
  \textbf{Industry association}
\item
  \textbf{Health}, public health and health care system support
  (professional training)
\item
  \textbf{Arts and Culture} including sports and international culture
  exchange
\item
  \textbf{General}, usually grant-making organizations, Or working on
  general international communication, including among governments, or
  working on multiple fields not overlapping
\end{itemize}

Our second variable is ``time\_elapsed''. This variable is derived the
time difference between ROs' registration date and January 1, 2017 when
the law took effect. The longer the time elapsed since registration
should be achieved by INGOs, it indicates that it took longer time for
them to seek the content of both the PSU and Public Security Bureaus to
be their supervisions or regulators and grant them legal identity.

\hypertarget{control-variables}{%
\subsubsection{Control Variables}\label{control-variables}}

Our first control variable is ``local\_connet''. It is a dichotomous
variable indicating whether operating locally is built into the RO's
mission. There are cases where the aim or mission of the INGO attached
to a locality, either having a county or city name in their RO name or
purposes, or the INGO are actually set up by people in China and they
registered the RO to communicate between the ``hometown'' and the INGO
set up abroad. So we include this variable in our model to how having
local connection is associated with the operational space of ROs as well
as how the contentious level associates with operation space when we
account for this factor.

We also cluster our 633 RO cases by the province where they are
registered in our hierarchical Bayesian modeling. Thus, we account for
any variance caused by the socioeconomic and institutional differences
in various provinces of China. And the level province is the apporoiate
level to cluster because all the ROs are registered at the provincial
public security bureaus.

\hypertarget{regression-model}{%
\subsection{Regression Model}\label{regression-model}}

Our data provides us with rich descriptive detail of the types of INGOs
allowed to register in China following the advent of the ONGO law, and
we explore patterns in this data below. In addition to presenting
descriptive summary statistics, we create a multilevel Bayesian
regression model to examine the complex effects that issue area, local
connections, and registration timing have on organizational flexibility.
This approach allows us to hold specific variables constant and generate
predictions for hypothetical new, not-yet-registered INGOs, providing us
with stronger empirical implications. Additionally, Bayesian modeling
allows us to calculate the posterior distribution of our different
estimands. Rather than report a single value for the proportion of
registered INGOs worked on specific issues, we can estimate posterior
credible intervals that represent the probability that the true
proportion falls within a specific range. We report posterior medians
and 95\% credible intervals throughout our analysis. Importantly, these
intervals do not behave like more traditional frequentist confidence
intervals. Instead, they can be interpreted as the probability that a
reported estimate falls within the range, given the data and modeling
choices.

\begin{figure}

{\centering \includegraphics[width=0.8\textwidth,height=\textheight]{manuscript_files/figure-pdf/fig-province-count-collapsed-1.pdf}

}

\caption{\label{fig-province-count-collapsed}Count of the number of
provinces each INGO is authorized to operate in. The left panel shows
the full distribution of INGOs registered in 2--31 provinces; the right
panel collapses these in-between counts to a single category.}

\end{figure}

Modeling the count of provinces each INGO is authorized to operate in
presents a unique statistical challenge. As seen in
Figure~\ref{fig-province-count-collapsed}, roughly 30\% of INGOs are
registered in only one province, 40\% are registered nationwide, while
the remaining 30\% are registered in 2--31 provinces. Our main variable
of interest is thus a mix of continuous outcomes (i.e.~a range of
provinces) bounded between two discrete outcomes (i.e.~one province and
all provinces). Standard modeling approaches like ordinary least squares
regression (OLS) cannot accurately capture the unique features of the
data and will generate predictions that fall outside allowable bounds
(i.e.~negative counts of provinces or more than 32 provinces). If we
transform the count of provinces to a percentage, Beta regression would
work well, as it is naturally limited outcomes within a 0--1 range.
However, Beta regression cannot handle values that are exactly 0 or 1,
making it inappropriate for our data with its inflated counts at 0 (1)
and 100\% (32). To account for values at the bounds, we rely on ordered
Beta regression (\protect\hyperlink{ref-Kubinec:2022}{Kubinec 2022}),
and extension of zero-and-one-inflated Beta regression that allows us to
simultaneously model the continuous range of provinces (2--31) and the
discrete outcomes (1 province and 32 provinces) without relying on
percentages. We can thus explore the dynamics of each of our independent
variables of interest in multiple ways---we can see (1) how each
variable predicts that an organizations works in one province,
nationwide, or somewhere in between, and (2) how each variable predicts
the overall expected count of provinces.

Equation~\ref{eq-ordbeta} provides a formal definition of our modeling
choices. Since we are primarily interested in how an INGO's issue area,
its local connections, and the timing of its registration after January
2017, we include these as explanatory variables. We also include
province-specific random offsets for each intercept to account for
between-region differences in how INGOs are regulated. We use weakly
informative priors for all model parameters.

\begin{figure*}

\begin{equation}\protect\hypertarget{eq-ordbeta}{}{
\begin{aligned}
\text{Count of provinces}\ \sim&\ \operatorname{Ordered\ Beta}(\mu_{i_j}, \phi_y, k_{0_y}, k_{1_y}) & \text{Registered provinces for INGO $i$ in province $j$}\\[8pt]
\mu_{i_j} =&\ (\beta_0 + b_{0_j}) + \beta_1\ \text{Issue area}\ + & \text{Average outcome}\\
&\ \beta_2\ \text{Local connections}\ + \\
&\ \beta_3\ \text{Years since law took effect} \\
b_{0_j} =&\ \mathcal{N}(0, \sigma_0) & \text{Random province offsets} \\[8pt]
\beta_0\ \sim&\ \operatorname{Student\,t}(\nu = 3, \mu = 0, \sigma = 2.5) & \text{Prior for global intercept} \\
\beta_{1..3}\ \sim&\ \mathcal{N}(0, 5) & \text{Prior for global coefficients} \\
\sigma_0\ \sim&\ \operatorname{Student\,t}(3, 0, 2.5) & \text{Prior for between-province variability} \\
\phi_y\ \sim&\ \operatorname{Exponential}(1 / 100) & \text{Prior for within-province variability} \\
k_{0_y}, k_{1_y}\ \sim&\ \operatorname{Dirichlet}(1, 1, 1) & \text{Prior for 0–continuous and continuous–1 cutpoints} \\
\end{aligned}
}\label{eq-ordbeta}\end{equation}

\end{figure*}

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{descriptive-results}{%
\subsection{Descriptive Results}\label{descriptive-results}}

\hypertarget{regression-results}{%
\subsection{Regression Results}\label{regression-results}}

\hypertarget{issue-area}{%
\subsubsection{Issue area}\label{issue-area}}

\hypertarget{local-connections}{%
\subsubsection{Local connections}\label{local-connections}}

In our second empirical expectation, we posit that since INGOs that seek
out local connections and that are focused on more local China-specific
issues, those organizations should be registered in fewer provinces. The
results from our model confirm this expectation.

TODO 12ish expected provinces for INGOs with no local connections; 21ish
for INGOs with local connections

TODO We can take advantage of the continuous + discrete features of
ordered beta and see BLAH BLAH. After simulating 1,000 hypothetical new
INGOs, organizations without local connections are predicted to work
nationally in all provinces nearly 50\% of the time (ASDF-ASDF credible
interval), and are predicted to work in 2 or more provinces 35\% of the
time. These organizations with no local connections or local
programmatic focus are only predicted to work in a single province
15ish\% of the time. In contrast, INGOs \emph{with} local connections
are far more likely to only work in one province (35\%), or only work in
a handful of provinces. These locally-focused organizations are only
predicted to work nationally 25\% of the time.

TODO Graphs

\hypertarget{registration-timing}{%
\subsubsection{Registration timing}\label{registration-timing}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Carothers:2016}{}}%
Carothers, Thomas. 2016. {``Closing {Space} for {International
Democracy} and {Human Rights Support}.''} \emph{Journal of Human Rights
Practice} 8 (3): 358--77. \url{https://doi.org/10.1093/jhuman/huw012}.

\leavevmode\vadjust pre{\hypertarget{ref-ChaudhryHeiss:2020}{}}%
Chaudhry, Suparna, and Andrew Heiss. 2020. {``Closing {Space} and the
{Restructuring} of {Global Activism}: {Causes} and {Consequences} of the
{Global Crackdown} on {NGOs}.''}

\leavevmode\vadjust pre{\hypertarget{ref-ChaudhryHeiss:2022a}{}}%
---------. 2022a. {``Closing {Space} and the {Restructuring} of {Global
Activism Causes} and {Consequences} of the {Global Crackdown} on
{NGOs}.''} In \emph{Beyond the {Boomerang}: {From Transnational Advocacy
Networks} to {Transcalar Advocacy} in {International Politics}}, edited
by Christopher L. Pallas and Elizabeth A. Bloodgood, 23--35.
{Tuscaloosa, Alabama}: {University of Alabama Press}.

\leavevmode\vadjust pre{\hypertarget{ref-ChaudhryHeiss:2022}{}}%
---------. 2022b. {``{NGO} Repression as a Predictor of Worsening Human
Rights Abuses.''} \emph{Journal of Human Rights} 21 (2): 123--40.
\url{https://doi.org/10.1080/14754835.2022.2030205}.

\leavevmode\vadjust pre{\hypertarget{ref-DupuyPrakash:2020}{}}%
Dupuy, Kendra, and Aseem Prakash. 2020. {``Global {Backlash} Against
{Foreign Funding} to {Domestic Nongovernmental Organizations}.''} In
\emph{The {Nonprofit Sector}: {A Research Handbook}, {Third Edition28}.
{Global Backlash} Against {Foreign Funding} to {Domestic Nongovernmental
Organizations}}, 618--30. {Stanford University Press}.
\url{https://doi.org/10.1515/9781503611085-038}.

\leavevmode\vadjust pre{\hypertarget{ref-Feng:2017}{}}%
Feng, Chongyi. 2017. {``The {NGO} Law in {China} and Its Impact on
{Overseas} Funded {NGOs}.''} \emph{Cosmopolitan Civil Societies: An
Interdisciplinary Journal} 9 (3, 3): 95--105.
\url{https://doi.org/10.5130/ccs.v9i3.5601}.

\leavevmode\vadjust pre{\hypertarget{ref-Han:2011}{}}%
Han, Junkui. 2011. \emph{Overeseas NGO in China: Going Together with an
Opening-up China}. {Social Sciences Academic Press of China}.

\leavevmode\vadjust pre{\hypertarget{ref-Jia:2017}{}}%
Jia, Xijin. 2017. {``Analysis on the Effect of {China}'s Overseas {NGO}
Law Under the Differences in Legal Thinking.''} \emph{The China
Nonprofit Review} 9 (1): 23--43.

\leavevmode\vadjust pre{\hypertarget{ref-Kubinec:2022}{}}%
Kubinec, Robert. 2022. {``Ordered {Beta Regression}: {A Parsimonious},
{Well-Fitting Model} for {Continuous Data} with {Lower} and {Upper
Bounds}.''} \emph{Political Analysis}, 1--18.
\url{https://doi.org/10.1017/pan.2022.20}.

\leavevmode\vadjust pre{\hypertarget{ref-Li:2020}{}}%
Li, Shuoyan. 2020. {``Global {Civil Society Under} the {New INGO
Regulatory Law}: {A Comparative Case Study} on {Two INGOs} in
{China}.''} \emph{VOLUNTAS: International Journal of Voluntary and
Nonprofit Organizations} 31 (4): 751--61.
\url{https://doi.org/10.1007/s11266-019-00101-y}.

\leavevmode\vadjust pre{\hypertarget{ref-Shieh:2018}{}}%
Shieh, Shawn. 2018. {``The {Chinese State} and {Overseas NGOs}: {From
Regulatory Ambiguity} to the {Overseas NGO Law}.''} \emph{Nonprofit
Policy Forum} 9 (1). \url{https://doi.org/10.1515/npf-2017-0034}.

\leavevmode\vadjust pre{\hypertarget{ref-Sidel:2023}{}}%
Sidel, Mark. 2023. {``Vietnam's {Closing Legal Space} for {Civil
Society} --- {U}.{S}.-{Asia Law Institute}.''} {U.S.-Asia Law
Institute}. 2023.
\url{https://usali.org/usali-perspectives-blog/vietnams-closing-space-for-civil-society}.

\leavevmode\vadjust pre{\hypertarget{ref-TeetsHsu:2016}{}}%
Teets, Jessica, and Carolyn Hsu. 2016. {``Is {China} s {New Overseas NGO
Management Law Sounding} the {Death Knell} for {Civil Society}? {Maybe
Not}.''} \emph{The Asia-Pacific Journal}.

\leavevmode\vadjust pre{\hypertarget{ref-ToeplerZimmerFrohlich:2020}{}}%
Toepler, Stefan, Annette Zimmer, Christian Fröhlich, and Katharina
Obuch. 2020. {``The {Changing Space} for {NGOs}: {Civil Society} in
{Authoritarian} and {Hybrid Regimes}.''} \emph{VOLUNTAS: International
Journal of Voluntary and Nonprofit Organizations} 31 (4): 649--62.
\url{https://doi.org/10.1007/s11266-020-00240-7}.

\leavevmode\vadjust pre{\hypertarget{ref-Ye:2021}{}}%
Ye, Meng. 2021. {``Building an Enabling Legal Environment: Laws and
Policies on Social Enterprises in {China}.''} \emph{Journal of Asian
Public Policy} 14 (2): 182--99.
\url{https://doi.org/10.1080/17516234.2020.1824263}.

\leavevmode\vadjust pre{\hypertarget{ref-YeHuang:2018}{}}%
Ye, Meng, and Haoming Huang. 2018. {``Observations of the First Year
Implementation of the Law of Activities of Overseas NGOs in China.''} In
\emph{Annual Report on China's Philanthropy Development (2018)},
208--33. {Beijing}: {Social Sciences Academic Press of China}.

\leavevmode\vadjust pre{\hypertarget{ref-Yin:2009}{}}%
Yin, Deyong. 2009. {``China's {Attitude} Toward {Foreign NGOs}.''}
\emph{Washington University Global Studies Law Review} 8 (3): 521--44.
\url{https://heinonline.org/HOL/P?h=hein.journals/wasglo8\&i=529}.

\end{CSLReferences}

\end{document}

### 2023-04-09 notebook/analysis-issue.qmd
Move epreds to targets too

@@
 tar_load(ongo)
-tar_load(c(m_full_ordbeta, preds_issue))
+tar_load(c(m_full_ordbeta, preds_issue, epreds_issue))
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
@@
 ```{r plot-epred-issue}
-epreds <- m_full_ordbeta |> 
-  epred_draws(datagrid(model = m_full_ordbeta, work_field_code1 = unique), 
-              ndraws = 1000)
-
-epreds |> 
-  ungroup() |> 
+epreds_issue |> 
   mutate(work_field_code1 = fct_reorder(work_field_code1, .epred)) |> 
@@
   summarize(count = n()) |> 
-  group_by(work_field_code1) |> 
-  mutate(prop = count / sum(count) * 100)
+  group_by(work_field_code1, draw) |> 
+  mutate(prop = count / sum(count))
 

### 2023-04-09 R/funs_models.R

@@ -116,7 +116,7 @@ f_preds_local <- function(model, ndraws = 100) {
     mutate(preds = map(draw, ~{
       model |> 
         predicted_draws(datagrid(model = model, local_connect = unique), 
-                        ndraws = 1000)
+                        ndraws = 1000, seed = 58214)
     }))
 }
 
@@ -125,6 +125,27 @@ f_preds_timing <- function(model, ndraws = 100) {
     mutate(preds = map(draw, ~{
       model |> 
         predicted_draws(datagrid(model = model, years_since_law = 0:5), 
-                        ndraws = 1000)
+                        ndraws = 1000, seed = 58214)
     }))
+}
+
+f_epreds_issue <- function(model, ndraws = 1000) {
+  model |> 
+    epred_draws(datagrid(model = model, work_field_code1 = unique), 
+                ndraws = ndraws, seed = 58214) |> 
+    ungroup()
+}
+
+f_epreds_local <- function(model, ndraws = 1000) {
+  model |> 
+    epred_draws(datagrid(model = model, local_connect = unique), 
+                ndraws = ndraws, seed = 58214) |> 
+    ungroup()
+}
+
+f_epreds_timing <- function(model, ndraws = 1000) {
+  model |> 
+    epred_draws(datagrid(model = model, years_since_law = 0:5), 
+                ndraws = ndraws, seed = 58214) |> 
+    ungroup()
 }

### 2023-04-09 _targets.R

@@ -68,6 +68,10 @@ list(
   tar_target(preds_local, f_preds_local(m_full_ordbeta)),
   tar_target(preds_timing, f_preds_timing(m_full_ordbeta)),
   
+  tar_target(epreds_issue, f_epreds_issue(m_full_ordbeta)),
+  tar_target(epreds_local, f_epreds_local(m_full_ordbeta)),
+  tar_target(epreds_timing, f_epreds_timing(m_full_ordbeta)),
+  
   ## Analysis notebook ----
   tar_quarto(manuscript_nice, path = "manuscript", quiet = FALSE),
   tar_quarto(website, path = ".", quiet = FALSE),

### 2023-04-09 manuscript/manuscript.qmd
Add issue area and local connections section

@@
 tar_load(ongo_mapdata)
+tar_load(c(preds_issue, preds_local, preds_timing,
+           epreds_issue, epreds_local, epreds_timing))
 
@@
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+
+prop_to_provinces <- function(x, lower = 1, upper = 32) {
+  (x * (upper - lower)) + lower
+}
 ```
@@
 
+Following our first empirical expectation, we predict that INGOs working on less contentious issues should be registered in more provinces and have more geographic flexibility in operating throughout the country.
+To explore this, we can take advantage of the simultaneous continuous and discrete features of ordered Beta regression and see how often an INGO in each issue area is predicted to work in a single province, across all provinces, or some number in between.
+@fig-issue-preds-1 presents a summary of predicted posterior outcomes for 1,000 hypothetical INGOs, varying each possible issue area and holding all other variables at their mean or modal values.
+Several notable trends emerge from the model results.
+INGOs focused on arts and culture are overwhelming the most likely kind of organization to work nationally—arts and culture organizations are predicted to work in all 32 provinces 80% of the time (with a credible interval of 78–83%) and are only predicted to work in a single province a rare 3–5% of the time.
+Education-focused INGOs, on the other hand, are the least likely kind of organization to be registered in all 32 provinces and are predicted to do so only 32–38% of the time.
+Education INGOs are the most likely to be registered in only one province, with that predicted outcome appearing 24–29% of the time—at least 10 percentage points higher than any other issue area's predicted proportion.
+All other issue areas follow roughly the patterns in predictions: the most common outcome is for organizations to work nationally (50–60% of the time), followed by working in at least 2 provinces (25–40% of the time), followed by working in a single province (10–20% of the time).
+@fig-issue-preds-2 shows the continuous posterior distribution of the average number of provinces INGOs are expected to be registered in across all types of issue areas, but accounting for the 1- and 32-only provinces simultaneously.
+We can see a similar trend—arts and culture INGOs are predicted to work in 28–30 provinces on average, while education INGOs are only predicted to work in 12–20.
+All other issues range between 20–28 provinces.
+
+::: {#fig-issue-preds layout-ncol=1}
+
+```{r fig-issue-preds-1, fig.width=6, fig.height=4.5}
+#| include: true
+#| echo: false
+#| fig-subcap: "Proportions of posterior predictions of INGOs working in 1 province, all 32 provinces, or somewhere in between. Distinct x-axis categories sum to 100% across the panels."
+preds_issue_plot <- preds_issue |> 
+  unnest(preds) |> 
+  mutate(outcome = case_when(
+    .prediction == 0 ~ "1 province",
+    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
+    .prediction == 1 ~ "32 provinces"
+  )) %>% 
+  group_by(outcome, work_field_code1, draw) %>% 
+  summarize(count = n()) |> 
+  group_by(work_field_code1, draw) |> 
+  mutate(prop = count / sum(count)) |> 
+  ungroup() |> 
+  mutate(work_field_code1 = fct_reorder(work_field_code1, prop))
+
+# preds_issue_plot |> 
+#   group_by(outcome, work_field_code1) |>
+#   median_qi(prop)
+
+ggplot(preds_issue_plot, aes(x = work_field_code1, y = prop)) +
+  stat_pointinterval(color = clrs[5], .width = 0.95, fatten_point = 1) +
+  facet_wrap(vars(outcome), ncol = 1, scales = "free_y") +
+  scale_x_discrete(labels = label_wrap(10)) +
+  scale_y_continuous(labels = label_percent()) +
+  labs(x = NULL, y = "Proportion of predictions",
+       caption = "Point shows posterior median; lines show 95% credible interval") +
+  theme_ongo()
+```
+
+```{r fig-issue-preds-2}
+#| include: true
+#| echo: false
+#| fig-subcap: "Distribution of the expectation of posterior predictions.
+These distributions take into account single-province and nationwide predictions and represent the overall conditional average geographic range for INGOs."
+epreds_issue |> 
+  mutate(work_field_code1 = fct_reorder(work_field_code1, .epred)) |> 
+  ggplot(aes(x = .epred, y = work_field_code1)) +
+  stat_halfeye(fill = clrs[5], .width = c(0.8, 0.95)) +
+  scale_x_continuous(labels = label_percent(),
+                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
+                                         name = "Expected provinces",
+                                         breaks = seq(8, 32, 4))) +
+  guides(fill = "none") +
+  labs(x = "Expected proportion of provinces", y = NULL,
+       caption = "Point shows posterior median; lines show 80% and 95% credible intervals") +
+  theme_ongo() +
+  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
+```
+
+Posterior predictions from ordered Beta regression model, conditional on organization issue area.
+
+:::
+
 ### Local connections
@@
 The results from our model confirm this expectation.
+@fig-local-preds-1 shows the distribution of predicted posterior outcomes for 1,000 hypothetical INGOs.
+Organizations without local connections are predicted to work nationally across all provinces nearly half of the time (with a 95% credible interval of 46–51%), and are predicted to work in two or more provinces 32–37% of the time.
+These organizations with no local connections or local programmatic focus are only predicted to work in a single province 15–19% of the time.
+In contrast, INGOs *with* local connections are far more likely to only work in one province (32–38%), or only work in a handful of provinces (36–41%).
+For these locally-focused organizations, the least common prediction is to work nationally, with only a 23–29% probability.
+@fig-local-preds-2 shows the posterior distribution of the average number of provinces INGOs are expected to be registered in, conditional on their local connections.
+The same relationship holds—an INGO without local connections is predicted to work in 19–24 provinces on average, while an organization with local connections is only predicted to work in 8–17.
 
-TODO 12ish expected provinces for INGOs with no local connections; 21ish for INGOs with local connections
+```{r fig-local-preds, fig.width=6, fig.height=2.5}
+#| include: true
+#| echo: false
+#| fig-cap: "Posterior predictions from ordered Beta regression model, conditional on having local connections."
+#| fig-subcap: 
+#|   - "Proportions of posterior predictions of INGOs working in 1 province, all 32 provinces, or somewhere in between. Distinct x-axis categories sum to 100% across the panels."
+#|   - "Distribution of the expectation of posterior predictions.
+These distributions take into account single-province and nationwide predictions and represent the overall conditional average geographic range for INGOs."
+preds_local_plot <- preds_local |> 
+  unnest(preds) |> 
+  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
+  mutate(outcome = case_when(
+    .prediction == 0 ~ "1 province",
+    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
+    .prediction == 1 ~ "32 provinces"
+  )) %>% 
+  group_by(outcome, local_connect, draw) %>% 
+  summarize(count = n()) |> 
+  group_by(local_connect, draw) |> 
+  mutate(prop = count / sum(count))
 
-TODO We can take advantage of the continuous + discrete features of ordered beta and see BLAH BLAH.
-After simulating 1,000 hypothetical new INGOs, organizations without local connections are predicted to work nationally in all provinces nearly 50% of the time (ASDF-ASDF credible interval), and are predicted to work in 2 or more provinces 35% of the time.
-These organizations with no local connections or local programmatic focus are only predicted to work in a single province 15ish% of the time.
-In contrast, INGOs *with* local connections are far more likely to only work in one province (35%), or only work in a handful of provinces.
-These locally-focused organizations are only predicted to work nationally 25% of the time.
+# preds_local_plot |>
+#   group_by(outcome, local_connect) |>
+#   median_qi(prop)
+#
+# epreds_local |>
+#   mutate(.epred = prop_to_provinces(.epred)) |> 
+#   group_by(local_connect) |>
+#   median_qi(.epred)
 
-TODO Graphs
+ggplot(preds_local_plot, aes(x = local_connect, y = prop)) +
+  stat_pointinterval(color = clrs[2], .width = c(0.95), fatten_point = 1) +
+  facet_wrap(vars(outcome)) +
+  scale_x_discrete(labels = label_wrap(10)) +
+  scale_y_continuous(labels = label_percent()) +
+  labs(x = NULL, y = "Proportion of predictions",
+       caption = "Point shows posterior median; lines show 95% credible interval") +
+  theme_ongo()
+
+epreds_local |> 
+  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
+  ggplot(aes(x = .epred, y = local_connect)) +
+  stat_halfeye(fill = clrs[2], .width = c(0.8, 0.95)) +
+  scale_x_continuous(labels = label_percent(),
+                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
+                                         name = "Expected provinces",
+                                         breaks = seq(8, 32, 4))) +
+  guides(fill = "none") +
+  labs(x = "Expected proportion of provinces", y = NULL,
+       caption = "Point shows posterior median; lines show 80% and 95% credible intervals") +
+  theme_ongo() +
+  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
+```
+
+INGOs with locally focused missions and connections with local provincial officials are thus far more likely to purposely limit their activities to specific provinces, while organizations with broader non-local missions have a larger geographic reach.
+While we cannot precisely tell which direction the causal story works with this phenomenon, we can make some reasonable speculations.
+It is likely that locally-oriented INGOs purposely network and seek out connections with local PSUs before formally registering, thus fostering better relationships with government officials and furthering the organization's mission within its limited provinces.
+It is also likely, given the high probability of national reach, that organizations without local connections purposely do not spend the time and effort to cultivate those relationships, as it is not necessary to operate across many provinces.
+A rival explanation that having local connections reduces an organization's flexibility does not seem warranted.
+Although INGOs with local connections do have a more limited geographic scope, INGOs appear to purposely limit the number of provinces they work in in order to focus more on their local work.
 

### 2023-04-10 manuscript/manuscript.qmd
Add speculation for education INGOs

@@
 
-```{r fig-issue-preds-1, fig.width=6, fig.height=4.5}
+```{r fig-issue-preds-1, fig.width=6, fig.height=4.5, cache=TRUE}
 #| include: true
@@
     .prediction == 1 ~ "32 provinces"
-  )) %>% 
-  group_by(outcome, work_field_code1, draw) %>% 
+  )) |> 
+  group_by(outcome, work_field_code1, draw) |> 
   summarize(count = n()) |> 
@@
 
+As explained previously, we expect that the contentiousness of an NGO's issue area should influence its geographic reach and overall flexibility.
+No INGOs engaged in contentious issues like human rights advocacy have successfully registered in China, but there is some slight variation in the level of contention even among organizations working on less contentious issues like humanitarian assistance, health, and the environment.
+Education is particularly notable as the least flexible and most geographically restricted subsector.
+While education is typically considered a low-contention issue, in China fears of Western influence through educational institutions were an original impetus for the ONGO law.
+In 2006, an article in a CCP-owned newspaper warned that the growing presence of international NGOs would "undermine national security," "destroy political stability," "foster corruption," "propagate foreign practices," and "spy on and gather information on China's military, political, and economic information" [@Yin:2009, 534].
+The idea that INGOs would "propagate foreign practices" had especially powerful salience, since increased exposure to the West through international NGOs had the potential to "lead to adoption of Western ideas of liberty, further endangering government control over the populace" [@HsiaWhite:2002, 337].
+Educational NGOs were one particular avenue for the West to exert influence in the country—the directors and presidents of dozens of China's largest domestic NGOs have received doctoral degrees from and hold visiting appointments at Cornell, Duke, UNC-Chapel Hill, Harvard, Yale, and other prominent US universities [@Wang:2012, 108–9], and their training and connections abroad have influenced their programming and advocacy at home.
+In 2006, one Chinese NGO leader candidly explained that "foreign influence is definitely great.
+There is conceptual influence.
+Foreign NGOs' working methods also affect Chinese NGOs" [@Wang:2012, 110].
+Education can thus be seen as one of the more contentious issues allowed under the ONGO law, and thus more closely regulated and restricted.
+
 ### Local connections
@@
     .prediction == 1 ~ "32 provinces"
-  )) %>% 
-  group_by(outcome, local_connect, draw) %>% 
+  )) |> 
+  group_by(outcome, local_connect, draw) |> 
   summarize(count = n()) |> 
@@
 
-INGOs with locally focused missions and connections with local provincial officials are thus far more likely to purposely limit their activities to specific provinces, while organizations with broader non-local missions have a larger geographic reach.
+International NGOs with locally focused missions and connections with local provincial officials are thus far more likely to purposely limit their activities to specific provinces, while organizations with broader non-local missions have a larger geographic reach.
 While we cannot precisely tell which direction the causal story works with this phenomenon, we can make some reasonable speculations.

### 2023-04-10 manuscript/manuscript.qmd
Add registration timing section

@@
 We test whether and how INGO operational space under the ONGO law is influenced by organizations’ issue areas.
-We argue that the less contensious the issue areas INGOs work in the more likely they are granted greater operational space, measured by thenumber of provinces they are allowed to work in by the registration documentation.
+We argue that the less contensious the issue areas INGOs work in the more likely they are granted greater operational space, measured by the number of provinces they are allowed to work in by the registration documentation.
 China provides an excellent setting for testing the "closing space" and "changing space" theoretical understanding because the 2017 ONGO law hypothetically regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities.
@@
 tar_load(c(preds_issue, preds_local, preds_timing,
-           epreds_issue, epreds_local, epreds_timing))
+           epreds_issue, epreds_local, epreds_timing,
+           epreds_timing_local))
 
@@
 \begin{aligned}
-\text{Count of provinces}\ \sim&\ \operatorname{Ordered\ Beta}(\mu_{i_j}, \phi_y, k_{0_y}, k_{1_y}) & \text{Registered provinces for INGO $i$ in province $j$}\\[8pt]
+\text{Count of provinces}\ \sim&\ \operatorname{Ordered\,Beta}(\mu_{i_j}, \phi_y, k_{0_y}, k_{1_y}) & \text{Registered provinces for INGO $i$ in province $j$}\\[8pt]
 \mu_{i_j} =&\ (\beta_0 + b_{0_j}) + \beta_1\ \text{Issue area}\ + & \text{Average outcome}\\
@@
 
-## Descriptive Results
+## Descriptive findings
 
-## Regression Results
+## Posterior predictions
 
@@
 To explore this, we can take advantage of the simultaneous continuous and discrete features of ordered Beta regression and see how often an INGO in each issue area is predicted to work in a single province, across all provinces, or some number in between.
-@fig-issue-preds-1 presents a summary of predicted posterior outcomes for 1,000 hypothetical INGOs, varying each possible issue area and holding all other variables at their mean or modal values.
+@fig-issue-preds-ordbeta presents a summary of predicted posterior outcomes for 1,000 hypothetical INGOs, varying each possible issue area and holding all other variables at their mean or modal values.
 Several notable trends emerge from the model results.
@@
 
-```{r fig-issue-preds-1, fig.width=6, fig.height=4.5, cache=TRUE}
+```{r fig-issue-preds-ordbeta, fig.width=6, fig.height=4.5, cache=TRUE}
 #| include: true
@@
 
-# Discussion
+The ONGO Law officially came into effect on January 1, 2017, and as seen previously in @fig-registration-timeline, the first year of the law saw the greatest total number of registrations.
+In our third empirical expectation, we propose that these early registrants under the new law were both less of a threat to regime stability and a higher priority for bureaucratic processing, and thus should be registered in more provinces and have more geographic flexibility throughout the country.
+However, the results of our model support the *reverse* of this expectation.
+@fig-timing-preds-1 once again shows the predicted posterior outcomes for 1,000 simulated INGOs across a range of time since January 2017.
+Organizations that registered in the first year are predicted to work in all provinces 41–46% of the time, and are predicted to work in two or more provinces 34–39% of the time.
+These early INGOs are the most likely to be registered in only one province and are predicted to do so 17–23% of the time.
+After the initial wave of registrations in 2017, the likelihood of nationwide reach steadily increases and replaces both the probability of a single province or a partial range of provinces.
+By the end of 2022—5 years after the ONGO Law took effect—the probability of national -level registration increases to 55–61% while the probability of working in a range of provinces increases to predicted to work in two or more provinces increase to 27–32%.
+These late INGOs are the least likely to be registered in only one province and are predicted to do so only 17–22% of the time.
+@fig-timing-preds-2 demonstrates the same results with the posterior distribution of the expected count of provinces over five years since 2017.
+INGOs that register early are predicted to work in 17–22 provinces, while those that wait until 2022 are predicted to work in 21–28.
+
+::: {#fig-timing-preds layout-ncol=1}
+
+```{r fig-timing-preds-1, fig.width=6, fig.height=3}
+#| include: true
+#| echo: false
+#| fig-subcap: "Proportions of posterior predictions of INGOs working in 1 province, all 32 provinces, or somewhere in between. Distinct x-axis values sum to 100% across the panels."
+preds_timing_plot <- preds_timing |> 
+  unnest(preds) |> 
+  mutate(outcome = case_when(
+    .prediction == 0 ~ "1 province",
+    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
+    .prediction == 1 ~ "32 provinces"
+  )) %>% 
+  group_by(outcome, years_since_law, draw) %>% 
+  summarize(count = n()) |> 
+  group_by(years_since_law, draw) |> 
+  mutate(prop = count / sum(count))
+
+# preds_timing_plot |>
+#   group_by(outcome, years_since_law) |>
+#   median_qi(prop)
+# 
+# epreds_timing |>
+#   mutate(.epred = prop_to_provinces(.epred)) |>
+#   group_by(years_since_law) |>
+#   median_qi(.epred)
+
+ggplot(preds_timing_plot, aes(x = years_since_law, y = prop)) +
+  stat_lineribbon(.width = c(0.5, 0.8, 0.95), 
+                  alpha = 0.35, fill = clrs[7], color = clrs[7]) +
+  facet_wrap(vars(outcome), nrow = 1) +
+  scale_y_continuous(labels = label_percent()) +
+  labs(x = "Years since law took effect (2017)", 
+       y = "Proportion of predictions",
+       caption = "Shaded regions show the 50%, 80%, and 95% credible intervals") +
+  theme_ongo()
+```
+
+```{r fig-timing-preds-2, fig.width=6, fig.height=3}
+#| include: true
+#| echo: false
+#| fig-subcap: "Distribution of the expectation of posterior predictions.
+These distributions take into account single-province and nationwide predictions and represent the overall conditional average geographic range for INGOs."
+epreds_timing |> 
+  ggplot(aes(x = years_since_law, y = .epred)) +
+  stat_lineribbon(.width = c(0.5, 0.8, 0.95), 
+                  alpha = 0.35, fill = clrs[7], color = clrs[7]) +
+  scale_y_continuous(labels = label_percent(),
+                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
+                                         name = "Expected provinces",
+                                         breaks = seq(15, 27, 3))) +
+  guides(fill = "none") +
+  labs(x = "Years since law took effect (2017)", y = "Expected proportion of provinces",
+       caption = "Shaded regions show the 50%, 80%, and 95% credible intervals") +
+  theme_ongo() +
+  theme(axis.title.y.right = element_text(hjust = 1, margin = margin(l = 10), angle = 90),
+        axis.ticks.y.right = element_line(linewidth = 0.25, color = "grey50"))
+```
+
+Posterior predictions from ordered Beta regression model, conditional on time since registration.
+
+:::
+
+We lack sufficient theory or data to explain why this trend goes against our expectations, but we can again make reasonable speculations.
+As we saw previously with INGOs and local connections, organizations appear to strategically seek out the best avenues and methods for registering.
+Organizations that participated in the initial wave of registrations in 2017 likely had closer connections with local officials and were able to speed through the bureaucratic process registration more easily.
+As a preliminary test of this speculation, we rerun our main model with an interaction between years since registration and local connections to see how the effect of local connections changes over time.
+As seen in @fig-timing-local, early registrants in 2017 without local connections are more likely to have a larger geographic reach, registering in an average of 19–23 provinces, while their locally-focused counterparts are only expected to register in an average of 7–16 provinces.
+Accordingly, it may be that organizations with local connections are more likely to register early because of their pre-existing bureaucratic relationships, while organizations with a larger national reach take longer to undertake the registration process and thus register later.
+Further research on this point is warranted.
+
+```{r fig-timing-local, fig.width=6, fig.height=3}
+#| include: true
+#| echo: false
+#| fig-cap: "Distribution of the expectation of posterior predictions across both time and local connections.
+These distributions take into account single-province and nationwide predictions and represent the overall conditional average geographic range for INGOs."
+epreds_timing_local |> 
+  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
+  ggplot(aes(x = years_since_law, y = .epred)) +
+  stat_lineribbon(.width = c(0.5, 0.8, 0.95), 
+                  alpha = 0.35, fill = clrs[7], color = clrs[7]) +
+  scale_y_continuous(labels = label_percent(),
+                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
+                                         name = "Expected provinces",
+                                         breaks = seq(3, 27, 4))) +
+  guides(fill = "none") +
+  labs(x = "Years since law took effect (2017)", y = "Expected proportion of provinces",
+       caption = "Shaded regions show the 50%, 80%, and 95% credible intervals") +
+  facet_wrap(vars(local_connect)) +
+  theme_ongo() +
+  theme(axis.title.y.right = element_text(hjust = 1, margin = margin(l = 10), angle = 90),
+        axis.ticks.y.right = element_line(linewidth = 0.25, color = "grey50"))
+```
+
+# Discussion and conclusion
 

### 2023-04-10 R/funs_models.R

@@ -88,6 +88,22 @@ f_full_ordbeta <- function(data) {
   return(model)
 }
 
+f_full_interaction_ordbeta <- function(data) {
+  library(ordbetareg)
+  
+  BAYES_SEED <- 860215  # From random.org
+  
+  model <- ordbetareg(
+    bf(
+      province_count ~ work_field_code1 + local_connect * years_since_law + (1 | province_code)
+    ), 
+    data = data,
+    true_bounds = c(1, 32),
+    seed = BAYES_SEED)
+  
+  return(model)
+}
+
 # f_lotsa_preds <- function(model, column_name, ndraws = 100) {
 #   # This dynamically generates the grid, essentially building this command:
 #   #   datagrid(model = model, local_connect = unique)
@@ -146,6 +162,14 @@ f_epreds_local <- function(model, ndraws = 1000) {
 f_epreds_timing <- function(model, ndraws = 1000) {
   model |> 
     epred_draws(datagrid(model = model, years_since_law = 0:5), 
+                ndraws = ndraws, seed = 58214) |> 
+    ungroup()
+}
+
+f_epreds_timing_local <- function(model, ndraws = 1000) {
+  model |> 
+    epred_draws(datagrid(model = model, 
+                         local_connect = unique, years_since_law = 0:5), 
                 ndraws = ndraws, seed = 58214) |> 
     ungroup()
 }

### 2023-04-10 _targets.R

@@ -62,6 +62,7 @@ list(
   
   tar_target(m_full_zoib, f_full_zoib(ongo)),
   tar_target(m_full_ordbeta, f_full_ordbeta(ongo)),
+  tar_target(m_full_interaction_ordbeta, f_full_interaction_ordbeta(ongo)),
   
   ## Posterior predictions ----
   tar_target(preds_issue, f_preds_issue(m_full_ordbeta)),
@@ -71,6 +72,7 @@ list(
   tar_target(epreds_issue, f_epreds_issue(m_full_ordbeta)),
   tar_target(epreds_local, f_epreds_local(m_full_ordbeta)),
   tar_target(epreds_timing, f_epreds_timing(m_full_ordbeta)),
+  tar_target(epreds_timing_local, f_epreds_timing_local(m_full_ordbeta)),
   
   ## Analysis notebook ----
   tar_quarto(manuscript_nice, path = "manuscript", quiet = FALSE),

### 2023-04-10 manuscript/manuscript.qmd
Add descriptive section

@@
 library(tidybayes)
+library(sf)
+library(ggrepel)
 library(marginaleffects)
@@
 # Load targets 
-tar_load(ongo)
-tar_load(ongo_mapdata)
+tar_load(c(ongo, ongo_mapdata))
 tar_load(c(preds_issue, preds_local, preds_timing,
@@
 
-## Descriptive findings
+## Descriptive overview of data
+
+Before examining the posterior results of the statistical, we first describe some of the general trends in INGO registration during the first 5 years of the ONGO law.
+We use our data to explore (1) when INGOs registered, (2) what kinds of issues registered INGOs work on, and (3) how large of a geographic reach INGOs have.
+
+First, @fig-registration-timeline shows the distribution of the count of new INGO registrations since January 1, 2017.
+A couple dozen organizations were able to register immediately after the law took effect during the first quarter of 2017, while hundreds more registered during the rest of that year.
+Nearly half of all currently-registered INGOs in China—48%—registered in 2017.
+After the initial first-year wave, the count of new registrations has declined slowly since 2018.
+
+```{r fig-registration-timeline, fig.width=6, fig.height=3}
+#| include: true
+#| echo: false
+#| fig-cap: "Count of international NGO registrations until the 2017 ONGO Law, divided by quarters"
+ggplot(ongo, aes(x = registration_date)) +
+  geom_histogram(binwidth = 365.25/4, boundary = ymd("2017-01-01"), 
+                 fill = clrs[6], color = "white") +
+  scale_x_date(date_breaks = "years", date_labels = "%Y") +
+  labs(x = NULL, y = "Count of new INGO registrations") +
+  theme_ongo()
+```
+
+Next, @fig-issue-props shows the distribution of issue areas that registered INGOs focus on.
+The two most common issues are economic, trade, and industry associations, representing 50% of all INGOs.
+Many of these organizations are bilateral chambers of commerce or other multilateral trade organizations such as the Japan-China Economic Association, the Silk Road Chamber of International Commerce, and the Canada China Business Council, and most are not more stereotypical international humanitarian organizations.
+Charitable, humanitarian, education, and health INGOs are far less common than their trade and industry counterparts.
+For instance, charity and humanitarian organizations like World Vision, Save the Children, and the Salvation Army comprise only 12% (73) of all INGOs.
+
+```{r fig-issue-props, fig.width=6, fig.height=3}
+#| include: true
+#| echo: false
+#| fig-cap: "Count of international NGO registrations, divided by issue area"
+issue_count <- ongo |> 
+  drop_na(work_field_code1) |> 
+  group_by(work_field_code1) |>
+  summarize(n = n()) |> 
+  mutate(work_field_code1 = fct_reorder(work_field_code1, n))
+
+ggplot(issue_count, aes(y = work_field_code1, x = n)) +
+  geom_col(fill = clrs[5]) +
+  scale_x_continuous(sec.axis = sec_axis(trans = ~ . / sum(issue_count$n),
+                                         labels = label_percent())) +
+  labs(x = "Count of INGOs", y = NULL) +
+  theme_ongo() +
+  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
+```
+
+Finally, there are clear geographic trends in INGO registration.
+As seen in @fig-home-office-map, the majority of INGOs are headquartered in Beijing (166), Shanghai (137), and Guangdong Province (46).
+INGOs must select a home office for their Chinese operations, but they are not necessarily limited to work within their home provinces.
+As described earlier, each INGO is authorized to work in a list of approved provinces, and the count provinces follows a unique three-level distribution, seen previously in @fig-province-count-collapsed, with 30% of INGOs authorized to work in just one province, 40% authorized to work nationally, and 30% authorized to work in a multiple provinces, but not in the whole country.
+
+```{r fig-home-office-map}
+#| include: true
+#| echo: false
+#| fig-cap: "Count of international NGO registrations, divided by issue area"
+# Use aes(geometry) and stat = "sf_coordinates" to make geom_label_repel() work
+# with geom_sf(): https://github.com/slowkow/ggrepel/issues/111#issuecomment-416853013
+ggplot() +
+  geom_sf(data = ongo_mapdata, aes(fill = ro_count), 
+          linewidth = 0.3, color = "white") +
+  scale_fill_distiller(palette = "Reds", direction = 1, guide = "none") +
+  geom_label_repel(data = filter(ongo_mapdata, ro_count > 0), 
+                   aes(label = ro_count, geometry = geometry),
+                   stat = "sf_coordinates", seed = 1234, label.size = 0.1, size = 3,
+                   segment.color = "black", segment.size = 0.5, min.segment.length = 0) +
+  coord_sf(crs = st_crs("EPSG:4480")) +  # China Geodetic Coordinate System 2000
+  theme_void()
+```
 
 ## Posterior predictions
+
+Next we explore our data in more depth by generating and analyzing posterior predictions from our ordered Beta regression model, varying specific variables of interest while holding all others constant.
 

### 2023-04-10 manuscript/manuscript.qmd
Woohoo major final edits for MPSA panel

@@
 title: "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
-date: "2023-04-07"
+date: "2023-04-09"
 author:
@@
 abstract: |
-  China’s 2017 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international NGOs (INGOs).
+  China’s 2017 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international nongovernmental organizations (INGOs).
 However, the effects of this global crackdown on INGOs have been difficult to measure since there is often divergence between the formal de jure regulations and the de facto implementation of these laws.
 Additionally, the severity and consistency of the enforcement of these laws often depends on the type of services provided by these organizations.
-In this paper, we measure the effect of China’s ONGO law on INGO operations in the five years since the passage of the law.
-We test whether and how INGO operational space under the ONGO law is influenced by organizations’ issue areas.
-We argue that the less contensious the issue areas INGOs work in the more likely they are granted greater operational space, measured by the number of provinces they are allowed to work in by the registration documentation.
-China provides an excellent setting for testing the "closing space" and "changing space" theoretical understanding because the 2017 ONGO law hypothetically regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities.
-We test our argument by analyzing administrative data from 633 registered representative offices of INGOs registered in China between 2017–2021 and test our hypothesis with multilevel Bayesian models.
+In this paper, we explore the effect of China’s ONGO law on INGO operations in the five years since the passage of the law.
+We test whether and how INGO operational space under the ONGO law is influenced by organizations' issue areas.
+We argue that the less contensious the issue areas INGOs work in the more likely they are granted greater operational space, measured by the number of provinces they are legally authorized to work in.
+China provides an excellent setting for examining the phenomenon of closing space civic space, since the 2017 ONGO law hypothetically regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities.
+We test our argument by analyzing administrative data from 633 registered representative offices of INGOs registered in China between 2017–2021 and test our hypothesis with a multilevel Bayesian model.
 Our results speak to the broader literature on closing civic space and provide an empirical illustration of the practical effect of NGO restrictions on global civil society.
@@
 
-# Introduction
+In the past decade, nearly 100 countries have proposed or enacted legal measures designed to restrict civil society [@ICNL:2021], and only 21% of countries have open and unrestricted civic space [@ChaudhryHeiss:2022a; @Civicus:2023].
+This global trend of closing or shrinking civic space [@Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016] has affected countries of all regime types, including both autocracies and democracies such as Morocco and Palestine [@AtiaHerrold:2018], India [@press-trust-india:2019], Vietnam [@Sidel:2023], Canada [@CIVICUS:2013], and the United States [@Cramer:2020].
+On April 28, 2016, China passed its own set of legal restrictions on civil society with its Law of the People’s Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China, or "ONGO Law," which formally took effect on January 1, 2017.
+As an authoritarian state with a growing nonprofit sector, the Chinese model of implementing restrictive laws for international NGOs (INGOs) has important implications for understanding the dynamics of how civil society laws can be used as policy tools to harness INGOs.
 
-In recent decades, there has been a global tend of “closing space” for civil society across jurisdictions such as Russia, India and Vietnam.[@DupuyPrakash:2020; @ChaudhryHeiss:2020; @Heiss:2017; @Sidel:2023; AtiaHerrold:2018] (*to update citation*).
-An ubiquitous manifestation of such trend is rolling out restrictive laws that regulate international NGOs (INGOs).[@DupuyPrakash:2020; @ChaudhryHeiss:2022a].
-China’s promulgation of the Law of the People’s Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China (the “ONGO Law”) on April 28, 2016 was considered part of a recent global wave of legal restrictions on INGOs.
-As an authoritarian jurisdiction with a growing nonprofit sector, the Chinese model of implementing restrictive laws for INGOs has great implications for scholarly understanding of the dynamics of how such laws are used as policy tools to harness INGOs in practice.
-The purpose of this study is to empirically examine how the ONGO Law has impacted INGO's presence as well as the operational space after the law took effect.
-By inquiring the *de facto* implementation of the law in addition to formal *de jure* regulations, we intent to inquire into a more comprehensive and data-based picture of the operational space for INGOs.
-It will also test out the evolving theory of the "closing space" or "changing space" for INGOs hold true in a representative empirical setting of the mainland China.
+The purpose of this study is to empirically examine how the ONGO Law has influenced the population of INGOs that have successfully registered in China since 2017, and in particular how the ONGO Law has shaped the operational space allowed for INGO operations in the country.
+By examining the *de facto* implementation of the law in addition to its formal *de jure* regulations, we provide a more comprehensive and data-based picture of the operational space for INGOs.
+By relying on representative empirical data from mainland China, our study also contributes to a growing body of research on the effects of closing civic space on INGO behavior and strategies.
 
-INGOs came to China after the Reform and Opening-up policy was adopted by the authority and have been playing pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China’s domestic nonprofit sector [@Yin:2009].
-Before the promulgation of the ONGO Law, the regulation of INGOs in China was obscure [Shieh:2018; Spires:2022].
-The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations by the State Council that specifies the registration of representative offices (“ROs”) of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic NGOs.
+International NGOs began to play an important role in China in the early 1990s as part of the country's Reform and Opening-Up policy, and organizations like Save the Children and the Ford Foundation established local offices and branches.
+Since then, INGOs and global civil society have played pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China’s domestic nonprofit sector [@Yin:2009].
+Prior to the implementation of the 2017 ONGO Law, regulation of INGOs in China was obscure [@Shieh:2018; @Spires:2022].
+The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations by the State Council that specifies the registration of representative offices ("ROs") of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic NGOs.
 However, the actual application of the regulation was very limited.
-Up until the ONGO Law took effect on January 1, 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs according to the Regulation on the Management of Foundations, while some Chinese officials estimated in 2016 that there were roughly over 7000 ONGOs operating in China [@YeHuang:2018].
+Up until the ONGO Law took effect in 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs, while some Chinese officials estimated in 2016 that there were roughly over 7,000 INGOs operating in China [@YeHuang:2018].
 
-Many INGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [Sidel:2016], though there were no clear requirements for them to have a formal legal presence in China[@Han:2011].
-They choose to have a formal legal identity for the convenience such as signing labor contracts directly with employees.
-However, the legal form of foreign-funded company is not quite compatible with the nature of ONGOs.
-Under the Chinese legal system, enterprises should be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms for them — foundations, associations and social service organizations [@Ye:2021].
-Thus, ONGOs obtaining legal identity in this way have to navigate through a legal framework designed for the for-profit institutional logic, e.g, focusing on project investors' right to investment return.
+Many INGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [@Sidel:2016], though there were no clear requirements for them to have a formal legal presence in China [@Han:2011].
+However, the legal form of foreign-funded company is not quite compatible with the nonprofit nature of INGOs.
+Under the Chinese legal system, enterprises are intended to be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms, such as foundations, associations, and social service organizations [@Ye:2021].
+Thus, INGOs obtaining legal identity in this way have to navigate through a legal framework designed for a for-profit institutional logic, e.g, focusing on project investors' right to investment returns.
 
-The legal framework governing ONGOs was overhauled by the Chinese ONGO Law.
-The new law applies to all Overseas (including Hong Kong, Macau and Taiwan) non-governmental organizations that conduct not-for-profit activities in the fields of Economic Development, Education, Science, Technology, Culture, Public Health, Sports, Environment Protection, Poverty Alleviation, and Disaster Relief etc.
-(Article 3).
-In other words, after the Overseas NGOs became effective, any nonprofit activities conducted by those ONGOs that cannot successfully obtaining proper legal authorization according to the law will be deemed illegal.
-Specifically, the ONGO law stipulates two ways to lawfully conduct nonprofit activities in China for ONGOs: registering ROs or filing information for documentation of temporary activities with the Ministry of Public Security (“MPS”) and Provincial-level Public Security bureaus, which are the registering and regulatory authority for ONGOs designated by the law.
-Registering an RO would be lawful identity gaining channel for INGOs seeking for on-going presence in China while temporary activities are suitable for INGOs that need to conduct one-off programs that last no longer than one year.
+The legal framework governing INGOs was overhauled by the 2017 Chinese ONGO Law.
+The new law applies to all overseas (including Hong Kong, Macau, and Taiwan) non-governmental organizations that conduct not-for-profit activities in the fields of economic development, education, science, technology, culture, public health, sports, environment protection, poverty alleviation, and disaster relief (Article 3).
+The ONGO Law stipulates two ways for INGOs to lawfully conduct nonprofit activities in China: (1) submitting an application for formal permanent registration, or (2) filing documentation of temporary activities with the Ministry of Public Security and provincial-level Public Security Bureaus, which are the registering and regulatory authority for INGOs.
+Formal registration an RO with a legal identity and allows them to th maintain an ongoing present in the country, while temporary activities are suitable for INGOs that need to conduct one-off programs that last no longer than one year.
+The law's registration requirements were strictly enforced—after the Overseas NGO Law came into effect, any INGOs that could not successfully obtain proper legal authorization would be deemed illegal.
 
-This paper studies the the empirical data of the registration of ROs in the years following the enactment of the ONGO Law to uncover the association between INGO issue areas and the composition of successful RO registration and the operational space granted.
-Registering RO under the ONGO Law requiring the consent of a Chinese professional supervisory unit (the "PSU"), which are governmental or quasi-governmental overseeing the INGO's issue area to co-supervise the INGOs with Public Security bureaus.
-And it turns out that obtaining the consent of a PSU to apply for registration became a key challenge for ONGOs, because potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018].
-Therefore, the composition of the successfully registered RO inform us whether ROs working on different issue areas have varied level of difficulty in obtaining legal status.
-Moreover, We measure the later with a proxy of the number of provinces that the ROs are authorized to operate.
-Specifically, the registration document of an RO would specify the field of work and mission for the RO and list the range of provinces that the RO is authorized to conduct nonprofit activities in (Article 18).
-Some ROs are authorized to operate across mainland China, which is 32 provincial administrative regions in total, but there are also many that are authorized to operate in one to multiple provinces but not all.
-We use the number of provinces that ROs are authorized to work in as a proxy to measure the operational space for INGOs in China based on the empirical understanding that INGOs need to or hope to have the approval to be able to carry out their programs in a geographical scope as larger as possible.
-[@Li:2020]
+This paper explores the characteristics of all registered INGOs in China in the five years after the ONGO Law became effective and examings the association between INGO issue areas and the operational space granted to them in the country.
+Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)—a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus.
+Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018].
+INGOs vary in their ability to attract partner PSUs, and organizations that are unable to find corresponding PSUs are more limited in their geographic reach within the country.
+INGOs are authorized to operate within China on a province-by-province basis.
+Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.
+We use the number of provinces that INGOs are authorized to work in as a proxy to measure the operational space for INGOs in China based on the assumption that INGOs need to or hope to have the approval to be able to carry out their programs in a geographical scope as large as possible [@Li:2020].
 
-# Literature and Theoretical Background
+In this paper, we first explore existing theories of closing civic space, authoritarian regulation of civil society, and differential regulation of international vs.
+domestic NGOs.
+We then propose a set of empirical expectations for INGOs registering in China following the 2017 ONGO Law.
+We describe our data, which includes registration and organization-level details for all 633 INGOs registered between January 1, 2017 and December 31, 2021, and our descriptive and empirical approach to analyzing the data.
+We then present the findings from our data, exploring each of our empirical expectations, and conclude with a discussion of how these results connect to larger themes of the global closure of civic space.
 
-## Literature on Closing Space for INGOs
+# Theoretical background and expectations
 
-Contentiousness, regime stability, other reasons (to add studies on this construct globally)
+::: {.callout-warning}
+Apologies! This section is still *incredibly* drafty!
+:::
 
-## Literature on differenciated attitudes towards INGOs (as reveal in implementation)
+China's 2017 ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down on international NGOs [@ChaudhryHeiss:2022; @Carothers:2016].
+Studies on the law has been focused on discussing the historical and political impetus of passing the law [@Shieh:2018] or analyzing the regulatory regimes it that has established and potential implications for INGOs operating in China [@Feng:2017; @TeetsHsu:2016).
+However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs’ operations and projects have been affected by the law after successfully gaining legal registration and documentation.
+A few studies [@Jia:2017; @YeHuang:2018)] have reflected on the implementation of the ONGO Law after its first year, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations.
+However, a more up-to-date and comprehensive understanding of the effects of the ONGO law is still lacking.
+
+This paper aims to fill these gaps by empirically examining how the "closing space" hypothesis applies to China in the years after the ONGO Law took effect.
+China provides an excellent setting for testing these theories because China's promulgation of restrictive INGO law as an authoritarian jurisdiction fits the observed global trends in recent years, thus can serve as an representative case to deepen scholarly understanding around these themes.
+Also, the level of ambiguity of the legal framework gives ample room for arbitrary discretion and conflicting attitudes by authorities, enabling us to analyze rules in form (*de jure*) as well as rules in use (*de facto*).
+
+## The "closing space" phenomenon
+
+Contentiousness, regime stability, other reasons [see @Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016].
+
+Main idea: organizations that work on more contentious issues like human rights advocacy face stricter regulations [@Bush:2015; @ChaudhryHeiss:2021]
+
+## De jure vs. de facto implementation of civil society regulations
+
+@ChaudhryHeiss:2022 and the divergence in de jure and de facto regulations—the implementation doesn't have to match the written law, and often the written law can serve as a "weapon hanging on the wall that never fires" that serves as a warning to potentially uncooperative NGOs [@Kozenko:2015].
+See also [@ToeplerZimmerFrohlich:2020; @Plantan:2022]
+
+::: {.content-hidden}
 
@@
 
-*de jure* vs. *de facto* difference "represents a bureaucratic form of repression" [@ChaudhryHeiss:2022]
+:::
 
-The promulgation of China’s ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down International NGOs [@ChaudhryHeiss:2022; @Carothers:2016].
-Studies on the law has been focused on discussing the historical and political impetus of passing the law (Shieh, 2018) or analyzing the regulatory regimes it that has established and potential implications for INGOs operating in China [@Feng:2017;@TeetsHsu:2016).
-However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs’ operations and projects have been affected by the law after successfully gaining legal registration and documentation.
-A couple of studies [@Jia:2017; @YeHuang:2018)] conducted reflections on the first year’s implementation of China’s ONGO Law, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations.
-However, a more up-to-date and comprehensive understanding of the effects of the ONGO law is still lacking.
+## Empirical expectations
 
-This paper aims to fill these gaps by empirically examining how the "closing space" hypothesis applies to China in the years after the ONGO Law took effect.
-China provides an excellent setting for testing these theories because China's promulgation of restrictive INGO law as an authoritarian jurisdiction fits the observed global trends in recent years, thus can serve as an representative case to deepen scholarly understanding around these themes.
-Also, the level of ambiguity of the legal framework gives ample room for arbitrary discretion and conflicting attitudes by authorities, enabling us to analyze rules in form (*de jure*) as well as rules in use (*de facto*).
+Based on extant literature and theoretical understanding, we argue that the operation space INGOs are granted is associated with the level of contentious their missions, i.e., the issue areas they work in.
+Since the level of contentiousness is also manifested by the level of difficulty they face while seeking lawful registration.
 
-Based on extant literature and theoretical understanding, we hypothesize that the operation space INGOs are granted is associated with the level of contentious their missions, i.e., the issue areas they work in.
-Since the level of contentious is also manifested by the level of difficulty they face while seeking lawful registration.
-We also hypothesize that large operational space of INGOs is negatively associated the time elapsed since the law took effect when they successfully got registered.
+- **Expectation 1** (issue area): Because they are seen as less of a threat to regime stability, INGOs working on less contentious issues should be registered in more provinces
 
-The follow section is structured as follow.
-In the data and methods section, we first report the data cleaning and coding process and measurements used in our empirical analysis.
-Then we explain the rationale for choosing ordered beta regression to fit our models.
-In the Results section, we report and interpret both descriptive analysis and regression analysis results.
-We conclude the paper by discussing the implications of our findings with respective to more general scholarly understanding of the closing space of international civil society.
+Relationships with PSUs are a critical part of the INGO registration process.
+No PSU is obligated to take on a supervisory role for an INGO, and interested organizations have to cultivate relationships with local officials.
+Accordingly, many of the INGOs we observe in our data either demonstrate close connections with local governmental authorities or frame their activities and services with a narrower geographic scope.
+
+Using the number of provinces an INGO is authorized to work in as a proxy for organizational flexibility and reach might not reflect reality.
+Some INGOs explicitly limit their operations to specific provinces, either because their programming is more tailored to local conditions, or because they do not feel a need to go through the longer process of obtaining national-level registration.
+Accordingly, we temper our issue area expectation with a measure of explicitly local purpose.
+Organizations that have no intention of registering nationally should be registered in fewer provinces:
+
+- **Expectation 2** (local connections): Because they are explicitly focused on local issues, INGos with more local connections should be registered in fewer provinces
+
+Finally, we also expect that the operational space for INGOs is negatively associated with the time elapsed since the law took effect:
+
+- **Expectation 3** (registration timing): Because formal registration can take a long time and can involve many bureaucratic hurdles, INGOs that registered soon after the law took effect should be be (1) less of a threat and (2) a higher priority for processing, and so should be registered in more provinces
 
@@
 
-The data used in this paper was collected from INGOs' public registration documents disclosed by MPS’s Overseas NGO Office on the online service platform for INGOs.
-We also use ChinaFile's China ONGO data for complementary purpose, we merge in the English organization name in ChinaFile for the sake of transparency of our analysis to broader communities.
-The data we collected spans from January 1, 2017, when the law took effect, to December 31, 2021, with data for 633 ROs in total.
-The filing document of ROs disclose the name, the registration date, the registration authority (which public security bureau regulates it), the PSU, the address and issue area or purposes of the RO and the specific provinces they can work in.
+The data used in this paper was collected from INGOs' public registration documents disclosed by the Ministry of Public Security's Overseas NGO Office online service platform.
+The data spans from January 1, 2017, when the law took effect, to December 31, 2021, with data for 633 registered organizations.
+The filing documents for ROs disclose the name, the address, the registration date, the registration authority (which public security bureau regulates it), the PSU, the issue area or purposes of the RO, and the specific provinces they can work in.
+We merge our INGO data with additional data from ChinaFile, including English organization names, for the sake of transparency and accessibility.
+
 We code the variables we use in the empirical analysis from the registration information.
-Most of the coding and data cleaning work is objective data wrangling process, such as parsing out the province each RO is in from the address, or calculating the total number provinces approved in the registration document.
-Meanwhile, the coding of issue areas are conducted by the authors based on the areas set out Article 3 (specified above) and clustering of the issue areas of the actually registered ROs.
-(to cross-validate among authors).
+Most of our data cleaning work is an objective data wrangling process, such as parsing out the province each RO is in from the address, or calculating the total number provinces approved in the registration document.
+Meanwhile, the qualitative coding of issue areas is conducted by the authors
 
@@
 
-### Dependent Variables
+### Dependent variable
 
-Our dependent variable is "geo_scope_num", the count of the total number of provinces each RO is authorized to operate in.
+Our dependent variable is the count of the total number of provinces each INGO is authorized to operate in.
 We derived this variable from the specific list of authorized provinces as recorded in the RO's registration documentation.
 As discussed above, we use this measurement as a proxy for operational space for INGOs, because any geographical constraints on the RO impacts on the flexibility of the INGO operations.
-For example, in circumstances where emergency like the COVID 19 pandemic hits, it would be extremely hard for INGOs to plan beforehand which areas would need their service.
-Thus, we assume INGOs that are not set up with any locally-bound purposes would need to or hope to (if there is not yet such needs) be able to operate in as broader geographical scope as possible.
+For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas would need their service.
+Thus, we assume INGOs that are not set up with any locally-bound purposes would need to or hope to (if there is not yet such need) be able to operate in as broad a geographical scope as possible.
 
-### Independent Variables
+### Independent variables
 
-Our first independent variable is "work_field_code1", the issue area we code from mission statement specified in the RO's registration documentation.
-Given there is certain level of subjectivity in the coding process, the coding of issue areas are cross-checked between the researchers (to do).
-The coding rules for overlapping issue areas can be found in the Appendix (to add).
-We decided to have 9 issue areas groups based on list of lawful fields of work specified by the Article 3 of the ONGO Law and how actual issue areas cluster for registered ROs.
-
-Below is the list of issue areas INGOs' registered ROs are coded into.
+Our key independent variables correspond to each of our three empirical expectations.
+First we code each INGO's issue area based on its mission statement reported in its registration documentation.
+Given there is certain level of subjectivity in the coding process, the coding of issue areas are cross-checked between the researchers—Author 1 assigned each organization into one of the issue areas defined in Article 3 of the ONGO Law, and Author 2 cross-checked the coding for ambiguous cases.
+We include our coding rules for overlapping issue areas in the appendix (in the future).
+We categorize each organization into one of the following nine issue areas:
 
@@
 - **Arts and Culture** including sports and international culture exchange
-- **General**, usually grant-making organizations, Or working on general international communication, including among governments, or working on multiple fields not overlapping
+- **General**, usually grant-making organizations, or working on general international communication, including among governments, or working on multiple fields not overlapping
 
-Our second variable is "time_elapsed".
-This variable is derived the time difference between ROs' registration date and January 1, 2017 when the law took effect.
-The longer the time elapsed since registration should be achieved by INGOs, it indicates that it took longer time for them to seek the content of both the PSU and Public Security Bureaus to be their supervisions or regulators and grant them legal identity.
+Our second variable is a dichotomous indicator of whether the INGO explicitly states that it intends to operate locally.
+There are cases where the aim or mission of the INGO attached to a locality, either having a county or city name in their RO name or purposes, or the INGO are actually set up by people in China and they registered the RO to communicate between the "hometown" and the INGO set up abroad.
+We thus include this variable in our analysis to explore how having local connections is associated with the operational space of ROs.
 
-### Control Variables
+Our final variable measures how much time elapsed between the January 1, 2017 (when the law took effect) and the organization's official registration date.
+This indicates how long it took INGOs to seek the consent and supervisory authority of both a PSU and the Public Security Bureau and to complete all other necessary bureaucratic requirements.
 
-Our first control variable is "local_connet".
-It is a dichotomous variable indicating whether operating locally is built into the RO's mission.
-There are cases where the aim or mission of the INGO attached to a locality, either having a county or city name in their RO name or purposes, or the INGO are actually set up by people in China and they registered the RO to communicate between the "hometown" and the INGO set up abroad.
-So we include this variable in our model to how having local connection is associated with the operational space of ROs as well as how the contentious level associates with operation space when we account for this factor.
-
-We also cluster our 633 RO cases by the province where they are registered in our hierarchical Bayesian modeling.
-Thus, we account for any variance caused by the socioeconomic and institutional differences in various provinces of China.
-And the level province is the apporoiate level to cluster because all the ROs are registered at the provincial public security bureaus.
-
-## Regression Model
+## Multilevel Bayesian model
 
@@
 
-Before examining the posterior results of the statistical, we first describe some of the general trends in INGO registration during the first 5 years of the ONGO law.
+Before examining the posterior results of our statistical model, we first describe some of the general trends in INGO registration during the first 5 years of the ONGO law.
 We use our data to explore (1) when INGOs registered, (2) what kinds of issues registered INGOs work on, and (3) how large of a geographic reach INGOs have.
@@
 After the initial wave of registrations in 2017, the likelihood of nationwide reach steadily increases and replaces both the probability of a single province or a partial range of provinces.
-By the end of 2022—5 years after the ONGO Law took effect—the probability of national -level registration increases to 55–61% while the probability of working in a range of provinces increases to predicted to work in two or more provinces increase to 27–32%.
+By the end of 2021—5 years after the ONGO Law took effect—the probability of national -level registration increases to 55–61% while the probability of working in a range of provinces increases to predicted to work in two or more provinces increase to 27–32%.
 These late INGOs are the least likely to be registered in only one province and are predicted to do so only 17–22% of the time.
 @fig-timing-preds-2 demonstrates the same results with the posterior distribution of the expected count of provinces over five years since 2017.
-INGOs that register early are predicted to work in 17–22 provinces, while those that wait until 2022 are predicted to work in 21–28.
+INGOs that register early are predicted to work in 17–22 provinces, while those that wait until 2021 are predicted to work in 21–28.
 
@@
 
+::: {.callout-warning}
+**Still TODO!**
+:::
+
 # References

### 2023-04-10 manuscript/manuscript.qmd
Use correct subfigure syntax so that LaTeX is happy

@@
                       fig.width = 6, fig.height = (6 * 0.618),
-                      out.width = "80%", collapse = TRUE)
+                      out.width = "100%", collapse = TRUE)
 
@@
 To explore this, we can take advantage of the simultaneous continuous and discrete features of ordered Beta regression and see how often an INGO in each issue area is predicted to work in a single province, across all provinces, or some number in between.
-@fig-issue-preds-ordbeta presents a summary of predicted posterior outcomes for 1,000 hypothetical INGOs, varying each possible issue area and holding all other variables at their mean or modal values.
+@fig-issue-preds-1 presents a summary of predicted posterior outcomes for 1,000 hypothetical INGOs, varying each possible issue area and holding all other variables at their mean or modal values.
 Several notable trends emerge from the model results.
@@
 
-::: {#fig-issue-preds layout-ncol=1}
-
-```{r fig-issue-preds-ordbeta, fig.width=6, fig.height=4.5, cache=TRUE}
+```{r fig-issue-preds, fig.width=6, fig.height=4.5, cache=TRUE}
 #| include: true
 #| echo: false
-#| fig-subcap: "Proportions of posterior predictions of INGOs working in 1 province, all 32 provinces, or somewhere in between. Distinct x-axis categories sum to 100% across the panels."
+#| layout-ncol: 1
+#| fig-cap: "Posterior predictions from ordered Beta regression model, conditional on organization issue area."
+#| fig-subcap: 
+#|   - "Proportions of posterior predictions of INGOs working in 1 province, all 32 provinces, or somewhere in between. Distinct x-axis categories sum to 100% across the panels."
+#|   - "Distribution of the expectation of posterior predictions.
+These distributions take into account single-province and nationwide predictions and represent the overall conditional average geographic range for INGOs."
 preds_issue_plot <- preds_issue |> 
@@
   theme_ongo()
-```
 
-```{r fig-issue-preds-2}
-#| include: true
-#| echo: false
-#| fig-subcap: "Distribution of the expectation of posterior predictions.
-These distributions take into account single-province and nationwide predictions and represent the overall conditional average geographic range for INGOs."
 epreds_issue |> 
@@
 ```
-
-Posterior predictions from ordered Beta regression model, conditional on organization issue area.
-
-:::
 
@@
 #| echo: false
+#| layout-ncol: 1
 #| fig-cap: "Posterior predictions from ordered Beta regression model, conditional on having local connections."
@@
 
-::: {#fig-timing-preds layout-ncol=1}
-
-```{r fig-timing-preds-1, fig.width=6, fig.height=3}
+```{r fig-timing-preds, fig.width=6, fig.height=3}
 #| include: true
 #| echo: false
-#| fig-subcap: "Proportions of posterior predictions of INGOs working in 1 province, all 32 provinces, or somewhere in between. Distinct x-axis values sum to 100% across the panels."
+#| layout-ncol: 1
+#| fig-cap: "Posterior predictions from ordered Beta regression model, conditional on time since registration."
+#| fig-subcap: 
+#|   - "Proportions of posterior predictions of INGOs working in 1 province, all 32 provinces, or somewhere in between. Distinct x-axis values sum to 100% across the panels."
+#|   - "Distribution of the expectation of posterior predictions.
+These distributions take into account single-province and nationwide predictions and represent the overall conditional average geographic range for INGOs."
 preds_timing_plot <- preds_timing |> 
@@
   theme_ongo()
-```
 
-```{r fig-timing-preds-2, fig.width=6, fig.height=3}
-#| include: true
-#| echo: false
-#| fig-subcap: "Distribution of the expectation of posterior predictions.
-These distributions take into account single-province and nationwide predictions and represent the overall conditional average geographic range for INGOs."
 epreds_timing |> 
@@
 ```
-
-Posterior predictions from ordered Beta regression model, conditional on time since registration.
-
-:::
 

### 2023-04-10 index.qmd
Add abstract to notebook website

@@
 
-Abstract goes here
+China’s 2017 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international nongovernmental organizations (INGOs).
+However, the effects of this global crackdown on INGOs have been difficult to measure since there is often divergence between the formal de jure regulations and the de facto implementation of these laws.
+Additionally, the severity and consistency of the enforcement of these laws often depends on the type of services provided by these organizations.
+In this paper, we explore the effect of China’s ONGO law on INGO operations in the five years since the passage of the law.
+We test whether and how INGO operational space under the ONGO law is influenced by organizations' issue areas.
+We argue that the less contensious the issue areas INGOs work in the more likely they are granted greater operational space, measured by the number of provinces they are legally authorized to work in.
+China provides an excellent setting for examining the phenomenon of closing space civic space, since the 2017 ONGO law hypothetically regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities.
+We test our argument by analyzing administrative data from 633 registered representative offices of INGOs registered in China between 2017–2021 and test our hypothesis with a multilevel Bayesian model.
+Our results speak to the broader literature on closing civic space and provide an empirical illustration of the practical effect of NGO restrictions on global civil society.
 

### 2023-04-10 index.qmd
Expand explanation for province random effects

@@
 We test whether and how INGO operational space under the ONGO law is influenced by organizations' issue areas.
-We argue that the less contensious the issue areas INGOs work in the more likely they are granted greater operational space, measured by the number of provinces they are legally authorized to work in.
+We argue that the less contentious the issue areas INGOs work in the more likely they are granted greater operational space, measured by the number of provinces they are legally authorized to work in.
 China provides an excellent setting for examining the phenomenon of closing space civic space, since the 2017 ONGO law hypothetically regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities.

### 2023-04-10 manuscript/manuscript.qmd
Expand explanation for province random effects

@@
 Since we are primarily interested in how an INGO's issue area, its local connections, and the timing of its registration after January 2017, we include these as explanatory variables.
-We also include province-specific random offsets for each intercept to account for between-region differences in how INGOs are regulated.
+We also include province-specific random offsets for each intercept to account for between-region differences in how INGOs are regulated, since every RO is overseen by provincial-level Public Security Bureaus.
 We use weakly informative priors for all model parameters.

### 2023-04-10 manuscript/manuscript.qmd
Use quarto profiles to create multiple versions of PDFs

@@
 title: "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
+short-title: "China's ONGO Law and International Civil Society"
 date: "2023-04-09"
@@
   - Chinese ONGO law
+code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/compassionate-clam>"
 bibliography: references.bib
@@
 China's 2017 ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down on international NGOs [@ChaudhryHeiss:2022; @Carothers:2016].
-Studies on the law has been focused on discussing the historical and political impetus of passing the law [@Shieh:2018] or analyzing the regulatory regimes it that has established and potential implications for INGOs operating in China [@Feng:2017; @TeetsHsu:2016).
+Studies on the law has been focused on discussing the historical and political impetus of passing the law [@Shieh:2018] or analyzing the regulatory regimes it that has established and potential implications for INGOs operating in China [@Feng:2017; @TeetsHsu:2016].
 However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs’ operations and projects have been affected by the law after successfully gaining legal registration and documentation.
-A few studies [@Jia:2017; @YeHuang:2018)] have reflected on the implementation of the ONGO Law after its first year, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations.
+A few studies [@Jia:2017; @YeHuang:2018] have reflected on the implementation of the ONGO Law after its first year, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations.
 However, a more up-to-date and comprehensive understanding of the effects of the ONGO law is still lacking.
@@
 
-```{r fig-issue-preds, fig.width=6, fig.height=4.5, cache=TRUE}
+```{r fig-issue-preds, fig.width=6, fig.height=4.5}
 #| include: true

### 2023-04-10 _targets.R

@@ -75,7 +75,8 @@ list(
   tar_target(epreds_timing_local, f_epreds_timing_local(m_full_ordbeta)),
   
   ## Analysis notebook ----
-  tar_quarto(manuscript_nice, path = "manuscript", quiet = FALSE),
+  tar_quarto(manuscript_nice, path = "manuscript", quiet = FALSE, profile = "nice"),
+  tar_quarto(manuscript_manuscripty, path = "manuscript", quiet = FALSE, profile = "ms"),
   tar_quarto(website, path = ".", quiet = FALSE),
   
   tar_target(deploy_script, here_rel("deploy.sh"), format = "file"),

### 2023-04-18 presentations/2023-04-16_mpsa/index.qmd
Add embedded slides

@@
 published-title: "Presented"
+image: first-slide.png
 page-layout: full
@@
 
-Slides will be embedded here.
+<div class="ratio ratio-16x9">
+<iframe class="slide-deck" src="https://docs.google.com/presentation/d/1kCvKXx68-dG8cdpS9k6rCyNVBNMzxOU5ZwH0BaEF4Nc/embed?start=false&loop=false&delayms=3000" allowfullscreen="true" mozallowfullscreen="true" webkitallowfullscreen="true"></iframe>
+</div>
 

### 2023-08-23 manuscript/manuscript.qmd
updated manuscript

@@
 However, the legal form of foreign-funded company is not quite compatible with the nonprofit nature of INGOs.
-Under the Chinese legal system, enterprises are intended to be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms, such as foundations, associations, and social service organizations [@Ye:2021].
-Thus, INGOs obtaining legal identity in this way have to navigate through a legal framework designed for a for-profit institutional logic, e.g, focusing on project investors' right to investment returns.
+Under the Chinese legal system, enterprises are intended to be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms, including foundations, associations, and social service organizations [@Ye:2021].
+Thus, INGOs obtaining legal identity in this way have to navigate through a legal framework designed for a for-profit institutional logic, e.g, focusing on protecting investors' right to investment returns.
 
@@
 The ONGO Law stipulates two ways for INGOs to lawfully conduct nonprofit activities in China: (1) submitting an application for formal permanent registration, or (2) filing documentation of temporary activities with the Ministry of Public Security and provincial-level Public Security Bureaus, which are the registering and regulatory authority for INGOs.
-Formal registration an RO with a legal identity and allows them to th maintain an ongoing present in the country, while temporary activities are suitable for INGOs that need to conduct one-off programs that last no longer than one year.
-The law's registration requirements were strictly enforced—after the Overseas NGO Law came into effect, any INGOs that could not successfully obtain proper legal authorization would be deemed illegal.
+Formal registration of an RO allows them to maintain an ongoing present in the country, while temporary activities are intended for INGOs that need to conduct one-off programs that last no longer than one year.
+Abiding by these two channels to obtain lawful presence is mandatory for INGOs after the Overseas NGO Law came into effect, any INGOs that could not successfully obtain proper legal authorization would be deemed illegal.
 
-This paper explores the characteristics of all registered INGOs in China in the five years after the ONGO Law became effective and examings the association between INGO issue areas and the operational space granted to them in the country.
+This paper explores the characteristics of all registered INGOs in China in the five years after the ONGO Law became effective and examines the association between INGO issue areas and the operational space granted to them in the country.
 Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)—a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus.
@@
 
-Based on extant literature and theoretical understanding, we argue that the operation space INGOs are granted is associated with the level of contentious their missions, i.e., the issue areas they work in.
+Based on extant literature and theoretical understanding, we argue that the operation space INGOs are granted is associated with the level of contentiousness their missions, i.e., the issue areas they work in.
 Since the level of contentiousness is also manifested by the level of difficulty they face while seeking lawful registration.
@@
 The data used in this paper was collected from INGOs' public registration documents disclosed by the Ministry of Public Security's Overseas NGO Office online service platform.
-The data spans from January 1, 2017, when the law took effect, to December 31, 2021, with data for 633 registered organizations.
+The platform is a website maintained by the registrar of INGOs and regularly publicize the administrative documentation of all the ROs and temporary activities registered or filled across China.
+The data used in this study spans from January 1, 2017, when the law took effect, to December 31, 2021, with information for all 633 registered organizations approved as of the cutoff point.
 The filing documents for ROs disclose the name, the address, the registration date, the registration authority (which public security bureau regulates it), the PSU, the issue area or purposes of the RO, and the specific provinces they can work in.
-We merge our INGO data with additional data from ChinaFile, including English organization names, for the sake of transparency and accessibility.
+We merge our INGO data with additional data of Chinese INGO data from ChinaFile, a project that translate and code the MPS platform data, to include their English organization names, for the sake of transparency and accessibility.
 
 We code the variables we use in the empirical analysis from the registration information.
-Most of our data cleaning work is an objective data wrangling process, such as parsing out the province each RO is in from the address, or calculating the total number provinces approved in the registration document.
-Meanwhile, the qualitative coding of issue areas is conducted by the authors
+Most of our data cleaning work is an objective data wrangling process, such as parsing out the province each RO registered in from the address, or calculating the total number provinces approved in the registration document.
+Meanwhile, the qualitative coding of issue areas is conducted by the authors, based on consistent coding rules agreed by the authors.
 
@@
 
-Our second variable is a dichotomous indicator of whether the INGO explicitly states that it intends to operate locally.
-There are cases where the aim or mission of the INGO attached to a locality, either having a county or city name in their RO name or purposes, or the INGO are actually set up by people in China and they registered the RO to communicate between the "hometown" and the INGO set up abroad.
+Our second independent variable is a dichotomous indicator of whether the INGO explicitly states that it intends to operate locally (below province level).
+There are cases where the aim of the INGO is attached to a locality, either having a county or city name in their RO name or purposes, or the INGO are actually set up by people in China and they registered the RO to communicate between the "hometown" and the INGO set up abroad.
 We thus include this variable in our analysis to explore how having local connections is associated with the operational space of ROs.
 
-Our final variable measures how much time elapsed between the January 1, 2017 (when the law took effect) and the organization's official registration date.
-This indicates how long it took INGOs to seek the consent and supervisory authority of both a PSU and the Public Security Bureau and to complete all other necessary bureaucratic requirements.
+Our final independent variable measures how much time elapsed between the January 1, 2017 (when the law took effect) and the organization's official registration date.
+There is great variance in the timing of registering an RO among INGOs, since there has been a *de facto* grace period for INGOs to seek legal presence after the law took effect.
+This is largely because both INGOs and the regulators needed some transitional time to explore the specific implementation of the law as large ambiguity was left when the law was passed.
+We use this temporal variable as a proxy for the motivation or eagerness of INGOs to register an RO, for some INGOs are inclined to avoid the cumbersome registration procedures at the early stage if there is no real consequences for continuing operations without registration, while others took the time to talk with multiple potential PSUs to find a more suitable superior or regulatory dynamic.
+(to find a citation for this, probably Spires, if there is one.)
 

### 2023-09-13 notebook/analysis-timing.qmd
Switch to native pipe

@@
 ```{r plot-epred-timing-lineribbon}
-epreds %>% 
+epreds |> 
   ggplot(aes(x = years_since_law, y = .epred)) +
@@
     .prediction == 1 ~ "32 provinces"
-  )) %>% 
-  group_by(outcome, years_since_law, draw) %>% 
+  )) |> 
+  group_by(outcome, years_since_law, draw) |>
   summarize(count = n()) |> 

### 2023-09-13 notebook/model-details.qmd
Switch to native pipe

@@
 
-posterior_categories <- full_posterior %>% 
-  ungroup() %>% 
+posterior_categories <- full_posterior |> 
+  ungroup() |> 
   mutate(outcome = case_when(
@@
     .prediction == 1 ~ "32"
-  )) %>% 
-  group_by(outcome, .draw) %>% 
-  summarize(count = n()) %>% 
+  )) |> 
+  group_by(outcome, .draw) |> 
+  summarize(count = n()) |> 
   ungroup()
@@
 
-plot_categories <- posterior_categories %>% 
+plot_categories <- posterior_categories |> 
   ggplot(aes(x = outcome, y = count)) +

### 2023-09-13 R/funs_data.R

@@ -113,7 +113,7 @@ clean_ongo_data <- function(manual, chinafile, province_name) {
            )) |> 
     mutate(province_cat = factor(province_cat, 
                                  levels = c("Single province", "Multiple provinces", "All provinces"),
-                                 ordered = TRUE)) %>% 
+                                 ordered = TRUE)) |> 
     mutate(time_since_law_passed = interval(ymd("2017-01-01"), registration_date),
            days_since_law = time_since_law_passed / days(1),
            months_since_law = time_since_law_passed / months(1),

### 2023-09-13 _targets.R
Use new updated data

@@ -42,7 +42,7 @@ tar_source()
 list(
   ## Raw data files ----
   tar_target(ongo_manual_file,
-             here_rel("data", "manual_data", "ongo-manual-clean.csv"),
+             here_rel("data", "manual_data", "ongo-manual-20230912.csv"),
              format = "file"),
   
   ## Graphics ----

### 2023-09-13 R/funs_models.R
Remove older models we're not using anymore

@@ -2,76 +2,6 @@ suppressPackageStartupMessages(library(tidybayes))
 library(marginaleffects)
 
 # Model definitions
-f_basic_zoib <- function(data) {
-  BAYES_SEED <- 102819  # From random.org
-  
-  zoib_priors <- c(prior(student_t(1, 0, 3), class = Intercept),
-                   prior(student_t(1, 0, 3), class = b),
-                   prior(student_t(1, 0, 3), class = b, dpar = zoi))
-  
-  model <- brm(
-    bf(
-      # mu: mean of the 0-1 values; logit scale
-      province_pct ~ work_field_code1,
-      # zoi: zero-or-one-inflated part; logit scale
-      zoi ~ work_field_code1,
-      # coi: one-inflated part, conditional on the 0s; logit scale
-      #   This is set to a fixed 1 because there are no zeros; this effectively
-      #   makes a one-inflated beta regression
-      coi = 1), 
-    data = data,
-    family = zero_one_inflated_beta(), 
-    prior = zoib_priors,
-    seed = BAYES_SEED)
-  
-  return(model)
-}
-
-f_basic_ologit <- function(data) {
-  BAYES_SEED <- 659022  # From random.org
-  
-  ologit_priors <- c(prior(student_t(1, 0, 3), class = Intercept),
-                     prior(student_t(1, 0, 3), class = b))
-  
-  model <- brm(
-    bf(
-      province_cat ~ work_field_code1
-    ), 
-    data = data,
-    family = cumulative(), 
-    prior = ologit_priors,
-    seed = BAYES_SEED)
-  
-  return(model)
-}
-
-
-f_full_zoib <- function(data) {
-  BAYES_SEED <- 102819  # From random.org
-  
-  zoib_priors <- c(prior(student_t(1, 0, 3), class = Intercept),
-                   prior(student_t(1, 0, 3), class = b),
-                   prior(student_t(1, 0, 3), class = b, dpar = zoi))
-  
-  model <- brm(
-    bf(
-      # mu: mean of the 0-1 values; logit scale
-      province_pct ~ work_field_code1 + local_connect + local_aim + psu_level + (1 | province_code),
-      # zoi: zero-or-one-inflated part; logit scale
-      zoi ~ work_field_code1 + local_connect + local_aim + psu_level + (1 | province_code),
-      # coi: one-inflated part, conditional on the 0s; logit scale
[…]

### 2023-09-13 _targets.R

@@ -57,10 +57,6 @@ list(
              clean_map_data(ongo)),
   
   ## Models ----
-  tar_target(m_basic_zoib, f_basic_zoib(ongo)),
-  tar_target(m_basic_ologit, f_basic_ologit(ongo)),
-  
-  tar_target(m_full_zoib, f_full_zoib(ongo)),
   tar_target(m_full_ordbeta, f_full_ordbeta(ongo)),
   tar_target(m_full_interaction_ordbeta, f_full_interaction_ordbeta(ongo)),
   

### 2023-09-13 notebook/model-details.qmd
Add MCMC run times and create pages for future diagnostics

@@
 library(scales)
+library(glue)
+library(gt)
+library(gtExtras)
 
@@
 tar_load(ongo)
-tar_load(m_full_ordbeta)
+tar_load(c(m_full_ordbeta, m_full_interaction_ordbeta))
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+invisible(list2env(tar_read(table_functions), .GlobalEnv))
 
@@
 TODO: Timing
+
+```{r calculate-model-times}
+models <- tribble(
+  ~model_name, ~model,
+  "Full model", m_full_ordbeta,
+  "Full model with `local_connect * years_since_law` interaction", m_full_interaction_ordbeta,
+) |> 
+  mutate(duration = map(model, ~{
+    .$fit |> 
+      rstan::get_elapsed_time() |> 
+      as_tibble() |> 
+      summarize(total = as.duration(max(warmup + sample)))
+  })) |> 
+  select(-model) |> 
+  unnest(duration)
+
+dur <- as.period(as.duration(sum(models$total)))
+
+total_run_time <- glue(
+  "{hours} hours, {minutes} minutes, and {seconds} seconds",
+  hours = hour(dur), minutes = minute(dur), seconds = round(second(dur), 0)
+)
+```
+
+We ran these models on a 2021 M1 MacBook Pro with 32 GB of RAM, with 4 MCMC chains spread across 8 cores, with two CPU threads per chain, using Stan through brms through cmdstanr.
+
+In total, it took `r total_run_time` to run everything.
+
+```{r mcmc-duration-table}
+models |> 
+  gt() |> 
+  tab_footnote(
+    footnote = "Duration of the longest-running MCMC chain",
+    locations = cells_column_labels(columns = total)
+  ) |> 
+  cols_label(
+    model_name = "Model",
+    total = "Total time"
+  ) |> 
+  cols_align(
+    align = "left",
+    columns = everything()
+  ) |>
+  fmt_markdown(columns = model_name) |> 
+  grand_summary_rows(
+    columns = c(total),
+    fns = list(`Overall total` = ~as.duration(sum(.)))
+  ) |> 
+  opt_footnote_marks(marks = "standard") |> 
+  opt_horizontal_padding(3) |> 
+  opts_theme()
+```

### 2023-09-13 R/fun_tables.R

@@ -1,0 +1,11 @@
+opts_int <- function(x, ...) {
+  x %>% 
+    opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE, ...)
+}
+
+opts_theme <- function(x) {
+  x %>% 
+    opt_table_font(font = "IBM Plex Sans") %>% 
+    tab_options(column_labels.font.weight = "bold",
+      row_group.font.weight = "bold")
+}

### 2023-09-13 _targets.R

@@ -45,8 +45,9 @@ list(
              here_rel("data", "manual_data", "ongo-manual-20230912.csv"),
              format = "file"),
   
-  ## Graphics ----
+  ## Graphics and tables ----
   tar_target(graphic_functions, lst(theme_ongo, set_annotation_fonts, clrs)),
+  tar_target(table_functions, lst(opts_int, opts_theme)),
 
   ## Process and clean data ----
   tar_target(chinafile_clean, load_clean_chinafile()),

### 2023-09-13 R/fun_tables.R
oops use native pipe

@@ -1,11 +1,11 @@
 opts_int <- function(x, ...) {
-  x %>% 
+  x |> 
     opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE, ...)
 }
 
 opts_theme <- function(x) {
-  x %>% 
-    opt_table_font(font = "IBM Plex Sans") %>% 
+  x |> 
+    opt_table_font(font = "IBM Plex Sans") |> 
     tab_options(column_labels.font.weight = "bold",
       row_group.font.weight = "bold")
 }

### 2023-09-13 notebook/model-details.qmd
Add model diagnostics

@@
 invisible(list2env(tar_read(table_functions), .GlobalEnv))
-
-prop_to_provinces <- function(x, lower = 1, upper = 32) {
-  (x * (upper - lower)) + lower
-}
 ```
-
-TODO: Formal definition and justification for ordered beta instead of ZOIB
-
-```{r build-posterior-preds}
-full_posterior <- predicted_draws(m_full_ordbeta, 
-                                  newdata = m_full_ordbeta$data, 
-                                  ndraws = 100)
-
-posterior_categories <- full_posterior |> 
-  ungroup() |> 
-  mutate(outcome = case_when(
-    .prediction == 0 ~ "1",
-    .prediction > 0 & .prediction < 1 ~ "1–32",
-    .prediction == 1 ~ "32"
-  )) |> 
-  group_by(outcome, .draw) |> 
-  summarize(count = n()) |> 
-  ungroup()
-
-actual_counts <- m_full_ordbeta$data |> 
-  mutate(outcome = case_when(
-    province_count == 0 ~ "1",
-    province_count > 0 & province_count < 1 ~ "1–32",
-    province_count == 1 ~ "32"
-  )) |> 
-  group_by(outcome) |> 
-  summarize(count = n())
-
-plot_categories <- posterior_categories |> 
-  ggplot(aes(x = outcome, y = count)) +
-  geom_col(data = actual_counts, fill = "grey70") +
-  stat_pointinterval() +
-  labs(x = NULL, y = "Observed and predicted counts",
-       title = "Posterior predictions of discrete and continuous outcomes") +
-  coord_cartesian(ylim = c(0, 300)) +
-  theme_ongo()
-
-actual_middle <- m_full_ordbeta$data |> 
-  filter(province_count > 0 & province_count < 1) |> 
-  mutate(province_count = prop_to_provinces(province_count))
-
-plot_continuous <- full_posterior |> 
-  mutate(.prediction = prop_to_provinces(.prediction)) |> 
-  filter(.prediction > 1 & .prediction < 32) |> 
-  ggplot(aes(x = .prediction, group = .draw)) +
-  geom_density(linewidth = 0.05, bounds = c(1, 32)) +
-  geom_density(data = actual_middle, aes(x = province_count),
-               inherit.aes = FALSE, bounds = c(1, 32)) +
-  labs(x = "Discrete and continuous predicted outcomes",
-       y = "Probability density") +
-  theme_ongo()
-```
-
-```{r combined-posterior-preds, fig.width=6, fig.height=5}
-arrow_part <- ggplot() +
-  annotate(geom = "segment", x = 0.35, xend = 0.65, y = 0.9, yend = 0.9) +
-  annotate(geom = "segment", x = 0.5, xend = 0.5, y = 0.9, yend = 0.1,
-           arrow = arrow(angle = 30, type = "closed", length = unit(0.1, "inches"))) +
-  scale_x_continuous(limits = c(0, 1)) +
-  theme_void()
-
-plot_categories / arrow_part / plot_continuous +
-  plot_layout(heights = c(0.45, 0.1, 0.45))
-```
-
-```{r}
-# ordbetareg's built-in way, just to check
-# pp_check_ordbeta(m_full_ordbeta, ndraws = 100)
-```
-
-TODO: MCMC diagnostics
-
-TODO: Timing
 

### 2023-09-13 notebook/model-diagnostics.qmd
Add model diagnostics

---
title: Model diagnostics
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.align = "center", fig.retina = 3,
  fig.width = 6, fig.height = (6 * 0.618),
  out.width = "80%", collapse = TRUE,
  dev = "ragg_png"
)

options(
  digits = 3, width = 120,
  dplyr.summarise.inform = FALSE,
  knitr.kable.NA = ""
)
```

```{r libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(tidybayes)
library(glue)
library(patchwork)
library(gt)
library(gtExtras)

tar_config_set(
  store = here::here("_targets"),
  script = here::here("_targets.R")
)

tar_load(m_full_ordbeta)

invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(table_functions), .GlobalEnv))

theme_set(theme_ongo())

prop_to_provinces <- function(x, lower = 1, upper = 32) {
  (x * (upper - lower)) + lower
}
```

```{r}
get_variables(m_full_ordbeta)
```

### Traceplots

These should look like hairy caterpillars.

They do.

```{r mcmc-trace}
params_to_show <- c(
  "b_Intercept", "b_work_field_code1Health",
  "phi", "cutzero"
)

m_full_ordbeta |> 
  tidybayes::gather_draws(!!!syms(params_to_show)) |> 
  ggplot(aes(x = .iteration, y = .value, color = factor(.chain))) +
  geom_line(linewidth = 0.1) +
  scale_color_viridis_d(option = "rocket", end = 0.85) +
  labs(color = "Chain") +
  facet_wrap(vars(.variable), scales = "free_y")
```

### Trace rank plots (trank plots)

These are histograms of the ranks of the parameter draws across the four chains. If the chains are exploring the same space efficiently, the histograms should be similar and overlapping and no one chain should have a specific rank for a long time [@McElreath:2020, 284].

They do.

```{r mcmc-trank}
m_full_ordbeta |> 
  tidybayes::gather_draws(!!!syms(params_to_show)) |> 
  group_by(.variable) |> 
  mutate(draw_rank = rank(.value)) |> 
  ggplot(aes(x = draw_rank, color = factor(.chain))) +
  stat_bin(geom = "step", binwidth = 200, position = position_identity(), boundary = 0) +
  scale_color_viridis_d(option = "rocket", end = 0.85) +
  labs(color = "Chain") +
  facet_wrap(vars(.variable), scales = "free_y")
```

## Posterior predictions

The model should generate predictions that align with the observed outcomes. It does.

```{r build-posterior-preds}
full_posterior <- predicted_draws(m_full_ordbeta, 
                                  newdata = m_full_ordbeta$data, 
                                  ndraws = 100)

posterior_categories <- full_posterior |> 
  ungroup() |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "1",
    .prediction > 0 & .prediction < 1 ~ "1–32",
    .prediction == 1 ~ "32"
  )) |> 
  group_by(outcome, .draw) |> 
  summarize(count = n()) |> 
  ungroup()

actual_counts <- m_full_ordbeta$data |> 
  mutate(outcome = case_when(
    province_count == 0 ~ "1",
    province_count > 0 & province_count < 1 ~ "1–32",
    province_count == 1 ~ "32"
  )) |> 
  group_by(outcome) |> 
  summarize(count = n())

plot_categories <- posterior_categories |> 
  ggplot(aes(x = outcome, y = count)) +
  geom_col(data = actual_counts, fill = "grey70") +
  stat_pointinterval() +
  labs(x = NULL, y = "Observed and predicted counts",
       title = "Posterior predictions of discrete and continuous outcomes") +
  coord_cartesian(ylim = c(0, 300))

actual_middle <- m_full_ordbeta$data |> 
  filter(province_count > 0 & province_count < 1) |> 
  mutate(province_count = prop_to_provinces(province_count))

plot_continuous <- full_posterior |> 
  mutate(.prediction = prop_to_provinces(.prediction)) |> 
  filter(.prediction > 1 & .prediction < 32) |> 
  ggplot(aes(x = .prediction, group = .draw)) +
  geom_density(linewidth = 0.05, bounds = c(1, 32)) +
  geom_density(data = actual_middle, aes(x = province_count),
               inherit.aes = FALSE, bounds = c(1, 32)) +
  labs(x = "Discrete and continuous predicted outcomes",
       y = "Probability density")
```

```{r combined-posterior-preds, fig.width=6, fig.height=5}
arrow_part <- ggplot() +
  annotate(geom = "segment", x = 0.35, xend = 0.65, y = 0.9, yend = 0.9) +
  annotate(geom = "segment", x = 0.5, xend = 0.5, y = 0.9, yend = 0.1,
           arrow = arrow(angle = 30, type = "closed", length = unit(0.1, "inches"))) +
  scale_x_continuous(limits = c(0, 1)) +
  theme_void()

plot_categories / arrow_part / plot_continuous +
  plot_layout(heights = c(0.45, 0.1, 0.45))
```

```{r}
# ordbetareg's built-in way, just to check
# ordbetareg::pp_check_ordbeta(m_full_ordbeta, ndraws = 100)
```

### 2023-09-13 _targets.R
update to the 20230913 data file

@@ -42,7 +42,7 @@ tar_source()
 list(
   ## Raw data files ----
   tar_target(ongo_manual_file,
-             here_rel("data", "manual_data", "ongo-manual-20230912.csv"),
+             here_rel("data", "manual_data", "ongo-manual-20230913.csv"),
              format = "file"),
   
   ## Graphics and tables ----

### 2023-09-13 notebook/analysis-issue.qmd
Use binary-encoded issue areas to account for multiple work areas

@@
 tar_load(ongo)
-tar_load(c(m_full_ordbeta, preds_issue, epreds_issue))
+tar_load(c(m_full_ordbeta, preds_issue, epreds_issue, issue_indicator_lookup))
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
@@
 epreds_issue |> 
-  mutate(work_field_code1 = fct_reorder(work_field_code1, .epred)) |> 
-  ggplot(aes(x = .epred, y = work_field_code1)) +
+  left_join(issue_indicator_lookup, by = join_by(issue_area)) |> 
+  mutate(issue_area_nice = fct_reorder(issue_area_nice, .epred)) |> 
+  ggplot(aes(x = .epred, y = issue_area_nice)) +
   stat_halfeye(fill = clrs[5]) +
@@
 preds_issue_plot <- preds_issue |> 
-  unnest(preds) |> 
+  left_join(issue_indicator_lookup, by = join_by(issue_area)) |> 
   mutate(outcome = case_when(
@@
   )) |> 
-  group_by(outcome, work_field_code1, draw) |> 
+  group_by(outcome, issue_area_nice, draw) |> 
   summarize(count = n()) |> 
-  group_by(work_field_code1, draw) |> 
+  group_by(issue_area_nice, draw) |> 
   mutate(prop = count / sum(count))
 
-ggplot(preds_issue_plot, aes(x = work_field_code1, y = prop)) +
+ggplot(preds_issue_plot, aes(x = issue_area_nice, y = prop)) +
   stat_pointinterval(color = clrs[5], fatten_point = 1) +

### 2023-09-13 R/funs_data.R

@@ -103,6 +103,10 @@ clean_ongo_data <- function(manual, chinafile, province_name) {
            local_aim = ifelse(!is.na(local_aim), 1, 0),
            local_org_name = ifelse(!is.na(local_org_name), 1, 0),
            local_connect = ifelse(cn_background + local_aim + local_org_name == 0, FALSE, TRUE)) |> 
+    # Remove "Chinese background" from work_field_code2
+    mutate(work_field_code2 = case_match(work_field_code2, 
+                                         "Chinese background" ~ NA, 
+                                         .default = work_field_code2)) |> 
     # Create different versions of the outcome variable
     mutate(province_count = geo_scope_num,
            province_pct = province_count / 32,
@@ -118,8 +122,58 @@ clean_ongo_data <- function(manual, chinafile, province_name) {
            days_since_law = time_since_law_passed / days(1),
            months_since_law = time_since_law_passed / months(1),
            years_since_law = time_since_law_passed / years(1)) |> 
-    mutate(year_registered = year(registration_date))
+    mutate(
+      year_registered = year(registration_date),
+      year_registered_cat = factor(year_registered)
+    ) |> 
+    filter(!is.na(work_field))
   
   return(ongo)
 }
 
+widen_data <- function(dat) {
+  dat_long <- dat |>
+    # Make the data long
+    pivot_longer(
+      cols = c(work_field_code1, work_field_code2),
+      names_to = "work_field_code_column",
+      values_to = "issue_area",
+      values_drop_na = TRUE
+    ) |>
+    # Remove tiny categories for now
+    filter(!(issue_area %in% c("Sports", "Equality and advocacy"))) |> 
+    # Add an "issue_" prefix to all the values
+    mutate(issue_area = paste0(
+      "issue_",
+      janitor::make_clean_names(issue_area, allow_dupes = TRUE)
+    ))
+  
+  dat_indicators <- dat_long |> 
+    # Make the data wide with a column per issue, with each column being true if
+    # the organization works on that issue and false otherwise
+    pivot_wider(
+      names_from = issue_area, values_from = issue_area, 
+      values_fn = \(x) !is.na(x), values_fill = FALSE, 
+      id_cols = "ro_id"
+    )
+  
+  dat_combined <- dat |> 
+    left_join(dat_indicators, by = join_by(ro_id))
+
+  return(dat_combined)
+}
+
[…]

### 2023-09-13 R/funs_models.R

@@ -9,7 +9,12 @@ f_full_ordbeta <- function(data) {
   
   model <- ordbetareg(
     bf(
-      province_count ~ work_field_code1 + local_connect + years_since_law + (1 | province_code)
+      province_count ~ 
+        issue_arts_and_culture + issue_education +
+        issue_industry_association + issue_economy_and_trade + 
+        issue_charity_and_humanitarian + issue_general + issue_health +
+        issue_environment + issue_science_and_technology +
+        local_connect + years_since_law + year_registered_cat
     ), 
     data = data,
     true_bounds = c(1, 32),
@@ -25,7 +30,12 @@ f_full_interaction_ordbeta <- function(data) {
   
   model <- ordbetareg(
     bf(
-      province_count ~ work_field_code1 + local_connect * years_since_law + (1 | province_code)
+      province_count ~ 
+        issue_arts_and_culture + issue_education +
+        issue_industry_association + issue_economy_and_trade + 
+        issue_charity_and_humanitarian + issue_general + issue_health +
+        issue_environment + issue_science_and_technology +
+        (local_connect * years_since_law) + year_registered_cat
     ), 
     data = data,
     true_bounds = c(1, 32),
@@ -48,13 +58,25 @@ f_full_interaction_ordbeta <- function(data) {
 #     mutate(preds = map(draw, ~predicted_draws(model, grid, ndraws = 1000)))
 # }
 
-f_preds_issue <- function(model, ndraws = 500) {
+f_preds_issue <- function(model, lookup, ndraws = 500) {
+  issue_matrix <- matrix(FALSE, nrow = nrow(lookup), ncol = nrow(lookup))
+  diag(issue_matrix) <- TRUE
+  colnames(issue_matrix) <- lookup$issue_area
+  
+  newdata <- datagrid(model = model) |> 
+    select(-starts_with("issue")) |> 
+    cross_join(as_tibble(issue_matrix))
+  
   tibble(draw = 1:ndraws) |> 
     mutate(preds = map(draw, ~{
       model |> 
-        predicted_draws(datagrid(model = model, work_field_code1 = unique), 
-                        ndraws = 1000)
-    }))
+        predicted_draws(newdata, ndraws = 1000)
+    })) |> 
+    unnest(preds) |> 
+    ungroup() |> 
[…]

### 2023-09-13 _targets.R

@@ -52,21 +52,24 @@ list(
   ## Process and clean data ----
   tar_target(chinafile_clean, load_clean_chinafile()),
   tar_target(province_name, province_cn_to_en()),
-  tar_target(ongo,
-             clean_ongo_data(ongo_manual_file, chinafile_clean, province_name)),
-  tar_target(ongo_mapdata,
-             clean_map_data(ongo)),
+  tar_target(
+    ongo,
+    clean_ongo_data(ongo_manual_file, chinafile_clean, province_name)
+  ),
+  tar_target(ongo_wide, widen_data(ongo)),
+  tar_target(ongo_mapdata, clean_map_data(ongo)),
+  tar_target(issue_indicator_lookup, make_issue_indicator_lookup(ongo)),
   
   ## Models ----
-  tar_target(m_full_ordbeta, f_full_ordbeta(ongo)),
+  tar_target(m_full_ordbeta, f_full_ordbeta(ongo_wide)),
   tar_target(m_full_interaction_ordbeta, f_full_interaction_ordbeta(ongo)),
   
   ## Posterior predictions ----
-  tar_target(preds_issue, f_preds_issue(m_full_ordbeta)),
+  tar_target(preds_issue, f_preds_issue(m_full_ordbeta, issue_indicator_lookup)),
   tar_target(preds_local, f_preds_local(m_full_ordbeta)),
   tar_target(preds_timing, f_preds_timing(m_full_ordbeta)),
   
-  tar_target(epreds_issue, f_epreds_issue(m_full_ordbeta)),
+  tar_target(epreds_issue, f_epreds_issue(m_full_ordbeta, issue_indicator_lookup)),
   tar_target(epreds_local, f_epreds_local(m_full_ordbeta)),
   tar_target(epreds_timing, f_epreds_timing(m_full_ordbeta)),
   tar_target(epreds_timing_local, f_epreds_timing_local(m_full_ordbeta)),

### 2023-09-13 manuscript/manuscript.qmd
Fix missing space
Fix issue area plots in manuscript

@@
            epreds_issue, epreds_local, epreds_timing,
-           epreds_timing_local))
+           epreds_timing_local, issue_indicator_lookup))
 
@@
 \end{aligned}
-$$ {#eq-ordbeta}
+$${#eq-ordbeta}
 
@@
 #| fig-cap: "Count of international NGO registrations, divided by issue area"
+# TODO: Use issue_area instead of work_field_code
 issue_count <- ongo |> 
@@
   )) |> 
-  group_by(outcome, work_field_code1, draw) |> 
+  group_by(outcome, issue_area_nice, draw) |> 
   summarize(count = n()) |> 
-  group_by(work_field_code1, draw) |> 
+  group_by(issue_area_nice, draw) |> 
   mutate(prop = count / sum(count)) |> 
   ungroup() |> 
-  mutate(work_field_code1 = fct_reorder(work_field_code1, prop))
+  mutate(issue_area_nice = fct_reorder(issue_area_nice, prop))
 
 # preds_issue_plot |>
-#   group_by(outcome, work_field_code1) |>
+#   group_by(outcome, issue_area_nice) |>
 #   median_qi(prop)
 
-ggplot(preds_issue_plot, aes(x = work_field_code1, y = prop)) +
+ggplot(preds_issue_plot, aes(x = issue_area_nice, y = prop)) +
   stat_pointinterval(color = clrs[5], .width = 0.95, fatten_point = 1) +
@@
 epreds_issue |> 
-  mutate(work_field_code1 = fct_reorder(work_field_code1, .epred)) |> 
-  ggplot(aes(x = .epred, y = work_field_code1)) +
+  left_join(issue_indicator_lookup, by = join_by(issue_area)) |> 
+  mutate(issue_area_nice = fct_reorder(issue_area_nice, .epred)) |> 
+  ggplot(aes(x = .epred, y = issue_area_nice)) +
   stat_halfeye(fill = clrs[5], .width = c(0.8, 0.95)) +
@@
     .prediction == 1 ~ "32 provinces"
-  )) %>% 
-  group_by(outcome, years_since_law, draw) %>% 
+  )) |> 
+  group_by(outcome, years_since_law, draw) |>  
   summarize(count = n()) |> 

### 2023-09-13 _targets.R

@@ -62,7 +62,7 @@ list(
   
   ## Models ----
   tar_target(m_full_ordbeta, f_full_ordbeta(ongo_wide)),
-  tar_target(m_full_interaction_ordbeta, f_full_interaction_ordbeta(ongo)),
+  tar_target(m_full_interaction_ordbeta, f_full_interaction_ordbeta(ongo_wide)),
   
   ## Posterior predictions ----
   tar_target(preds_issue, f_preds_issue(m_full_ordbeta, issue_indicator_lookup)),

### 2023-09-14 notebook/analysis-issue.qmd
woohoo stacked bar chart with uncertainty in the boundaries
Idea via https://github.com/mjskay/ggdist/issues/109

@@
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+set_annotation_fonts()
 
@@
 
-```{r plot-pred-discrete-continuous-local, message=FALSE, fig.width=6, fig.height=6}
+```{r plot-pred-discrete-continuous-local-bars, fig.width=8, fig.height=3}
 preds_issue_plot <- preds_issue |> 
@@
 
-ggplot(preds_issue_plot, aes(x = issue_area_nice, y = prop)) +
-  stat_pointinterval(color = clrs[5], fatten_point = 1) +
-  expand_limits(y = 0) +
-  facet_wrap(vars(outcome), ncol = 1) +
-  scale_x_discrete(labels = label_wrap(10)) +
-  scale_y_continuous(labels = label_percent()) +
-  labs(x = NULL, y = "Proportion of predictions") +
-  theme_ongo()
+preds_issue_plot_order <- preds_issue_plot |> 
+  filter(outcome == "32 provinces") |>
+  group_by(issue_area_nice) |> 
+  summarize(median_prop = median(prop)) |> 
+  arrange(median_prop) |> 
+  mutate(issue_area_nice_labels = str_wrap(issue_area_nice, 15)) |> 
+  mutate(issue_area_nice = fct_inorder(issue_area_nice))
+
+preds_issue_text <- preds_issue_plot |> 
+  group_by(outcome, issue_area_nice) |> 
+  summarize(median_prop = median(prop)) |> 
+  group_by(issue_area_nice) |> 
+  mutate(y = (median_prop / 2) + lag(cumsum(median_prop), default = 0)) |> 
+  mutate(y = 1 - y) |> 
+  mutate(prop_nice = label_percent(accuracy = 1)(median_prop)) |> 
+  mutate(issue_area_nice = factor(
+    issue_area_nice, 
+    levels = preds_issue_plot_order$issue_area_nice,
+    labels = preds_issue_plot_order$issue_area_nice_labels
+  ))
+
+preds_issue_plot |> 
+  mutate(issue_area_nice = factor(
+    issue_area_nice, 
+    levels = preds_issue_plot_order$issue_area_nice,
+    labels = preds_issue_plot_order$issue_area_nice_labels
+  )) |> 
+  ggplot(aes(x = draw, y = prop)) +
+  geom_col(aes(fill = outcome), position = "stack", linewidth = 0, width = 1) +
+  geom_text(
+    data = preds_issue_text,
+    aes(x = 250, y = y, label = prop_nice),
+    size = 3, fontface = "bold", color = "white"
+  ) +
+  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
+  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
+  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
+  facet_wrap(vars(issue_area_nice), strip.position = "bottom", nrow = 1) +
+  labs(x = NULL, y = "Proportion of predictions", fill = NULL) +
+  theme_ongo() +
+  theme(
+    panel.grid.major = element_blank(),
+    panel.border = element_blank(),
+    panel.spacing = unit(5, "pt"),
+    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
+  )
 ```

### 2023-09-14 notebook/analysis-issue.qmd
Show ci in plot instead of median

--- 2023-09-13 notebook/analysis-issue.qmd
@@
 
-```{r plot-pred-discrete-continuous-local, message=FALSE, fig.width=6, fig.height=6}
+```{r plot-pred-discrete-continuous-local-bars, fig.width=8, fig.height=3, out.width="100%"}
 preds_issue_plot <- preds_issue |> 
@@
 
-ggplot(preds_issue_plot, aes(x = issue_area_nice, y = prop)) +
-  stat_pointinterval(color = clrs[5], fatten_point = 1) +
-  expand_limits(y = 0) +
-  facet_wrap(vars(outcome), ncol = 1) +
-  scale_x_discrete(labels = label_wrap(10)) +
-  scale_y_continuous(labels = label_percent()) +
-  labs(x = NULL, y = "Proportion of predictions") +
-  theme_ongo()
+preds_issue_plot_order <- preds_issue_plot |> 
+  filter(outcome == "32 provinces") |>
+  group_by(issue_area_nice) |> 
+  summarize(median_prop = median(prop)) |> 
+  arrange(median_prop) |> 
+  mutate(issue_area_nice_labels = str_wrap(issue_area_nice, 15)) |> 
+  mutate(issue_area_nice = fct_inorder(issue_area_nice))
+
+preds_issue_text <- preds_issue_plot |> 
+  group_by(outcome, issue_area_nice) |> 
+  summarize(median_prop = median_qi(prop)) |> 
+  unnest(median_prop) |> 
+  group_by(issue_area_nice) |> 
+  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
+  mutate(y_plot = 1 - y_plot) |> 
+  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
+  mutate(prop_ci_nice = glue::glue(
+    "{ymin}–{ymax}",
+    ymin = label_number(accuracy = 1, scale = 100)(ymin),
+    ymax = label_percent(accuracy = 1)(ymax)
+  )) |> 
+  mutate(issue_area_nice = factor(
+    issue_area_nice, 
+    levels = preds_issue_plot_order$issue_area_nice,
+    labels = preds_issue_plot_order$issue_area_nice_labels
+  ))
+
+preds_issue_plot |> 
+  mutate(issue_area_nice = factor(
+    issue_area_nice, 
+    levels = preds_issue_plot_order$issue_area_nice,
+    labels = preds_issue_plot_order$issue_area_nice_labels
+  )) |> 
+  ggplot(aes(x = draw, y = prop)) +
+  geom_col(aes(fill = outcome), position = "stack", linewidth = 0, width = 1) +
+  geom_text(
+    data = preds_issue_text,
+    aes(x = 250, y = y_plot, label = prop_ci_nice),
+    size = 3, fontface = "bold", color = "white"
+  ) +
+  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
+  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
+  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
+  facet_wrap(vars(issue_area_nice), strip.position = "bottom", nrow = 1) +
+  labs(x = NULL, y = "Proportion of predictions", fill = NULL) +
+  theme_ongo() +
+  theme(
+    panel.grid.major = element_blank(),
+    panel.border = element_blank(),
+    panel.spacing = unit(5, "pt"),
+    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
+  )
 ```

### 2023-09-14 R/funs_graphics.R
Use fontface bc that's the actual argument name oops

@@ -1,8 +1,8 @@
 clrs <- MetBrewer::met.brewer("Tam")
 
 set_annotation_fonts <- function() {
-  ggplot2::update_geom_defaults("label", list(family = "IBM Plex Sans Condensed", face = "plain"))
-  ggplot2::update_geom_defaults("text", list(family = "IBM Plex Sans Condensed", face = "plain"))
+  ggplot2::update_geom_defaults("label", list(family = "IBM Plex Sans Condensed", fontface = "plain"))
+  ggplot2::update_geom_defaults("text", list(family = "IBM Plex Sans Condensed", fontface = "plain"))
 }
 
 theme_ongo <- function(base_size = 11, base_family = "IBM Plex Sans Condensed", prior = FALSE) {

### 2023-09-14 notebook/analysis-timing.qmd
Stacked area plot for year predictions

@@
   epred_draws(datagrid(model = m_full_ordbeta, years_since_law = 0:5), 
-              ndraws = 1000)
+              ndraws = 1000) |> 
+  mutate(years_since_law = 2017 + years_since_law)
 
@@
   mutate(years_since_law = factor(years_since_law)) |> 
-  ggplot(aes(x = .epred, y = years_since_law)) +
+  ggplot(aes(x = .epred, y = fct_rev(years_since_law))) +
   stat_halfeye(fill = clrs[7]) +
@@
   guides(fill = "none") +
-  labs(x = "Expected proportion of provinces", y = "Years since law took effect in 2017") +
+  labs(x = "Expected proportion of provinces", y = "Year") +
   theme_ongo() +
@@
   ggplot(aes(x = years_since_law, y = .epred)) +
-  scale_x_reverse() +
   scale_y_continuous(labels = label_percent(),
@@
                                          name = "Expected provinces")) +
-  labs(x = "Years since law took effect (2017)", 
+  labs(x = "Year", 
        y = "Expected proportion of provinces") +
@@
 
-```{r plot-pred-discrete-continuous-timing, message=FALSE}
+```{r plot-pred-discrete-continuous-timing-area}
 preds_timing_plot <- preds_timing |> 
@@
   )) |> 
+  mutate(years_since_law = 2017 + years_since_law) |> 
   group_by(outcome, years_since_law, draw) |>
@@
 
-ggplot(preds_timing_plot, aes(x = years_since_law, y = prop)) +
-  stat_lineribbon(alpha = 0.35, fill = clrs[7], color = clrs[7]) +
-  expand_limits(y = 0) +
-  facet_wrap(vars(outcome)) +
-  scale_x_reverse(breaks = c(0:5)) +
-  scale_y_continuous(labels = label_percent()) +
-  labs(x = "Years since law took effect (2017)", 
-       y = "Proportion of predictions") +
-  theme_ongo()
+layers <- preds_timing_plot |> 
+  filter(draw <= 50) |> 
+  split(~ draw) |> 
+  lapply(\(x) {
+    geom_area(
+      data = x,
+      aes(y = prop, fill = outcome),
+      alpha = 0.05
+    )
+  })
+
+preds_timing_text <- preds_timing_plot |> 
+  filter(years_since_law == 2017.2) |> 
+  group_by(outcome) |> 
+  summarize(median_prop = median_qi(prop)) |> 
+  unnest(median_prop) |> 
+  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
+  mutate(y_plot = 1 - y_plot) |> 
+  mutate(years_since_law = 2017.2)
+
+ggplot(preds_timing_plot, aes(x = years_since_law)) +
+  layers +
+  geom_text(
+    data = preds_timing_text, 
+    aes(y = y_plot, label = outcome),
+    color = "white",
+    hjust = 0, fontface = "bold", size = 4, show.legend = FALSE
+  ) +
+  scale_x_continuous(expand = expansion(mult = 0.02)) +
+  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
+  scale_color_manual(values = colorspace::darken(clrs[c(3, 5, 7)], 0.1)) +
+  scale_fill_manual(values = colorspace::lighten(clrs[c(3, 5, 7)], 0)) +
+  labs(x = "Year", y = "Predicted probability of outcome") +
+  guides(fill = "none") +
+  theme_ongo() +
+  theme(
+    panel.grid.major = element_blank()
+  )
 ```

### 2023-09-14 R/funs_models.R

@@ -92,7 +92,7 @@ f_preds_timing <- function(model, ndraws = 100) {
   tibble(draw = 1:ndraws) |> 
     mutate(preds = map(draw, ~{
       model |> 
-        predicted_draws(datagrid(model = model, years_since_law = 0:5), 
+        predicted_draws(datagrid(model = model, years_since_law = seq(0, 5, by = 0.1)), 
                         ndraws = 1000, seed = 58214)
     }))
 }

### 2023-09-14 notebook/analysis-issue.qmd
Better labeling of 1, 1-32, and 32 outcomes

@@
   mutate(outcome = case_when(
-    .prediction == 0 ~ "1 province",
-    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
-    .prediction == 1 ~ "32 provinces"
+    .prediction == 0 ~ "Only 1 province",
+    .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
+    .prediction == 1 ~ "All 32 provinces"
   )) |> 
+  mutate(outcome = factor(
+    outcome, 
+    levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"))
+  ) |> 
   group_by(outcome, issue_area_nice, draw) |> 
@@
 preds_issue_plot_order <- preds_issue_plot |> 
-  filter(outcome == "32 provinces") |>
+  filter(outcome == "All 32 provinces") |>
   group_by(issue_area_nice) |> 

### 2023-09-14 notebook/analysis-timing.qmd
Better labeling of 1, 1-32, and 32 outcomes

@@
   mutate(outcome = case_when(
-    .prediction == 0 ~ "1 province",
-    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
-    .prediction == 1 ~ "32 provinces"
+    .prediction == 0 ~ "Only 1 province",
+    .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
+    .prediction == 1 ~ "All 32 provinces"
   )) |> 
+  mutate(outcome = factor(
+    outcome, 
+    levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"))
+  ) |> 
   mutate(years_since_law = 2017 + years_since_law) |> 

### 2023-09-15 manuscript/manuscript.qmd
tiny typo

@@
 However, Beta regression cannot handle values that are exactly 0 or 1, making it inappropriate for our data with its inflated counts at 0 (1) and 100% (32).
-To account for values at the bounds, we rely on ordered Beta regression [@Kubinec:2022], and extension of zero-and-one-inflated Beta regression that allows us to simultaneously model the continuous range of provinces (2–31) and the discrete outcomes (1 province and 32 provinces) without relying on percentages.
+To account for values at the bounds, we rely on ordered Beta regression [@Kubinec:2022], an extension of zero-and-one-inflated Beta regression that allows us to simultaneously model the continuous range of provinces (2–31) and the discrete outcomes (1 province and 32 provinces) without relying on percentages.
 We can thus explore the dynamics of each of our independent variables of interest in multiple ways—we can see (1) how each variable predicts that an organizations works in one province, nationwide, or somewhere in between, and (2) how each variable predicts the overall expected count of provinces.

### 2023-09-15 notebook/model-details.qmd
Add ordered beta illustration + model results table

@@
 ---
-title: Model details
+title: Model details and results
 ---
@@
 library(targets)
-library(brms)
-library(marginaleffects)
-library(tidybayes)
-library(ggdist)
-library(patchwork)
 library(scales)
@@
 library(gtExtras)
+library(modelsummary)
 
@@
 tar_load(ongo)
-tar_load(c(m_full_ordbeta, m_full_interaction_ordbeta))
+tar_load(c(m_full_ordbeta))
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
 invisible(list2env(tar_read(table_functions), .GlobalEnv))
+
+theme_set(theme_ongo())
 ```
+
+# Model run times
 
@@
   "Full model", m_full_ordbeta,
-  "Full model with `local_connect * years_since_law` interaction", m_full_interaction_ordbeta,
 ) |> 
@@
 ```
+
+# Model results
+
+Raw coefficients aren't super useful for interpreting things, but here's a table of them for fun.
+
+```{r results-table}
+modelsummary(
+  m_full_ordbeta,
+  statistic = "[{conf.low}, {conf.high}]",
+  ci_method = "hdi",
+  metrics = c("R2"),
+  output = "gt"
+) |> 
+  opts_theme()
+```

### 2023-09-15 notebook/ordbeta.qmd
Add ordered beta illustration + model results table

---
title: "Why ordered beta regression"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
                      fig.width = 6, fig.height = (6 * 0.618),
                      out.width = "80%", collapse = TRUE,
                      dev = "png", dev.args = list(type = "cairo-png"))

options(digits = 3, width = 120,
        dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

```{r load-libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(brms)
library(ordbetareg)
library(marginaleffects)
library(tidybayes)
library(ggdist)
library(patchwork)
library(scales)

# Generated via random.org
set.seed(196491)

# Load targets
tar_load(ongo)
tar_load(c(m_full_ordbeta, m_full_zoib))
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))

theme_set(theme_ongo())
```

The distribution of our outcome here—the number of provinces an INGO is authorized to work in—posts a unique statistical challenge. It's a mix of three different processes. 30ish% of INGOs are registered only in one province, 40% are registered in all provinces, and the remaining 30ish% are registered in 2–31 provinces.

```{r plot-province-count-collapsed, fig.width=6, fig.height=3}
provinces_collapsed <- ongo |> 
  drop_na(province_count) |> 
  mutate(province_count = case_when(
    province_count == 1 ~ "1",
    province_count > 1 & province_count < 32 ~ "2–31",
    province_count == 32 ~ "32"
  ))

p1 <- ggplot(ongo, aes(x = province_count)) +
  geom_histogram(binwidth = 1, linewidth = 0.1, boundary = 0,
                 fill = clrs[6], color = "white") +
  scale_y_continuous(breaks = seq(0, 250, 50)) +
  labs(x = "Provinces INGOs are authorized to work in", y = "Count") +
  theme_ongo()

p2 <- ggplot(provinces_collapsed, aes(x = province_count)) + 
  geom_bar(fill = clrs[6]) +
  scale_x_discrete(labels = label_wrap(10)) +
  scale_y_continuous(sec.axis = sec_axis(trans = ~ . / nrow(provinces_collapsed),
                                         labels = label_percent()),
                     breaks = seq(0, 250, 50)) +
  labs(x = NULL, y = NULL) +
  theme_ongo()

(p1 | p2) + 
  plot_layout(nrow = 1, widths = c(0.7, 0.3))
```

Additionally, the outcome is bounded between 1 and 32 and we don't want predicted values to go beyond those limits. Using something like OLS thus doesn't work, since (1) it can't capture all three of the only-one, nationwide, or somewhere-in-between processes, and (2) it just draws straight lines that will create predictions like −5 or 42 provinces.

# Proportions instead of counts

We can constrain predictions of the outcome variable by working with proportions instead of counts, which lets us use Beta regression, which naturally limits outcomes to between 0–1. We can scale the count variable down to a 0–1 range by making 32 provinces = 1, 1 province = 0, and all the in-between province counts some percentage. Just dividing the count by 32 doesn't quite work—32/32 is indeed 1, but 1/32 is `r 1/32`, not the 0 we're looking for. Instead, we can subtract 1 from the province count and the total, so that 32 provinces is 31/31, 1 province is 0/31, and so on:

$$
\frac{\text{Province count} - 1}{32 - 1}
$$

We can reverse this process too by multiplying the proportion by 31 and adding 1:

$$
[\text{Province count} \times (32 - 1)] + 1
$$

We can make this easier and more generalizable with some helper functions:

```{r helper-functions}
#| code-fold: show
provinces_to_prop <- function(x, lower = 1, upper = 32) {
  (x - lower) / (upper - lower)
}

prop_to_provinces <- function(x, lower = 1, upper = 32) {
  (x * (upper - lower)) + lower
}

provinces_to_prop(c(1, 5, 19, 32))
prop_to_provinces(provinces_to_prop(c(1, 5, 19, 32)))
```

The distribution of proportions is the same as it was for counts, as expected, but now everything is between 0 and 1 and with a lot of values that are exactly 0 or 1:

```{r plot-province-prop}
ongo |> 
  mutate(province_prop = provinces_to_prop(province_count)) |> 
  # Add some variables for plotting
  mutate(
    is_zero = province_prop == 0,
    is_one = province_prop == 1,
    province_prop = case_when(
      is_zero ~ -0.01,
      is_one ~ 1.02,
      .default = province_prop
    )
  ) |> 
  mutate(outcome_type = case_when(
    is_zero ~ "1 province (0%)",
    is_one ~ "32 provinces (100%)",
    .default = "2–32 provinces"
  )) |> 
  ggplot(aes(x = province_prop)) +
  geom_histogram(
    aes(fill = outcome_type),
    bins = 32, linewidth = 0.1, boundary = 0,
    color = "white") +
  scale_x_continuous(labels = label_percent()) +
  scale_y_continuous(breaks = seq(0, 250, 50)) +
  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
  labs(
    x = "Scaled proportion of provinces INGOs are authorized to work in", 
    y = "Count", fill = NULL) +
  theme_ongo()
```

# Zero-one-inflated Beta (ZOIB) regression

Beta regression by itself can't deal with values that are exactly 0 or 1, but we can use zero-one-inflated beta (ZOIB) regression to deal with them ([see this for a guide about that](https://www.andrewheiss.com/blog/2021/11/08/beta-regression-guide/)). For zero-one-inflated regression, we actually model three different processes:

1. A logistic regression model that predicts if an outcome is either (1) exactly 0 or 1 or (2) not exactly 0 or 1. This is typically defined as $\alpha$, or `zoi` in {brms}
2. A logistic regression model that predicts if the exactly-0-or-1 outcomes are either (1) 0 or (2) 1. This is typically defined as $\gamma$, or `coi` in {brms}
3. A Beta regression model that works with the not-exactly-0-or-1 outcomes. These Beta parameters are typically defined as $\mu$ and $\phi$, or `name_of_outcome` and `phi` in {brms}

This kind of model works really well for our weird {0, (0, 1), 1} outcome, but it requires that we specify covariates for each process of the model. That's both neat (if we have theoretical reasons that the 0 process is different from the 1 process, for instance, we can use different covariates) and intimidating (SO MANY PARAMETERS).

As an example, here's what our full model looks like when using zero-one-inflated regression:

```{r model-zoib-example, eval=FALSE}
#| code-fold: show
m_full_zoib <- brm(
  bf(
    # mu: mean of the 0-1 values; logit scale
    province_pct ~ issue_arts_and_culture + issue_education +
      issue_industry_association + issue_economy_and_trade + 
      issue_charity_and_humanitarian + issue_general + issue_health +
      issue_environment + issue_science_and_technology +
      local_connect + years_since_law + year_registered_cat,
    # zoi: zero-or-one-inflated part; logit scale
    zoi ~ issue_arts_and_culture + issue_education +
      issue_industry_association + issue_economy_and_trade + 
      issue_charity_and_humanitarian + issue_general + issue_health +
      issue_environment + issue_science_and_technology +
      local_connect + years_since_law + year_registered_cat,
    # coi: one-inflated part, conditional on the 0s; logit scale
    coi ~ issue_arts_and_culture + issue_education +
      issue_industry_association + issue_economy_and_trade + 
      issue_charity_and_humanitarian + issue_general + issue_health +
      issue_environment + issue_science_and_technology +
      local_connect + years_since_law + year_registered_cat), 
  data = data,
  family = zero_one_inflated_beta(),
  ...
)
```

The model fits the outcome really well!

```{r show-zoib-pp_check, message=FALSE}
pp_check(m_full_zoib)
```

But holy cow it's a huge model. Check out how many different parameters it spits out:

```{r show-zoib-summary}
#| code-fold: show
m_full_zoib
```

If we're interested in the effect of one of these coefficients, like `issue_arts_and_culture`, we need need to work with three different versions of it: `issue_arts_and_culture` (for the 0-1 process), `zoi_issue_arts_and_culture` (for the exactly-0-or-1 process), and `coi_issue_arts_and_culture` (for the 0 or 1 process). To do this, we can calculate predictions that average over (or marginalize over) all three submodels. We can do that with `marginaleffects::predictions()` and `marginaleffects::avg_comparisons()`:

```{r mfx-zoib}
p1 <- m_full_zoib |> 
  predictions(datagrid(issue_arts_and_culture = unique)) |> 
  posterior_draws() |> 
  ggplot(aes(x = draw, y = issue_arts_and_culture, fill = issue_arts_and_culture)) +
  stat_halfeye() +
  scale_fill_manual(values = clrs[c(1, 6)]) +
  scale_x_continuous(labels = label_percent()) +
  guides(fill = "none") +
  labs(x = "Predicted proportion of provinces")

p2 <- m_full_zoib |> 
  avg_comparisons(
    datagrid(issue_arts_and_culture = unique),
    variables = "issue_arts_and_culture"
  ) |> 
  posterior_draws() |> 
  mutate(term_nice = paste0(term, "\n(", contrast, ")")) |> 
  ggplot(aes(x = draw, y = term_nice)) +
  stat_halfeye(fill = clrs[4]) +
  scale_x_continuous(labels = label_number(accuracy = 1, scale = 100, suffix = " pp.")) +
  guides(fill = "none") +
  labs(x = "Difference in predicted proportions\n(marginal effect of issue area)", y = NULL)

p1 / p2
```

# Ordered Beta regression

Zero-one-inflated Beta regression works, but it's complicated. So instead, we can use a special version of ZOIB regression called "ordered Beta regression" [@Kubinec:2022]—[see here for a tutorial about it](https://www.robertkubinec.com/post/limited_dvs/).

To *grossly* oversimplify how this all works, an ordered Beta model is essentially a zero-one-inflated Beta model fused with an ordinal logistic regression model. With ordered logit, we model the probability of ordered categories (e.g. "strongly disagree", "disagree", "neutral", "agree", "strongly agree") with a single set of covariates that predicts cutpoints between each category. That is, each coefficient shows the effect of moving from "strongly disagree" to any of the other options, then ("strongly disagree" or "disagree") to the other options, and so on, with cutpoint parameters showing the boundaries or thresholds between the probabilities of these categories. Since there's only one underlying process, there's only one set of coefficients to work with, which makes post-processing and interpretation fairly straightforward—there's no need to worry about separate `zoi` and `coi` parts!

Ordered Beta models apply the same intuition to Beta regression. Beta regression can't handle outcomes that are exactly 0 or 1, so we can create three ordered categories to use as an outcome variable: (1) exactly 0, (2) somewhere between 0 and 1, and (3) exactly 1. Then, instead of using logistic regression to model the process of moving along the range of probabilities for these categories (i.e. from "exactly 0" to ("somewhere between 0 and 1" or "exactly 1") and then from ("exactly 0" or "somewhere between 0 and 1") to "exactly 1"), we use Beta regression, which captures continuous values between 0-1.

The `ordbetareg()` function from {ordbetareg} is a wrapper around `brm()` that handles this hybrid sort of model. It also automatically scales down the data to be a percentage within specific bounds, so we don't need to model `province_pct`, and can model `province_count` directly.

```{r model-ordbeta-example, eval=FALSE}
#| code-fold: show
m_full_ordbeta <- ordbetareg(
  bf(
    province_count ~ 
      issue_arts_and_culture + issue_education +
      issue_industry_association + issue_economy_and_trade + 
      issue_charity_and_humanitarian + issue_general + issue_health +
      issue_environment + issue_science_and_technology +
      local_connect + years_since_law + year_registered_cat
  ), 
  data = data,
  true_bounds = c(1, 32),
  ...
)
```

Check out these results. We have just one set of coefficients now (no more `zoi` and `coi`), and we have ordered-logit-esque cutpoints for moving between the exactly-0 and exactly-1 categories. It's Beta regression *and* ordered regression at the same time. Magic!

```{r show-ordbeta-summary}
#| code-fold: show
m_full_ordbeta
```

These coefficients are on an uninterpretable log odds scale (since it's a Beta regression model), so we need to use something like {marginaleffects} or `posterior_epred()` to get these into useful proportion scale estimates:

```{r mfx-ordbeta}
p3 <- m_full_ordbeta |> 
  predictions(datagrid(issue_arts_and_culture = unique)) |> 
  posterior_draws() |> 
  ggplot(aes(x = draw, y = issue_arts_and_culture, fill = issue_arts_and_culture)) +
  stat_halfeye() +
  scale_fill_manual(values = clrs[c(2, 7)]) +
  scale_x_continuous(labels = label_percent()) +
  guides(fill = "none") +
  labs(x = "Predicted proportion of provinces")

p4 <- m_full_ordbeta |> 
  avg_comparisons(
    datagrid(issue_arts_and_culture = unique),
    variables = "issue_arts_and_culture"
  ) |> 
  posterior_draws() |> 
  mutate(term_nice = paste0(term, "\n(", contrast, ")")) |> 
  ggplot(aes(x = draw, y = term_nice)) +
  stat_halfeye(fill = clrs[5]) +
  scale_x_continuous(labels = label_number(accuracy = 1, scale = 100, suffix = " pp.")) +
  guides(fill = "none") +
  labs(x = "Difference in predicted proportions\n(marginal effect of issue area)", y = NULL)

p3 / p4
```

The estimates are roughly comparable to the zero-one-inflated model, though @Kubinec:2022 shows that the ordered Beta results are generally more accurate and less biased. Plus this model fit a ton faster since we didn't need to specify complete separate models for the `zoi` and `coi` processes.

```{r compare-mfx}
(p1 / p3) | (p2 / p4)
```

The posterior predictions are also pretty neat and different. The standard `pp_check()` function doesn't work because the model generates both categorical and continuous predictions, so {ordbetareg} comes with its own `pp_check_ordbeta()` that contains plots in slots named `$discrete` and `$continuous`. It automatically converts the proportion/probability-scale predicted outcomes back into discrete counts, so instead of seeing predictions that range from 0% to 100%, we get predictions for exactly 1, exactly 32, and between 1 and 32 provinces. Neat! ([See here for a fancier, more manual version of these plots.](/notebook/model-diagnostics.qmd#posterior-predictions))

```{r show-ordbeta-pp_check}
#| code-fold: show
posterior_check <- pp_check_ordbeta(m_full_ordbeta, ndraws = 100)
posterior_check$discrete
posterior_check$continuous
```

### 2023-09-15 R/funs_data.R

@@ -2,6 +2,16 @@ library(glue)
 library(rvest)
 suppressPackageStartupMessages(library(lubridate))
 
+# Helper functions for switching between province counts and proportions
+provinces_to_prop <- function(x, lower = 1, upper = 32) {
+  (x - lower) / (upper - lower)
+}
+
+prop_to_provinces <- function(x, lower = 1, upper = 32) {
+  (x * (upper - lower)) + lower
+}
+
+
 load_clean_chinafile <- function() {
   chinafile <- read_html(glue("https://web.archive.org/web/20220922181643/",
                               "https://jessicachinafile.github.io/index_RO_table.html")) |> 
@@ -109,7 +119,7 @@ clean_ongo_data <- function(manual, chinafile, province_name) {
                                          .default = work_field_code2)) |> 
     # Create different versions of the outcome variable
     mutate(province_count = geo_scope_num,
-           province_pct = province_count / 32,
+           province_pct = provinces_to_prop(province_count),
            province_cat = case_when(
              province_count == 1 ~ "Single province",
              province_count > 1 & province_count < 32 ~ "Multiple provinces",

### 2023-09-15 R/funs_models.R

@@ -23,22 +23,37 @@ f_full_ordbeta <- function(data) {
   return(model)
 }
 
-f_full_interaction_ordbeta <- function(data) {
-  library(ordbetareg)
+f_full_zoib <- function(data) {
+  BAYES_SEED <- 102819  # From random.org
   
-  BAYES_SEED <- 860215  # From random.org
+  zoib_priors <- c(prior(student_t(1, 0, 3), class = Intercept),
+    prior(student_t(1, 0, 3), class = b),
+    prior(student_t(1, 0, 3), class = b, dpar = zoi),
+    prior(student_t(1, 0, 3), class = b, dpar = coi))
   
-  model <- ordbetareg(
+  model <- brm(
     bf(
-      province_count ~ 
-        issue_arts_and_culture + issue_education +
+      # mu: mean of the 0-1 values; logit scale
+      province_pct ~ issue_arts_and_culture + issue_education +
         issue_industry_association + issue_economy_and_trade + 
         issue_charity_and_humanitarian + issue_general + issue_health +
         issue_environment + issue_science_and_technology +
-        (local_connect * years_since_law) + year_registered_cat
-    ), 
+        local_connect + years_since_law + year_registered_cat,
+      # zoi: zero-or-one-inflated part; logit scale
+      zoi ~ issue_arts_and_culture + issue_education +
+        issue_industry_association + issue_economy_and_trade + 
+        issue_charity_and_humanitarian + issue_general + issue_health +
+        issue_environment + issue_science_and_technology +
+        local_connect + years_since_law + year_registered_cat,
+      # coi: one-inflated part, conditional on the 0s; logit scale
+      coi ~ issue_arts_and_culture + issue_education +
+        issue_industry_association + issue_economy_and_trade + 
+        issue_charity_and_humanitarian + issue_general + issue_health +
+        issue_environment + issue_science_and_technology +
+        local_connect + years_since_law + year_registered_cat), 
     data = data,
-    true_bounds = c(1, 32),
+    family = zero_one_inflated_beta(), 
+    prior = zoib_priors,
     seed = BAYES_SEED)
   
   return(model)

### 2023-09-15 _targets.R

@@ -48,6 +48,7 @@ list(
   ## Graphics and tables ----
   tar_target(graphic_functions, lst(theme_ongo, set_annotation_fonts, clrs)),
   tar_target(table_functions, lst(opts_int, opts_theme)),
+  tar_target(count_prop_functions, lst(provinces_to_prop, prop_to_provinces)),
 
   ## Process and clean data ----
   tar_target(chinafile_clean, load_clean_chinafile()),
@@ -62,8 +63,8 @@ list(
   
   ## Models ----
   tar_target(m_full_ordbeta, f_full_ordbeta(ongo_wide)),
-  tar_target(m_full_interaction_ordbeta, f_full_interaction_ordbeta(ongo_wide)),
-  
+  tar_target(m_full_zoib, f_full_zoib(ongo_wide)),
+
   ## Posterior predictions ----
   tar_target(preds_issue, f_preds_issue(m_full_ordbeta, issue_indicator_lookup)),
   tar_target(preds_local, f_preds_local(m_full_ordbeta)),

### 2023-09-15 notebook/ordbeta.qmd
tiny typos

@@
 
-The distribution of our outcome here—the number of provinces an INGO is authorized to work in—posts a unique statistical challenge.
+The distribution of our outcome here—the number of provinces an INGO is authorized to work in—poses a unique statistical challenge.
 It's a mix of three different processes.
@@
     is_one ~ "32 provinces (100%)",
-    .default = "2–32 provinces"
+    .default = "2–31 provinces"
   )) |> 

### 2023-09-15 notebook/analysis-issue.qmd
Better handling of outcome labels

@@
     .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
-    .prediction == 1 ~ "All 32 provinces"
+    .prediction == 1 ~ "All 32 provinces",
+    .ptype = factor(
+      levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"), 
+      ordered = TRUE)
   )) |> 
-  mutate(outcome = factor(
-    outcome, 
-    levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"))
-  ) |> 
   group_by(outcome, issue_area_nice, draw) |> 

### 2023-09-15 notebook/analysis-timing.qmd
Better handling of outcome labels

--- 2023-09-14 notebook/analysis-timing.qmd
@@
   mutate(outcome = case_when(
-    .prediction == 0 ~ "1 province",
-    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
-    .prediction == 1 ~ "32 provinces"
+    .prediction == 0 ~ "Only 1 province",
+    .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
+    .prediction == 1 ~ "All 32 provinces",
+    .ptype = factor(
+      levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"), 
+      ordered = TRUE)
   )) |> 

### 2023-09-15 notebook/model-diagnostics.qmd
Use coefficient that actually exists
Add ordered beta illustration + model results table
Better handling of outcome labels

@@
 
-```{r}
-get_variables(m_full_ordbeta)
-```
-
-### Traceplots
+# Traceplots
 
@@
 params_to_show <- c(
-  "b_Intercept", "b_work_field_code1Health",
+  "b_Intercept", "b_issue_healthTRUE",
   "phi", "cutzero"
@@
 
-### Trace rank plots (trank plots)
+# Trace rank plots (trank plots)
 
@@
 
-## Posterior predictions
+# Posterior predictions
 
@@
   mutate(outcome = case_when(
-    .prediction == 0 ~ "1",
-    .prediction > 0 & .prediction < 1 ~ "1–32",
-    .prediction == 1 ~ "32"
+    .prediction == 0 ~ "Only 1 province",
+    .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
+    .prediction == 1 ~ "All 32 provinces",
+    .ptype = factor(
+      levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"), 
+      ordered = TRUE)
   )) |> 
@@
   mutate(outcome = case_when(
-    province_count == 0 ~ "1",
-    province_count > 0 & province_count < 1 ~ "1–32",
-    province_count == 1 ~ "32"
+    province_count == 0 ~ "Only 1 province",
+    province_count > 0 & province_count < 1 ~ "Between 1–32 provinces",
+    province_count == 1 ~ "All 32 provinces",
+    .ptype = factor(
+      levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"), 
+      ordered = TRUE)
   )) |> 

### 2023-09-15 manuscript/manuscript.qmd
Updated manuscript date to indicate updates have been made

@@
 short-title: "China's ONGO Law and International Civil Society"
-date: "2023-04-09"
+date: "2023-08-22"
 author:

### 2023-09-16 manuscript/manuscript.qmd
updated citation

@@
 This global trend of closing or shrinking civic space [@Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016] has affected countries of all regime types, including both autocracies and democracies such as Morocco and Palestine [@AtiaHerrold:2018], India [@press-trust-india:2019], Vietnam [@Sidel:2023], Canada [@CIVICUS:2013], and the United States [@Cramer:2020].
-On April 28, 2016, China passed its own set of legal restrictions on civil society with its Law of the People’s Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China, or "ONGO Law," which formally took effect on January 1, 2017.
+On April 28, 2016, China passed its own set of legal restrictions on civil society with its Law of the People's Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China, or "ONGO Law," which formally took effect on January 1, 2017.
 As an authoritarian state with a growing nonprofit sector, the Chinese model of implementing restrictive laws for international NGOs (INGOs) has important implications for understanding the dynamics of how civil society laws can be used as policy tools to harness INGOs.
@@
 International NGOs began to play an important role in China in the early 1990s as part of the country's Reform and Opening-Up policy, and organizations like Save the Children and the Ford Foundation established local offices and branches.
-Since then, INGOs and global civil society have played pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China’s domestic nonprofit sector [@Yin:2009].
+Since then, INGOs and global civil society have played pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China's domestic nonprofit sector [@Yin:2009].
 Prior to the implementation of the 2017 ONGO Law, regulation of INGOs in China was obscure [@Shieh:2018; @Spires:2022].
@@
 
-Many INGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [@Sidel:2016], though there were no clear requirements for them to have a formal legal presence in China [@Han:2011].
+Many INGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [@Sidel:2016], though there were no clear requirements for them to have a formal legal presence in China [@Han:2011; @HolbigLang:2022; @Yin:2009].
 However, the legal form of foreign-funded company is not quite compatible with the nonprofit nature of INGOs.
@@
 This paper explores the characteristics of all registered INGOs in China in the five years after the ONGO Law became effective and examines the association between INGO issue areas and the operational space granted to them in the country.
-Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)—a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus.
+Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus.
 Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018].
@@
 
-::: {.callout-warning}
+::: callout-warning
 Apologies! This section is still *incredibly* drafty!
@@
 Studies on the law has been focused on discussing the historical and political impetus of passing the law [@Shieh:2018] or analyzing the regulatory regimes it that has established and potential implications for INGOs operating in China [@Feng:2017; @TeetsHsu:2016].
-However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs’ operations and projects have been affected by the law after successfully gaining legal registration and documentation.
+However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs' operations and projects have been affected by the law after successfully gaining legal registration and documentation.
 A few studies [@Jia:2017; @YeHuang:2018] have reflected on the implementation of the ONGO Law after its first year, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations.
@@
 China provides an excellent setting for testing these theories because China's promulgation of restrictive INGO law as an authoritarian jurisdiction fits the observed global trends in recent years, thus can serve as an representative case to deepen scholarly understanding around these themes.
-Also, the level of ambiguity of the legal framework gives ample room for arbitrary discretion and conflicting attitudes by authorities, enabling us to analyze rules in form (*de jure*) as well as rules in use (*de facto*).
+Also, the level of ambiguity of the legal framework gives ample room for arbitrary discretion and conflicting attitudes by authorities[@Jia:2017], enabling us to analyze rules in form (*de jure*) as well as rules in use (*de facto*).
 
@@
 
-@ChaudhryHeiss:2022 and the divergence in de jure and de facto regulations—the implementation doesn't have to match the written law, and often the written law can serve as a "weapon hanging on the wall that never fires" that serves as a warning to potentially uncooperative NGOs [@Kozenko:2015].
+@ChaudhryHeiss:2022 and the divergence in de jure and de facto regulations---the implementation doesn't have to match the written law, and often the written law can serve as a "weapon hanging on the wall that never fires" that serves as a warning to potentially uncooperative NGOs [@Kozenko:2015].
 See also [@ToeplerZimmerFrohlich:2020; @Plantan:2022]
 
-::: {.content-hidden}
-
+::: content-hidden
 "We discuss the role of civil society organizations (CSOs) as agents of democratization and note the emergence of dual, at times apparently conflicting policy postures within authoritarian regimes (restriction and repression for some CSOs vs.
@@
 Also, [@Plantan:2022] finds "that I find" evidence of selective implementation that reveals which groups are seen as threatening or beneficial."
-
 :::
@@
 First we code each INGO's issue area based on its mission statement reported in its registration documentation.
-Given there is certain level of subjectivity in the coding process, the coding of issue areas are cross-checked between the researchers—Author 1 assigned each organization into one of the issue areas defined in Article 3 of the ONGO Law, and Author 2 cross-checked the coding for ambiguous cases.
+Given there is certain level of subjectivity in the coding process, the coding of issue areas are cross-checked between the researchers---Author 1 assigned each organization into one of the issue areas defined in Article 3 of the ONGO Law, and Author 2 cross-checked the coding for ambiguous cases.
 We include our coding rules for overlapping issue areas in the appendix (in the future).
@@
 Our final independent variable measures how much time elapsed between the January 1, 2017 (when the law took effect) and the organization's official registration date.
-There is great variance in the timing of registering an RO among INGOs, since there has been a *de facto* grace period for INGOs to seek legal presence after the law took effect.
+There is great variance in the timing of registering an RO among INGOs, since there has been a *de facto* grace period for INGOs to seek legal presence after the law took effect[@Shieh:2018].
 This is largely because both INGOs and the regulators needed some transitional time to explore the specific implementation of the law as large ambiguity was left when the law was passed.
@@
 Modeling the count of provinces each INGO is authorized to operate in presents a unique statistical challenge.
-As seen in @fig-province-count-collapsed, roughly 30% of INGOs are registered in only one province, 40% are registered nationwide, while the remaining 30% are registered in 2–31 provinces.
+As seen in @fig-province-count-collapsed, roughly 30% of INGOs are registered in only one province, 40% are registered nationwide, while the remaining 30% are registered in 2--31 provinces.
 Our main variable of interest is thus a mix of continuous outcomes (i.e.
@@
 negative counts of provinces or more than 32 provinces).
-If we transform the count of provinces to a percentage, Beta regression would work well, as it is naturally limited outcomes within a 0–1 range.
+If we transform the count of provinces to a percentage, Beta regression would work well, as it is naturally limited outcomes within a 0--1 range.
 However, Beta regression cannot handle values that are exactly 0 or 1, making it inappropriate for our data with its inflated counts at 0 (1) and 100% (32).
-To account for values at the bounds, we rely on ordered Beta regression [@Kubinec:2022], an extension of zero-and-one-inflated Beta regression that allows us to simultaneously model the continuous range of provinces (2–31) and the discrete outcomes (1 province and 32 provinces) without relying on percentages.
-We can thus explore the dynamics of each of our independent variables of interest in multiple ways—we can see (1) how each variable predicts that an organizations works in one province, nationwide, or somewhere in between, and (2) how each variable predicts the overall expected count of provinces.
+To account for values at the bounds, we rely on ordered Beta regression [@Kubinec:2022], an extension of zero-and-one-inflated Beta regression that allows us to simultaneously model the continuous range of provinces (2--31) and the discrete outcomes (1 province and 32 provinces) without relying on percentages.
+We can thus explore the dynamics of each of our independent variables of interest in multiple ways---we can see (1) how each variable predicts that an organizations works in one province, nationwide, or somewhere in between, and (2) how each variable predicts the overall expected count of provinces.
 
@@
 
-::: {.column-page-inset-right}
-
+::: column-page-inset-right
 $$
@@
 \end{aligned}
-$${#eq-ordbeta}
-
+$$ {#eq-ordbeta}
 :::
@@
 A couple dozen organizations were able to register immediately after the law took effect during the first quarter of 2017, while hundreds more registered during the rest of that year.
-Nearly half of all currently-registered INGOs in China—48%—registered in 2017.
+Nearly half of all currently-registered INGOs in China---48%---registered in 2017.
 After the initial first-year wave, the count of new registrations has declined slowly since 2018.
@@
 Several notable trends emerge from the model results.
-INGOs focused on arts and culture are overwhelming the most likely kind of organization to work nationally—arts and culture organizations are predicted to work in all 32 provinces 80% of the time (with a credible interval of 78–83%) and are only predicted to work in a single province a rare 3–5% of the time.
-Education-focused INGOs, on the other hand, are the least likely kind of organization to be registered in all 32 provinces and are predicted to do so only 32–38% of the time.
-Education INGOs are the most likely to be registered in only one province, with that predicted outcome appearing 24–29% of the time—at least 10 percentage points higher than any other issue area's predicted proportion.
-All other issue areas follow roughly the patterns in predictions: the most common outcome is for organizations to work nationally (50–60% of the time), followed by working in at least 2 provinces (25–40% of the time), followed by working in a single province (10–20% of the time).
+INGOs focused on arts and culture are overwhelming the most likely kind of organization to work nationally---arts and culture organizations are predicted to work in all 32 provinces 80% of the time (with a credible interval of 78--83%) and are only predicted to work in a single province a rare 3--5% of the time.
+Education-focused INGOs, on the other hand, are the least likely kind of organization to be registered in all 32 provinces and are predicted to do so only 32--38% of the time.
+Education INGOs are the most likely to be registered in only one province, with that predicted outcome appearing 24--29% of the time---at least 10 percentage points higher than any other issue area's predicted proportion.
+All other issue areas follow roughly the patterns in predictions: the most common outcome is for organizations to work nationally (50--60% of the time), followed by working in at least 2 provinces (25--40% of the time), followed by working in a single province (10--20% of the time).
 @fig-issue-preds-2 shows the continuous posterior distribution of the average number of provinces INGOs are expected to be registered in across all types of issue areas, but accounting for the 1- and 32-only provinces simultaneously.
-We can see a similar trend—arts and culture INGOs are predicted to work in 28–30 provinces on average, while education INGOs are only predicted to work in 12–20.
-All other issues range between 20–28 provinces.
+We can see a similar trend---arts and culture INGOs are predicted to work in 28--30 provinces on average, while education INGOs are only predicted to work in 12--20.
+All other issues range between 20--28 provinces.
 
@@
 The idea that INGOs would "propagate foreign practices" had especially powerful salience, since increased exposure to the West through international NGOs had the potential to "lead to adoption of Western ideas of liberty, further endangering government control over the populace" [@HsiaWhite:2002, 337].
-Educational NGOs were one particular avenue for the West to exert influence in the country—the directors and presidents of dozens of China's largest domestic NGOs have received doctoral degrees from and hold visiting appointments at Cornell, Duke, UNC-Chapel Hill, Harvard, Yale, and other prominent US universities [@Wang:2012, 108–9], and their training and connections abroad have influenced their programming and advocacy at home.
+Educational NGOs were one particular avenue for the West to exert influence in the country---the directors and presidents of dozens of China's largest domestic NGOs have received doctoral degrees from and hold visiting appointments at Cornell, Duke, UNC-Chapel Hill, Harvard, Yale, and other prominent US universities [@Wang:2012, 108--9], and their training and connections abroad have influenced their programming and advocacy at home.
 In 2006, one Chinese NGO leader candidly explained that "foreign influence is definitely great.
@@
 @fig-local-preds-1 shows the distribution of predicted posterior outcomes for 1,000 hypothetical INGOs.
-Organizations without local connections are predicted to work nationally across all provinces nearly half of the time (with a 95% credible interval of 46–51%), and are predicted to work in two or more provinces 32–37% of the time.
-These organizations with no local connections or local programmatic focus are only predicted to work in a single province 15–19% of the time.
-In contrast, INGOs *with* local connections are far more likely to only work in one province (32–38%), or only work in a handful of provinces (36–41%).
-For these locally-focused organizations, the least common prediction is to work nationally, with only a 23–29% probability.
+Organizations without local connections are predicted to work nationally across all provinces nearly half of the time (with a 95% credible interval of 46--51%), and are predicted to work in two or more provinces 32--37% of the time.
+These organizations with no local connections or local programmatic focus are only predicted to work in a single province 15--19% of the time.
+In contrast, INGOs *with* local connections are far more likely to only work in one province (32--38%), or only work in a handful of provinces (36--41%).
+For these locally-focused organizations, the least common prediction is to work nationally, with only a 23--29% probability.
 @fig-local-preds-2 shows the posterior distribution of the average number of provinces INGOs are expected to be registered in, conditional on their local connections.
-The same relationship holds—an INGO without local connections is predicted to work in 19–24 provinces on average, while an organization with local connections is only predicted to work in 8–17.
+The same relationship holds---an INGO without local connections is predicted to work in 19--24 provinces on average, while an organization with local connections is only predicted to work in 8--17.
 
@@
 @fig-timing-preds-1 once again shows the predicted posterior outcomes for 1,000 simulated INGOs across a range of time since January 2017.
-Organizations that registered in the first year are predicted to work in all provinces 41–46% of the time, and are predicted to work in two or more provinces 34–39% of the time.
-These early INGOs are the most likely to be registered in only one province and are predicted to do so 17–23% of the time.
+Organizations that registered in the first year are predicted to work in all provinces 41--46% of the time, and are predicted to work in two or more provinces 34--39% of the time.
+These early INGOs are the most likely to be registered in only one province and are predicted to do so 17--23% of the time.
 After the initial wave of registrations in 2017, the likelihood of nationwide reach steadily increases and replaces both the probability of a single province or a partial range of provinces.
-By the end of 2021—5 years after the ONGO Law took effect—the probability of national -level registration increases to 55–61% while the probability of working in a range of provinces increases to predicted to work in two or more provinces increase to 27–32%.
-These late INGOs are the least likely to be registered in only one province and are predicted to do so only 17–22% of the time.
+By the end of 2021---5 years after the ONGO Law took effect---the probability of national -level registration increases to 55--61% while the probability of working in a range of provinces increases to predicted to work in two or more provinces increase to 27--32%.
+These late INGOs are the least likely to be registered in only one province and are predicted to do so only 17--22% of the time.
 @fig-timing-preds-2 demonstrates the same results with the posterior distribution of the expected count of provinces over five years since 2017.
-INGOs that register early are predicted to work in 17–22 provinces, while those that wait until 2021 are predicted to work in 21–28.
+INGOs that register early are predicted to work in 17--22 provinces, while those that wait until 2021 are predicted to work in 21--28.
 
@@
 As a preliminary test of this speculation, we rerun our main model with an interaction between years since registration and local connections to see how the effect of local connections changes over time.
-As seen in @fig-timing-local, early registrants in 2017 without local connections are more likely to have a larger geographic reach, registering in an average of 19–23 provinces, while their locally-focused counterparts are only expected to register in an average of 7–16 provinces.
+As seen in @fig-timing-local, early registrants in 2017 without local connections are more likely to have a larger geographic reach, registering in an average of 19--23 provinces, while their locally-focused counterparts are only expected to register in an average of 7--16 provinces.
 Accordingly, it may be that organizations with local connections are more likely to register early because of their pre-existing bureaucratic relationships, while organizations with a larger national reach take longer to undertake the registration process and thus register later.
@@
 
-::: {.callout-warning}
+::: callout-warning
 **Still TODO!**

### 2023-09-20 notebook/model-details.qmd
Add mathy notation + prior plots

@@
 library(modelsummary)
+library(ggtext)
+library(brms)
+library(tidybayes)
+library(patchwork)
 
@@
 theme_set(theme_ongo())
+set_annotation_fonts()
+```
+
+# Model definition
+
+$$
+\begin{align}
+&\ \textbf{Registered provinces for INGO } i \\
+\text{Count of provinces}\ \sim&\ \operatorname{Ordered\,Beta}(\mu_{i_j}, \phi_y, k_{1_y}, k_{2_y}) \\[8pt]
+&\ \textbf{Model of outcome average} \\
+% Put the huge equation in a nested \begin{aligned}[t] environment so that 
+% \mathrlap{} can go around it so that the annotations in the priors can be 
+% aligned closer to the math
+\mu_i =&\ 
+  \mathrlap{\begin{aligned}[t]
+  & \beta_0 + \beta_1\ \text{Issue[Arts and culture]} + \beta_2\ \text{Issue[Education]}\ +\\
+  & \beta_3\ \text{Issue[Industry association]} + \beta_4\ \text{Issue[Economy and trade]}\ + \\
+  & \beta_5\ \text{Issue[Charity and humanitarian]} + \beta_6\ \text{Issue[General]}\ + \\
+  & \beta_7\ \text{Issue[Health]} + \beta_8\ \text{Issue[Environment]}\ + \\
+  & \beta_9\ \text{Issue[Science and technology]} + \beta_{10}\ \text{Local connections}\ + \\
+  & \beta_{11}\ \text{Time since Januay 2017} + \beta_{12}\ \text{Year registered}
+  \end{aligned}}\\[8pt]
+&\ \textbf{Priors} \\
+\beta_0\ \sim&\ \operatorname{Student\,t}(\nu = 3, \mu = 0, \sigma = 2.5) && \text{Intercept} \\
+\beta_{1..12}\ \sim&\ \mathcal{N}(0, 5) && \text{Coefficients} \\
+\phi_y\ \sim&\ \operatorname{Exponential}(1 / 100) && \text{Variability in province count} \\
+k_{1_y}, k_{2_y}\ \sim&\ \operatorname{Induced\,Dirichlet}(1, 1, 1), && \text{0–continuous and continuous–1 cutpoints} \\
+&\ \quad \text{or } \bigl[P(\alpha_1), P(\alpha_1 + \alpha_2)\bigr] && \quad\text{(boundaries between 3 Dirichlet columns)}
+\end{align}
+$$
+
+# Model priors
+
+These are all pretty standard.
+I'd like to use a Student t for the coefficients in addition to the intercept, but the prior distributional families are baked into `ordbetareg()` and the only way to change them is to create a custom {brms} family based on the code in `ordbetareg()` and that's a lot of hassle.
+So we'll live with a normal distribution for the coefficients.
+
+The only new-to-me distribution here is the Dirichlet prior for the cutpoints, so I wrote a whole blog post about it here.
+This is a little confusing, though.
+`ordbetareg()` requires a three-element Dirichlet distribution that contains three columns of probabilities, one per submodel: the only-zero part, the between-zero-and-one part, and the only-one part.
+However, it doesn't use these three probabilities directly.
+Instead, it uses an [*induced* Dirichlet distribution](https://betanalpha.github.io/assets/case_studies/ordinal_regression.html) [@Kubinec:2022, p.
+524], meaning that it works with the *boundaries between the categories* and not the Dirichlet columns themselves ([see here for more about that, plus some neat visualizations of the cutpoints](https://www.andrewheiss.com/blog/2023/09/18/understanding-dirichlet-beta-intuition/#bonus-later-addition-boundaries-between-categories)).
+
+$\operatorname{Dirichlet}(1, 1, 1)$ represents a uniform distribution of three related columns in a matrix, each with a probability of 33%, since the sum of the three probabilities must be 100%.
+
+$$
+\begin{align}
+\textbf{E}(\alpha_1) &= \frac{\alpha_1}{\sum{\alpha}} = \frac{1}{1 + 1 + 1} = \frac{1}{3} = 0.333 \\[8pt]
+\textbf{E}(\alpha_2) &= \frac{\alpha_2}{\sum{\alpha}} = \frac{1}{1 + 1 + 1} = \frac{1}{3} = 0.333 \\[8pt]
+\textbf{E}(\alpha_3) &= \frac{\alpha_3}{\sum{\alpha}} = \frac{1}{1 + 1 + 1} = \frac{1}{3} = 0.333
+\end{align}
+$$
+
+We can find the distributions of the boundaries between these columns too—$k_1$, or the boundary between the $\alpha_1$ and $\alpha_2$ columns, is immediately after $\alpha_1$, or at 0.33; $k_2$, or the boundary between $\alpha_2$ and $\alpha_3$, is immediately after $\alpha_2$, which is at ($\alpha_1 + \alpha_2$), or 0.66.
+Because Dirichlet is just a fancy multivariate version of a Beta distribution, each of the $\alpha$ columns by itself is a Beta distribution, and by extension, the $k$ boundaries between the $\alpha$ columns are also Beta distributions:
+
+$$
+\begin{align}
+k_1 &= \textbf{E}(\alpha_1) = \frac{1}{3} & k_2 &= (\textbf{E}(\alpha_2) + \textbf{E}(\alpha_2)) = \frac{2}{3}\\
+&= \operatorname{Beta}(1, 2) & &= \operatorname{Beta}(2, 1)
+\end{align}
+$$
+
+So here's what all our priors look like:
+
+```{r plot-priors}
+prior_summary(m_full_ordbeta) |>
+  bind_rows(
+    tibble(
+      prior = c("beta(1, 2)", "beta(2, 1)"),
+      class = c("k1", "k2")
+    )
+  ) |>
+  parse_dist() |>
+  filter(
+    prior != "",
+    !str_detect(prior, "^induced")
+  ) |>
+  mutate(class_nice = case_match(
+    class,
+    "Intercept" ~ "β<sub>0</sub>",
+    "b" ~ "β<sub>1–12</sub>",
+    "phi" ~ "φ",
+    "k1" ~ "k<sub>1</sub>",
+    "k2" ~ "k<sub>2</sub>"
+  )) |>
+  mutate(prior_nice = str_to_sentence(str_replace(prior, "_", " "))) |>
+  mutate(class = factor(class, levels = c("Intercept", "b", "phi"))) |>
+  arrange(class) |>
+  mutate(nice_title = glue("**{class_nice}**: {prior_nice}")) %>%
+  mutate(nice_title = fct_inorder(nice_title)) %>%
+  ggplot(aes(y = 0, dist = .dist, args = .args, fill = prior)) +
+  stat_slab(normalize = "panels") +
+  scale_x_continuous(labels = label_comma(style_negative = "minus")) +
+  scale_fill_manual(values = clrs[c(6, 8, 5, 3, 1)]) +
+  facet_wrap(vars(nice_title), scales = "free_x", nrow = 2) +
+  guides(fill = "none") +
+  labs(
+    x = NULL, y = NULL,
+    caption = "k<sub>1</sub> and k<sub>2</sub> are the cutpoints or category boundaries from Dirichlet(1, 1, 1)"
+  ) +
+  theme_ongo(prior = TRUE) +
+  theme(
+    strip.text = element_markdown(), 
+    plot.caption = element_markdown(hjust = 0)
+  )
 ```

### 2023-09-20 R/funs_models.R

@@ -18,6 +18,9 @@ f_full_ordbeta <- function(data) {
     ), 
     data = data,
     true_bounds = c(1, 32),
+    coef_prior_mean = 0,
+    coef_prior_SD = 2.5,
+    phi_prior = 1/100,
     seed = BAYES_SEED)
   
   return(model)

### 2023-09-20 manuscript/manuscript.qmd
Use linewidth

@@
 p1 <- ggplot(ongo, aes(x = province_count)) +
-  geom_histogram(binwidth = 1, size = 0.1, boundary = 0,
+  geom_histogram(binwidth = 1, linewidth = 0.1, boundary = 0,
                  fill = clrs[6], color = "white") +
@@
 Modeling the count of provinces each INGO is authorized to operate in presents a unique statistical challenge.
-As seen in @fig-province-count-collapsed, roughly 30% of INGOs are registered in only one province, 40% are registered nationwide, while the remaining 30% are registered in 2--31 provinces.
+As seen in @fig-province-count-collapsed, roughly 30% of INGOs are registered in only one province, 40% are registered nationwide, while the remaining 30% are registered in 2–31 provinces.
 Our main variable of interest is thus a mix of continuous outcomes (i.e.
@@
 negative counts of provinces or more than 32 provinces).
-If we transform the count of provinces to a percentage, Beta regression would work well, as it is naturally limited outcomes within a 0--1 range.
+If we transform the count of provinces to a percentage, Beta regression would work well, as it is naturally limited to outcomes within a 0–1 range.
 However, Beta regression cannot handle values that are exactly 0 or 1, making it inappropriate for our data with its inflated counts at 0 (1) and 100% (32).
-To account for values at the bounds, we rely on ordered Beta regression [@Kubinec:2022], an extension of zero-and-one-inflated Beta regression that allows us to simultaneously model the continuous range of provinces (2--31) and the discrete outcomes (1 province and 32 provinces) without relying on percentages.
-We can thus explore the dynamics of each of our independent variables of interest in multiple ways---we can see (1) how each variable predicts that an organizations works in one province, nationwide, or somewhere in between, and (2) how each variable predicts the overall expected count of provinces.
+To account for values at the bounds, we rely on ordered Beta regression [@Kubinec:2022], an extension of zero-and-one-inflated Beta regression that allows us to simultaneously model the continuous range of provinces (2–31) and the discrete outcomes (1 province and 32 provinces) without relying on percentages.
+We can thus explore the dynamics of each of our independent variables of interest in multiple ways—we can see (1) how each variable predicts that an organizations works in one province, nationwide, or somewhere in between, and (2) how each variable predicts the overall expected count of provinces.
 

### 2023-09-21 notebook/model-details.qmd
little typos

@@
 &\ \textbf{Registered provinces for INGO } i \\
-\text{Count of provinces}\ \sim&\ \operatorname{Ordered\,Beta}(\mu_{i_j}, \phi_y, k_{1_y}, k_{2_y}) \\[8pt]
+\text{Count of provinces}\ \sim&\ \operatorname{Ordered\,Beta}(\mu_i, \phi_y, k_{1_y}, k_{2_y}) \\[8pt]
 &\ \textbf{Model of outcome average} \\
@@
 
-The only new-to-me distribution here is the Dirichlet prior for the cutpoints, so I wrote a whole blog post about it here.
+The only new-to-me distribution here is the Dirichlet prior for the cutpoints, so [I wrote a whole blog post about it here](https://www.andrewheiss.com/blog/2023/09/18/understanding-dirichlet-beta-intuition/).
 This is a little confusing, though.

### 2023-09-21 notebook/analysis-local.qmd
Add fuzzy stacked bar chart for local connections

@@
 tar_load(ongo)
-tar_load(c(m_full_ordbeta, preds_local))
+tar_load(c(m_full_ordbeta, preds_local, epreds_local))
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+set_annotation_fonts()
 
@@
 ```{r plot-epred-local}
-epreds <- m_full_ordbeta |> 
-  epred_draws(datagrid(model = m_full_ordbeta, local_connect = unique), 
-              ndraws = 1000)
-
-epreds |> 
-  ungroup() |> 
+epreds_local |> 
   mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
@@
                                          name = "Expected provinces",
-                                         breaks = seq(8, 32, 4))) +
+                                         breaks = seq(0, 32, 4))) +
   guides(fill = "none") +
   labs(x = "Expected proportion of provinces", y = NULL) +
+  coord_cartesian(xlim = c(0, 1)) +
   theme_ongo() +
@@
 
-```{r plot-pred-discrete-continuous-local, message=FALSE}
+```{r plot-pred-discrete-continuous-local-bars, message=FALSE, fig.width=4.5, fig.height=3.5, out.width="60%"}
 preds_local_plot <- preds_local |> 
@@
   summarize(count = n()) |> 
+  group_by(local_connect, draw) |> 
+  mutate(prop = count / sum(count))
+
+preds_local_text <- preds_local_plot |> 
+  group_by(outcome, local_connect) |> 
+  summarize(median_prop = median_qi(prop)) |> 
+  unnest(median_prop) |> 
   group_by(local_connect) |> 
-  mutate(prop = count / sum(count) * 100)
+  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
+  mutate(y_plot = 1 - y_plot) |> 
+  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
+  mutate(prop_ci_nice = glue::glue(
+    "{ymin}–{ymax}",
+    ymin = label_number(accuracy = 1, scale = 100)(ymin),
+    ymax = label_percent(accuracy = 1)(ymax)
+  ))
 
-ggplot(preds_local_plot, aes(x = local_connect, y = prop)) +
-  stat_pointinterval(color = clrs[2]) +
-  expand_limits(y = 0) +
-  facet_wrap(vars(outcome)) +
-  scale_x_discrete(labels = label_wrap(10)) +
-  scale_y_continuous(labels = label_percent()) +
-  labs(x = NULL, y = "Proportion of predictions") +
-  theme_ongo()
+preds_local_plot |> 
+  ggplot(aes(x = draw, y = prop)) +
+  geom_col(aes(fill = outcome), position = position_stack(), linewidth = 0, width = 1) +
+  geom_text(
+    data = preds_local_text,
+    aes(x = 250, y = y_plot, label = prop_ci_nice),
+    size = 3, fontface = "bold", color = "white"
+  ) +
+  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
+  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
+  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
+  facet_wrap(vars(local_connect), strip.position = "bottom", nrow = 1) +
+  labs(x = NULL, y = "Proportion of predictions", fill = NULL) +
+  theme_ongo() +
+  theme(
+    panel.grid.major = element_blank(),
+    panel.border = element_blank(),
+    panel.spacing = unit(5, "pt"),
+    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
+  )
 ```

### 2023-09-21 R/funs_models.R

@@ -97,7 +97,7 @@ f_preds_issue <- function(model, lookup, ndraws = 500) {
     select(-value)
 }
 
-f_preds_local <- function(model, ndraws = 100) {
+f_preds_local <- function(model, ndraws = 500) {
   tibble(draw = 1:ndraws) |> 
     mutate(preds = map(draw, ~{
       model |> 

### 2023-09-21 notebook/analysis-issue.qmd
Move prop_to_provinces to a target
It was getting repetitive

@@
 set_annotation_fonts()
-
-prop_to_provinces <- function(x, lower = 1, upper = 32) {
-  (x * (upper - lower)) + lower
-}
 ```

### 2023-09-21 _targets.R

@@ -46,7 +46,10 @@ list(
              format = "file"),
   
   ## Graphics and tables ----
-  tar_target(graphic_functions, lst(theme_ongo, set_annotation_fonts, clrs)),
+  tar_target(graphic_functions, lst(
+    theme_ongo, set_annotation_fonts, clrs, 
+    prop_to_provinces, provinces_to_prop)
+  ),
   tar_target(table_functions, lst(opts_int, opts_theme)),
   tar_target(count_prop_functions, lst(provinces_to_prop, prop_to_provinces)),
 

### 2023-09-25 notebook/model-details.qmd
Create a temporary no-stripe class for gt tables
bc of https://github.com/quarto-dev/quarto-cli/issues/6945

@@
 ```{r mcmc-duration-table}
+#| classes: no-stripe
 models |> 
@@
 ```{r results-table}
+#| classes: no-stripe
 modelsummary(

### 2023-09-25 notebook/model-details.qmd
lol typo

@@
   & \beta_9\ \text{Issue[Science and technology]} + \beta_{10}\ \text{Local connections}\ + \\
-  & \beta_{11}\ \text{Time since Januay 2017} + \beta_{12}\ \text{Year registered}
+  & \beta_{11}\ \text{Time since January 2017} + \beta_{12}\ \text{Year registered}
   \end{aligned}}\\[8pt]

### 2023-09-25 manuscript/manuscript.qmd
Move prop_to_provinces to a target
It was getting repetitive
Add new structure skeleton + TODOs for assignments

@@
 short-title: "China's ONGO Law and International Civil Society"
-date: "2023-08-22"
+date: "2023-09-25"
 author:
@@
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+```
 
-prop_to_provinces <- function(x, lower = 1, upper = 32) {
-  (x * (upper - lower)) + lower
-}
-```
+# Introduction
 
@@
 
+# Legal background
+
+TODO: Andrew/Meng - overview of ONGO law and multiple pathways - TAs vs. ROs - take lots of the stuff from the introduction and move it here
+
+TODO: Andrew - image of TA/RO pathways
+
 # Theoretical background and expectations
+
+TODO: Andrew: This 2017 law fits with a broader global phenomenon of closing civic space… General crackdown stuff + China crackdown stuff + our addition
 
@@
 
+## Closing space in China
+
+TODO: Meng - China crackdown lit
+
 ## Empirical expectations
+
+Main structure for these expectations + our analysis:
+
+- Stats + case study: **Flexibility**
+- Stats + case study: **Contentiousness**
+- Case study: **Relationship with PSU and government** (stats/descriptive bc lots of chambers of commerce
 
@@
 
-## Multilevel Bayesian model
+## Modeling approach
 
@@
 
+# Flexibility, contentiousness, and government relationships: The cases of Greenpeace and The Nature Conservancy
+
+TODO: Meng - TA vs. RO, exploring main mechanisms of flexibility, contentiousness, and relationships
+
 # Discussion and conclusion
+
+TODO: Andrew: Not fully exploring the TA thing here - that's in another paper
 

### 2023-09-26 R/funs_graphics.R
Bigger caption

@@ -11,7 +11,7 @@ theme_ongo <- function(base_size = 11, base_family = "IBM Plex Sans Condensed", 
           title = element_text(size = rel(1), family = "IBM Plex Sans Condensed", face = "bold"),
           plot.subtitle = element_text(size = rel(0.8),
                                        family = "IBM Plex Sans Condensed", face = "plain"),
-          plot.caption = element_text(margin = margin(t = 10), size = rel(0.6),
+          plot.caption = element_text(margin = margin(t = 10), size = rel(0.75),
                                       family = "IBM Plex Sans Condensed", face = "plain"),
           panel.border = element_rect(color = "grey50", fill = NA, linewidth = 0.15),
           panel.spacing = unit(1, "lines"),

### 2023-09-26 manuscript/manuscript.qmd
Better math

@@
 
-::: column-page-inset-right
+:::{.column-page-inset}
 $$
 \begin{aligned}
-\text{Count of provinces}\ \sim&\ \operatorname{Ordered\,Beta}(\mu_{i_j}, \phi_y, k_{0_y}, k_{1_y}) & \text{Registered provinces for INGO $i$ in province $j$}\\[8pt]
-\mu_{i_j} =&\ (\beta_0 + b_{0_j}) + \beta_1\ \text{Issue area}\ + & \text{Average outcome}\\
-&\ \beta_2\ \text{Local connections}\ + \\
-&\ \beta_3\ \text{Years since law took effect} \\
-b_{0_j} =&\ \mathcal{N}(0, \sigma_0) & \text{Random province offsets} \\[8pt]
-\beta_0\ \sim&\ \operatorname{Student\,t}(\nu = 3, \mu = 0, \sigma = 2.5) & \text{Prior for global intercept} \\
-\beta_{1..3}\ \sim&\ \mathcal{N}(0, 5) & \text{Prior for global coefficients} \\
-\sigma_0\ \sim&\ \operatorname{Student\,t}(3, 0, 2.5) & \text{Prior for between-province variability} \\
-\phi_y\ \sim&\ \operatorname{Exponential}(1 / 100) & \text{Prior for within-province variability} \\
-k_{0_y}, k_{1_y}\ \sim&\ \operatorname{Dirichlet}(1, 1, 1) & \text{Prior for 0–continuous and continuous–1 cutpoints} \\
+&\ \textbf{Registered provinces for INGO } i \\
+\text{Count of provinces}\ \sim&\ \operatorname{Ordered\,Beta}(\mu_i, \phi_y, k_{1_y}, k_{2_y}) \\[8pt]
+&\ \textbf{Model of outcome average} \\
+% Put the huge equation in a nested \begin{aligned}[t] environment so that 
+% \mathrlap{} can go around it so that the annotations in the priors can be 
+% aligned closer to the math
+\mu_i =&\ 
+  \mathrlap{\begin{aligned}[t]
+  & \beta_0 + \beta_1\ \text{Issue[Arts and culture]} + \beta_2\ \text{Issue[Education]}\ +\\
+  & \beta_3\ \text{Issue[Industry association]} + \beta_4\ \text{Issue[Economy and trade]}\ + \\
+  & \beta_5\ \text{Issue[Charity and humanitarian]} + \beta_6\ \text{Issue[General]}\ + \\
+  & \beta_7\ \text{Issue[Health]} + \beta_8\ \text{Issue[Environment]}\ + \\
+  & \beta_9\ \text{Issue[Science and technology]} + \beta_{10}\ \text{Local connections}\ + \\
+  & \beta_{11}\ \text{Time since January 2017} + \beta_{12}\ \text{Year registered}
+  \end{aligned}}\\[8pt]
+&\ \textbf{Priors} \\
+\beta_0\ \sim&\ \operatorname{Student\,t}(\nu = 3, \mu = 0, \sigma = 2.5) && \text{Intercept} \\
+\beta_{1..12}\ \sim&\ \mathcal{N}(0, 5) && \text{Coefficients} \\
+\phi_y\ \sim&\ \operatorname{Exponential}(1 / 100) && \text{Variability in province count} \\
+k_{1_y}, k_{2_y}\ \sim&\ \operatorname{Induced\,Dirichlet}(1, 1, 1), && \text{0–continuous and continuous–1 cutpoints} \\
+&\ \quad \text{or } \bigl[P(\alpha_1), P(\alpha_1 + \alpha_2)\bigr] && \quad\text{(boundaries between 3 Dirichlet columns)}
 \end{aligned}

### 2023-09-26 manuscript/manuscript.qmd
Better fig-issue-preds

@@
 
-```{r fig-issue-preds, fig.width=6, fig.height=4.5}
+```{r fig-issue-preds, fig.width=8, fig.height=6}
 #| include: true
 #| echo: false
-#| layout-ncol: 1
-#| fig-cap: "Posterior predictions from ordered Beta regression model, conditional on organization issue area."
-#| fig-subcap: 
-#|   - "Proportions of posterior predictions of INGOs working in 1 province, all 32 provinces, or somewhere in between. Distinct x-axis categories sum to 100% across the panels."
-#|   - "Distribution of the expectation of posterior predictions.
-These distributions take into account single-province and nationwide predictions and represent the overall conditional average geographic range for INGOs."
+#| column: body-outset
+#| fig-cap: "**Top**: Posterior predictions from ordered Beta regression model,
+#|   conditional on organization issue area, showing the predicted proportion of
+#|   INGOs working in 1 province, all 32 provinces, or somewhere in between. The
+#|   vertical slices of the bars depict 500 posterior samples; the fuzziness
+#|   represents the uncertainty in category boundaries. 95% credible intervals 
+#|   are shown as ranges in each category **Bottom**: Expectation (or average) of
+#|   posterior predictive distributions. These distributions take into account 
+#|   single-province and nationwide predictions and represent the *overall*
+#|   conditional average geographic range for INGOs."
 preds_issue_plot <- preds_issue |> 
@@
   group_by(issue_area_nice, draw) |> 
-  mutate(prop = count / sum(count)) |> 
-  ungroup() |> 
-  mutate(issue_area_nice = fct_reorder(issue_area_nice, prop))
+  mutate(prop = count / sum(count))
 
-# preds_issue_plot |>
-#   group_by(outcome, issue_area_nice) |>
-#   median_qi(prop)
+preds_issue_plot_order <- preds_issue_plot |> 
+  filter(outcome == "All 32 provinces") |>
+  group_by(issue_area_nice) |> 
+  summarize(median_prop = median(prop)) |> 
+  arrange(median_prop) |> 
+  mutate(issue_area_nice_labels = str_wrap(issue_area_nice, 15)) |> 
+  mutate(issue_area_nice = fct_inorder(issue_area_nice))
 
-ggplot(preds_issue_plot, aes(x = issue_area_nice, y = prop)) +
-  stat_pointinterval(color = clrs[5], .width = 0.95, fatten_point = 1) +
-  facet_wrap(vars(outcome), ncol = 1, scales = "free_y") +
-  scale_x_discrete(labels = label_wrap(10)) +
-  scale_y_continuous(labels = label_percent()) +
-  labs(x = NULL, y = "Proportion of predictions",
-       caption = "Point shows posterior median; lines show 95% credible interval") +
-  theme_ongo()
+preds_issue_text <- preds_issue_plot |> 
+  group_by(outcome, issue_area_nice) |> 
+  summarize(median_prop = median_qi(prop)) |> 
+  unnest(median_prop) |> 
+  group_by(issue_area_nice) |> 
+  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
+  mutate(y_plot = 1 - y_plot) |> 
+  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
+  mutate(prop_ci_nice = glue::glue(
+    "{ymin}–{ymax}",
+    ymin = label_number(accuracy = 1, scale = 100)(ymin),
+    ymax = label_percent(accuracy = 1)(ymax)
+  )) |> 
+  mutate(issue_area_nice = factor(
+    issue_area_nice, 
+    levels = preds_issue_plot_order$issue_area_nice,
+    labels = preds_issue_plot_order$issue_area_nice_labels
+  ))
 
-epreds_issue |> 
+p1 <- preds_issue_plot |> 
+  mutate(issue_area_nice = factor(
+    issue_area_nice, 
+    levels = preds_issue_plot_order$issue_area_nice,
+    labels = preds_issue_plot_order$issue_area_nice_labels
+  )) |> 
+  ggplot(aes(x = draw, y = prop)) +
+  geom_col(aes(fill = outcome), position = "stack", linewidth = 0, width = 1) +
+  geom_text(
+    data = preds_issue_text,
+    aes(x = 250, y = y_plot, label = prop_ci_nice),
+    size = 3, fontface = "bold", color = "white"
+  ) +
+  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
+  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
+  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
+  facet_wrap(vars(issue_area_nice), strip.position = "bottom", nrow = 1) +
+  labs(
+    x = NULL, y = "Proportion of predictions", fill = NULL,
+    title = "Overall expected proportion of type of geographic reach across issue area",
+    subtitle = "Posterior predictions of outcome categories"
+  ) +
+  theme_ongo() +
+  theme(
+    panel.grid.major = element_blank(),
+    panel.border = element_blank(),
+    panel.spacing = unit(5, "pt"),
+    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
+  )
+
+p2 <- epreds_issue |>
   left_join(issue_indicator_lookup, by = join_by(issue_area)) |>
-  mutate(issue_area_nice = fct_reorder(issue_area_nice, .epred)) |> 
-  ggplot(aes(x = .epred, y = issue_area_nice)) +
-  stat_halfeye(fill = clrs[5], .width = c(0.8, 0.95)) +
-  scale_x_continuous(labels = label_percent(),
-                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
+  mutate(issue_area_nice = factor(
+    issue_area_nice,
+    levels = preds_issue_plot_order$issue_area_nice,
+    labels = preds_issue_plot_order$issue_area_nice_labels
+  )) |>
+  ggplot(aes(x = issue_area_nice, y = .epred)) +
+  stat_halfeye(fill = clrs[6], color = clrs[8]) +
+  scale_x_discrete(labels = NULL) +
+  scale_y_continuous(
+    labels = label_percent(),
+    sec.axis = sec_axis(
+      trans = ~ prop_to_provinces(.),
       name = "Expected provinces",
-                                         breaks = seq(8, 32, 4))) +
+      breaks = seq(2, 32, 6)
+    )
+  ) +
+  facet_wrap(vars(issue_area_nice), strip.position = "bottom", nrow = 1, scales = "free_x") +
   guides(fill = "none") +
-  labs(x = "Expected proportion of provinces", y = NULL,
-       caption = "Point shows posterior median; lines show 80% and 95% credible intervals") +
+  labs(
+    x = NULL, y = "Proportion of provinces",
+    title = "Overall expected proportion of provinces",
+    subtitle = "Expectation of posterior predictions"
+  ) +
   theme_ongo() +
-  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
+  theme(
+    panel.grid.major.x = element_blank(),
+    axis.ticks.y.right = element_line(linewidth = 0.25, color = "grey50"),
+    axis.title.y.right = element_text(hjust = 0),
+    panel.border = element_blank(),
+    panel.spacing = unit(5, "pt"),
+    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
+  )
+
+(p1 / plot_spacer() / p2) +
+  plot_layout(heights = c(0.65, 0.02, 0.33))
 ```

### 2023-09-26 manuscript/manuscript.qmd
Tweaks to fig-issue-preds

@@
   )) |>
-  ggplot(aes(x = issue_area_nice, y = .epred)) +
+  ggplot(aes(x = issue_area_nice, y = prop_to_provinces(.epred))) +
   stat_halfeye(fill = clrs[6], color = clrs[8]) +
@@
   scale_y_continuous(
-    labels = label_percent(),
+    breaks = seq(0, 32, 8),
     sec.axis = sec_axis(
-      trans = ~ prop_to_provinces(.),
-      name = "Expected provinces",
-      breaks = seq(2, 32, 6)
+      trans = ~ provinces_to_prop(.),
+      name = "Proportion of provinces",
+      breaks = seq(0, 1, 0.25),
+      labels = label_percent()
     )
@@
   labs(
-    x = NULL, y = "Proportion of provinces",
-    title = "Overall expected proportion of provinces",
+    x = NULL, y = "Expected provinces",
+    title = "Overall expected count of provinces",
     subtitle = "Expectation of posterior predictions"
@@
     panel.grid.major.x = element_blank(),
-    axis.ticks.y.right = element_line(linewidth = 0.25, color = "grey50"),
-    axis.title.y.right = element_text(hjust = 0),
     panel.border = element_blank(),

### 2023-09-26 R/funs_graphics.R

@@ -23,6 +23,7 @@ theme_ongo <- function(base_size = 11, base_family = "IBM Plex Sans Condensed", 
                                     family = "IBM Plex Sans Condensed", face = "bold"),
           axis.title.x = element_text(hjust = 0, margin = margin(t = 10)),
           axis.title.y = element_text(hjust = 1, margin = margin(r = 10)),
+          axis.title.y.right = element_text(hjust = 0, margin = margin(l = 10)),
           legend.position = "bottom",
           legend.title = element_text(size = rel(0.7), vjust = 0.5,
                                       family = "IBM Plex Sans Condensed", face = "plain"),

### 2023-09-26 manuscript/manuscript.qmd
Add updated local connections plot

--- 2023-09-26 manuscript/manuscript.qmd
@@
 
-```{r fig-issue-preds, fig.width=6, fig.height=4.5}
+```{r fig-issue-preds, fig.width=8, fig.height=6}
 #| include: true
 #| echo: false
-#| layout-ncol: 1
-#| fig-cap: "Posterior predictions from ordered Beta regression model, conditional on organization issue area."
-#| fig-subcap: 
-#|   - "Proportions of posterior predictions of INGOs working in 1 province, all 32 provinces, or somewhere in between. Distinct x-axis categories sum to 100% across the panels."
-#|   - "Distribution of the expectation of posterior predictions.
-These distributions take into account single-province and nationwide predictions and represent the overall conditional average geographic range for INGOs."
+#| column: body-outset
+#| fig-cap: "*Top*: Posterior predictions from ordered Beta regression model,
+#|   conditional on organization issue area, showing the predicted proportion of
+#|   INGOs working in 1 province, all 32 provinces, or somewhere in between. The
+#|   vertical slices of the bars depict 500 posterior samples; the fuzziness
+#|   represents the uncertainty in category boundaries. 95% credible intervals 
+#|   are shown as ranges in each category. *Bottom*: Expectation (or average) of
+#|   posterior predictive distributions. These distributions take into account 
+#|   single-province and nationwide predictions and represent the *overall*
+#|   conditional average geographic range for INGOs. Points show posterior 
+#|   median; lines show 80% and 95% credible intervals."
 preds_issue_plot <- preds_issue |> 
@@
   group_by(issue_area_nice, draw) |> 
-  mutate(prop = count / sum(count)) |> 
-  ungroup() |> 
-  mutate(issue_area_nice = fct_reorder(issue_area_nice, prop))
+  mutate(prop = count / sum(count))
 
-# preds_issue_plot |>
-#   group_by(outcome, issue_area_nice) |>
-#   median_qi(prop)
+preds_issue_plot_order <- preds_issue_plot |> 
+  filter(outcome == "All 32 provinces") |>
+  group_by(issue_area_nice) |> 
+  summarize(median_prop = median(prop)) |> 
+  arrange(median_prop) |> 
+  mutate(issue_area_nice_labels = str_wrap(issue_area_nice, 15)) |> 
+  mutate(issue_area_nice = fct_inorder(issue_area_nice))
 
-ggplot(preds_issue_plot, aes(x = issue_area_nice, y = prop)) +
-  stat_pointinterval(color = clrs[5], .width = 0.95, fatten_point = 1) +
-  facet_wrap(vars(outcome), ncol = 1, scales = "free_y") +
-  scale_x_discrete(labels = label_wrap(10)) +
-  scale_y_continuous(labels = label_percent()) +
-  labs(x = NULL, y = "Proportion of predictions",
-       caption = "Point shows posterior median; lines show 95% credible interval") +
-  theme_ongo()
+preds_issue_text <- preds_issue_plot |> 
+  group_by(outcome, issue_area_nice) |> 
+  summarize(median_prop = median_qi(prop)) |> 
+  unnest(median_prop) |> 
+  group_by(issue_area_nice) |> 
+  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
+  mutate(y_plot = 1 - y_plot) |> 
+  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
+  mutate(prop_ci_nice = glue::glue(
+    "{ymin}–{ymax}",
+    ymin = label_number(accuracy = 1, scale = 100)(ymin),
+    ymax = label_percent(accuracy = 1)(ymax)
+  )) |> 
+  mutate(issue_area_nice = factor(
+    issue_area_nice, 
+    levels = preds_issue_plot_order$issue_area_nice,
+    labels = preds_issue_plot_order$issue_area_nice_labels
+  ))
 
-epreds_issue |> 
+p1 <- preds_issue_plot |> 
+  mutate(issue_area_nice = factor(
+    issue_area_nice, 
+    levels = preds_issue_plot_order$issue_area_nice,
+    labels = preds_issue_plot_order$issue_area_nice_labels
+  )) |> 
+  ggplot(aes(x = draw, y = prop)) +
+  geom_col(aes(fill = outcome), position = "stack", linewidth = 0, width = 1) +
+  geom_text(
+    data = preds_issue_text,
+    aes(x = 250, y = y_plot, label = prop_ci_nice),
+    size = 3, fontface = "bold", color = "white"
+  ) +
+  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
+  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
+  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
+  facet_wrap(vars(issue_area_nice), strip.position = "bottom", nrow = 1) +
+  labs(
+    x = NULL, y = "Proportion of predictions", fill = NULL,
+    title = "Expected proportion of type of geographic reach across issue area",
+    subtitle = "Posterior predictions of outcome categories"
+  ) +
+  theme_ongo() +
+  theme(
+    panel.grid.major = element_blank(),
+    panel.border = element_blank(),
+    panel.spacing = unit(5, "pt"),
+    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
+  )
+
+p2 <- epreds_issue |>
   left_join(issue_indicator_lookup, by = join_by(issue_area)) |>
-  mutate(issue_area_nice = fct_reorder(issue_area_nice, .epred)) |> 
-  ggplot(aes(x = .epred, y = issue_area_nice)) +
-  stat_halfeye(fill = clrs[5], .width = c(0.8, 0.95)) +
-  scale_x_continuous(labels = label_percent(),
-                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
-                                         name = "Expected provinces",
-                                         breaks = seq(8, 32, 4))) +
+  mutate(issue_area_nice = factor(
+    issue_area_nice,
+    levels = preds_issue_plot_order$issue_area_nice,
+    labels = preds_issue_plot_order$issue_area_nice_labels
+  )) |>
+  ggplot(aes(x = issue_area_nice, y = prop_to_provinces(.epred))) +
+  stat_halfeye(fill = clrs[6], color = clrs[8]) +
+  scale_x_discrete(labels = NULL) +
+  scale_y_continuous(
+    breaks = seq(0, 32, 8),
+    sec.axis = sec_axis(
+      trans = ~ provinces_to_prop(.),
+      name = "Proportion of provinces",
+      breaks = seq(0, 1, 0.25),
+      labels = label_percent()
+    )
+  ) +
+  facet_wrap(vars(issue_area_nice), strip.position = "bottom", nrow = 1, scales = "free_x") +
   guides(fill = "none") +
-  labs(x = "Expected proportion of provinces", y = NULL,
-       caption = "Point shows posterior median; lines show 80% and 95% credible intervals") +
+  labs(
+    x = NULL, y = "Expected provinces",
+    title = "Expected count of provinces",
+    subtitle = "Expectation of posterior predictions"
+  ) +
+  coord_cartesian(ylim = c(1, 32)) +
   theme_ongo() +
-  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
+  theme(
+    panel.grid.major.x = element_blank(),
+    panel.border = element_blank(),
+    panel.spacing = unit(5, "pt"),
+    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
+  )
+
+(p1 / plot_spacer() / p2) +
+  plot_layout(heights = c(0.65, 0.02, 0.33))
 ```
@@
 
-```{r fig-local-preds, fig.width=6, fig.height=2.5}
+```{r fig-local-preds, fig.width=8, fig.height=4}
 #| include: true
 #| echo: false
-#| layout-ncol: 1
-#| fig-cap: "Posterior predictions from ordered Beta regression model, conditional on having local connections."
-#| fig-subcap: 
-#|   - "Proportions of posterior predictions of INGOs working in 1 province, all 32 provinces, or somewhere in between. Distinct x-axis categories sum to 100% across the panels."
-#|   - "Distribution of the expectation of posterior predictions.
-These distributions take into account single-province and nationwide predictions and represent the overall conditional average geographic range for INGOs."
+#| fig-cap: "Posterior predictions from ordered Beta regression model, 
+#|   conditional on having local connections. *Top*: Predicted proportion of 
+#|   INGOs working in 1 province, all 32 provinces, or somewhere in between. 
+#|   The vertical slices of the bars depict 500 posterior samples; the fuzziness 
+#|   represents the uncertainty in category boundaries. 95% credible intervals 
+#|   are shown as ranges in each category. *Bottom*: Expectation (or average) of 
+#|   posterior predictive distributions. These distributions take into account 
+#|   single-province and nationwide predictions and represent the *overall* 
+#|   conditional average geographic range for INGOs. Points show posterior 
+#|   median; lines show 80% and 95% credible intervals."
 preds_local_plot <- preds_local |> 
@@
 
-# preds_local_plot |>
-#   group_by(outcome, local_connect) |>
-#   median_qi(prop)
-#
-# epreds_local |>
-#   mutate(.epred = prop_to_provinces(.epred)) |> 
-#   group_by(local_connect) |>
-#   median_qi(.epred)
+preds_local_text <- preds_local_plot |> 
+  group_by(outcome, local_connect) |> 
+  summarize(median_prop = median_qi(prop)) |> 
+  unnest(median_prop) |> 
+  group_by(local_connect) |> 
+  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
+  mutate(y_plot = 1 - y_plot) |> 
+  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
+  mutate(prop_ci_nice = glue::glue(
+    "{ymin}–{ymax}",
+    ymin = label_number(accuracy = 1, scale = 100)(ymin),
+    ymax = label_percent(accuracy = 1)(ymax)
+  ))
 
-ggplot(preds_local_plot, aes(x = local_connect, y = prop)) +
-  stat_pointinterval(color = clrs[2], .width = c(0.95), fatten_point = 1) +
-  facet_wrap(vars(outcome)) +
-  scale_x_discrete(labels = label_wrap(10)) +
-  scale_y_continuous(labels = label_percent()) +
-  labs(x = NULL, y = "Proportion of predictions",
-       caption = "Point shows posterior median; lines show 95% credible interval") +
-  theme_ongo()
+p1 <- preds_local_plot |> 
+  ggplot(aes(x = draw, y = prop)) +
+  geom_col(aes(fill = outcome), position = position_stack(), linewidth = 0, width = 1) +
+  geom_text(
+    data = preds_local_text,
+    aes(x = 250, y = y_plot, label = prop_ci_nice),
+    size = 3, fontface = "bold", color = "white"
+  ) +
+  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
+  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
+  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
+  facet_wrap(vars(local_connect), strip.position = "bottom", nrow = 1) +
+  labs(
+    x = NULL, y = "Proportion of predictions", fill = NULL,
+    title = "Expected proportion of type of geographic\nreach across local connections",
+    subtitle = "Posterior predictions of outcome categories"
+  ) +
+  theme_ongo() +
+  theme(
+    panel.grid.major = element_blank(),
+    panel.border = element_blank(),
+    panel.spacing = unit(5, "pt"),
+    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
+  )
 
-epreds_local |> 
+p2 <- epreds_local |>
   mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |>
-  ggplot(aes(x = .epred, y = local_connect)) +
-  stat_halfeye(fill = clrs[2], .width = c(0.8, 0.95)) +
-  scale_x_continuous(labels = label_percent(),
-                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
-                                         name = "Expected provinces",
-                                         breaks = seq(8, 32, 4))) +
+  ggplot(aes(x = local_connect, y = prop_to_provinces(.epred))) +
+  stat_halfeye(fill = clrs[6], color = clrs[8]) +
+  scale_x_discrete(labels = NULL) +
+  scale_y_continuous(
+    breaks = seq(0, 32, 8),
+    sec.axis = sec_axis(
+      trans = ~ provinces_to_prop(.),
+      name = "Proportion of provinces",
+      breaks = seq(0, 1, 0.25),
+      labels = label_percent()
+    )
+  ) +
+  facet_wrap(vars(local_connect), strip.position = "bottom", nrow = 1, scales = "free_x") +
   guides(fill = "none") +
-  labs(x = "Expected proportion of provinces", y = NULL,
-       caption = "Point shows posterior median; lines show 80% and 95% credible intervals") +
+  labs(
+    x = NULL, y = "Expected provinces",
+    title = "Expected count of provinces",
+    subtitle = "Expectation of posterior predictions"
+  ) +
+  coord_cartesian(ylim = c(1, 32)) +
   theme_ongo() +
-  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
+  theme(
+    panel.grid.major.x = element_blank(),
+    panel.border = element_blank(),
+    panel.spacing = unit(5, "pt"),
+    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
+  )
+
+(p1 | p2) +
+  plot_layout(widths = c(0.6, 0.4))
 ```

### 2023-09-27 notebook/model-details.qmd
Better math
Re-add model with interaction

@@
 tar_load(ongo)
-tar_load(c(m_full_ordbeta))
+tar_load(c(m_full_ordbeta, m_full_ordbeta_interaction))
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
@@
 $$
-\begin{align}
+\begin{aligned}
 &\ \textbf{Registered provinces for INGO } i \\
@@
 &\ \quad \text{or } \bigl[P(\alpha_1), P(\alpha_1 + \alpha_2)\bigr] && \quad\text{(boundaries between 3 Dirichlet columns)}
-\end{align}
+\end{aligned}
 $$
@@
   "Full model", m_full_ordbeta,
+  "Model with local connections × time interaction", m_full_ordbeta_interaction
 ) |> 
@@
 modelsummary(
-  m_full_ordbeta,
+  list(m_full_ordbeta, m_full_ordbeta_interaction),
   statistic = "[{conf.low}, {conf.high}]",

### 2023-09-27 R/funs_models.R

@@ -26,6 +26,30 @@ f_full_ordbeta <- function(data) {
   return(model)
 }
 
+f_full_ordbeta_interaction <- function(data) {
+  library(ordbetareg)
+  
+  BAYES_SEED <- 121171  # From random.org
+  
+  model <- ordbetareg(
+    bf(
+      province_count ~ 
+        issue_arts_and_culture + issue_education +
+        issue_industry_association + issue_economy_and_trade + 
+        issue_charity_and_humanitarian + issue_general + issue_health +
+        issue_environment + issue_science_and_technology +
+        (local_connect * years_since_law) + year_registered_cat
+    ), 
+    data = data,
+    true_bounds = c(1, 32),
+    coef_prior_mean = 0,
+    coef_prior_SD = 2.5,
+    phi_prior = 1/100,
+    seed = BAYES_SEED)
+  
+  return(model)
+}
+
 f_full_zoib <- function(data) {
   BAYES_SEED <- 102819  # From random.org
   
@@ -142,7 +166,8 @@ f_epreds_local <- function(model, ndraws = 1000) {
 f_epreds_timing <- function(model, ndraws = 1000) {
   model |> 
     epred_draws(datagrid(model = model, years_since_law = 0:5), 
-                ndraws = ndraws, seed = 58214) |> 
+                ndraws = 1000, seed = 58214) |> 
+    mutate(years_since_law = 2017 + years_since_law) |> 
     ungroup()
 }
 
@@ -151,5 +176,6 @@ f_epreds_timing_local <- function(model, ndraws = 1000) {
     epred_draws(datagrid(model = model, 
                          local_connect = unique, years_since_law = 0:5), 
                 ndraws = ndraws, seed = 58214) |> 
+    mutate(years_since_law = 2017 + years_since_law) |> 
     ungroup()
 }

### 2023-09-27 _targets.R

@@ -66,6 +66,7 @@ list(
   
   ## Models ----
   tar_target(m_full_ordbeta, f_full_ordbeta(ongo_wide)),
+  tar_target(m_full_ordbeta_interaction, f_full_ordbeta_interaction(ongo_wide)),
   tar_target(m_full_zoib, f_full_zoib(ongo_wide)),
 
   ## Posterior predictions ----
@@ -76,7 +77,7 @@ list(
   tar_target(epreds_issue, f_epreds_issue(m_full_ordbeta, issue_indicator_lookup)),
   tar_target(epreds_local, f_epreds_local(m_full_ordbeta)),
   tar_target(epreds_timing, f_epreds_timing(m_full_ordbeta)),
-  tar_target(epreds_timing_local, f_epreds_timing_local(m_full_ordbeta)),
+  tar_target(epreds_timing_local, f_epreds_timing_local(m_full_ordbeta_interaction)),
   
   ## Analysis notebook ----
   tar_quarto(manuscript_nice, path = "manuscript", quiet = FALSE, profile = "nice"),

### 2023-09-27 manuscript/manuscript.qmd
Update timing plots

@@
   labs(
-    x = NULL, y = "Proportion of predictions", fill = NULL,
-    title = "Expected proportion of type of geographic reach across issue area",
+    x = NULL, y = "Predicted probability of geographic reach", fill = NULL,
+    title = "Predicted proportion of type of geographic reach across issue area",
     subtitle = "Posterior predictions of outcome categories"
@@
   labs(
-    x = NULL, y = "Proportion of predictions", fill = NULL,
-    title = "Expected proportion of type of geographic\nreach across local connections",
+    x = NULL, y = "Predicted probability of geographic reach", fill = NULL,
+    title = "Predicted proportion of type of\ngeographic reach across local connections",
     subtitle = "Posterior predictions of outcome categories"
@@
 
-```{r fig-timing-preds, fig.width=6, fig.height=3}
+```{r fig-timing-preds, fig.width=8, fig.height=4}
 #| include: true
 #| echo: false
-#| layout-ncol: 1
-#| fig-cap: "Posterior predictions from ordered Beta regression model, conditional on time since registration."
-#| fig-subcap: 
-#|   - "Proportions of posterior predictions of INGOs working in 1 province, all 32 provinces, or somewhere in between. Distinct x-axis values sum to 100% across the panels."
-#|   - "Distribution of the expectation of posterior predictions.
-These distributions take into account single-province and nationwide predictions and represent the overall conditional average geographic range for INGOs."
+#| fig-cap: "Posterior predictions from ordered Beta regression model, 
+#|   conditional on time since law took effect in January 2017. *Top*: Predicted 
+#|   proportion of INGOs working in 1 province, all 32 provinces, or somewhere 
+#|   in between. Filled areas depict 50 posterior samples of the outcome category 
+#|   probabilities, so the fuzziness represents the uncertainty in category 
+#|   boundaries. *Bottom*: Expectation (or average) of posterior predictive 
+#|   distributions. This distribution takes into account single-province and 
+#|   nationwide predictions and represents the *overall* conditional average 
+#|   geographic range for INGOs over time. Shaded regions show the 50%, 80%, 
+#|   and 95% credible intervals."
 preds_timing_plot <- preds_timing |> 
@@
   mutate(outcome = case_when(
-    .prediction == 0 ~ "1 province",
-    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
-    .prediction == 1 ~ "32 provinces"
+    .prediction == 0 ~ "Only 1 province",
+    .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
+    .prediction == 1 ~ "All 32 provinces",
+    .ptype = factor(
+      levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"), 
+      ordered = TRUE)
   )) |> 
+  mutate(years_since_law = 2017 + years_since_law) |> 
   group_by(outcome, years_since_law, draw) |>
   summarize(count = n()) |> 
-  group_by(years_since_law, draw) |> 
-  mutate(prop = count / sum(count))
+  group_by(years_since_law) |> 
+  mutate(prop = count / sum(count) * 100)
 
-# preds_timing_plot |>
-#   group_by(outcome, years_since_law) |>
-#   median_qi(prop)
-# 
-# epreds_timing |>
-#   mutate(.epred = prop_to_provinces(.epred)) |>
-#   group_by(years_since_law) |>
-#   median_qi(.epred)
+preds_timing_text <- preds_timing_plot |> 
+  filter(years_since_law == 2017.2) |> 
+  group_by(outcome) |> 
+  summarize(median_prop = median_qi(prop)) |> 
+  unnest(median_prop) |> 
+  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
+  mutate(y_plot = 1 - y_plot) |> 
+  mutate(years_since_law = 2017.2)
 
-ggplot(preds_timing_plot, aes(x = years_since_law, y = prop)) +
-  stat_lineribbon(.width = c(0.5, 0.8, 0.95), 
-                  alpha = 0.35, fill = clrs[7], color = clrs[7]) +
-  facet_wrap(vars(outcome), nrow = 1) +
-  scale_y_continuous(labels = label_percent()) +
-  labs(x = "Years since law took effect (2017)", 
-       y = "Proportion of predictions",
-       caption = "Shaded regions show the 50%, 80%, and 95% credible intervals") +
+layers <- preds_timing_plot |> 
+  filter(draw <= 50) |> 
+  split(~ draw) |> 
+  lapply(\(x) {
+    geom_area(
+      data = x,
+      aes(y = prop, fill = outcome),
+      alpha = 0.1
+    )
+  })
+
+p1 <- ggplot(preds_timing_plot, aes(x = years_since_law)) +
+  layers +
+  geom_text(
+    data = preds_timing_text, 
+    aes(y = y_plot, label = outcome),
+    color = "white",
+    hjust = 0, fontface = "bold", size = 3, show.legend = FALSE
+  ) +
+  scale_x_continuous(expand = expansion(mult = 0.02)) +
+  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
+  scale_color_manual(values = colorspace::darken(clrs[c(3, 5, 7)], 0.1)) +
+  scale_fill_manual(values = colorspace::lighten(clrs[c(3, 5, 7)], 0)) +
+  labs(
+    x = NULL, y = "Predicted probability of geographic reach", fill = NULL,
+    title = "Predicted proportion of type of \ngeographic reach since January 2017",
+    subtitle = "Posterior predictions of outcome categories"
+  ) +
+  guides(fill = "none") +
+  theme_ongo() +
+  theme(
+    panel.grid.major = element_blank()
+  )
+
+p2 <- epreds_timing |>
+  ggplot(aes(x = years_since_law, y = prop_to_provinces(.epred))) +
+  stat_lineribbon(
+    .width = c(0.5, 0.8, 0.95),
+    alpha = 0.35, fill = clrs[6], color = clrs[6]
+  ) +
+  scale_y_continuous(
+    breaks = seq(0, 32, 8),
+    sec.axis = sec_axis(
+      trans = ~ provinces_to_prop(.),
+      name = "Proportion of provinces",
+      breaks = seq(0, 1, 0.25),
+      labels = label_percent()
+    )
+  ) +
+  labs(
+    x = NULL, y = "Expected provinces",
+    title = "Expected count of provinces",
+    subtitle = "Expectation of posterior predictions"
+  ) +
+  coord_cartesian(ylim = c(1, 32)) +
   theme_ongo()
 
-epreds_timing |> 
-  ggplot(aes(x = years_since_law, y = .epred)) +
-  stat_lineribbon(.width = c(0.5, 0.8, 0.95), 
-                  alpha = 0.35, fill = clrs[7], color = clrs[7]) +
-  scale_y_continuous(labels = label_percent(),
-                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
-                                         name = "Expected provinces",
-                                         breaks = seq(15, 27, 3))) +
-  guides(fill = "none") +
-  labs(x = "Years since law took effect (2017)", y = "Expected proportion of provinces",
-       caption = "Shaded regions show the 50%, 80%, and 95% credible intervals") +
-  theme_ongo() +
-  theme(axis.title.y.right = element_text(hjust = 1, margin = margin(l = 10), angle = 90),
-        axis.ticks.y.right = element_line(linewidth = 0.25, color = "grey50"))
+p1 | p2
 ```
@@
 
-```{r fig-timing-local, fig.width=6, fig.height=3}
+```{r fig-timing-local, fig.width=6, fig.height=3, out.width="80%"}
 #| include: true
 #| echo: false
-#| fig-cap: "Distribution of the expectation of posterior predictions across both time and local connections.
-These distributions take into account single-province and nationwide predictions and represent the overall conditional average geographic range for INGOs."
+#| fig-cap: "Expectation (or average) of posterior predictive distributions 
+#|   from model with interaction between local connections and time since 
+#|   January 2017. These predictions take into account single-province and 
+#|   nationwide predictions and represent the overall conditional average 
+#|   geographic range for INGOs over time across, conditional on local 
+#|   connections. Shaded regions show the 50%, 80%, and 95% credible intervals"
 epreds_timing_local |>
   mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |>
-  ggplot(aes(x = years_since_law, y = .epred)) +
-  stat_lineribbon(.width = c(0.5, 0.8, 0.95), 
-                  alpha = 0.35, fill = clrs[7], color = clrs[7]) +
-  scale_y_continuous(labels = label_percent(),
-                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
-                                         name = "Expected provinces",
-                                         breaks = seq(3, 27, 4))) +
+  ggplot(aes(x = years_since_law, y = prop_to_provinces(.epred))) +
+  stat_lineribbon(
+    .width = c(0.5, 0.8, 0.95),
+    alpha = 0.35, fill = clrs[6], color = clrs[6]
+  ) +
+  scale_y_continuous(
+    breaks = seq(0, 32, 8),
+    sec.axis = sec_axis(
+      trans = ~ provinces_to_prop(.),
+      name = "Proportion of provinces",
+      breaks = seq(0, 1, 0.25),
+      labels = label_percent()
+    )
+  ) +
   guides(fill = "none") +
-  labs(x = "Years since law took effect (2017)", y = "Expected proportion of provinces",
-       caption = "Shaded regions show the 50%, 80%, and 95% credible intervals") +
+  labs(
+    x = NULL, y = "Expected provinces",
+    title = "Expected count of provinces across local connections",
+    subtitle = "Expectation of posterior predictions"
+  ) +
+  coord_cartesian(ylim = c(1, 32)) +
   facet_wrap(vars(local_connect)) +
-  theme_ongo() +
-  theme(axis.title.y.right = element_text(hjust = 1, margin = margin(l = 10), angle = 90),
-        axis.ticks.y.right = element_line(linewidth = 0.25, color = "grey50"))
+  theme_ongo()
 ```

### 2023-09-27 manuscript/manuscript.qmd
Add figure showing RO/TA pathways

@@
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+set_annotation_fonts()
 ```
@@
 
-TODO: Andrew - image of TA/RO pathways
+TODO: Andrew - image of TA/RO pathways @fig-ro-ta-pathways
+
+```{r fig-ro-ta-pathways, fig.width=6, fig.height=3}
+#| echo: false
+#| include: true
+#| warning: false
+#| message: false
+#| fig-cap: "Two possible pathways for international NGOs to legally work in 
+#|   China, either as formal Registered Organizations (ROs) or by undertaking 
+#|   specific Temporary Activities (TAs)"
+library(tidygraph)
+library(ggraph)
+
+ro_nodes <- tibble(
+  step = c(
+    "Find a professional supervisory unit (PSU)",
+    "Obtain PSU approval",
+    "Open organization bank accounts",
+    "Keep programming withing approved scope",
+    "Submit annual work plans (×2)",
+    "Submit annual reports (×2)"
+  ),
+  type = "Registered organization (RO)"
+)
+ro_edges <- tibble(from = 1:5, to = 2:6)
+ro_graph <- tbl_graph(nodes = ro_nodes, edges = ro_edges)
+
+ta_nodes <- tibble(
+  step = c(
+    "Find an eligible Chinese partner to file paperwork",
+    "Obtain PSU approval",
+    "Channel money through partner’s bank",
+    "Keep programming withing approved scope",
+    "Finish work within a year",
+    "Submit final project report"
+  ),
+  type = "Temporary activities (TA)"
+)
+ta_edges <- tibble(from = 1:5, to = 2:6)
+ta_graph <- tbl_graph(nodes = ta_nodes, edges = ta_edges)
+
+combined_graph <- bind_graphs(ro_graph, ta_graph)
+
+ggraph(combined_graph, layout = "tree") +
+  geom_node_label(
+    aes(x = x, y = y, label = step), 
+    size = 2.5, label.r = unit(0, units = "pt")
+  ) +
+  geom_edge_link(
+    aes(
+      start_cap = label_rect(node1.step, padding = margin(5, 5, 5, 5, "pt")),
+      end_cap = label_rect(node2.step, padding = margin(5, 5, 5, 5, "pt"))
+    ),
+    arrow = arrow(angle = 30, length = unit(6, "pt"), type = "closed"),
+    edge_linewidth = 0.25
+  ) +
+  facet_nodes(vars(type), scales = "free_x") +
+  labs(x = NULL, y = NULL) +
+  theme_ongo() +
+  theme(
+    panel.grid.major = element_blank(),
+    panel.border = element_blank(),
+    axis.text = element_blank(),
+    strip.text = element_text(hjust = 0.5)
+  )
+```
 

### 2023-09-27 manuscript/manuscript.qmd
Add initial theoretical diagram

@@
 library(marginaleffects)
+library(tidygraph)
+library(ggraph)
 library(patchwork)
@@
 #|   specific Temporary Activities (TAs)"
-library(tidygraph)
-library(ggraph)
-
 ro_nodes <- tibble(
@@
 ## Empirical expectations
+
+See @fig-theory
+
+```{r fig-theory, fig.width=6, fig.height=2}
+#| echo: false
+#| include: true
+#| warning: false
+#| message: false
+#| fig-cap: "Diagram of our theoretical framework showing three possible determinants of INGO operational flexibility: the contentiousness of the INGO's issue area, the inherent geographic scope of the INGO's operations, and the government's interest in and relationship with the INGO."
+theory_nodes <- tribble(
+  ~id, ~name, ~x, ~y, ~highlight,
+  1,   "Issue contentiousness", 1, 0, FALSE,
+  2,   "Operational flexibility", 3, 0, TRUE,
+  3,   "Local focus", 2, 1, FALSE,
+  4,   "Government relationship and interest", 2, -1, FALSE
+)
+
+theory_edges <- tribble(
+  ~from, ~to,
+  1, 2,
+  3, 1,
+  3, 2,
+  1, 4,
+  4, 2
+)
+
+theory_graph <- tbl_graph(nodes = theory_nodes, edges = theory_edges)
+
+ggraph(theory_graph, x = x, y = y) + 
+  geom_edge_link(
+    aes(
+      end_cap = label_rect(node2.name, padding = margin(10, 5, 10, 5, "pt"))
+    ),
+    arrow = arrow(angle = 30, length = unit(6, "pt"), type = "closed"),
+    edge_linewidth = 0.25
+  ) +
+  geom_node_label(
+    aes(x = x, y = y, label = name, fill = highlight), 
+    size = 3, label.r = unit(0, units = "pt"), fontface = "bold"
+  ) +
+  scale_x_continuous(expand = expansion(add = 0.3)) +
+  scale_y_continuous(expand = expansion(add = 0.2)) +
+  scale_fill_manual(values = c("white", clrs[1]), guide = "none") +
+  labs(x = NULL, y = NULL) +
+  theme_ongo() +
+  theme(
+    panel.grid.major = element_blank(),
+    panel.border = element_blank(),
+    axis.text = element_blank(),
+  )
+```
 

### 2023-11-21 manuscript/manuscript.qmd

@@
 On April 28, 2016, China passed its own set of legal restrictions on civil society with its Law of the People's Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China, or "ONGO Law," which formally took effect on January 1, 2017.
-As an authoritarian state with a growing nonprofit sector, the Chinese model of implementing restrictive laws for international NGOs (INGOs) has important implications for understanding the dynamics of how civil society laws can be used as policy tools to harness INGOs.
+The laws requires all international NGOs (INGOs) to either register representative offices (ROs) or file temporary activities to lawfully operate in mainland China.As an authoritarian state with a growing nonprofit sector, the Chinese model of implementing restrictive laws for international NGOs (INGOs) has important implications for understanding the dynamics of how civil society laws can be used as policy tools to harness INGOs.
+
+TODO: Andrew - update and coordinate the introductory paragraphs with the theoretical framing below
+
+*Meng's notes/suggestions*: to highlight the theoretical significance in the very beginning (just listing the idea pool for moment, not concise enough):
+
+ 1.
+A frequently approach to close the space of INGOs is passing restrictive laws/institutional approach.
+[@DeMattee:2019].
+To further understanding this global phenomena , China is an important case to explore the impacts such restrictive laws have on the operation of INGOs.
+Such legal restrictions can be either direct (denial of legal access/cannot register) or covert (red-tape, requiring the approval of PSUs, or the uncertainty of having to filing TAs case by case)
+
+ 2.
+*de facto* vs.
+*de jure* (incorporating the paragraph below) and differentiated treatment for more vs.
+less contentious INGOs.
+Authoritarian -> arbitrary and varied application of the law -> different *operating space*
 
@@
 By relying on representative empirical data from mainland China, our study also contributes to a growing body of research on the effects of closing civic space on INGO behavior and strategies.
+
+3.
+Laws and policies as a *policy tool* and behavioral shifit: to tame INGO to be more cooperative to government.
+The requirement of PSU and Chinese partner to re-direct INGOs to be more authority friendly.
+
+The impacts on international civil society  we examine include not only access or representation of INGOs in China, but also whether there is change of behaviors [@WuNie:2021].
+Mention the concept of *flexibility (in the sense of adjusting to change)* too?
+
+This paper explores the characteristics of all registered INGOs in China in the five years after the ONGO Law became effective and examines the association between INGO issue areas and the operational space granted to them in the country.
+Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus.
+Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018].
+INGOs vary in their ability to attract partner PSUs, and organizations that are unable to find corresponding PSUs are more limited in their geographic reach within the country.
+INGOs are authorized to operate within China on a province-by-province basis.
+Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.
+We use the number of provinces that INGOs are authorized to work in as a proxy to measure the operational space for INGOs in China based on the assumption that INGOs need to or hope to have the approval to be able to carry out their programs in a geographical scope as large as possible [@Li:2020].
+
+In this paper, we first explore existing theories of closing civic space, authoritarian regulation of civil society, and differential regulation of international vs.
+domestic NGOs.
+We then propose a set of empirical expectations for INGOs registering in China following the 2017 ONGO Law.
+We describe our data, which includes registration and organization-level details for all 633 INGOs registered between January 1, 2017 and December 31, 2021, and our descriptive and empirical approach to analyzing the data.
+We then present the findings from our data, exploring each of our empirical expectations, and conclude with a discussion of how these results connect to larger themes of the global closure of civic space.
+
+# Legal background
 
@@
 
-This paper explores the characteristics of all registered INGOs in China in the five years after the ONGO Law became effective and examines the association between INGO issue areas and the operational space granted to them in the country.
-Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus.
-Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018].
-INGOs vary in their ability to attract partner PSUs, and organizations that are unable to find corresponding PSUs are more limited in their geographic reach within the country.
-INGOs are authorized to operate within China on a province-by-province basis.
-Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.
-We use the number of provinces that INGOs are authorized to work in as a proxy to measure the operational space for INGOs in China based on the assumption that INGOs need to or hope to have the approval to be able to carry out their programs in a geographical scope as large as possible [@Li:2020].
-
-In this paper, we first explore existing theories of closing civic space, authoritarian regulation of civil society, and differential regulation of international vs.
-domestic NGOs.
-We then propose a set of empirical expectations for INGOs registering in China following the 2017 ONGO Law.
-We describe our data, which includes registration and organization-level details for all 633 INGOs registered between January 1, 2017 and December 31, 2021, and our descriptive and empirical approach to analyzing the data.
-We then present the findings from our data, exploring each of our empirical expectations, and conclude with a discussion of how these results connect to larger themes of the global closure of civic space.
-
-# Legal background
-
-TODO: Andrew/Meng - overview of ONGO law and multiple pathways - TAs vs. ROs - take lots of the stuff from the introduction and move it here
+TODO: Meng - add brief explanations of the TA/RO pathways figure and articulate the "cooperative requirements part", i.e., seeking a psu or Chinese partner
 
@@
 
+(Meng added)
+
 ## De jure vs. de facto implementation of civil society regulations
@@
 
-## Closing space in China
+## China's INGO as a policy tool 
+*note* changed the sub-title to incorporate the policy tool lense too.
 

### 2023-11-21 manuscript/manuscript.qmd
Merge my stuff with Meng's stuff

@@
 On April 28, 2016, China passed its own set of legal restrictions on civil society with its Law of the People's Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China, or "ONGO Law," which formally took effect on January 1, 2017.
-The laws requires all international NGOs (INGOs) to either register representative offices (ROs) or file temporary activities to lawfully operate in mainland China.As an authoritarian state with a growing nonprofit sector, the Chinese model of implementing restrictive laws for international NGOs (INGOs) has important implications for understanding the dynamics of how civil society laws can be used as policy tools to harness INGOs.
+The law requires all international NGOs (INGOs) to either register representative offices (ROs) or file temporary activities to lawfully operate in mainland China.As an authoritarian state with a growing nonprofit sector, the Chinese model of implementing restrictive laws for international NGOs (INGOs) has important implications for understanding the dynamics of how civil society laws can be used as policy tools to harness INGOs.
 
@@
 
+ 3.
+Laws and policies as a *policy tool* and behavioral shifit: to tame INGO to be more cooperative to government.
+The requirement of PSU and Chinese partner to re-direct INGOs to be more authority friendly.
+
+The impacts on international civil society  we examine include not only access or representation of INGOs in China, but also whether there is change of behaviors [@WuNie:2021].
+Mention the concept of *flexibility (in the sense of adjusting to change)* too?
+
 The purpose of this study is to empirically examine how the ONGO Law has influenced the population of INGOs that have successfully registered in China since 2017, and in particular how the ONGO Law has shaped the operational space allowed for INGO operations in the country.
@@
 By relying on representative empirical data from mainland China, our study also contributes to a growing body of research on the effects of closing civic space on INGO behavior and strategies.
-
-3.
-Laws and policies as a *policy tool* and behavioral shifit: to tame INGO to be more cooperative to government.
-The requirement of PSU and Chinese partner to re-direct INGOs to be more authority friendly.
-
-The impacts on international civil society  we examine include not only access or representation of INGOs in China, but also whether there is change of behaviors [@WuNie:2021].
-Mention the concept of *flexibility (in the sense of adjusting to change)* too?
 
@@
 
+In this paper, we first explore the ongoing phenomena of closing civic space and authoritarian regulation of civil society, examining how governments conceptualize the role of international civil society in their domestic politics and why governments select regulatory regimes for international NGOs.
+We then investigate how international NGOs have responded and adapted to more restrictive regulatory environments and theorize that a key component of INGO regulatory adaptation is *organizational flexibility*, or the ability to operate with greater latitude in host countries.
+We propose two key determinants of this flexibility: (1) organizational characteristics and (2) host government preferences and relationships TODO and their interplay/interaction.
+We illustrate this theory using the case of China TODO stats and case studies, mixed method, demonstrating how INGOs that address issues that align with government preferences enjoy the most organizational flexibility in the country.
+
+# Closing civic space
+
+## The global constriction of civic space
+
+## The "closing space" phenomenon
+
+Many different reasons for these restrictions and several purposes - INGOs pose a threat to regime stability, but they also provide governments with services and technical expertise.
+Civil society/CSO/NGO + host government definition - De Mattee and institutional taxonomy.
+My stuff on gatekeeping vs.
+program capture.
+
+INGO regulations are implemented and enforced differentially - difference in de jure and de facto.
+This differential enforcement is one mechanism to allow host governments to harness the aspects of INGO programming that align with their domestic policy preferences while limiting INGO behavior that could threaten regime stability.
+
+Why pass laws in the first place and why enforcement differently?
+
+@ChaudhryHeiss:2022 and the divergence in de jure and de facto regulations---the implementation doesn't have to match the written law, and often the written law can serve as a "weapon hanging on the wall that never fires" that serves as a warning to potentially uncooperative NGOs [@Kozenko:2015].
+See also [@ToeplerZimmerFrohlich:2020; @Plantan:2022]
+
+"We discuss the role of civil society organizations (CSOs) as agents of democratization and note the emergence of dual, at times apparently conflicting policy postures within authoritarian regimes (restriction and repression for some CSOs vs.
+financial support and opportunities for collaboration for others)." [@ToeplerZimmerFrohlich:2020]
+
+Also, [@Plantan:2022] finds "that I find" evidence of selective implementation that reveals which groups are seen as threatening or beneficial."
+
+The presence of de jure regulations and the strictness of their de facto enforcement are both determined by the interplay between INGO characteristics and government preferences.
+
+Contentiousness, regime stability, other reasons [see @Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016].
+
+Main idea: organizations that work on more contentious issues like human rights advocacy face stricter regulations [@Bush:2015; @ChaudhryHeiss:2021]
+
+## Closing civic space in China
+
+China provides a fascinating example of both authoritarian preferences for INGO regulations and INGO adaptations to these regulations.
+
+3.
+Laws and policies as a *policy tool* and behavioral shifit: to tame INGO to be more cooperative to government.
+The requirement of PSU and Chinese partner to re-direct INGOs to be more authority friendly.
+
+Many INGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [@Sidel:2016], though there were no clear requirements for them to have a formal legal presence in China [@Han:2011; @HolbigLang:2022; @Yin:2009].
+However, the legal form of foreign-funded company is not quite compatible with the nonprofit nature of INGOs.
+Under the Chinese legal system, enterprises are intended to be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms, including foundations, associations, and social service organizations [@Ye:2021].
+Thus, INGOs obtaining legal identity in this way have to navigate through a legal framework designed for a for-profit institutional logic, e.g, focusing on protecting investors' right to investment returns.
+
+This paper explores the characteristics of all registered INGOs in China in the five years after the ONGO Law became effective and examines the association between INGO issue areas and the operational space granted to them in the country.
+Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus.
+Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018].
+INGOs vary in their ability to attract partner PSUs, and organizations that are unable to find corresponding PSUs are more limited in their geographic reach within the country.
+INGOs are authorized to operate within China on a province-by-province basis.
+Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.
+We use the number of provinces that INGOs are authorized to work in as a proxy to measure the operational space for INGOs in China based on the assumption that INGOs need to or hope to have the approval to be able to carry out their programs in a geographical scope as large as possible [@Li:2020].
+
+In this paper, we first explore existing theories of closing civic space, authoritarian regulation of civil society, and differential regulation of international vs.
+domestic NGOs.
+We then propose a set of empirical expectations for INGOs registering in China following the 2017 ONGO Law.
+We describe our data, which includes registration and organization-level details for all 633 INGOs registered between January 1, 2017 and December 31, 2021, and our descriptive and empirical approach to analyzing the data.
+We then present the findings from our data, exploring each of our empirical expectations, and conclude with a discussion of how these results connect to larger themes of the global closure of civic space.
+
 # Legal background
@@
 #| fig-cap: "Two possible pathways for international NGOs to legally work in 
-#|   China, either as formal Registered Organizations (ROs) or by undertaking 
-#|   specific Temporary Activities (TAs)"
+#|   China under the 2017 ONGO law, either as formal Registered Organizations 
+#|   (ROs) or by undertaking specific Temporary Activities (TAs)"
 ro_nodes <- tibble(
@@
     "Open organization bank accounts",
-    "Keep programming withing approved scope",
-    "Submit annual work plans (×2)",
-    "Submit annual reports (×2)"
+    "Keep programming within approved scope",
+    "Submit annual work plans to PSU and Public Security Bureau",
+    "Submit annual reports to PSU and Public Security Bureau"
   ),
@@
     "Channel money through partner’s bank",
-    "Keep programming withing approved scope",
+    "Keep programming within approved scope",
     "Finish work within a year",
-    "Submit final project report"
+    "Submit final project report to Public Security Bureau"
   ),
@@
 
-::: callout-warning
-Apologies! This section is still *incredibly* drafty!
-:::
-
 China's 2017 ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down on international NGOs [@ChaudhryHeiss:2022; @Carothers:2016].
@@
 ## China's INGO as a policy tool
+
 *note* changed the sub-title to incorporate the policy tool lense too.
@@
   3,   "Local focus", 2, 1, FALSE,
-  4,   "Government relationship and interest", 2, -1, FALSE
+  4,   "Government preferences", 2, -1, FALSE
 )
@@
   1, 4,
+  4, 1,
   4, 2
@@
 
-theory_graph <- tbl_graph(nodes = theory_nodes, edges = theory_edges)
+theory_graph <- tbl_graph(nodes = theory_nodes, edges = theory_edges, directed = TRUE)
 
@@
     aes(
+      start_cap = label_rect(node1.name, padding = margin(10, 5, 10, 5, "pt")),
       end_cap = label_rect(node2.name, padding = margin(10, 5, 10, 5, "pt"))
@@
 
-Main structure for these expectations + our analysis:
-
-- Stats + case study: **Flexibility**
-- Stats + case study: **Contentiousness**
-- Case study: **Relationship with PSU and government** (stats/descriptive bc lots of chambers of commerce
+Based on this framework, we can identify and test several theoretical expectations:
 
@@
 
--   **Expectation 1** (issue area): Because they are seen as less of a threat to regime stability, INGOs working on less contentious issues should be registered in more provinces
+In 2018 Batke and Hang posited that the ONGO law was showing signs of reorienting the missions of legally recognized INGOs and the overall scope of international civil society to be more explicitly aligned with government preferences.
+@HolbigLang:2022 recently confirmed this prediction, finding that the issue areas addressed by legally recognized INGOs have "shift[ed] towards fields of activity high up the government’s domestic policy agenda" [-@HolbigLang:2022, p.
+587].
+
+Following our theory, government preferences thus directly influence INGO issue areas, which in turn shapes the amount of flexibility enjoyed by the INGO.
+Accordingly, we expect that INGOs working on non-contentious, regime-aligned issues will have greater reach throughout the country:
+
+- **Theoretical expectation 1**: Because they are seen as less of a threat to regime stability and more aligned with government policy preferences, INGOs working on less contentious issues should be registered in more provinces.
 
@@
 
--   **Expectation 2** (local connections): Because they are explicitly focused on local issues, INGos with more local connections should be registered in fewer provinces
-
-Finally, we also expect that the operational space for INGOs is negatively associated with the time elapsed since the law took effect:
-
--   **Expectation 3** (registration timing): Because formal registration can take a long time and can involve many bureaucratic hurdles, INGOs that registered soon after the law took effect should be be (1) less of a threat and (2) a higher priority for processing, and so should be registered in more provinces
-
-# Data and methods
+- **Theoretical expectation 2**: Because they are explicitly focused on local issues, INGOs with explicitly local missions should be registered in fewer provinces.
+
+Finally, we also expect that the operational space for INGOs is negatively associated with the time elapsed since the law took effect.
+The mechanism behind this expectation is directly related to both issue area and government preferences.
+
+- **Theoretical expectation 3** (registration timing): Because formal registration can take a long time and can involve many bureaucratic hurdles, INGOs that registered soon after the law took effect should be be (1) less of a threat and (2) a higher priority for processing, and so should be registered in more provinces.
+
+# Data and empirical approach
+
+Main structure for these expectations + our analysis:
+
+We test these theoretical expectations using a mixed methods approach. Using
+
+- Stats + case study: **Flexibility**
+- Stats + case study: **Contentiousness**
+- Case study: **Relationship with PSU and government** (stats/descriptive bc lots of chambers of commerce
 
@@
 #| echo: false
-#| fig-cap: "Count of international NGO registrations until the 2017 ONGO Law, divided by quarters"
+#| fig-cap: "Count of international NGO registrations under the 2017 ONGO Law, divided by quarters"
 ggplot(ongo, aes(x = registration_date)) +

### 2023-11-27 manuscript/manuscript.qmd
Conditionally hide introduction heading
See https://github.com/quarto-dev/quarto-cli/issues/7593
Rearrange sections and clean up outline

@@
 short-title: "China's ONGO Law and International Civil Society"
-date: "2023-09-25"
+date: "2023-11-27"
 author:
@@
 
-# Introduction
+::: {.content-visible when-format="html"}
+# Introduction {.hide}
+:::
 
@@
 On April 28, 2016, China passed its own set of legal restrictions on civil society with its Law of the People's Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China, or "ONGO Law," which formally took effect on January 1, 2017.
-The law requires all international NGOs (INGOs) to either register representative offices (ROs) or file temporary activities to lawfully operate in mainland China.As an authoritarian state with a growing nonprofit sector, the Chinese model of implementing restrictive laws for international NGOs (INGOs) has important implications for understanding the dynamics of how civil society laws can be used as policy tools to harness INGOs.
-
-TODO: Andrew - update and coordinate the introductory paragraphs with the theoretical framing below
-
-*Meng's notes/suggestions*: to highlight the theoretical significance in the very beginning (just listing the idea pool for moment, not concise enough):
+The law requires all international NGOs (INGOs) to either register representative offices (ROs) or file temporary activities to lawfully operate in mainland China.
+As an authoritarian state with a growing nonprofit sector, the Chinese model of implementing restrictive laws for international NGOs (INGOs) has important implications for understanding the dynamics of how civil society laws can be used as policy tools to harness INGOs.
+
+We make three general theoretical contributions in this paper:
 
 1.
-A frequently approach to close the space of INGOs is passing restrictive laws/institutional approach.
-[@DeMattee:2019].
+Expansion of work using institutional approaches to examine the regulation and restriction of civil society - [@DeMattee:2019].
 To further understanding this global phenomena , China is an important case to explore the impacts such restrictive laws have on the operation of INGOs.
@@
 2.
-*de facto* vs.
-*de jure* (incorporating the paragraph below) and differentiated treatment for more vs.
+Looking at how civil society laws act as a policy tool that regimes can leverage to shift NGO behavior: to tame INGO to be more cooperative to government.
+The requirement of PSU and Chinese partner to re-direct INGOs to be more authority friendly - The impacts on international civil society we examine include not only access or representation of INGOs in China, but also whether there is change of behaviors [@WuNie:2021].
+Mention the concept of *flexibility (in the sense of adjusting to change)* too?
+
+3.
+Exploring differentiated application of these laws - *de facto* vs.
+*de jure* and differentiated treatment for more vs.
 less contentious INGOs.
@@
 
- 3.
-Laws and policies as a *policy tool* and behavioral shifit: to tame INGO to be more cooperative to government.
-The requirement of PSU and Chinese partner to re-direct INGOs to be more authority friendly.
-
-The impacts on international civil society  we examine include not only access or representation of INGOs in China, but also whether there is change of behaviors [@WuNie:2021].
-Mention the concept of *flexibility (in the sense of adjusting to change)* too?
+TODO: New cool thing here is that we can look at de facto implementation in greater detail.
+Existing studies use things like V-Dem's core civil society index or civil society repression index to capture the general regulatory environment, but changes in those scores aren't necessarily tied to specific laws.
+Here we can see that differential enforcement/de facto/de jure stuff directly
 
@@
 
-In this paper, we first explore existing theories of closing civic space, authoritarian regulation of civil society, and differential regulation of international vs.
-domestic NGOs.
-We then propose a set of empirical expectations for INGOs registering in China following the 2017 ONGO Law.
-We describe our data, which includes registration and organization-level details for all 633 INGOs registered between January 1, 2017 and December 31, 2021, and our descriptive and empirical approach to analyzing the data.
-We then present the findings from our data, exploring each of our empirical expectations, and conclude with a discussion of how these results connect to larger themes of the global closure of civic space.
-
 In this paper, we first explore the ongoing phenomena of closing civic space and authoritarian regulation of civil society, examining how governments conceptualize the role of international civil society in their domestic politics and why governments select regulatory regimes for international NGOs.
@@
 
-# Closing civic space
-
-## The global constriction of civic space
-
-## The "closing space" phenomenon
-
-Many different reasons for these restrictions and several purposes - INGOs pose a threat to regime stability, but they also provide governments with services and technical expertise.
-Civil society/CSO/NGO + host government definition - De Mattee and institutional taxonomy.
-My stuff on gatekeeping vs.
-program capture.
-
-INGO regulations are implemented and enforced differentially - difference in de jure and de facto.
-This differential enforcement is one mechanism to allow host governments to harness the aspects of INGO programming that align with their domestic policy preferences while limiting INGO behavior that could threaten regime stability.
-
-Why pass laws in the first place and why enforcement differently?
-
-@ChaudhryHeiss:2022 and the divergence in de jure and de facto regulations---the implementation doesn't have to match the written law, and often the written law can serve as a "weapon hanging on the wall that never fires" that serves as a warning to potentially uncooperative NGOs [@Kozenko:2015].
-See also [@ToeplerZimmerFrohlich:2020; @Plantan:2022]
-
-"We discuss the role of civil society organizations (CSOs) as agents of democratization and note the emergence of dual, at times apparently conflicting policy postures within authoritarian regimes (restriction and repression for some CSOs vs.
-financial support and opportunities for collaboration for others)." [@ToeplerZimmerFrohlich:2020]
-
-Also, [@Plantan:2022] finds "that I find" evidence of selective implementation that reveals which groups are seen as threatening or beneficial."
-
-The presence of de jure regulations and the strictness of their de facto enforcement are both determined by the interplay between INGO characteristics and government preferences.
-
-Contentiousness, regime stability, other reasons [see @Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016].
-
-Main idea: organizations that work on more contentious issues like human rights advocacy face stricter regulations [@Bush:2015; @ChaudhryHeiss:2021]
-
-## Closing civic space in China
+# Closing civic space in China - legal background thing
 
 China provides a fascinating example of both authoritarian preferences for INGO regulations and INGO adaptations to these regulations.
-
-3.
-Laws and policies as a *policy tool* and behavioral shifit: to tame INGO to be more cooperative to government.
-The requirement of PSU and Chinese partner to re-direct INGOs to be more authority friendly.
 
@@
 
-# Legal background
+---
 
@@
 
-# Theoretical background and expectations
+# Theoretical background
 
@@
 China provides an excellent setting for testing these theories because China's promulgation of restrictive INGO law as an authoritarian jurisdiction fits the observed global trends in recent years, thus can serve as an representative case to deepen scholarly understanding around these themes.
-Also, the level of ambiguity of the legal framework gives ample room for arbitrary discretion and conflicting attitudes by authorities[@Jia:2017], enabling us to analyze rules in form (*de jure*) as well as rules in use (*de facto*).
-
-## The "closing space" phenomenon
+Also, the level of ambiguity of the legal framework gives ample room for arbitrary discretion and conflicting attitudes by authorities [@Jia:2017], enabling us to analyze rules in form (*de jure*) as well as rules in use (*de facto*).
+
+## The "closing space" phenomenon - Institutional approach to closing space
+
+Many different reasons for these restrictions and several purposes - INGOs pose a threat to regime stability, but they also provide governments with services and technical expertise.
+Civil society/CSO/NGO + host government definition - De Mattee and institutional taxonomy.
+My stuff on gatekeeping vs.
+program capture.
 
@@
 
-## De jure vs. de facto implementation of civil society regulations
+## Regulations as policy tool to shape behavior
+
+*note* changed the sub-title to incorporate the policy tool lense too.
+
+TODO: Meng - China crackdown lit
+
+## De jure vs. de facto implementation of civil society regulations - Differential enforcement
 
@@
 See also [@ToeplerZimmerFrohlich:2020; @Plantan:2022]
+INGO regulations are implemented and enforced differentially - difference in de jure and de facto.
+This differential enforcement is one mechanism to allow host governments to harness the aspects of INGO programming that align with their domestic policy preferences while limiting INGO behavior that could threaten regime stability.
+
+Why pass laws in the first place and why enforcement differently?
+
+@ChaudhryHeiss:2022 and the divergence in de jure and de facto regulations---the implementation doesn't have to match the written law, and often the written law can serve as a "weapon hanging on the wall that never fires" that serves as a warning to potentially uncooperative NGOs [@Kozenko:2015].
+See also [@ToeplerZimmerFrohlich:2020; @Plantan:2022]
+
+"We discuss the role of civil society organizations (CSOs) as agents of democratization and note the emergence of dual, at times apparently conflicting policy postures within authoritarian regimes (restriction and repression for some CSOs vs.
+financial support and opportunities for collaboration for others)." [@ToeplerZimmerFrohlich:2020]
+
+Also, [@Plantan:2022] finds "that I find" evidence of selective implementation that reveals which groups are seen as threatening or beneficial."
+
+The presence of de jure regulations and the strictness of their de facto enforcement are both determined by the interplay between INGO characteristics and government preferences.
+
+Contentiousness, regime stability, other reasons [see @Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016].
+
+Main idea: organizations that work on more contentious issues like human rights advocacy face stricter regulations [@Bush:2015; @ChaudhryHeiss:2021]
 
@@
 
-## China's INGO as a policy tool
-
-*note* changed the sub-title to incorporate the policy tool lense too.
-
-TODO: Meng - China crackdown lit
-
-## Empirical expectations
+# Empirical expectations
 
@@
 - Stats + case study: **Contentiousness**
-- Case study: **Relationship with PSU and government** (stats/descriptive bc lots of chambers of commerce
+- Case study: **Relationship with PSU and government** (stats/descriptive bc lots of chambers of commerce)
 
@@
 
+Paragraph justifying why the case study is needed
+
+Education, Environment, lower expected operating space (flexibility?)
+
+So Issue areas can predict some level of flexibility/restrictions INGOs receive, but that is not the full story, the relations with the government (one more dimension/variable) also plays important roles, see TNC vs.
+Greenpeace
+
 TODO: Meng - TA vs. RO, exploring main mechanisms of flexibility, contentiousness, and relationships
@@
 
-::: callout-warning
-**Still TODO!**
-:::
-
 # References

### 2023-11-27 manuscript/manuscript.qmd
Remove redundant ¶s

@@
 
-Many INGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [@Sidel:2016], though there were no clear requirements for them to have a formal legal presence in China [@Han:2011; @HolbigLang:2022; @Yin:2009].
-However, the legal form of foreign-funded company is not quite compatible with the nonprofit nature of INGOs.
-Under the Chinese legal system, enterprises are intended to be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms, including foundations, associations, and social service organizations [@Ye:2021].
-Thus, INGOs obtaining legal identity in this way have to navigate through a legal framework designed for a for-profit institutional logic, e.g, focusing on protecting investors' right to investment returns.
-
-This paper explores the characteristics of all registered INGOs in China in the five years after the ONGO Law became effective and examines the association between INGO issue areas and the operational space granted to them in the country.
-Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus.
-Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018].
-INGOs vary in their ability to attract partner PSUs, and organizations that are unable to find corresponding PSUs are more limited in their geographic reach within the country.
-INGOs are authorized to operate within China on a province-by-province basis.
-Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.
-We use the number of provinces that INGOs are authorized to work in as a proxy to measure the operational space for INGOs in China based on the assumption that INGOs need to or hope to have the approval to be able to carry out their programs in a geographical scope as large as possible [@Li:2020].
-
-In this paper, we first explore existing theories of closing civic space, authoritarian regulation of civil society, and differential regulation of international vs.
-domestic NGOs.
-We then propose a set of empirical expectations for INGOs registering in China following the 2017 ONGO Law.
-We describe our data, which includes registration and organization-level details for all 633 INGOs registered between January 1, 2017 and December 31, 2021, and our descriptive and empirical approach to analyzing the data.
-We then present the findings from our data, exploring each of our empirical expectations, and conclude with a discussion of how these results connect to larger themes of the global closure of civic space.
-
----
-
 International NGOs began to play an important role in China in the early 1990s as part of the country's Reform and Opening-Up policy, and organizations like Save the Children and the Ford Foundation established local offices and branches.

### 2023-11-27 manuscript/manuscript.qmd
Some more rearranging/clarification

@@
 
-- Stats + case study: **Flexibility**
+1: issue - stats + case study
+2: localness - stats
+3: timing - stats
+
+- Stats + case study: **Local**
 - Stats + case study: **Contentiousness**
@@
 
-# Flexibility, contentiousness, and government relationships: The cases of Greenpeace and The Nature Conservancy
-
-Paragraph justifying why the case study is needed
-
-Education, Environment, lower expected operating space (flexibility?)
+# Contentiousness and government relationships: The cases of Greenpeace and The Nature Conservancy
+
+Paragraph justifying why the case study is needed - stats are cool but missing details about contentiousness of issues - also, stats only look at ROs, not TAs or any ONGOs that left the country, so we're missing some dynamics of ONGO-government relations.
+We can explore our empirical expectations in more depth by looking at a comparative case study of Greenpeace and NC
+
+Education, Environment, lower expected operating space
 
@@
 
-TODO: Meng - TA vs. RO, exploring main mechanisms of flexibility, contentiousness, and relationships
+TODO: Meng - TA vs. RO, exploring main mechanisms of contentiousness, and relationships
 

### 2023-11-28 manuscript/manuscript.qmd
More cleanup + added TODOs for each remaining section

@@
 abstract: |
-  China’s 2017 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international nongovernmental organizations (INGOs).
+  TODO: **Update this based on the finished version of the paper.** China’s 2017 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international nongovernmental organizations (INGOs).
 However, the effects of this global crackdown on INGOs have been difficult to measure since there is often divergence between the formal de jure regulations and the de facto implementation of these laws.
@@
 
-We make three general theoretical contributions in this paper:
-
-1.
-Expansion of work using institutional approaches to examine the regulation and restriction of civil society - [@DeMattee:2019].
-To further understanding this global phenomena , China is an important case to explore the impacts such restrictive laws have on the operation of INGOs.
-Such legal restrictions can be either direct (denial of legal access/cannot register) or covert (red-tape, requiring the approval of PSUs, or the uncertainty of having to filing TAs case by case)
-
-2.
-Looking at how civil society laws act as a policy tool that regimes can leverage to shift NGO behavior: to tame INGO to be more cooperative to government.
-The requirement of PSU and Chinese partner to re-direct INGOs to be more authority friendly - The impacts on international civil society we examine include not only access or representation of INGOs in China, but also whether there is change of behaviors [@WuNie:2021].
-Mention the concept of *flexibility (in the sense of adjusting to change)* too?
-
-3.
-Exploring differentiated application of these laws - *de facto* vs.
-*de jure* and differentiated treatment for more vs.
-less contentious INGOs.
-Authoritarian -> arbitrary and varied application of the law -> different *operating space*
-
-TODO: New cool thing here is that we can look at de facto implementation in greater detail.
-Existing studies use things like V-Dem's core civil society index or civil society repression index to capture the general regulatory environment, but changes in those scores aren't necessarily tied to specific laws.
-Here we can see that differential enforcement/de facto/de jure stuff directly
-
 The purpose of this study is to empirically examine how the ONGO Law has influenced the population of INGOs that have successfully registered in China since 2017, and in particular how the ONGO Law has shaped the operational space allowed for INGO operations in the country.
@@
 
+TODO: Andrew - make this a paragraph, not a list.
+
+We make three general theoretical contributions in this paper:
+
+1.
+Expansion of work using institutional approaches to examine the regulation and restriction of civil society - [@DeMattee:2019].
+To further understanding this global phenomena , China is an important case to explore the impacts such restrictive laws have on the operation of INGOs.
+Such legal restrictions can be either direct (denial of legal access/cannot register) or covert (red-tape, requiring the approval of PSUs, or the uncertainty of having to filing TAs case by case)
+
+2.
+Looking at how civil society laws act as a policy tool that regimes can leverage to shift NGO behavior: to tame INGO to be more cooperative to government.
+The requirement of PSU and Chinese partner to re-direct INGOs to be more authority friendly - The impacts on international civil society we examine include not only access or representation of INGOs in China, but also whether there is change of behaviors [@WuNie:2021].
+Mention the concept of *flexibility (in the sense of adjusting to change)* too?
+
+3.
+Exploring differentiated application of these laws - *de facto* vs.
+*de jure* and differentiated treatment for more vs.
+less contentious INGOs.
+Authoritarian -> arbitrary and varied application of the law -> different *operating space*
+
+TODO: Andrew: Also, new cool thing here is that we can look at de facto implementation in greater detail.
+Existing studies use things like V-Dem's core civil society index or civil society repression index to capture the general regulatory environment, but changes in those scores aren't necessarily tied to specific laws.
+Here we can see that differential enforcement/de facto/de jure stuff directly
+
+TODO: Andrew: Roadmap of paper, to add later
 In this paper, we first explore the ongoing phenomena of closing civic space and authoritarian regulation of civil society, examining how governments conceptualize the role of international civil society in their domestic politics and why governments select regulatory regimes for international NGOs.
@@
 
-TODO: Meng - add brief explanations of the TA/RO pathways figure and articulate the "cooperative requirements part", i.e., seeking a psu or Chinese partner
-
-TODO: Andrew - image of TA/RO pathways @fig-ro-ta-pathways
+TODO: Meng - add brief explanations of the TA/RO pathways figure in @fig-ro-ta-pathways and articulate the "cooperative requirements part", i.e., seeking a psu or Chinese partner
 
@@
 
+TODO: Andrew: I'll clean up/rewrite this section and the section headings, etc.
+
+## The "closing space" phenomenon - Institutional approach to closing space
+
 China's 2017 ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down on international NGOs [@ChaudhryHeiss:2022; @Carothers:2016].
@@
 
-## The "closing space" phenomenon - Institutional approach to closing space
-
 Many different reasons for these restrictions and several purposes - INGOs pose a threat to regime stability, but they also provide governments with services and technical expertise.
@@
 
-Main idea: organizations that work on more contentious issues like human rights advocacy face stricter regulations [@Bush:2015; @ChaudhryHeiss:2021]
-
-(Meng added)
-
 ## Regulations as policy tool to shape behavior
@@
 ## De jure vs. de facto implementation of civil society regulations - Differential enforcement
+
+TODO: Andrew - I'll clean up this section
 
@@
 See also [@ToeplerZimmerFrohlich:2020; @Plantan:2022]
+
+"We discuss the role of civil society organizations (CSOs) as agents of democratization and note the emergence of dual, at times apparently conflicting policy postures within authoritarian regimes (restriction and repression for some CSOs vs.
+financial support and opportunities for collaboration for others)." [@ToeplerZimmerFrohlich:2020]
+
 INGO regulations are implemented and enforced differentially - difference in de jure and de facto.
@@
 
-Contentiousness, regime stability, other reasons [see @Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016].
-
 Main idea: organizations that work on more contentious issues like human rights advocacy face stricter regulations [@Bush:2015; @ChaudhryHeiss:2021]
 
-::: content-hidden
-"We discuss the role of civil society organizations (CSOs) as agents of democratization and note the emergence of dual, at times apparently conflicting policy postures within authoritarian regimes (restriction and repression for some CSOs vs.
-financial support and opportunities for collaboration for others)." [@ToeplerZimmerFrohlich:2020]
-
-Also, [@Plantan:2022] finds "that I find" evidence of selective implementation that reveals which groups are seen as threatening or beneficial."
-:::
-
-# Empirical expectations
+# Empirical expectations and analytical approach
+
+TODO: Andrew: I'll clean up this section
 
@@
 - **Theoretical expectation 3** (registration timing): Because formal registration can take a long time and can involve many bureaucratic hurdles, INGOs that registered soon after the law took effect should be be (1) less of a threat and (2) a higher priority for processing, and so should be registered in more provinces.
-
-# Data and empirical approach
-
-Main structure for these expectations + our analysis:
 
@@
 
+TODO: Meng
+
 Paragraph justifying why the case study is needed - stats are cool but missing details about contentiousness of issues - also, stats only look at ROs, not TAs or any ONGOs that left the country, so we're missing some dynamics of ONGO-government relations.
@@
 
-TODO: Meng - TA vs. RO, exploring main mechanisms of contentiousness, and relationships
+TODO: Meng - TA vs. RO, exploring main mechanisms of contentiousness and relationships
 
@@
 # References
+
+::: {#refs .bibliography}
+:::

### 2023-11-28 manuscript/manuscript.qmd
Strike out the organizational flexibility stuff in the intro
Eventually this whole paragraph will match the rest of the paper, once the rest of the paper is more done

@@
 In this paper, we first explore the ongoing phenomena of closing civic space and authoritarian regulation of civil society, examining how governments conceptualize the role of international civil society in their domestic politics and why governments select regulatory regimes for international NGOs.
-We then investigate how international NGOs have responded and adapted to more restrictive regulatory environments and theorize that a key component of INGO regulatory adaptation is *organizational flexibility*, or the ability to operate with greater latitude in host countries.
-We propose two key determinants of this flexibility: (1) organizational characteristics and (2) host government preferences and relationships TODO and their interplay/interaction.
-We illustrate this theory using the case of China TODO stats and case studies, mixed method, demonstrating how INGOs that address issues that align with government preferences enjoy the most organizational flexibility in the country.
+~~We then investigate how international NGOs have responded and adapted to more restrictive regulatory environments and theorize that a key component of INGO regulatory adaptation is the ability to operate with greater latitude in host countries.
+We propose two key determinants of this flexibility: (1) organizational characteristics and (2) host government preferences and relationships TODO and their interplay/interaction.~~ We illustrate this theory using the case of China TODO stats and case studies, mixed method, demonstrating how INGOs that address issues that align with government preferences enjoy the most organizational flexibility in the country.
 

### 2023-11-28 manuscript/manuscript.qmd
Reminder to me about "operational space"

@@
 In this paper, we first explore the ongoing phenomena of closing civic space and authoritarian regulation of civil society, examining how governments conceptualize the role of international civil society in their domestic politics and why governments select regulatory regimes for international NGOs.
-~~We then investigate how international NGOs have responded and adapted to more restrictive regulatory environments and theorize that a key component of INGO regulatory adaptation is the ability to operate with greater latitude in host countries.
+Term we'll use = operational space, not flexibility ~~We then investigate how international NGOs have responded and adapted to more restrictive regulatory environments and theorize that a key component of INGO regulatory adaptation is the ability to operate with greater latitude in host countries.
 We propose two key determinants of this flexibility: (1) organizational characteristics and (2) host government preferences and relationships TODO and their interplay/interaction.~~ We illustrate this theory using the case of China TODO stats and case studies, mixed method, demonstrating how INGOs that address issues that align with government preferences enjoy the most organizational flexibility in the country.

### 2023-11-29 manuscript/manuscript.qmd
Fix cross-references for multi-paneled figures

@@
 short-title: "China's ONGO Law and International Civil Society"
-date: "2023-11-27"
+date: "2023-11-29"
 author:
@@
 To explore this, we can take advantage of the simultaneous continuous and discrete features of ordered Beta regression and see how often an INGO in each issue area is predicted to work in a single province, across all provinces, or some number in between.
-@fig-issue-preds-1 presents a summary of predicted posterior outcomes for 1,000 hypothetical INGOs, varying each possible issue area and holding all other variables at their mean or modal values.
+@fig-issue-preds(a) presents a summary of predicted posterior outcomes for 1,000 hypothetical INGOs, varying each possible issue area and holding all other variables at their mean or modal values.
 Several notable trends emerge from the model results.
@@
 All other issue areas follow roughly the patterns in predictions: the most common outcome is for organizations to work nationally (50--60% of the time), followed by working in at least 2 provinces (25--40% of the time), followed by working in a single province (10--20% of the time).
-@fig-issue-preds-2 shows the continuous posterior distribution of the average number of provinces INGOs are expected to be registered in across all types of issue areas, but accounting for the 1- and 32-only provinces simultaneously.
+@fig-issue-preds(b) shows the continuous posterior distribution of the average number of provinces INGOs are expected to be registered in across all types of issue areas, but accounting for the 1- and 32-only provinces simultaneously.
 We can see a similar trend---arts and culture INGOs are predicted to work in 28--30 provinces on average, while education INGOs are only predicted to work in 12--20.
@@
 #| column: body-outset
-#| fig-cap: "*Top*: Posterior predictions from ordered Beta regression model,
+#| fig-cap: "**A**: Posterior predictions from ordered Beta regression model,
 #|   conditional on organization issue area, showing the predicted proportion of
@@
 #|   represents the uncertainty in category boundaries. 95% credible intervals 
-#|   are shown as ranges in each category. *Bottom*: Expectation (or average) of
+#|   are shown as ranges in each category. **B**: Expectation (or average) of
 #|   posterior predictive distributions. These distributions take into account 
@@
 #|   median; lines show 80% and 95% credible intervals."
+
 preds_issue_plot <- preds_issue |> 
@@
     title = "Predicted proportion of type of geographic reach across issue area",
-    subtitle = "Posterior predictions of outcome categories"
+    subtitle = "Posterior predictions of outcome categories",
+    tag = "A"
   ) +
@@
     title = "Expected count of provinces",
-    subtitle = "Expectation of posterior predictions"
+    subtitle = "Expectation of posterior predictions",
+    tag = "B"
   ) +
@@
 The results from our model confirm this expectation.
-@fig-local-preds-1 shows the distribution of predicted posterior outcomes for 1,000 hypothetical INGOs.
+@fig-local-preds(a) shows the distribution of predicted posterior outcomes for 1,000 hypothetical INGOs.
 Organizations without local connections are predicted to work nationally across all provinces nearly half of the time (with a 95% credible interval of 46--51%), and are predicted to work in two or more provinces 32--37% of the time.
@@
 For these locally-focused organizations, the least common prediction is to work nationally, with only a 23--29% probability.
-@fig-local-preds-2 shows the posterior distribution of the average number of provinces INGOs are expected to be registered in, conditional on their local connections.
+@fig-local-preds(b) shows the posterior distribution of the average number of provinces INGOs are expected to be registered in, conditional on their local connections.
 The same relationship holds---an INGO without local connections is predicted to work in 19--24 provinces on average, while an organization with local connections is only predicted to work in 8--17.
@@
 #| fig-cap: "Posterior predictions from ordered Beta regression model, 
-#|   conditional on having local connections. *Top*: Predicted proportion of 
+#|   conditional on having local connections. **A**: Predicted proportion of 
 #|   INGOs working in 1 province, all 32 provinces, or somewhere in between. 
@@
 #|   represents the uncertainty in category boundaries. 95% credible intervals 
-#|   are shown as ranges in each category. *Bottom*: Expectation (or average) of 
+#|   are shown as ranges in each category. **B**: Expectation (or average) of 
 #|   posterior predictive distributions. These distributions take into account 
@@
 #|   median; lines show 80% and 95% credible intervals."
+
 preds_local_plot <- preds_local |> 
@@
     title = "Predicted proportion of type of\ngeographic reach across local connections",
-    subtitle = "Posterior predictions of outcome categories"
+    subtitle = "Posterior predictions of outcome categories",
+    tag = "A"
   ) +
@@
 However, the results of our model support the *reverse* of this expectation.
-@fig-timing-preds-1 once again shows the predicted posterior outcomes for 1,000 simulated INGOs across a range of time since January 2017.
+@fig-timing-preds(a) once again shows the predicted posterior outcomes for 1,000 simulated INGOs across a range of time since January 2017.
 Organizations that registered in the first year are predicted to work in all provinces 41--46% of the time, and are predicted to work in two or more provinces 34--39% of the time.
@@
 After the initial wave of registrations in 2017, the likelihood of nationwide reach steadily increases and replaces both the probability of a single province or a partial range of provinces.
-By the end of 2021---5 years after the ONGO Law took effect---the probability of national -level registration increases to 55--61% while the probability of working in a range of provinces increases to predicted to work in two or more provinces increase to 27--32%.
+By the end of 2021---5 years after the ONGO Law took effect---the probability of national-level registration increases to 55--61% while the probability of working in a range of provinces increases to predicted to work in two or more provinces increase to 27--32%.
 These late INGOs are the least likely to be registered in only one province and are predicted to do so only 17--22% of the time.
-@fig-timing-preds-2 demonstrates the same results with the posterior distribution of the expected count of provinces over five years since 2017.
+@fig-timing-preds(b) demonstrates the same results with the posterior distribution of the expected count of provinces over five years since 2017.
 INGOs that register early are predicted to work in 17--22 provinces, while those that wait until 2021 are predicted to work in 21--28.
@@
 #| fig-cap: "Posterior predictions from ordered Beta regression model, 
-#|   conditional on time since law took effect in January 2017. *Top*: Predicted 
+#|   conditional on time since law took effect in January 2017. **A**: Predicted 
 #|   proportion of INGOs working in 1 province, all 32 provinces, or somewhere 
@@
 #|   probabilities, so the fuzziness represents the uncertainty in category 
-#|   boundaries. *Bottom*: Expectation (or average) of posterior predictive 
+#|   boundaries. **B**: Expectation (or average) of posterior predictive 
 #|   distributions. This distribution takes into account single-province and 
@@
 #|   and 95% credible intervals."
+
 preds_timing_plot <- preds_timing |> 
@@
     title = "Predicted proportion of type of \ngeographic reach since January 2017",
-    subtitle = "Posterior predictions of outcome categories"
+    subtitle = "Posterior predictions of outcome categories",
+    tag = "A"
   ) +

### 2023-11-29 manuscript/manuscript.qmd
Shift lit review points order and add explanation of the results of timing

@@
 less contentious INGOs.
-Authoritarian -> arbitrary and varied application of the law -> different *operating space*
+Authoritarian -\> arbitrary and varied application of the law -\> different *operating space*
 
@@
 
-TODO: Andrew: Roadmap of paper, to add later
-In this paper, we first explore the ongoing phenomena of closing civic space and authoritarian regulation of civil society, examining how governments conceptualize the role of international civil society in their domestic politics and why governments select regulatory regimes for international NGOs.
+TODO: Andrew: Roadmap of paper, to add later In this paper, we first explore the ongoing phenomena of closing civic space and authoritarian regulation of civil society, examining how governments conceptualize the role of international civil society in their domestic politics and why governments select regulatory regimes for international NGOs.
 Term we'll use = operational space, not flexibility ~~We then investigate how international NGOs have responded and adapted to more restrictive regulatory environments and theorize that a key component of INGO regulatory adaptation is the ability to operate with greater latitude in host countries.
@@
 However, the actual application of the regulation was very limited.
-Up until the ONGO Law took effect in 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs, while some Chinese officials estimated in 2016 that there were roughly over 7,000 INGOs operating in China [@YeHuang:2018].
+Up until the ONGO Law took effect in 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs, while some Chinese officials estimated in 2016 that there were roughly over 7,000 INGOs operating in China [@YeHuang:2018; Spires:2020a].
 
@@
 
-TODO: Andrew: This 2017 law fits with a broader global phenomenon of closing civic space… General crackdown stuff + China crackdown stuff + our addition
+TODO: Andrew: This 2017 law fits with a broader global phenomenon of closing civic space... General crackdown stuff + China crackdown stuff + our addition
 
@@
 
-## Regulations as policy tool to shape behavior
-
-*note* changed the sub-title to incorporate the policy tool lense too.
-
-TODO: Meng - China crackdown lit
-
 ## De jure vs. de facto implementation of civil society regulations - Differential enforcement
@@
 Main idea: organizations that work on more contentious issues like human rights advocacy face stricter regulations [@Bush:2015; @ChaudhryHeiss:2021]
+
+## China's Overseas NGO law as a policy tool and its implications
+
+*note* changed the sub-title to incorporate the policy tool lense too.
+
+TODO: Meng - China crackdown lit
 
@@
 In 2018 Batke and Hang posited that the ONGO law was showing signs of reorienting the missions of legally recognized INGOs and the overall scope of international civil society to be more explicitly aligned with government preferences.
-@HolbigLang:2022 recently confirmed this prediction, finding that the issue areas addressed by legally recognized INGOs have "shift[ed] towards fields of activity high up the government’s domestic policy agenda" [-@HolbigLang:2022, p.
+@HolbigLang:2022 recently confirmed this prediction, finding that the issue areas addressed by legally recognized INGOs have "shift\[ed\] towards fields of activity high up the government's domestic policy agenda" [-@HolbigLang:2022, p.
 587].
@@
 
-1: issue - stats + case study
-2: localness - stats
-3: timing - stats
+1: issue - stats + case study 2: localness - stats 3: timing - stats
 
@@
 negative counts of provinces or more than 32 provinces).
-If we transform the count of provinces to a percentage, Beta regression would work well, as it is naturally limited to outcomes within a 0–1 range.
+If we transform the count of provinces to a percentage, Beta regression would work well, as it is naturally limited to outcomes within a 0--1 range.
 However, Beta regression cannot handle values that are exactly 0 or 1, making it inappropriate for our data with its inflated counts at 0 (1) and 100% (32).
-To account for values at the bounds, we rely on ordered Beta regression [@Kubinec:2022], an extension of zero-and-one-inflated Beta regression that allows us to simultaneously model the continuous range of provinces (2–31) and the discrete outcomes (1 province and 32 provinces) without relying on percentages.
-We can thus explore the dynamics of each of our independent variables of interest in multiple ways—we can see (1) how each variable predicts that an organizations works in one province, nationwide, or somewhere in between, and (2) how each variable predicts the overall expected count of provinces.
+To account for values at the bounds, we rely on ordered Beta regression [@Kubinec:2022], an extension of zero-and-one-inflated Beta regression that allows us to simultaneously model the continuous range of provinces (2--31) and the discrete outcomes (1 province and 32 provinces) without relying on percentages.
+We can thus explore the dynamics of each of our independent variables of interest in multiple ways---we can see (1) how each variable predicts that an organizations works in one province, nationwide, or somewhere in between, and (2) how each variable predicts the overall expected count of provinces.
 
@@
 
-:::{.column-page-inset}
+::: column-page-inset
 $$
@@
 As we saw previously with INGOs and local connections, organizations appear to strategically seek out the best avenues and methods for registering.
-Organizations that participated in the initial wave of registrations in 2017 likely had closer connections with local officials and were able to speed through the bureaucratic process registration more easily.
+[@Jia:2017a] Organizations that participated in the initial wave of registrations in 2017 likely had closer connections with local officials and were able to speed through the bureaucratic process registration more easily.
 As a preliminary test of this speculation, we rerun our main model with an interaction between years since registration and local connections to see how the effect of local connections changes over time.
@@
 Accordingly, it may be that organizations with local connections are more likely to register early because of their pre-existing bureaucratic relationships, while organizations with a larger national reach take longer to undertake the registration process and thus register later.
-Further research on this point is warranted.
+Another possible explanation is interpreting earlier timing in registration as more eager to register as discussed in the measurement section.
+INGOs that self-perceive as more contentious would be more nervous about the legal consequences of not being able to register and thus be more eager to seek registration earlier [@ChinaPhilanthropyReserchInstitute:2018].
+Compared with their more "rest-assured" peers, INGOs seeking to register earlier are more likely to have reduced operational space.
+To understand the underlying mechanism with registration timing, further research is warranted.
 

### 2023-11-29 manuscript/manuscript.qmd
Add interpretation on environmental issue area after education

@@
 
+Additionally, the INGOs that survived the registration thresholds are those already "censored" to be relatively safe and non-contentious.
+This can help explain why some seemingly more contentious issue areas, e.g., environmental INGOs enjoy relatively more operational space.
+According to [@Plantan:2022], Chinese authorities can see the work of environmental INGOs as providing benefits such as political stability and "selectively ncourage low risk groups and selectively channel higher risk groups into permitted areas".
+We will further this discussion with the case analysis of two environmental INGOs later.
+
 ### Local connections

### 2023-11-29 manuscript/manuscript.qmd
Overhaul of the structure in Introduction

@@
 
+TODO: Andrew - review all the re-structuring made by Meng
+
 In the past decade, nearly 100 countries have proposed or enacted legal measures designed to restrict civil society [@ICNL:2021], and only 21% of countries have open and unrestricted civic space [@ChaudhryHeiss:2022a; @Civicus:2023].
@@
 The law requires all international NGOs (INGOs) to either register representative offices (ROs) or file temporary activities to lawfully operate in mainland China.
-As an authoritarian state with a growing nonprofit sector, the Chinese model of implementing restrictive laws for international NGOs (INGOs) has important implications for understanding the dynamics of how civil society laws can be used as policy tools to harness INGOs.
-
-The purpose of this study is to empirically examine how the ONGO Law has influenced the population of INGOs that have successfully registered in China since 2017, and in particular how the ONGO Law has shaped the operational space allowed for INGO operations in the country.
-By examining the *de facto* implementation of the law in addition to its formal *de jure* regulations, we provide a more comprehensive and data-based picture of the operational space for INGOs.
-By relying on representative empirical data from mainland China, our study also contributes to a growing body of research on the effects of closing civic space on INGO behavior and strategies.
-
-This paper explores the characteristics of all registered INGOs in China in the five years after the ONGO Law became effective and examines the association between INGO issue areas and the operational space granted to them in the country.
+
+As an authoritarian state with a growing nonprofit sector, the Chinese model of implementing restrictive laws for international NGOs (INGOs) has important implications for understanding the dynamics of how civil society laws can be used as policy tools to harness the activities of INGOs.
+Globally, theoretical frameworks such as [@DeMattee:2019] focus on the
+institutional approaches, i.e., restrictive laws to crack down international civil society.
+(TO DO: whether to explain INGO vs.
+Civil Society as mentioned by MPSA reviewers).
+To further understanding this global phenomena , China is an important case to explore the impacts such restrictive laws have on the operation of INGOs.
+Such legal restrictions can be either direct (denial of legal access/cannot register) or covert (red-tape, requiring the approval of PSUs, or the uncertainty of having to filing TAs case by case).
+
+This paper explores the characteristics of all registered INGOs in China in the five years after the ONGO Law became effective and examines how the ONGO Law has influenced the population of INGOs that have successfully registered in China, as well as the association between factors such as INGO issue areas and the operational space granted to them in the country.
+Scholars have discussed the discrepancy that can exist between the *de facto* implementation of the law and the formal *de jure* regulations.
+(Andrew TO DO: add literature).
+We engage with this conversation by analyzing a more comprehensive and data-based picture of INGOs operating in China in the post ONGO law era.
+Exploring differentiated application of these laws and differentiated treatment for more vs.
+less contentious INGOs.
+Authoritarian -\> arbitrary and varied application of the law -\> different *operating space*
+
+TODO: Andrew: Also, new cool thing here is that we can look at de facto implementation in greater detail.
+Existing studies use things like V-Dem's core civil society index or civil society repression index to capture the general regulatory environment, but changes in those scores aren't necessarily tied to specific laws.
+Here we can see that differential enforcement/de facto/de jure stuff directly
+
+Our study also contributes to a growing body of research on the effects of closing civic space on INGO behavior and strategies using a mixed-method approach.
+Looking at how civil society laws act as a policy tool that regimes can leverage to shift NGO behavior: to tame INGO to be more cooperative to government.
+The requirement of PSU and Chinese partner to re-direct INGOs to be more authority friendly - The impacts on international civil society we examine include not only access or representation of INGOs in China, but also whether there is change of behaviors [@WuNie:2021].
+In addition to quantitative analysis of the administrative data of 633 registered offices of INGOs.
+We also explored how the relationship with the government and the organizational flexibility of INGOs can come into play under the ONGO law.
+
+TODO: Andrew: Roadmap of paper, to add later In this paper, we first explore the ongoing phenomena of closing civic space and authoritarian regulation of civil society, examining how governments conceptualize the role of international civil society in their domestic politics and why governments select regulatory regimes for international NGOs.
+Term we'll use = operational space, not flexibility ~~We then investigate how international NGOs have responded and adapted to more restrictive regulatory environments and theorize that a key component of INGO regulatory adaptation is the ability to operate with greater latitude in host countries.
+We propose two key determinants of this flexibility: (1) organizational characteristics and (2) host government preferences and relationships TODO and their interplay/interaction.~~ We illustrate this theory using the case of China TODO stats and case studies, mixed method, demonstrating how INGOs that address issues that align with government preferences enjoy the most organizational flexibility in the country.
+
+# The legal framework established by the ONGO law
+
+International NGOs began to play an important role in China in the early 1990s as part of the country's Reform and Opening-Up policy, and organizations like Save the Children and the Ford Foundation established local offices and branches.
+Since then, INGOs and global civil society have played pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China's domestic nonprofit sector [@Yin:2009].
+Prior to the implementation of the 2017 ONGO Law, regulation of INGOs in China was obscure [@Shieh:2018; @Spires:2022].
+The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations by the State Council that specifies the registration of representative offices ("ROs") of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic NGOs.
+However, the actual application of the regulation was very limited.
+Up until the ONGO Law took effect in 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs, while some Chinese officials estimated in 2016 that there were roughly over 7,000 INGOs operating in China [@YeHuang:2018; Spires:2020a].
+
+Many INGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [@Sidel:2016], though there were no clear requirements for them to have a formal legal presence in China [@Han:2011; @HolbigLang:2022; @Yin:2009].
+However, the legal form of foreign-funded company is not quite compatible with the nonprofit nature of INGOs.
+Under the Chinese legal system, enterprises are intended to be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms, including foundations, associations, and social service organizations [@Ye:2021].
+Thus, INGOs obtaining legal identity in this way have to navigate through a legal framework designed for a for-profit institutional logic, e.g, focusing on protecting investors' right to investment returns.
+
+The legal framework governing INGOs was overhauled by the 2017 Chinese ONGO Law.
+The new law applies to all overseas (including Hong Kong, Macau, and Taiwan) non-governmental organizations that conduct not-for-profit activities in the fields of economic development, education, science, technology, culture, public health, sports, environment protection, poverty alleviation, and disaster relief (Article 3).
+The ONGO Law stipulates two ways for INGOs to lawfully conduct nonprofit activities in China: (1) submitting an application for formal permanent registration, or (2) filing documentation of temporary activities with the Ministry of Public Security and provincial-level Public Security Bureaus, which are the registering and regulatory authority for INGOs.
+Formal registration of an RO allows them to maintain an ongoing present in the country, while temporary activities are intended for INGOs that need to conduct one-off programs that last no longer than one year.
+Abiding by these two channels to obtain lawful presence is mandatory for INGOs after the Overseas NGO Law came into effect, any INGOs that could not successfully obtain proper legal authorization would be deemed illegal.
+
 Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus.
@@
 We use the number of provinces that INGOs are authorized to work in as a proxy to measure the operational space for INGOs in China based on the assumption that INGOs need to or hope to have the approval to be able to carry out their programs in a geographical scope as large as possible [@Li:2020].
-
-TODO: Andrew - make this a paragraph, not a list.
-
-We make three general theoretical contributions in this paper:
-
-1.
-Expansion of work using institutional approaches to examine the regulation and restriction of civil society - [@DeMattee:2019].
-To further understanding this global phenomena , China is an important case to explore the impacts such restrictive laws have on the operation of INGOs.
-Such legal restrictions can be either direct (denial of legal access/cannot register) or covert (red-tape, requiring the approval of PSUs, or the uncertainty of having to filing TAs case by case)
-
-2.
-Looking at how civil society laws act as a policy tool that regimes can leverage to shift NGO behavior: to tame INGO to be more cooperative to government.
-The requirement of PSU and Chinese partner to re-direct INGOs to be more authority friendly - The impacts on international civil society we examine include not only access or representation of INGOs in China, but also whether there is change of behaviors [@WuNie:2021].
-Mention the concept of *flexibility (in the sense of adjusting to change)* too?
-
-3.
-Exploring differentiated application of these laws - *de facto* vs.
-*de jure* and differentiated treatment for more vs.
-less contentious INGOs.
-Authoritarian -\> arbitrary and varied application of the law -\> different *operating space*
-
-TODO: Andrew: Also, new cool thing here is that we can look at de facto implementation in greater detail.
-Existing studies use things like V-Dem's core civil society index or civil society repression index to capture the general regulatory environment, but changes in those scores aren't necessarily tied to specific laws.
-Here we can see that differential enforcement/de facto/de jure stuff directly
-
-TODO: Andrew: Roadmap of paper, to add later In this paper, we first explore the ongoing phenomena of closing civic space and authoritarian regulation of civil society, examining how governments conceptualize the role of international civil society in their domestic politics and why governments select regulatory regimes for international NGOs.
-Term we'll use = operational space, not flexibility ~~We then investigate how international NGOs have responded and adapted to more restrictive regulatory environments and theorize that a key component of INGO regulatory adaptation is the ability to operate with greater latitude in host countries.
-We propose two key determinants of this flexibility: (1) organizational characteristics and (2) host government preferences and relationships TODO and their interplay/interaction.~~ We illustrate this theory using the case of China TODO stats and case studies, mixed method, demonstrating how INGOs that address issues that align with government preferences enjoy the most organizational flexibility in the country.
-
-# Closing civic space in China - legal background thing
-
-China provides a fascinating example of both authoritarian preferences for INGO regulations and INGO adaptations to these regulations.
-
-International NGOs began to play an important role in China in the early 1990s as part of the country's Reform and Opening-Up policy, and organizations like Save the Children and the Ford Foundation established local offices and branches.
-Since then, INGOs and global civil society have played pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China's domestic nonprofit sector [@Yin:2009].
-Prior to the implementation of the 2017 ONGO Law, regulation of INGOs in China was obscure [@Shieh:2018; @Spires:2022].
-The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations by the State Council that specifies the registration of representative offices ("ROs") of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic NGOs.
-However, the actual application of the regulation was very limited.
-Up until the ONGO Law took effect in 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs, while some Chinese officials estimated in 2016 that there were roughly over 7,000 INGOs operating in China [@YeHuang:2018; Spires:2020a].
-
-Many INGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [@Sidel:2016], though there were no clear requirements for them to have a formal legal presence in China [@Han:2011; @HolbigLang:2022; @Yin:2009].
-However, the legal form of foreign-funded company is not quite compatible with the nonprofit nature of INGOs.
-Under the Chinese legal system, enterprises are intended to be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms, including foundations, associations, and social service organizations [@Ye:2021].
-Thus, INGOs obtaining legal identity in this way have to navigate through a legal framework designed for a for-profit institutional logic, e.g, focusing on protecting investors' right to investment returns.
-
-The legal framework governing INGOs was overhauled by the 2017 Chinese ONGO Law.
-The new law applies to all overseas (including Hong Kong, Macau, and Taiwan) non-governmental organizations that conduct not-for-profit activities in the fields of economic development, education, science, technology, culture, public health, sports, environment protection, poverty alleviation, and disaster relief (Article 3).
-The ONGO Law stipulates two ways for INGOs to lawfully conduct nonprofit activities in China: (1) submitting an application for formal permanent registration, or (2) filing documentation of temporary activities with the Ministry of Public Security and provincial-level Public Security Bureaus, which are the registering and regulatory authority for INGOs.
-Formal registration of an RO allows them to maintain an ongoing present in the country, while temporary activities are intended for INGOs that need to conduct one-off programs that last no longer than one year.
-Abiding by these two channels to obtain lawful presence is mandatory for INGOs after the Overseas NGO Law came into effect, any INGOs that could not successfully obtain proper legal authorization would be deemed illegal.
 

### 2023-11-30 manuscript/manuscript.qmd
Update early figures (fixes #21)

@@
 #|   (ROs) or by undertaking specific Temporary Activities (TAs)"
+
 ro_nodes <- tibble(
@@
     "Find an eligible Chinese partner to file paperwork",
-    "Obtain PSU approval",
-    "Channel money through partner’s bank",
+    "File activity information with Public Security Bureau",
     "Keep programming within approved scope",
@@
 )
-ta_edges <- tibble(from = 1:5, to = 2:6)
+ta_edges <- tibble(from = 1:4, to = 2:5)
 ta_graph <- tbl_graph(nodes = ta_nodes, edges = ta_edges)
@@
 #| message: false
-#| fig-cap: "Diagram of our theoretical framework showing three possible determinants of INGO operational flexibility: the contentiousness of the INGO's issue area, the inherent geographic scope of the INGO's operations, and the government's interest in and relationship with the INGO."
+#| fig-cap: "Diagram of our theoretical framework showing three possible determinants of INGO operational space: the contentiousness of the INGO's issue area, the inherent geographic scope of the INGO's operations, and the government's interest in and relationship with the INGO."
 theory_nodes <- tribble(
@@
   1,   "Issue contentiousness", 1, 0, FALSE,
-  2,   "Operational flexibility", 3, 0, TRUE,
+  2,   "Operational space", 3, 0, TRUE,
   3,   "Local focus", 2, 1, FALSE,

### 2023-11-30 R/funs_data.R
Get data from CIVICUS

@@ -1,6 +1,5 @@
 library(glue)
 library(rvest)
-suppressPackageStartupMessages(library(lubridate))
 
 # Helper functions for switching between province counts and proportions
 provinces_to_prop <- function(x, lower = 1, upper = 32) {
@@ -11,17 +10,50 @@ prop_to_provinces <- function(x, lower = 1, upper = 32) {
   (x * (upper - lower)) + lower
 }
 
+load_clean_civicus <- function() {
+  library(countrycode)
+  
+  civicus <- read_html(
+    glue(
+      "http://web.archive.org/web/20230903154216/",
+      "https://monitor.civicus.org/widgets/world/"
+    )) |>
+    html_element(xpath = '//*[@id="countries-list-container"]/div[2]/table') |> 
+    html_table() |>
+    filter(Country != "Greenland") |> 
+    rename(Rating = `Current rating`) |> 
+    mutate(
+      iso3 = countrycode(
+        Country, "country.name", "iso3c",
+        custom_match = c("Kosovo" = "XXK", "Micronesia" = "FSM")
+      ),
+      Score = as.numeric(str_extract(Score, "^(\\d+)/", group = 1)),
+      Rating = factor(
+        Rating,
+        levels = c("Closed", "Repressed", "Obstructed", "Narrowed", "Open"),
+        ordered = TRUE
+      )
+    )
+  
+  return(civicus)
+}
 
 load_clean_chinafile <- function() {
-  chinafile <- read_html(glue("https://web.archive.org/web/20220922181643/",
-                              "https://jessicachinafile.github.io/index_RO_table.html")) |> 
+  chinafile <- read_html(
+    glue(
+      "https://web.archive.org/web/20220922181643/",
+      "https://jessicachinafile.github.io/index_RO_table.html"
+    )
+  ) |>
     html_element(css = "#filter") |>
     html_table() |>
-    select(org_name_cn = `Organization Name (Chinese)`,
-           org_name_en = `Organization Name (English)`) |>
+    select(
+      org_name_cn = `Organization Name (Chinese)`,
+      org_name_en = `Organization Name (English)`
+    ) |>
     group_by(org_name_cn) |>
     slice(1)
-  
+
   return(chinafile)
 }
 

### 2023-11-30 _targets.R

@@ -54,6 +54,7 @@ list(
   tar_target(count_prop_functions, lst(provinces_to_prop, prop_to_provinces)),
 
   ## Process and clean data ----
+  tar_target(civicus_clean, load_clean_civicus()),
   tar_target(chinafile_clean, load_clean_chinafile()),
   tar_target(province_name, province_cn_to_en()),
   tar_target(

### 2023-12-01 manuscript/manuscript.qmd
Finish polishing introduction

@@
 
-knitr::opts_chunk$set(echo = FALSE, include = FALSE, 
-                      warning = FALSE, message = FALSE)
-
-knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
+knitr::opts_chunk$set(
+  echo = FALSE, include = FALSE,
+  warning = FALSE, message = FALSE
+)
+
+knitr::opts_chunk$set(
+  fig.align = "center", fig.retina = 3,
   fig.width = 6, fig.height = (6 * 0.618),
-                      out.width = "100%", collapse = TRUE)
-
-options(digits = 3, width = 120,
+  out.width = "100%", collapse = TRUE
+)
+
+options(
+  digits = 3, width = 120,
   dplyr.summarise.inform = FALSE,
-        knitr.kable.NA = "")
+  knitr.kable.NA = ""
+)
 ```
@@
 library(tidyverse)
+library(sf)
 library(scales)
-library(lubridate)
 library(tidybayes)
-library(sf)
 library(ggrepel)
@@
 library(patchwork)
-library(kableExtra)
 library(gt)
@@
 
-tar_config_set(store = here::here('_targets'),
-               script = here::here('_targets.R'))
-
 # Generated via random.org
@@
 
-# Load targets 
-tar_load(c(ongo, ongo_mapdata))
-tar_load(c(preds_issue, preds_local, preds_timing,
+# Targets stuff
+tar_config_set(
+  store = here::here("_targets"),
+  script = here::here("_targets.R")
+)
+
+tar_load(c(ongo, ongo_mapdata, civicus_clean))
+tar_load(c(
+  preds_issue, preds_local, preds_timing,
   epreds_issue, epreds_local, epreds_timing,
-           epreds_timing_local, issue_indicator_lookup))
+  epreds_timing_local, issue_indicator_lookup
+))
 
@@
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+
+theme_set(theme_ongo())
 set_annotation_fonts()
+```
+
+```{r civicus-stuff}
+civicus_prop <- civicus_clean |> 
+  group_by(open = Score > 80) |> 
+  summarize(total = n()) |> 
+  mutate(
+    prop = total / sum(total),
+    prop_nice = label_percent(accuracy = 1)(prop)
+  ) |> 
+  mutate(open = janitor::make_clean_names(open)) |> 
+  split(~open)
 ```
@@
 
-TODO: Andrew - review all the re-structuring made by Meng
-
-In the past decade, nearly 100 countries have proposed or enacted legal measures designed to restrict civil society [@ICNL:2021], and only 21% of countries have open and unrestricted civic space [@ChaudhryHeiss:2022a; @Civicus:2023].
-This global trend of closing or shrinking civic space [@Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016] has affected countries of all regime types, including both autocracies and democracies such as Morocco and Palestine [@AtiaHerrold:2018], India [@press-trust-india:2019], Vietnam [@Sidel:2023], Canada [@CIVICUS:2013], and the United States [@Cramer:2020].
-On April 28, 2016, China passed its own set of legal restrictions on civil society with its Law of the People's Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China, or "ONGO Law," which formally took effect on January 1, 2017.
-The law requires all international NGOs (INGOs) to either register representative offices (ROs) or file temporary activities to lawfully operate in mainland China.
-
-As an authoritarian state with a growing nonprofit sector, the Chinese model of implementing restrictive laws for international NGOs (INGOs) has important implications for understanding the dynamics of how civil society laws can be used as policy tools to harness the activities of INGOs.
-Globally, theoretical frameworks such as [@DeMattee:2019] focus on the
-institutional approaches, i.e., restrictive laws to crack down international civil society.
-(TO DO: whether to explain INGO vs.
-Civil Society as mentioned by MPSA reviewers).
-To further understanding this global phenomena , China is an important case to explore the impacts such restrictive laws have on the operation of INGOs.
-Such legal restrictions can be either direct (denial of legal access/cannot register) or covert (red-tape, requiring the approval of PSUs, or the uncertainty of having to filing TAs case by case).
-
-This paper explores the characteristics of all registered INGOs in China in the five years after the ONGO Law became effective and examines how the ONGO Law has influenced the population of INGOs that have successfully registered in China, as well as the association between factors such as INGO issue areas and the operational space granted to them in the country.
-Scholars have discussed the discrepancy that can exist between the *de facto* implementation of the law and the formal *de jure* regulations.
-(Andrew TO DO: add literature).
-We engage with this conversation by analyzing a more comprehensive and data-based picture of INGOs operating in China in the post ONGO law era.
-Exploring differentiated application of these laws and differentiated treatment for more vs.
-less contentious INGOs.
-Authoritarian -\> arbitrary and varied application of the law -\> different *operating space*
-
-TODO: Andrew: Also, new cool thing here is that we can look at de facto implementation in greater detail.
-Existing studies use things like V-Dem's core civil society index or civil society repression index to capture the general regulatory environment, but changes in those scores aren't necessarily tied to specific laws.
-Here we can see that differential enforcement/de facto/de jure stuff directly
-
-Our study also contributes to a growing body of research on the effects of closing civic space on INGO behavior and strategies using a mixed-method approach.
-Looking at how civil society laws act as a policy tool that regimes can leverage to shift NGO behavior: to tame INGO to be more cooperative to government.
-The requirement of PSU and Chinese partner to re-direct INGOs to be more authority friendly - The impacts on international civil society we examine include not only access or representation of INGOs in China, but also whether there is change of behaviors [@WuNie:2021].
-In addition to quantitative analysis of the administrative data of 633 registered offices of INGOs.
-We also explored how the relationship with the government and the organizational flexibility of INGOs can come into play under the ONGO law.
-
-TODO: Andrew: Roadmap of paper, to add later In this paper, we first explore the ongoing phenomena of closing civic space and authoritarian regulation of civil society, examining how governments conceptualize the role of international civil society in their domestic politics and why governments select regulatory regimes for international NGOs.
-Term we'll use = operational space, not flexibility ~~We then investigate how international NGOs have responded and adapted to more restrictive regulatory environments and theorize that a key component of INGO regulatory adaptation is the ability to operate with greater latitude in host countries.
-We propose two key determinants of this flexibility: (1) organizational characteristics and (2) host government preferences and relationships TODO and their interplay/interaction.~~ We illustrate this theory using the case of China TODO stats and case studies, mixed method, demonstrating how INGOs that address issues that align with government preferences enjoy the most organizational flexibility in the country.
-
-# The legal framework established by the ONGO law
+In the past two decades, nearly 100 countries have proposed or enacted legal measures designed to restrict nongovernmental organizations (NGOs) and civil society more broadly [@Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016].[^ngo-clarification] According to the CIVICUS Civil Society Monitor, as of 2023 only `r civicus_prop$true$prop_nice` of countries have open and unrestricted civic space [@ChaudhryHeiss:2022a; @CIVICUSMonitor].
+This global trend of closing or shrinking civic space has affected countries of all regime types, including both autocracies and democracies such as Morocco and Palestine [@AtiaHerrold:2018], India [@press-trust-india:2019], Vietnam [@Sidel:2023], Canada [@CIVICUS:2013], and the United States [@Cramer:2020].
+On April 28, 2016, China passed its own set of civil society restrictions with its Law of the People's Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China---or "ONGO Law"---which formally took effect on January 1, 2017.
+The law requires all international NGOs (INGOs) to either establish formal in-country representative offices (ROs) or file short-term temporary activities (TAs) to lawfully operate in mainland China.
+Without recognized legal status, INGOs are prohibited from working in the country, and even with legal recognition, INGO programming is limited to government-approved activities.
+
+[^ngo-clarification]: "Civil society" is a broad concept that includes a range of organizational forms, both formal and informal.
+In this paper, we look at nongovernmental organizations (NGOs), often called nonprofit organizations or third sector organizations—formal non-profit-seeking organizations that are neither privately-owned nor government-controlled.
+We define international NGOs as organizations that conduct work predominantly in at least one other country outside of their home country.
+
+As an authoritarian state with a growing nonprofit sector, China's regulatory regime for INGOs serves as an important example for understanding and exploring how autocracies use restrictive laws as policy tools as they engage with international civil society.
+The restrictive policies implemented by China's 2017 ONGO law serve dueling purposes that both harness the benefits and reduce the risks of INGOs.
+The law is designed to decrease demand for foreign civil society organizations and limit the influence they might have over domestic policies [@DeMattee:2018; @DeMattee:2019], while also allowing the regime to benefit from the expertise, services, and reputational advantages of working partnering with international civil society [@Plantan:2022; @Heiss:2019].
+These dual demands lead to differential enforcement of civil society laws and a divergence between formal *de jure* regulations and the *de facto* implementation of those laws [@ChaudhryHeiss:2022], as the government enforces civil society regulations selectively depending on regime preferences for INGO services.
+
+In this paper, we use the case of China to explore how the dual demands to both restrict and embrace INGOs have shaped the international nonprofit sector in the five years since the 2017 ONGO Law came into effect.
+We examine how the ONGO Law has influenced the population of INGOs that have successfully registered in China, as well as the association between factors such as INGO issue areas and the operational space granted to them in the country.
+Through our study, we make several contributions to a growing body of research on the effects of closing civic space on INGO behavior and strategies.
+First, we expand work that uses institutional approaches to understanding civil society regulations, which argues that states strategically regulate INGOs to maintain regime stability, choosing forms of regulation and repression that minimize threats to internal political stability [@Chaudhry:2022; @DeMattee:2018; @DeMattee:2019; @Heiss:2019].
+Second, we explore how authoritarian civil society regulations act as policy tools that regimes can leverage to shift INGO behavior in their favor and how restrictive laws can reshape and tame organizational strategies [@Li:2020; @WuNie:2021; @LianMurdie:2023].
+Third, we build on work by @LiFarid:2023 to explore how, as policy tools, these regulations lead to differentiated application of the law depending on organizational characteristics.
+We argue that INGO issue areas, missions, and pre-existing relationships with local government officials influence the degree of operating space available for INGOs.
+
+By focusing on INGO operational space in China, we provide a unique view into the *de facto* regulatory environment for foreign civil society in an authoritarian state.
+Many previous studies use broad indexes of civil society openness, such as the core civil society index from the Varieties of Democracy project [@LianMurdie:2023; @ChaudhryHeiss:2022].
+These measures capture the general regulatory environment for all civil society—including domestic NGOs, INGOs, and informal organizations—but do not reflect the specific implementation of laws for INGOs.
+In this paper, though, we use a mixed methods approach to explore the regulatory environment for INGOs in particular, providing much a richer description of authoritarian regulation of international civil society.
+
+Below, we provide a brief overview of China's 2017 ONGO Law and the different regulatory mechanisms—and practical limitations—it provides for INGOs to obtain legal access to the country.
+We then summarize existing research on authoritarian regulation of INGOs and the differential application of these laws based on regime preferences and organizational characteristics, and propose a set of empirical expectations based on this literature.
+We test these expectations with a mixed methods research design, combining Bayeisan analysis of administrative data from 633 formally registered INGOs with a comparative case study of Greenpeace and The Nature Conservancy, two INGOs working on similar issue areas which took different approaches to operating in China after 2017.
+We conclude with a broader discussion of authoritarian civil society regulations and propose future methods for exploring the practical operating environment for INGOs working in such regimes.
+
+# The legal framework established by the 2017 ONGO law
 
@@
 However, the actual application of the regulation was very limited.
-Up until the ONGO Law took effect in 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs, while some Chinese officials estimated in 2016 that there were roughly over 7,000 INGOs operating in China [@YeHuang:2018; Spires:2020a].
+Up until the ONGO Law took effect in 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs, while some Chinese officials estimated in 2016 that there were roughly over 7,000 INGOs operating in China [@YeHuang:2018; @Spires:2020a].
 
@@
     "Open organization bank accounts",
+    "Submit annual work plans to PSU and Public Security Bureau",
     "Keep programming within approved scope",
-    "Submit annual work plans to PSU and Public Security Bureau",
     "Submit annual reports to PSU and Public Security Bureau"
@@
 TODO: Meng - China crackdown lit
+
+@LiFarid:2023
+
+Such legal restrictions can be either direct (denial of legal access/cannot register) or covert (red-tape, requiring the approval of PSUs, or the uncertainty of having to filing TAs case by case).
 
@@
 We use this temporal variable as a proxy for the motivation or eagerness of INGOs to register an RO, for some INGOs are inclined to avoid the cumbersome registration procedures at the early stage if there is no real consequences for continuing operations without registration, while others took the time to talk with multiple potential PSUs to find a more suitable superior or regulatory dynamic.
-(to find a citation for this, probably Spires, if there is one.)
+(TODO: find a citation for this, probably Spires, if there is one.)
 

### 2023-12-01 manuscript/manuscript.qmd
Tighten up legal background section

@@
 
-International NGOs began to play an important role in China in the early 1990s as part of the country's Reform and Opening-Up policy, and organizations like Save the Children and the Ford Foundation established local offices and branches.
+International NGOs began to play an important role in China in the early 1990s as part of the country's Reform and Opening-Up policy, and organizations sucg as Save the Children and the Ford Foundation established local offices and branches.
 Since then, INGOs and global civil society have played pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China's domestic nonprofit sector [@Yin:2009].
-Prior to the implementation of the 2017 ONGO Law, regulation of INGOs in China was obscure [@Shieh:2018; @Spires:2022].
+Prior to the implementation of the 2017 ONGO Law, regulation of INGOs in China was ambiguous [@Shieh:2018; @Spires:2022].
 The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations by the State Council that specifies the registration of representative offices ("ROs") of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic NGOs.
-However, the actual application of the regulation was very limited.
-Up until the ONGO Law took effect in 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs, while some Chinese officials estimated in 2016 that there were roughly over 7,000 INGOs operating in China [@YeHuang:2018; @Spires:2020a].
-
-Many INGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [@Sidel:2016], though there were no clear requirements for them to have a formal legal presence in China [@Han:2011; @HolbigLang:2022; @Yin:2009].
-However, the legal form of foreign-funded company is not quite compatible with the nonprofit nature of INGOs.
-Under the Chinese legal system, enterprises are intended to be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms, including foundations, associations, and social service organizations [@Ye:2021].
-Thus, INGOs obtaining legal identity in this way have to navigate through a legal framework designed for a for-profit institutional logic, e.g, focusing on protecting investors' right to investment returns.
+However, the actual application of the regulation was very limited: until the ONGO Law took effect in 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs, while some Chinese officials estimated in 2016 that there were roughly over 7,000 INGOs operating in China [@YeHuang:2018; @Spires:2020a].
+
+Many INGOs gained legal status within mainland China by registering as foreign-funded companies [@Sidel:2016], though there were no clear requirements to have a formal legal presence in China [@Han:2011; @HolbigLang:2022; @Yin:2009].
+However, the legal form of foreign-funded company is not quite compatible with the non-profit-distributing nature of INGOs.
+Under the Chinese legal system, enterprises were intended to be for-profit entities while nonprofit organizations were required to choose other standalone legal forms, such as foundations, associations, and social service organizations [@Ye:2021].
+Thus, INGOs obtaining legal status had to navigate a legal framework designed for a for-profit institutional logic, which often conflicted with nonprofit characteristics like their lack of private investment returns.
 
 The legal framework governing INGOs was overhauled by the 2017 Chinese ONGO Law.
-The new law applies to all overseas (including Hong Kong, Macau, and Taiwan) non-governmental organizations that conduct not-for-profit activities in the fields of economic development, education, science, technology, culture, public health, sports, environment protection, poverty alleviation, and disaster relief (Article 3).
-The ONGO Law stipulates two ways for INGOs to lawfully conduct nonprofit activities in China: (1) submitting an application for formal permanent registration, or (2) filing documentation of temporary activities with the Ministry of Public Security and provincial-level Public Security Bureaus, which are the registering and regulatory authority for INGOs.
-Formal registration of an RO allows them to maintain an ongoing present in the country, while temporary activities are intended for INGOs that need to conduct one-off programs that last no longer than one year.
-Abiding by these two channels to obtain lawful presence is mandatory for INGOs after the Overseas NGO Law came into effect, any INGOs that could not successfully obtain proper legal authorization would be deemed illegal.
-
-Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus.
-Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018].
-INGOs vary in their ability to attract partner PSUs, and organizations that are unable to find corresponding PSUs are more limited in their geographic reach within the country.
-INGOs are authorized to operate within China on a province-by-province basis.
-Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.
-We use the number of provinces that INGOs are authorized to work in as a proxy to measure the operational space for INGOs in China based on the assumption that INGOs need to or hope to have the approval to be able to carry out their programs in a geographical scope as large as possible [@Li:2020].
-
-TODO: Meng - add brief explanations of the TA/RO pathways figure in @fig-ro-ta-pathways and articulate the "cooperative requirements part", i.e., seeking a psu or Chinese partner
+The new law applies to all overseas (including Hong Kong, Macau, and Taiwan) non-governmental organizations that conduct not-for-profit activities in the fields of economic development, education, science, technology, culture, public health, sports, environment protection, poverty alleviation, and disaster relief.
+The ONGO Law provides two pathways for INGOs to lawfully conduct nonprofit activities in China (see @fig-ro-ta-pathways): (1) submitting an application for formal permanent registration as ROs, or (2) filing documentation of temporary activities (TAs) with the Ministry of Public Security and provincial-level Public Security Bureaus.
+Formal registration as an RO allows INGOs to maintain an ongoing presence in the country, while TAs are intended for INGOs that need to conduct one-off programs that last no longer than one year.
+Using one of these two channels to obtain legal status became mandatory in 2017 and any INGOs that could not successfully obtain proper legal authorization were deemed illegal.
 
@@
 ```
+
+Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus.
+Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018].
+INGOs that are unable to find a PSU willing to support their proposed programming are unable to work in the country.
+The mechanisms of the ONGO Law thus provide the government with latitude to selectively partner with INGOs that align with regime preferences while providing layers of oversight and control.
 
@@
 
-Our dependent variable is the count of the total number of provinces each INGO is authorized to operate in.
-We derived this variable from the specific list of authorized provinces as recorded in the RO's registration documentation.
-As discussed above, we use this measurement as a proxy for operational space for INGOs, because any geographical constraints on the RO impacts on the flexibility of the INGO operations.
-For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas would need their service.
-Thus, we assume INGOs that are not set up with any locally-bound purposes would need to or hope to (if there is not yet such need) be able to operate in as broad a geographical scope as possible.
+As seen previously, INGOs must partner with professional supervisory units (PSUs) to become ROs.
+Organizations vary in their ability to attract partner PSUs, and INGOs that are unable to find corresponding PSUs are more limited in their geographic reach within the country.
+INGOs are authorized to operate within China on a province-by-province basis.
+Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.
+We use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that INGOs need to or hope to be able to carry out their programs in as broad a geographical scope as possible [@Li:2020].
+For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas might need their service.
+Having the potential to shift programs to other provinces as needed thus provides a form of operational space.
 
@@
 Given there is certain level of subjectivity in the coding process, the coding of issue areas are cross-checked between the researchers---Author 1 assigned each organization into one of the issue areas defined in Article 3 of the ONGO Law, and Author 2 cross-checked the coding for ambiguous cases.
-We include our coding rules for overlapping issue areas in the appendix (in the future).
+We include our coding rules for overlapping issue areas in the appendix (TODO).
 We categorize each organization into one of the following nine issue areas:

### 2023-12-01 manuscript/manuscript.qmd
Start streamlining theory section

@@
 Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018].
-INGOs that are unable to find a PSU willing to support their proposed programming are unable to work in the country.
-The mechanisms of the ONGO Law thus provide the government with latitude to selectively partner with INGOs that align with regime preferences while providing layers of oversight and control.
+
+Organizations vary in their ability to attract partner PSUs, and INGOs that are unable to find corresponding PSUs are more limited in their geographic reach within the country.
+INGOs are authorized to operate within China on a province-by-province basis.
+Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.
+In this paper, we use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that INGOs need to or hope to be able to carry out their programs in as broad a geographical scope as possible [@Li:2020].
+For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas might need their service.
+Having the potential to shift programs to other provinces as needed thus provides a form of operational space.
 
@@
 
+In 2018, @BatkeHang:2018 posited that the ONGO law was showing signs of reorienting the missions of legally recognized INGOs and the overall scope of international civil society to be more explicitly aligned with government preferences.
+@HolbigLang:2022 recently confirmed this prediction, finding that the issue areas addressed by legally recognized INGOs have "shift\[ed\] towards fields of activity high up the government's domestic policy agenda" [-@HolbigLang:2022, p.
+587].
+
 # Empirical expectations and analytical approach
@@
 TODO: Andrew: I'll clean up this section
+
+Operational space is determined by the interaction between NGO characteristics and regime preferences
 
@@
 
-In 2018 Batke and Hang posited that the ONGO law was showing signs of reorienting the missions of legally recognized INGOs and the overall scope of international civil society to be more explicitly aligned with government preferences.
-@HolbigLang:2022 recently confirmed this prediction, finding that the issue areas addressed by legally recognized INGOs have "shift\[ed\] towards fields of activity high up the government's domestic policy agenda" [-@HolbigLang:2022, p.
-587].
-
 Following our theory, government preferences thus directly influence INGO issue areas, which in turn shapes the amount of flexibility enjoyed by the INGO.
@@
 
-As seen previously, INGOs must partner with professional supervisory units (PSUs) to become ROs.
-Organizations vary in their ability to attract partner PSUs, and INGOs that are unable to find corresponding PSUs are more limited in their geographic reach within the country.
-INGOs are authorized to operate within China on a province-by-province basis.
-Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.
-We use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that INGOs need to or hope to be able to carry out their programs in as broad a geographical scope as possible [@Li:2020].
-For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas might need their service.
-Having the potential to shift programs to other provinces as needed thus provides a form of operational space.
+As seen previously, INGOs must partner with professional supervisory units (PSUs) to become ROs. TODO describe the province count variable
 
@@
 Our final independent variable measures how much time elapsed between the January 1, 2017 (when the law took effect) and the organization's official registration date.
-There is great variance in the timing of registering an RO among INGOs, since there has been a *de facto* grace period for INGOs to seek legal presence after the law took effect[@Shieh:2018].
+There is great variance in the timing of registering an RO among INGOs, since there has been a *de facto* grace period for INGOs to seek legal presence after the law took effect [@Shieh:2018].
 This is largely because both INGOs and the regulators needed some transitional time to explore the specific implementation of the law as large ambiguity was left when the law was passed.
@@
 
-@eq-ordbeta provides a formal definition of our modeling choices.
 Since we are primarily interested in how an INGO's issue area, its local connections, and the timing of its registration after January 2017, we include these as explanatory variables.
-We also include province-specific random offsets for each intercept to account for between-region differences in how INGOs are regulated, since every RO is overseen by provincial-level Public Security Bureaus.
-We use weakly informative priors for all model parameters.
-
-::: column-page-inset
+We also include random province intercepts to account for between-region differences in how INGOs are regulated, since every RO is overseen by provincial-level Public Security Bureaus.
+We use the following model and priors (see appendix TODO for more details):
+
 $$
@@
 &\ \textbf{Model of outcome average} \\
-% Put the huge equation in a nested \begin{aligned}[t] environment so that 
-% \mathrlap{} can go around it so that the annotations in the priors can be 
-% aligned closer to the math
 \mu_i =&\ 
@@
 \end{aligned}
-$$ {#eq-ordbeta}
-:::
+$$
 
@@
 :::
+
+\newpage
+
+:::: {#appendix-count}
+
+# Appendix
+
+::::

### 2023-12-01 manuscript/manuscript.qmd
Add table of issue areas + example organizations

@@
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+invisible(list2env(tar_read(table_functions), .GlobalEnv))
 
@@
 We include our coding rules for overlapping issue areas in the appendix (TODO).
-We categorize each organization into one of the following nine issue areas:
-
--   **Economy and trade**
--   **Environment** (including animal protection)
--   **Education** (including youth development)
--   **Charity and humanitarian** poverty alleviation, disaster relief, etc., including rural development
--   **Science and technology**
--   **Industry association**
--   **Health**, public health and health care system support (professional training)
--   **Arts and Culture** including sports and international culture exchange
--   **General**, usually grant-making organizations, or working on general international communication, including among governments, or working on multiple fields not overlapping
+We categorize each organization into nine different issue areas (see @tbl-issues).
+
+::: {#tbl-issues}
+
+```{r}
+#| label: table-issues
+#| include: true
+tribble(
+  ~Issue, ~Examples,
+  "Arts and culture", "World Dance Council; Special Olympics",
+  "Charity and humanitarian", "Save the Children; Half the Sky Foundation",
+  "Economy and trade", "World Economic Forum; Chile-China Chamber of Commerce",
+  "Education", "Children’s Education Foundation; BSK International",
+  "Environment", "The Nature Conservancy; World Wide Fund for Nature",
+  "General", "Bill and Melinda Gates Foundation; Ford Foundation",
+  "Health", "American Heart Association; Operation Smile",
+  "Industry association", "World Cement Association; Colombian Coffee Growers Federation",
+  "Science and technology", "Royal Aeronautical Society; American Society of Civil Engineers"
+) |> 
+  gt() |> 
+  tab_footnote(
+    footnote = "Includes poverty alleviation, disaster relief, rural development, etc.",
+    locations = cells_body(columns = Issue, rows = 2)
+  ) |> 
+  tab_footnote(
+    footnote = "Includes grant-making organizations, organizations working on general international communication, and organizations working on multiple non-overlapping issues",
+    locations = cells_body(columns = Issue, rows = 6)
+  ) |> 
+  cols_width(Issue ~ gt_pct(20), Examples ~ gt_pct(50)) |> 
+  tab_style(
+    style = cell_text(v_align = "top"),
+    locations = cells_body()
+  ) |>
+  opts_theme() |> 
+  tab_options(
+    quarto.disable_processing = TRUE
+  )
+```
+
+Possible INGO issue areas and example organizations
+
+:::
 

### 2023-12-01 R/fun_tables.R

@@ -9,3 +9,30 @@ opts_theme <- function(x) {
     tab_options(column_labels.font.weight = "bold",
       row_group.font.weight = "bold")
 }
+
+gt_linebreak <- function(x) {
+  if (fmt_out == "latex") {
+    x %>% 
+      str_replace_all("\\[", "{[}") %>% 
+      str_replace_all("\\]", "{]}") %>% 
+      kableExtra::linebreak(align = "c")
+  } else {
+    str_replace(x, "\\n", "<br>")
+  }
+}
+
+fmt_markdown_latex <- function(x, columns) {
+  if (fmt_out == "latex") {
+    fmt_passthrough(x, columns = columns, escape = FALSE)
+  } else {
+    fmt_markdown(x, columns = columns)
+  }
+}
+
+gt_pct <- function(x, page_width = 6) {
+  if (knitr::pandoc_to("latex")) {
+    paste0(page_width * (x / 100), "in")
+  } else {
+    gt::pct(x)
+  }
+}

### 2023-12-01 _targets.R

@@ -50,7 +50,7 @@ list(
     theme_ongo, set_annotation_fonts, clrs, 
     prop_to_provinces, provinces_to_prop)
   ),
-  tar_target(table_functions, lst(opts_int, opts_theme)),
+  tar_target(table_functions, lst(opts_int, opts_theme, gt_linebreak, gt_pct, fmt_markdown_latex)),
   tar_target(count_prop_functions, lst(provinces_to_prop, prop_to_provinces)),
 
   ## Process and clean data ----

### 2023-12-01 manuscript/manuscript.qmd
Make Taiwan gray + use better interior border lines

@@
 #| echo: false
-#| fig-cap: "Count of international NGO registrations, divided by issue area"
+#| fig-cap: "Count of registered organizations across provinces"
+# Extract the intersections of provinces so that we don't plot the outside
+# borders and distort the coastlines. See https://stackoverflow.com/a/57138069 
+# and https://ikashnitsky.phd/2023/map-borders/
+interior_borders <- st_intersection(ongo_mapdata) %>% 
+  filter(n.overlaps > 1) |> 
+  # Remove weird points that st_intersection() adds
+  filter(!(st_geometry_type(geometry) %in% c("POINT", "MULTIPOINT")))
+
 # Use aes(geometry) and stat = "sf_coordinates" to make geom_label_repel() work
@@
 ggplot() +
-  geom_sf(data = ongo_mapdata, aes(fill = ro_count), 
-          linewidth = 0.3, color = "white") +
-  scale_fill_distiller(palette = "Reds", direction = 1, guide = "none") +
-  geom_label_repel(data = filter(ongo_mapdata, ro_count > 0), 
+  geom_sf(data = ongo_mapdata, aes(fill = ro_count), color = NA) +
+  geom_sf(data = interior_borders, linewidth = 0.3, color = "white") +
+  scale_fill_distiller(palette = "Reds", direction = 1, guide = "none", na.value = "gray80") +
+  geom_label_repel(
+    data = filter(ongo_mapdata, ro_count > 0),
     aes(label = ro_count, geometry = geometry),
-                   stat = "sf_coordinates", seed = 1234, label.size = 0.1, size = 3,
-                   segment.color = "black", segment.size = 0.5, min.segment.length = 0) +
+    stat = "sf_coordinates", seed = 1234, label.size = 0.05, size = 3,
+    color = "black", fill = scales::alpha("white", 0.7),
+    segment.color = "black", segment.size = 0.25, min.segment.length = 0
+  ) +
   coord_sf(crs = st_crs("EPSG:4480")) +  # China Geodetic Coordinate System 2000

### 2023-12-01 R/funs_data.R

@@ -118,9 +118,13 @@ clean_map_data <- function(ongo) {
     summarise(ro_count = n())
   
   # Join ONGO count to map
-  mapdata <- sf_china |>  
+  mapdata <- sf_china |>
     left_join(province_count, by = "province_cn") |> 
-    mutate(ro_count = ifelse(is.na(ro_count), 0, ro_count))
+    mutate(ro_count = ifelse(is.na(ro_count), 0, ro_count)) |> 
+    mutate(
+      is_taiwan = province_cn == "台湾",
+      ro_count = ifelse(is_taiwan, NA, ro_count)
+    )
   
   return(mapdata)
 }

### 2023-12-01 R/funs_graphics.R

@@ -2,6 +2,7 @@ clrs <- MetBrewer::met.brewer("Tam")
 
 set_annotation_fonts <- function() {
   ggplot2::update_geom_defaults("label", list(family = "IBM Plex Sans Condensed", fontface = "plain"))
+  ggplot2::update_geom_defaults("label_repel", list(family = "IBM Plex Sans Condensed", fontface = "plain"))
   ggplot2::update_geom_defaults("text", list(family = "IBM Plex Sans Condensed", fontface = "plain"))
 }
 

### 2023-12-01 manuscript/manuscript.qmd
Add case study

@@
 
-TODO: Meng
-
-Paragraph justifying why the case study is needed - stats are cool but missing details about contentiousness of issues - also, stats only look at ROs, not TAs or any ONGOs that left the country, so we're missing some dynamics of ONGO-government relations.
-We can explore our empirical expectations in more depth by looking at a comparative case study of Greenpeace and NC
-
-Education, Environment, lower expected operating space
-
-So Issue areas can predict some level of flexibility/restrictions INGOs receive, but that is not the full story, the relations with the government (one more dimension/variable) also plays important roles, see TNC vs.
-Greenpeace
-
-TODO: Meng - TA vs. RO, exploring main mechanisms of contentiousness and relationships
+We also conducted the qualitative study of two selected cases of INGOs in China to further understand the patterns revealed in the quantitative modeling and to examine a more comprehensive picture of how the operations of INGOs have been impacted by the ONGO Law.
+As explained, the registration documentation data enables us to analyze how the operational space is associated with issue areas and other factors for those INGOs that could successfully register.
+However, for INGOs that could not get registered but try to maintain their legal presence in China, a typical choice would be constantly filing temporary activities [@Corsetti:2019].
+So, we purposefully selected two environmental INGOs with different registration status to conduct a comparative analysis.
+One of them, the Nature Conservancy (“TNC”), successfully registered a RO under the ONGO Law, while the other INGO, Greenpeace has been filing temporary activities one after another since 2017 to continue carrying out programs in China.
+We use secondary data including public interviews (previously conducted by one of the authors) and their websites, in addition to official ONGO Law records of ROs and temporary activities to conduct the case studies.
+
+TNC and Greenpeace are both well-known INGOs working in the environmental issue area.
+Their headquarters are based in western countries and have offices around the world.
+They started to have long-standing offices in Beijing around the turn of the century, with TNC in 1998 and Greenpeace in 2001.
+Despite these similarities, the two INGOs had quite different experiences to sustain their legal presence in China after the ONGO Law took effect.
+According to records by the MPS, TNC’s RO was registered on May 19, 2017, with the National Forestry and Grassland Administration as their PSU.
+The RO in Beijing is eligible to operate in 27 provinces.
+Comparatively, Greenpeace has not registered any RO as of December 1, 2023.
+Instead, they have filed  67 temporary activities, almost going through the filing process 10 times each year.
+
+There are various drawbacks to having to constantly file temporary activities.
+First would be high administrative costs.
+Since the filing of temporary activities needs to be submitted by INGOs’ Chinese partners, it would mean discussing and securing the partnerships 67 times, mostly with different organizations.
+Moreover, this model also imposes high uncertainty to the operation of INGOs.
+There is no guarantee whether the next Chinese partner would agree to collaborate and file the documentation for them.
+And it is impossible to run longer-term projects, given all temporary activities cannot last longer than a year.
+Finally, temporary activities would be programs Chinese partners feel comfortable to collaborate in, i.e., safe activities with little political and administrative risks.
+So there is less flexibility in the kinds of work an INGO can with temporary activities.
+
+What factors could have contributed to the contrasting experiences of TNC and Greenpeace under the ONGO Law?
+After analyzing the data, the working approach and relationship with the government emerged as pivotal differences between the two INGOs, which fits existing discussions on the differential treatment of INGOs based on their relationship with the authority [TO DO: add citations].
+In a public interview with TNC’s RO in China about their registration experience, the chief representative stated TNC’s working approach in China has been “science-based”, using “non-confrontational, collaborative approach in working closely with governments, the business community and others” [@ChinaPhilanthropyReserchInstitute:2018a].
+Over the years, they have provided technical support for the central government and local governments like the Yunnan and Zhejiang Province to build national parks and nature reserve areas and helped drafted such documents as the China Biodiversity Conservation Strategy and Action Plan (2011-2030).
+Using the non-confrontational working model and establishing long partnerships with the government enabled TNC to secure the content of a national governmental agency in corresponding issue area to be their PSU, and thus successfully got registered and authorized to operate in relatively large number of provinces.
+In contrast, Greenpeace states in their mission that they work as “independent campaigning organizations that use peaceful protest and creative confrontation to expose global environmental problems”.
+Their description of the work in China also uses such key words as “brings change”, “non-violent direct action”, and “impartiality and independence”.
+One project Greenpeace shares on their website their exposure of the damages the company Sinar Mas Group's did in southwest Yunnan back in 2004.
+The conducted three rounds of  independent investigation and later revealed that the multinational paper industry company used reforestation as a cover while actually logging Yunnan's natural forests.
+Although this confrontation was not with the government, it showcases Greenpeace’s investigative, watch dog like work stance.
+To the authority, it would mean less predictable and manageable.
+
+::: {#tbl-case-study}
+
+```{r}
+#| label: table-case-study
+#| include: true
+
+compare_table <- read_csv("data/manual_data/table_case_study.csv")
+
+compare_table |> 
+  gt() |> 
+#  cols_width(Issue ~ gt_pct(20), Examples ~ gt_pct(50)) |> 
+  tab_style(
+    style = cell_text(v_align = "top"),
+    locations = cells_body()
+  ) |>
+  opts_theme() |> 
+  tab_options(
+    quarto.disable_processing = TRUE
+  )
+```
+
+Comparison of the work of The Nature Conservancy and Greenpeace in China
+
+:::
+
+@table-case-study summarizes the comparison of the cases of TNC and Greenpeace.
+The case study shows that in addition to the correlation of issue area and operational space found in the quantitative model, the dimension of relationship with the government also exerts influence on the contentious level and restrictions INGOs can face, revealing the potential patterns of differential treatment INGOs can receive in the *de facto* implementation of the law.
+Greenpeace also showed high organizational flexibility in the face of high legal barriers with the ONGO law : despite the various drawbacks discussed above, they were still able to keep conducting programs in China.
+A more evasive group of INGOs after the ONGO law would be those not having the same level of flexibility as Greenpeace and have left China either not choosing to seek registration or failed to do so and not able file temporary activities constantly.
+The variance in organizational flexibility can be worthy of further research.
 

### 2023-12-02 manuscript/manuscript.qmd
Rearrange theoretical framework figure

--- 2023-12-01 manuscript/manuscript.qmd
@@
 Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018].
-
 Organizations vary in their ability to attract partner PSUs, and INGOs that are unable to find corresponding PSUs are more limited in their geographic reach within the country.
@@
 Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.
-In this paper, we use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that INGOs need to or hope to be able to carry out their programs in as broad a geographical scope as possible [@Li:2020].
-For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas might need their service.
-Having the potential to shift programs to other provinces as needed thus provides a form of operational space.
-
-# Theoretical background
-
-TODO: Andrew: This 2017 law fits with a broader global phenomenon of closing civic space... General crackdown stuff + China crackdown stuff + our addition
-
-TODO: Andrew: I'll clean up/rewrite this section and the section headings, etc.
-
-## The "closing space" phenomenon - Institutional approach to closing space
+
+# Closing space, differential enforcement, and INGO operational space
+
+The 2017 ONGO Law's provision of two legal pathways for registration is an example of administrative crackdown [@Chaudhry:2022] an example of fit within the broader global phen
+
+Why crack down?
+
+Many different reasons for these restrictions and several purposes - INGOs pose a threat to regime stability, but they also provide governments with services and technical expertise.
+Civil society/CSO/NGO + host government definition - De Mattee and institutional taxonomy.
+My stuff on gatekeeping vs.
+program capture.
+
+Contentiousness, regime stability, other reasons [see @Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016].
+
+To situate our analysis of the impacts of China's ONGO Law in existing work on closing civic space, we propose a theoretical framework to explain
+
+---
 
@@
 
-Many different reasons for these restrictions and several purposes - INGOs pose a threat to regime stability, but they also provide governments with services and technical expertise.
-Civil society/CSO/NGO + host government definition - De Mattee and institutional taxonomy.
-My stuff on gatekeeping vs.
-program capture.
-
-Contentiousness, regime stability, other reasons [see @Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016].
+The government can thus use the RO registration process to limit the potential reach of INGOs.
+
+In this paper, we use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that INGOs need to or hope to be able to carry out their programs in as broad a geographical scope as possible [@Li:2020].
+For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas might need their service.
+Having the potential to shift programs to other provinces as needed thus provides a form of operational space.
+
+TODO: Andrew: This 2017 law fits with a broader global phenomenon of closing civic space... General crackdown stuff + China crackdown stuff + our addition
+
+TODO: Andrew: I'll clean up/rewrite this section and the section headings, etc.
 
@@
 
-```{r fig-theory, fig.width=6, fig.height=2}
+```{r fig-theory, fig.width=6, fig.height=1.75}
 #| echo: false
@@
   ~id, ~name, ~x, ~y, ~highlight,
-  1,   "Issue contentiousness", 1, 0, FALSE,
-  2,   "Operational space", 3, 0, TRUE,
-  3,   "Local focus", 2, 1, FALSE,
-  4,   "Government preferences", 2, -1, FALSE
+  1,   "Issue contentiousness", 2, 1, FALSE,
+  2,   "Operational space", 2, 0, TRUE,
+  3,   "Local focus", 3, 1, FALSE,
+  4,   "Government preferences", 1, 1, FALSE
 )
@@
     aes(
-      start_cap = label_rect(node1.name, padding = margin(10, 5, 10, 5, "pt")),
-      end_cap = label_rect(node2.name, padding = margin(10, 5, 10, 5, "pt"))
+      start_cap = label_rect(node1.name, padding = margin(10, 0, 10, -05, "pt")),
+      end_cap = label_rect(node2.name, padding = margin(10, -5, 10, -5, "pt"))
     ),
@@
   ) +
-  scale_x_continuous(expand = expansion(add = 0.3)) +
+  scale_x_continuous(expand = expansion(add = 0.4)) +
   scale_y_continuous(expand = expansion(add = 0.2)) +

### 2023-12-02 manuscript/manuscript.qmd
change to my non-student email and correct some typos

@@
   affiliation: Georgia State University
-  email: mye2@student.gsu.edu
+  email: mye2@gsu.edu
   orcid: 0000-0002-6552-8338
@@
 Over the years, they have provided technical support for the central government and local governments like the Yunnan and Zhejiang Province to build national parks and nature reserve areas and helped drafted such documents as the China Biodiversity Conservation Strategy and Action Plan (2011-2030).
-Using the non-confrontational working model and establishing long partnerships with the government enabled TNC to secure the content of a national governmental agency in corresponding issue area to be their PSU, and thus successfully got registered and authorized to operate in relatively large number of provinces.
+Using the non-confrontational working model and establishing long partnerships with the government enabled TNC to secure the consent of a national governmental agency in corresponding issue area to be their PSU, and thus successfully got registered and authorized to operate in a relatively large number of provinces.
 In contrast, Greenpeace states in their mission that they work as “independent campaigning organizations that use peaceful protest and creative confrontation to expose global environmental problems”.
 Their description of the work in China also uses such key words as “brings change”, “non-violent direct action”, and “impartiality and independence”.
-One project Greenpeace shares on their website their exposure of the damages the company Sinar Mas Group's did in southwest Yunnan back in 2004.
-The conducted three rounds of  independent investigation and later revealed that the multinational paper industry company used reforestation as a cover while actually logging Yunnan's natural forests.
-Although this confrontation was not with the government, it showcases Greenpeace’s investigative, watch dog like work stance.
+One project Greenpeace shares on their website was the exposure of the damages the company Sinar Mas Group's did in southwest Yunnan back in 2004.
+They conducted three rounds of  independent investigations and later revealed that the multinational paper industry company used reforestation as a cover while actually logging Yunnan's natural forests.
+Although this confrontation was not with the government, it showcases Greenpeace’s investigative, watchdog like work stance.
 To the authority, it would mean less predictable and manageable.

### 2023-12-02 manuscript/manuscript.qmd
Minor edits to case study table + add table to repo

@@
 #|   connections. Shaded regions show the 50%, 80%, and 95% credible intervals"
+
 epreds_timing_local |>
@@
 
-compare_table <- read_csv("data/manual_data/table_case_study.csv")
+compare_table <- read_csv(here::here("data", "manual_data", "table-case-study.csv"))
 
 compare_table |> 
-  gt() |> 
-#  cols_width(Issue ~ gt_pct(20), Examples ~ gt_pct(50)) |> 
+  gt(rowname_col = "Characteristic") |> 
+  cols_width(Characteristic ~ gt_pct(20), everything() ~ gt_pct(30)) |>
   tab_style(
@@
   ) |>
+  tab_style(
+    style = cell_text(v_align = "top", weight = "bold"),
+    locations = cells_stub()
+  ) |>
   opts_theme() |> 
@@
 
-@table-case-study summarizes the comparison of the cases of TNC and Greenpeace.
+@tbl-case-study summarizes the comparison of the cases of TNC and Greenpeace.
 The case study shows that in addition to the correlation of issue area and operational space found in the quantitative model, the dimension of relationship with the government also exerts influence on the contentious level and restrictions INGOs can face, revealing the potential patterns of differential treatment INGOs can receive in the *de facto* implementation of the law.

### 2023-12-03 manuscript/manuscript.qmd
Update legal and DV section

@@
 Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018].
-Organizations vary in their ability to attract partner PSUs, and INGOs that are unable to find corresponding PSUs are more limited in their geographic reach within the country.
+Organizations vary in their ability to attract partner PSUs, and INGOs that are unable to find suitable PSUs can end up not being able to registered or registered with great limitation in terms of work areas and geographical reach.
 INGOs are authorized to operate within China on a province-by-province basis.
@@
 
-As seen previously, INGOs must partner with professional supervisory units (PSUs) to become ROs. TODO describe the province count variable
+As explained, the dependent variable is the count of provinces that INGOs are authorized to work in as documented in their official registration record.
+The documentation lists the specific provincial regions each INGO RO can conduct activities in and we derive the number of provinces based on the lists.
+Since the maximum count of provinces INGOs can possibly work in is 32, this variable ranges from 1 to 32.
 
@@
 
-# Contentiousness and government relationships: The cases of Greenpeace and The Nature Conservancy
+# Contentiousness and government relationships: The cases ofThe Nature Conservancy and Greenpeace
 

### 2023-12-03 manuscript/manuscript.qmd
Start big cleanup/consolidation of lit review/theory/expectations sections

@@
 
-# Closing space, differential enforcement, and INGO operational space
-
-The 2017 ONGO Law's provision of two legal pathways for registration is an example of administrative crackdown [@Chaudhry:2022] an example of fit within the broader global phen
-
-Why crack down?
-
-Many different reasons for these restrictions and several purposes - INGOs pose a threat to regime stability, but they also provide governments with services and technical expertise.
-Civil society/CSO/NGO + host government definition - De Mattee and institutional taxonomy.
-My stuff on gatekeeping vs.
-program capture.
-
-Contentiousness, regime stability, other reasons [see @Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016].
-
-To situate our analysis of the impacts of China's ONGO Law in existing work on closing civic space, we propose a theoretical framework to explain
-
----
-
-China's 2017 ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down on international NGOs [@ChaudhryHeiss:2022; @Carothers:2016].
-Studies on the law has been focused on discussing the historical and political impetus of passing the law [@Shieh:2018] or analyzing the regulatory regimes it that has established and potential implications for INGOs operating in China [@Feng:2017; @TeetsHsu:2016].
-However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs' operations and projects have been affected by the law after successfully gaining legal registration and documentation.
-A few studies [@Jia:2017; @YeHuang:2018] have reflected on the implementation of the ONGO Law after its first year, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations.
-However, a more up-to-date and comprehensive understanding of the effects of the ONGO law is still lacking.
-
-This paper aims to fill these gaps by empirically examining how the "closing space" hypothesis applies to China in the years after the ONGO Law took effect.
-China provides an excellent setting for testing these theories because China's promulgation of restrictive INGO law as an authoritarian jurisdiction fits the observed global trends in recent years, thus can serve as an representative case to deepen scholarly understanding around these themes.
-Also, the level of ambiguity of the legal framework gives ample room for arbitrary discretion and conflicting attitudes by authorities [@Jia:2017], enabling us to analyze rules in form (*de jure*) as well as rules in use (*de facto*).
-
-The government can thus use the RO registration process to limit the potential reach of INGOs.
-
-In this paper, we use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that INGOs need to or hope to be able to carry out their programs in as broad a geographical scope as possible [@Li:2020].
-For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas might need their service.
-Having the potential to shift programs to other provinces as needed thus provides a form of operational space.
-
-TODO: Andrew: This 2017 law fits with a broader global phenomenon of closing civic space... General crackdown stuff + China crackdown stuff + our addition
-
-TODO: Andrew: I'll clean up/rewrite this section and the section headings, etc.
-
-## De jure vs. de facto implementation of civil society regulations - Differential enforcement
-
-TODO: Andrew - I'll clean up this section
-
-@ChaudhryHeiss:2022 and the divergence in de jure and de facto regulations---the implementation doesn't have to match the written law, and often the written law can serve as a "weapon hanging on the wall that never fires" that serves as a warning to potentially uncooperative NGOs [@Kozenko:2015].
-See also [@ToeplerZimmerFrohlich:2020; @Plantan:2022]
-
-"We discuss the role of civil society organizations (CSOs) as agents of democratization and note the emergence of dual, at times apparently conflicting policy postures within authoritarian regimes (restriction and repression for some CSOs vs.
-financial support and opportunities for collaboration for others)." [@ToeplerZimmerFrohlich:2020]
-
-INGO regulations are implemented and enforced differentially - difference in de jure and de facto.
-This differential enforcement is one mechanism to allow host governments to harness the aspects of INGO programming that align with their domestic policy preferences while limiting INGO behavior that could threaten regime stability.
-
-Why pass laws in the first place and why enforcement differently?
-
-@ChaudhryHeiss:2022 and the divergence in de jure and de facto regulations---the implementation doesn't have to match the written law, and often the written law can serve as a "weapon hanging on the wall that never fires" that serves as a warning to potentially uncooperative NGOs [@Kozenko:2015].
-See also [@ToeplerZimmerFrohlich:2020; @Plantan:2022]
-
-"We discuss the role of civil society organizations (CSOs) as agents of democratization and note the emergence of dual, at times apparently conflicting policy postures within authoritarian regimes (restriction and repression for some CSOs vs.
-financial support and opportunities for collaboration for others)." [@ToeplerZimmerFrohlich:2020]
-
-Also, [@Plantan:2022] finds "that I find" evidence of selective implementation that reveals which groups are seen as threatening or beneficial."
-
-The presence of de jure regulations and the strictness of their de facto enforcement are both determined by the interplay between INGO characteristics and government preferences.
-
-Main idea: organizations that work on more contentious issues like human rights advocacy face stricter regulations [@Bush:2015; @ChaudhryHeiss:2021]
-
-## China's Overseas NGO law as a policy tool and its implications
-
+# Civil society laws as authoritarian policy tools for shaping INGO operational space
+
+The 2017 ONGO Law's provision of two legal pathways for registration—each with different degrees of freedom—is an example of the broader phenomenon of closing civic space.
+In the past two decades, authoritarian states have used administrative and legal measures to control and curtail the influence of global civil society.
+A rich literature in comparative politics explores how authoritarian regimes counterintuitively use democratic institutions for their own benefit and survival [@Kendall-TaylorFrantz:2014a; @GandhiPrzeworski:2007].
+Authoritarian states hold elections [@LevitskyWay:2010], permit popular protests [@Weiss:2013], and allow opposition parties in the legislature and set executive term limits [@Meng:2020].
+However, autocrats use these democratic-appearing institutions to limit possible threats to regime stability.
+Elections, protests, and apparent political reform are allowed, but only in ways that bolster the government's stability, and these institutions are kept weak and "dependent on the regime to ensure that they do not develop any real power or autonomy" [@FrantzEzrow:2011, 7].
+
+Civil society organizations are another political institution that autocrats must balance as part of their stability-seeking calculus.
+Despite the fact that NGOs can act as "agents of democratization" [@ToeplerZimmerFrohlich:2020], thus posing a threat to non-democratic rule, most authoritarian states permit the growth of domestic and international civil society [@DeMattee:2019; @Heiss:2019; @Heiss:2019a].
+INGOs provide needed resources and expertise in humanitarian relief, environmental policy, education, development, and autocrats can rely on these services to strengthen their regime by providing better public goods.
+At the same time, INGOs can pose a threat to stability by exposing human rights abuses, encouraging unwanted political reform, and engaging in political advocacy [@Heiss:2019; @ToeplerZimmerFrohlich:2020].
+To capture the benefits and reduce the risk of working with global civil society, most authoritarian states regulate civil society in nonviolent ways.
+Instead of beating activists or arresting NGO leaders, states have relied on "administrative crackdown," [@Chaudhry:2022] or laws that create barriers to NGO advocacy, entry, and funding [@ChristensenWeinstein:2013; @ChaudhryHeiss:2022; @CarothersBrechenmacher:2014].
+
+These laws, however, are a blunt tool that tend to target civil society as a whole—authoritarian states do not create one set of formal laws that applies only to regime-friendly INGOs and another set that applies to more risky INGOs.
+Instead, there is a divergence between the formal *de jure* laws and the *de facto* implementation of their accompanying regulations.
+In practice, NGO laws have tended to not be applied universally, and formal laws often can serve as a "weapon hanging on the wall that never fires," acting a warning to potentially uncooperative NGOs [@Kozenko:2015].
+Autocrats engage with INGOs in diverging ways, providing financial support and opportunities for collaboration with those that align with government policy preferences, and using legal mechanisms to restrict or expel those that do not [@ToeplerZimmerFrohlich:2020; @Plantan:2022; @LiFarid:2023].
+
+Laws act as policy tools that allow the government to TODO allow host governments to harness the aspects of INGO programming that align with their domestic policy preferences while limiting INGO behavior that could threaten regime stability.
+authoritarian civil society regulations act as policy tools that regimes can leverage to shift INGO behavior in their favor and how restrictive laws can reshape and tame organizational strategies [@Li:2020; @WuNie:2021; @LianMurdie:2023].
 *note* changed the sub-title to incorporate the policy tool lense too.
@@
 @LiFarid:2023
-
-Such legal restrictions can be either direct (denial of legal access/cannot register) or covert (red-tape, requiring the approval of PSUs, or the uncertainty of having to filing TAs case by case).
 
@@
 
-# Empirical expectations and analytical approach
-
-TODO: Andrew: I'll clean up this section
-
-Operational space is determined by the interaction between NGO characteristics and regime preferences
+TODO: Framework
+
+# INGO operating space in authoritarian contexts
+
+Anti-INGO laws thus creating different degrees of INGO "operating space," or the TODO.
+
+We propose a framework for understanding INGO operating space
 
 See @fig-theory
+
+We look at operating space and some of the factors that shape it.
+The law is designed in a way to give the government the power to selectively grow or shrink the operating space available to INGOs, and organizations work within those bounds to maximize that space
 
@@
 #| message: false
-#| fig-cap: "Diagram of our theoretical framework showing three possible determinants of INGO operational space: the contentiousness of the INGO's issue area, the inherent geographic scope of the INGO's operations, and the government's interest in and relationship with the INGO."
+#| fig-cap: "Diagram of our theoretical framework showing three possible determinants of INGO operational space: the government's interest in and relationship with the INGO, the contentiousness of the INGO's issue area, and the inherent geographic scope of the INGO's operations."
 theory_nodes <- tribble(
@@
 
-Based on this framework, we can identify and test several theoretical expectations:
-
+The presence of de jure regulations and the strictness of their de facto enforcement are both determined by the interplay between INGO characteristics and government preferences.
+
+TODO: Issue area and contentiousness and government preferences **and realignment through policy**
+
+Main idea: organizations that work on more contentious issues like human rights advocacy face stricter regulations [@Bush:2015; @ChaudhryHeiss:2021]
+
+Finally, the natural scope of an INGO's activities can shape its allowed operational space outside of authoritarian stability seeking calculus.
+Many INGOs purposely keep themselves small, non-confrontational, and non-political and limit themselves to work in only a small part of their target countries, having no plans to go beyond their hyperlocal scope.
+This naturally limits their operational space, but the limits are self-imposed and not directly related to government regulations.
+
+---
+
+# Exploring INGO operating space in China
+
+Below, we apply this framework to China
+
+Why China: in-depth look at the implementation of a single formal anti-INGO law and how it has reshaped the operating space available to global civil society
+China provides a unique case for looking at the the exact mechanism for controlling and leveraging global civil society as an act of authoritarian stability seeking.
+
+China's 2017 ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down on international NGOs [@ChaudhryHeiss:2022; @Carothers:2016].
+Studies on the law has been focused on discussing the historical and political impetus of passing the law [@Shieh:2018] or analyzing the regulatory regimes it that has established and potential implications for INGOs operating in China [@Feng:2017; @TeetsHsu:2016].
+However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs' operations and projects have been affected by the law after successfully gaining legal registration and documentation.
+A few studies [@Jia:2017; @YeHuang:2018] have reflected on the implementation of the ONGO Law after its first year, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations.
+However, a more up-to-date and comprehensive understanding of the effects of the ONGO law is still lacking.
+
+This paper aims to fill these gaps by empirically examining how the "closing space" hypothesis applies to China in the years after the ONGO Law took effect.
+China provides an excellent setting for testing these theories because China's promulgation of restrictive INGO law as an authoritarian jurisdiction fits the observed global trends in recent years, thus can serve as an representative case to deepen scholarly understanding around these themes.
+Also, the level of ambiguity of the legal framework gives ample room for arbitrary discretion and conflicting attitudes by authorities [@Jia:2017], enabling us to analyze rules in form (*de jure*) as well as rules in use (*de facto*).
+
+The government can thus use the RO registration process to limit the potential reach of INGOs.
+
+In this paper, we use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that INGOs need to or hope to be able to carry out their programs in as broad a geographical scope as possible [@Li:2020].
+For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas might need their service.
+Having the potential to shift programs to other provinces as needed thus provides a form of operational space.
+
+With this framework and theoretical background, we use the case of China to explore three theoretical expectations. 
 Based on extant literature and theoretical understanding, we argue that the operation space INGOs are granted is associated with the level of contentiousness their missions, i.e., the issue areas they work in.
@@
 ## Data
+
+TODO Andrew: Make it clear that this section is just about the data for the statsy stuff, not the case study
 
@@
 We lack sufficient theory or data to explain why this trend goes against our expectations, but we can again make reasonable speculations.
-As we saw previously with INGOs and local connections, organizations appear to strategically seek out the best avenues and methods for registering.
-[@Jia:2017a] Organizations that participated in the initial wave of registrations in 2017 likely had closer connections with local officials and were able to speed through the bureaucratic process registration more easily.
+As we saw previously with INGOs and local connections, organizations appear to strategically seek out the best avenues and methods for registering [@Jia:2017a].
+Organizations that participated in the initial wave of registrations in 2017 likely had closer connections with local officials and were able to speed through the bureaucratic process registration more easily.
 As a preliminary test of this speculation, we rerun our main model with an interaction between years since registration and local connections to see how the effect of local connections changes over time.
@@
 
-# Contentiousness and government relationships: The cases ofThe Nature Conservancy and Greenpeace
+## Contentiousness and government relationships: The cases of The Nature Conservancy and Greenpeace
 
@@
 What factors could have contributed to the contrasting experiences of TNC and Greenpeace under the ONGO Law?
-After analyzing the data, the working approach and relationship with the government emerged as pivotal differences between the two INGOs, which fits existing discussions on the differential treatment of INGOs based on their relationship with the authority [TO DO: add citations].
+After analyzing the data, the working approach and relationship with the government emerged as pivotal differences between the two INGOs, which fits existing discussions on the differential treatment of INGOs based on their relationship with the authority [TODO: add citations].
 In a public interview with TNC’s RO in China about their registration experience, the chief representative stated TNC’s working approach in China has been “science-based”, using “non-confrontational, collaborative approach in working closely with governments, the business community and others” [@ChinaPhilanthropyReserchInstitute:2018a].

### 2023-12-04 manuscript/manuscript.qmd
Finish cleaning and consolidating lit review/theory/expectations sections

@@
 ---
-title: "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
+title: "The Operational Space of International Civil Society Under Authoritarian Regulations: The Case of China"
 short-title: "China's ONGO Law and International Civil Society"
-date: "2023-11-29"
+date: "2023-12-03"
 author:
@@
 Second, we explore how authoritarian civil society regulations act as policy tools that regimes can leverage to shift INGO behavior in their favor and how restrictive laws can reshape and tame organizational strategies [@Li:2020; @WuNie:2021; @LianMurdie:2023].
-Third, we build on work by @LiFarid:2023 to explore how, as policy tools, these regulations lead to differentiated application of the law depending on organizational characteristics.
+Third, we explore how these regulations lead to differentiated application of the law depending on organizational characteristics.
 We argue that INGO issue areas, missions, and pre-existing relationships with local government officials influence the degree of operating space available for INGOs.
@@
 
-International NGOs began to play an important role in China in the early 1990s as part of the country's Reform and Opening-Up policy, and organizations sucg as Save the Children and the Ford Foundation established local offices and branches.
+International NGOs began to play an important role in China in the early 1990s as part of the country's Reform and Opening-Up policy, and organizations such as Save the Children and the Ford Foundation established local offices and branches.
 Since then, INGOs and global civil society have played pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China's domestic nonprofit sector [@Yin:2009].
@@
 The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations by the State Council that specifies the registration of representative offices ("ROs") of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic NGOs.
-However, the actual application of the regulation was very limited: until the ONGO Law took effect in 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs, while some Chinese officials estimated in 2016 that there were roughly over 7,000 INGOs operating in China [@YeHuang:2018; @Spires:2020a].
+However, the actual application of the regulation was very limited: until the ONGO Law took effect in 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs, while some Chinese officials estimated in 2016 that there were roughly over 7,000 INGOs operating in China [@YeHuang:2018; @Spires:2020].
 
@@
 
-# Civil society laws as authoritarian policy tools for shaping INGO operational space
+# Civil society laws in the service of regime stability
 
@@
 Instead, there is a divergence between the formal *de jure* laws and the *de facto* implementation of their accompanying regulations.
-In practice, NGO laws have tended to not be applied universally, and formal laws often can serve as a "weapon hanging on the wall that never fires," acting a warning to potentially uncooperative NGOs [@Kozenko:2015].
-Autocrats engage with INGOs in diverging ways, providing financial support and opportunities for collaboration with those that align with government policy preferences, and using legal mechanisms to restrict or expel those that do not [@ToeplerZimmerFrohlich:2020; @Plantan:2022; @LiFarid:2023].
-
-Laws act as policy tools that allow the government to TODO allow host governments to harness the aspects of INGO programming that align with their domestic policy preferences while limiting INGO behavior that could threaten regime stability.
-authoritarian civil society regulations act as policy tools that regimes can leverage to shift INGO behavior in their favor and how restrictive laws can reshape and tame organizational strategies [@Li:2020; @WuNie:2021; @LianMurdie:2023].
-*note* changed the sub-title to incorporate the policy tool lense too.
-
-TODO: Meng - China crackdown lit
-
-@LiFarid:2023
-
+In practice, NGO laws tend to not be applied universally and formal laws often serve as a "weapon hanging on the wall that never fires," acting a warning to potentially uncooperative NGOs [@Kozenko:2015].
+Instead, autocrats engage with INGOs in opposing ways, providing financial support and opportunities for collaboration with those that align with government policy preferences, and using legal mechanisms to restrict or expel those that do not [@ToeplerZimmerFrohlich:2020; @Plantan:2022; @LiFarid:2023].
+
+The authoritarian benefits of civil society regulations go beyond simply allowing or disallowing specific INGOs.
+The flexible *de facto* implementation of formal civil society laws allows authoritarians to "use nonprofit regulation as a tool of political control to shore up their continued rule" [@Spires:2020, 573], providing them with an additional policy tool for their stability-seeking calculus.
+These laws allow governments to capture and reshape INGO programming in their favor.
+@LianMurdie:2023 illustrate how increased civil society restrictions have counterintuitively led to an increase in cooperative, regime-friendly INGO programming, with INGOs praising government policies, engaging in joint programming with the government, and changing longstanding programs to align with government desires.
+China's ONGO law illustrates this dynamic well.
+The ONGO law requires that INGOs partner with provincial government agencies and find collaborating PSUs, which provides the government with more influence over INGO decision making.
+For example, Oxfam gained RO status in 2017, but only after negotiations with its proposed PSU forced it to stop collaborating with other organizations and local agencies [@Li:2020].
 In 2018, @BatkeHang:2018 posited that the ONGO law was showing signs of reorienting the missions of legally recognized INGOs and the overall scope of international civil society to be more explicitly aligned with government preferences.
-@HolbigLang:2022 recently confirmed this prediction, finding that the issue areas addressed by legally recognized INGOs have "shift\[ed\] towards fields of activity high up the government's domestic policy agenda" [-@HolbigLang:2022, p.
+Holbig & Lang confirmed this prediction, finding that the issue areas addressed by legally recognized INGOs had "shift\[ed\] towards fields of activity high up the government's domestic policy agenda" [-@HolbigLang:2022, p.
 587].
-
-TODO: Framework
-
-# INGO operating space in authoritarian contexts
-
-Anti-INGO laws thus creating different degrees of INGO "operating space," or the TODO.
-
-We propose a framework for understanding INGO operating space
-
-See @fig-theory
-
-We look at operating space and some of the factors that shape it.
-The law is designed in a way to give the government the power to selectively grow or shrink the operating space available to INGOs, and organizations work within those bounds to maximize that space
+Civil society laws thus filter out organizations opposed to the host regime's policy preferences and grant increased government control over safer and more beneficial INGOs.
+
+# Authoritarian policy tools and INGO operational space: theory and expectations
+
+The strategic and individualized enforcement of broad civil society laws in authoritarian regimes creates a regulatory environment where each INGO faces a different set of constraints.
+We term this an INGO's "operational space," or the degree of legal and practical flexibility an organization can rely on in its target country.
+INGOs with a large amount of operational space can can engage in a wider range of programs, address more potentially contentious issues, and enjoy broader geographic scope without fear of interference from the host government, even in the presence of formal *de jure* anti-NGO laws.
+Organizations with less operational space, on the other hand, face stricter *de facto* enforcement of anti-NGO laws and are more constrained in the programs, strategies, issues, and regions they can work on.
 
@@
 
-The presence of de jure regulations and the strictness of their de facto enforcement are both determined by the interplay between INGO characteristics and government preferences.
-
-TODO: Issue area and contentiousness and government preferences **and realignment through policy**
-
-Main idea: organizations that work on more contentious issues like human rights advocacy face stricter regulations [@Bush:2015; @ChaudhryHeiss:2021]
-
+In @fig-theory, we propose that the interplay between INGO characteristics and government preferences is a key determinant of individual INGO operating space [@LiFarid:2023; @ChaudhryHeiss:2021].
+Authoritarian states seek out INGOs that provide direct benefits and public goods, while avoiding INGOs that threaten their stability.
+For instance, states in need of foreign aid and development will be more open to INGOs working on those issues, while states looking for increased trade will seek out INGOs focused on economic partnerships.
+Because their primary issue areas are aligned with regime preferences, INGOs benefit from greater operational space and face fewer restrictions.
+In contrast, states engaged in human rights abuses or fearful of foreign influence over other domestic policies will reduce—or even close—the operational space allowed for INGOs addressing these issues.
+Notably, the arrow between government preferences and issue area is bidirectional, reflecting the government's ability to use civil society regulations to directly realign INGO programming in the regime's favor.
 Finally, the natural scope of an INGO's activities can shape its allowed operational space outside of authoritarian stability seeking calculus.
 Many INGOs purposely keep themselves small, non-confrontational, and non-political and limit themselves to work in only a small part of their target countries, having no plans to go beyond their hyperlocal scope.
-This naturally limits their operational space, but the limits are self-imposed and not directly related to government regulations.
-
----
-
-# Exploring INGO operating space in China
-
-Below, we apply this framework to China
-
-Why China: in-depth look at the implementation of a single formal anti-INGO law and how it has reshaped the operating space available to global civil society
-China provides a unique case for looking at the the exact mechanism for controlling and leveraging global civil society as an act of authoritarian stability seeking.
-
-China's 2017 ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down on international NGOs [@ChaudhryHeiss:2022; @Carothers:2016].
-Studies on the law has been focused on discussing the historical and political impetus of passing the law [@Shieh:2018] or analyzing the regulatory regimes it that has established and potential implications for INGOs operating in China [@Feng:2017; @TeetsHsu:2016].
-However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs' operations and projects have been affected by the law after successfully gaining legal registration and documentation.
-A few studies [@Jia:2017; @YeHuang:2018] have reflected on the implementation of the ONGO Law after its first year, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations.
-However, a more up-to-date and comprehensive understanding of the effects of the ONGO law is still lacking.
-
-This paper aims to fill these gaps by empirically examining how the "closing space" hypothesis applies to China in the years after the ONGO Law took effect.
-China provides an excellent setting for testing these theories because China's promulgation of restrictive INGO law as an authoritarian jurisdiction fits the observed global trends in recent years, thus can serve as an representative case to deepen scholarly understanding around these themes.
-Also, the level of ambiguity of the legal framework gives ample room for arbitrary discretion and conflicting attitudes by authorities [@Jia:2017], enabling us to analyze rules in form (*de jure*) as well as rules in use (*de facto*).
-
-The government can thus use the RO registration process to limit the potential reach of INGOs.
-
-In this paper, we use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that INGOs need to or hope to be able to carry out their programs in as broad a geographical scope as possible [@Li:2020].
+This naturally limits their operational space, but these limits are self-imposed and not directly related to government regulations.
+
+To test the relationships between government preferences, INGO issue area, and INGO operational space, we apply this framework to China's ONGO law.
+Previous research has looked at the practical implementation of civil society laws on a global scale [@LianMurdie:2023; @Chaudhry:2022], which naturally blurs the specific policy mechanisms regimes use for controlling and leveraging global civil society.
+By analyzing the population of formally registered INGOs between 2017–2022, we can more precisely explore how a single formal anti-INGO law has shaped the operational space for foreign organizations working in the country.
+Specifically, we can observe exactly how the Chinese government has used the RO registration process to strategically limit the potential reach of INGOs and reshape their issue areas.
+We use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that INGOs need to or hope to be able to carry out their programs in as broad a geographical scope as possible [@Li:2020].
 For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas might need their service.
@@
 
-With this framework and theoretical background, we use the case of China to explore three theoretical expectations. 
-Based on extant literature and theoretical understanding, we argue that the operation space INGOs are granted is associated with the level of contentiousness their missions, i.e., the issue areas they work in.
-Since the level of contentiousness is also manifested by the level of difficulty they face while seeking lawful registration.
-
-Following our theory, government preferences thus directly influence INGO issue areas, which in turn shapes the amount of flexibility enjoyed by the INGO.
-Accordingly, we expect that INGOs working on non-contentious, regime-aligned issues will have greater reach throughout the country:
-
--   **Theoretical expectation 1**: Because they are seen as less of a threat to regime stability and more aligned with government policy preferences, INGOs working on less contentious issues should be registered in more provinces.
-
-Relationships with PSUs are a critical part of the INGO registration process.
-No PSU is obligated to take on a supervisory role for an INGO, and interested organizations have to cultivate relationships with local officials.
-Accordingly, many of the INGOs we observe in our data either demonstrate close connections with local governmental authorities or frame their activities and services with a narrower geographic scope.
+We propose a set of theoretical expectations based on @fig-theory that structure our analysis.
+First, we expect that INGOs working on non-contentious, regime-aligned issues will have greater reach throughout the country:
+
+> **E~1~**: Because they are seen as less of a threat to regime stability and more aligned with government policy preferences, INGOs working on less contentious issues should be registered in more provinces.
 
@@
 
--   **Theoretical expectation 2**: Because they are explicitly focused on local issues, INGOs with explicitly local missions should be registered in fewer provinces.
+> **E~2~**: Because they are explicitly focused on local issues, INGOs with explicitly local missions should be registered in fewer provinces.
 
 Finally, we also expect that the operational space for INGOs is negatively associated with the time elapsed since the law took effect.
-The mechanism behind this expectation is directly related to both issue area and government preferences.
-
--   **Theoretical expectation 3** (registration timing): Because formal registration can take a long time and can involve many bureaucratic hurdles, INGOs that registered soon after the law took effect should be be (1) less of a threat and (2) a higher priority for processing, and so should be registered in more provinces.
+The mechanism behind this expectation is directly related to both issue area and government preferences:
+
+> **E~3~**: Because formal registration can take a long time and can involve many bureaucratic hurdles, INGOs that registered soon after the law took effect should be be (1) less of a threat and (2) a higher priority for processing, and so should be registered in more provinces.
 

### 2023-12-04 manuscript/manuscript.qmd
Clean and shrink data and methods section

@@
 [^ngo-clarification]: "Civil society" is a broad concept that includes a range of organizational forms, both formal and informal.
-In this paper, we look at nongovernmental organizations (NGOs), often called nonprofit organizations or third sector organizations—formal non-profit-seeking organizations that are neither privately-owned nor government-controlled.
+In this paper, we look at nongovernmental organizations (NGOs), often called nonprofit organizations or third sector organizations---formal non-profit-seeking organizations that are neither privately-owned nor government-controlled.
 We define international NGOs as organizations that conduct work predominantly in at least one other country outside of their home country.
@@
 Many previous studies use broad indexes of civil society openness, such as the core civil society index from the Varieties of Democracy project [@LianMurdie:2023; @ChaudhryHeiss:2022].
-These measures capture the general regulatory environment for all civil society—including domestic NGOs, INGOs, and informal organizations—but do not reflect the specific implementation of laws for INGOs.
+These measures capture the general regulatory environment for all civil society---including domestic NGOs, INGOs, and informal organizations---but do not reflect the specific implementation of laws for INGOs.
 In this paper, though, we use a mixed methods approach to explore the regulatory environment for INGOs in particular, providing much a richer description of authoritarian regulation of international civil society.
 
-Below, we provide a brief overview of China's 2017 ONGO Law and the different regulatory mechanisms—and practical limitations—it provides for INGOs to obtain legal access to the country.
+Below, we provide a brief overview of China's 2017 ONGO Law and the different regulatory mechanisms---and practical limitations---it provides for INGOs to obtain legal access to the country.
 We then summarize existing research on authoritarian regulation of INGOs and the differential application of these laws based on regime preferences and organizational characteristics, and propose a set of empirical expectations based on this literature.
@@
 
-The 2017 ONGO Law's provision of two legal pathways for registration—each with different degrees of freedom—is an example of the broader phenomenon of closing civic space.
+The 2017 ONGO Law's provision of two legal pathways for registration---each with different degrees of freedom---is an example of the broader phenomenon of closing civic space.
 In the past two decades, authoritarian states have used administrative and legal measures to control and curtail the influence of global civil society.
@@
 
-These laws, however, are a blunt tool that tend to target civil society as a whole—authoritarian states do not create one set of formal laws that applies only to regime-friendly INGOs and another set that applies to more risky INGOs.
+These laws, however, are a blunt tool that tend to target civil society as a whole---authoritarian states do not create one set of formal laws that applies only to regime-friendly INGOs and another set that applies to more risky INGOs.
 Instead, there is a divergence between the formal *de jure* laws and the *de facto* implementation of their accompanying regulations.
@@
 Because their primary issue areas are aligned with regime preferences, INGOs benefit from greater operational space and face fewer restrictions.
-In contrast, states engaged in human rights abuses or fearful of foreign influence over other domestic policies will reduce—or even close—the operational space allowed for INGOs addressing these issues.
+In contrast, states engaged in human rights abuses or fearful of foreign influence over other domestic policies will reduce---or even close---the operational space allowed for INGOs addressing these issues.
 Notably, the arrow between government preferences and issue area is bidirectional, reflecting the government's ability to use civil society regulations to directly realign INGO programming in the regime's favor.
@@
 
-We test these theoretical expectations using a mixed methods approach. Using
-
-1: issue - stats + case study 2: localness - stats 3: timing - stats
-
--   Stats + case study: **Local**
--   Stats + case study: **Contentiousness**
--   Case study: **Relationship with PSU and government** (stats/descriptive bc lots of chambers of commerce)
+# Data and methods
+
+We examine these theoretical expectations using a mixed methods approach.
+First, we explore a rich dataset of all ROs registered in China between 2017–2021 using a combination of descriptive statistics and Bayesian models to understand how the international nonprofit sector in China has been reshaped since the implementation of the ONGO law.
+We then complement this statistical analysis with a comparative case study of two INGOs---Greenpeace and The Nature Conservancy---to explore in detail how the ONGO has specifically influenced organizational operational space.
 
@@
 
-TODO Andrew: Make it clear that this section is just about the data for the statsy stuff, not the case study
-
-The data used in this paper was collected from INGOs' public registration documents disclosed by the Ministry of Public Security's Overseas NGO Office online service platform.
-The platform is a website maintained by the registrar of INGOs and regularly publicize the administrative documentation of all the ROs and temporary activities registered or filled across China.
-The data used in this study spans from January 1, 2017, when the law took effect, to December 31, 2021, with information for all 633 registered organizations approved as of the cutoff point.
-The filing documents for ROs disclose the name, the address, the registration date, the registration authority (which public security bureau regulates it), the PSU, the issue area or purposes of the RO, and the specific provinces they can work in.
-We merge our INGO data with additional data of Chinese INGO data from ChinaFile, a project that translate and code the MPS platform data, to include their English organization names, for the sake of transparency and accessibility.
-
-We code the variables we use in the empirical analysis from the registration information.
-Most of our data cleaning work is an objective data wrangling process, such as parsing out the province each RO registered in from the address, or calculating the total number provinces approved in the registration document.
-Meanwhile, the qualitative coding of issue areas is conducted by the authors, based on consistent coding rules agreed by the authors.
+Our data comes from INGOs' public registration documents disclosed by the Ministry of Public Security's Overseas NGO Office, which maintains a website with complete documentation of all the ROs and temporary activities registered or filled across China.
+We include all INGO registrations between January 1, 2017, when the law took effect, to December 31, 2021, with information for all `r nrow(ongo)` registered organizations.
+The filing documents for ROs disclose each INGO's name, address, registration date, regulating Public Security Bureau, professional supervisory unit (PSU),  issue area or purposes of the RO, and the specific provinces they can work in.
+We merge this INGO data with translated English organization names data from ChinaFile.
+Our data and reproducible code is available at `ANONYMIZED_DOI_URL`.
 
@@
 
-### Dependent variable
-
-As explained, the dependent variable is the count of provinces that INGOs are authorized to work in as documented in their official registration record.
-The documentation lists the specific provincial regions each INGO RO can conduct activities in and we derive the number of provinces based on the lists.
-Since the maximum count of provinces INGOs can possibly work in is 32, this variable ranges from 1 to 32.
-
-### Independent variables
-
-Our key independent variables correspond to each of our three empirical expectations.
+Our dependent variable is the count of provinces that INGOs are authorized to work in.
+We derive this value from the official registration record, which lists all the provincial regions each INGO RO can conduct activities in.
+This value ranges from 1–32 (the total number of Chinese provinces).
+
+Our key independent variables correspond to each of our three theoretical expectations.
 First we code each INGO's issue area based on its mission statement reported in its registration documentation.
-Given there is certain level of subjectivity in the coding process, the coding of issue areas are cross-checked between the researchers---Author 1 assigned each organization into one of the issue areas defined in Article 3 of the ONGO Law, and Author 2 cross-checked the coding for ambiguous cases.
+Given there is certain level of subjectivity in the coding process, we cross-checked our manual coding of issue areas---Author 1 assigned each organization into one of the issue areas defined in Article 3 of the ONGO Law, and Author 2 cross-checked the coding for ambiguous cases.
 We include our coding rules for overlapping issue areas in the appendix (TODO).
@@
 
-Our second independent variable is a dichotomous indicator of whether the INGO explicitly states that it intends to operate locally (below province level).
-There are cases where the aim of the INGO is attached to a locality, either having a county or city name in their RO name or purposes, or the INGO are actually set up by people in China and they registered the RO to communicate between the "hometown" and the INGO set up abroad.
-We thus include this variable in our analysis to explore how having local connections is associated with the operational space of ROs.
-
-Our final independent variable measures how much time elapsed between the January 1, 2017 (when the law took effect) and the organization's official registration date.
+Our second independent variable is a dichotomous indicator of whether the INGO explicitly states that it intends to operate locally or subprovincially.
+There are cases where the aim of the INGO is attached to a locality, either having a county or city name in their RO name or purposes, or the INGO is actually set up by people in China who registered the RO to communicate between the "hometown" and the INGO set up abroad.
+
+Our final independent variable measures how much time elapsed between January 1, 2017 (when the law took effect) and the organization's official registration date.
 There is great variance in the timing of registering an RO among INGOs, since there has been a *de facto* grace period for INGOs to seek legal presence after the law took effect [@Shieh:2018].
@@
 
-## Descriptive overview of data
+## Descriptive overview
 
@@
 
-Following our first empirical expectation, we predict that INGOs working on less contentious issues should be registered in more provinces and have more geographic flexibility in operating throughout the country.
+Following our first empirical expectation, we predict that INGOs working on less contentious issues should be registered in more provinces and have more geographic flexibility to work throughout the country.
 To explore this, we can take advantage of the simultaneous continuous and discrete features of ordered Beta regression and see how often an INGO in each issue area is predicted to work in a single province, across all provinces, or some number in between.

### 2023-12-04 manuscript/manuscript.qmd
Fix some typos

@@
 We then summarize existing research on authoritarian regulation of INGOs and the differential application of these laws based on regime preferences and organizational characteristics, and propose a set of empirical expectations based on this literature.
-We test these expectations with a mixed methods research design, combining Bayeisan analysis of administrative data from 633 formally registered INGOs with a comparative case study of Greenpeace and The Nature Conservancy, two INGOs working on similar issue areas which took different approaches to operating in China after 2017.
+We test these expectations with a mixed methods research design, combining Bayeisan analysis of administrative data from `r nrow(ongo)` formally registered INGOs with a comparative case study of Greenpeace and The Nature Conservancy, two INGOs working on similar issue areas which took different approaches to operating in China after 2017.
 We conclude with a broader discussion of authoritarian civil society regulations and propose future methods for exploring the practical operating environment for INGOs working in such regimes.
@@
 This can help explain why some seemingly more contentious issue areas, e.g., environmental INGOs enjoy relatively more operational space.
-According to [@Plantan:2022], Chinese authorities can see the work of environmental INGOs as providing benefits such as political stability and "selectively ncourage low risk groups and selectively channel higher risk groups into permitted areas".
+According to [@Plantan:2022], Chinese authorities can see the work of environmental INGOs as providing benefits such as political stability and "selectively encourage low risk groups and selectively channel higher risk groups into permitted areas".
 We will further this discussion with the case analysis of two environmental INGOs later.

### 2023-12-04 manuscript/manuscript.qmd
Minor revisions + update legal section + add coding rules
Resolved some of the TO DOs

@@
 ---
-title: "The Operational Space of International Civil Society Under Authoritarian Regulations: The Case of China"
+title: "Operational constraints and closing civic space: International NGO restrictions and China’s Overseas NGO law"
 short-title: "China's ONGO Law and International Civil Society"
@@
 This global trend of closing or shrinking civic space has affected countries of all regime types, including both autocracies and democracies such as Morocco and Palestine [@AtiaHerrold:2018], India [@press-trust-india:2019], Vietnam [@Sidel:2023], Canada [@CIVICUS:2013], and the United States [@Cramer:2020].
-On April 28, 2016, China passed its own set of civil society restrictions with its Law of the People's Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China---or "ONGO Law"---which formally took effect on January 1, 2017.
-The law requires all international NGOs (INGOs) to either establish formal in-country representative offices (ROs) or file short-term temporary activities (TAs) to lawfully operate in mainland China.
+On April 28, 2016, China passed its own set of civil society restrictions with its Law of the People's Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China---or "2016 ONGO Law"---which formally took effect on January 1, 2017.
+The law requires all international NGOs (INGOs) to either establish formal in-country representative offices (ROs) or file short-term temporary activities to lawfully operate in mainland China.
 Without recognized legal status, INGOs are prohibited from working in the country, and even with legal recognition, INGO programming is limited to government-approved activities.
@@
 
-By focusing on INGO operational space in China, we provide a unique view into the *de facto* regulatory environment for foreign civil society in an authoritarian state.
+By focusing on INGO operational space in China, we provide a unique empirical view into the *de facto* regulatory environment for foreign civil society in an authoritarian state.
 Many previous studies use broad indexes of civil society openness, such as the core civil society index from the Varieties of Democracy project [@LianMurdie:2023; @ChaudhryHeiss:2022].
 These measures capture the general regulatory environment for all civil society---including domestic NGOs, INGOs, and informal organizations---but do not reflect the specific implementation of laws for INGOs.
-In this paper, though, we use a mixed methods approach to explore the regulatory environment for INGOs in particular, providing much a richer description of authoritarian regulation of international civil society.
-
-Below, we provide a brief overview of China's 2017 ONGO Law and the different regulatory mechanisms---and practical limitations---it provides for INGOs to obtain legal access to the country.
+In this paper, though, we use a mixed methods approach to explore the regulatory environment for INGOs in particular, providing a much richer description and analysis of the impact of INGO laws.
+
+Below, we provide a brief overview of China's 2016 ONGO Law and the different regulatory mechanisms---and practical limitations---it provides for INGOs to obtain legal access to the country.
 We then summarize existing research on authoritarian regulation of INGOs and the differential application of these laws based on regime preferences and organizational characteristics, and propose a set of empirical expectations based on this literature.
@@
 
-# The legal framework established by the 2017 ONGO law
-
-International NGOs began to play an important role in China in the early 1990s as part of the country's Reform and Opening-Up policy, and organizations such as Save the Children and the Ford Foundation established local offices and branches.
+# The legal framework established by the 2016 ONGO law
+
+International NGOs began to play an important role in China in the early 1990s as part of the country's Reform and Opening-Up policy, and organizations such as Save the Children and the Ford Foundation established local offices.
 Since then, INGOs and global civil society have played pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China's domestic nonprofit sector [@Yin:2009].
 Prior to the implementation of the 2017 ONGO Law, regulation of INGOs in China was ambiguous [@Shieh:2018; @Spires:2022].
-The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations by the State Council that specifies the registration of representative offices ("ROs") of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic NGOs.
-However, the actual application of the regulation was very limited: until the ONGO Law took effect in 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs, while some Chinese officials estimated in 2016 that there were roughly over 7,000 INGOs operating in China [@YeHuang:2018; @Spires:2020].
-
-Many INGOs gained legal status within mainland China by registering as foreign-funded companies [@Sidel:2016], though there were no clear requirements to have a formal legal presence in China [@Han:2011; @HolbigLang:2022; @Yin:2009].
-However, the legal form of foreign-funded company is not quite compatible with the non-profit-distributing nature of INGOs.
-Under the Chinese legal system, enterprises were intended to be for-profit entities while nonprofit organizations were required to choose other standalone legal forms, such as foundations, associations, and social service organizations [@Ye:2021].
-Thus, INGOs obtaining legal status had to navigate a legal framework designed for a for-profit institutional logic, which often conflicted with nonprofit characteristics like their lack of private investment returns.
-
-The legal framework governing INGOs was overhauled by the 2017 Chinese ONGO Law.
-The new law applies to all overseas (including Hong Kong, Macau, and Taiwan) non-governmental organizations that conduct not-for-profit activities in the fields of economic development, education, science, technology, culture, public health, sports, environment protection, poverty alleviation, and disaster relief.
-The ONGO Law provides two pathways for INGOs to lawfully conduct nonprofit activities in China (see @fig-ro-ta-pathways): (1) submitting an application for formal permanent registration as ROs, or (2) filing documentation of temporary activities (TAs) with the Ministry of Public Security and provincial-level Public Security Bureaus.
-Formal registration as an RO allows INGOs to maintain an ongoing presence in the country, while TAs are intended for INGOs that need to conduct one-off programs that last no longer than one year.
-Using one of these two channels to obtain legal status became mandatory in 2017 and any INGOs that could not successfully obtain proper legal authorization were deemed illegal.
+The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations that specifies the registration of ROs of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic nonprofits.
+However, the actual application of the regulation was very limited: until the ONGO Law took effect in 2017, there were fewer than 30 foreign foundation ROs registered, while some Chinese officials estimated in 2016 that there were roughly over 7,000 INGOs operating in China [@YeHuang:2018; @Spires:2020].
+
+Many INGOs gained legal status by registering as foreign-invested companies [@Sidel:2016], for the administrative convenience such as hiring employees [@HolbigLang:2022; @Yin:2009].
+However, such a legal form is not quite compatible with the non-profit-distributing nature of INGOs.
+Chinese companies are intended to be for-profit only, while nonprofits are regulated under other legal forms, such as foundations and social service organizations [@Ye:2021].
+Thus, INGOs registered ad foreign-invested companies had to navigate through for-profit institutional logics, with doctrines like protecting shareholders' investment returns.
+
+The legal framework governing INGOs was overhauled by the 2016 ONGO Law.
+The new law applies to all overseas (including Hong Kong, Macau, and Taiwan) NGOs that conduct not-for-profit activities in the fields of economic development, education, science, technology, culture, public health, sports, environment protection, poverty alleviation, and disaster relief.
+The ONGO Law provides two pathways for INGOs to lawfully operate in China (see @fig-ro-ta-pathways): (1) submitting an application for formal permanent registration as ROs, or (2) filing documentation of temporary activities with the Public Security Bureaus.
+Formal registration as an RO allows INGOs to maintain an ongoing presence in the country, while temporary activities are intended for INGOs that need to conduct one-off programs that last no longer than one year.
+Using one of these two channels to obtain legal status became mandatory in 2017.
 
@@
   ),
-  type = "Registered organization (RO)"
+  type = "Representative offices"
 )
@@
   ),
-  type = "Temporary activities (TA)"
+  type = "Temporary activities"
 )
@@
 Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.
+Similarly, INGOs need to find an eligible Chinese partner, including governmental, quasi-governmental and non-profit organizations to file temporary activities for them.
+After successfully gaining legal status, INGOs also need to abide by the operational regulations by the law, such as no fundraising within mainland China, only channeling the funds through RO's registered account or the Chinese partners' accounts, filing reports regularly and stay within the geographical and issue scopes as approved.
 
@@
 These laws allow governments to capture and reshape INGO programming in their favor.
-@LianMurdie:2023 illustrate how increased civil society restrictions have counterintuitively led to an increase in cooperative, regime-friendly INGO programming, with INGOs praising government policies, engaging in joint programming with the government, and changing longstanding programs to align with government desires.
+@LianMurdie:2023 illustrate how increased civil society restrictions have counter-intuitively led to an increase in cooperative, regime-friendly INGO programming, with INGOs praising government policies, engaging in joint programming with the government, and changing longstanding programs to align with government desires.
 China's ONGO law illustrates this dynamic well.
-The ONGO law requires that INGOs partner with provincial government agencies and find collaborating PSUs, which provides the government with more influence over INGO decision making.
+The ONGO law requires that INGOs partner with government agencies and find collaborating PSUs, which provides the government with more influence over INGO decision making.
 For example, Oxfam gained RO status in 2017, but only after negotiations with its proposed PSU forced it to stop collaborating with other organizations and local agencies [@Li:2020].
@@
 Previous research has looked at the practical implementation of civil society laws on a global scale [@LianMurdie:2023; @Chaudhry:2022], which naturally blurs the specific policy mechanisms regimes use for controlling and leveraging global civil society.
-By analyzing the population of formally registered INGOs between 2017–2022, we can more precisely explore how a single formal anti-INGO law has shaped the operational space for foreign organizations working in the country.
+By analyzing the population of formally registered INGOs between 2017–2021, we can more precisely explore how a single formal anti-INGO law has shaped the operational space for foreign organizations working in the country.
 Specifically, we can observe exactly how the Chinese government has used the RO registration process to strategically limit the potential reach of INGOs and reshape their issue areas.
@@
 We examine these theoretical expectations using a mixed methods approach.
-First, we explore a rich dataset of all ROs registered in China between 2017–2021 using a combination of descriptive statistics and Bayesian models to understand how the international nonprofit sector in China has been reshaped since the implementation of the ONGO law.
-We then complement this statistical analysis with a comparative case study of two INGOs---Greenpeace and The Nature Conservancy---to explore in detail how the ONGO has specifically influenced organizational operational space.
+First, we explore a rich dataset of all ROs registered in China between 2017–2021 using a combination of descriptive statistics and Bayesian models to understand how the international civil society in China has been reshaped since the implementation of the ONGO law.
+We then complement this statistical analysis with a comparative case study of two INGOs---The Nature Conservancy and Greenpeace ---to explore in detail how the ONGO has specifically influenced organizational operational space.
 
@@
 Our data comes from INGOs' public registration documents disclosed by the Ministry of Public Security's Overseas NGO Office, which maintains a website with complete documentation of all the ROs and temporary activities registered or filled across China.
-We include all INGO registrations between January 1, 2017, when the law took effect, to December 31, 2021, with information for all `r nrow(ongo)` registered organizations.
-The filing documents for ROs disclose each INGO's name, address, registration date, regulating Public Security Bureau, professional supervisory unit (PSU),  issue area or purposes of the RO, and the specific provinces they can work in.
+We include all INGO registrations between January 1, 2017, when the law took effect, to December 31, 2021, with information for all `r nrow(ongo)` actively registered organizations.
+The filing documents for ROs disclose each INGO's name, address, registration date, regulating Public Security Bureau, PSU, issue area and purposes of the RO, and the specific provinces they can work in.
 We merge this INGO data with translated English organization names data from ChinaFile.
@@
 We derive this value from the official registration record, which lists all the provincial regions each INGO RO can conduct activities in.
-This value ranges from 1–32 (the total number of Chinese provinces).
+This value ranges from 1–32 (the total number of province-level jurisdictions in mainland China).
 
@@
 Given there is certain level of subjectivity in the coding process, we cross-checked our manual coding of issue areas---Author 1 assigned each organization into one of the issue areas defined in Article 3 of the ONGO Law, and Author 2 cross-checked the coding for ambiguous cases.
-We include our coding rules for overlapping issue areas in the appendix (TODO).
+We include our coding rules for overlapping issue areas in the appendix.
 We categorize each organization into nine different issue areas (see @tbl-issues).
@@
 
-Our second independent variable is a dichotomous indicator of whether the INGO explicitly states that it intends to operate locally or subprovincially.
+Our second independent variable is a dichotomous indicator of whether the INGO explicitly states that it intends to operate locally or sub-provincially.
 There are cases where the aim of the INGO is attached to a locality, either having a county or city name in their RO name or purposes, or the INGO is actually set up by people in China who registered the RO to communicate between the "hometown" and the INGO set up abroad.
@@
 There is great variance in the timing of registering an RO among INGOs, since there has been a *de facto* grace period for INGOs to seek legal presence after the law took effect [@Shieh:2018].
-This is largely because both INGOs and the regulators needed some transitional time to explore the specific implementation of the law as large ambiguity was left when the law was passed.
+This is largely because both INGOs and the regulators needed some transitional time to explore the specific application of the law as large ambiguity was left when the law was passed.
 We use this temporal variable as a proxy for the motivation or eagerness of INGOs to register an RO, for some INGOs are inclined to avoid the cumbersome registration procedures at the early stage if there is no real consequences for continuing operations without registration, while others took the time to talk with multiple potential PSUs to find a more suitable superior or regulatory dynamic.
-(TODO: find a citation for this, probably Spires, if there is one.)
+[@Jia:2017a]
 
@@
 Finally, temporary activities would be programs Chinese partners feel comfortable to collaborate in, i.e., safe activities with little political and administrative risks.
-So there is less flexibility in the kinds of work an INGO can with temporary activities.
+So there is less flexibility in the kinds of work an INGO can do with temporary activities.
 
 What factors could have contributed to the contrasting experiences of TNC and Greenpeace under the ONGO Law?
-After analyzing the data, the working approach and relationship with the government emerged as pivotal differences between the two INGOs, which fits existing discussions on the differential treatment of INGOs based on their relationship with the authority [TODO: add citations].
+After analyzing the data, the working approach and relationship with the government emerged as pivotal differences between the two INGOs, which fits existing discussions on the differential treatment of INGOs based on their relationship with the authority [@Plantan:2022].
 In a public interview with TNC’s RO in China about their registration experience, the chief representative stated TNC’s working approach in China has been “science-based”, using “non-confrontational, collaborative approach in working closely with governments, the business community and others” [@ChinaPhilanthropyReserchInstitute:2018a].
-Over the years, they have provided technical support for the central government and local governments like the Yunnan and Zhejiang Province to build national parks and nature reserve areas and helped drafted such documents as the China Biodiversity Conservation Strategy and Action Plan (2011-2030).
-Using the non-confrontational working model and establishing long partnerships with the government enabled TNC to secure the consent of a national governmental agency in corresponding issue area to be their PSU, and thus successfully got registered and authorized to operate in a relatively large number of provinces.
+Over the years, they have provided technical support for the central government and local governments like the Yunnan and Zhejiang Provinces to build national parks and nature reserve areas and helped drafted such documents as the China Biodiversity Conservation Strategy and Action Plan (2011-2030).
+Using the non-confrontational working model and establishing long partnerships with the government enabled TNC to secure the consent of a national governmental agency in corresponding issue area to be their PSU, and thus successfully got registered and authorized to operate in a larger number of provinces.
 In contrast, Greenpeace states in their mission that they work as “independent campaigning organizations that use peaceful protest and creative confrontation to expose global environmental problems”.
@@
 The case study shows that in addition to the correlation of issue area and operational space found in the quantitative model, the dimension of relationship with the government also exerts influence on the contentious level and restrictions INGOs can face, revealing the potential patterns of differential treatment INGOs can receive in the *de facto* implementation of the law.
+
+# Discussion and conclusion
+
+TODO: Andrew: Not fully exploring the TA thing here - that's in another paper
+
 Greenpeace also showed high organizational flexibility in the face of high legal barriers with the ONGO law : despite the various drawbacks discussed above, they were still able to keep conducting programs in China.
@@
 
-# Discussion and conclusion
-
-TODO: Andrew: Not fully exploring the TA thing here - that's in another paper
-
 # References
@@
 
+## Coding rules for issue ares
+
+1. Education vs. Charity
+If charitable activities are all education related, e.g. building schools, donating education facilities and books, coded as education
+If the aids provided include other community support, e.g. building bridges, roads, medical facilities, coded as charity
+
+2. Economy and trade vs. Industry association
+If the trade promoted is focused on a particular industry (poultry, grains etc.), coded as industry association
+
+3. Arts and culture 
+Include sports organizations too.
+
+4. Industry association vs. health, science and technology, arts and culture
+
+There are professional association on health providers and certain techniques.
+Coded as health, science & technology if work areas go beyond serving members only: for example conducting activities of promoting and training about certain techniques.
+
+If specialized association only serves the member companies: coded as industry associations
+
+5. Health vs. Charity 
+If only providing medical aids to underprivileged communities, not building schools etc., coded as health
+
+6. Charity vs. General 
+If multiple work, e.g., poverty alleviation, education, health can be encompassed by Charity and humanitarian, then the former
+
+7. Multiple ROs are coded based on the overall work area spans of the INGO, not the specific RO, so to ensure the issue area coding is consistent across ROs
+
 ::::

### 2023-12-04 manuscript/manuscript.qmd
Omitted a "TA"

@@
 #| fig-cap: "Two possible pathways for international NGOs to legally work in 
-#|   China under the 2017 ONGO law, either as formal Registered Organizations 
-#|   (ROs) or by undertaking specific Temporary Activities (TAs)"
+#|   China under the 2017 ONGO law, either as formal Representative Offices 
+#|   or by undertaking specific Temporary Activities"
 

### 2023-12-04 R/funs_graphics.R
Load ggrepel here so that label_repel's defaults can be set

@@ -1,6 +1,8 @@
 clrs <- MetBrewer::met.brewer("Tam")
 
 set_annotation_fonts <- function() {
+  library(ggrepel)
+  
   ggplot2::update_geom_defaults("label", list(family = "IBM Plex Sans Condensed", fontface = "plain"))
   ggplot2::update_geom_defaults("label_repel", list(family = "IBM Plex Sans Condensed", fontface = "plain"))
   ggplot2::update_geom_defaults("text", list(family = "IBM Plex Sans Condensed", fontface = "plain"))

### 2023-12-04 manuscript/manuscript.qmd
Get rid of moiré effect by using geom_area instead of geom_col

@@
   ggplot(aes(x = draw, y = prop)) +
-  geom_col(aes(fill = outcome), position = "stack", linewidth = 0, width = 1) +
+  geom_area(aes(fill = outcome), position = position_stack()) +
   geom_text(
@@
   ggplot(aes(x = draw, y = prop)) +
-  geom_col(aes(fill = outcome), position = position_stack(), linewidth = 0, width = 1) +
+  geom_area(aes(fill = outcome), position = position_stack()) +
   geom_text(

### 2023-12-04 manuscript/manuscript.qmd
Add conclusion skeleton

@@
 title: "Operational constraints and closing civic space: International NGO restrictions and China’s Overseas NGO law"
-short-title: "China's ONGO Law and International Civil Society"
+short-title: "Operational constraints and closing civic space"
 date: "2023-12-03"
@@
 
-# Results
+# Results and discussion
 
@@
 
-# Discussion and conclusion
+# Conclusion
+
+1. Summary
+2. Limitations
+3. Implications for policy/nonprofits
+4. Implications for future research
+
+(yay Marc Bellemare https://marcfbellemare.com/wordpress/12060)
 

### 2023-12-04 manuscript/manuscript.qmd
Consistently use 2016 law instead of 2017 law

@@
 abstract: |
-  TODO: **Update this based on the finished version of the paper.** China’s 2017 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international nongovernmental organizations (INGOs).
+  TODO: **Update this based on the finished version of the paper.** China’s 2016 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international nongovernmental organizations (INGOs).
 However, the effects of this global crackdown on INGOs have been difficult to measure since there is often divergence between the formal de jure regulations and the de facto implementation of these laws.
@@
 We argue that the less contentious the issue areas INGOs work in the more likely they are granted greater operational space, measured by the number of provinces they are legally authorized to work in.
-China provides an excellent setting for examining the phenomenon of closing space civic space, since the 2017 ONGO law hypothetically regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities.
+China provides an excellent setting for examining the phenomenon of closing space civic space, since the 2016 ONGO law hypothetically regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities.
 We test our argument by analyzing administrative data from 633 registered representative offices of INGOs registered in China between 2017–2021 and test our hypothesis with a multilevel Bayesian model.
@@
 As an authoritarian state with a growing nonprofit sector, China's regulatory regime for INGOs serves as an important example for understanding and exploring how autocracies use restrictive laws as policy tools as they engage with international civil society.
-The restrictive policies implemented by China's 2017 ONGO law serve dueling purposes that both harness the benefits and reduce the risks of INGOs.
+The restrictive policies implemented by China's 2016 ONGO law serve dueling purposes that both harness the benefits and reduce the risks of INGOs.
 The law is designed to decrease demand for foreign civil society organizations and limit the influence they might have over domestic policies [@DeMattee:2018; @DeMattee:2019], while also allowing the regime to benefit from the expertise, services, and reputational advantages of working partnering with international civil society [@Plantan:2022; @Heiss:2019].
@@
 
-In this paper, we use the case of China to explore how the dual demands to both restrict and embrace INGOs have shaped the international nonprofit sector in the five years since the 2017 ONGO Law came into effect.
+In this paper, we use the case of China to explore how the dual demands to both restrict and embrace INGOs have shaped the international nonprofit sector in the five years since the 2016 ONGO Law came into effect.
 We examine how the ONGO Law has influenced the population of INGOs that have successfully registered in China, as well as the association between factors such as INGO issue areas and the operational space granted to them in the country.
@@
 Since then, INGOs and global civil society have played pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China's domestic nonprofit sector [@Yin:2009].
-Prior to the implementation of the 2017 ONGO Law, regulation of INGOs in China was ambiguous [@Shieh:2018; @Spires:2022].
+Prior to the implementation of the 2016 ONGO Law, regulation of INGOs in China was ambiguous [@Shieh:2018; @Spires:2022].
 The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations that specifies the registration of ROs of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic nonprofits.
@@
 #| fig-cap: "Two possible pathways for international NGOs to legally work in 
-#|   China under the 2017 ONGO law, either as formal Representative Offices 
+#|   China under the 2016 ONGO law, either as formal Representative Offices 
 #|   or by undertaking specific Temporary Activities"
@@
 
-The 2017 ONGO Law's provision of two legal pathways for registration---each with different degrees of freedom---is an example of the broader phenomenon of closing civic space.
+The 2016 ONGO Law's provision of two legal pathways for registration---each with different degrees of freedom---is an example of the broader phenomenon of closing civic space.
 In the past two decades, authoritarian states have used administrative and legal measures to control and curtail the influence of global civil society.
@@
 #| echo: false
-#| fig-cap: "Count of international NGO registrations under the 2017 ONGO Law, divided by quarters"
+#| fig-cap: "Count of international NGO registrations under the 2016 ONGO Law, divided by quarters"
 ggplot(ongo, aes(x = registration_date)) +

### 2023-12-05 manuscript/manuscript.qmd
Add conclusion!

@@
 
-1. Summary
-2. Limitations
-3. Implications for policy/nonprofits
-4. Implications for future research
-
-(yay Marc Bellemare https://marcfbellemare.com/wordpress/12060)
-
-TODO: Andrew: Not fully exploring the TA thing here - that's in another paper
-
-Greenpeace also showed high organizational flexibility in the face of high legal barriers with the ONGO law : despite the various drawbacks discussed above, they were still able to keep conducting programs in China.
-A more evasive group of INGOs after the ONGO law would be those not having the same level of flexibility as Greenpeace and have left China either not choosing to seek registration or failed to do so and not able file temporary activities constantly.
-The variance in organizational flexibility can be worthy of further research.
+Political institutions are central to authoritarian stability as autocrats work to co-opt and balance institutional challenges to their regime.
+Autocrats treat civil society—both domestic and international—as yet another actor in their stability-seeking calculus.
+The ongoing phenomenon of closing civic space, where governments worldwide continue to impose repressive regulations on civil society, can be seen as a strategy for stabilizing authoritarian rule [@DeMattee:2019; @CarothersBrechenmacher:2014; @Heiss:2019].
+Notably, these laws are not enforced universally or consistently.
+The strategic enforcement of civil society laws creates a divergence between formal *de jure* regulations and the *de facto* implementation of those laws.
+Formal laws provide a legal framework for regulating INGOs, but government flexibility in enforcing those laws allows regimes to (1) act leniently towards organizations that offer services and expertise that benefit the regime, and (2) restrict, repress, or expel organizations that are deemed a risk to regime stability.
+
+We argue that regime preferences interact with organizations' issue areas to create variation in INGO operational space, or the *de facto* regulatory environment afforded to INGOs.
+We explore this theory by analyzing a novel dataset of all INGOs that have successfully registered in China since the implementation of the 2016 ONGO Law, a legal mechanism that provided the government with the ability to grow and shrink INGO operational space in strategic ways.
+By focusing on a specific law in one country, our work provides rich empirical illustrations of the mechanics of authoritarian administrative crackdown.
+We find that INGOs that work on issues that are less threatening and more aligned with regime preferences—such as arts & culture INGOs, industry associations, and scientific organizations—are registered in more provinces and thus enjoy a greater degree of operational space, while organizations that pose a potential threat—like education INGOs—are far more limited geographically.
+Our case study finds similar results.
+Because of its less confrontational approach and its connections to local government officials, The Nature Conservancy was able to obtain RO status and benefit from increased operational space while the more advocacy-focused Greenpeace has resorted to filing dozens of program-specific temporary activities.
+
+Studying INGOs in authoritarian regimes poses a number of limitations, but the concept of operational space can address some of these issues in the future.
+First, we can only observe organizations that successfully registered as ROs.
+We cannot make comparisons with INGOs that left the country prior to 2017 or INGOs that have explicitly chosen to not work in China.
+This is not an issue specific to China—analyzing the international nonprofit sector of any country that has passed similar laws will raise similar issues of selection bias.
+The Chinese context provides one possible way forward: future research can further explore relationship between INGOs and regime preferences by comparing characteristics of INGOs that register as ROs or undertake temporary activities using already-available administrative data.
+Second, this paper focuses exclusively on INGO regulations in China, and the specific legal mechanisms for controlling INGOs in other countries will naturally differ.
+However, the findings are still instructive.
+We have illustrated how the interpretation and implementation of one INGO law has reshaped the role of international civil society, leading to a preponderance of regime-friendly NGOs, many of which have realigned their programming with government preferences.
+It is likely that a similar dynamic plays out in other countries—regimes legislate civil society broadly and enforce those laws specifically and individually.
+Future research can analyze the determinants of INGO operational space in other authoritarian states, which can help INGOs facing legal crackdown abroad strengthen their organizational flexibility in the face of restricted legal environments.
 

### 2023-12-05 manuscript/manuscript.qmd
Move long-running plot-making code to targets

@@
 ))
+tar_load(c(preds_issue_plot, preds_local_plot, preds_timing_plot))
 
@@
 
-preds_issue_plot <- preds_issue |> 
-  left_join(issue_indicator_lookup, by = join_by(issue_area)) |> 
-  mutate(outcome = case_when(
-    .prediction == 0 ~ "Only 1 province",
-    .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
-    .prediction == 1 ~ "All 32 provinces",
-    .ptype = factor(
-      levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"), 
-      ordered = TRUE)
-  )) |> 
-  group_by(outcome, issue_area_nice, draw) |> 
-  summarize(count = n()) |> 
-  group_by(issue_area_nice, draw) |> 
-  mutate(prop = count / sum(count))
-
 preds_issue_plot_order <- preds_issue_plot |> 
@@
 
-preds_local_plot <- preds_local |> 
-  unnest(preds) |> 
-  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
-  mutate(outcome = case_when(
-    .prediction == 0 ~ "Only 1 province",
-    .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
-    .prediction == 1 ~ "All 32 provinces",
-    .ptype = factor(
-      levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"), 
-      ordered = TRUE)
-  )) |> 
-  group_by(outcome, local_connect, draw) |> 
-  summarize(count = n()) |> 
-  group_by(local_connect, draw) |> 
-  mutate(prop = count / sum(count))
-
 preds_local_text <- preds_local_plot |> 
@@
 #|   and 95% credible intervals."
-
-preds_timing_plot <- preds_timing |> 
-  unnest(preds) |> 
-  mutate(outcome = case_when(
-    .prediction == 0 ~ "Only 1 province",
-    .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
-    .prediction == 1 ~ "All 32 provinces",
-    .ptype = factor(
-      levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"), 
-      ordered = TRUE)
-  )) |> 
-  mutate(years_since_law = 2017 + years_since_law) |> 
-  group_by(outcome, years_since_law, draw) |>
-  summarize(count = n()) |> 
-  group_by(years_since_law) |> 
-  mutate(prop = count / sum(count) * 100)
 

### 2023-12-05 R/funs_plots_tables.R

@@ -36,3 +36,83 @@ gt_pct <- function(x, page_width = 6) {
     gt::pct(x)
   }
 }
+
+
+# Storing ggplot objects as rds files is BAD 
+#   (https://github.com/hadley/ggplot2-book/issues/344)
+#
+# But in this project, the posterior predictions plots take a while to build and
+# making them targets would speed things up. And storing plots as targets is
+# recommended when working with {targets}---the basic walkthrough in the manual
+# even shows how to create a plot as a target.
+# 
+# ggplot objects are strange beasts because they store a copy of the overall
+# environment when serialized into rds files. When working with regular-sized
+# datasets, this isn't really ever a problem. But when working with tidy
+# data frames of MCMC chains with millions and millions of rows, this can create
+# rds files that are hundreds or thousands of MBs, which is wild.
+#
+# This post goes into more details about how to fix it: 
+# https://ropensci.org/blog/2022/12/06/save-ggplot2-targets/
+#
+# The easiest way to fix it is to just not store the plot and instead store the
+# underlying data, since that takes the most computational time. Here, we build
+# the plot-specific data frames so that the manuscript renders more quickly.
+build_preds_issue_plot_data <- function(preds, lookup) {
+  preds_issue_plot <- preds |> 
+    left_join(lookup, by = join_by(issue_area)) |> 
+    mutate(outcome = case_when(
+      .prediction == 0 ~ "Only 1 province",
+      .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
+      .prediction == 1 ~ "All 32 provinces",
+      .ptype = factor(
+        levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"), 
+        ordered = TRUE)
+    )) |> 
+    group_by(outcome, issue_area_nice, draw) |> 
+    summarize(count = n()) |> 
+    group_by(issue_area_nice, draw) |> 
+    mutate(prop = count / sum(count))
+  
+  return(preds_issue_plot)
+}
+
+build_preds_local_plot_data <- function(preds) {
+  preds_local_plot <- preds |> 
+    unnest(preds) |> 
+    mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
+    mutate(outcome = case_when(
+      .prediction == 0 ~ "Only 1 province",
[…]

### 2023-12-05 _targets.R

@@ -80,6 +80,10 @@ list(
   tar_target(epreds_timing, f_epreds_timing(m_full_ordbeta)),
   tar_target(epreds_timing_local, f_epreds_timing_local(m_full_ordbeta_interaction)),
   
+  tar_target(preds_issue_plot, build_preds_issue_plot_data(preds_issue, issue_indicator_lookup)),
+  tar_target(preds_local_plot, build_preds_local_plot_data(preds_local)),
+  tar_target(preds_timing_plot, build_preds_timing_plot_data(preds_timing)),
+  
   ## Analysis notebook ----
   tar_quarto(manuscript_nice, path = "manuscript", quiet = FALSE, profile = "nice"),
   tar_quarto(manuscript_manuscripty, path = "manuscript", quiet = FALSE, profile = "ms"),

### 2023-12-05 R/funs_graphics.R
Only set default repelled label font if ggrepel is loaded

@@ -1,11 +1,12 @@
 clrs <- MetBrewer::met.brewer("Tam")
 
 set_annotation_fonts <- function() {
-  library(ggrepel)
-  
   ggplot2::update_geom_defaults("label", list(family = "IBM Plex Sans Condensed", fontface = "plain"))
-  ggplot2::update_geom_defaults("label_repel", list(family = "IBM Plex Sans Condensed", fontface = "plain"))
   ggplot2::update_geom_defaults("text", list(family = "IBM Plex Sans Condensed", fontface = "plain"))
+
+  if (isNamespaceLoaded("ggrepel")) {
+    ggplot2::update_geom_defaults("label_repel", list(family = "IBM Plex Sans Condensed", fontface = "plain"))
+  }
 }
 
 theme_ongo <- function(base_size = 11, base_family = "IBM Plex Sans Condensed", prior = FALSE) {

### 2023-12-05 manuscript/manuscript.qmd
Add thin colored border on geom_area to avoid anti-aliasing issues

@@
   ggplot(aes(x = draw, y = prop)) +
-  geom_area(aes(fill = outcome), position = position_stack()) +
+  geom_area(
+    aes(fill = outcome, color = after_scale(fill)), 
+    position = position_stack(), linewidth = 0.1
+  ) +
   geom_text(

### 2023-12-05 manuscript/manuscript.qmd
Move lots of figure caption details to labs()

--- 2023-12-05 manuscript/manuscript.qmd
@@
 library(patchwork)
+library(glue)
 library(gt)
@@
 
-```{r fig-issue-preds, fig.width=8, fig.height=6}
+```{r fig-issue-preds, fig.width=8, fig.height=6.5}
 #| include: true
@@
 #| column: body-outset
-#| fig-cap: "**A**: Posterior predictions from ordered Beta regression model,
-#|   conditional on organization issue area, showing the predicted proportion of
-#|   INGOs working in 1 province, all 32 provinces, or somewhere in between. The
-#|   vertical slices of the bars depict 500 posterior samples; the fuzziness
-#|   represents the uncertainty in category boundaries. 95% credible intervals 
-#|   are shown as ranges in each category. **B**: Expectation (or average) of
-#|   posterior predictive distributions. These distributions take into account 
-#|   single-province and nationwide predictions and represent the *overall*
-#|   conditional average geographic range for INGOs. Points show posterior 
-#|   median; lines show 80% and 95% credible intervals."
+#| fig-cap: "Posterior predictions conditional on organization issue area. 
+#|   **A**: Predicted proportion of INGOs working in 1 province, all 32 
+#|   provinces, or somewhere in between. 
+#|   **B**: Expectation of posterior predictive distributions."
 
@@
   ggplot(aes(x = draw, y = prop)) +
-  geom_area(aes(fill = outcome), position = position_stack()) +
+  geom_area(
+    aes(fill = outcome, color = after_scale(fill)),
+    position = position_stack(), linewidth = 0.1
+  ) +
   geom_text(
@@
     subtitle = "Posterior predictions of outcome categories",
-    tag = "A"
+    tag = "A",
+    caption = str_wrap(
+      glue(
+        "The vertical slices of the bars depict 500 posterior samples;",
+        "the fuzziness represents the uncertainty in category boundaries.",
+        "95% credible intervals are shown as ranges in each category",
+        .sep = " "
+      ),
+      width = 120
+    )
   ) +
@@
     title = "Expected count of provinces",
-    subtitle = "Expectation of posterior predictions",
-    tag = "B"
+    subtitle = "Expectation (or average) of posterior predictions",
+    tag = "B",
+    caption = str_wrap(
+      glue(
+        "These distributions take into account single-province and nationwide predictions",
+        "and represent the overall conditional average geographic range for INGOs.",
+        "Points show posterior median; lines show 80% and 95% intervals.",
+        .sep = " "
+      ),
+      width = 120
+    )
   ) +
@@
 
-(p1 / plot_spacer() / p2) +
-  plot_layout(heights = c(0.65, 0.02, 0.33))
+p1 / p2
 ```
@@
 
-```{r fig-local-preds, fig.width=8, fig.height=4}
+```{r fig-local-preds, fig.width=8, fig.height=4.5}
 #| include: true
 #| echo: false
-#| fig-cap: "Posterior predictions from ordered Beta regression model, 
-#|   conditional on having local connections. **A**: Predicted proportion of 
-#|   INGOs working in 1 province, all 32 provinces, or somewhere in between. 
-#|   The vertical slices of the bars depict 500 posterior samples; the fuzziness 
-#|   represents the uncertainty in category boundaries. 95% credible intervals 
-#|   are shown as ranges in each category. **B**: Expectation (or average) of 
-#|   posterior predictive distributions. These distributions take into account 
-#|   single-province and nationwide predictions and represent the *overall* 
-#|   conditional average geographic range for INGOs. Points show posterior 
-#|   median; lines show 80% and 95% credible intervals."
+#| fig-cap: "Posterior predictions conditional on having local connections. 
+#|   **A**: Predicted proportion of INGOs working in 1 province, all 32 
+#|   provinces, or somewhere in between. 
+#|   **B**: Expectation of posterior predictive distributions."
 
@@
     subtitle = "Posterior predictions of outcome categories",
-    tag = "A"
+    tag = "A",
+    caption = str_wrap(
+      glue(
+        "The vertical slices of the bars depict 500 posterior samples;",
+        "the fuzziness represents the uncertainty in category boundaries.",
+        "95% credible intervals are shown as ranges in each category",
+        .sep = " "
+      ),
+      width = 80
+    )
   ) +
@@
     title = "Expected count of provinces",
-    subtitle = "Expectation of posterior predictions",
-    tag = "B"
+    subtitle = "Expectation (or average) of posterior predictions",
+    tag = "B",
+    caption = str_wrap(
+      glue(
+        "These distributions take into account single-province and nationwide predictions",
+        "and represent the overall conditional average geographic range for INGOs.",
+        "Points show posterior median; lines show 80% and 95% intervals.",
+        .sep = " "
+      ),
+      width = 50
+    )
   ) +
@@
 (p1 | p2) +
-  plot_layout(widths = c(0.6, 0.4))
+  plot_layout(widths = c(0.63, 0.37), guides = "collect")
 ```
@@
 
-```{r fig-timing-preds, fig.width=8, fig.height=4}
+```{r fig-timing-preds, fig.width=8, fig.height=4.5}
 #| include: true
 #| echo: false
-#| fig-cap: "Posterior predictions from ordered Beta regression model, 
-#|   conditional on time since law took effect in January 2017. **A**: Predicted 
-#|   proportion of INGOs working in 1 province, all 32 provinces, or somewhere 
-#|   in between. Filled areas depict 50 posterior samples of the outcome category 
-#|   probabilities, so the fuzziness represents the uncertainty in category 
-#|   boundaries. **B**: Expectation (or average) of posterior predictive 
-#|   distributions. This distribution takes into account single-province and 
-#|   nationwide predictions and represents the *overall* conditional average 
-#|   geographic range for INGOs over time. Shaded regions show the 50%, 80%, 
-#|   and 95% credible intervals."
+#| fig-cap: "Posterior predictions conditional on time since law took effect. 
+#|   **A**: Predicted proportion of INGOs working in 1 province, all 32 
+#|   provinces, or somewhere in between. 
+#|   **B**: Expectation of posterior predictive distributions."
 
@@
     subtitle = "Posterior predictions of outcome categories",
-    tag = "A"
+    tag = "A",
+    caption = str_wrap(
+      glue(
+        "Filled areas depict 50 posterior samples of the outcome category probabilities,",
+        "so the fuzziness represents the uncertainty in category boundaries; ",
+        .sep = " "
+      ),
+      width = 60
+    )
   ) +
@@
     title = "Expected count of provinces",
-    subtitle = "Expectation of posterior predictions",
-    tag = "B"
+    subtitle = "Expectation (or average) of posterior predictions",
+    tag = "B",
+    caption = str_wrap(
+      glue(
+        "This distribution takes into account single-province and nationwide",
+        "predictions and represents the overall conditional average geographic",
+        "range for INGOs over time.",
+        "Shaded regions show the 50%, 80%, and 95% credible intervals.",
+        .sep = " "
+      ),
+      width = 65
+    )
   ) +
@@
 
-```{r fig-timing-local, fig.width=6, fig.height=3, out.width="80%"}
+```{r fig-timing-local, fig.width=6, fig.height=3.4, out.width="80%"}
 #| include: true
 #| echo: false
-#| fig-cap: "Expectation (or average) of posterior predictive distributions 
-#|   from model with interaction between local connections and time since 
-#|   January 2017. These predictions take into account single-province and 
-#|   nationwide predictions and represent the overall conditional average 
-#|   geographic range for INGOs over time across, conditional on local 
-#|   connections. Shaded regions show the 50%, 80%, and 95% credible intervals"
+#| fig-cap: "Expectation of posterior predictive distributions from model with 
+#|   interaction between local connections and time since January 2017."
 
@@
     title = "Expected count of provinces across local connections",
-    subtitle = "Expectation of posterior predictions"
+    subtitle = "Expectation of posterior predictions",
+    caption = str_wrap(
+      glue(
+        "These distributions take into account single-province and nationwide",
+        "predictions and represents the overall conditional average geographic",
+        "range for INGOs over time.",
+        "Shaded regions show the 50%, 80%, and 95% credible intervals.",
+        .sep = " "
+      ),
+      width = 90
+    )
   ) +

### 2023-12-05 R/funs_graphics.R

@@ -15,7 +15,7 @@ theme_ongo <- function(base_size = 11, base_family = "IBM Plex Sans Condensed", 
           title = element_text(size = rel(1), family = "IBM Plex Sans Condensed", face = "bold"),
           plot.subtitle = element_text(size = rel(0.8),
                                        family = "IBM Plex Sans Condensed", face = "plain"),
-          plot.caption = element_text(margin = margin(t = 10), size = rel(0.75),
+          plot.caption = element_text(margin = margin(t = 10), size = rel(0.75), hjust = 0,
                                       family = "IBM Plex Sans Condensed", face = "plain"),
           panel.border = element_rect(color = "grey50", fill = NA, linewidth = 0.15),
           panel.spacing = unit(1, "lines"),

### 2023-12-05 manuscript/manuscript.qmd
Shrink/edit intro and legal framework
Word count is now under 9,000!

@@
 In the past two decades, nearly 100 countries have proposed or enacted legal measures designed to restrict nongovernmental organizations (NGOs) and civil society more broadly [@Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016].[^ngo-clarification] According to the CIVICUS Civil Society Monitor, as of 2023 only `r civicus_prop$true$prop_nice` of countries have open and unrestricted civic space [@ChaudhryHeiss:2022a; @CIVICUSMonitor].
-This global trend of closing or shrinking civic space has affected countries of all regime types, including both autocracies and democracies such as Morocco and Palestine [@AtiaHerrold:2018], India [@press-trust-india:2019], Vietnam [@Sidel:2023], Canada [@CIVICUS:2013], and the United States [@Cramer:2020].
 On April 28, 2016, China passed its own set of civil society restrictions with its Law of the People's Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China---or "2016 ONGO Law"---which formally took effect on January 1, 2017.
@@
 [^ngo-clarification]: "Civil society" is a broad concept that includes a range of organizational forms, both formal and informal.
-In this paper, we look at nongovernmental organizations (NGOs), often called nonprofit organizations or third sector organizations---formal non-profit-seeking organizations that are neither privately-owned nor government-controlled.
-We define international NGOs as organizations that conduct work predominantly in at least one other country outside of their home country.
-
-As an authoritarian state with a growing nonprofit sector, China's regulatory regime for INGOs serves as an important example for understanding and exploring how autocracies use restrictive laws as policy tools as they engage with international civil society.
-The restrictive policies implemented by China's 2016 ONGO law serve dueling purposes that both harness the benefits and reduce the risks of INGOs.
-The law is designed to decrease demand for foreign civil society organizations and limit the influence they might have over domestic policies [@DeMattee:2018; @DeMattee:2019], while also allowing the regime to benefit from the expertise, services, and reputational advantages of working partnering with international civil society [@Plantan:2022; @Heiss:2019].
-These dual demands lead to differential enforcement of civil society laws and a divergence between formal *de jure* regulations and the *de facto* implementation of those laws [@ChaudhryHeiss:2022], as the government enforces civil society regulations selectively depending on regime preferences for INGO services.
-
-In this paper, we use the case of China to explore how the dual demands to both restrict and embrace INGOs have shaped the international nonprofit sector in the five years since the 2016 ONGO Law came into effect.
+In this paper, we look at nonprofit organizations or third sector organizations---formal non-profit-seeking organizations that are neither privately-owned nor government-controlled.
+We define international NGOs as organizations that work predominantly in at least one other country outside of their home country.
+
+As an authoritarian state with a growing nonprofit sector, China's regulatory regime for INGOs serves as an example for understanding how autocracies use restrictive laws as policy tools as they engage with international civil society.
+The policies implemented by China's 2016 ONGO law serve dueling purposes that both harness the benefits and reduce the risks of INGOs.
+The law is designed to decrease demand for foreign civil society organizations and limit the influence they might have over domestic policies [@DeMattee:2018; @DeMattee:2019] while also allowing the regime to benefit from the expertise, services, and reputational advantages of working partnering with international civil society [@Plantan:2022; @Heiss:2019].
+These dual demands lead to differential enforcement and divergence between formal *de jure* regulations and the *de facto* implementation of those laws [@ChaudhryHeiss:2022], as the government enforces regulations selectively depending on regime preferences for INGO services.
+
+In this paper, we use the case of China to explore how the demands to both restrict and embrace INGOs have shaped the international nonprofit sector in the five years since the 2016 ONGO Law came into effect.
 We examine how the ONGO Law has influenced the population of INGOs that have successfully registered in China, as well as the association between factors such as INGO issue areas and the operational space granted to them in the country.
-Through our study, we make several contributions to a growing body of research on the effects of closing civic space on INGO behavior and strategies.
+We contribute to a growing body of research on the effects of closing civic space on INGO behavior and strategies.
 First, we expand work that uses institutional approaches to understanding civil society regulations, which argues that states strategically regulate INGOs to maintain regime stability, choosing forms of regulation and repression that minimize threats to internal political stability [@Chaudhry:2022; @DeMattee:2018; @DeMattee:2019; @Heiss:2019].
-Second, we explore how authoritarian civil society regulations act as policy tools that regimes can leverage to shift INGO behavior in their favor and how restrictive laws can reshape and tame organizational strategies [@Li:2020; @WuNie:2021; @LianMurdie:2023].
+Second, we explore how authoritarian civil society regulations act as policy tools that regimes can leverage to shift INGO behavior in their favor and how these laws reshape and tame organizational strategies [@Li:2020; @WuNie:2021; @LianMurdie:2023].
 Third, we explore how these regulations lead to differentiated application of the law depending on organizational characteristics.
@@
 By focusing on INGO operational space in China, we provide a unique empirical view into the *de facto* regulatory environment for foreign civil society in an authoritarian state.
-Many previous studies use broad indexes of civil society openness, such as the core civil society index from the Varieties of Democracy project [@LianMurdie:2023; @ChaudhryHeiss:2022].
-These measures capture the general regulatory environment for all civil society---including domestic NGOs, INGOs, and informal organizations---but do not reflect the specific implementation of laws for INGOs.
-In this paper, though, we use a mixed methods approach to explore the regulatory environment for INGOs in particular, providing a much richer description and analysis of the impact of INGO laws.
-
-Below, we provide a brief overview of China's 2016 ONGO Law and the different regulatory mechanisms---and practical limitations---it provides for INGOs to obtain legal access to the country.
-We then summarize existing research on authoritarian regulation of INGOs and the differential application of these laws based on regime preferences and organizational characteristics, and propose a set of empirical expectations based on this literature.
-We test these expectations with a mixed methods research design, combining Bayeisan analysis of administrative data from `r nrow(ongo)` formally registered INGOs with a comparative case study of Greenpeace and The Nature Conservancy, two INGOs working on similar issue areas which took different approaches to operating in China after 2017.
-We conclude with a broader discussion of authoritarian civil society regulations and propose future methods for exploring the practical operating environment for INGOs working in such regimes.
+Broader indexes of civil society openness---such as the core civil society index from the Varieties of Democracy project [@LianMurdie:2023; @ChaudhryHeiss:2022]---capture the general regulatory environment for all civil society more broadly, but do not reflect the specific implementation of laws for INGOs.
+In this paper, we use a mixed methods approach to explore the regulatory environment for INGOs in particular, providing a much richer description and analysis of the impact of INGO laws.
+
+Below, we provide a brief overview of China's 2016 ONGO Law and the different regulatory mechanisms it provides for INGOs to obtain legal access to the country.
+We then synthesize existing research on authoritarian regulation of INGOs and the differential application of these laws based on regime preferences and organizational characteristics, and propose a set of empirical expectations based on this literature.
+We test these expectations with a mixed methods research design, combining Bayesian analysis of administrative data from all `r nrow(ongo)` formally registered INGOs with a comparative case study of Greenpeace and The Nature Conservancy, two environmental INGOs that took different approaches to operating in China after 2017.
+We conclude with a broader discussion of authoritarian civil society regulations and propose future approaches for exploring the practical operating environment for INGOs working in such regimes.
 
@@
 
-International NGOs began to play an important role in China in the early 1990s as part of the country's Reform and Opening-Up policy, and organizations such as Save the Children and the Ford Foundation established local offices.
-Since then, INGOs and global civil society have played pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China's domestic nonprofit sector [@Yin:2009].
-Prior to the implementation of the 2016 ONGO Law, regulation of INGOs in China was ambiguous [@Shieh:2018; @Spires:2022].
-The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations that specifies the registration of ROs of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic nonprofits.
-However, the actual application of the regulation was very limited: until the ONGO Law took effect in 2017, there were fewer than 30 foreign foundation ROs registered, while some Chinese officials estimated in 2016 that there were roughly over 7,000 INGOs operating in China [@YeHuang:2018; @Spires:2020].
-
-Many INGOs gained legal status by registering as foreign-invested companies [@Sidel:2016], for the administrative convenience such as hiring employees [@HolbigLang:2022; @Yin:2009].
-However, such a legal form is not quite compatible with the non-profit-distributing nature of INGOs.
-Chinese companies are intended to be for-profit only, while nonprofits are regulated under other legal forms, such as foundations and social service organizations [@Ye:2021].
-Thus, INGOs registered ad foreign-invested companies had to navigate through for-profit institutional logics, with doctrines like protecting shareholders' investment returns.
-
-The legal framework governing INGOs was overhauled by the 2016 ONGO Law.
-The new law applies to all overseas (including Hong Kong, Macau, and Taiwan) NGOs that conduct not-for-profit activities in the fields of economic development, education, science, technology, culture, public health, sports, environment protection, poverty alleviation, and disaster relief.
-The ONGO Law provides two pathways for INGOs to lawfully operate in China (see @fig-ro-ta-pathways): (1) submitting an application for formal permanent registration as ROs, or (2) filing documentation of temporary activities with the Public Security Bureaus.
+International NGOs began to play an important role in China in the early 1990s as part of the country's Reform and Opening-Up policy, and global civil society has played pivotal roles in providing funding, organizational and program management skills, and catalytic support for China's emerging domestic nonprofit sector [@Yin:2009].
+Before the 2016 ONGO Law, the regulation of INGOs in China was ambiguous [@Shieh:2018; @Spires:2022].
+The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations, which required that foreign foundations register with the Ministry of Civil Affairs, the regulating agency for domestic nonprofits.
+However, the actual application of the regulation was very limited: fewer than 30 foreign foundations registered, compared to estimates of over 7,000 INGOs working in China in 2016 [@YeHuang:2018; @Spires:2020].
+Many INGOs gained legal status by registering as foreign-invested companies [@Sidel:2016], allowing them to hire local employees [@HolbigLang:2022; @Yin:2009].
+However, this legal form is not quite compatible with the non-profit-distributing, social service orientation of civil society [@Ye:2021].
+INGOs registered as foreign-invested companies had to navigate incongruous for-profit regulations, such as rules protecting shareholders' investment returns.
+
+The legal framework governing INGOs was overhauled by the 2016 ONGO Law, which applies to all overseas (including Hong Kong, Macau, and Taiwan) NGOs that conduct not-for-profit activities in mainland China.
+The ONGO Law provides two pathways for INGOs to lawfully operate in China (see @fig-ro-ta-pathways): (1) submitting an application for formal permanent registration as registered organizations (ROs), or (2) filing documentation of temporary activities with provincial Public Security Bureaus.
 Formal registration as an RO allows INGOs to maintain an ongoing presence in the country, while temporary activities are intended for INGOs that need to conduct one-off programs that last no longer than one year.
 Using one of these two channels to obtain legal status became mandatory in 2017.
+INGOs are authorized to operate within China on a province-by-province basis.
+Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.
 
@@
 #| fig-cap: "Two possible pathways for international NGOs to legally work in 
-#|   China under the 2016 ONGO law, either as formal Representative Offices 
-#|   or by undertaking specific Temporary Activities"
+#|   China under the 2016 ONGO law"
 
@@
 
-Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus.
-Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018].
-Organizations vary in their ability to attract partner PSUs, and INGOs that are unable to find suitable PSUs can end up not being able to registered or registered with great limitation in terms of work areas and geographical reach.
-INGOs are authorized to operate within China on a province-by-province basis.
-Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.
-Similarly, INGOs need to find an eligible Chinese partner, including governmental, quasi-governmental and non-profit organizations to file temporary activities for them.
-After successfully gaining legal status, INGOs also need to abide by the operational regulations by the law, such as no fundraising within mainland China, only channeling the funds through RO's registered account or the Chinese partners' accounts, filing reports regularly and stay within the geographical and issue scopes as approved.
+Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental agency related to an INGO's issue area that oversees and co-supervises the INGO with provincial Public Security Bureaus.
+Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, as potential PSUs have no legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018].
+INGOs vary in their ability to attract partner PSUs, and organizations that struggle to find suitable PSUs face limitations in their scope and geographic reach.
+After successfully gaining legal status, INGOs must follow the law's operational regulations, such as no fundraising within mainland China, only channeling funds through the RO's or PSU's bank accounts, filing reports regularly, and staying within the geographical and issue scopes as approved.
+INGOs undertaking temporary activities also need to find an eligible Chinese partner---including governmental, quasi-governmental, or non-profit organizations---and must keep their programs within approved limits, but the process is less onerous.
 

### 2023-12-05 manuscript/manuscript.qmd
Shrink authoritarian institutions section

@@
 The 2016 ONGO Law's provision of two legal pathways for registration---each with different degrees of freedom---is an example of the broader phenomenon of closing civic space.
-In the past two decades, authoritarian states have used administrative and legal measures to control and curtail the influence of global civil society.
+In the past two decades, authoritarian states have used administrative and legal measures to curtail the influence of global civil society.
 A rich literature in comparative politics explores how authoritarian regimes counterintuitively use democratic institutions for their own benefit and survival [@Kendall-TaylorFrantz:2014a; @GandhiPrzeworski:2007].
-Authoritarian states hold elections [@LevitskyWay:2010], permit popular protests [@Weiss:2013], and allow opposition parties in the legislature and set executive term limits [@Meng:2020].
-However, autocrats use these democratic-appearing institutions to limit possible threats to regime stability.
-Elections, protests, and apparent political reform are allowed, but only in ways that bolster the government's stability, and these institutions are kept weak and "dependent on the regime to ensure that they do not develop any real power or autonomy" [@FrantzEzrow:2011, 7].
-
-Civil society organizations are another political institution that autocrats must balance as part of their stability-seeking calculus.
+Authoritarian states hold elections, allow opposition parties in the legislature, and set executive term limits [@LevitskyWay:2010; @Meng:2020], but use these democratic-appearing institutions to hedge against possible threats to regime stability.
+Quasi-democratic institutions are allowed, but only in ways that bolster the government's stability, and these institutions are kept weak and "dependent on the regime to ensure that they do not develop any real power or autonomy" [@FrantzEzrow:2011, 7].
+
+Civil society is a democratic political institution that autocrats balance as part of their stability-seeking calculus.
 Despite the fact that NGOs can act as "agents of democratization" [@ToeplerZimmerFrohlich:2020], thus posing a threat to non-democratic rule, most authoritarian states permit the growth of domestic and international civil society [@DeMattee:2019; @Heiss:2019; @Heiss:2019a].
-INGOs provide needed resources and expertise in humanitarian relief, environmental policy, education, development, and autocrats can rely on these services to strengthen their regime by providing better public goods.
+INGOs provide needed resources and expertise in humanitarian relief, environmental policy, education, development, and autocrats can rely on these services to consolidate power by providing improved public goods.
 At the same time, INGOs can pose a threat to stability by exposing human rights abuses, encouraging unwanted political reform, and engaging in political advocacy [@Heiss:2019; @ToeplerZimmerFrohlich:2020].
-To capture the benefits and reduce the risk of working with global civil society, most authoritarian states regulate civil society in nonviolent ways.
-Instead of beating activists or arresting NGO leaders, states have relied on "administrative crackdown," [@Chaudhry:2022] or laws that create barriers to NGO advocacy, entry, and funding [@ChristensenWeinstein:2013; @ChaudhryHeiss:2022; @CarothersBrechenmacher:2014].
-
-These laws, however, are a blunt tool that tend to target civil society as a whole---authoritarian states do not create one set of formal laws that applies only to regime-friendly INGOs and another set that applies to more risky INGOs.
+To capture the benefits and reduce the risk of working with INGOs, most authoritarian states rely on "administrative crackdown," [@Chaudhry:2022] or laws that create barriers to NGO advocacy, entry, and funding [@ChristensenWeinstein:2013; @ChaudhryHeiss:2022; @CarothersBrechenmacher:2014].
+These laws, however, are a blunt tool that tend to target civil society as a whole---states do not create one set of formal laws that applies only to regime-friendly INGOs and another set that applies to more risky INGOs.
 Instead, there is a divergence between the formal *de jure* laws and the *de facto* implementation of their accompanying regulations.
-In practice, NGO laws tend to not be applied universally and formal laws often serve as a "weapon hanging on the wall that never fires," acting a warning to potentially uncooperative NGOs [@Kozenko:2015].
-Instead, autocrats engage with INGOs in opposing ways, providing financial support and opportunities for collaboration with those that align with government policy preferences, and using legal mechanisms to restrict or expel those that do not [@ToeplerZimmerFrohlich:2020; @Plantan:2022; @LiFarid:2023].
+In practice, NGO laws tend to not be applied universally and formal laws often serve as a "weapon hanging on the wall that never fires" [@Kozenko:2015], acting a warning to potentially uncooperative NGOs.
 
 The authoritarian benefits of civil society regulations go beyond simply allowing or disallowing specific INGOs.
+Autocrats engage with INGOs in opposing ways, providing financial support and opportunities for collaboration with those that align with government policy preferences, and using legal mechanisms to restrict or expel those that do not [@ToeplerZimmerFrohlich:2020; @Plantan:2022; @LiFarid:2023].
 The flexible *de facto* implementation of formal civil society laws allows authoritarians to "use nonprofit regulation as a tool of political control to shore up their continued rule" [@Spires:2020, 573], providing them with an additional policy tool for their stability-seeking calculus.
 These laws allow governments to capture and reshape INGO programming in their favor.
-@LianMurdie:2023 illustrate how increased civil society restrictions have counter-intuitively led to an increase in cooperative, regime-friendly INGO programming, with INGOs praising government policies, engaging in joint programming with the government, and changing longstanding programs to align with government desires.
+@LianMurdie:2023 illustrate how increased civil society restrictions have counterintuitively led to an increase in cooperative, regime-friendly INGO programming, with INGOs praising government policies, engaging in joint programming with the government, and changing longstanding programs to align with government desires.
+
 China's ONGO law illustrates this dynamic well.
-The ONGO law requires that INGOs partner with government agencies and find collaborating PSUs, which provides the government with more influence over INGO decision making.
+The ONGO law requirement to partner with Public Security Bureaus and collaborate with PSUs provides the government with direct influence over INGO decision making.
 For example, Oxfam gained RO status in 2017, but only after negotiations with its proposed PSU forced it to stop collaborating with other organizations and local agencies [@Li:2020].

### 2023-12-06 manuscript/manuscript.qmd
More editing/shrinking, mostly in theory, lit review, and methods sections

@@
 
-In the past two decades, nearly 100 countries have proposed or enacted legal measures designed to restrict nongovernmental organizations (NGOs) and civil society more broadly [@Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016].[^ngo-clarification] According to the CIVICUS Civil Society Monitor, as of 2023 only `r civicus_prop$true$prop_nice` of countries have open and unrestricted civic space [@ChaudhryHeiss:2022a; @CIVICUSMonitor].
+In the past two decades, nearly 100 countries have proposed or enacted legal measures designed to restrict nongovernmental organizations (NGOs) and civil society more broadly [@Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016].[^ngo-clarification] According to the CIVICUS Civil Society Monitor, as of 2023 only `r civicus_prop$true$prop_nice` of countries have open and unrestricted civic space [@CIVICUSMonitor].
 On April 28, 2016, China passed its own set of civil society restrictions with its Law of the People's Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China---or "2016 ONGO Law"---which formally took effect on January 1, 2017.
@@
 Despite the fact that NGOs can act as "agents of democratization" [@ToeplerZimmerFrohlich:2020], thus posing a threat to non-democratic rule, most authoritarian states permit the growth of domestic and international civil society [@DeMattee:2019; @Heiss:2019; @Heiss:2019a].
-INGOs provide needed resources and expertise in humanitarian relief, environmental policy, education, development, and autocrats can rely on these services to consolidate power by providing improved public goods.
+INGOs provide needed resources and expertise in humanitarian relief, education, and development, and autocrats can rely on these services to consolidate power by providing improved public goods.
 At the same time, INGOs can pose a threat to stability by exposing human rights abuses, encouraging unwanted political reform, and engaging in political advocacy [@Heiss:2019; @ToeplerZimmerFrohlich:2020].
-To capture the benefits and reduce the risk of working with INGOs, most authoritarian states rely on "administrative crackdown," [@Chaudhry:2022] or laws that create barriers to NGO advocacy, entry, and funding [@ChristensenWeinstein:2013; @ChaudhryHeiss:2022; @CarothersBrechenmacher:2014].
-These laws, however, are a blunt tool that tend to target civil society as a whole---states do not create one set of formal laws that applies only to regime-friendly INGOs and another set that applies to more risky INGOs.
+To capture the benefits and reduce the risk of working with INGOs, most authoritarian states rely on "administrative crackdown" [@Chaudhry:2022], or laws that create barriers to NGO advocacy, entry, and funding [@ChristensenWeinstein:2013; @ChaudhryHeiss:2022; @CarothersBrechenmacher:2014].
+These laws, however, are a blunt tool and target civil society as a whole---states do not create one set of formal laws that applies only to regime-friendly INGOs and another set that applies to more risky INGOs.
 Instead, there is a divergence between the formal *de jure* laws and the *de facto* implementation of their accompanying regulations.
-In practice, NGO laws tend to not be applied universally and formal laws often serve as a "weapon hanging on the wall that never fires" [@Kozenko:2015], acting a warning to potentially uncooperative NGOs.
+In practice, NGO laws tend to not be applied universally, and formal laws often serve as a "weapon hanging on the wall that never fires" [@Kozenko:2015], acting as a warning to potentially uncooperative NGOs.
 
@@
 These laws allow governments to capture and reshape INGO programming in their favor.
-@LianMurdie:2023 illustrate how increased civil society restrictions have counterintuitively led to an increase in cooperative, regime-friendly INGO programming, with INGOs praising government policies, engaging in joint programming with the government, and changing longstanding programs to align with government desires.
+Globally, increased civil society restrictions have counterintuitively led to an increase in cooperative, regime-friendly INGO programming, with INGOs praising government policies, engaging in joint programming with the government, and changing longstanding programs to align with government desires [@LianMurdie:2023].
 
 China's ONGO law illustrates this dynamic well.
-The ONGO law requirement to partner with Public Security Bureaus and collaborate with PSUs provides the government with direct influence over INGO decision making.
+The ONGO law requirement to partner with Public Security Bureaus and collaborate with PSUs provides the government with direct influence over INGO decision-making.
 For example, Oxfam gained RO status in 2017, but only after negotiations with its proposed PSU forced it to stop collaborating with other organizations and local agencies [@Li:2020].
-In 2018, @BatkeHang:2018 posited that the ONGO law was showing signs of reorienting the missions of legally recognized INGOs and the overall scope of international civil society to be more explicitly aligned with government preferences.
-Holbig & Lang confirmed this prediction, finding that the issue areas addressed by legally recognized INGOs had "shift\[ed\] towards fields of activity high up the government's domestic policy agenda" [-@HolbigLang:2022, p.
+In 2018, INGO programming showed signs of reorienting to be more explicitly aligned with government preferences [@BatkeHang:2018], and by 2021, the issue areas addressed by legally recognized INGOs had clearly "shift\[ed\] towards fields of activity high up the government's domestic policy agenda" [@HolbigLang:2022, p.
 587].
@@
 The strategic and individualized enforcement of broad civil society laws in authoritarian regimes creates a regulatory environment where each INGO faces a different set of constraints.
-We term this an INGO's "operational space," or the degree of legal and practical flexibility an organization can rely on in its target country.
-INGOs with a large amount of operational space can can engage in a wider range of programs, address more potentially contentious issues, and enjoy broader geographic scope without fear of interference from the host government, even in the presence of formal *de jure* anti-NGO laws.
-Organizations with less operational space, on the other hand, face stricter *de facto* enforcement of anti-NGO laws and are more constrained in the programs, strategies, issues, and regions they can work on.
+We term this an INGO's "operational space," or the degree of legal and practical flexibility an organization faces in its target country.
+INGOs with a large amount of operational space can engage in a wider range of programs, address more contentious issues, and enjoy broader geographic scope without fear of interference from the host government, even in the presence of formal *de jure* anti-NGO laws.
+Organizations with less operational space face stricter *de facto* regulatory environments and are more constrained in the programs, strategies, issues, and regions they can work on.
 
@@
 #| message: false
-#| fig-cap: "Diagram of our theoretical framework showing three possible determinants of INGO operational space: the government's interest in and relationship with the INGO, the contentiousness of the INGO's issue area, and the inherent geographic scope of the INGO's operations."
+#| fig-cap: "Three proposed determinants of INGO operational space."
 theory_nodes <- tribble(
@@
 In @fig-theory, we propose that the interplay between INGO characteristics and government preferences is a key determinant of individual INGO operating space [@LiFarid:2023; @ChaudhryHeiss:2021].
-Authoritarian states seek out INGOs that provide direct benefits and public goods, while avoiding INGOs that threaten their stability.
+Authoritarian states seek out INGOs that provide direct benefits, while avoiding INGOs that threaten their stability.
 For instance, states in need of foreign aid and development will be more open to INGOs working on those issues, while states looking for increased trade will seek out INGOs focused on economic partnerships.
@@
 In contrast, states engaged in human rights abuses or fearful of foreign influence over other domestic policies will reduce---or even close---the operational space allowed for INGOs addressing these issues.
-Notably, the arrow between government preferences and issue area is bidirectional, reflecting the government's ability to use civil society regulations to directly realign INGO programming in the regime's favor.
-Finally, the natural scope of an INGO's activities can shape its allowed operational space outside of authoritarian stability seeking calculus.
+Notably, the arrow between government preferences and issue area is bidirectional, reflecting the government's ability to use civil society regulations to realign INGO programming in the regime's favor, and the INGO's potential ability to reshape government preferences [@Heiss:2019a].
+Finally, the natural scope of an INGO's activities influences its allowed operational space outside of authoritarian stability-seeking calculus.
 Many INGOs purposely keep themselves small, non-confrontational, and non-political and limit themselves to work in only a small part of their target countries, having no plans to go beyond their hyperlocal scope.
@@
 Specifically, we can observe exactly how the Chinese government has used the RO registration process to strategically limit the potential reach of INGOs and reshape their issue areas.
-We use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that INGOs need to or hope to be able to carry out their programs in as broad a geographical scope as possible [@Li:2020].
+We use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that INGOs desire to engage in work in as broad a geographical scope as possible [@Li:2020].
 For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas might need their service.
@@
 
-We propose a set of theoretical expectations based on @fig-theory that structure our analysis.
+To structure our analysis, we propose a set of theoretical expectations based on @fig-theory.
 First, we expect that INGOs working on non-contentious, regime-aligned issues will have greater reach throughout the country:
@@
 
-> **E~3~**: Because formal registration can take a long time and can involve many bureaucratic hurdles, INGOs that registered soon after the law took effect should be be (1) less of a threat and (2) a higher priority for processing, and so should be registered in more provinces.
+> **E~3~**: Because formal registration can take a long time and can involve many bureaucratic hurdles, INGOs that registered soon after the law took effect should be (1) less of a threat and (2) a higher priority for processing, and so should be registered in more provinces.
 
@@
 This is largely because both INGOs and the regulators needed some transitional time to explore the specific application of the law as large ambiguity was left when the law was passed.
-We use this temporal variable as a proxy for the motivation or eagerness of INGOs to register an RO, for some INGOs are inclined to avoid the cumbersome registration procedures at the early stage if there is no real consequences for continuing operations without registration, while others took the time to talk with multiple potential PSUs to find a more suitable superior or regulatory dynamic.
-[@Jia:2017a]
+We use this temporal variable as a proxy for the motivation or eagerness of INGOs to register an RO, for some INGOs are inclined to avoid the cumbersome registration procedures at the early stage if there is no real consequences for continuing operations without registration, while others took the time to talk with multiple potential PSUs to find a more suitable superior or regulatory dynamic [@Jia:2017a].
 
@@
 
-Our data provides us with rich descriptive detail of the types of INGOs allowed to register in China following the advent of the ONGO law, and we explore patterns in this data below.
-In addition to presenting descriptive summary statistics, we create a multilevel Bayesian regression model to examine the complex effects that issue area, local connections, and registration timing have on organizational flexibility.
+In addition to presenting descriptive summary statistics, we use a multilevel Bayesian regression model to examine the complex effects that issue area, local connections, and registration timing have on organizational flexibility.
 This approach allows us to hold specific variables constant and generate predictions for hypothetical new, not-yet-registered INGOs, providing us with stronger empirical implications.
-Additionally, Bayesian modeling allows us to calculate the posterior distribution of our different estimands.
-Rather than report a single value for the proportion of registered INGOs worked on specific issues, we can estimate posterior credible intervals that represent the probability that the true proportion falls within a specific range.
-We report posterior medians and 95% credible intervals throughout our analysis.
-Importantly, these intervals do not behave like more traditional frequentist confidence intervals.
-Instead, they can be interpreted as the probability that a reported estimate falls within the range, given the data and modeling choices.
+Additionally, Bayesian modeling allows us better model the uncertainty associated with INGO operational space—instead of reporting a single value for the number of provinces INGOs have access to, we can and report posterior credible intervals that represent the probability that the average geographic reach falls within a specific range.
 
@@
 negative counts of provinces or more than 32 provinces).
-If we transform the count of provinces to a percentage, Beta regression would work well, as it is naturally limited to outcomes within a 0--1 range.
-However, Beta regression cannot handle values that are exactly 0 or 1, making it inappropriate for our data with its inflated counts at 0 (1) and 100% (32).
-To account for values at the bounds, we rely on ordered Beta regression [@Kubinec:2022], an extension of zero-and-one-inflated Beta regression that allows us to simultaneously model the continuous range of provinces (2--31) and the discrete outcomes (1 province and 32 provinces) without relying on percentages.
+To account for values at the bounds, we rely on ordered Beta regression [@Kubinec:2022], an extension of zero-and-one-inflated Beta regression that allows us to simultaneously model the continuous range of provinces (2--31) and the discrete outcomes (1 province and 32 provinces).
 We can thus explore the dynamics of each of our independent variables of interest in multiple ways---we can see (1) how each variable predicts that an organizations works in one province, nationwide, or somewhere in between, and (2) how each variable predicts the overall expected count of provinces.
@@
 We also include random province intercepts to account for between-region differences in how INGOs are regulated, since every RO is overseen by provincial-level Public Security Bureaus.
-We use the following model and priors (see appendix TODO for more details):
+We use the following model and priors; additional model details and results are available in the appendix and in TABLE TODO:
 
@@
         "and represent the overall conditional average geographic range for INGOs.",
-        "Points show posterior median; lines show 80% and 95% intervals.",
+        "Points show posterior median; lines show 80% and 95% credible intervals.",
         .sep = " "

### 2023-12-06 manuscript/manuscript.qmd
More shrinking in results section

@@
 
-In the past two decades, nearly 100 countries have proposed or enacted legal measures designed to restrict nongovernmental organizations (NGOs) and civil society more broadly [@Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016].[^ngo-clarification] According to the CIVICUS Civil Society Monitor, as of 2023 only `r civicus_prop$true$prop_nice` of countries have open and unrestricted civic space [@CIVICUSMonitor].
+In the past two decades, nearly 100 countries have proposed or enacted legal measures designed to restrict nongovernmental organizations (NGOs) and civil society more broadly [@Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyRonPrakash:2016].[^ngo-clarification] According to the CIVICUS Civil Society Monitor, as of 2023 only `r civicus_prop$true$prop_nice` of countries have open and unrestricted civic space [@CIVICUSMonitor].
 On April 28, 2016, China passed its own set of civil society restrictions with its Law of the People's Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China---or "2016 ONGO Law"---which formally took effect on January 1, 2017.
@@
 
-Before examining the posterior results of our statistical model, we first describe some of the general trends in INGO registration during the first 5 years of the ONGO law.
-We use our data to explore (1) when INGOs registered, (2) what kinds of issues registered INGOs work on, and (3) how large of a geographic reach INGOs have.
-
+W first describe some of the general patterns related to INGO operational space during the first 5 years of the ONGO law.
 First, @fig-registration-timeline shows the distribution of the count of new INGO registrations since January 1, 2017.
-A couple dozen organizations were able to register immediately after the law took effect during the first quarter of 2017, while hundreds more registered during the rest of that year.
+A couple dozen organizations were able to become ROs immediately after the law took effect during the first quarter of 2017, while hundreds more registered during the rest of that year.
 Nearly half of all currently-registered INGOs in China---48%---registered in 2017.
@@
 #| echo: false
-#| fig-cap: "Count of international NGO registrations under the 2016 ONGO Law, divided by quarters"
+#| fig-cap: "Count of international NGO registrations under the 2016 ONGO Law, 
+#|   divided by quarters"
 ggplot(ongo, aes(x = registration_date)) +
@@
 The two most common issues are economic, trade, and industry associations, representing 50% of all INGOs.
-Many of these organizations are bilateral chambers of commerce or other multilateral trade organizations such as the Japan-China Economic Association, the Silk Road Chamber of International Commerce, and the Canada China Business Council, and most are not more stereotypical international humanitarian organizations.
-Charitable, humanitarian, education, and health INGOs are far less common than their trade and industry counterparts.
-For instance, charity and humanitarian organizations like World Vision, Save the Children, and the Salvation Army comprise only 12% (73) of all INGOs.
+Many of these organizations are bilateral chambers of commerce or other multilateral trade organizations such as the Japan-China Economic Association, the Silk Road Chamber of International Commerce, and the Canada China Business Council.
+Charitable, humanitarian, education, and health INGOs are far less common than their trade and industry counterparts: charity and humanitarian organizations like World Vision, Save the Children, and the Salvation Army comprise only 12% (73) of all INGOs.
 
@@
 #| fig-cap: "Count of international NGO registrations, divided by issue area"
-# TODO: Use issue_area instead of work_field_code
+# MAYBE: Use issue_area instead of work_field_code
 issue_count <- ongo |> 
@@
 INGOs must select a home office for their Chinese operations, but they are not necessarily limited to work within their home provinces.
-As described earlier, each INGO is authorized to work in a list of approved provinces, and the count provinces follows a unique three-level distribution, seen previously in @fig-province-count-collapsed, with 30% of INGOs authorized to work in just one province, 40% authorized to work nationally, and 30% authorized to work in a multiple provinces, but not in the whole country.
+As described earlier, each INGO is authorized to work in a list of approved provinces, and the count of provinces follows a distinctive three-tiered distribution, seen previously in @fig-province-count-collapsed, with 30% of INGOs authorized to work in just one province, 40% authorized to work nationally, and 30% authorized to work in between 2--31 provinces.
 

### 2023-12-06 manuscript/appendix.qmd
Make the appendix a separate file
…so that we can have a separate bibliography for software + other methods-related things

--- 2023-12-06 manuscript/manuscript.qmd
@@
 ---
-title: "Operational constraints and closing civic space: International NGO restrictions and China’s Overseas NGO law"
-short-title: "Operational constraints and closing civic space"
-date: "2023-12-03"
+title: 'Online appendix for "Operational constraints and closing civic space: International NGO restrictions and China’s Overseas NGO law"'
+short-title: 'Online appendix for "Operational constraints and closing civic space"'
+date: "2023-12-06"
 author:
@@
   orcid: 0000-0002-3948-3914
-abstract: |
-  TODO: **Update this based on the finished version of the paper.** China’s 2016 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international nongovernmental organizations (INGOs).
-However, the effects of this global crackdown on INGOs have been difficult to measure since there is often divergence between the formal de jure regulations and the de facto implementation of these laws.
-Additionally, the severity and consistency of the enforcement of these laws often depends on the type of services provided by these organizations.
-In this paper, we explore the effect of China’s ONGO law on INGO operations in the five years since the passage of the law.
-We test whether and how INGO operational space under the ONGO law is influenced by organizations' issue areas.
-We argue that the less contentious the issue areas INGOs work in the more likely they are granted greater operational space, measured by the number of provinces they are legally authorized to work in.
-China provides an excellent setting for examining the phenomenon of closing space civic space, since the 2016 ONGO law hypothetically regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities.
-We test our argument by analyzing administrative data from 633 registered representative offices of INGOs registered in China between 2017–2021 and test our hypothesis with a multilevel Bayesian model.
-Our results speak to the broader literature on closing civic space and provide an empirical illustration of the practical effect of NGO restrictions on global civil society.
-keywords:
-  - international NGOs
-  - civil society
-  - authoritarianism
-  - Chinese ONGO law
 code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/compassionate-clam>"
@@
 link-citations: true
+crossref: 
+  tbl-title: Appendix Table
+  fig-title: Appendix Figure
 ---
@@
 ```
-
-```{r libraries-data}
-library(tidyverse)
-library(sf)
-library(scales)
-library(tidybayes)
-library(ggrepel)
-library(marginaleffects)
-library(tidygraph)
-library(ggraph)
-library(patchwork)
-library(glue)
-library(gt)
-library(targets)
-
-# Generated via random.org
-set.seed(8511)
-
-# Targets stuff
-tar_config_set(
-  store = here::here("_targets"),
-  script = here::here("_targets.R")
-)
-
-tar_load(c(ongo, ongo_mapdata, civicus_clean))
-tar_load(c(
-  preds_issue, preds_local, preds_timing,
-  epreds_issue, epreds_local, epreds_timing,
-  epreds_timing_local, issue_indicator_lookup
-))
-tar_load(c(preds_issue_plot, preds_local_plot, preds_timing_plot))
-
-# Plotting and modelsummary functions
-invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
-invisible(list2env(tar_read(table_functions), .GlobalEnv))
-
-theme_set(theme_ongo())
-set_annotation_fonts()
-```
-
-```{r civicus-stuff}
-civicus_prop <- civicus_clean |> 
-  group_by(open = Score > 80) |> 
-  summarize(total = n()) |> 
-  mutate(
-    prop = total / sum(total),
-    prop_nice = label_percent(accuracy = 1)(prop)
-  ) |> 
-  mutate(open = janitor::make_clean_names(open)) |> 
-  split(~open)
-```
-
-::: {.content-visible when-format="html"}
-# Introduction {.hide}
-:::
-
-In the past two decades, nearly 100 countries have proposed or enacted legal measures designed to restrict nongovernmental organizations (NGOs) and civil society more broadly [@Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyRonPrakash:2016].[^ngo-clarification] According to the CIVICUS Civil Society Monitor, as of 2023 only `r civicus_prop$true$prop_nice` of countries have open and unrestricted civic space [@CIVICUSMonitor].
-On April 28, 2016, China passed its own set of civil society restrictions with its Law of the People's Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China---or "2016 ONGO Law"---which formally took effect on January 1, 2017.
-The law requires all international NGOs (INGOs) to either establish formal in-country representative offices (ROs) or file short-term temporary activities to lawfully operate in mainland China.
-Without recognized legal status, INGOs are prohibited from working in the country, and even with legal recognition, INGO programming is limited to government-approved activities.
-
-[^ngo-clarification]: "Civil society" is a broad concept that includes a range of organizational forms, both formal and informal.
-In this paper, we look at nonprofit organizations or third sector organizations---formal non-profit-seeking organizations that are neither privately-owned nor government-controlled.
-We define international NGOs as organizations that work predominantly in at least one other country outside of their home country.
-
-As an authoritarian state with a growing nonprofit sector, China's regulatory regime for INGOs serves as an example for understanding how autocracies use restrictive laws as policy tools as they engage with international civil society.
-The policies implemented by China's 2016 ONGO law serve dueling purposes that both harness the benefits and reduce the risks of INGOs.
-The law is designed to decrease demand for foreign civil society organizations and limit the influence they might have over domestic policies [@DeMattee:2018; @DeMattee:2019] while also allowing the regime to benefit from the expertise, services, and reputational advantages of working partnering with international civil society [@Plantan:2022; @Heiss:2019].
-These dual demands lead to differential enforcement and divergence between formal *de jure* regulations and the *de facto* implementation of those laws [@ChaudhryHeiss:2022], as the government enforces regulations selectively depending on regime preferences for INGO services.
-
-In this paper, we use the case of China to explore how the demands to both restrict and embrace INGOs have shaped the international nonprofit sector in the five years since the 2016 ONGO Law came into effect.
-We examine how the ONGO Law has influenced the population of INGOs that have successfully registered in China, as well as the association between factors such as INGO issue areas and the operational space granted to them in the country.
-We contribute to a growing body of research on the effects of closing civic space on INGO behavior and strategies.
-First, we expand work that uses institutional approaches to understanding civil society regulations, which argues that states strategically regulate INGOs to maintain regime stability, choosing forms of regulation and repression that minimize threats to internal political stability [@Chaudhry:2022; @DeMattee:2018; @DeMattee:2019; @Heiss:2019].
-Second, we explore how authoritarian civil society regulations act as policy tools that regimes can leverage to shift INGO behavior in their favor and how these laws reshape and tame organizational strategies [@Li:2020; @WuNie:2021; @LianMurdie:2023].
-Third, we explore how these regulations lead to differentiated application of the law depending on organizational characteristics.
-We argue that INGO issue areas, missions, and pre-existing relationships with local government officials influence the degree of operating space available for INGOs.
-
-By focusing on INGO operational space in China, we provide a unique empirical view into the *de facto* regulatory environment for foreign civil society in an authoritarian state.
-Broader indexes of civil society openness---such as the core civil society index from the Varieties of Democracy project [@LianMurdie:2023; @ChaudhryHeiss:2022]---capture the general regulatory environment for all civil society more broadly, but do not reflect the specific implementation of laws for INGOs.
-In this paper, we use a mixed methods approach to explore the regulatory environment for INGOs in particular, providing a much richer description and analysis of the impact of INGO laws.
-
-Below, we provide a brief overview of China's 2016 ONGO Law and the different regulatory mechanisms it provides for INGOs to obtain legal access to the country.
-We then synthesize existing research on authoritarian regulation of INGOs and the differential application of these laws based on regime preferences and organizational characteristics, and propose a set of empirical expectations based on this literature.
-We test these expectations with a mixed methods research design, combining Bayesian analysis of administrative data from all `r nrow(ongo)` formally registered INGOs with a comparative case study of Greenpeace and The Nature Conservancy, two environmental INGOs that took different approaches to operating in China after 2017.
-We conclude with a broader discussion of authoritarian civil society regulations and propose future approaches for exploring the practical operating environment for INGOs working in such regimes.
-
-# The legal framework established by the 2016 ONGO law
-
-International NGOs began to play an important role in China in the early 1990s as part of the country's Reform and Opening-Up policy, and global civil society has played pivotal roles in providing funding, organizational and program management skills, and catalytic support for China's emerging domestic nonprofit sector [@Yin:2009].
-Before the 2016 ONGO Law, the regulation of INGOs in China was ambiguous [@Shieh:2018; @Spires:2022].
-The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations, which required that foreign foundations register with the Ministry of Civil Affairs, the regulating agency for domestic nonprofits.
-However, the actual application of the regulation was very limited: fewer than 30 foreign foundations registered, compared to estimates of over 7,000 INGOs working in China in 2016 [@YeHuang:2018; @Spires:2020].
-Many INGOs gained legal status by registering as foreign-invested companies [@Sidel:2016], allowing them to hire local employees [@HolbigLang:2022; @Yin:2009].
-However, this legal form is not quite compatible with the non-profit-distributing, social service orientation of civil society [@Ye:2021].
-INGOs registered as foreign-invested companies had to navigate incongruous for-profit regulations, such as rules protecting shareholders' investment returns.
-
-The legal framework governing INGOs was overhauled by the 2016 ONGO Law, which applies to all overseas (including Hong Kong, Macau, and Taiwan) NGOs that conduct not-for-profit activities in mainland China.
-The ONGO Law provides two pathways for INGOs to lawfully operate in China (see @fig-ro-ta-pathways): (1) submitting an application for formal permanent registration as registered organizations (ROs), or (2) filing documentation of temporary activities with provincial Public Security Bureaus.
-Formal registration as an RO allows INGOs to maintain an ongoing presence in the country, while temporary activities are intended for INGOs that need to conduct one-off programs that last no longer than one year.
-Using one of these two channels to obtain legal status became mandatory in 2017.
-INGOs are authorized to operate within China on a province-by-province basis.
-Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.
-
-```{r fig-ro-ta-pathways, fig.width=6, fig.height=3}
-#| echo: false
-#| include: true
-#| warning: false
-#| message: false
-#| fig-cap: "Two possible pathways for international NGOs to legally work in 
-#|   China under the 2016 ONGO law"
-
-ro_nodes <- tibble(
-  step = c(
-    "Find a professional supervisory unit (PSU)",
-    "Obtain PSU approval",
-    "Open organization bank accounts",
-    "Submit annual work plans to PSU and Public Security Bureau",
-    "Keep programming within approved scope",
-    "Submit annual reports to PSU and Public Security Bureau"
-  ),
-  type = "Representative offices"
-)
-ro_edges <- tibble(from = 1:5, to = 2:6)
-ro_graph <- tbl_graph(nodes = ro_nodes, edges = ro_edges)
-
-ta_nodes <- tibble(
-  step = c(
-    "Find an eligible Chinese partner to file paperwork",
-    "File activity information with Public Security Bureau",
-    "Keep programming within approved scope",
-    "Finish work within a year",
-    "Submit final project report to Public Security Bureau"
-  ),
-  type = "Temporary activities"
-)
-ta_edges <- tibble(from = 1:4, to = 2:5)
-ta_graph <- tbl_graph(nodes = ta_nodes, edges = ta_edges)
-
-combined_graph <- bind_graphs(ro_graph, ta_graph)
-
-ggraph(combined_graph, layout = "tree") +
-  geom_node_label(
-    aes(x = x, y = y, label = step), 
-    size = 2.5, label.r = unit(0, units = "pt")
-  ) +
-  geom_edge_link(
-    aes(
-      start_cap = label_rect(node1.step, padding = margin(5, 5, 5, 5, "pt")),
-      end_cap = label_rect(node2.step, padding = margin(5, 5, 5, 5, "pt"))
-    ),
-    arrow = arrow(angle = 30, length = unit(6, "pt"), type = "closed"),
-    edge_linewidth = 0.25
-  ) +
-  facet_nodes(vars(type), scales = "free_x") +
-  labs(x = NULL, y = NULL) +
-  theme_ongo() +
-  theme(
-    panel.grid.major = element_blank(),
-    panel.border = element_blank(),
-    axis.text = element_blank(),
-    strip.text = element_text(hjust = 0.5)
-  )
-```
-
-Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental agency related to an INGO's issue area that oversees and co-supervises the INGO with provincial Public Security Bureaus.
-Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, as potential PSUs have no legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018].
-INGOs vary in their ability to attract partner PSUs, and organizations that struggle to find suitable PSUs face limitations in their scope and geographic reach.
-After successfully gaining legal status, INGOs must follow the law's operational regulations, such as no fundraising within mainland China, only channeling funds through the RO's or PSU's bank accounts, filing reports regularly, and staying within the geographical and issue scopes as approved.
-INGOs undertaking temporary activities also need to find an eligible Chinese partner---including governmental, quasi-governmental, or non-profit organizations---and must keep their programs within approved limits, but the process is less onerous.
-
-# Civil society laws in the service of regime stability
-
-The 2016 ONGO Law's provision of two legal pathways for registration---each with different degrees of freedom---is an example of the broader phenomenon of closing civic space.
-In the past two decades, authoritarian states have used administrative and legal measures to curtail the influence of global civil society.
-A rich literature in comparative politics explores how authoritarian regimes counterintuitively use democratic institutions for their own benefit and survival [@Kendall-TaylorFrantz:2014a; @GandhiPrzeworski:2007].
-Authoritarian states hold elections, allow opposition parties in the legislature, and set executive term limits [@LevitskyWay:2010; @Meng:2020], but use these democratic-appearing institutions to hedge against possible threats to regime stability.
-Quasi-democratic institutions are allowed, but only in ways that bolster the government's stability, and these institutions are kept weak and "dependent on the regime to ensure that they do not develop any real power or autonomy" [@FrantzEzrow:2011, 7].
-
-Civil society is a democratic political institution that autocrats balance as part of their stability-seeking calculus.
-Despite the fact that NGOs can act as "agents of democratization" [@ToeplerZimmerFrohlich:2020], thus posing a threat to non-democratic rule, most authoritarian states permit the growth of domestic and international civil society [@DeMattee:2019; @Heiss:2019; @Heiss:2019a].
-INGOs provide needed resources and expertise in humanitarian relief, education, and development, and autocrats can rely on these services to consolidate power by providing improved public goods.
-At the same time, INGOs can pose a threat to stability by exposing human rights abuses, encouraging unwanted political reform, and engaging in political advocacy [@Heiss:2019; @ToeplerZimmerFrohlich:2020].
-To capture the benefits and reduce the risk of working with INGOs, most authoritarian states rely on "administrative crackdown" [@Chaudhry:2022], or laws that create barriers to NGO advocacy, entry, and funding [@ChristensenWeinstein:2013; @ChaudhryHeiss:2022; @CarothersBrechenmacher:2014].
-These laws, however, are a blunt tool and target civil society as a whole---states do not create one set of formal laws that applies only to regime-friendly INGOs and another set that applies to more risky INGOs.
-Instead, there is a divergence between the formal *de jure* laws and the *de facto* implementation of their accompanying regulations.
-In practice, NGO laws tend to not be applied universally, and formal laws often serve as a "weapon hanging on the wall that never fires" [@Kozenko:2015], acting as a warning to potentially uncooperative NGOs.
-
-The authoritarian benefits of civil society regulations go beyond simply allowing or disallowing specific INGOs.
-Autocrats engage with INGOs in opposing ways, providing financial support and opportunities for collaboration with those that align with government policy preferences, and using legal mechanisms to restrict or expel those that do not [@ToeplerZimmerFrohlich:2020; @Plantan:2022; @LiFarid:2023].
-The flexible *de facto* implementation of formal civil society laws allows authoritarians to "use nonprofit regulation as a tool of political control to shore up their continued rule" [@Spires:2020, 573], providing them with an additional policy tool for their stability-seeking calculus.
-These laws allow governments to capture and reshape INGO programming in their favor.
-Globally, increased civil society restrictions have counterintuitively led to an increase in cooperative, regime-friendly INGO programming, with INGOs praising government policies, engaging in joint programming with the government, and changing longstanding programs to align with government desires [@LianMurdie:2023].
-
-China's ONGO law illustrates this dynamic well.
-The ONGO law requirement to partner with Public Security Bureaus and collaborate with PSUs provides the government with direct influence over INGO decision-making.
-For example, Oxfam gained RO status in 2017, but only after negotiations with its proposed PSU forced it to stop collaborating with other organizations and local agencies [@Li:2020].
-In 2018, INGO programming showed signs of reorienting to be more explicitly aligned with government preferences [@BatkeHang:2018], and by 2021, the issue areas addressed by legally recognized INGOs had clearly "shift\[ed\] towards fields of activity high up the government's domestic policy agenda" [@HolbigLang:2022, p.
-587].
-Civil society laws thus filter out organizations opposed to the host regime's policy preferences and grant increased government control over safer and more beneficial INGOs.
-
-# Authoritarian policy tools and INGO operational space: theory and expectations
-
-The strategic and individualized enforcement of broad civil society laws in authoritarian regimes creates a regulatory environment where each INGO faces a different set of constraints.
-We term this an INGO's "operational space," or the degree of legal and practical flexibility an organization faces in its target country.
-INGOs with a large amount of operational space can engage in a wider range of programs, address more contentious issues, and enjoy broader geographic scope without fear of interference from the host government, even in the presence of formal *de jure* anti-NGO laws.
-Organizations with less operational space face stricter *de facto* regulatory environments and are more constrained in the programs, strategies, issues, and regions they can work on.
-
-```{r fig-theory, fig.width=6, fig.height=1.75}
-#| echo: false
-#| include: true
-#| warning: false
-#| message: false
-#| fig-cap: "Three proposed determinants of INGO operational space."
-theory_nodes <- tribble(
-  ~id, ~name, ~x, ~y, ~highlight,
-  1,   "Issue contentiousness", 2, 1, FALSE,
-  2,   "Operational space", 2, 0, TRUE,
-  3,   "Local focus", 3, 1, FALSE,
-  4,   "Government preferences", 1, 1, FALSE
-)
-
-theory_edges <- tribble(
-  ~from, ~to,
-  1, 2,
-  3, 1,
-  3, 2,
-  1, 4,
-  4, 1,
-  4, 2
-)
-
-theory_graph <- tbl_graph(nodes = theory_nodes, edges = theory_edges, directed = TRUE)
-
-ggraph(theory_graph, x = x, y = y) + 
-  geom_edge_link(
-    aes(
-      start_cap = label_rect(node1.name, padding = margin(10, 0, 10, -05, "pt")),
-      end_cap = label_rect(node2.name, padding = margin(10, -5, 10, -5, "pt"))
-    ),
-    arrow = arrow(angle = 30, length = unit(6, "pt"), type = "closed"),
-    edge_linewidth = 0.25
-  ) +
-  geom_node_label(
-    aes(x = x, y = y, label = name, fill = highlight), 
-    size = 3, label.r = unit(0, units = "pt"), fontface = "bold"
-  ) +
-  scale_x_continuous(expand = expansion(add = 0.4)) +
-  scale_y_continuous(expand = expansion(add = 0.2)) +
-  scale_fill_manual(values = c("white", clrs[1]), guide = "none") +
-  labs(x = NULL, y = NULL) +
-  theme_ongo() +
-  theme(
-    panel.grid.major = element_blank(),
-    panel.border = element_blank(),
-    axis.text = element_blank(),
-  )
-```
-
-In @fig-theory, we propose that the interplay between INGO characteristics and government preferences is a key determinant of individual INGO operating space [@LiFarid:2023; @ChaudhryHeiss:2021].
-Authoritarian states seek out INGOs that provide direct benefits, while avoiding INGOs that threaten their stability.
-For instance, states in need of foreign aid and development will be more open to INGOs working on those issues, while states looking for increased trade will seek out INGOs focused on economic partnerships.
-Because their primary issue areas are aligned with regime preferences, INGOs benefit from greater operational space and face fewer restrictions.
-In contrast, states engaged in human rights abuses or fearful of foreign influence over other domestic policies will reduce---or even close---the operational space allowed for INGOs addressing these issues.
-Notably, the arrow between government preferences and issue area is bidirectional, reflecting the government's ability to use civil society regulations to realign INGO programming in the regime's favor, and the INGO's potential ability to reshape government preferences [@Heiss:2019a].
-Finally, the natural scope of an INGO's activities influences its allowed operational space outside of authoritarian stability-seeking calculus.
-Many INGOs purposely keep themselves small, non-confrontational, and non-political and limit themselves to work in only a small part of their target countries, having no plans to go beyond their hyperlocal scope.
-This naturally limits their operational space, but these limits are self-imposed and not directly related to government regulations.
-
-To test the relationships between government preferences, INGO issue area, and INGO operational space, we apply this framework to China's ONGO law.
-Previous research has looked at the practical implementation of civil society laws on a global scale [@LianMurdie:2023; @Chaudhry:2022], which naturally blurs the specific policy mechanisms regimes use for controlling and leveraging global civil society.
-By analyzing the population of formally registered INGOs between 2017–2021, we can more precisely explore how a single formal anti-INGO law has shaped the operational space for foreign organizations working in the country.
-Specifically, we can observe exactly how the Chinese government has used the RO registration process to strategically limit the potential reach of INGOs and reshape their issue areas.
-We use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that INGOs desire to engage in work in as broad a geographical scope as possible [@Li:2020].
-For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas might need their service.
-Having the potential to shift programs to other provinces as needed thus provides a form of operational space.
-
-To structure our analysis, we propose a set of theoretical expectations based on @fig-theory.
-First, we expect that INGOs working on non-contentious, regime-aligned issues will have greater reach throughout the country:
-
-> **E~1~**: Because they are seen as less of a threat to regime stability and more aligned with government policy preferences, INGOs working on less contentious issues should be registered in more provinces.
-
-Using the number of provinces an INGO is authorized to work in as a proxy for organizational flexibility and reach might not reflect reality.
-Some INGOs explicitly limit their operations to specific provinces, either because their programming is more tailored to local conditions, or because they do not feel a need to go through the longer process of obtaining national-level registration.
-Accordingly, we temper our issue area expectation with a measure of explicitly local purpose.
-Organizations that have no intention of registering nationally should be registered in fewer provinces:
-
-> **E~2~**: Because they are explicitly focused on local issues, INGOs with explicitly local missions should be registered in fewer provinces.
-
-Finally, we also expect that the operational space for INGOs is negatively associated with the time elapsed since the law took effect.
-The mechanism behind this expectation is directly related to both issue area and government preferences:
-
-> **E~3~**: Because formal registration can take a long time and can involve many bureaucratic hurdles, INGOs that registered soon after the law took effect should be (1) less of a threat and (2) a higher priority for processing, and so should be registered in more provinces.
-
-# Data and methods
-
-We examine these theoretical expectations using a mixed methods approach.
-First, we explore a rich dataset of all ROs registered in China between 2017–2021 using a combination of descriptive statistics and Bayesian models to understand how the international civil society in China has been reshaped since the implementation of the ONGO law.
-We then complement this statistical analysis with a comparative case study of two INGOs---The Nature Conservancy and Greenpeace ---to explore in detail how the ONGO has specifically influenced organizational operational space.
-
-## Data
-
-Our data comes from INGOs' public registration documents disclosed by the Ministry of Public Security's Overseas NGO Office, which maintains a website with complete documentation of all the ROs and temporary activities registered or filled across China.
-We include all INGO registrations between January 1, 2017, when the law took effect, to December 31, 2021, with information for all `r nrow(ongo)` actively registered organizations.
-The filing documents for ROs disclose each INGO's name, address, registration date, regulating Public Security Bureau, PSU, issue area and purposes of the RO, and the specific provinces they can work in.
-We merge this INGO data with translated English organization names data from ChinaFile.
-Our data and reproducible code is available at `ANONYMIZED_DOI_URL`.
-
-## Measurement
-
-Our dependent variable is the count of provinces that INGOs are authorized to work in.
-We derive this value from the official registration record, which lists all the provincial regions each INGO RO can conduct activities in.
-This value ranges from 1–32 (the total number of province-level jurisdictions in mainland China).
-
-Our key independent variables correspond to each of our three theoretical expectations.
-First we code each INGO's issue area based on its mission statement reported in its registration documentation.
-Given there is certain level of subjectivity in the coding process, we cross-checked our manual coding of issue areas---Author 1 assigned each organization into one of the issue areas defined in Article 3 of the ONGO Law, and Author 2 cross-checked the coding for ambiguous cases.
-We include our coding rules for overlapping issue areas in the appendix.
-We categorize each organization into nine different issue areas (see @tbl-issues).
-
-::: {#tbl-issues}
-
-```{r}
-#| label: table-issues
-#| include: true
-tribble(
-  ~Issue, ~Examples,
-  "Arts and culture", "World Dance Council; Special Olympics",
-  "Charity and humanitarian", "Save the Children; Half the Sky Foundation",
-  "Economy and trade", "World Economic Forum; Chile-China Chamber of Commerce",
-  "Education", "Children’s Education Foundation; BSK International",
-  "Environment", "The Nature Conservancy; World Wide Fund for Nature",
-  "General", "Bill and Melinda Gates Foundation; Ford Foundation",
-  "Health", "American Heart Association; Operation Smile",
-  "Industry association", "World Cement Association; Colombian Coffee Growers Federation",
-  "Science and technology", "Royal Aeronautical Society; American Society of Civil Engineers"
-) |> 
-  gt() |> 
-  tab_footnote(
-    footnote = "Includes poverty alleviation, disaster relief, rural development, etc.",
-    locations = cells_body(columns = Issue, rows = 2)
-  ) |> 
-  tab_footnote(
-    footnote = "Includes grant-making organizations, organizations working on general international communication, and organizations working on multiple non-overlapping issues",
-    locations = cells_body(columns = Issue, rows = 6)
-  ) |> 
-  cols_width(Issue ~ gt_pct(20), Examples ~ gt_pct(50)) |> 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) |>
-  opts_theme() |> 
-  tab_options(
-    quarto.disable_processing = TRUE
-  )
-```
-
-Possible INGO issue areas and example organizations
-
-:::
-
-Our second independent variable is a dichotomous indicator of whether the INGO explicitly states that it intends to operate locally or sub-provincially.
-There are cases where the aim of the INGO is attached to a locality, either having a county or city name in their RO name or purposes, or the INGO is actually set up by people in China who registered the RO to communicate between the "hometown" and the INGO set up abroad.
-
-Our final independent variable measures how much time elapsed between January 1, 2017 (when the law took effect) and the organization's official registration date.
-There is great variance in the timing of registering an RO among INGOs, since there has been a *de facto* grace period for INGOs to seek legal presence after the law took effect [@Shieh:2018].
-This is largely because both INGOs and the regulators needed some transitional time to explore the specific application of the law as large ambiguity was left when the law was passed.
-We use this temporal variable as a proxy for the motivation or eagerness of INGOs to register an RO, for some INGOs are inclined to avoid the cumbersome registration procedures at the early stage if there is no real consequences for continuing operations without registration, while others took the time to talk with multiple potential PSUs to find a more suitable superior or regulatory dynamic [@Jia:2017a].
-
-## Modeling approach
-
-In addition to presenting descriptive summary statistics, we use a multilevel Bayesian regression model to examine the complex effects that issue area, local connections, and registration timing have on organizational flexibility.
-This approach allows us to hold specific variables constant and generate predictions for hypothetical new, not-yet-registered INGOs, providing us with stronger empirical implications.
-Additionally, Bayesian modeling allows us better model the uncertainty associated with INGO operational space—instead of reporting a single value for the number of provinces INGOs have access to, we can and report posterior credible intervals that represent the probability that the average geographic reach falls within a specific range.
-
-```{r fig-province-count-collapsed, fig.width=6, fig.height=3}
-#| include: true
-#| echo: false
-#| fig-cap: "Count of the number of provinces each INGO is authorized to operate in.
-The left panel shows the full distribution of INGOs registered in 2–31 provinces; the right panel collapses these in-between counts to a single category."
-provinces_collapsed <- ongo |> 
-  drop_na(province_count) |> 
-  mutate(province_count = case_when(
-    province_count == 1 ~ "1",
-    province_count > 1 & province_count < 32 ~ "2–31",
-    province_count == 32 ~ "32"
-  ))
-
-p1 <- ggplot(ongo, aes(x = province_count)) +
-  geom_histogram(binwidth = 1, linewidth = 0.1, boundary = 0,
-                 fill = clrs[6], color = "white") +
-  scale_y_continuous(breaks = seq(0, 250, 50)) +
-  labs(x = "Provinces INGOs are authorized to work in", y = "Count") +
-  theme_ongo()
-
-p2 <- ggplot(provinces_collapsed, aes(x = province_count)) + 
-  geom_bar(fill = clrs[6]) +
-  scale_x_discrete(labels = label_wrap(10)) +
-  scale_y_continuous(sec.axis = sec_axis(trans = ~ . / nrow(provinces_collapsed),
-                                         labels = label_percent()),
-                     breaks = seq(0, 250, 50)) +
-  labs(x = NULL, y = NULL) +
-  theme_ongo()
-
-(p1 | p2) + 
-  plot_layout(nrow = 1, widths = c(0.7, 0.3))
-```
-
-Modeling the count of provinces each INGO is authorized to operate in presents a unique statistical challenge.
-As seen in @fig-province-count-collapsed, roughly 30% of INGOs are registered in only one province, 40% are registered nationwide, while the remaining 30% are registered in 2--31 provinces.
-Our main variable of interest is thus a mix of continuous outcomes (i.e.
-a range of provinces) bounded between two discrete outcomes (i.e.
-one province and all provinces).
-Standard modeling approaches like ordinary least squares regression (OLS) cannot accurately capture the unique features of the data and will generate predictions that fall outside allowable bounds (i.e.
-negative counts of provinces or more than 32 provinces).
-To account for values at the bounds, we rely on ordered Beta regression [@Kubinec:2022], an extension of zero-and-one-inflated Beta regression that allows us to simultaneously model the continuous range of provinces (2--31) and the discrete outcomes (1 province and 32 provinces).
-We can thus explore the dynamics of each of our independent variables of interest in multiple ways---we can see (1) how each variable predicts that an organizations works in one province, nationwide, or somewhere in between, and (2) how each variable predicts the overall expected count of provinces.
-
-Since we are primarily interested in how an INGO's issue area, its local connections, and the timing of its registration after January 2017, we include these as explanatory variables.
-We also include random province intercepts to account for between-region differences in how INGOs are regulated, since every RO is overseen by provincial-level Public Security Bureaus.
-We use the following model and priors; additional model details and results are available in the appendix and in TABLE TODO:
-
-$$
-\begin{aligned}
-&\ \textbf{Registered provinces for INGO } i \\
-\text{Count of provinces}\ \sim&\ \operatorname{Ordered\,Beta}(\mu_i, \phi_y, k_{1_y}, k_{2_y}) \\[8pt]
-&\ \textbf{Model of outcome average} \\
-\mu_i =&\ 
-  \mathrlap{\begin{aligned}[t]
-  & \beta_0 + \beta_1\ \text{Issue[Arts and culture]} + \beta_2\ \text{Issue[Education]}\ +\\
-  & \beta_3\ \text{Issue[Industry association]} + \beta_4\ \text{Issue[Economy and trade]}\ + \\
-  & \beta_5\ \text{Issue[Charity and humanitarian]} + \beta_6\ \text{Issue[General]}\ + \\
-  & \beta_7\ \text{Issue[Health]} + \beta_8\ \text{Issue[Environment]}\ + \\
-  & \beta_9\ \text{Issue[Science and technology]} + \beta_{10}\ \text{Local connections}\ + \\
-  & \beta_{11}\ \text{Time since January 2017} + \beta_{12}\ \text{Year registered}
-  \end{aligned}}\\[8pt]
-&\ \textbf{Priors} \\
-\beta_0\ \sim&\ \operatorname{Student\,t}(\nu = 3, \mu = 0, \sigma = 2.5) && \text{Intercept} \\
-\beta_{1..12}\ \sim&\ \mathcal{N}(0, 5) && \text{Coefficients} \\
-\phi_y\ \sim&\ \operatorname{Exponential}(1 / 100) && \text{Variability in province count} \\
-k_{1_y}, k_{2_y}\ \sim&\ \operatorname{Induced\,Dirichlet}(1, 1, 1), && \text{0–continuous and continuous–1 cutpoints} \\
-&\ \quad \text{or } \bigl[P(\alpha_1), P(\alpha_1 + \alpha_2)\bigr] && \quad\text{(boundaries between 3 Dirichlet columns)}
-\end{aligned}
-$$
-
-# Results and discussion
-
-## Descriptive overview
-
-W first describe some of the general patterns related to INGO operational space during the first 5 years of the ONGO law.
-First, @fig-registration-timeline shows the distribution of the count of new INGO registrations since January 1, 2017.
-A couple dozen organizations were able to become ROs immediately after the law took effect during the first quarter of 2017, while hundreds more registered during the rest of that year.
-Nearly half of all currently-registered INGOs in China---48%---registered in 2017.
-After the initial first-year wave, the count of new registrations has declined slowly since 2018.
-
-```{r fig-registration-timeline, fig.width=6, fig.height=3}
-#| include: true
-#| echo: false
-#| fig-cap: "Count of international NGO registrations under the 2016 ONGO Law, 
-#|   divided by quarters"
-ggplot(ongo, aes(x = registration_date)) +
-  geom_histogram(binwidth = 365.25/4, boundary = ymd("2017-01-01"), 
-                 fill = clrs[6], color = "white") +
-  scale_x_date(date_breaks = "years", date_labels = "%Y") +
-  labs(x = NULL, y = "Count of new INGO registrations") +
-  theme_ongo()
-```
-
-Next, @fig-issue-props shows the distribution of issue areas that registered INGOs focus on.
-The two most common issues are economic, trade, and industry associations, representing 50% of all INGOs.
-Many of these organizations are bilateral chambers of commerce or other multilateral trade organizations such as the Japan-China Economic Association, the Silk Road Chamber of International Commerce, and the Canada China Business Council.
-Charitable, humanitarian, education, and health INGOs are far less common than their trade and industry counterparts: charity and humanitarian organizations like World Vision, Save the Children, and the Salvation Army comprise only 12% (73) of all INGOs.
-
-```{r fig-issue-props, fig.width=6, fig.height=3}
-#| include: true
-#| echo: false
-#| fig-cap: "Count of international NGO registrations, divided by issue area"
-# MAYBE: Use issue_area instead of work_field_code
-issue_count <- ongo |> 
-  drop_na(work_field_code1) |> 
-  group_by(work_field_code1) |>
-  summarize(n = n()) |> 
-  mutate(work_field_code1 = fct_reorder(work_field_code1, n))
-
-ggplot(issue_count, aes(y = work_field_code1, x = n)) +
-  geom_col(fill = clrs[5]) +
-  scale_x_continuous(sec.axis = sec_axis(trans = ~ . / sum(issue_count$n),
-                                         labels = label_percent())) +
-  labs(x = "Count of INGOs", y = NULL) +
-  theme_ongo() +
-  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
-```
-
-Finally, there are clear geographic trends in INGO registration.
-As seen in @fig-home-office-map, the majority of INGOs are headquartered in Beijing (166), Shanghai (137), and Guangdong Province (46).
-INGOs must select a home office for their Chinese operations, but they are not necessarily limited to work within their home provinces.
-As described earlier, each INGO is authorized to work in a list of approved provinces, and the count of provinces follows a distinctive three-tiered distribution, seen previously in @fig-province-count-collapsed, with 30% of INGOs authorized to work in just one province, 40% authorized to work nationally, and 30% authorized to work in between 2--31 provinces.
-
-```{r fig-home-office-map}
-#| include: true
-#| echo: false
-#| fig-cap: "Count of registered organizations across provinces"
-# Extract the intersections of provinces so that we don't plot the outside
-# borders and distort the coastlines. See https://stackoverflow.com/a/57138069 
-# and https://ikashnitsky.phd/2023/map-borders/
-interior_borders <- st_intersection(ongo_mapdata) %>% 
-  filter(n.overlaps > 1) |> 
-  # Remove weird points that st_intersection() adds
-  filter(!(st_geometry_type(geometry) %in% c("POINT", "MULTIPOINT")))
-
-# Use aes(geometry) and stat = "sf_coordinates" to make geom_label_repel() work
-# with geom_sf(): https://github.com/slowkow/ggrepel/issues/111#issuecomment-416853013
-ggplot() +
-  geom_sf(data = ongo_mapdata, aes(fill = ro_count), color = NA) +
-  geom_sf(data = interior_borders, linewidth = 0.3, color = "white") +
-  scale_fill_distiller(palette = "Reds", direction = 1, guide = "none", na.value = "gray80") +
-  geom_label_repel(
-    data = filter(ongo_mapdata, ro_count > 0),
-    aes(label = ro_count, geometry = geometry),
-    stat = "sf_coordinates", seed = 1234, label.size = 0.05, size = 3,
-    color = "black", fill = scales::alpha("white", 0.7),
-    segment.color = "black", segment.size = 0.25, min.segment.length = 0
-  ) +
-  coord_sf(crs = st_crs("EPSG:4480")) +  # China Geodetic Coordinate System 2000
-  theme_void()
-```
-
-## Posterior predictions
-
-Next we explore our data in more depth by generating and analyzing posterior predictions from our ordered Beta regression model, varying specific variables of interest while holding all others constant.
-
-### Issue area
-
-Following our first empirical expectation, we predict that INGOs working on less contentious issues should be registered in more provinces and have more geographic flexibility to work throughout the country.
-To explore this, we can take advantage of the simultaneous continuous and discrete features of ordered Beta regression and see how often an INGO in each issue area is predicted to work in a single province, across all provinces, or some number in between.
-@fig-issue-preds(a) presents a summary of predicted posterior outcomes for 1,000 hypothetical INGOs, varying each possible issue area and holding all other variables at their mean or modal values.
-Several notable trends emerge from the model results.
-INGOs focused on arts and culture are overwhelming the most likely kind of organization to work nationally---arts and culture organizations are predicted to work in all 32 provinces 80% of the time (with a credible interval of 78--83%) and are only predicted to work in a single province a rare 3--5% of the time.
-Education-focused INGOs, on the other hand, are the least likely kind of organization to be registered in all 32 provinces and are predicted to do so only 32--38% of the time.
-Education INGOs are the most likely to be registered in only one province, with that predicted outcome appearing 24--29% of the time---at least 10 percentage points higher than any other issue area's predicted proportion.
-All other issue areas follow roughly the patterns in predictions: the most common outcome is for organizations to work nationally (50--60% of the time), followed by working in at least 2 provinces (25--40% of the time), followed by working in a single province (10--20% of the time).
-@fig-issue-preds(b) shows the continuous posterior distribution of the average number of provinces INGOs are expected to be registered in across all types of issue areas, but accounting for the 1- and 32-only provinces simultaneously.
-We can see a similar trend---arts and culture INGOs are predicted to work in 28--30 provinces on average, while education INGOs are only predicted to work in 12--20.
-All other issues range between 20--28 provinces.
-
-```{r fig-issue-preds, fig.width=8, fig.height=6.5}
-#| include: true
-#| echo: false
-#| column: body-outset
-#| fig-cap: "Posterior predictions conditional on organization issue area. 
-#|   **A**: Predicted proportion of INGOs working in 1 province, all 32 
-#|   provinces, or somewhere in between. 
-#|   **B**: Expectation of posterior predictive distributions."
-
-preds_issue_plot_order <- preds_issue_plot |> 
-  filter(outcome == "All 32 provinces") |>
-  group_by(issue_area_nice) |> 
-  summarize(median_prop = median(prop)) |> 
-  arrange(median_prop) |> 
-  mutate(issue_area_nice_labels = str_wrap(issue_area_nice, 15)) |> 
-  mutate(issue_area_nice = fct_inorder(issue_area_nice))
-
-preds_issue_text <- preds_issue_plot |> 
-  group_by(outcome, issue_area_nice) |> 
-  summarize(median_prop = median_qi(prop)) |> 
-  unnest(median_prop) |> 
-  group_by(issue_area_nice) |> 
-  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
-  mutate(y_plot = 1 - y_plot) |> 
-  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
-  mutate(prop_ci_nice = glue::glue(
-    "{ymin}–{ymax}",
-    ymin = label_number(accuracy = 1, scale = 100)(ymin),
-    ymax = label_percent(accuracy = 1)(ymax)
-  )) |> 
-  mutate(issue_area_nice = factor(
-    issue_area_nice, 
-    levels = preds_issue_plot_order$issue_area_nice,
-    labels = preds_issue_plot_order$issue_area_nice_labels
-  ))
-
-p1 <- preds_issue_plot |>
-  mutate(issue_area_nice = factor(
-    issue_area_nice,
-    levels = preds_issue_plot_order$issue_area_nice,
-    labels = preds_issue_plot_order$issue_area_nice_labels
-  )) |>
-  ggplot(aes(x = draw, y = prop)) +
-  geom_area(
-    aes(fill = outcome, color = after_scale(fill)),
-    position = position_stack(), linewidth = 0.1
-  ) +
-  geom_text(
-    data = preds_issue_text,
-    aes(x = 250, y = y_plot, label = prop_ci_nice),
-    size = 3, fontface = "bold", color = "white"
-  ) +
-  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
-  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
-  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
-  facet_wrap(vars(issue_area_nice), strip.position = "bottom", nrow = 1) +
-  labs(
-    x = NULL, y = "Predicted probability of geographic reach", fill = NULL,
-    title = "Predicted proportion of type of geographic reach across issue area",
-    subtitle = "Posterior predictions of outcome categories",
-    tag = "A",
-    caption = str_wrap(
-      glue(
-        "The vertical slices of the bars depict 500 posterior samples;",
-        "the fuzziness represents the uncertainty in category boundaries.",
-        "95% credible intervals are shown as ranges in each category",
-        .sep = " "
-      ),
-      width = 120
-    )
-  ) +
-  theme_ongo() +
-  theme(
-    panel.grid.major = element_blank(),
-    panel.border = element_blank(),
-    panel.spacing = unit(5, "pt"),
-    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
-  )
-
-p2 <- epreds_issue |>
-  left_join(issue_indicator_lookup, by = join_by(issue_area)) |>
-  mutate(issue_area_nice = factor(
-    issue_area_nice,
-    levels = preds_issue_plot_order$issue_area_nice,
-    labels = preds_issue_plot_order$issue_area_nice_labels
-  )) |>
-  ggplot(aes(x = issue_area_nice, y = prop_to_provinces(.epred))) +
-  stat_halfeye(fill = clrs[6], color = clrs[8]) +
-  scale_x_discrete(labels = NULL) +
-  scale_y_continuous(
-    breaks = seq(0, 32, 8),
-    sec.axis = sec_axis(
-      trans = ~ provinces_to_prop(.),
-      name = "Proportion of provinces",
-      breaks = seq(0, 1, 0.25),
-      labels = label_percent()
-    )
-  ) +
-  facet_wrap(vars(issue_area_nice), strip.position = "bottom", nrow = 1, scales = "free_x") +
-  guides(fill = "none") +
-  labs(
-    x = NULL, y = "Expected provinces",
-    title = "Expected count of provinces",
-    subtitle = "Expectation (or average) of posterior predictions",
-    tag = "B",
-    caption = str_wrap(
-      glue(
-        "These distributions take into account single-province and nationwide predictions",
-        "and represent the overall conditional average geographic range for INGOs.",
-        "Points show posterior median; lines show 80% and 95% credible intervals.",
-        .sep = " "
-      ),
-      width = 120
-    )
-  ) +
-  coord_cartesian(ylim = c(1, 32)) +
-  theme_ongo() +
-  theme(
-    panel.grid.major.x = element_blank(),
-    panel.border = element_blank(),
-    panel.spacing = unit(5, "pt"),
-    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
-  )
-
-p1 / p2
-```
-
-As explained previously, we expect that the contentiousness of an NGO's issue area should influence its geographic reach and overall flexibility.
-No INGOs engaged in contentious issues like human rights advocacy have successfully registered in China, but there is some slight variation in the level of contention even among organizations working on less contentious issues like humanitarian assistance, health, and the environment.
-Education is particularly notable as the least flexible and most geographically restricted subsector.
-While education is typically considered a low-contention issue, in China fears of Western influence through educational institutions were an original impetus for the ONGO law.
-In 2006, an article in a CCP-owned newspaper warned that the growing presence of international NGOs would "undermine national security," "destroy political stability," "foster corruption," "propagate foreign practices," and "spy on and gather information on China's military, political, and economic information" [@Yin:2009, 534].
-The idea that INGOs would "propagate foreign practices" had especially powerful salience, since increased exposure to the West through international NGOs had the potential to "lead to adoption of Western ideas of liberty, further endangering government control over the populace" [@HsiaWhite:2002, 337].
-Educational NGOs were one particular avenue for the West to exert influence in the country---the directors and presidents of dozens of China's largest domestic NGOs have received doctoral degrees from and hold visiting appointments at Cornell, Duke, UNC-Chapel Hill, Harvard, Yale, and other prominent US universities [@Wang:2012, 108--9], and their training and connections abroad have influenced their programming and advocacy at home.
-In 2006, one Chinese NGO leader candidly explained that "foreign influence is definitely great.
-There is conceptual influence.
-Foreign NGOs' working methods also affect Chinese NGOs" [@Wang:2012, 110].
-Education can thus be seen as one of the more contentious issues allowed under the ONGO law, and thus more closely regulated and restricted.
-
-Additionally, the INGOs that survived the registration thresholds are those already "censored" to be relatively safe and non-contentious.
-This can help explain why some seemingly more contentious issue areas, e.g., environmental INGOs enjoy relatively more operational space.
-According to [@Plantan:2022], Chinese authorities can see the work of environmental INGOs as providing benefits such as political stability and "selectively encourage low risk groups and selectively channel higher risk groups into permitted areas".
-We will further this discussion with the case analysis of two environmental INGOs later.
-
-### Local connections
-
-In our second empirical expectation, we posit that since INGOs that seek out local connections and that are focused on more local China-specific issues, those organizations should be registered in fewer provinces.
-The results from our model confirm this expectation.
-@fig-local-preds(a) shows the distribution of predicted posterior outcomes for 1,000 hypothetical INGOs.
-Organizations without local connections are predicted to work nationally across all provinces nearly half of the time (with a 95% credible interval of 46--51%), and are predicted to work in two or more provinces 32--37% of the time.
-These organizations with no local connections or local programmatic focus are only predicted to work in a single province 15--19% of the time.
-In contrast, INGOs *with* local connections are far more likely to only work in one province (32--38%), or only work in a handful of provinces (36--41%).
-For these locally-focused organizations, the least common prediction is to work nationally, with only a 23--29% probability.
-@fig-local-preds(b) shows the posterior distribution of the average number of provinces INGOs are expected to be registered in, conditional on their local connections.
-The same relationship holds---an INGO without local connections is predicted to work in 19--24 provinces on average, while an organization with local connections is only predicted to work in 8--17.
-
-```{r fig-local-preds, fig.width=8, fig.height=4.5}
-#| include: true
-#| echo: false
-#| fig-cap: "Posterior predictions conditional on having local connections. 
-#|   **A**: Predicted proportion of INGOs working in 1 province, all 32 
-#|   provinces, or somewhere in between. 
-#|   **B**: Expectation of posterior predictive distributions."
-
-preds_local_text <- preds_local_plot |> 
-  group_by(outcome, local_connect) |> 
-  summarize(median_prop = median_qi(prop)) |> 
-  unnest(median_prop) |> 
-  group_by(local_connect) |> 
-  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
-  mutate(y_plot = 1 - y_plot) |> 
-  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
-  mutate(prop_ci_nice = glue::glue(
-    "{ymin}–{ymax}",
-    ymin = label_number(accuracy = 1, scale = 100)(ymin),
-    ymax = label_percent(accuracy = 1)(ymax)
-  ))
-
-p1 <- preds_local_plot |> 
-  ggplot(aes(x = draw, y = prop)) +
-  geom_area(
-    aes(fill = outcome, color = after_scale(fill)), 
-    position = position_stack(), linewidth = 0.1
-  ) +
-  geom_text(
-    data = preds_local_text,
-    aes(x = 250, y = y_plot, label = prop_ci_nice),
-    size = 3, fontface = "bold", color = "white"
-  ) +
-  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
-  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
-  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
-  facet_wrap(vars(local_connect), strip.position = "bottom", nrow = 1) +
-  labs(
-    x = NULL, y = "Predicted probability of geographic reach", fill = NULL,
-    title = "Predicted proportion of type of\ngeographic reach across local connections",
-    subtitle = "Posterior predictions of outcome categories",
-    tag = "A",
-    caption = str_wrap(
-      glue(
-        "The vertical slices of the bars depict 500 posterior samples;",
-        "the fuzziness represents the uncertainty in category boundaries.",
-        "95% credible intervals are shown as ranges in each category",
-        .sep = " "
-      ),
-      width = 80
-    )
-  ) +
-  theme_ongo() +
-  theme(
-    panel.grid.major = element_blank(),
-    panel.border = element_blank(),
-    panel.spacing = unit(5, "pt"),
-    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
-  )
-
-p2 <- epreds_local |>
-  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |>
-  ggplot(aes(x = local_connect, y = prop_to_provinces(.epred))) +
-  stat_halfeye(fill = clrs[6], color = clrs[8]) +
-  scale_x_discrete(labels = NULL) +
-  scale_y_continuous(
-    breaks = seq(0, 32, 8),
-    sec.axis = sec_axis(
-      trans = ~ provinces_to_prop(.),
-      name = "Proportion of provinces",
-      breaks = seq(0, 1, 0.25),
-      labels = label_percent()
-    )
-  ) +
-  facet_wrap(vars(local_connect), strip.position = "bottom", nrow = 1, scales = "free_x") +
-  guides(fill = "none") +
-  labs(
-    x = NULL, y = "Expected provinces",
-    title = "Expected count of provinces",
-    subtitle = "Expectation (or average) of posterior predictions",
-    tag = "B",
-    caption = str_wrap(
-      glue(
-        "These distributions take into account single-province and nationwide predictions",
-        "and represent the overall conditional average geographic range for INGOs.",
-        "Points show posterior median; lines show 80% and 95% credible intervals.",
-        .sep = " "
-      ),
-      width = 50
-    )
-  ) +
-  coord_cartesian(ylim = c(1, 32)) +
-  theme_ongo() +
-  theme(
-    panel.grid.major.x = element_blank(),
-    panel.border = element_blank(),
-    panel.spacing = unit(5, "pt"),
-    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
-  )
-
-(p1 | p2) +
-  plot_layout(widths = c(0.63, 0.37), guides = "collect")
-```
-
-International NGOs with locally focused missions and connections with local provincial officials are thus far more likely to purposely limit their activities to specific provinces, while organizations with broader non-local missions have a larger geographic reach.
-While we cannot precisely tell which direction the causal story works with this phenomenon, we can make some reasonable speculations.
-It is likely that locally-oriented INGOs purposely network and seek out connections with local PSUs before formally registering, thus fostering better relationships with government officials and furthering the organization's mission within its limited provinces.
-It is also likely, given the high probability of national reach, that organizations without local connections purposely do not spend the time and effort to cultivate those relationships, as it is not necessary to operate across many provinces.
-A rival explanation that having local connections reduces an organization's flexibility does not seem warranted.
-Although INGOs with local connections do have a more limited geographic scope, INGOs appear to purposely limit the number of provinces they work in in order to focus more on their local work.
-
-### Registration timing
-
-The ONGO Law officially came into effect on January 1, 2017, and as seen previously in @fig-registration-timeline, the first year of the law saw the greatest total number of registrations.
-In our third empirical expectation, we propose that these early registrants under the new law were both less of a threat to regime stability and a higher priority for bureaucratic processing, and thus should be registered in more provinces and have more geographic flexibility throughout the country.
-However, the results of our model support the *reverse* of this expectation.
-@fig-timing-preds(a) once again shows the predicted posterior outcomes for 1,000 simulated INGOs across a range of time since January 2017.
-Organizations that registered in the first year are predicted to work in all provinces 41--46% of the time, and are predicted to work in two or more provinces 34--39% of the time.
-These early INGOs are the most likely to be registered in only one province and are predicted to do so 17--23% of the time.
-After the initial wave of registrations in 2017, the likelihood of nationwide reach steadily increases and replaces both the probability of a single province or a partial range of provinces.
-By the end of 2021---5 years after the ONGO Law took effect---the probability of national-level registration increases to 55--61% while the probability of working in a range of provinces increases to predicted to work in two or more provinces increase to 27--32%.
-These late INGOs are the least likely to be registered in only one province and are predicted to do so only 17--22% of the time.
-@fig-timing-preds(b) demonstrates the same results with the posterior distribution of the expected count of provinces over five years since 2017.
-INGOs that register early are predicted to work in 17--22 provinces, while those that wait until 2021 are predicted to work in 21--28.
-
-```{r fig-timing-preds, fig.width=8, fig.height=4.5}
-#| include: true
-#| echo: false
-#| fig-cap: "Posterior predictions conditional on time since law took effect. 
-#|   **A**: Predicted proportion of INGOs working in 1 province, all 32 
-#|   provinces, or somewhere in between. 
-#|   **B**: Expectation of posterior predictive distributions."
-
-preds_timing_text <- preds_timing_plot |> 
-  filter(years_since_law == 2017.2) |> 
-  group_by(outcome) |> 
-  summarize(median_prop = median_qi(prop)) |> 
-  unnest(median_prop) |> 
-  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
-  mutate(y_plot = 1 - y_plot) |> 
-  mutate(years_since_law = 2017.2)
-
-layers <- preds_timing_plot |> 
-  filter(draw <= 50) |> 
-  split(~ draw) |> 
-  lapply(\(x) {
-    geom_area(
-      data = x,
-      aes(y = prop, fill = outcome),
-      alpha = 0.1
-    )
-  })
-
-p1 <- ggplot(preds_timing_plot, aes(x = years_since_law)) +
-  layers +
-  geom_text(
-    data = preds_timing_text, 
-    aes(y = y_plot, label = outcome),
-    color = "white",
-    hjust = 0, fontface = "bold", size = 3, show.legend = FALSE
-  ) +
-  scale_x_continuous(expand = expansion(mult = 0.02)) +
-  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
-  scale_color_manual(values = colorspace::darken(clrs[c(3, 5, 7)], 0.1)) +
-  scale_fill_manual(values = colorspace::lighten(clrs[c(3, 5, 7)], 0)) +
-  labs(
-    x = NULL, y = "Predicted probability of geographic reach", fill = NULL,
-    title = "Predicted proportion of type of \ngeographic reach since January 2017",
-    subtitle = "Posterior predictions of outcome categories",
-    tag = "A",
-    caption = str_wrap(
-      glue(
-        "Filled areas depict 50 posterior samples of the outcome category probabilities,",
-        "so the fuzziness represents the uncertainty in category boundaries; ",
-        .sep = " "
-      ),
-      width = 60
-    )
-  ) +
-  guides(fill = "none") +
-  theme_ongo() +
-  theme(
-    panel.grid.major = element_blank()
-  )
-
-p2 <- epreds_timing |>
-  ggplot(aes(x = years_since_law, y = prop_to_provinces(.epred))) +
-  stat_lineribbon(
-    .width = c(0.5, 0.8, 0.95),
-    alpha = 0.35, fill = clrs[6], color = clrs[6]
-  ) +
-  scale_y_continuous(
-    breaks = seq(0, 32, 8),
-    sec.axis = sec_axis(
-      trans = ~ provinces_to_prop(.),
-      name = "Proportion of provinces",
-      breaks = seq(0, 1, 0.25),
-      labels = label_percent()
-    )
-  ) +
-  labs(
-    x = NULL, y = "Expected provinces",
-    title = "Expected count of provinces",
-    subtitle = "Expectation (or average) of posterior predictions",
-    tag = "B",
-    caption = str_wrap(
-      glue(
-        "This distribution takes into account single-province and nationwide",
-        "predictions and represents the overall conditional average geographic",
-        "range for INGOs over time.",
-        "Shaded regions show the 50%, 80%, and 95% credible intervals.",
-        .sep = " "
-      ),
-      width = 65
-    )
-  ) +
-  coord_cartesian(ylim = c(1, 32)) +
-  theme_ongo()
-
-p1 | p2
-```
-
-We lack sufficient theory or data to explain why this trend goes against our expectations, but we can again make reasonable speculations.
-As we saw previously with INGOs and local connections, organizations appear to strategically seek out the best avenues and methods for registering [@Jia:2017a].
-Organizations that participated in the initial wave of registrations in 2017 likely had closer connections with local officials and were able to speed through the bureaucratic process registration more easily.
-As a preliminary test of this speculation, we rerun our main model with an interaction between years since registration and local connections to see how the effect of local connections changes over time.
-As seen in @fig-timing-local, early registrants in 2017 without local connections are more likely to have a larger geographic reach, registering in an average of 19--23 provinces, while their locally-focused counterparts are only expected to register in an average of 7--16 provinces.
-Accordingly, it may be that organizations with local connections are more likely to register early because of their pre-existing bureaucratic relationships, while organizations with a larger national reach take longer to undertake the registration process and thus register later.
-Another possible explanation is interpreting earlier timing in registration as more eager to register as discussed in the measurement section.
-INGOs that self-perceive as more contentious would be more nervous about the legal consequences of not being able to register and thus be more eager to seek registration earlier [@ChinaPhilanthropyReserchInstitute:2018].
-Compared with their more "rest-assured" peers, INGOs seeking to register earlier are more likely to have reduced operational space.
-To understand the underlying mechanism with registration timing, further research is warranted.
-
-```{r fig-timing-local, fig.width=6, fig.height=3.4, out.width="80%"}
-#| include: true
-#| echo: false
-#| fig-cap: "Expectation of posterior predictive distributions from model with 
-#|   interaction between local connections and time since January 2017."
-
-epreds_timing_local |>
-  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |>
-  ggplot(aes(x = years_since_law, y = prop_to_provinces(.epred))) +
-  stat_lineribbon(
-    .width = c(0.5, 0.8, 0.95),
-    alpha = 0.35, fill = clrs[6], color = clrs[6]
-  ) +
-  scale_y_continuous(
-    breaks = seq(0, 32, 8),
-    sec.axis = sec_axis(
-      trans = ~ provinces_to_prop(.),
-      name = "Proportion of provinces",
-      breaks = seq(0, 1, 0.25),
-      labels = label_percent()
-    )
-  ) +
-  guides(fill = "none") +
-  labs(
-    x = NULL, y = "Expected provinces",
-    title = "Expected count of provinces across local connections",
-    subtitle = "Expectation of posterior predictions",
-    caption = str_wrap(
-      glue(
-        "These distributions take into account single-province and nationwide",
-        "predictions and represents the overall conditional average geographic",
-        "range for INGOs over time.",
-        "Shaded regions show the 50%, 80%, and 95% credible intervals.",
-        .sep = " "
-      ),
-      width = 90
-    )
-  ) +
-  coord_cartesian(ylim = c(1, 32)) +
-  facet_wrap(vars(local_connect)) +
-  theme_ongo()
-```
-
-## Contentiousness and government relationships: The cases of The Nature Conservancy and Greenpeace
-
-We also conducted the qualitative study of two selected cases of INGOs in China to further understand the patterns revealed in the quantitative modeling and to examine a more comprehensive picture of how the operations of INGOs have been impacted by the ONGO Law.
-As explained, the registration documentation data enables us to analyze how the operational space is associated with issue areas and other factors for those INGOs that could successfully register.
-However, for INGOs that could not get registered but try to maintain their legal presence in China, a typical choice would be constantly filing temporary activities [@Corsetti:2019].
-So, we purposefully selected two environmental INGOs with different registration status to conduct a comparative analysis.
-One of them, the Nature Conservancy (“TNC”), successfully registered a RO under the ONGO Law, while the other INGO, Greenpeace has been filing temporary activities one after another since 2017 to continue carrying out programs in China.
-We use secondary data including public interviews (previously conducted by one of the authors) and their websites, in addition to official ONGO Law records of ROs and temporary activities to conduct the case studies.
-
-TNC and Greenpeace are both well-known INGOs working in the environmental issue area.
-Their headquarters are based in western countries and have offices around the world.
-They started to have long-standing offices in Beijing around the turn of the century, with TNC in 1998 and Greenpeace in 2001.
-Despite these similarities, the two INGOs had quite different experiences to sustain their legal presence in China after the ONGO Law took effect.
-According to records by the MPS, TNC’s RO was registered on May 19, 2017, with the National Forestry and Grassland Administration as their PSU.
-The RO in Beijing is eligible to operate in 27 provinces.
-Comparatively, Greenpeace has not registered any RO as of December 1, 2023.
-Instead, they have filed 67 temporary activities, almost going through the filing process 10 times each year.
-
-There are various drawbacks to having to constantly file temporary activities.
-First would be high administrative costs.
-Since the filing of temporary activities needs to be submitted by INGOs’ Chinese partners, it would mean discussing and securing the partnerships 67 times, mostly with different organizations.
-Moreover, this model also imposes high uncertainty to the operation of INGOs.
-There is no guarantee whether the next Chinese partner would agree to collaborate and file the documentation for them.
-And it is impossible to run longer-term projects, given all temporary activities cannot last longer than a year.
-Finally, temporary activities would be programs Chinese partners feel comfortable to collaborate in, i.e., safe activities with little political and administrative risks.
-So there is less flexibility in the kinds of work an INGO can do with temporary activities.
-
-What factors could have contributed to the contrasting experiences of TNC and Greenpeace under the ONGO Law?
-After analyzing the data, the working approach and relationship with the government emerged as pivotal differences between the two INGOs, which fits existing discussions on the differential treatment of INGOs based on their relationship with the authority [@Plantan:2022].
-In a public interview with TNC’s RO in China about their registration experience, the chief representative stated TNC’s working approach in China has been “science-based”, using “non-confrontational, collaborative approach in working closely with governments, the business community and others” [@ChinaPhilanthropyReserchInstitute:2018a].
-Over the years, they have provided technical support for the central government and local governments like the Yunnan and Zhejiang Provinces to build national parks and nature reserve areas and helped drafted such documents as the China Biodiversity Conservation Strategy and Action Plan (2011-2030).
-Using the non-confrontational working model and establishing long partnerships with the government enabled TNC to secure the consent of a national governmental agency in corresponding issue area to be their PSU, and thus successfully got registered and authorized to operate in a larger number of provinces.
-In contrast, Greenpeace states in their mission that they work as “independent campaigning organizations that use peaceful protest and creative confrontation to expose global environmental problems”.
-Their description of the work in China also uses such key words as “brings change”, “non-violent direct action”, and “impartiality and independence”.
-One project Greenpeace shares on their website was the exposure of the damages the company Sinar Mas Group's did in southwest Yunnan back in 2004.
-They conducted three rounds of  independent investigations and later revealed that the multinational paper industry company used reforestation as a cover while actually logging Yunnan's natural forests.
-Although this confrontation was not with the government, it showcases Greenpeace’s investigative, watchdog like work stance.
-To the authority, it would mean less predictable and manageable.
-
-::: {#tbl-case-study}
-
-```{r}
-#| label: table-case-study
-#| include: true
-
-compare_table <- read_csv(here::here("data", "manual_data", "table-case-study.csv"))
-
-compare_table |> 
-  gt(rowname_col = "Characteristic") |> 
-  cols_width(Characteristic ~ gt_pct(20), everything() ~ gt_pct(30)) |>
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) |>
-  tab_style(
-    style = cell_text(v_align = "top", weight = "bold"),
-    locations = cells_stub()
-  ) |>
-  opts_theme() |> 
-  tab_options(
-    quarto.disable_processing = TRUE
-  )
-```
-
-Comparison of the work of The Nature Conservancy and Greenpeace in China
-
-:::
-
-@tbl-case-study summarizes the comparison of the cases of TNC and Greenpeace.
-The case study shows that in addition to the correlation of issue area and operational space found in the quantitative model, the dimension of relationship with the government also exerts influence on the contentious level and restrictions INGOs can face, revealing the potential patterns of differential treatment INGOs can receive in the *de facto* implementation of the law.
-
-# Conclusion
-
-Political institutions are central to authoritarian stability as autocrats work to co-opt and balance institutional challenges to their regime.
-Autocrats treat civil society—both domestic and international—as yet another actor in their stability-seeking calculus.
-The ongoing phenomenon of closing civic space, where governments worldwide continue to impose repressive regulations on civil society, can be seen as a strategy for stabilizing authoritarian rule [@DeMattee:2019; @CarothersBrechenmacher:2014; @Heiss:2019].
-Notably, these laws are not enforced universally or consistently.
-The strategic enforcement of civil society laws creates a divergence between formal *de jure* regulations and the *de facto* implementation of those laws.
-Formal laws provide a legal framework for regulating INGOs, but government flexibility in enforcing those laws allows regimes to (1) act leniently towards organizations that offer services and expertise that benefit the regime, and (2) restrict, repress, or expel organizations that are deemed a risk to regime stability.
-
-We argue that regime preferences interact with organizations' issue areas to create variation in INGO operational space, or the *de facto* regulatory environment afforded to INGOs.
-We explore this theory by analyzing a novel dataset of all INGOs that have successfully registered in China since the implementation of the 2016 ONGO Law, a legal mechanism that provided the government with the ability to grow and shrink INGO operational space in strategic ways.
-By focusing on a specific law in one country, our work provides rich empirical illustrations of the mechanics of authoritarian administrative crackdown.
-We find that INGOs that work on issues that are less threatening and more aligned with regime preferences—such as arts & culture INGOs, industry associations, and scientific organizations—are registered in more provinces and thus enjoy a greater degree of operational space, while organizations that pose a potential threat—like education INGOs—are far more limited geographically.
-Our case study finds similar results.
-Because of its less confrontational approach and its connections to local government officials, The Nature Conservancy was able to obtain RO status and benefit from increased operational space while the more advocacy-focused Greenpeace has resorted to filing dozens of program-specific temporary activities.
-
-Studying INGOs in authoritarian regimes poses a number of limitations, but the concept of operational space can address some of these issues in the future.
-First, we can only observe organizations that successfully registered as ROs.
-We cannot make comparisons with INGOs that left the country prior to 2017 or INGOs that have explicitly chosen to not work in China.
-This is not an issue specific to China—analyzing the international nonprofit sector of any country that has passed similar laws will raise similar issues of selection bias.
-The Chinese context provides one possible way forward: future research can further explore relationship between INGOs and regime preferences by comparing characteristics of INGOs that register as ROs or undertake temporary activities using already-available administrative data.
-Second, this paper focuses exclusively on INGO regulations in China, and the specific legal mechanisms for controlling INGOs in other countries will naturally differ.
-However, the findings are still instructive.
-We have illustrated how the interpretation and implementation of one INGO law has reshaped the role of international civil society, leading to a preponderance of regime-friendly NGOs, many of which have realigned their programming with government preferences.
-It is likely that a similar dynamic plays out in other countries—regimes legislate civil society broadly and enforce those laws specifically and individually.
-Future research can analyze the determinants of INGO operational space in other authoritarian states, which can help INGOs facing legal crackdown abroad strengthen their organizational flexibility in the face of restricted legal environments.
-
-# References
-
-::: {#refs .bibliography}
-:::
-
-\newpage
-
-:::: {#appendix-count}
 
@@
 
-::::
+## Modeling details
+
+We use Stan through R and brms to estimate the model.
+We simulate 4 MCMC chains with 2,000 draws in each chain, 1,000 of which are used for warmup, resulting in 4,000 (1,000 × 4) draws per model parameter.
+We assess convergence with visual inspection, and all chains converge.
+Complete results from all the models, along with posterior predictive checks, goodness-of-fit measures, and model diagnostics—as well as our code and data—are available `ANONYMIZED_URL`.
+
+TODO: Model definition and priors like NVSQ paper

### 2023-12-06 manuscript/manuscript.qmd
Make the appendix a separate file
…so that we can have a separate bibliography for software + other methods-related things

@@
 :::
-
-\newpage
-
-:::: {#appendix-count}
-
-# Appendix
-
-## Coding rules for issue ares
-
-1. Education vs. Charity
-If charitable activities are all education related, e.g. building schools, donating education facilities and books, coded as education
-If the aids provided include other community support, e.g. building bridges, roads, medical facilities, coded as charity
-
-2. Economy and trade vs. Industry association
-If the trade promoted is focused on a particular industry (poultry, grains etc.), coded as industry association
-
-3. Arts and culture 
-Include sports organizations too.
-
-4. Industry association vs. health, science and technology, arts and culture
-
-There are professional association on health providers and certain techniques.
-Coded as health, science & technology if work areas go beyond serving members only: for example conducting activities of promoting and training about certain techniques.
-
-If specialized association only serves the member companies: coded as industry associations
-
-5. Health vs. Charity 
-If only providing medical aids to underprivileged communities, not building schools etc., coded as health
-
-6. Charity vs. General 
-If multiple work, e.g., poverty alleviation, education, health can be encompassed by Charity and humanitarian, then the former
-
-7. Multiple ROs are coded based on the overall work area spans of the INGO, not the specific RO, so to ensure the issue area coding is consistent across ROs
-
-::::

### 2023-12-06 manuscript/manuscript.qmd
Fx a few minor tupos

@@
 The filing documents for ROs disclose each INGO's name, address, registration date, regulating Public Security Bureau, PSU, issue area and purposes of the RO, and the specific provinces they can work in.
-We merge this INGO data with translated English organization names data from ChinaFile.
-Our data and reproducible code is available at `ANONYMIZED_DOI_URL`.
+We merge this INGO data with translated English organization names from ChinaFile.
+Our data and reproducible code are available at `ANONYMIZED_DOI_URL`.
 
@@
 Our key independent variables correspond to each of our three theoretical expectations.
-First we code each INGO's issue area based on its mission statement reported in its registration documentation.
-Given there is certain level of subjectivity in the coding process, we cross-checked our manual coding of issue areas---Author 1 assigned each organization into one of the issue areas defined in Article 3 of the ONGO Law, and Author 2 cross-checked the coding for ambiguous cases.
+First, we code each INGO's issue area based on its mission statement reported in its registration documentation.
+Given the subjectivity in the coding process, we cross-checked our manual coding of issue areas---Author 1 assigned each organization to one of the issue areas defined in Article 3 of the ONGO Law, and Author 2 cross-checked the coding for ambiguous cases.
 We include our coding rules for overlapping issue areas in the appendix.
@@
 Our final independent variable measures how much time elapsed between January 1, 2017 (when the law took effect) and the organization's official registration date.
-There is great variance in the timing of registering an RO among INGOs, since there has been a *de facto* grace period for INGOs to seek legal presence after the law took effect [@Shieh:2018].
+There is great variance in the timing of registering an RO among INGOs, since there was a brief grace period for INGOs to seek legal presence after the law took effect [@Shieh:2018].
 This is largely because both INGOs and the regulators needed some transitional time to explore the specific application of the law as large ambiguity was left when the law was passed.
-We use this temporal variable as a proxy for the motivation or eagerness of INGOs to register an RO, for some INGOs are inclined to avoid the cumbersome registration procedures at the early stage if there is no real consequences for continuing operations without registration, while others took the time to talk with multiple potential PSUs to find a more suitable superior or regulatory dynamic [@Jia:2017a].
+We use this temporal variable as a proxy for the motivation or eagerness of INGOs to register an RO, for some INGOs are inclined to avoid the cumbersome registration procedures at the early stage if there are no real consequences for continuing operations without registration, while others took the time to talk with multiple potential PSUs to find a more suitable superior or regulatory dynamic [@Jia:2017a].
 
@@
 This approach allows us to hold specific variables constant and generate predictions for hypothetical new, not-yet-registered INGOs, providing us with stronger empirical implications.
-Additionally, Bayesian modeling allows us better model the uncertainty associated with INGO operational space—instead of reporting a single value for the number of provinces INGOs have access to, we can and report posterior credible intervals that represent the probability that the average geographic reach falls within a specific range.
+Additionally, Bayesian modeling allows us to analyze the uncertainty associated with INGO operational space—instead of reporting a single value for the number of provinces INGOs have access to, we report posterior credible intervals that represent the probability that the average geographic reach falls within a specific range.
 
@@
 #| echo: false
-#| fig-cap: "Count of the number of provinces each INGO is authorized to operate in.
-The left panel shows the full distribution of INGOs registered in 2–31 provinces; the right panel collapses these in-between counts to a single category."
+#| fig-cap: "Count of the number of provinces each INGO is authorized to operate 
+#|   in. The left panel shows the full distribution of INGOs registered in 2–31 
+#|   provinces; the right panel collapses these in-between counts into to a 
+#|   single category."
+
 provinces_collapsed <- ongo |> 
@@
 To account for values at the bounds, we rely on ordered Beta regression [@Kubinec:2022], an extension of zero-and-one-inflated Beta regression that allows us to simultaneously model the continuous range of provinces (2--31) and the discrete outcomes (1 province and 32 provinces).
-We can thus explore the dynamics of each of our independent variables of interest in multiple ways---we can see (1) how each variable predicts that an organizations works in one province, nationwide, or somewhere in between, and (2) how each variable predicts the overall expected count of provinces.
+We can thus explore the dynamics of each of our independent variables of interest in multiple ways---we can see how each variable (1) predicts that an organization works in one province, nationwide, or somewhere in between, and (2) predicts the overall expected count of provinces.
 
@@
 
-W first describe some of the general patterns related to INGO operational space during the first 5 years of the ONGO law.
+We first describe some of the general patterns related to INGO operational space during the first 5 years of the ONGO law.
 First, @fig-registration-timeline shows the distribution of the count of new INGO registrations since January 1, 2017.
 A couple dozen organizations were able to become ROs immediately after the law took effect during the first quarter of 2017, while hundreds more registered during the rest of that year.
-Nearly half of all currently-registered INGOs in China---48%---registered in 2017.
+Nearly half of all currently registered INGOs in China---48%---registered in 2017.
 After the initial first-year wave, the count of new registrations has declined slowly since 2018.
@@
 
-Next we explore our data in more depth by generating and analyzing posterior predictions from our ordered Beta regression model, varying specific variables of interest while holding all others constant.
+Next, we explore our data in more depth by generating and analyzing posterior predictions from our ordered Beta regression model, varying specific variables of interest while holding all others constant.
 

### 2023-12-06 manuscript/appendix.qmd
Add software references

@@
 
-We use Stan through R and brms to estimate the model.
-We simulate 4 MCMC chains with 2,000 draws in each chain, 1,000 of which are used for warmup, resulting in 4,000 (1,000 × 4) draws per model parameter.
+We use Stan [@Stan-2-26-1 v2.26.1; @cmdstan-2-3-1 v2.3.1] through R [@rproject-4-3-1 v4.3.1] and **brms** [@Burkner:2017 v2.20.5] to estimate the model We simulate 4 MCMC chains with 2,000 draws in each chain, 1,000 of which are used for warmup, resulting in 4,000 (1,000 × 4) draws per model parameter.
 We assess convergence with visual inspection, and all chains converge.

### 2023-12-06 R/funs_data.R
Add a column for English province names bc I can't read Chinese :)

@@ -102,6 +102,48 @@ clean_map_data <- function(ongo) {
   suppressPackageStartupMessages(library(sf))
   suppressPackageStartupMessages(library(mapchina))
   
+  # Manual lookup table for Andrew :)
+  provinces_zh2en <- tribble(
+    ~Name_Province, ~province_en,
+    "上海市", "Shanghai",
+    "云南省", "Yunnan Province",
+    "内蒙古自治区", "Inner Mongolia Autonomous Region",
+    "北京市", "Beijing",
+    "台湾省", "Taiwan Province",
+    "吉林省", "Jilin Province",
+    "四川省", "Sichuan Province",
+    "天津市", "Tianjin City",
+    "宁夏回族自治区", "Ningxia Hui Autonomous Region",
+    "安徽省", "Anhui Province",
+    "山东省", "Shandong Province",
+    "山西省", "Shanxi Province",
+    "广东省", "Guangdong Province",
+    "广西壮族自治区", "Guangxi Zhuang Autonomous Region",
+    "新疆维吾尔自治区", "Xinjiang Uygur Autonomous Region",
+    "江苏省", "Jiangsu Province",
+    "江西省", "Jiangxi Province",
+    "河北省", "Hebei Province",
+    "河南省", "Henan Province",
+    "浙江省", "Zhejiang Province",
+    "海南省", "Hainan",
+    "湖北省", "Hubei Province",
+    "湖南省", "Hunan Province",
+    "澳门特别行政区", "Macao Special Administrative Region",
+    "甘肃省", "Gansu Province",
+    "福建省", "Fujian Province",
+    "西藏自治区", "Tibet Autonomous Region",
+    "贵州省", "Guizhou Province",
+    "辽宁省", "Liaoning Province",
+    "重庆市", "Chongqing",
+    "陕西省", "Shaanxi Province",
+    "青海省", "Qinghai Province",
+    "香港特别行政区", "Hong Kong Special Administrative Region",
+    "黑龙江省", "Heilongjiang Province"
+  ) |>
+    mutate(province_en_short = str_remove_all(
+      province_en, " Province| Autonomous Region| Special Administrative Region"
+    ))
+  
   # Clean up the geographic data
   suppressMessages({
     sf_use_s2(FALSE)  # https://github.com/xmc811/mapchina/issues/7#issuecomment-1028792066
@@ -120,9 +162,10 @@ clean_map_data <- function(ongo) {
   # Join ONGO count to map
[…]

### 2023-12-06 manuscript/manuscript.qmd
Move descriptive results to data section + add inline chunks + more editing

@@
 link-citations: true
+toc-depth: 4
 ---
@@
 
+```{r calc-summaries}
+provinces <- ongo_mapdata |> 
+  st_drop_geometry() |> 
+  mutate(rank = dense_rank(-ro_count)) |> 
+  mutate(list_name = janitor::make_clean_names(province_en_short)) |> 
+  split(~ list_name)
+
+# Get the RO count for the 4th-ranked province
+province4th <- provinces |> 
+  map(~filter(.x, rank == 4)) |> 
+  keep(~nrow(.x) > 0)
+
+loc <- ongo |> 
+  count(local_connect) |> 
+  mutate(prop = n / sum(n)) |> 
+  mutate(prop_nice = label_percent(accuracy = 1)(prop)) |> 
+  mutate(local_connect = janitor::make_clean_names(local_connect)) |> 
+  split(~ local_connect)
+
+# MAYBE: Use issue_area instead of work_field_code
+issue_count <- ongo |> 
+  drop_na(work_field_code1) |> 
+  group_by(work_field_code1) |>
+  summarize(n = n()) |> 
+  mutate(work_field_code1 = fct_reorder(work_field_code1, n))
+
+issues <- issue_count |> 
+  mutate(prop = n / sum(n)) |> 
+  mutate(prop_nice = label_percent(accuracy = 1)(prop)) |> 
+  mutate(work_field_code1 = janitor::make_clean_names(work_field_code1)) |> 
+  split(~ work_field_code1)
+```
+
+```{r calc-preds}
+# Issue area
+preds_issue_plot_order <- preds_issue_plot |> 
+  filter(outcome == "All 32 provinces") |>
+  group_by(issue_area_nice) |> 
+  summarize(median_prop = median(prop)) |> 
+  arrange(median_prop) |> 
+  mutate(issue_area_nice_labels = str_wrap(issue_area_nice, 15)) |> 
+  mutate(issue_area_nice = fct_inorder(issue_area_nice))
+
+preds_issue_text <- preds_issue_plot |> 
+  group_by(outcome, issue_area_nice) |> 
+  summarize(median_prop = median_qi(prop)) |> 
+  unnest(median_prop) |> 
+  group_by(issue_area_nice) |> 
+  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
+  mutate(y_plot = 1 - y_plot) |> 
+  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
+  mutate(prop_ci_nice = glue::glue(
+    "{ymin}–{ymax}",
+    ymin = label_number(accuracy = 1, scale = 100)(ymin),
+    ymax = label_percent(accuracy = 1)(ymax)
+  )) |> 
+  mutate(issue_area_nice = factor(
+    issue_area_nice, 
+    levels = preds_issue_plot_order$issue_area_nice,
+    labels = preds_issue_plot_order$issue_area_nice_labels
+  ))
+
+p_issue <- preds_issue_text |> 
+  group_by(outcome) |> 
+  mutate(issue_area_nice = janitor::make_clean_names(issue_area_nice)) |> 
+  group_by(issue_area_nice) |> 
+  mutate(outcome = janitor::make_clean_names(outcome)) |> 
+  ungroup() |> 
+  split(~ issue_area_nice + outcome)
+
+# Local connections
+preds_local_text <- preds_local_plot |> 
+  group_by(outcome, local_connect) |> 
+  summarize(median_prop = median_qi(prop)) |> 
+  unnest(median_prop) |> 
+  group_by(local_connect) |> 
+  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
+  mutate(y_plot = 1 - y_plot) |> 
+  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
+  mutate(prop_ci_nice = glue::glue(
+    "{ymin}–{ymax}",
+    ymin = label_number(accuracy = 1, scale = 100)(ymin),
+    ymax = label_percent(accuracy = 1)(ymax)
+  ))
+```
+
 ::: {.content-visible when-format="html"}
@@
 To capture the benefits and reduce the risk of working with INGOs, most authoritarian states rely on "administrative crackdown" [@Chaudhry:2022], or laws that create barriers to NGO advocacy, entry, and funding [@ChristensenWeinstein:2013; @ChaudhryHeiss:2022; @CarothersBrechenmacher:2014].
-These laws, however, are a blunt tool and target civil society as a whole---states do not create one set of formal laws that applies only to regime-friendly INGOs and another set that applies to more risky INGOs.
+These laws, however, are a blunt tool and target civil society as a whole---states do not create one set of formal laws that applies only to regime-friendly INGOs and another set that applies to riskier INGOs.
 Instead, there is a divergence between the formal *de jure* laws and the *de facto* implementation of their accompanying regulations.
@@
 We examine these theoretical expectations using a mixed methods approach.
-First, we explore a rich dataset of all ROs registered in China between 2017–2021 using a combination of descriptive statistics and Bayesian models to understand how the international civil society in China has been reshaped since the implementation of the ONGO law.
-We then complement this statistical analysis with a comparative case study of two INGOs---The Nature Conservancy and Greenpeace ---to explore in detail how the ONGO has specifically influenced organizational operational space.
+First, we explore a rich dataset of all ROs registered in China between 2017–2021 using Bayesian regression models to understand how the international civil society in China has been reshaped since the implementation of the ONGO law.
+We then complement this statistical analysis with a comparative case study of two INGOs---The Nature Conservancy and Greenpeace---to explore in detail how the ONGO has specifically influenced organizational operational space.
 
@@
 
-## Measurement
-
 Our dependent variable is the count of provinces that INGOs are authorized to work in.
 We derive this value from the official registration record, which lists all the provincial regions each INGO RO can conduct activities in.
-This value ranges from 1–32 (the total number of province-level jurisdictions in mainland China).
+This value ranges from 1–32, the total number of province-level jurisdictions in mainland China.
+There are clear geographic trends in this measure.
+@fig-home-office-map shows that Beijing (`r provinces$beijing$ro_count`), Shanghai (`r provinces$shanghai$ro_count`), and Guangdong Province (`r provinces$guangdong$ro_count`) host the most ROs, while other provinces have as many as `r province4th[[1]]$ro_count` and as few as 1 permitted RO.
+
+```{r fig-home-office-map}
+#| include: true
+#| echo: false
+#| fig-cap: "Count of registered organizations across provinces"
+# Extract the intersections of provinces so that we don't plot the outside
+# borders and distort the coastlines. See https://stackoverflow.com/a/57138069 
+# and https://ikashnitsky.phd/2023/map-borders/
+interior_borders <- st_intersection(ongo_mapdata) %>% 
+  filter(n.overlaps > 1) |> 
+  # Remove weird points that st_intersection() adds
+  filter(!(st_geometry_type(geometry) %in% c("POINT", "MULTIPOINT")))
+
+# Use aes(geometry) and stat = "sf_coordinates" to make geom_label_repel() work
+# with geom_sf(): https://github.com/slowkow/ggrepel/issues/111#issuecomment-416853013
+ggplot() +
+  geom_sf(data = ongo_mapdata, aes(fill = ro_count), color = NA) +
+  geom_sf(data = interior_borders, linewidth = 0.3, color = "white") +
+  scale_fill_distiller(palette = "Reds", direction = 1, guide = "none", na.value = "gray80") +
+  geom_label_repel(
+    data = filter(ongo_mapdata, ro_count > 0),
+    aes(label = ro_count, geometry = geometry),
+    stat = "sf_coordinates", seed = 1234, label.size = 0.05, size = 3,
+    color = "black", fill = scales::alpha("white", 0.7),
+    segment.color = "black", segment.size = 0.25, min.segment.length = 0
+  ) +
+  coord_sf(crs = st_crs("EPSG:4480")) +  # China Geodetic Coordinate System 2000
+  theme_void()
+```
 
@@
 First, we code each INGO's issue area based on its mission statement reported in its registration documentation.
-Given the subjectivity in the coding process, we cross-checked our manual coding of issue areas---Author 1 assigned each organization to one of the issue areas defined in Article 3 of the ONGO Law, and Author 2 cross-checked the coding for ambiguous cases.
-We include our coding rules for overlapping issue areas in the appendix.
+Given the subjectivity in the coding process, we cross-checked our manual coding of issue areas (see the appendix for a description of our coding).
 We categorize each organization into nine different issue areas (see @tbl-issues).
+@fig-issue-props shows the distribution of these issue areas.
+The two most common issues are economic, trade, and industry associations, representing `r label_percent()((issues$industry_association$n + issues$economy_and_trade$n) / sum(issue_count$n))` (`r issues$industry_association$n + issues$economy_and_trade$n`) of all INGOs.
+Many of these organizations are bilateral chambers of commerce or other multilateral trade organizations.
+Charitable, humanitarian, education, and health INGOs are far less common than their trade and industry counterparts: charity and humanitarian organizations comprise `r issues$charity_and_humanitarian$prop_nice` (`r issues$charity_and_humanitarian$n`) of ROs.
 
@@
   "Arts and culture", "World Dance Council; Special Olympics",
-  "Charity and humanitarian", "Save the Children; Half the Sky Foundation",
-  "Economy and trade", "World Economic Forum; Chile-China Chamber of Commerce",
+  "Charity and humanitarian", "Save the Children; World Vision",
+  "Economy and trade", "World Economic Forum; Canada China Business Council",
   "Education", "Children’s Education Foundation; BSK International",
@@
 
+```{r fig-issue-props, fig.width=6, fig.height=3}
+#| include: true
+#| echo: false
+#| fig-cap: "Count of international NGO registrations, divided by issue area"
+
+ggplot(issue_count, aes(y = work_field_code1, x = n)) +
+  geom_col(fill = clrs[5]) +
+  scale_x_continuous(sec.axis = sec_axis(trans = ~ . / sum(issue_count$n),
+                                         labels = label_percent())) +
+  labs(x = "Count of INGOs", y = NULL) +
+  theme_ongo() +
+  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
+```
+
 Our second independent variable is a dichotomous indicator of whether the INGO explicitly states that it intends to operate locally or sub-provincially.
 There are cases where the aim of the INGO is attached to a locality, either having a county or city name in their RO name or purposes, or the INGO is actually set up by people in China who registered the RO to communicate between the "hometown" and the INGO set up abroad.
-
-Our final independent variable measures how much time elapsed between January 1, 2017 (when the law took effect) and the organization's official registration date.
-There is great variance in the timing of registering an RO among INGOs, since there was a brief grace period for INGOs to seek legal presence after the law took effect [@Shieh:2018].
+Of the `r nrow(ongo)` ROs, `r loc$true$n` (`r loc$true$prop_nice`) have a narrow local focus.
+
+Our final independent variable measures how much time elapsed between January 1, 2017 and the organization's official registration date.
+There is great variance in registration timing, since there was a brief grace period for INGOs to seek legal presence after the law took effect [@Shieh:2018].
+Nearly half of all ROs---48%---registered in 2017, and the count of new registrations gradually declined after the initial first-year wave (see @fig-registration-timeline).
 This is largely because both INGOs and the regulators needed some transitional time to explore the specific application of the law as large ambiguity was left when the law was passed.
-We use this temporal variable as a proxy for the motivation or eagerness of INGOs to register an RO, for some INGOs are inclined to avoid the cumbersome registration procedures at the early stage if there are no real consequences for continuing operations without registration, while others took the time to talk with multiple potential PSUs to find a more suitable superior or regulatory dynamic [@Jia:2017a].
+We use this temporal variable as a proxy for the motivation or eagerness of INGOs to register as an RO, since INGOs may have been inclined to avoid the cumbersome registration procedures at the early stage if there were no real consequences for delaying, while others took the time to talk with multiple potential PSUs to find a more suitable superior or regulatory dynamic [@Jia:2017a].
+
+```{r fig-registration-timeline, fig.width=6, fig.height=3}
+#| include: true
+#| echo: false
+#| fig-cap: "Count of international NGO registrations under the 2016 ONGO Law, 
+#|   divided by quarters"
+
+ggplot(ongo, aes(x = registration_date)) +
+  geom_histogram(binwidth = 365.25/4, boundary = ymd("2017-01-01"), 
+                 fill = clrs[6], color = "white") +
+  scale_x_date(date_breaks = "years", date_labels = "%Y") +
+  labs(x = NULL, y = "Count of new INGO registrations") +
+  theme_ongo()
+```
 
@@
 
-In addition to presenting descriptive summary statistics, we use a multilevel Bayesian regression model to examine the complex effects that issue area, local connections, and registration timing have on organizational flexibility.
+We use a multilevel Bayesian regression model to examine the complex effects that issue area, local connections, and registration timing have on organizational flexibility.
 This approach allows us to hold specific variables constant and generate predictions for hypothetical new, not-yet-registered INGOs, providing us with stronger empirical implications.
-Additionally, Bayesian modeling allows us to analyze the uncertainty associated with INGO operational space—instead of reporting a single value for the number of provinces INGOs have access to, we report posterior credible intervals that represent the probability that the average geographic reach falls within a specific range.
+Additionally, Bayesian modeling allows us to analyze the uncertainty associated with INGO operational space---instead of reporting a single value for the number of provinces INGOs have access to, we report posterior credible intervals that represent the probability that the average geographic reach falls within a specific range.
 
@@
 
-## Descriptive overview
-
-We first describe some of the general patterns related to INGO operational space during the first 5 years of the ONGO law.
-First, @fig-registration-timeline shows the distribution of the count of new INGO registrations since January 1, 2017.
-A couple dozen organizations were able to become ROs immediately after the law took effect during the first quarter of 2017, while hundreds more registered during the rest of that year.
-Nearly half of all currently registered INGOs in China---48%---registered in 2017.
-After the initial first-year wave, the count of new registrations has declined slowly since 2018.
-
-```{r fig-registration-timeline, fig.width=6, fig.height=3}
-#| include: true
-#| echo: false
-#| fig-cap: "Count of international NGO registrations under the 2016 ONGO Law, 
-#|   divided by quarters"
-ggplot(ongo, aes(x = registration_date)) +
-  geom_histogram(binwidth = 365.25/4, boundary = ymd("2017-01-01"), 
-                 fill = clrs[6], color = "white") +
-  scale_x_date(date_breaks = "years", date_labels = "%Y") +
-  labs(x = NULL, y = "Count of new INGO registrations") +
-  theme_ongo()
-```
-
-Next, @fig-issue-props shows the distribution of issue areas that registered INGOs focus on.
-The two most common issues are economic, trade, and industry associations, representing 50% of all INGOs.
-Many of these organizations are bilateral chambers of commerce or other multilateral trade organizations such as the Japan-China Economic Association, the Silk Road Chamber of International Commerce, and the Canada China Business Council.
-Charitable, humanitarian, education, and health INGOs are far less common than their trade and industry counterparts: charity and humanitarian organizations like World Vision, Save the Children, and the Salvation Army comprise only 12% (73) of all INGOs.
-
-```{r fig-issue-props, fig.width=6, fig.height=3}
-#| include: true
-#| echo: false
-#| fig-cap: "Count of international NGO registrations, divided by issue area"
-# MAYBE: Use issue_area instead of work_field_code
-issue_count <- ongo |> 
-  drop_na(work_field_code1) |> 
-  group_by(work_field_code1) |>
-  summarize(n = n()) |> 
-  mutate(work_field_code1 = fct_reorder(work_field_code1, n))
-
-ggplot(issue_count, aes(y = work_field_code1, x = n)) +
-  geom_col(fill = clrs[5]) +
-  scale_x_continuous(sec.axis = sec_axis(trans = ~ . / sum(issue_count$n),
-                                         labels = label_percent())) +
-  labs(x = "Count of INGOs", y = NULL) +
-  theme_ongo() +
-  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
-```
-
-Finally, there are clear geographic trends in INGO registration.
-As seen in @fig-home-office-map, the majority of INGOs are headquartered in Beijing (166), Shanghai (137), and Guangdong Province (46).
-INGOs must select a home office for their Chinese operations, but they are not necessarily limited to work within their home provinces.
-As described earlier, each INGO is authorized to work in a list of approved provinces, and the count of provinces follows a distinctive three-tiered distribution, seen previously in @fig-province-count-collapsed, with 30% of INGOs authorized to work in just one province, 40% authorized to work nationally, and 30% authorized to work in between 2--31 provinces.
-
-```{r fig-home-office-map}
-#| include: true
-#| echo: false
-#| fig-cap: "Count of registered organizations across provinces"
-# Extract the intersections of provinces so that we don't plot the outside
-# borders and distort the coastlines. See https://stackoverflow.com/a/57138069 
-# and https://ikashnitsky.phd/2023/map-borders/
-interior_borders <- st_intersection(ongo_mapdata) %>% 
-  filter(n.overlaps > 1) |> 
-  # Remove weird points that st_intersection() adds
-  filter(!(st_geometry_type(geometry) %in% c("POINT", "MULTIPOINT")))
-
-# Use aes(geometry) and stat = "sf_coordinates" to make geom_label_repel() work
-# with geom_sf(): https://github.com/slowkow/ggrepel/issues/111#issuecomment-416853013
-ggplot() +
-  geom_sf(data = ongo_mapdata, aes(fill = ro_count), color = NA) +
-  geom_sf(data = interior_borders, linewidth = 0.3, color = "white") +
-  scale_fill_distiller(palette = "Reds", direction = 1, guide = "none", na.value = "gray80") +
-  geom_label_repel(
-    data = filter(ongo_mapdata, ro_count > 0),
-    aes(label = ro_count, geometry = geometry),
-    stat = "sf_coordinates", seed = 1234, label.size = 0.05, size = 3,
-    color = "black", fill = scales::alpha("white", 0.7),
-    segment.color = "black", segment.size = 0.25, min.segment.length = 0
-  ) +
-  coord_sf(crs = st_crs("EPSG:4480")) +  # China Geodetic Coordinate System 2000
-  theme_void()
-```
-
-## Posterior predictions
-
-Next, we explore our data in more depth by generating and analyzing posterior predictions from our ordered Beta regression model, varying specific variables of interest while holding all others constant.
+## Model results
 
@@
 
-Following our first empirical expectation, we predict that INGOs working on less contentious issues should be registered in more provinces and have more geographic flexibility to work throughout the country.
-To explore this, we can take advantage of the simultaneous continuous and discrete features of ordered Beta regression and see how often an INGO in each issue area is predicted to work in a single province, across all provinces, or some number in between.
-@fig-issue-preds(a) presents a summary of predicted posterior outcomes for 1,000 hypothetical INGOs, varying each possible issue area and holding all other variables at their mean or modal values.
+Next, we explore the data in more depth by generating and analyzing posterior predictions from our model.
+Following our first empirical expectation, we predict that INGOs working on less contentious issues should be registered in more provinces and thus have more geographic flexibility.
+We take advantage of the simultaneous continuous and discrete features of ordered Beta regression and see how often an INGO in each issue area is predicted to work in a single province, across all provinces, or some number in between.
+@fig-issue-preds(a) presents a summary of predicted posterior outcomes for 1,000 hypothetical INGOs, varying each issue area and holding all other variables at their mean or modal values.
 Several notable trends emerge from the model results.
-INGOs focused on arts and culture are overwhelming the most likely kind of organization to work nationally---arts and culture organizations are predicted to work in all 32 provinces 80% of the time (with a credible interval of 78--83%) and are only predicted to work in a single province a rare 3--5% of the time.
-Education-focused INGOs, on the other hand, are the least likely kind of organization to be registered in all 32 provinces and are predicted to do so only 32--38% of the time.
-Education INGOs are the most likely to be registered in only one province, with that predicted outcome appearing 24--29% of the time---at least 10 percentage points higher than any other issue area's predicted proportion.
-All other issue areas follow roughly the patterns in predictions: the most common outcome is for organizations to work nationally (50--60% of the time), followed by working in at least 2 provinces (25--40% of the time), followed by working in a single province (10--20% of the time).
+INGOs focused on arts and culture are overwhelming the most likely kind of organization to work nationally---arts and culture organizations are predicted to work in all 32 provinces `r p_issue$arts_and_culture.all_32_provinces$prop_ci_nice` of the time and are only predicted to work in a single province a rare `r p_issue$arts_and_culture.only_1_province$prop_ci_nice` of the time.
+Education-focused INGOs, on the other hand, are the least likely kind of organization to be registered in all 32 provinces and are predicted to do so only `r p_issue$education.all_32_provinces$prop_ci_nice` of the time.
+Education INGOs are the most likely to be registered in only one province, with that predicted outcome appearing `r p_issue$education.only_1_province$prop_ci_nice` of the time---15--20 percentage points higher than any other issue area's predicted proportion.
+All other issue areas follow roughly similar patterns in predictions: the most common outcome is for organizations to work nationally (≈45--60% of the time), followed by working in at least 2 provinces (≈25--35% of the time), followed by working in a single province (≈15--30% of the time).
 @fig-issue-preds(b) shows the continuous posterior distribution of the average number of provinces INGOs are expected to be registered in across all types of issue areas, but accounting for the 1- and 32-only provinces simultaneously.
@@
 #|   **B**: Expectation of posterior predictive distributions."
-
-preds_issue_plot_order <- preds_issue_plot |> 
-  filter(outcome == "All 32 provinces") |>
-  group_by(issue_area_nice) |> 
-  summarize(median_prop = median(prop)) |> 
-  arrange(median_prop) |> 
-  mutate(issue_area_nice_labels = str_wrap(issue_area_nice, 15)) |> 
-  mutate(issue_area_nice = fct_inorder(issue_area_nice))
-
-preds_issue_text <- preds_issue_plot |> 
-  group_by(outcome, issue_area_nice) |> 
-  summarize(median_prop = median_qi(prop)) |> 
-  unnest(median_prop) |> 
-  group_by(issue_area_nice) |> 
-  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
-  mutate(y_plot = 1 - y_plot) |> 
-  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
-  mutate(prop_ci_nice = glue::glue(
-    "{ymin}–{ymax}",
-    ymin = label_number(accuracy = 1, scale = 100)(ymin),
-    ymax = label_percent(accuracy = 1)(ymax)
-  )) |> 
-  mutate(issue_area_nice = factor(
-    issue_area_nice, 
-    levels = preds_issue_plot_order$issue_area_nice,
-    labels = preds_issue_plot_order$issue_area_nice_labels
-  ))
 
@@
 
-preds_local_text <- preds_local_plot |> 
-  group_by(outcome, local_connect) |> 
-  summarize(median_prop = median_qi(prop)) |> 
-  unnest(median_prop) |> 
-  group_by(local_connect) |> 
-  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
-  mutate(y_plot = 1 - y_plot) |> 
-  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
-  mutate(prop_ci_nice = glue::glue(
-    "{ymin}–{ymax}",
-    ymin = label_number(accuracy = 1, scale = 100)(ymin),
-    ymax = label_percent(accuracy = 1)(ymax)
-  ))
-
 p1 <- preds_local_plot |> 
@@
 
-The ONGO Law officially came into effect on January 1, 2017, and as seen previously in @fig-registration-timeline, the first year of the law saw the greatest total number of registrations.
-In our third empirical expectation, we propose that these early registrants under the new law were both less of a threat to regime stability and a higher priority for bureaucratic processing, and thus should be registered in more provinces and have more geographic flexibility throughout the country.
-However, the results of our model support the *reverse* of this expectation.
-@fig-timing-preds(a) once again shows the predicted posterior outcomes for 1,000 simulated INGOs across a range of time since January 2017.
-Organizations that registered in the first year are predicted to work in all provinces 41--46% of the time, and are predicted to work in two or more provinces 34--39% of the time.
+In our third empirical expectation, we propose that these early registrants were both less of a threat to regime stability and a higher priority for bureaucratic processing and thus should be registered in more provinces.
+However, the results of our model support the opposite of this expectation.
+@fig-timing-preds(a) presents the predicted posterior outcomes for 1,000 simulated INGOs over time.
+Organizations that registered in the first year have a 41--46% probability of working in all provinces and are predicted to work in two or more provinces 34--39% of the time.
 These early INGOs are the most likely to be registered in only one province and are predicted to do so 17--23% of the time.
-After the initial wave of registrations in 2017, the likelihood of nationwide reach steadily increases and replaces both the probability of a single province or a partial range of provinces.
-By the end of 2021---5 years after the ONGO Law took effect---the probability of national-level registration increases to 55--61% while the probability of working in a range of provinces increases to predicted to work in two or more provinces increase to 27--32%.
-These late INGOs are the least likely to be registered in only one province and are predicted to do so only 17--22% of the time.
-@fig-timing-preds(b) demonstrates the same results with the posterior distribution of the expected count of provinces over five years since 2017.
+After 2017, the likelihood of nationwide reach steadily increases and replaces both the probability of a single province or a partial range of provinces.
+By the end of 2021 the probability of national-level registration increases to 55--61% while the probability of working in a range of provinces increases to predicted to work in two or more provinces increase to 27--32%.
+These later INGOs are the least likely to be registered in only one province.
+@fig-timing-preds(b) demonstrates the expected count of provinces over five years since 2017.
 INGOs that register early are predicted to work in 17--22 provinces, while those that wait until 2021 are predicted to work in 21--28.
@@
       glue(
-        "Filled areas depict 50 posterior samples of the outcome category probabilities,",
-        "so the fuzziness represents the uncertainty in category boundaries; ",
+        "Filled areas depict 50 posterior samples of the outcome category probabilities;",
+        "the fuzziness represents the uncertainty in category boundaries; ",
         .sep = " "
@@
 Political institutions are central to authoritarian stability as autocrats work to co-opt and balance institutional challenges to their regime.
-Autocrats treat civil society—both domestic and international—as yet another actor in their stability-seeking calculus.
+Autocrats treat civil society---both domestic and international---as yet another actor in their stability-seeking calculus.
 The ongoing phenomenon of closing civic space, where governments worldwide continue to impose repressive regulations on civil society, can be seen as a strategy for stabilizing authoritarian rule [@DeMattee:2019; @CarothersBrechenmacher:2014; @Heiss:2019].
@@
 By focusing on a specific law in one country, our work provides rich empirical illustrations of the mechanics of authoritarian administrative crackdown.
-We find that INGOs that work on issues that are less threatening and more aligned with regime preferences—such as arts & culture INGOs, industry associations, and scientific organizations—are registered in more provinces and thus enjoy a greater degree of operational space, while organizations that pose a potential threat—like education INGOs—are far more limited geographically.
+We find that INGOs that work on issues that are less threatening and more aligned with regime preferences---such as arts & culture INGOs, industry associations, and scientific organizations—are registered in more provinces and thus enjoy a greater degree of operational space, while organizations that pose a potential threat---like education INGOs---are far more limited geographically.
 Our case study finds similar results.
@@
 We cannot make comparisons with INGOs that left the country prior to 2017 or INGOs that have explicitly chosen to not work in China.
-This is not an issue specific to China—analyzing the international nonprofit sector of any country that has passed similar laws will raise similar issues of selection bias.
+This is not an issue specific to China---analyzing the international nonprofit sector of any country that has passed similar laws will raise similar issues of selection bias.
 The Chinese context provides one possible way forward: future research can further explore relationship between INGOs and regime preferences by comparing characteristics of INGOs that register as ROs or undertake temporary activities using already-available administrative data.
@@
 We have illustrated how the interpretation and implementation of one INGO law has reshaped the role of international civil society, leading to a preponderance of regime-friendly NGOs, many of which have realigned their programming with government preferences.
-It is likely that a similar dynamic plays out in other countries—regimes legislate civil society broadly and enforce those laws specifically and individually.
+It is likely that a similar dynamic plays out in other countries---regimes legislate civil society broadly and enforce those laws specifically and individually.
 Future research can analyze the determinants of INGO operational space in other authoritarian states, which can help INGOs facing legal crackdown abroad strengthen their organizational flexibility in the face of restricted legal environments.

### 2023-12-06 manuscript/manuscript.qmd
lol use already-existing province lookup table

@@
 provinces <- ongo_mapdata |> 
+  drop_na(province_code) |> 
   st_drop_geometry() |> 
   mutate(rank = dense_rank(-ro_count)) |> 
-  mutate(list_name = janitor::make_clean_names(province_en_short)) |> 
+  mutate(list_name = janitor::make_clean_names(province_en)) |> 
   split(~ list_name)

### 2023-12-06 R/funs_data.R

@@ -65,7 +65,7 @@ province_cn_to_en <- function() {
     "天津",      "Tianjin",        "TJ",
     "重庆",      "Chongqing",      "CQ",
     "河北",      "Hebei",          "HE",
-    "山西",      "Beijing",        "SX",
+    "山西",      "Shanxi",         "SX",
     "内蒙",      "Inner Mongolia", "NM",
     "辽宁",      "Liaoning",       "LN",
     "吉林",      "Jilin",          "JL",
@@ -98,51 +98,9 @@ province_cn_to_en <- function() {
 }
 
 
-clean_map_data <- function(ongo) {
+clean_map_data <- function(ongo, province_name) {
   suppressPackageStartupMessages(library(sf))
   suppressPackageStartupMessages(library(mapchina))
-  
-  # Manual lookup table for Andrew :)
-  provinces_zh2en <- tribble(
-    ~Name_Province, ~province_en,
-    "上海市", "Shanghai",
-    "云南省", "Yunnan Province",
-    "内蒙古自治区", "Inner Mongolia Autonomous Region",
-    "北京市", "Beijing",
-    "台湾省", "Taiwan Province",
-    "吉林省", "Jilin Province",
-    "四川省", "Sichuan Province",
-    "天津市", "Tianjin City",
-    "宁夏回族自治区", "Ningxia Hui Autonomous Region",
-    "安徽省", "Anhui Province",
-    "山东省", "Shandong Province",
-    "山西省", "Shanxi Province",
-    "广东省", "Guangdong Province",
-    "广西壮族自治区", "Guangxi Zhuang Autonomous Region",
-    "新疆维吾尔自治区", "Xinjiang Uygur Autonomous Region",
-    "江苏省", "Jiangsu Province",
-    "江西省", "Jiangxi Province",
-    "河北省", "Hebei Province",
-    "河南省", "Henan Province",
-    "浙江省", "Zhejiang Province",
-    "海南省", "Hainan",
-    "湖北省", "Hubei Province",
-    "湖南省", "Hunan Province",
-    "澳门特别行政区", "Macao Special Administrative Region",
-    "甘肃省", "Gansu Province",
-    "福建省", "Fujian Province",
-    "西藏自治区", "Tibet Autonomous Region",
-    "贵州省", "Guizhou Province",
-    "辽宁省", "Liaoning Province",
-    "重庆市", "Chongqing",
-    "陕西省", "Shaanxi Province",
-    "青海省", "Qinghai Province",
[…]

### 2023-12-06 _targets.R

@@ -62,7 +62,7 @@ list(
     clean_ongo_data(ongo_manual_file, chinafile_clean, province_name)
   ),
   tar_target(ongo_wide, widen_data(ongo)),
-  tar_target(ongo_mapdata, clean_map_data(ongo)),
+  tar_target(ongo_mapdata, clean_map_data(ongo, province_name)),
   tar_target(issue_indicator_lookup, make_issue_indicator_lookup(ongo)),
   
   ## Models ----

### 2023-12-06 manuscript/manuscript.qmd
Finish adding inline chunks for issue area results

@@
   count(local_connect) |> 
-  mutate(prop = n / sum(n)) |> 
-  mutate(prop_nice = label_percent(accuracy = 1)(prop)) |> 
+  mutate(
+    prop = n / sum(n),
+    prop_nice = label_percent(accuracy = 1)(prop)
+  ) |> 
   mutate(local_connect = janitor::make_clean_names(local_connect)) |> 
@@
   split(~ work_field_code1)
+
+isssue_province_counts <- epreds_issue |> 
+  group_by(issue_area) |> 
+  mutate(count = prop_to_provinces(.epred)) |> 
+  median_qi(count) |> 
+  mutate(across(c(.lower, .upper), list(whole = ~round(., 0)))) |> 
+  mutate(count_median = round(count, 0)) |> 
+  mutate(range = glue("{.lower_whole}–{.upper_whole}")) |> 
+  split(~ issue_area)
+
+ros_2017 <- ongo |> 
+  count(pre_2018 = registration_date < ymd("2018-01-01")) |> 
+  mutate(
+    prop = n / sum(n),
+    prop_nice = label_percent(accuracy = 1)(prop)
+  ) |> 
+  filter(pre_2018 == TRUE) |> 
+  as.list()
 ```
@@
 There is great variance in registration timing, since there was a brief grace period for INGOs to seek legal presence after the law took effect [@Shieh:2018].
-Nearly half of all ROs---48%---registered in 2017, and the count of new registrations gradually declined after the initial first-year wave (see @fig-registration-timeline).
+Nearly half of all ROs---`r ros_2017$prop_nice`---registered in 2017, and the count of new registrations gradually declined after the initial first-year wave (see @fig-registration-timeline).
 This is largely because both INGOs and the regulators needed some transitional time to explore the specific application of the law as large ambiguity was left when the law was passed.
@@
 @fig-issue-preds(a) presents a summary of predicted posterior outcomes for 1,000 hypothetical INGOs, varying each issue area and holding all other variables at their mean or modal values.
+
 Several notable trends emerge from the model results.
@@
 @fig-issue-preds(b) shows the continuous posterior distribution of the average number of provinces INGOs are expected to be registered in across all types of issue areas, but accounting for the 1- and 32-only provinces simultaneously.
-We can see a similar trend---arts and culture INGOs are predicted to work in 28--30 provinces on average, while education INGOs are only predicted to work in 12--20.
-All other issues range between 20--28 provinces.
+We can see a similar trend---arts and culture INGOs are predicted to work in `r isssue_province_counts$arts_and_culture$range` provinces on average, while education INGOs are only predicted to work in `r isssue_province_counts$education$range`.
+All other issues range between 15--25 provinces.
 

### 2023-12-06 manuscript/manuscript.qmd
Shrink local connections section

--- 2023-12-06 manuscript/manuscript.qmd
@@
 library(glue)
+library(janitor)
 library(gt)
@@
   ) |> 
-  mutate(open = janitor::make_clean_names(open)) |> 
+  mutate(open = make_clean_names(open)) |> 
   split(~open)
@@
 
-```{r calc-summaries}
+```{r calc-provinces}
 provinces <- ongo_mapdata |> 
+  drop_na(province_code) |> 
   st_drop_geometry() |> 
   mutate(rank = dense_rank(-ro_count)) |> 
-  mutate(list_name = janitor::make_clean_names(province_en_short)) |> 
+  mutate(list_name = make_clean_names(province_en)) |> 
   split(~ list_name)
@@
   keep(~nrow(.x) > 0)
-
-loc <- ongo |> 
-  count(local_connect) |> 
-  mutate(prop = n / sum(n)) |> 
-  mutate(prop_nice = label_percent(accuracy = 1)(prop)) |> 
-  mutate(local_connect = janitor::make_clean_names(local_connect)) |> 
-  split(~ local_connect)
-
+```
+
+```{r calc-issues}
 # MAYBE: Use issue_area instead of work_field_code
@@
   mutate(prop_nice = label_percent(accuracy = 1)(prop)) |> 
-  mutate(work_field_code1 = janitor::make_clean_names(work_field_code1)) |> 
+  mutate(work_field_code1 = make_clean_names(work_field_code1)) |> 
   split(~ work_field_code1)
-```
-
-```{r calc-preds}
-# Issue area
+
 preds_issue_plot_order <- preds_issue_plot |> 
@@
   group_by(outcome) |> 
-  mutate(issue_area_nice = janitor::make_clean_names(issue_area_nice)) |> 
+  mutate(issue_area_nice = make_clean_names(issue_area_nice)) |> 
   group_by(issue_area_nice) |> 
-  mutate(outcome = janitor::make_clean_names(outcome)) |> 
+  mutate(outcome = make_clean_names(outcome)) |> 
   ungroup() |> 
@@
 
-# Local connections
+c_issue <- epreds_issue |> 
+  group_by(issue_area) |> 
+  mutate(count = prop_to_provinces(.epred)) |> 
+  median_qi(count) |> 
+  mutate(across(c(.lower, .upper), list(whole = ~round(., 0)))) |> 
+  mutate(count_median = round(count, 0)) |> 
+  mutate(range = glue("{.lower_whole}–{.upper_whole}")) |> 
+  split(~ issue_area)
+```
+
+```{r calc-local-connections}
+loc <- ongo |> 
+  count(local_connect) |> 
+  mutate(
+    prop = n / sum(n),
+    prop_nice = label_percent(accuracy = 1)(prop)
+  ) |> 
+  mutate(local_connect = make_clean_names(local_connect)) |> 
+  split(~ local_connect)
+
 preds_local_text <- preds_local_plot |> 
@@
   ))
+
+p_loc <- preds_local_text |> 
+  group_by(outcome) |> 
+  mutate(local_connect = make_clean_names(local_connect)) |> 
+  group_by(local_connect) |> 
+  mutate(outcome = make_clean_names(outcome)) |> 
+  ungroup() |> 
+  split(~ local_connect + outcome)
+
+c_local <- epreds_local |> 
+  mutate(local_connect = case_match(local_connect, TRUE ~ "true", FALSE ~ "false")) |> 
+  group_by(local_connect) |> 
+  mutate(count = prop_to_provinces(.epred)) |> 
+  median_qi(count) |> 
+  mutate(across(c(.lower, .upper), list(whole = ~round(., 0)))) |> 
+  mutate(count_median = round(count, 0)) |> 
+  mutate(range = glue("{.lower_whole}–{.upper_whole}")) |> 
+  split(~ local_connect)
+```
+
+```{r calc-timing}
+ros_2017 <- ongo |> 
+  count(pre_2018 = registration_date < ymd("2018-01-01")) |> 
+  mutate(
+    prop = n / sum(n),
+    prop_nice = label_percent(accuracy = 1)(prop)
+  ) |> 
+  filter(pre_2018 == TRUE) |> 
+  as.list()
 ```
@@
 Below, we provide a brief overview of China's 2016 ONGO Law and the different regulatory mechanisms it provides for INGOs to obtain legal access to the country.
-We then synthesize existing research on authoritarian regulation of INGOs and the differential application of these laws based on regime preferences and organizational characteristics, and propose a set of empirical expectations based on this literature.
+We then synthesize existing research on authoritarian regulation of INGOs and the differential application of these laws based on regime preferences and organizational characteristics, and propose a set of theoretical expectations based on this literature.
 We test these expectations with a mixed methods research design, combining Bayesian analysis of administrative data from all `r nrow(ongo)` formally registered INGOs with a comparative case study of Greenpeace and The Nature Conservancy, two environmental INGOs that took different approaches to operating in China after 2017.
@@
 Next, we explore the data in more depth by generating and analyzing posterior predictions from our model.
-Following our first empirical expectation, we predict that INGOs working on less contentious issues should be registered in more provinces and thus have more geographic flexibility.
+Following our first theoretical expectation, we predict that INGOs working on less contentious issues should be registered in more provinces and thus have more geographic flexibility.
 We take advantage of the simultaneous continuous and discrete features of ordered Beta regression and see how often an INGO in each issue area is predicted to work in a single province, across all provinces, or some number in between.
 @fig-issue-preds(a) presents a summary of predicted posterior outcomes for 1,000 hypothetical INGOs, varying each issue area and holding all other variables at their mean or modal values.
+
 Several notable trends emerge from the model results.
@@
 @fig-issue-preds(b) shows the continuous posterior distribution of the average number of provinces INGOs are expected to be registered in across all types of issue areas, but accounting for the 1- and 32-only provinces simultaneously.
-We can see a similar trend---arts and culture INGOs are predicted to work in 28--30 provinces on average, while education INGOs are only predicted to work in 12--20.
-All other issues range between 20--28 provinces.
+We can see a similar trend---arts and culture INGOs are predicted to work in `r c_issue$arts_and_culture$range` provinces on average, while education INGOs are only predicted to work in `r c_issue$education$range`.
+All other issues range between 15--25 provinces.
 
@@
 No INGOs engaged in contentious issues like human rights advocacy have successfully registered in China, but there is some slight variation in the level of contention even among organizations working on less contentious issues like humanitarian assistance, health, and the environment.
+INGOs that survived the registration thresholds are those already "censored" and deemed to be safe and non-contentious.
+This can help explain why some seemingly more contentious issue areas such as environmental INGOs enjoy relatively more operational space.
+Chinese authorities can see the work of environmental INGOs as providing benefits such as political stability and "selectively encourage low risk groups and selectively channel higher risk groups into permitted areas" [@Plantan:2022, 504].
+
 Education is particularly notable as the least flexible and most geographically restricted subsector.
@@
 Foreign NGOs' working methods also affect Chinese NGOs" [@Wang:2012, 110].
-Education can thus be seen as one of the more contentious issues allowed under the ONGO law, and thus more closely regulated and restricted.
-
-Additionally, the INGOs that survived the registration thresholds are those already "censored" to be relatively safe and non-contentious.
-This can help explain why some seemingly more contentious issue areas, e.g., environmental INGOs enjoy relatively more operational space.
-According to [@Plantan:2022], Chinese authorities can see the work of environmental INGOs as providing benefits such as political stability and "selectively encourage low risk groups and selectively channel higher risk groups into permitted areas".
-We will further this discussion with the case analysis of two environmental INGOs later.
+Education is therefore one of the more contentious issues allowed under the ONGO law, and thus more closely regulated and restricted.
 
@@
 
-In our second empirical expectation, we posit that since INGOs that seek out local connections and that are focused on more local China-specific issues, those organizations should be registered in fewer provinces.
+In our second theoretical expectation, we posit that since INGOs that seek out local connections and that are focused on more local China-specific issues, those organizations should be registered in fewer provinces.
 The results from our model confirm this expectation.
-@fig-local-preds(a) shows the distribution of predicted posterior outcomes for 1,000 hypothetical INGOs.
-Organizations without local connections are predicted to work nationally across all provinces nearly half of the time (with a 95% credible interval of 46--51%), and are predicted to work in two or more provinces 32--37% of the time.
-These organizations with no local connections or local programmatic focus are only predicted to work in a single province 15--19% of the time.
-In contrast, INGOs *with* local connections are far more likely to only work in one province (32--38%), or only work in a handful of provinces (36--41%).
-For these locally-focused organizations, the least common prediction is to work nationally, with only a 23--29% probability.
+@fig-local-preds(a) shows that organizations without local connections are predicted to work nationally across all provinces nearly half of the time (with a 95% credible interval of `r p_loc$no_local_connections.all_32_provinces$prop_ci_nice`), with a `r p_loc$no_local_connections.between_1_32_provinces$prop_ci_nice` probability of working in two or more provinces.
+INGOs without local connections only have a `r p_loc$no_local_connections.only_1_province$prop_ci_nice` probability of working in a single province.
+In contrast, INGOs with local connections are far more likely to only work in one province (`r p_loc$local_connections.only_1_province$prop_ci_nice`), or only work in a handful of provinces (`r p_loc$local_connections.between_1_32_provinces$prop_ci_nice`).
+For these locally-focused organizations, the least common prediction is to work nationally, with only a `r p_loc$local_connections.all_32_provinces$prop_ci_nice` probability.
 @fig-local-preds(b) shows the posterior distribution of the average number of provinces INGOs are expected to be registered in, conditional on their local connections.
-The same relationship holds---an INGO without local connections is predicted to work in 19--24 provinces on average, while an organization with local connections is only predicted to work in 8--17.
+The same relationship holds---an INGO without local connections is predicted to work in `r c_local$false$range` provinces on average, while an organization with local connections is only predicted to work in `r c_local$true$range`.
 
@@
 
-International NGOs with locally focused missions and connections with local provincial officials are thus far more likely to purposely limit their activities to specific provinces, while organizations with broader non-local missions have a larger geographic reach.
+International NGOs with locally focused missions and connections with provincial officials are thus far more likely to purposely limit their activities to specific provinces, while organizations with broader missions have a larger geographic reach.
 While we cannot precisely tell which direction the causal story works with this phenomenon, we can make some reasonable speculations.
@@
 It is also likely, given the high probability of national reach, that organizations without local connections purposely do not spend the time and effort to cultivate those relationships, as it is not necessary to operate across many provinces.
-A rival explanation that having local connections reduces an organization's flexibility does not seem warranted.
-Although INGOs with local connections do have a more limited geographic scope, INGOs appear to purposely limit the number of provinces they work in in order to focus more on their local work.
+A rival explanation that having local connections reduces an organization's operational space does not seem warranted—although INGOs with local connections do have a more limited geographic scope, organizations appear to purposely limit the number of provinces they work in in order to focus more on their local work.
 
@@
 
-In our third empirical expectation, we propose that these early registrants were both less of a threat to regime stability and a higher priority for bureaucratic processing and thus should be registered in more provinces.
+In our third theoretical expectation, we propose that these early registrants were both less of a threat to regime stability and a higher priority for bureaucratic processing and thus should be registered in more provinces.
 However, the results of our model support the opposite of this expectation.

### 2023-12-06 manuscript/manuscript.qmd
Shrink timing section

@@
 p_issue <- preds_issue_text |> 
-  group_by(outcome) |> 
-  mutate(issue_area_nice = make_clean_names(issue_area_nice)) |> 
-  group_by(issue_area_nice) |> 
-  mutate(outcome = make_clean_names(outcome)) |> 
+  mutate(issue_area_nice = make_clean_names(issue_area_nice, allow_dupes = TRUE)) |> 
+  mutate(outcome = make_clean_names(outcome, allow_dupes = TRUE)) |> 
   ungroup() |> 
@@
 p_loc <- preds_local_text |> 
-  group_by(outcome) |> 
-  mutate(local_connect = make_clean_names(local_connect)) |> 
-  group_by(local_connect) |> 
-  mutate(outcome = make_clean_names(outcome)) |> 
+  mutate(local_connect = make_clean_names(local_connect, allow_dupes = TRUE)) |> 
+  mutate(outcome = make_clean_names(outcome, allow_dupes = TRUE)) |> 
   ungroup() |> 
@@
   as.list()
+
+p_timing <- preds_timing_plot |> 
+  filter(years_since_law %in% c(2017, 2022)) |> 
+  group_by(years_since_law, outcome) |> 
+  summarize(median_prop = median_qi(prop)) |> 
+  unnest(median_prop) |> 
+  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
+  mutate(prop_ci_nice = glue::glue(
+    "{ymin}–{ymax}",
+    ymin = label_number(accuracy = 1, scale = 100)(ymin),
+    ymax = label_percent(accuracy = 1)(ymax)
+  )) |> 
+  group_by(outcome) |> 
+  mutate(years_since_law = make_clean_names(years_since_law)) |> 
+  group_by(years_since_law) |> 
+  mutate(outcome = make_clean_names(outcome)) |> 
+  ungroup() |> 
+  split(~ years_since_law + outcome)
+
+c_timing <- epreds_timing |> 
+  filter(years_since_law %in% c(2017, 2022)) |> 
+  group_by(years_since_law) |> 
+  mutate(count = prop_to_provinces(.epred)) |> 
+  median_qi(count) |> 
+  mutate(across(c(.lower, .upper), list(whole = ~round(., 0)))) |> 
+  mutate(count_median = round(count, 0)) |> 
+  mutate(range = glue("{.lower_whole}–{.upper_whole}")) |> 
+  mutate(years_since_law = make_clean_names(years_since_law)) |> 
+  split(~ years_since_law)
+
+c_timing_local <- epreds_timing_local |> 
+  filter(years_since_law %in% c(2017, 2022)) |> 
+  mutate(local_connect = case_match(local_connect, TRUE ~ "true", FALSE ~ "false")) |> 
+  group_by(local_connect, years_since_law) |> 
+  mutate(count = prop_to_provinces(.epred)) |> 
+  median_qi(count) |> 
+  mutate(across(c(.lower, .upper), list(whole = ~round(., 0)))) |> 
+  mutate(count_median = round(count, 0)) |> 
+  mutate(range = glue("{.lower_whole}–{.upper_whole}")) |> 
+  mutate(years_since_law = make_clean_names(years_since_law, allow_dupes = TRUE)) |> 
+  split(~ years_since_law + local_connect)
 ```
@@
 # and https://ikashnitsky.phd/2023/map-borders/
-interior_borders <- st_intersection(ongo_mapdata) %>% 
+interior_borders <- st_intersection(ongo_mapdata) |>
   filter(n.overlaps > 1) |> 
@@
 
-International NGOs with locally focused missions and connections with provincial officials are thus far more likely to purposely limit their activities to specific provinces, while organizations with broader missions have a larger geographic reach.
+INGOs with locally focused missions and connections with provincial officials are thus far more likely to purposely limit their activities to specific provinces, while organizations with broader missions have a larger geographic reach.
 While we cannot precisely tell which direction the causal story works with this phenomenon, we can make some reasonable speculations.
@@
 
-In our third theoretical expectation, we propose that these early registrants were both less of a threat to regime stability and a higher priority for bureaucratic processing and thus should be registered in more provinces.
+In our third theoretical expectation, we propose that early registrants were both less of a threat to regime stability and a higher priority for bureaucratic processing and thus should be registered in more provinces.
 However, the results of our model support the opposite of this expectation.
-@fig-timing-preds(a) presents the predicted posterior outcomes for 1,000 simulated INGOs over time.
-Organizations that registered in the first year have a 41--46% probability of working in all provinces and are predicted to work in two or more provinces 34--39% of the time.
-These early INGOs are the most likely to be registered in only one province and are predicted to do so 17--23% of the time.
+In @fig-timing-preds(a) organizations that registered in the first year have a `r p_timing$x2017.all_32_provinces$prop_ci_nice` probability of working in all provinces and are predicted to work in two or more provinces `r p_timing$x2017.between_1_32_provinces$prop_ci_nice` of the time.
+These early INGOs are the most likely to be registered in only one province and are predicted to do so `r p_timing$x2017.only_1_province$prop_ci_nice` of the time.
 After 2017, the likelihood of nationwide reach steadily increases and replaces both the probability of a single province or a partial range of provinces.
-By the end of 2021 the probability of national-level registration increases to 55--61% while the probability of working in a range of provinces increases to predicted to work in two or more provinces increase to 27--32%.
-These later INGOs are the least likely to be registered in only one province.
+By the end of 2021 the probability of national-level registration increases to `r p_timing$x2022.all_32_provinces$prop_ci_nice` while the probability of working in a range of provinces increases to predicted to work in two or more provinces remains around `r p_timing$x2022.between_1_32_provinces$prop_ci_nice`.
+These later INGOs are the least likely to be registered in only one province, with a probability of `r p_timing$x2022.only_1_province$prop_ci_nice`.
 @fig-timing-preds(b) demonstrates the expected count of provinces over five years since 2017.
-INGOs that register early are predicted to work in 17--22 provinces, while those that wait until 2021 are predicted to work in 21--28.
+INGOs that register early are predicted to work in `r c_timing$x2017$range` provinces on average, while those that wait until 2021 are predicted to work in a far more uncertain `r c_timing$x2022$range`.
 
@@
 
-We lack sufficient theory or data to explain why this trend goes against our expectations, but we can again make reasonable speculations.
-As we saw previously with INGOs and local connections, organizations appear to strategically seek out the best avenues and methods for registering [@Jia:2017a].
+We lack sufficient theory to explain why this trend goes against our expectations, but we can again make reasonable speculations.
+As we saw previously with INGOs and local connections, organizations appear to strategically seek out the best avenues for registering [@Jia:2017a].
 Organizations that participated in the initial wave of registrations in 2017 likely had closer connections with local officials and were able to speed through the bureaucratic process registration more easily.
 As a preliminary test of this speculation, we rerun our main model with an interaction between years since registration and local connections to see how the effect of local connections changes over time.
-As seen in @fig-timing-local, early registrants in 2017 without local connections are more likely to have a larger geographic reach, registering in an average of 19--23 provinces, while their locally-focused counterparts are only expected to register in an average of 7--16 provinces.
-Accordingly, it may be that organizations with local connections are more likely to register early because of their pre-existing bureaucratic relationships, while organizations with a larger national reach take longer to undertake the registration process and thus register later.
-Another possible explanation is interpreting earlier timing in registration as more eager to register as discussed in the measurement section.
-INGOs that self-perceive as more contentious would be more nervous about the legal consequences of not being able to register and thus be more eager to seek registration earlier [@ChinaPhilanthropyReserchInstitute:2018].
-Compared with their more "rest-assured" peers, INGOs seeking to register earlier are more likely to have reduced operational space.
+As seen in @fig-timing-local, early registrants in 2017 without local connections are more likely to have a larger geographic reach, registering in an average of `r c_timing_local$x2017.false$range` provinces, while their locally-focused counterparts are only expected to register in an average of `r c_timing_local$x2017.true$range` provinces.
+Accordingly, it may be that INGOs with local connections are more likely to register early because of their pre-existing bureaucratic relationships, while organizations with a larger national reach take longer to undertake the registration process and thus register later.
+Another possible explanation could be that earlier registration signals greater eagerness to reduce the uncertainty surrounding organizational legal status.
+INGOs that perceive themselves as more contentious may be more nervous about the legal consequences of not being able to register and thus be more willing to seek registration earlier [@ChinaPhilanthropyReserchInstitute:2018].
+Compared with their safer, less contentious peers, INGOs seeking to register earlier are more likely to have reduced operational space.
 To understand the underlying mechanism with registration timing, further research is warranted.

### 2023-12-06 manuscript/manuscript.qmd
Shrink conclusion

@@
 First, we expand work that uses institutional approaches to understanding civil society regulations, which argues that states strategically regulate INGOs to maintain regime stability, choosing forms of regulation and repression that minimize threats to internal political stability [@Chaudhry:2022; @DeMattee:2018; @DeMattee:2019; @Heiss:2019].
-Second, we explore how authoritarian civil society regulations act as policy tools that regimes can leverage to shift INGO behavior in their favor and how these laws reshape and tame organizational strategies [@Li:2020; @WuNie:2021; @LianMurdie:2023].
+Second, we explore how authoritarian civil society regulations act as policy tools that regimes can leverage to shift INGO behavior in their favor and how these laws reshape and tame organizational strategies [@Li:2020; @LianMurdie:2023].
 Third, we explore how these regulations lead to differentiated application of the law depending on organizational characteristics.
@@
 A rich literature in comparative politics explores how authoritarian regimes counterintuitively use democratic institutions for their own benefit and survival [@Kendall-TaylorFrantz:2014a; @GandhiPrzeworski:2007].
-Authoritarian states hold elections, allow opposition parties in the legislature, and set executive term limits [@LevitskyWay:2010; @Meng:2020], but use these democratic-appearing institutions to hedge against possible threats to regime stability.
+Authoritarian states hold elections, allow opposition parties in the legislature, and set executive term limits [@Meng:2020], but use these democratic-appearing institutions to hedge against possible threats to regime stability.
 Quasi-democratic institutions are allowed, but only in ways that bolster the government's stability, and these institutions are kept weak and "dependent on the regime to ensure that they do not develop any real power or autonomy" [@FrantzEzrow:2011, 7].
@@
 However, the findings are still instructive.
-We have illustrated how the interpretation and implementation of one INGO law has reshaped the role of international civil society, leading to a preponderance of regime-friendly NGOs, many of which have realigned their programming with government preferences.
-It is likely that a similar dynamic plays out in other countries---regimes legislate civil society broadly and enforce those laws specifically and individually.
-Future research can analyze the determinants of INGO operational space in other authoritarian states, which can help INGOs facing legal crackdown abroad strengthen their organizational flexibility in the face of restricted legal environments.
+We have illustrated how the implementation of one INGO law has reshaped the role of international civil society, leading to a preponderance of regime-friendly NGOs, many of which have realigned their programming with government preferences.
+It is likely that a similar dynamic plays out in other countries---regimes legislate civil society broadly and enforce those laws specifically.
+Future research might analyze the determinants of INGO operational space in other authoritarian states, which can help INGOs facing legal crackdown abroad strengthen their organizational flexibility in the face of legal restrictions.
 

### 2023-12-07 manuscript/manuscript.qmd
Shrink/edit case study section

@@
 No INGOs engaged in contentious issues like human rights advocacy have successfully registered in China, but there is some slight variation in the level of contention even among organizations working on less contentious issues like humanitarian assistance, health, and the environment.
-INGOs that survived the registration thresholds are those already "censored" and deemed to be safe and non-contentious.
-This can help explain why some seemingly more contentious issue areas such as environmental INGOs enjoy relatively more operational space.
-Chinese authorities can see the work of environmental INGOs as providing benefits such as political stability and "selectively encourage low risk groups and selectively channel higher risk groups into permitted areas" [@Plantan:2022, 504].
-
 Education is particularly notable as the least flexible and most geographically restricted subsector.
@@
 
-We also conducted the qualitative study of two selected cases of INGOs in China to further understand the patterns revealed in the quantitative modeling and to examine a more comprehensive picture of how the operations of INGOs have been impacted by the ONGO Law.
-As explained, the registration documentation data enables us to analyze how the operational space is associated with issue areas and other factors for those INGOs that could successfully register.
-However, for INGOs that could not get registered but try to maintain their legal presence in China, a typical choice would be constantly filing temporary activities [@Corsetti:2019].
-So, we purposefully selected two environmental INGOs with different registration status to conduct a comparative analysis.
-One of them, the Nature Conservancy (“TNC”), successfully registered a RO under the ONGO Law, while the other INGO, Greenpeace has been filing temporary activities one after another since 2017 to continue carrying out programs in China.
-We use secondary data including public interviews (previously conducted by one of the authors) and their websites, in addition to official ONGO Law records of ROs and temporary activities to conduct the case studies.
-
-TNC and Greenpeace are both well-known INGOs working in the environmental issue area.
-Their headquarters are based in western countries and have offices around the world.
-They started to have long-standing offices in Beijing around the turn of the century, with TNC in 1998 and Greenpeace in 2001.
-Despite these similarities, the two INGOs had quite different experiences to sustain their legal presence in China after the ONGO Law took effect.
-According to records by the MPS, TNC’s RO was registered on May 19, 2017, with the National Forestry and Grassland Administration as their PSU.
-The RO in Beijing is eligible to operate in 27 provinces.
-Comparatively, Greenpeace has not registered any RO as of December 1, 2023.
-Instead, they have filed 67 temporary activities, almost going through the filing process 10 times each year.
-
-There are various drawbacks to having to constantly file temporary activities.
-First would be high administrative costs.
-Since the filing of temporary activities needs to be submitted by INGOs’ Chinese partners, it would mean discussing and securing the partnerships 67 times, mostly with different organizations.
-Moreover, this model also imposes high uncertainty to the operation of INGOs.
-There is no guarantee whether the next Chinese partner would agree to collaborate and file the documentation for them.
-And it is impossible to run longer-term projects, given all temporary activities cannot last longer than a year.
-Finally, temporary activities would be programs Chinese partners feel comfortable to collaborate in, i.e., safe activities with little political and administrative risks.
-So there is less flexibility in the kinds of work an INGO can do with temporary activities.
-
-What factors could have contributed to the contrasting experiences of TNC and Greenpeace under the ONGO Law?
-After analyzing the data, the working approach and relationship with the government emerged as pivotal differences between the two INGOs, which fits existing discussions on the differential treatment of INGOs based on their relationship with the authority [@Plantan:2022].
-In a public interview with TNC’s RO in China about their registration experience, the chief representative stated TNC’s working approach in China has been “science-based”, using “non-confrontational, collaborative approach in working closely with governments, the business community and others” [@ChinaPhilanthropyReserchInstitute:2018a].
-Over the years, they have provided technical support for the central government and local governments like the Yunnan and Zhejiang Provinces to build national parks and nature reserve areas and helped drafted such documents as the China Biodiversity Conservation Strategy and Action Plan (2011-2030).
-Using the non-confrontational working model and establishing long partnerships with the government enabled TNC to secure the consent of a national governmental agency in corresponding issue area to be their PSU, and thus successfully got registered and authorized to operate in a larger number of provinces.
-In contrast, Greenpeace states in their mission that they work as “independent campaigning organizations that use peaceful protest and creative confrontation to expose global environmental problems”.
-Their description of the work in China also uses such key words as “brings change”, “non-violent direct action”, and “impartiality and independence”.
-One project Greenpeace shares on their website was the exposure of the damages the company Sinar Mas Group's did in southwest Yunnan back in 2004.
-They conducted three rounds of  independent investigations and later revealed that the multinational paper industry company used reforestation as a cover while actually logging Yunnan's natural forests.
-Although this confrontation was not with the government, it showcases Greenpeace’s investigative, watchdog like work stance.
-To the authority, it would mean less predictable and manageable.
+The results from our model provide useful insight into the operational space of INGOs that have been able to formally register.
+These organizations have been pre-screened and deemed to be safe and non-contentious.
+This can help explain why some seemingly more contentious issue areas such as environmental INGOs enjoy relatively more operational space (see @fig-issue-preds).
+Chinese authorities can benefit politically from the of environmental INGOs and "selectively encourage low risk groups and selectively channel higher risk groups into permitted areas" [@Plantan:2022, 504].
+Using our data, however, we are unable to make comparisons with already-vetted INGOs and other potentially more contentious organizations, which limits our analysis of the determinants of operational space.
+To address this, we compare the cases of two environmental INGOs: (1) The Nature Conservancy (TNC), which successfully registered as RO under the ONGO Law, and (2) Greenpeace, which has filed dozens of sequential temporary activities.
+
+TNC and Greenpeace are both well-known environmental INGOs.
+Both are based in Western countries and both have offices around the world.
+They each began working in China around the turn of the century, with TNC in establishing an office in Beijing in 1998 and Greenpeace in 2001.
+Despite these similarities, the two INGOs have had quite different experiences to sustain their legal presence in China after the ONGO Law took effect.
+TNC obtained RO status in May 2017, partnering with the National Forestry and Grassland Administration as their PSU, and receiving authorization to work in 27 provinces.
+In contrast, Greenpeace has not received RO status and has instead filed 67 temporary activities, filing new documentation nearly ten times each year.
+
+There are several drawbacks to having to constantly file temporary activities [@Corsetti:2019], resulting in far more limited INGO operational space than under RO regulations (recall @fig-ro-ta-pathways).
+Securing a new partnership with a Chinese organization for each activity and co-filing the requisite paperwork imposes substantial administrative costs.
+This approach also creates high uncertainty, since there is no guarantee that a current partner organization would agree to repeat their supervisory role for the next project.
+Moreover, INGO programming has an inherent short-term focus, given that temporary activities cannot last longer than a year.
+Finally, temporary activities need to focus on safe activities with few political risks in order to attract potential Chinese partners.
+
+One key difference in these two organizations' differing registration strategies is their relationship with the government and alignment with government preferences.
+TNC has stated that its work "science-based" and that the organization uses a "non-confrontational, collaborative approach in working closely with governments, the business community and others.
+[@ChinaPhilanthropyReserchInstitute:2018a] Over its past two decades of work in China, TNC has provided technical support for the central government and local governments in Yunnan and Zhejiang Provinces, consulting on policies that have led to the establishment of national parks and nature reserves, and helping draft environmental policy proposals like the China National Biodiversity Conservation Strategy and Action Plan (2011–2030).
+This deliberately non-confrontational model, coupled with long-established partnerships with the government enabled TNC to secure the consent of a environment-focused national governmental agency to act as their PSU, which in turn allowed TNC to have a wider geographic reach throughout the country.
+Moreover, TNC's work with local and national governments has generally been aligned with government preferences and directly benefits the regime.
+
+In contrast, Greenpeace engages in direct advocacy, "us[ing] peaceful protest and creative confrontation to expose global environmental problems" [@todo].
+The organization describes its work in China with phrases like "non-violent direct action," "impartiality and independence," and "brings change", indicating its dedication to maintaining organizational independence as it acts as an environmental watchdog [@todo].
+In 2004, for instance, Greenpeace conducted three rounds of independent investigations into damages caused by the Sinar Mas Group, revealing how the Asian multinational corporation used promises of reforestation work as a cover while logging natural forests in Yunnan [@todo].
+Greenpeace's ongoing independent advocacy work is often at odds with regime preferences, and from the government's perspective, its Chinese programming is unpredictable and less directly manageable.
+As a result, few potential PSUs have shown interest in sponsoring any potential registration attempt, and Greenpeace has chosen to not try to permanently register and instead work through repeated temporary activities.
+
+@tbl-case-study summarizes the cases of TNC and Greenpeace.
+In addition to confirming the correlation between issue area and operational space found in the statistical model, the cases highlight how government preferences exert influence on both the degree of contentious programming INGOs are allowed to undertake and the severity of legal restrictions INGOs can face.
 
@@
 
-@tbl-case-study summarizes the comparison of the cases of TNC and Greenpeace.
-The case study shows that in addition to the correlation of issue area and operational space found in the quantitative model, the dimension of relationship with the government also exerts influence on the contentious level and restrictions INGOs can face, revealing the potential patterns of differential treatment INGOs can receive in the *de facto* implementation of the law.
-
 # Conclusion

### 2023-12-07 manuscript/manuscript.qmd
Remove second RO definition

@@
 The legal framework governing INGOs was overhauled by the 2016 ONGO Law, which applies to all overseas (including Hong Kong, Macau, and Taiwan) NGOs that conduct not-for-profit activities in mainland China.
-The ONGO Law provides two pathways for INGOs to lawfully operate in China (see @fig-ro-ta-pathways): (1) submitting an application for formal permanent registration as registered organizations (ROs), or (2) filing documentation of temporary activities with provincial Public Security Bureaus.
+The ONGO Law provides two pathways for INGOs to lawfully operate in China (see @fig-ro-ta-pathways): (1) submitting an application for formal permanent registration as registered organizations, or (2) filing documentation of temporary activities with provincial Public Security Bureaus.
 Formal registration as an RO allows INGOs to maintain an ongoing presence in the country, while temporary activities are intended for INGOs that need to conduct one-off programs that last no longer than one year.

### 2023-12-07 manuscript/manuscript.qmd
Add source links in case study

@@
 TNC has stated that its work "science-based" and that the organization uses a "non-confrontational, collaborative approach in working closely with governments, the business community and others.
-[@ChinaPhilanthropyReserchInstitute:2018a] Over its past two decades of work in China, TNC has provided technical support for the central government and local governments in Yunnan and Zhejiang Provinces, consulting on policies that have led to the establishment of national parks and nature reserves, and helping draft environmental policy proposals like the China National Biodiversity Conservation Strategy and Action Plan (2011–2030).
+[@ChinaPhilanthropyReserchInstitute:2018a] Over its past two decades of work in China, TNC has provided technical support for the central government and local governments in Yunnan and Zhejiang Provinces, consulting on policies that have led to the establishment of national parks and nature reserves, and helping draft environmental policy proposals like the China National Biodiversity Conservation Strategy and Action Plan (2011–2030)[@todo]<https://www.nature.org/en-us/about-us/where-we-work/asia-pacific/china/stories-in-china/china-overview/>.
 This deliberately non-confrontational model, coupled with long-established partnerships with the government enabled TNC to secure the consent of a environment-focused national governmental agency to act as their PSU, which in turn allowed TNC to have a wider geographic reach throughout the country.
@@
 
-In contrast, Greenpeace engages in direct advocacy, "us[ing] peaceful protest and creative confrontation to expose global environmental problems" [@todo].
-The organization describes its work in China with phrases like "non-violent direct action," "impartiality and independence," and "brings change", indicating its dedication to maintaining organizational independence as it acts as an environmental watchdog [@todo].
-In 2004, for instance, Greenpeace conducted three rounds of independent investigations into damages caused by the Sinar Mas Group, revealing how the Asian multinational corporation used promises of reforestation work as a cover while logging natural forests in Yunnan [@todo].
+In contrast, Greenpeace engages in direct advocacy, "us[ing] peaceful protest and creative confrontation to expose global environmental problems" [@todo]<https://www.greenpeace.org/usa/about/>.
+The organization describes its work in China with phrases like "non-violent direct action," "impartiality and independence," and "brings change", indicating its dedication to maintaining organizational independence as it acts as an environmental watchdog [@todo]<https://www.greenpeace.org.cn/about/mission-and-value/>.
+In 2004, for instance, Greenpeace conducted three rounds of independent investigations into damages caused by the Sinar Mas Group, revealing how the Asian multinational corporation used promises of reforestation work as a cover while logging natural forests in Yunnan [@todo]<https://www.greenpeace.org.cn/2022/11/18/%e4%ba%a4%e9%94%8b%e4%ba%9a%e6%b4%b2%e6%9c%80%e5%a4%a7%e9%80%a0%e7%ba%b8%e5%b7%a8%e9%b3%84%ef%bc%8c%e5%ae%88%e6%8a%a4%e4%ba%91%e5%8d%97%e5%a4%a9%e7%84%b6%e6%9e%97-%e7%bb%bf%e8%89%b2%e5%92%8c/>.
 Greenpeace's ongoing independent advocacy work is often at odds with regime preferences, and from the government's perspective, its Chinese programming is unpredictable and less directly manageable.

### 2023-12-07 manuscript/manuscript.qmd
minor revision in case study section

@@
 TNC and Greenpeace are both well-known environmental INGOs.
-Both are based in Western countries and both have offices around the world.
+Both are based in Western countries and have offices around the world.
 They each began working in China around the turn of the century, with TNC in establishing an office in Beijing in 1998 and Greenpeace in 2001.
@@
 
-There are several drawbacks to having to constantly file temporary activities [@Corsetti:2019], resulting in far more limited INGO operational space than under RO regulations (recall @fig-ro-ta-pathways).
+Essentially, constantly filing temporary activities has become a circumvent for INGOs like Greenpeace to maintain long-term presence in China [@Corsetti:2019].
+However, choosing a legal channel mostly meant for one-off programs results in far more limited INGO operational space than under RO regulations (recall @fig-ro-ta-pathways).
 Securing a new partnership with a Chinese organization for each activity and co-filing the requisite paperwork imposes substantial administrative costs.
-This approach also creates high uncertainty, since there is no guarantee that a current partner organization would agree to repeat their supervisory role for the next project.
+This approach also creates high uncertainty, since there is no guarantee that a current partner organization would agree to repeat their role for the next project.
 Moreover, INGO programming has an inherent short-term focus, given that temporary activities cannot last longer than a year.

### 2023-12-07 manuscript/manuscript.qmd
Add Nancy edits

@@
   - Chinese ONGO law
+word-count: 7938
 code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/compassionate-clam>"
@@
 c_issue <- epreds_issue |> 
+  mutate(issue_area = str_remove_all(issue_area, "issue_")) |> 
   group_by(issue_area) |> 
@@
 On April 28, 2016, China passed its own set of civil society restrictions with its Law of the People's Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China---or "2016 ONGO Law"---which formally took effect on January 1, 2017.
-The law requires all international NGOs (INGOs) to either establish formal in-country representative offices (ROs) or file short-term temporary activities to lawfully operate in mainland China.
+The law requires all international NGOs (INGOs) to either establish formal in-country representative offices or file short-term temporary activities to lawfully operate in mainland China.
 Without recognized legal status, INGOs are prohibited from working in the country, and even with legal recognition, INGO programming is limited to government-approved activities.
@@
 
-As an authoritarian state with a growing nonprofit sector, China's regulatory regime for INGOs serves as an example for understanding how autocracies use restrictive laws as policy tools as they engage with international civil society.
+As an authoritarian state with a growing nonprofit sector, China's regulatory regime for INGOs serves as an example for understanding how autocracies use restrictive laws as policy tools to engage with international civil society.
 The policies implemented by China's 2016 ONGO law serve dueling purposes that both harness the benefits and reduce the risks of INGOs.
-The law is designed to decrease demand for foreign civil society organizations and limit the influence they might have over domestic policies [@DeMattee:2018; @DeMattee:2019] while also allowing the regime to benefit from the expertise, services, and reputational advantages of working partnering with international civil society [@Plantan:2022; @Heiss:2019].
+The law is designed to decrease demand for foreign civil society organizations and limit the influence they might have over domestic policies [@DeMattee:2018; @DeMattee:2019] while also allowing the regime to benefit from the expertise, services, and reputational advantages of working with international civil society [@Plantan:2022; @Heiss:2019].
 These dual demands lead to differential enforcement and divergence between formal *de jure* regulations and the *de facto* implementation of those laws [@ChaudhryHeiss:2022], as the government enforces regulations selectively depending on regime preferences for INGO services.
 
-In this paper, we use the case of China to explore how the demands to both restrict and embrace INGOs have shaped the international nonprofit sector in the five years since the 2016 ONGO Law came into effect.
+In this paper, we use the case of China to explore how demands to both restrict and embrace INGOs have shaped the international nonprofit sector in the five years since the 2016 ONGO Law came into effect.
 We examine how the ONGO Law has influenced the population of INGOs that have successfully registered in China, as well as the association between factors such as INGO issue areas and the operational space granted to them in the country.
@@
 By focusing on INGO operational space in China, we provide a unique empirical view into the *de facto* regulatory environment for foreign civil society in an authoritarian state.
-Broader indexes of civil society openness---such as the core civil society index from the Varieties of Democracy project [@LianMurdie:2023; @ChaudhryHeiss:2022]---capture the general regulatory environment for all civil society more broadly, but do not reflect the specific implementation of laws for INGOs.
-In this paper, we use a mixed methods approach to explore the regulatory environment for INGOs in particular, providing a much richer description and analysis of the impact of INGO laws.
+General indexes of civil society openness---such as the core civil society index from the Varieties of Democracy project [@LianMurdie:2023; @ChaudhryHeiss:2022]---capture the regulatory environment for civil society more broadly, but do not reflect the specific implementation of laws for INGOs.
+In this paper, we use a mixed methods approach to explore the regulatory environment for INGOs in particular, providing a richer description and analysis of the impact of INGO laws.
 
@@
 The legal framework governing INGOs was overhauled by the 2016 ONGO Law, which applies to all overseas (including Hong Kong, Macau, and Taiwan) NGOs that conduct not-for-profit activities in mainland China.
-The ONGO Law provides two pathways for INGOs to lawfully operate in China (see @fig-ro-ta-pathways): (1) submitting an application for formal permanent registration as registered organizations, or (2) filing documentation of temporary activities with provincial Public Security Bureaus.
+The ONGO Law provides two pathways for INGOs to lawfully operate in China (see @fig-ro-ta-pathways): (1) submitting an application for official status with a representative office (RO), or (2) filing documentation of temporary activities with provincial Public Security Bureaus.
 Formal registration as an RO allows INGOs to maintain an ongoing presence in the country, while temporary activities are intended for INGOs that need to conduct one-off programs that last no longer than one year.
@@
 Specifically, we can observe exactly how the Chinese government has used the RO registration process to strategically limit the potential reach of INGOs and reshape their issue areas.
-We use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that INGOs desire to engage in work in as broad a geographical scope as possible [@Li:2020].
+We use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that, in general, most INGOs desire to engage in work in as broad a geographical scope as possible [@Li:2020].
 For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas might need their service.
@@
 
-Our data comes from INGOs' public registration documents disclosed by the Ministry of Public Security's Overseas NGO Office, which maintains a website with complete documentation of all the ROs and temporary activities registered or filled across China.
-We include all INGO registrations between January 1, 2017, when the law took effect, to December 31, 2021, with information for all `r nrow(ongo)` actively registered organizations.
+Our data comes from INGOs' public registration documents disclosed by the Ministry of Public Security's Overseas NGO Office, which maintains a website with complete documentation of all the ROs registered and temporary activities filed across China.
+We include all RO registrations between January 1, 2017, when the law took effect, to December 31, 2021, with information for all `r nrow(ongo)` actively registered organizations.
 The filing documents for ROs disclose each INGO's name, address, registration date, regulating Public Security Bureau, PSU, issue area and purposes of the RO, and the specific provinces they can work in.
@@
 Nearly half of all ROs---`r ros_2017$prop_nice`---registered in 2017, and the count of new registrations gradually declined after the initial first-year wave (see @fig-registration-timeline).
-This is largely because both INGOs and the regulators needed some transitional time to explore the specific application of the law as large ambiguity was left when the law was passed.
+This is largely because both INGOs and regulators needed transitional time to explore the specific application of the law during the ambiguous first few months.
 We use this temporal variable as a proxy for the motivation or eagerness of INGOs to register as an RO, since INGOs may have been inclined to avoid the cumbersome registration procedures at the early stage if there were no real consequences for delaying, while others took the time to talk with multiple potential PSUs to find a more suitable superior or regulatory dynamic [@Jia:2017a].
@@
 #|   in. The left panel shows the full distribution of INGOs registered in 2–31 
-#|   provinces; the right panel collapses these in-between counts into to a 
+#|   provinces; the right panel collapses these in-between counts into a 
 #|   single category."
@@
 
-Since we are primarily interested in how an INGO's issue area, its local connections, and the timing of its registration after January 2017, we include these as explanatory variables.
+Since we are primarily interested in the influence of INGO's issue area, its local connections, and the timing of its registration on its operational space, we include these as explanatory variables.
 We also include random province intercepts to account for between-region differences in how INGOs are regulated, since every RO is overseen by provincial-level Public Security Bureaus.
@@
 Following our first theoretical expectation, we predict that INGOs working on less contentious issues should be registered in more provinces and thus have more geographic flexibility.
-We take advantage of the simultaneous continuous and discrete features of ordered Beta regression and see how often an INGO in each issue area is predicted to work in a single province, across all provinces, or some number in between.
+We take advantage of the simultaneous continuous and discrete features of ordered Beta regression to see how often an INGO in each issue area is predicted to work in a single province, across all provinces, or some number in between.
 @fig-issue-preds(a) presents a summary of predicted posterior outcomes for 1,000 hypothetical INGOs, varying each issue area and holding all other variables at their mean or modal values.
@@
 Several notable trends emerge from the model results.
-INGOs focused on arts and culture are overwhelming the most likely kind of organization to work nationally---arts and culture organizations are predicted to work in all 32 provinces `r p_issue$arts_and_culture.all_32_provinces$prop_ci_nice` of the time and are only predicted to work in a single province a rare `r p_issue$arts_and_culture.only_1_province$prop_ci_nice` of the time.
+INGOs focused on arts and culture are overwhelmingly the most likely kind of organization to work nationally---arts and culture organizations are predicted to work in all 32 provinces `r p_issue$arts_and_culture.all_32_provinces$prop_ci_nice` of the time and are only predicted to work in a single province a rare `r p_issue$arts_and_culture.only_1_province$prop_ci_nice` of the time.
 Education-focused INGOs, on the other hand, are the least likely kind of organization to be registered in all 32 provinces and are predicted to do so only `r p_issue$education.all_32_provinces$prop_ci_nice` of the time.
-Education INGOs are the most likely to be registered in only one province, with that predicted outcome appearing `r p_issue$education.only_1_province$prop_ci_nice` of the time---15--20 percentage points higher than any other issue area's predicted proportion.
+Education INGOs are the most likely to be registered in only one province, with that predicted outcome appearing `r p_issue$education.only_1_province$prop_ci_nice` of the time, 15--20 percentage points higher than any other issue area's predicted proportion.
 All other issue areas follow roughly similar patterns in predictions: the most common outcome is for organizations to work nationally (≈45--60% of the time), followed by working in at least 2 provinces (≈25--35% of the time), followed by working in a single province (≈15--30% of the time).
@@
 Education is particularly notable as the least flexible and most geographically restricted subsector.
-While education is typically considered a low-contention issue, in China fears of Western influence through educational institutions were an original impetus for the ONGO law.
+While education is typically considered a low-contention issue, fears of Western influence through educational institutions were an original impetus for China's ONGO law.
 In 2006, an article in a CCP-owned newspaper warned that the growing presence of international NGOs would "undermine national security," "destroy political stability," "foster corruption," "propagate foreign practices," and "spy on and gather information on China's military, political, and economic information" [@Yin:2009, 534].
@@
 Foreign NGOs' working methods also affect Chinese NGOs" [@Wang:2012, 110].
-Education is therefore one of the more contentious issues allowed under the ONGO law, and thus more closely regulated and restricted.
+Education is therefore one of the more contentious issues allowed under the ONGO law, and is thus more closely regulated and restricted.
 
@@
 
-In our second theoretical expectation, we posit that since INGOs that seek out local connections and that are focused on more local China-specific issues, those organizations should be registered in fewer provinces.
+In our second theoretical expectation, we posit that INGOs with an explicitly local focus should be registered in fewer provinces.
 The results from our model confirm this expectation.
@@
 However, the results of our model support the opposite of this expectation.
-In @fig-timing-preds(a) organizations that registered in the first year have a `r p_timing$x2017.all_32_provinces$prop_ci_nice` probability of working in all provinces and are predicted to work in two or more provinces `r p_timing$x2017.between_1_32_provinces$prop_ci_nice` of the time.
+In @fig-timing-preds(a) organizations that registered in the first year have a `r p_timing$x2017.all_32_provinces$prop_ci_nice` probability of working in all provinces and a `r p_timing$x2017.between_1_32_provinces$prop_ci_nice` probability of working in two or more provinces.
 These early INGOs are the most likely to be registered in only one province and are predicted to do so `r p_timing$x2017.only_1_province$prop_ci_nice` of the time.
@@
 Another possible explanation could be that earlier registration signals greater eagerness to reduce the uncertainty surrounding organizational legal status.
-INGOs that perceive themselves as more contentious may be more nervous about the legal consequences of not being able to register and thus be more willing to seek registration earlier [@ChinaPhilanthropyReserchInstitute:2018].
+INGOs that perceive themselves as more contentious may be more nervous about the legal consequences of not being able to register and thus be more willing to seek registration earlier [@ChinaPhilanthropyResearchInstitute:2018].
 Compared with their safer, less contentious peers, INGOs seeking to register earlier are more likely to have reduced operational space.
@@
 This can help explain why some seemingly more contentious issue areas such as environmental INGOs enjoy relatively more operational space (see @fig-issue-preds).
-Chinese authorities can benefit politically from the of environmental INGOs and "selectively encourage low risk groups and selectively channel higher risk groups into permitted areas" [@Plantan:2022, 504].
+Since Chinese authorities can benefit politically from the work of environmental INGOs, they "selectively encourage low risk groups and selectively channel higher risk groups into permitted areas" [@Plantan:2022, 504].
 Using our data, however, we are unable to make comparisons with already-vetted INGOs and other potentially more contentious organizations, which limits our analysis of the determinants of operational space.
@@
 Both are based in Western countries and have offices around the world.
-They each began working in China around the turn of the century, with TNC in establishing an office in Beijing in 1998 and Greenpeace in 2001.
-Despite these similarities, the two INGOs have had quite different experiences to sustain their legal presence in China after the ONGO Law took effect.
+They each began working in China around the turn of the century, with TNC establishing an office in Beijing in 1998 and Greenpeace in 2001.
+Despite these similarities, the two INGOs have had quite different experiences in maintaining their legal presence in China after the ONGO Law took effect.
 TNC obtained RO status in May 2017, partnering with the National Forestry and Grassland Administration as their PSU, and receiving authorization to work in 27 provinces.
-In contrast, Greenpeace has not received RO status and has instead filed 67 temporary activities, filing new documentation nearly ten times each year.
-
-Essentially, constantly filing temporary activities has become a circumvent for INGOs like Greenpeace to maintain long-term presence in China [@Corsetti:2019].
-However, choosing a legal channel mostly meant for one-off programs results in far more limited INGO operational space than under RO regulations (recall @fig-ro-ta-pathways).
+In contrast, Greenpeace has not received RO status and has instead filed 67 temporary activities, submitting new documentation more than ten times each year.
+
+Repeatedly filing temporary activities has become a common alternative method for INGOs like Greenpeace to maintain long-term presence in China [@Corsetti:2019].
+However, choosing a legal channel originally designed for one-off programs results in far more limited INGO operational space than under RO regulations (recall @fig-ro-ta-pathways).
 Securing a new partnership with a Chinese organization for each activity and co-filing the requisite paperwork imposes substantial administrative costs.
@@
 One key difference in these two organizations' differing registration strategies is their relationship with the government and alignment with government preferences.
-TNC has stated that its work "science-based" and that the organization uses a "non-confrontational, collaborative approach in working closely with governments, the business community and others.
-[@ChinaPhilanthropyReserchInstitute:2018a] Over its past two decades of work in China, TNC has provided technical support for the central government and local governments in Yunnan and Zhejiang Provinces, consulting on policies that have led to the establishment of national parks and nature reserves, and helping draft environmental policy proposals like the China National Biodiversity Conservation Strategy and Action Plan (2011–2030)[@todo]<https://www.nature.org/en-us/about-us/where-we-work/asia-pacific/china/stories-in-china/china-overview/>.
+TNC has stated that its work is "science-based" and that the organization uses a "non-confrontational, collaborative approach in working closely with governments, the business community and others" [@ChinaPhilanthropyResearchInstitute:2018a].
+Over its past two decades of work in China, TNC has provided technical support for the central government and local governments in Yunnan and Zhejiang Provinces, consulting on policies that have led to the establishment of national parks and nature reserves, and helping draft environmental policy proposals like the China National Biodiversity Conservation Strategy and Action Plan (2011–2030)[@todo]<https://www.nature.org/en-us/about-us/where-we-work/asia-pacific/china/stories-in-china/china-overview/>.
 This deliberately non-confrontational model, coupled with long-established partnerships with the government enabled TNC to secure the consent of a environment-focused national governmental agency to act as their PSU, which in turn allowed TNC to have a wider geographic reach throughout the country.
@@
 In contrast, Greenpeace engages in direct advocacy, "us[ing] peaceful protest and creative confrontation to expose global environmental problems" [@todo]<https://www.greenpeace.org/usa/about/>.
-The organization describes its work in China with phrases like "non-violent direct action," "impartiality and independence," and "brings change", indicating its dedication to maintaining organizational independence as it acts as an environmental watchdog [@todo]<https://www.greenpeace.org.cn/about/mission-and-value/>.
+The organization describes its work in China with phrases like "non-violent direct action," "impartiality and independence," and "brings change," indicating its dedication to maintaining organizational independence as it acts as an environmental watchdog [@todo]<https://www.greenpeace.org.cn/about/mission-and-value/>.
 In 2004, for instance, Greenpeace conducted three rounds of independent investigations into damages caused by the Sinar Mas Group, revealing how the Asian multinational corporation used promises of reforestation work as a cover while logging natural forests in Yunnan [@todo]<https://www.greenpeace.org.cn/2022/11/18/%e4%ba%a4%e9%94%8b%e4%ba%9a%e6%b4%b2%e6%9c%80%e5%a4%a7%e9%80%a0%e7%ba%b8%e5%b7%a8%e9%b3%84%ef%bc%8c%e5%ae%88%e6%8a%a4%e4%ba%91%e5%8d%97%e5%a4%a9%e7%84%b6%e6%9e%97-%e7%bb%bf%e8%89%b2%e5%92%8c/>.
 Greenpeace's ongoing independent advocacy work is often at odds with regime preferences, and from the government's perspective, its Chinese programming is unpredictable and less directly manageable.
-As a result, few potential PSUs have shown interest in sponsoring any potential registration attempt, and Greenpeace has chosen to not try to permanently register and instead work through repeated temporary activities.
+As a result, few potential PSUs have shown interest in sponsoring any potential registration attempt, and Greenpeace has chosen to work through repeated temporary activities rather than trying to gain RO status.
 
@@
 This is not an issue specific to China---analyzing the international nonprofit sector of any country that has passed similar laws will raise similar issues of selection bias.
-The Chinese context provides one possible way forward: future research can further explore relationship between INGOs and regime preferences by comparing characteristics of INGOs that register as ROs or undertake temporary activities using already-available administrative data.
+The Chinese context provides one possible way forward: future research can further explore the relationship between INGOs and regime preferences by comparing characteristics of INGOs that register as ROs or undertake temporary activities using already-available administrative data.
 Second, this paper focuses exclusively on INGO regulations in China, and the specific legal mechanisms for controlling INGOs in other countries will naturally differ.

### 2023-12-07 manuscript/manuscript.qmd
Improve map fill and labeling

@@
 
+ongo_mapdata <- ongo_mapdata |> 
+  # Change provinces with 0 ONGOs to NA for plotting
+  mutate(ro_count = ifelse(ro_count == 0, NA, ro_count)) |> 
+  # Manually repel some provinces
+  mutate(repel = case_when(
+    province_en %in% c("Shanghai", "Tianjin") ~ "right",
+    province_en == "Beijing" ~ "up",
+    province_en == "Hebei" ~ "left",
+    .default = "none"
+  ))
+
 # Use aes(geometry) and stat = "sf_coordinates" to make geom_label_repel() work
@@
 ggplot() +
-  geom_sf(data = ongo_mapdata, aes(fill = ro_count), color = NA) +
+  geom_sf(data = filter(ongo_mapdata, !is_taiwan), aes(fill = sqrt(ro_count)), color = NA) +
+  geom_sf(data = filter(ongo_mapdata, is_taiwan), fill = "gray70", color = NA) +
   geom_sf(data = interior_borders, linewidth = 0.3, color = "white") +
-  scale_fill_distiller(palette = "Reds", direction = 1, guide = "none", na.value = "gray80") +
+  scale_fill_distiller(palette = "Reds", direction = 1, guide = "none", na.value = "gray94") +
+  geom_sf_label(
+    data = filter(ongo_mapdata, ro_count > 0, repel == "none"),
+    aes(label = ro_count),
+    label.size = 0.05, size = 3, 
+    color = "black", fill = scales::alpha("white", 0.8)
+  ) +
   geom_label_repel(
-    data = filter(ongo_mapdata, ro_count > 0),
+    data = filter(ongo_mapdata, ro_count > 0, repel == "right"),
     aes(label = ro_count, geometry = geometry),
     stat = "sf_coordinates", seed = 1234, label.size = 0.05, size = 3,
-    color = "black", fill = scales::alpha("white", 0.7),
-    segment.color = "black", segment.size = 0.25, min.segment.length = 0
+    color = "black", fill = scales::alpha("white", 0.8),
+    segment.color = "black", segment.size = 0.25, min.segment.length = 0,
+    direction = "x", nudge_x = 1.5
+  ) +
+  geom_label_repel(
+    data = filter(ongo_mapdata, ro_count > 0, repel == "left"),
+    aes(label = ro_count, geometry = geometry),
+    stat = "sf_coordinates", seed = 1234, label.size = 0.05, size = 3,
+    color = "black", fill = scales::alpha("white", 0.8),
+    segment.color = "black", segment.size = 0.25, min.segment.length = 0,
+    direction = "x", nudge_x = -1.5
+  ) +
+  geom_label_repel(
+    data = filter(ongo_mapdata, ro_count > 0, repel == "up"),
+    aes(label = ro_count, geometry = geometry),
+    stat = "sf_coordinates", seed = 1234, label.size = 0.05, size = 3,
+    color = "black", fill = scales::alpha("white", 0.8),
+    segment.color = "black", segment.size = 0.25, min.segment.length = 0,
+    direction = "y", nudge_y = 1.5
   ) +

### 2023-12-07 manuscript/appendix.qmd
Move descriptive results to data section + add inline chunks + more editing
Move mathy stuff to appendix

@@
 
+$$
+\begin{aligned}
+&\ \textbf{Registered provinces for INGO } i \\
+\text{Count of provinces}\ \sim&\ \operatorname{Ordered\,Beta}(\mu_i, \phi_y, k_{1_y}, k_{2_y}) \\[8pt]
+&\ \textbf{Model of outcome average} \\
+\mu_i =&\ 
+  \mathrlap{\begin{aligned}[t]
+  & \beta_0 + \beta_1\ \text{Issue[Arts and culture]} + \beta_2\ \text{Issue[Education]}\ +\\
+  & \beta_3\ \text{Issue[Industry association]} + \beta_4\ \text{Issue[Economy and trade]}\ + \\
+  & \beta_5\ \text{Issue[Charity and humanitarian]} + \beta_6\ \text{Issue[General]}\ + \\
+  & \beta_7\ \text{Issue[Health]} + \beta_8\ \text{Issue[Environment]}\ + \\
+  & \beta_9\ \text{Issue[Science and technology]} + \beta_{10}\ \text{Local connections}\ + \\
+  & \beta_{11}\ \text{Time since January 2017} + \beta_{12}\ \text{Year registered}
+  \end{aligned}}\\[8pt]
+&\ \textbf{Priors} \\
+\beta_0\ \sim&\ \operatorname{Student\,t}(\nu = 3, \mu = 0, \sigma = 2.5) && \text{Intercept} \\
+\beta_{1..12}\ \sim&\ \mathcal{N}(0, 5) && \text{Coefficients} \\
+\phi_y\ \sim&\ \operatorname{Exponential}(1 / 100) && \text{Variability in province count} \\
+k_{1_y}, k_{2_y}\ \sim&\ \operatorname{Induced\,Dirichlet}(1, 1, 1), && \text{0–continuous and continuous–1 cutpoints} \\
+&\ \quad \text{or } \bigl[P(\alpha_1), P(\alpha_1 + \alpha_2)\bigr] && \quad\text{(boundaries between 3 Dirichlet columns)}
+\end{aligned}
+$$
+
 ## Coding rules for issue ares
+
+Author 1 assigned each organization to one of the issue areas defined in Article 3 of the ONGO Law, and Author 2 cross-checked the coding for ambiguous cases
 

### 2023-12-07 manuscript/manuscript.qmd
Move mathy stuff to appendix

@@
 We also include random province intercepts to account for between-region differences in how INGOs are regulated, since every RO is overseen by provincial-level Public Security Bureaus.
-We use the following model and priors; additional model details and results are available in the appendix and in TABLE TODO:
-
-$$
-\begin{aligned}
-&\ \textbf{Registered provinces for INGO } i \\
-\text{Count of provinces}\ \sim&\ \operatorname{Ordered\,Beta}(\mu_i, \phi_y, k_{1_y}, k_{2_y}) \\[8pt]
-&\ \textbf{Model of outcome average} \\
-\mu_i =&\ 
-  \mathrlap{\begin{aligned}[t]
-  & \beta_0 + \beta_1\ \text{Issue[Arts and culture]} + \beta_2\ \text{Issue[Education]}\ +\\
-  & \beta_3\ \text{Issue[Industry association]} + \beta_4\ \text{Issue[Economy and trade]}\ + \\
-  & \beta_5\ \text{Issue[Charity and humanitarian]} + \beta_6\ \text{Issue[General]}\ + \\
-  & \beta_7\ \text{Issue[Health]} + \beta_8\ \text{Issue[Environment]}\ + \\
-  & \beta_9\ \text{Issue[Science and technology]} + \beta_{10}\ \text{Local connections}\ + \\
-  & \beta_{11}\ \text{Time since January 2017} + \beta_{12}\ \text{Year registered}
-  \end{aligned}}\\[8pt]
-&\ \textbf{Priors} \\
-\beta_0\ \sim&\ \operatorname{Student\,t}(\nu = 3, \mu = 0, \sigma = 2.5) && \text{Intercept} \\
-\beta_{1..12}\ \sim&\ \mathcal{N}(0, 5) && \text{Coefficients} \\
-\phi_y\ \sim&\ \operatorname{Exponential}(1 / 100) && \text{Variability in province count} \\
-k_{1_y}, k_{2_y}\ \sim&\ \operatorname{Induced\,Dirichlet}(1, 1, 1), && \text{0–continuous and continuous–1 cutpoints} \\
-&\ \quad \text{or } \bigl[P(\alpha_1), P(\alpha_1 + \alpha_2)\bigr] && \quad\text{(boundaries between 3 Dirichlet columns)}
-\end{aligned}
-$$
+The appendix contains complete details of our modeling approach, priors, model definition, and tables of raw results.
 

### 2023-12-07 manuscript/manuscript.qmd
Add TNC and Greenpeace citations

@@
 short-title: "Operational constraints and closing civic space"
-date: "2023-12-03"
+date: "2023-12-07"
 author:
@@
   - Chinese ONGO law
-word-count: 7938
+word-count: 7984
 code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/compassionate-clam>"
@@
 It is also likely, given the high probability of national reach, that organizations without local connections purposely do not spend the time and effort to cultivate those relationships, as it is not necessary to operate across many provinces.
-A rival explanation that having local connections reduces an organization's operational space does not seem warranted—although INGOs with local connections do have a more limited geographic scope, organizations appear to purposely limit the number of provinces they work in in order to focus more on their local work.
+A rival explanation that having local connections reduces an organization's operational space does not seem warranted---although INGOs with local connections do have a more limited geographic scope, organizations appear to purposely limit the number of provinces they work in in order to focus more on their local work.
 
@@
 TNC has stated that its work is "science-based" and that the organization uses a "non-confrontational, collaborative approach in working closely with governments, the business community and others" [@ChinaPhilanthropyResearchInstitute:2018a].
-Over its past two decades of work in China, TNC has provided technical support for the central government and local governments in Yunnan and Zhejiang Provinces, consulting on policies that have led to the establishment of national parks and nature reserves, and helping draft environmental policy proposals like the China National Biodiversity Conservation Strategy and Action Plan (2011–2030)[@todo]<https://www.nature.org/en-us/about-us/where-we-work/asia-pacific/china/stories-in-china/china-overview/>.
+Over its past two decades of work in China, TNC has provided technical support for the central government and local governments in Yunnan and Zhejiang Provinces, consulting on policies that have led to the establishment of national parks and nature reserves, and helping draft environmental policy proposals like the China National Biodiversity Conservation Strategy and Action Plan (2011–2030) [@TheNatureConservancy:2023].
 This deliberately non-confrontational model, coupled with long-established partnerships with the government enabled TNC to secure the consent of a environment-focused national governmental agency to act as their PSU, which in turn allowed TNC to have a wider geographic reach throughout the country.
@@
 
-In contrast, Greenpeace engages in direct advocacy, "us[ing] peaceful protest and creative confrontation to expose global environmental problems" [@todo]<https://www.greenpeace.org/usa/about/>.
-The organization describes its work in China with phrases like "non-violent direct action," "impartiality and independence," and "brings change," indicating its dedication to maintaining organizational independence as it acts as an environmental watchdog [@todo]<https://www.greenpeace.org.cn/about/mission-and-value/>.
-In 2004, for instance, Greenpeace conducted three rounds of independent investigations into damages caused by the Sinar Mas Group, revealing how the Asian multinational corporation used promises of reforestation work as a cover while logging natural forests in Yunnan [@todo]<https://www.greenpeace.org.cn/2022/11/18/%e4%ba%a4%e9%94%8b%e4%ba%9a%e6%b4%b2%e6%9c%80%e5%a4%a7%e9%80%a0%e7%ba%b8%e5%b7%a8%e9%b3%84%ef%bc%8c%e5%ae%88%e6%8a%a4%e4%ba%91%e5%8d%97%e5%a4%a9%e7%84%b6%e6%9e%97-%e7%bb%bf%e8%89%b2%e5%92%8c/>.
+In contrast, Greenpeace engages in direct advocacy, using peaceful---but confrontational---protests to expose environmental abuses and shame governments and for-profit corporations that harm the environment.
+The organization describes its work in China with phrases like "non-violent direct action," "impartiality and independence," and "brings change," indicating its dedication to maintaining organizational independence as it acts as an environmental watchdog [@Greenpeace:2023].
+In 2004, for instance, Greenpeace conducted three rounds of independent investigations into damages caused by the Sinar Mas Group, revealing how the Asian multinational corporation used promises of reforestation work as a cover while logging natural forests in Yunnan [@Greenpeace:2022].
 Greenpeace's ongoing independent advocacy work is often at odds with regime preferences, and from the government's perspective, its Chinese programming is unpredictable and less directly manageable.
@@
 By focusing on a specific law in one country, our work provides rich empirical illustrations of the mechanics of authoritarian administrative crackdown.
-We find that INGOs that work on issues that are less threatening and more aligned with regime preferences---such as arts & culture INGOs, industry associations, and scientific organizations—are registered in more provinces and thus enjoy a greater degree of operational space, while organizations that pose a potential threat---like education INGOs---are far more limited geographically.
+We find that INGOs that work on issues that are less threatening and more aligned with regime preferences---such as arts & culture INGOs, industry associations, and scientific organizations---are registered in more provinces and thus enjoy a greater degree of operational space, while organizations that pose a potential threat---like education INGOs---are far more limited geographically.
 Our case study finds similar results.

### 2023-12-07 notebook/manuscript.qmd
Make the manuscript a target
Correctly render the appendix and manuscript with targets

@@
 # Add the manuscript target as a dependency to the overall website
-# targets::tar_load(c(manuscript_nice, manuscript_manuscripty))
+targets::tar_load(
+  c(manuscript_nice, manuscript_manuscripty,
+    appendix_nice, appendix_manuscripty)
+)
 ```

### 2023-12-07 _targets.R

@@ -86,7 +86,9 @@ list(
   
   ## Analysis notebook ----
   tar_quarto(manuscript_nice, path = "manuscript", quiet = FALSE, profile = "nice"),
+  tar_quarto(appendix_nice, path = "manuscript", quiet = FALSE, profile = "appendix-nice"),
   tar_quarto(manuscript_manuscripty, path = "manuscript", quiet = FALSE, profile = "ms"),
+  tar_quarto(appendix_manuscripty, path = "manuscript", quiet = FALSE, profile = "appendix-ms"),
   tar_quarto(website, path = ".", quiet = FALSE),
   
   tar_target(deploy_script, here_rel("deploy.sh"), format = "file"),

### 2023-12-07 notebook/appendix.qmd
Add appendix to website

---
title: Appendix
toc: false
page-layout: full
---

```{r include=FALSE}
# Add the manuscript target as a dependency to the overall website
targets::tar_load(
  c(appendix_nice, appendix_manuscripty)
)
```

```{=html}
<p class="text-center">
  <a class="btn btn-success btn-sm mb-1" href="/manuscript/output/appendix.html" target="appendix">
  <i class="fa-solid fa-file-lines"></i> &ensp;HTML
  </a>

  <a class="btn btn-success btn-sm mb-1" href="/manuscript/output/appendix.html" target="_blank">
  <i class="fa-solid fa-arrow-up-right-from-square"></i>&ensp;HTML <small>(new window)</small>
  </a>

  <a class="btn btn-danger btn-sm mb-1" href="/manuscript/output/appendix.pdf" target="appendix">
  <i class="fa-solid fa-file-pdf"></i>&ensp;PDF
  </a>

  <a class="btn btn-danger btn-sm mb-1" target="_blank" href="/manuscript/output/appendix.pdf">
  <i class="fa-solid fa-file-arrow-down"></i>&ensp;PDF <small>(download)</small>
  </a>

  <a class="btn btn-warning btn-sm mb-1" href="/manuscript/output-ms/appendix-ms.pdf" target="appendix">
  <i class="fa-solid fa-file-pdf"></i>&ensp;Manuscripty PDF
  </a>

  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/manuscript/output-ms/appendix-ms.pdf">
  <i class="fa-solid fa-file-arrow-down"></i>&ensp;Manuscripty PDF <small>(download)</small>
  </a>
</p>

<iframe src="/manuscript/output/appendix.html" frameborder="0" style="overflow:hidden;height:90%;width:100%;border:2px solid #ccc;" height="90%" width="100%" name="appendix"></iframe>
```

### 2023-12-07 notebook/manuscript.qmd
Add appendix to website

--- 2023-04-07 notebook/manuscript.qmd
@@
 # Add the manuscript target as a dependency to the overall website
-# targets::tar_load(c(manuscript_nice, manuscript_manuscripty))
+targets::tar_load(
+  c(manuscript_nice, manuscript_manuscripty)
+)
 ```

### 2023-12-07 manuscript/manuscript.qmd
Use smaller font size in tables

@@
 
+\footnotesize
+\renewcommand*{\arraystretch}{1.75}
+
 ```{r}
@@
   "Economy and trade", "World Economic Forum; Canada China Business Council",
-  "Education", "Children’s Education Foundation; BSK International",
+  "Education", "Children's Education Foundation; BSK International",
   "Environment", "The Nature Conservancy; World Wide Fund for Nature",
@@
 
+\newpage
+
 # References

### 2023-12-07 manuscript/appendix.qmd
Update title

@@
 ---
-title: 'Online appendix for "Operational constraints and closing civic space: International NGO restrictions and China’s Overseas NGO law"'
-short-title: 'Online appendix for "Operational constraints and closing civic space"'
-date: "2023-12-06"
+title: >-
+  Online appendix for "Enforcing Boundaries: China's Overseas NGO Law and Operational Constraints for Global Civil Society"
+short-title: 'Online appendix for "Enforcing Boundaries"'
+date: "2023-12-07"
 author:

### 2023-12-07 manuscript/manuscript.qmd
Update title

@@
 ---
-title: "Operational constraints and closing civic space: International NGO restrictions and China’s Overseas NGO law"
-short-title: "Operational constraints and closing civic space"
+title: "Enforcing Boundaries: China's Overseas NGO Law and Operational Constraints for Global Civil Society"
+short-title: "Enforcing Boundaries"
 date: "2023-12-07"

### 2023-12-07 manuscript/appendix.qmd
Finish appendix

@@
 link-citations: true
-crossref: 
-  tbl-title: Appendix Table
-  fig-title: Appendix Figure
 ---
@@
 
-# Appendix
+```{r libraries-data}
+library(tidyverse)
+library(scales)
+library(modelsummary)
+library(gt)
+library(targets)
+
+# Generated via random.org
+set.seed(8511)
+
+# Targets stuff
+tar_config_set(
+  store = here::here("_targets"),
+  script = here::here("_targets.R")
+)
+
+tar_load(c(models_tbl))
+
+# Plotting and modelsummary functions
+invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+invisible(list2env(tar_read(table_functions), .GlobalEnv))
+
+theme_set(theme_ongo())
+set_annotation_fonts()
+```
+
+# Model details and results
+
+We use Stan [@Stan-2-26-1 v2.26.1; @cmdstan-2-3-1 v2.3.1] through R [@rproject-4-3-1 v4.3.1] and **brms** [@Burkner:2017 v2.20.5] to estimate our ordered Beta regression models [@Kubinec:2022].
+We simulate 4 MCMC chains with 2,000 draws in each chain, 1,000 of which are used for warmup, resulting in 4,000 (1,000 × 4) draws per model parameter.
+We assess convergence with visual inspection, and all chains converge.
+Complete results from all the models, along with posterior predictive checks, goodness-of-fit measures, and model diagnostics—as well as our code and data—are available `ANONYMIZED_URL`.
+We include the formal definition and priors for our model below.
 
@@
 
-## Coding rules for issue ares
+\newpage
 
-Author 1 assigned each organization to one of the issue areas defined in Article 3 of the ONGO Law, and Author 2 cross-checked the coding for ambiguous cases
+::: {#tbl-coefs-orig}
 
-1. Education vs. Charity
-If charitable activities are all education related, e.g. building schools, donating education facilities and books, coded as education
-If the aids provided include other community support, e.g. building bridges, roads, medical facilities, coded as charity
+\footnotesize
 
-2. Economy and trade vs. Industry association
-If the trade promoted is focused on a particular industry (poultry, grains etc.), coded as industry association
+```{r}
+#| label: table-coefs-orig
+#| include: true
 
-3. Arts and culture 
-Include sports organizations too.
+notes <- c(
+  "Estimates are median posterior log odds from ordered Beta regression models;",
+  "95% credible intervals (highest density posterior interval, or HDPI) in brackets."
+)
 
-4. Industry association vs. health, science and technology, arts and culture
+modelsummary(
+  models_tbl$msl, 
+  estimate = "{estimate}",
+  statistic = "[{conf.low}, {conf.high}]",
+  fmt = fmt_significant(2),
+  coef_map = models_tbl$nice_coefs,
+  output = "gt"
+) |> 
+  opts_theme() |>
+  tab_footnote(
+    footnote = paste(notes, collapse = " ")
+  ) %>%
+  opts_theme() |>
+  tab_options(
+    quarto.disable_processing = TRUE
+  )
+```
 
-There are professional association on health providers and certain techniques.
-Coded as health, science & technology if work areas go beyond serving members only: for example conducting activities of promoting and training about certain techniques.
+Complete model coefficients
 
-If specialized association only serves the member companies: coded as industry associations
+:::
 
-5. Health vs. Charity 
-If only providing medical aids to underprivileged communities, not building schools etc., coded as health
+\clearpage
 
-6. Charity vs. General 
-If multiple work, e.g., poverty alleviation, education, health can be encompassed by Charity and humanitarian, then the former
+# Coding rules for issue ares
 
-7. Multiple ROs are coded based on the overall work area spans of the INGO, not the specific RO, so to ensure the issue area coding is consistent across ROs
+Author 1 assigned each organization to one of the issue areas defined in Article 3 of the ONGO Law, and Author 2 cross-checked the coding for ambiguous cases.
+Organizations with multiple ROs are coded based on the overall issue area of the INGO, not the specific RO, so to ensure the issue area coding is consistent across ROs.
 
-## Modeling details
+We followed these rules for categorizing INGOs' stated missions into issue areas:
 
-We use Stan [@Stan-2-26-1 v2.26.1; @cmdstan-2-3-1 v2.3.1] through R [@rproject-4-3-1 v4.3.1] and **brms** [@Burkner:2017 v2.20.5] to estimate the model We simulate 4 MCMC chains with 2,000 draws in each chain, 1,000 of which are used for warmup, resulting in 4,000 (1,000 × 4) draws per model parameter.
-We assess convergence with visual inspection, and all chains converge.
-Complete results from all the models, along with posterior predictive checks, goodness-of-fit measures, and model diagnostics—as well as our code and data—are available `ANONYMIZED_URL`.
+- **Education vs.
+Charity and humanitarian**: If charitable activities are all education related (e.g., building schools, donating education facilities and books), code as *Education*.
+If activities include other community support (e.g., building bridges, roads, medical facilities), code as *Charity and humanitarian*.
+- **Economy and trade vs. Industry association**: If the trade promoted is focused on a particular industry (e.g., poultry, grains, etc.), code as *Industry association*.
+- **Arts and culture**: Include sports organizations.
+- **Industry association vs.
+Health & Science and technology & Arts and culture**: There are professional associations for health providers, scientific associations, and artistic industries.
+If activities go beyond only serving members only, code as *Health* or *Science and technology* or *Arts and culture*; if activities are limited to member-only service, code as *Industry association*.
+- **Health vs. Charity and humanitarian**: If activities only provide medical assistance to underprivileged communities, code as *Health*.
+- **Charity and humanitarian vs.
+General**: If there are overlapping issue areas (e.g., poverty alleviation, education, health), code as *General*, then code the apparent primary issue area as a second work area.
 
-TODO: Model definition and priors like NVSQ paper
+# References

### 2023-12-07 R/funs_plots_tables.R

@@ -37,6 +37,41 @@ gt_pct <- function(x, page_width = 6) {
   }
 }
 
+build_modelsummary <- function(models) {
+  suppressPackageStartupMessages(library(modelsummary))
+  
+  nice_coefs <- c(
+    "b_Intercept" = "Intercept",
+    "b_issue_arts_and_cultureTRUE" = "Issue [Arts and culture]",
+    "b_issue_educationTRUE" = "Issue [Education]",
+    "b_issue_industry_associationTRUE" = "Issue [Industry association]",
+    "b_issue_economy_and_tradeTRUE" = "Issue [Economy and trade]",
+    "b_issue_charity_and_humanitarianTRUE" = "Issue [Charity and humanitarian]",
+    "b_issue_generalTRUE" = "Issue [General]",
+    "b_issue_healthTRUE" = "Issue [Health]",
+    "b_issue_environmentTRUE" = "Issue [Environment]",
+    "b_issue_science_and_technologyTRUE" = "Issue [Science and technology]",
+    "b_local_connectTRUE" = "Local connections",
+    "b_years_since_law" = "Years since law",
+    "b_year_registered_cat2018" = "Year registered [2018]",
+    "b_year_registered_cat2019" = "Year registered [2019]",
+    "b_year_registered_cat2020" = "Year registered [2020]",
+    "b_year_registered_cat2021" = "Year registered [2021]",
+    "b_local_connectTRUE:years_since_law" = "Local connections × years since law",
+    "phi" = "φ"
+  )
+  
+  msl <- modelsummary(
+    models, 
+    output = "modelsummary_list",
+    statistic = "[{conf.low}, {conf.high}]",
+    ci_method = "hdi",
+    metrics = c("R2")
+  )
+  
+  return(lst(msl, nice_coefs))
+}
+
 
 # Storing ggplot objects as rds files is BAD 
 #   (https://github.com/hadley/ggplot2-book/issues/344)

### 2023-12-07 _targets.R

@@ -91,6 +91,9 @@ list(
   tar_quarto(appendix_manuscripty, path = "manuscript", quiet = FALSE, profile = "appendix-ms"),
   tar_quarto(website, path = ".", quiet = FALSE),
   
+  # Build tables here because they take a while
+  tar_target(models_tbl, build_modelsummary(list(m_full_ordbeta, m_full_ordbeta_interaction))),
+  
   tar_target(deploy_script, here_rel("deploy.sh"), format = "file"),
   tar_target(deploy, {
     # Force a dependency

### 2023-12-07 README.qmd
Add abstract

@@
 
-China’s 2017 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international NGOs (INGOs).
-However, the effects of this global crackdown on INGOs have been difficult to measure since there is often divergence between the formal de jure regulations and the de facto implementation of these laws.
-The enforcement of these laws also depends on the services provided by these organizations.
-In particular, authoritarian regimes display conflicting attitudes towards claim-making (e.g.
-advocacy) INGOs versus service-providing (e.g.
-humanitarian assistance) INGOs.
-In this paper, we measure the effect of China’s ONGO law on INGO operations since 2017.
-We test how INGO operational flexibility under the ONGO law is influenced by organizations’ issue areas.
-We argue that service provision INGOs have greater flexibility and are allowed to work in a larger number of provinces than their claim-making counterparts.
-China provides an excellent setting for testing our claim—the 2017 ONGO law regulates both claim-making and service-providing NGOs, and ambiguity in the law gives ample room for arbitrary discretion by authorities.
-We test our argument using multilevel Bayesian models with administrative data from 635 registered representative offices of INGOs registered in China between 2017–2021.
-Our results speak to the broader literature on closing civic space and provide an empirical illustration of the practical effect of NGO restrictions on global civil society.
+China's 2016 Overseas NGO (ONGO) Law is part of a larger global trend of increased legal restrictions on international nongovernmental organizations (INGOs).
+A growing body of research analyzes the broad effects of this crackdown on INGOs, finding a divergence in formal *de jure* laws and the *de facto* implementation of those laws.
+The causes and mechanisms of this divergence remains less explored.
+Why do authoritarian governments allow—and often collaborate—with some INGOs while harshly regulating or expelling others?
+What determines the openness of the practical legal operating environment for INGOs?
+In this paper, we use the case of China to explore how political demands to both restrict and embrace INGOs have shaped the international nonprofit sector in the five years since the ONGO Law came into effect.
+We argue that in an effort to bolster regime stability, governments use civil society laws as policy tools to influence INGO behavior.
+We find that INGO issue areas, missions, and pre-existing relationships with local government officials influence the degree of operating space available for INGOs.
+We test this argument with a mixed methods research design, combining Bayesian analysis of administrative data from all formally registered INGOs with a comparative case study of two environmental INGOs.
+Our findings offer insights into the practical effects of INGO restrictions and the dynamics of closing civic space worldwide.
 

### 2023-12-07 index.qmd
Add abstract

--- 2023-03-25 index.qmd
@@
 
-Abstract goes here
+China's 2016 Overseas NGO (ONGO) Law is part of a larger global trend of increased legal restrictions on international nongovernmental organizations (INGOs).
+A growing body of research analyzes the broad effects of this crackdown on INGOs, finding a divergence in formal *de jure* laws and the *de facto* implementation of those laws.
+The causes and mechanisms of this divergence remains less explored.
+Why do authoritarian governments allow—and often collaborate—with some INGOs while harshly regulating or expelling others?
+What determines the openness of the practical legal operating environment for INGOs?
+In this paper, we use the case of China to explore how political demands to both restrict and embrace INGOs have shaped the international nonprofit sector in the five years since the ONGO Law came into effect.
+We argue that in an effort to bolster regime stability, governments use civil society laws as policy tools to influence INGO behavior.
+We find that INGO issue areas, missions, and pre-existing relationships with local government officials influence the degree of operating space available for INGOs.
+We test this argument with a mixed methods research design, combining Bayesian analysis of administrative data from all formally registered INGOs with a comparative case study of two environmental INGOs.
+Our findings offer insights into the practical effects of INGO restrictions and the dynamics of closing civic space worldwide.
 

### 2023-12-07 manuscript/manuscript.qmd
Add abstract

@@
 abstract: |
-  TODO: **Update this based on the finished version of the paper.** China’s 2016 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international nongovernmental organizations (INGOs).
-However, the effects of this global crackdown on INGOs have been difficult to measure since there is often divergence between the formal de jure regulations and the de facto implementation of these laws.
-Additionally, the severity and consistency of the enforcement of these laws often depends on the type of services provided by these organizations.
-In this paper, we explore the effect of China’s ONGO law on INGO operations in the five years since the passage of the law.
-We test whether and how INGO operational space under the ONGO law is influenced by organizations' issue areas.
-We argue that the less contentious the issue areas INGOs work in the more likely they are granted greater operational space, measured by the number of provinces they are legally authorized to work in.
-China provides an excellent setting for examining the phenomenon of closing space civic space, since the 2016 ONGO law hypothetically regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities.
-We test our argument by analyzing administrative data from 633 registered representative offices of INGOs registered in China between 2017–2021 and test our hypothesis with a multilevel Bayesian model.
-Our results speak to the broader literature on closing civic space and provide an empirical illustration of the practical effect of NGO restrictions on global civil society.
+  China's 2016 Overseas NGO (ONGO) Law is part of a larger global trend of increased legal restrictions on international nongovernmental organizations (INGOs).
+A growing body of research analyzes the broad effects of this crackdown on INGOs, finding a divergence in formal *de jure* laws and the *de facto* implementation of those laws.
+The causes and mechanisms of this divergence remains less explored.
+Why do authoritarian governments allow—and often collaborate—with some INGOs while harshly regulating or expelling others?
+What determines the openness of the practical legal operating environment for INGOs?
+In this paper, we use the case of China to explore how political demands to both restrict and embrace INGOs have shaped the international nonprofit sector in the five years since the ONGO Law came into effect.
+We argue that in an effort to bolster regime stability, governments use civil society laws as policy tools to influence INGO behavior.
+We find that INGO issue areas, missions, and pre-existing relationships with local government officials influence the degree of operating space available for INGOs.
+We test this argument with a mixed methods research design, combining Bayesian analysis of administrative data from all formally registered INGOs with a comparative case study of two environmental INGOs.
+Our findings offer insights into the practical effects of INGO restrictions and the dynamics of closing civic space worldwide.
 keywords:

### 2023-12-07 manuscript/manuscript.qmd
lol typo in abstract
Add word count

@@
 A growing body of research analyzes the broad effects of this crackdown on INGOs, finding a divergence in formal *de jure* laws and the *de facto* implementation of those laws.
-The causes and mechanisms of this divergence remains less explored.
+The causes and mechanisms of this divergence remain less explored.
 Why do authoritarian governments allow—and often collaborate—with some INGOs while harshly regulating or expelling others?
@@
   - Chinese ONGO law
-word-count: 7984
+word-count: 7,984
 code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/compassionate-clam>"

### 2023-12-07 manuscript/manuscript.qmd
Last-minute tweaks

@@
 - name: Andrew Heiss
-  affiliation: Georgia State University
+  affiliations: 
+    - id: gsu
+      name: Georgia State University
+      department: Andrew Young School of Policy Studies, Department of Public Management and Policy
+      address: "55 Park Place NE, #464"
+      city: Atlanta
+      region: GA
+      country: USA
+      postal-code: 30303
   email: aheiss@gsu.edu
   orcid: 0000-0002-3948-3914
+  attributes:
+    corresponding: true
+correspondence-prefix: "Correspondence concerning this article should be addressed to"
 abstract: |
@@
   - Chinese ONGO law
-word-count: 7,984
+word-count: "7,984"
 code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/compassionate-clam>"
@@
 
-```{r fig-issue-preds, fig.width=8, fig.height=6.5}
+```{r fig-issue-preds, fig.width=8.5, fig.height=7.5}
 #| include: true

### 2023-12-10 manuscript/manuscript.qmd
Add additional statements

@@
 Our findings offer insights into the practical effects of INGO restrictions and the dynamics of closing civic space worldwide.
+additional-info: |
+  **Compliance with Ethical Standards:** This study does not involve human subjects, so the need for participant protection measures such as informed consent, confidentiality, and privacy safeguards was not applicable.
+
+  **Data Availability:** All data and replication code will be made publicly available. Organization names will be omitted for anonymity.
+
+  **Funding:** This research received no external funding.
+
+  **Conflict of Interest:** The authors declare that they have no conflict of interest.
 keywords:

### 2024-01-19 manuscript/manuscript.qmd
revised the Introduction sections
- use clearer explanation of the research questions and how the constructs of de jure and de facto are embedded
- No longer using mixed method

@@
 
-In this paper, we use the case of China to explore how demands to both restrict and embrace INGOs have shaped the international nonprofit sector in the five years since the 2016 ONGO Law came into effect.
-We examine how the ONGO Law has influenced the population of INGOs that have successfully registered in China, as well as the association between factors such as INGO issue areas and the operational space granted to them in the country.
+In this paper, we empirically study the case of China's ONGO Law to explore whether and how *de facto* execution of discretion by the government varies by different types of INGOs while *de jure* regulations are the same.
+Specifically, we analyze how factors including issue areas are associated with the operational space of INGOs, in terms of both successful registration and the geographical scope approved to operate in, drawing from administrative data of the five years since the 2016 ONGO Law came into effect.
 We contribute to a growing body of research on the effects of closing civic space on INGO behavior and strategies.
@@
 General indexes of civil society openness---such as the core civil society index from the Varieties of Democracy project [@LianMurdie:2023; @ChaudhryHeiss:2022]---capture the regulatory environment for civil society more broadly, but do not reflect the specific implementation of laws for INGOs.
-In this paper, we use a mixed methods approach to explore the regulatory environment for INGOs in particular, providing a richer description and analysis of the impact of INGO laws.
+Existing literature on China's ONGO Law mostly discussed the *de jure* legislation around the time when the law was implemented (to add reference) or reports case studies of how selected INGOs navigated the new legal framework shortly after the law took effect (to add reference).
+This paper is the first large N study of all registered INGOs and expands the time frame to the five years enforcement of the ONGO Law, providing insights for both scholars and practitioners on how the operational space of INGOs varies by issue areas and factors such as local connections.
 
@@
 We then synthesize existing research on authoritarian regulation of INGOs and the differential application of these laws based on regime preferences and organizational characteristics, and propose a set of theoretical expectations based on this literature.
-We test these expectations with a mixed methods research design, combining Bayesian analysis of administrative data from all `r nrow(ongo)` formally registered INGOs with a comparative case study of Greenpeace and The Nature Conservancy, two environmental INGOs that took different approaches to operating in China after 2017.
+We test these expectations with descriptive statistics and multilevel Bayesian modeling of administrative data from all `r nrow(ongo)` formally registered INGOs.
+We interpret and discuss the quantitative results by drawing from practical cases of INGOs practical survial strategies under the ONGO Law era.
 We conclude with a broader discussion of authoritarian civil society regulations and propose future approaches for exploring the practical operating environment for INGOs working in such regimes.

### 2024-01-23 manuscript/manuscript.qmd
add citations

@@
 General indexes of civil society openness---such as the core civil society index from the Varieties of Democracy project [@LianMurdie:2023; @ChaudhryHeiss:2022]---capture the regulatory environment for civil society more broadly, but do not reflect the specific implementation of laws for INGOs.
-Existing literature on China's ONGO Law mostly discussed the *de jure* legislation around the time when the law was implemented (to add reference) or reports case studies of how selected INGOs navigated the new legal framework shortly after the law took effect (to add reference).
+Existing literature on China's ONGO Law mostly discussed the *de jure* legislation around the time when the law was implemented [Feng:2017; TeetsHsu:2016] or reports case studies of how selected INGOs navigated the new legal framework shortly after the law took effect [@Li:2020; WuNie:2021].
 This paper is the first large N study of all registered INGOs and expands the time frame to the five years enforcement of the ONGO Law, providing insights for both scholars and practitioners on how the operational space of INGOs varies by issue areas and factors such as local connections.

### 2024-01-23 manuscript/manuscript.qmd
Revised the theoretical sections
Did some radical changes including dropping Ep 3

@@
 We test these expectations with descriptive statistics and multilevel Bayesian modeling of administrative data from all `r nrow(ongo)` formally registered INGOs.
-We interpret and discuss the quantitative results by drawing from practical cases of INGOs practical survial strategies under the ONGO Law era.
-We conclude with a broader discussion of authoritarian civil society regulations and propose future approaches for exploring the practical operating environment for INGOs working in such regimes.
+We interpret and discuss the quantitative results by drawing from cases of INGOs practical survival strategies under the ONGO Law era.
+We conclude with a broader discussion of authoritarian civil society regulations and propose future approaches for understanding the *de facto* operating environment for INGOs working in such regimes.
 
@@
 We term this an INGO's "operational space," or the degree of legal and practical flexibility an organization faces in its target country.
-INGOs with a large amount of operational space can engage in a wider range of programs, address more contentious issues, and enjoy broader geographic scope without fear of interference from the host government, even in the presence of formal *de jure* anti-NGO laws.
+INGOs with a large amount of operational space can engage in a wider range of programs, address more contentious issues, and enjoy broader geographic scope without fear of interference from the host government, even in the presence of formal *de jure* restrictive INGO laws.
 Organizations with less operational space face stricter *de facto* regulatory environments and are more constrained in the programs, strategies, issues, and regions they can work on.
@@
 
-In @fig-theory, we propose that the interplay between INGO characteristics and government preferences is a key determinant of individual INGO operating space [@LiFarid:2023; @ChaudhryHeiss:2021].
-Authoritarian states seek out INGOs that provide direct benefits, while avoiding INGOs that threaten their stability.
+In @fig-theory, we propose that INGOs' issue areas, capturing the the interplay between INGO characteristics and government preferences is a key determinant of individual INGO operating space [@LiFarid:2023; @ChaudhryHeiss:2021].
+INGO laws that are intentionally ambiguous with large room of discretion can serve as policy tools for authoritarian states to seek out INGOs that provide direct benefits, while avoiding INGOs that threaten their stability.
 For instance, states in need of foreign aid and development will be more open to INGOs working on those issues, while states looking for increased trade will seek out INGOs focused on economic partnerships.
@@
 Notably, the arrow between government preferences and issue area is bidirectional, reflecting the government's ability to use civil society regulations to realign INGO programming in the regime's favor, and the INGO's potential ability to reshape government preferences [@Heiss:2019a].
-Finally, the natural scope of an INGO's activities influences its allowed operational space outside of authoritarian stability-seeking calculus.
-Many INGOs purposely keep themselves small, non-confrontational, and non-political and limit themselves to work in only a small part of their target countries, having no plans to go beyond their hyperlocal scope.
-This naturally limits their operational space, but these limits are self-imposed and not directly related to government regulations.
-
-To test the relationships between government preferences, INGO issue area, and INGO operational space, we apply this framework to China's ONGO law.
-Previous research has looked at the practical implementation of civil society laws on a global scale [@LianMurdie:2023; @Chaudhry:2022], which naturally blurs the specific policy mechanisms regimes use for controlling and leveraging global civil society.
+Additionally, the natural scope of an INGO's activities influences its approved operational space outside of authoritarian stability-seeking calculus.
+Many INGOs have a mission that focuses on local issues and communities.
+Also, the timing the of registration and the choice of office location in various provinces with great disparities in socio-economic environment can influence the inherent scope of INGOs.
+We will account for such factors in the study too.
+
+To test the relationships between government preferences, INGO issue area, and INGO operational space, we apply this conceptual model to China's ONGO law.
+Previous research has looked at *A posteriori* (notes: I don't know if it is a correct use of latin words, I want to say how the INGO sector is like in a timeframe after the law) effects of civil society laws on a global scale [@LianMurdie:2023; @Chaudhry:2022], which naturally blurs the specific policy mechanisms regimes use for controlling and leveraging global civil society.
 By analyzing the population of formally registered INGOs between 2017–2021, we can more precisely explore how a single formal anti-INGO law has shaped the operational space for foreign organizations working in the country.
@@
 
-To structure our analysis, we propose a set of theoretical expectations based on @fig-theory.
-First, we expect that INGOs working on non-contentious, regime-aligned issues will have greater reach throughout the country:
-
-> **E~1~**: Because they are seen as less of a threat to regime stability and more aligned with government policy preferences, INGOs working on less contentious issues should be registered in more provinces.
-
-Using the number of provinces an INGO is authorized to work in as a proxy for organizational flexibility and reach might not reflect reality.
-Some INGOs explicitly limit their operations to specific provinces, either because their programming is more tailored to local conditions, or because they do not feel a need to go through the longer process of obtaining national-level registration.
+To structure our analysis, we propose a set of theoretical expectations based on @fig-theory. First, we expect that the *de facto* operational space of INGOs varies by INGO issue areas:
+
+> **E~1~**: Because issue areas reflect varied level of contentiousneeds and government preferences, the number of provinces INGOs are approved to operate in is associated with their issue areas.
+
+We use the number of provinces an INGO is authorized to work in as a proxy for organizational flexibility.
+The rationale is it is preferable for INGOs to have a larger approved geographical operation scope on paper though they may not actually conduct activities there.
+Case studies showed that INGOs such as Oxfam and World Vision went through the cumbersome process to register multiple ROs to  cover all the provinces they need to work in [@Li:2020].
+Their ideal goal is registering an office with authorization to world across China Mainland but was not approved so, ie.
+encountered with more restriction with each registration.
+Moreover, having a larger number approved scope is important for INGOs that want to be prepared to changing target community needs in emergency situations as the COVID-19 and are prudent in legal risk management when the definition of activities is ambuguous under the INGO law.
+
+The exceptions are cases where INGOs have a clear local-oriented focus, such as having a locality name in their registered RO purpose or names.
+Because they do not feel a need to go through the longer process of obtaining national-level registration.
 Accordingly, we temper our issue area expectation with a measure of explicitly local purpose.
@@
 
-Finally, we also expect that the operational space for INGOs is negatively associated with the time elapsed since the law took effect.
-The mechanism behind this expectation is directly related to both issue area and government preferences:
-
-> **E~3~**: Because formal registration can take a long time and can involve many bureaucratic hurdles, INGOs that registered soon after the law took effect should be (1) less of a threat and (2) a higher priority for processing, and so should be registered in more provinces.
+We also took into account the temporal factor, the time elapsed since the law took effect when the ROs got registered.
+Since there was a *de facto* grace period for INGOs to seek registration even though theoretically all existing INGOs should obtain the legal status since Jan.
+1, 2017, the timing of registration for ROs varies greatly.
+More time elapsed since the enforcement of the law can either mean INGOs took more efforts to seek an ideal registration or they faced more difficulty to secure the required consent and approval, so we controlled for this variable.
+We introduced a province fixed effect in the model to account for socio-economic or institutional differences across provinces.
 
@@
 
-We examine these theoretical expectations using a mixed methods approach.
-First, we explore a rich dataset of all ROs registered in China between 2017–2021 using Bayesian regression models to understand how the international civil society in China has been reshaped since the implementation of the ONGO law.
-We then complement this statistical analysis with a comparative case study of two INGOs---The Nature Conservancy and Greenpeace---to explore in detail how the ONGO has specifically influenced organizational operational space.
+We examine these theoretical expectations with a rich dataset of all ROs registered in China between 2017–2021 using Bayesian regression models to understand how the international civil society in China has been reshaped since the implementation of the ONGO law.
 

### 2024-01-24 manuscript/appendix.qmd
Revision of the hypothesis section and below

@@
 
+# Comparison of the cases of TNC and Greenpeace
+
+@tbl-case-study summarizes the cases of TNC and Greenpeace.
+In addition to confirming the correlation between issue area and operational space found in the statistical model, the cases highlight how government preferences exert influence on both the degree of contentious programming INGOs are allowed to undertake and the severity of legal restrictions INGOs can face.
+
+::: {#tbl-case-study}
+
+\footnotesize
+\renewcommand*{\arraystretch}{1.75}
+
+```{r}
+#| label: table-case-study
+#| include: true
+
+compare_table <- read_csv(here::here("data", "manual_data", "table-case-study.csv"))
+
+compare_table |> 
+  gt(rowname_col = "Characteristic") |> 
+  cols_width(Characteristic ~ gt_pct(20), everything() ~ gt_pct(30)) |>
+  tab_style(
+    style = cell_text(v_align = "top"),
+    locations = cells_body()
+  ) |>
+  tab_style(
+    style = cell_text(v_align = "top", weight = "bold"),
+    locations = cells_stub()
+  ) |>
+  opts_theme() |> 
+  tab_options(
+    quarto.disable_processing = TRUE
+  )
+```
+
+Comparison of the work of The Nature Conservancy and Greenpeace in China
+
+:::
+
 # References

### 2024-01-24 manuscript/manuscript.qmd
Revision of the hypothesis section and below

@@
 Previous research has looked at *A posteriori* (notes: I don't know if it is a correct use of latin words, I want to say how the INGO sector is like in a timeframe after the law) effects of civil society laws on a global scale [@LianMurdie:2023; @Chaudhry:2022], which naturally blurs the specific policy mechanisms regimes use for controlling and leveraging global civil society.
-By analyzing the population of formally registered INGOs between 2017–2021, we can more precisely explore how a single formal anti-INGO law has shaped the operational space for foreign organizations working in the country.
-Specifically, we can observe exactly how the Chinese government has used the RO registration process to strategically limit the potential reach of INGOs and reshape their issue areas.
-We use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that, in general, most INGOs desire to engage in work in as broad a geographical scope as possible [@Li:2020].
-For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas might need their service.
-Having the potential to shift programs to other provinces as needed thus provides a form of operational space.
-
-To structure our analysis, we propose a set of theoretical expectations based on @fig-theory. First, we expect that the *de facto* operational space of INGOs varies by INGO issue areas:
-
-> **E~1~**: Because issue areas reflect varied level of contentiousneeds and government preferences, the number of provinces INGOs are approved to operate in is associated with their issue areas.
+By analyzing the population of formally registered INGOs between 2017–2021, we can more precisely explore how a single formal restrictive INGO law has shaped the operational space for foreign organizations working in the country.
+Specifically, we can observe exactly how the Chinese government has used the RO registration process to strategically limit the legal presence and potential reach of INGOs and reshape their issue areas.
+We conducted both a descriptive analysis of the composition of the issue areas of INGOs successfully registered under the INGO law and a regression analysis of the relationshp between INGO issue areas and their operational space.
 
@@
 Case studies showed that INGOs such as Oxfam and World Vision went through the cumbersome process to register multiple ROs to  cover all the provinces they need to work in [@Li:2020].
-Their ideal goal is registering an office with authorization to world across China Mainland but was not approved so, ie.
-encountered with more restriction with each registration.
-Moreover, having a larger number approved scope is important for INGOs that want to be prepared to changing target community needs in emergency situations as the COVID-19 and are prudent in legal risk management when the definition of activities is ambuguous under the INGO law.
-
-The exceptions are cases where INGOs have a clear local-oriented focus, such as having a locality name in their registered RO purpose or names.
+Their ideal goal is registering an office with authorization to work across China Mainland but was not approved so, ie.
+encountered more restriction with each registration.
+Moreover, having a larger number approved scope is important for INGOs that want to be prepared to changing target community needs in emergency situations as the COVID-19 and are prudent in legal risk management when the definition of activities is ambiguous under the INGO law.
+
+Thus, we propose a set of expectations based on the conceptual model in @fig-theory and rationales explained.
+First, we expect that the *de facto* operational space of INGOs varies by INGO issue areas:
+
+> **E~1~**: Because issue areas reflect varied level of contentiousneeds and government preferences, the number of provinces INGOs are approved to operate in is associated with their issue areas.
+
+In cases where INGOs have a clear local-oriented focus, such as having a locality name in their registered RO purpose or names.
 Because they do not feel a need to go through the longer process of obtaining national-level registration.
@@
 We also took into account the temporal factor, the time elapsed since the law took effect when the ROs got registered.
-Since there was a *de facto* grace period for INGOs to seek registration even though theoretically all existing INGOs should obtain the legal status since Jan.
-1, 2017, the timing of registration for ROs varies greatly.
-More time elapsed since the enforcement of the law can either mean INGOs took more efforts to seek an ideal registration or they faced more difficulty to secure the required consent and approval, so we controlled for this variable.
-We introduced a province fixed effect in the model to account for socio-economic or institutional differences across provinces.
+Since there was a *de facto* grace period for INGOs to seek registration even though theoretically all existing INGOs should obtain the legal status right after Jan.
+1, 2017, the timing of registration for ROs varies by years.
+More time elapsed since the enforcement of the law can mean INGOs took more efforts to seek an ideal registration results, and they are more rest-assured to maintain a not-yet-legal status because they do not work in contentious issue areas.
+For example, World Animal Protection has been wording in China since 2007, but they did not register their office until two years after the ONGO Law took effect.
+
+> **E~3~**: Because INGOs taking longer time in registration are less eager to gain legal status and having more time to choose a more ideal registration results, they should be registered in more provinces.
+
+Additionally, we introduced province fixed effects in the model to account for socio-economic or institutional differences across provinces, as well aw registration year fixed effects to account for any potential administrative processing variance during COVID years.
 
@@
 Our data and reproducible code are available at `ANONYMIZED_DOI_URL`.
+
+## Measurement and Descriptive Analysis
 
@@
 Given the subjectivity in the coding process, we cross-checked our manual coding of issue areas (see the appendix for a description of our coding).
-We categorize each organization into nine different issue areas (see @tbl-issues).
+We use a grounded approach and categorize each organization into nine different issue areas (see @tbl-issues).
 @fig-issue-props shows the distribution of these issue areas.
@@
 Charitable, humanitarian, education, and health INGOs are far less common than their trade and industry counterparts: charity and humanitarian organizations comprise `r issues$charity_and_humanitarian$prop_nice` (`r issues$charity_and_humanitarian$n`) of ROs.
+
+The composition of INGOs successfully got registered under the ONGO law shows that the populations of INGOs that are allowed a long-standing legal presence are predominantly trade and economic organisations and industry associations, or non-civil-society organizations.
 
@@
 
+(To do - Andrew: update the paragraph below with more explanations/justifications? )
 We use a multilevel Bayesian regression model to examine the complex effects that issue area, local connections, and registration timing have on organizational flexibility.
@@
 
-Since we are primarily interested in the influence of INGO's issue area, its local connections, and the timing of its registration on its operational space, we include these as explanatory variables.
+*Since we are primarily interested in the influence of INGO's issue area, its local connections, and the timing of its registration on its operational space, we include these as explanatory variables.
 We also include random province intercepts to account for between-region differences in how INGOs are regulated, since every RO is overseen by provincial-level Public Security Bureaus.
-The appendix contains complete details of our modeling approach, priors, model definition, and tables of raw results.
+The appendix contains complete details of our modeling approach, priors, model definition, and tables of raw results.*
+
+***To discuss this whole paragraph and add model formulas back***
 
@@
 ## Model results
+
+*add the discussion of "significance level, or the interpretation of credible intervals. That is move some of the notes to the figure to the main text?"*
 
@@
 
+The officially-endorsed environmental issue area in China is also less contentious.
+Take the The Nature Conservancy (TNC) and Greenpeace for example.
+They both well-known environmental INGOs with headquarters in Western countries.
+They each began working in China around the turn of the century, with TNC establishing an office in Beijing in 1998 and Greenpeace in 2001.
+However, one key difference in these two organizations is their working model and alignment with government preferences.
+TNC has stated that its work is "science-based" and that the organization uses a "non-confrontational, collaborative approach in working closely with governments, the business community and others" [@ChinaPhilanthropyResearchInstitute:2018a].In contrast, Greenpeace engages in direct advocacy, using peaceful---but confrontational---protests to expose environmental abuses and shame governments and for-profit corporations that harm the environment.
+The organization describes its work in China with phrases like "non-violent direct action," "impartiality and independence," and "brings change," indicating its dedication to maintaining organizational independence as it acts as an environmental watchdog [@Greenpeace:2023].
+Being the more contentious type of environment results in a contrasting fate for the Greenpeace from TNC.
+TNC obtained RO status in May 2017, partnering with the National Forestry and Grassland Administration as their PSU, and receiving authorization to work in 27 provinces.
+In contrast, Greenpeace has not received RO status and has instead filed 67 temporary activities, submitting new documentation more than ten times each year.
+Not only this means much limited operational space - only in the location of the activity - but also higher level of uncertainty and administrative costs.
+[@Plantan:2022] also found environmental organizations in China "increasingly align with central party-state priorities on environmental protection" and are intended to help bolster political stability.
+So the successfully registered environmental organizations are less contentious in China.
+
 ### Local connections
@@
 By the end of 2021 the probability of national-level registration increases to `r p_timing$x2022.all_32_provinces$prop_ci_nice` while the probability of working in a range of provinces increases to predicted to work in two or more provinces remains around `r p_timing$x2022.between_1_32_provinces$prop_ci_nice`.
-These later INGOs are the least likely to be registered in only one province, with a probability of `r p_timing$x2022.only_1_province$prop_ci_nice`.
+These later INGOs are the least likely to 8be registered in only one province, with a probability of `r p_timing$x2022.only_1_province$prop_ci_nice`.
 @fig-timing-preds(b) demonstrates the expected count of provinces over five years since 2017.
@@
 
-We lack sufficient theory to explain why this trend goes against our expectations, but we can again make reasonable speculations.
-As we saw previously with INGOs and local connections, organizations appear to strategically seek out the best avenues for registering [@Jia:2017a].
+To do: update the discussion according to the new Expectation 3
+
+*We lack sufficient theory to explain why this trend goes against our expectations, but we can again make reasonable speculations.* As we saw previously with INGOs and local connections, organizations appear to strategically seek out the best avenues for registering [@Jia:2017a].
 Organizations that participated in the initial wave of registrations in 2017 likely had closer connections with local officials and were able to speed through the bureaucratic process registration more easily.
@@
 
-## Contentiousness and government relationships: The cases of The Nature Conservancy and Greenpeace
-
-The results from our model provide useful insight into the operational space of INGOs that have been able to formally register.
-These organizations have been pre-screened and deemed to be safe and non-contentious.
-This can help explain why some seemingly more contentious issue areas such as environmental INGOs enjoy relatively more operational space (see @fig-issue-preds).
-Since Chinese authorities can benefit politically from the work of environmental INGOs, they "selectively encourage low risk groups and selectively channel higher risk groups into permitted areas" [@Plantan:2022, 504].
-Using our data, however, we are unable to make comparisons with already-vetted INGOs and other potentially more contentious organizations, which limits our analysis of the determinants of operational space.
-To address this, we compare the cases of two environmental INGOs: (1) The Nature Conservancy (TNC), which successfully registered as RO under the ONGO Law, and (2) Greenpeace, which has filed dozens of sequential temporary activities.
-
-TNC and Greenpeace are both well-known environmental INGOs.
-Both are based in Western countries and have offices around the world.
-They each began working in China around the turn of the century, with TNC establishing an office in Beijing in 1998 and Greenpeace in 2001.
-Despite these similarities, the two INGOs have had quite different experiences in maintaining their legal presence in China after the ONGO Law took effect.
-TNC obtained RO status in May 2017, partnering with the National Forestry and Grassland Administration as their PSU, and receiving authorization to work in 27 provinces.
-In contrast, Greenpeace has not received RO status and has instead filed 67 temporary activities, submitting new documentation more than ten times each year.
-
-Repeatedly filing temporary activities has become a common alternative method for INGOs like Greenpeace to maintain long-term presence in China [@Corsetti:2019].
-However, choosing a legal channel originally designed for one-off programs results in far more limited INGO operational space than under RO regulations (recall @fig-ro-ta-pathways).
-Securing a new partnership with a Chinese organization for each activity and co-filing the requisite paperwork imposes substantial administrative costs.
-This approach also creates high uncertainty, since there is no guarantee that a current partner organization would agree to repeat their role for the next project.
-Moreover, INGO programming has an inherent short-term focus, given that temporary activities cannot last longer than a year.
-Finally, temporary activities need to focus on safe activities with few political risks in order to attract potential Chinese partners.
-
-One key difference in these two organizations' differing registration strategies is their relationship with the government and alignment with government preferences.
-TNC has stated that its work is "science-based" and that the organization uses a "non-confrontational, collaborative approach in working closely with governments, the business community and others" [@ChinaPhilanthropyResearchInstitute:2018a].
-Over its past two decades of work in China, TNC has provided technical support for the central government and local governments in Yunnan and Zhejiang Provinces, consulting on policies that have led to the establishment of national parks and nature reserves, and helping draft environmental policy proposals like the China National Biodiversity Conservation Strategy and Action Plan (2011–2030) [@TheNatureConservancy:2023].
-This deliberately non-confrontational model, coupled with long-established partnerships with the government enabled TNC to secure the consent of a environment-focused national governmental agency to act as their PSU, which in turn allowed TNC to have a wider geographic reach throughout the country.
-Moreover, TNC's work with local and national governments has generally been aligned with government preferences and directly benefits the regime.
-
-In contrast, Greenpeace engages in direct advocacy, using peaceful---but confrontational---protests to expose environmental abuses and shame governments and for-profit corporations that harm the environment.
-The organization describes its work in China with phrases like "non-violent direct action," "impartiality and independence," and "brings change," indicating its dedication to maintaining organizational independence as it acts as an environmental watchdog [@Greenpeace:2023].
-In 2004, for instance, Greenpeace conducted three rounds of independent investigations into damages caused by the Sinar Mas Group, revealing how the Asian multinational corporation used promises of reforestation work as a cover while logging natural forests in Yunnan [@Greenpeace:2022].
-Greenpeace's ongoing independent advocacy work is often at odds with regime preferences, and from the government's perspective, its Chinese programming is unpredictable and less directly manageable.
-As a result, few potential PSUs have shown interest in sponsoring any potential registration attempt, and Greenpeace has chosen to work through repeated temporary activities rather than trying to gain RO status.
-
-@tbl-case-study summarizes the cases of TNC and Greenpeace.
-In addition to confirming the correlation between issue area and operational space found in the statistical model, the cases highlight how government preferences exert influence on both the degree of contentious programming INGOs are allowed to undertake and the severity of legal restrictions INGOs can face.
-
-::: {#tbl-case-study}
-
-\footnotesize
-\renewcommand*{\arraystretch}{1.75}
-
-```{r}
-#| label: table-case-study
-#| include: true
-
-compare_table <- read_csv(here::here("data", "manual_data", "table-case-study.csv"))
-
-compare_table |> 
-  gt(rowname_col = "Characteristic") |> 
-  cols_width(Characteristic ~ gt_pct(20), everything() ~ gt_pct(30)) |>
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) |>
-  tab_style(
-    style = cell_text(v_align = "top", weight = "bold"),
-    locations = cells_stub()
-  ) |>
-  opts_theme() |> 
-  tab_options(
-    quarto.disable_processing = TRUE
-  )
-```
-
-Comparison of the work of The Nature Conservancy and Greenpeace in China
-
-:::
-
 # Conclusion
@@
 Studying INGOs in authoritarian regimes poses a number of limitations, but the concept of operational space can address some of these issues in the future.
-First, we can only observe organizations that successfully registered as ROs.
-We cannot make comparisons with INGOs that left the country prior to 2017 or INGOs that have explicitly chosen to not work in China.
+The results from our model provide useful insight into the operational space of INGOs that have been able to formally register.
+These organizations have been pre-screened and deemed to be safe and non-contentious.
+This can help explain why some seemingly more contentious issue areas such as environmental INGOs enjoy relatively more operational space (see @fig-issue-preds).
+Since Chinese authorities can benefit politically from the work of environmental INGOs, they "selectively encourage low risk groups and selectively channel higher risk groups into permitted areas" [@Plantan:2022, 504].
+But given the focus of this paper on registered ROs, we cannot make comparisons with INGOs that left the country prior to 2017 or INGOs that have explicitly chosen to not work in China.
 This is not an issue specific to China---analyzing the international nonprofit sector of any country that has passed similar laws will raise similar issues of selection bias.

### 2024-02-23 manuscript/manuscript.qmd
Some initial minor changes

@@
 short-title: "Enforcing Boundaries"
-date: "2023-12-07"
+date: "2024-02-23"
 author:
@@
 General indexes of civil society openness---such as the core civil society index from the Varieties of Democracy project [@LianMurdie:2023; @ChaudhryHeiss:2022]---capture the regulatory environment for civil society more broadly, but do not reflect the specific implementation of laws for INGOs.
-Existing literature on China's ONGO Law mostly discussed the *de jure* legislation around the time when the law was implemented [Feng:2017; TeetsHsu:2016] or reports case studies of how selected INGOs navigated the new legal framework shortly after the law took effect [@Li:2020; WuNie:2021].
-This paper is the first large N study of all registered INGOs and expands the time frame to the five years enforcement of the ONGO Law, providing insights for both scholars and practitioners on how the operational space of INGOs varies by issue areas and factors such as local connections.
+Existing literature on China's ONGO Law mostly discussed the *de jure* legislation around the time when the law was implemented [@Feng:2017; @TeetsHsu:2016] or reports case studies of how selected INGOs navigated the new legal framework shortly after the law took effect [@Li:2020; @WuNie:2021].
+We contribute to this body of work by offering a quantitative analysis of *all* registered organizations across the first five years of enforcement of the ONGO Law, providing insights for both scholars and practitioners on how the operational space of INGOs varies by organizational factors and political context.
 

### 2024-02-23 manuscript/manuscript.qmd
Update theory section

@@
 
-```{r fig-theory, fig.width=6, fig.height=1.75}
+```{r fig-theory, fig.width=6, fig.height=2}
 #| echo: false
@@
   ~id, ~name,                         ~x,   ~y, ~highlight,
-  1,   "Issue contentiousness", 2, 1, FALSE,
-  2,   "Operational space", 2, 0, TRUE,
-  3,   "Local focus", 3, 1, FALSE,
-  4,   "Government preferences", 1, 1, FALSE
+  1,   "INGO operational space",      2,    1,  "Outcome",
+  2,   "INGO issue\ncontentiousness", 2,    3,  "INGO",
+  3,   "INGO preferences\nand resources", 2.5,    2,  "INGO",
+  4,   "Government\npreferences",     1,    3,  "Government",
+  5,   "Enforcement of law",          1.5,  2,  "Government"
 )
@@
   ~from, ~to,
-  1, 2,
   3, 1,
-  3, 2,
-  1, 4,
-  4, 1,
-  4, 2
+  5, 1,
+  2, 4,
+  4, 2,
+  4, 5,
+  2, 5
 )
@@
     aes(
-      start_cap = label_rect(node1.name, padding = margin(10, 0, 10, -05, "pt")),
-      end_cap = label_rect(node2.name, padding = margin(10, -5, 10, -5, "pt"))
+      start_cap = label_rect(node1.name, padding = margin(6, 0, 6, 0, "pt")),
+      end_cap = label_rect(node2.name, padding = margin(6, 0, 6, 0, "pt"))
     ),
-    arrow = arrow(angle = 30, length = unit(6, "pt"), type = "closed"),
+    arrow = arrow(angle = 30, length = unit(4, "pt"), type = "closed"),
     edge_linewidth = 0.25
@@
   geom_node_label(
-    aes(x = x, y = y, label = name, fill = highlight), 
-    size = 3, label.r = unit(0, units = "pt"), fontface = "bold"
+    aes(x = x, y = y, label = name, fill = highlight, color = highlight), 
+    size = 3, label.r = unit(0, units = "pt"), fontface = "bold", lineheight = 1, label.size = NA
   ) +
@@
   scale_y_continuous(expand = expansion(add = 0.2)) +
-  scale_fill_manual(values = c("white", clrs[1]), guide = "none") +
+  scale_fill_manual(values = 
+      c("Government" = clrs[7], "INGO" = clrs[5], "Outcome" = clrs[1]), 
+    guide = "none"
+  ) +
+  scale_color_manual(values = 
+      c("Government" = "white", "INGO" = "white", "Outcome" = "black"), 
+    guide = "none"
+  ) +
   labs(x = NULL, y = NULL) +
@@
     panel.border = element_blank(),
-    axis.text = element_blank(),
-  )
-```
-
-In @fig-theory, we propose that INGOs' issue areas, capturing the the interplay between INGO characteristics and government preferences is a key determinant of individual INGO operating space [@LiFarid:2023; @ChaudhryHeiss:2021].
-INGO laws that are intentionally ambiguous with large room of discretion can serve as policy tools for authoritarian states to seek out INGOs that provide direct benefits, while avoiding INGOs that threaten their stability.
-For instance, states in need of foreign aid and development will be more open to INGOs working on those issues, while states looking for increased trade will seek out INGOs focused on economic partnerships.
-Because their primary issue areas are aligned with regime preferences, INGOs benefit from greater operational space and face fewer restrictions.
+    axis.text = element_blank()
+  )
+```
+
+We sketch this relationship in @fig-theory, which demonstrates several key determinants of INGO operating space in authoritarian contexts.
+The left half of the diagram illustrates how the interplay of government preferences and INGO issue areas shapes how the government enforces its civil society laws, which in turn helps determine how much operating space an INGO can enjoy.
+In general, the alignment of an INGO's programming with government preferences determines how laws are enforced, which in turn helps determine how much operating space an INGO can enjoy.
+INGO laws that are intentionally ambiguous with large room for discretion can serve as policy tools for authoritarian states to seek out INGOs that provide direct benefits, while avoiding INGOs that threaten their stability [@LiFarid:2023; @ChaudhryHeiss:2021].
+For instance, states in need of foreign aid and development assistance will be more open to INGOs working on those issues, while states looking for increased trade will seek out INGOs focused on economic partnerships.
+Because their primary issue areas are aligned with regime preferences, the practical *de facto* enforcement of civil society will be less strict and INGOs will benefit from greater operational space and face fewer restrictions.
 In contrast, states engaged in human rights abuses or fearful of foreign influence over other domestic policies will reduce---or even close---the operational space allowed for INGOs addressing these issues.
-Notably, the arrow between government preferences and issue area is bidirectional, reflecting the government's ability to use civil society regulations to realign INGO programming in the regime's favor, and the INGO's potential ability to reshape government preferences [@Heiss:2019a].
-Additionally, the natural scope of an INGO's activities influences its approved operational space outside of authoritarian stability-seeking calculus.
-Many INGOs have a mission that focuses on local issues and communities.
-Also, the timing the of registration and the choice of office location in various provinces with great disparities in socio-economic environment can influence the inherent scope of INGOs.
-We will account for such factors in the study too.
+Notably, the arrow between government preferences and issue area is bidirectional.
+Restrictive civil society regulations create a population of allowed INGOs aligned with government preferences, either by attracting safe and noncontentious organizations, or by encouraging potentially contentious organizations to "tame" their programming [@Bush:2015].
+Conversely, once allowed in the country, INGOs can reshape government views and policies regarding both their given issue areas and civil society regulations more broadly [@Teets:2014; @Heiss:2019a].
+
+The right half of @fig-theory illustrates alternative determinants of INGO operational space that lie outside of organizations' potential contentiousness or relationships with the government.
+INGO preferences—that is, the strategy, mission, and goals—influence how much operational space is available in host countries.
+For instance, many INGOs have missions focused on local issues and communities—they work on specific projects with naturally limited scopes and have no need to expand their work.
+An INGO's available resources also determine its in-country flexibility.
+An organization with more funding, more employees, more connections with local regulators or politicians, or other types of resources can benefit from additional flexibility when working in its host country by, for instance, enjoying greater geographic access, more leeway in adherence to regulations, or a wider menu of possible strategies available to accomplish its mission.
+Organizations with fewer resources, on the other hand, will have more limited operational space.
 

### 2024-02-24 manuscript/manuscript.qmd
Switch to JSON-based references for better APA capitalization

@@
 code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/compassionate-clam>"
-bibliography: references.bib
+bibliography: references.json
 link-citations: true

### 2024-02-24 manuscript/manuscript.qmd
Add caveats for research design
Why we're only looking at ROs and why that's okay

@@
 set_annotation_fonts()
+
+# Manual TA stuff from other paper
+n_ongos_ta <- 1019
+n_ta <- 4011
 ```
@@
 INGOs undertaking temporary activities also need to find an eligible Chinese partner---including governmental, quasi-governmental, or non-profit organizations---and must keep their programs within approved limits, but the process is less onerous.
+According to data from the Chinese Ministry of Public Security and ChinaFile [@ChinaFile:2022], between January 1, 2017 and December 31, 2021, `r nrow(ongo)` organizations obtained RO status, while `r scales::label_comma()(n_ongos_ta)` organizations submitted documentation for `r scales::label_comma()(n_ta)`.
+Nearly twice as many INGOs have opted for an easier, but far more restricted, pathway for legally operating in China.
 
@@
 Specifically, we can observe exactly how the Chinese government has used the RO registration process to strategically limit the legal presence and potential reach of INGOs and reshape their issue areas.
-We conducted both a descriptive analysis of the composition of the issue areas of INGOs successfully registered under the INGO law and a regression analysis of the relationshp between INGO issue areas and their operational space.
+We conducted both a descriptive analysis of the composition of the issue areas of INGOs successfully registered under the INGO law and a regression analysis of the relationship between INGO issue areas and their operational space.
 
@@
 
-> **E~1~**: Because issue areas reflect varied level of contentiousneeds and government preferences, the number of provinces INGOs are approved to operate in is associated with their issue areas.
+> **E~1~**: Because issue areas reflect varied level of contentiousness and government preferences, the number of provinces INGOs are approved to operate in is associated with their issue areas.
 
@@
 We also took into account the temporal factor, the time elapsed since the law took effect when the ROs got registered.
-Since there was a *de facto* grace period for INGOs to seek registration even though theoretically all existing INGOs should obtain the legal status right after Jan.
-1, 2017, the timing of registration for ROs varies by years.
+Since there was a *de facto* grace period for INGOs to seek registration even though theoretically all existing INGOs should obtain the legal status right after January 1, 2017, the timing of registration for ROs varies by years.
 More time elapsed since the enforcement of the law can mean INGOs took more efforts to seek an ideal registration results, and they are more rest-assured to maintain a not-yet-legal status because they do not work in contentious issue areas.
@@
 
-Additionally, we introduced province fixed effects in the model to account for socio-economic or institutional differences across provinces, as well aw registration year fixed effects to account for any potential administrative processing variance during COVID years.
+Additionally, we introduced province fixed effects in the model to account for socio-economic or institutional differences across provinces, as well as registration year fixed effects to account for any potential administrative processing variance during COVID years.
+
+Before testing these expectations, we must first note a few important caveats.
+As discussed previously, international NGOs have two avenues for legally working in China: (1) formal registration as an RO and (2) ad hoc temporary activity (TA) status.
+The RO process is more costly and requires far more administrative and legal work, and as a result, nearly twice as many organizations have used temporary activities rather than formal registration.
+In this study, however, we do not look at patterns in TA use to explore INGO operational space.
+There is an incredible amount of variation in how TAs are used.
+Some organizations submit dozens of TA requests, possibly as a type of workaround to obtaining RO status, while others use them as true temporary activities, submitting requests for one-off conferences or workshops.
+INGOs using TAs thus do not work well as a test case of the relationship between INGO operational space and the de facto implementation of the ONGO law.
+More permanent ROs are more appropriate.
+Additionally, we cannot observe or measure the activities of INGOs that have not attempted to establish operations in the country or who left the country following the implementation of the ONGO law in 2017.
+The population of INGOs working with full, permanent legal status is thus limited only to organizations that have already been vetted as "safe" and acceptable by the government.
+Even under these conditions, though, we should expect to see variation in operational space, due to heterogeneity in both (1) government preferences and INGO issues (i.e.
+not all registered INGOs work on the same issues, and not all issues are of equal value or importance to the regime), and (2) INGO preferences and resources (i.e.
+not all INGOs have the same goals, missions, or resources).
 
@@
 The filing documents for ROs disclose each INGO's name, address, registration date, regulating Public Security Bureau, PSU, issue area and purposes of the RO, and the specific provinces they can work in.
-We merge this INGO data with translated English organization names from ChinaFile.
+We merge this INGO data with translated English organization names from ChinaFile [@ChinaFile:2022].
 Our data and reproducible code are available at `ANONYMIZED_DOI_URL`.
 
-## Measurement and Descriptive Analysis
+## Measurement and descriptive analysis
 

### 2024-02-24 manuscript/manuscript.qmd
Expanded introduction to E1

@@
 The causes and mechanisms of this divergence remain less explored.
-Why do authoritarian governments allow—and often collaborate—with some INGOs while harshly regulating or expelling others?
+Why do authoritarian governments allow---and often collaborate---with some INGOs while harshly regulating or expelling others?
 What determines the openness of the practical legal operating environment for INGOs?
@@
 Restrictive civil society regulations create a population of allowed INGOs aligned with government preferences, either by attracting safe and noncontentious organizations, or by encouraging potentially contentious organizations to "tame" their programming [@Bush:2015].
-Conversely, once allowed in the country, INGOs can reshape government views and policies regarding both their given issue areas and civil society regulations more broadly [@Teets:2014; @Heiss:2019a].
+Conversely, once allowed in the country, INGOs are not always passive victims of regulations and can, under particular conditions, reshape government views and policies regarding both their given issue areas and civil society regulations more broadly [@Teets:2014; @Heiss:2019a].
 
 The right half of @fig-theory illustrates alternative determinants of INGO operational space that lie outside of organizations' potential contentiousness or relationships with the government.
-INGO preferences—that is, the strategy, mission, and goals—influence how much operational space is available in host countries.
-For instance, many INGOs have missions focused on local issues and communities—they work on specific projects with naturally limited scopes and have no need to expand their work.
+An INGO's preferences---that is, its strategy, mission, and goals---also influence how much operational space is available in host countries.
+For instance, many INGOs have missions focused on local issues and communities---they work on specific projects with naturally limited scopes and have no need to expand their work.
+The nature of an organization's programming also influences its reach and flexibility: a human rights advocacy organization interested in holding a national government accountable for civil liberties abuses will have a much broader geographic and political scope---and thus require greater operational flexibility---than an education organization interested in supporting a handful of primary schools.
 An INGO's available resources also determine its in-country flexibility.
@@
 Organizations with fewer resources, on the other hand, will have more limited operational space.
-
-To test the relationships between government preferences, INGO issue area, and INGO operational space, we apply this conceptual model to China's ONGO law.
+These organization-level determinants can be seen as independent of government preferences
+
+To test the relationships between government preferences, INGO issue area, INGO characteristics, and operational space, we apply this conceptual model to China's 2017 ONGO law.
 Previous research has looked at *A posteriori* (notes: I don't know if it is a correct use of latin words, I want to say how the INGO sector is like in a timeframe after the law) effects of civil society laws on a global scale [@LianMurdie:2023; @Chaudhry:2022], which naturally blurs the specific policy mechanisms regimes use for controlling and leveraging global civil society.
 By analyzing the population of formally registered INGOs between 2017–2021, we can more precisely explore how a single formal restrictive INGO law has shaped the operational space for foreign organizations working in the country.
-Specifically, we can observe exactly how the Chinese government has used the RO registration process to strategically limit the legal presence and potential reach of INGOs and reshape their issue areas.
+Specifically, we can observe exactly how the Chinese government has used the RO registration process to strategically limit and reshape these organizations' operational space.
 We conducted both a descriptive analysis of the composition of the issue areas of INGOs successfully registered under the INGO law and a regression analysis of the relationship between INGO issue areas and their operational space.
 
-We use the number of provinces an INGO is authorized to work in as a proxy for organizational flexibility.
-The rationale is it is preferable for INGOs to have a larger approved geographical operation scope on paper though they may not actually conduct activities there.
-Case studies showed that INGOs such as Oxfam and World Vision went through the cumbersome process to register multiple ROs to cover all the provinces they need to work in [@Li:2020].
-Their ideal goal is registering an office with authorization to work across China Mainland but was not approved so, ie.
-encountered more restriction with each registration.
-Moreover, having a larger number approved scope is important for INGOs that want to be prepared to changing target community needs in emergency situations as the COVID-19 and are prudent in legal risk management when the definition of activities is ambiguous under the INGO law.
-
-Thus, we propose a set of expectations based on the conceptual model in @fig-theory and rationales explained.
-First, we expect that the *de facto* operational space of INGOs varies by INGO issue areas:
-
-> **E~1~**: Because issue areas reflect varied level of contentiousness and government preferences, the number of provinces INGOs are approved to operate in is associated with their issue areas.
-
-In cases where INGOs have a clear local-oriented focus, such as having a locality name in their registered RO purpose or names.
-Because they do not feel a need to go through the longer process of obtaining national-level registration.
-Accordingly, we temper our issue area expectation with a measure of explicitly local purpose.
-Organizations that have no intention of registering nationally should be registered in fewer provinces:
-
-> **E~2~**: Because they are explicitly focused on local issues, INGOs with explicitly local missions should be registered in fewer provinces.
-
-We also took into account the temporal factor, the time elapsed since the law took effect when the ROs got registered.
-Since there was a *de facto* grace period for INGOs to seek registration even though theoretically all existing INGOs should obtain the legal status right after January 1, 2017, the timing of registration for ROs varies by years.
-More time elapsed since the enforcement of the law can mean INGOs took more efforts to seek an ideal registration results, and they are more rest-assured to maintain a not-yet-legal status because they do not work in contentious issue areas.
-For example, World Animal Protection has been wording in China since 2007, but they did not register their office until two years after the ONGO Law took effect.
-
-> **E~3~**: Because INGOs taking longer time in registration are less eager to gain legal status and having more time to choose a more ideal registration results, they should be registered in more provinces.
-
-Additionally, we introduced province fixed effects in the model to account for socio-economic or institutional differences across provinces, as well as registration year fixed effects to account for any potential administrative processing variance during COVID years.
-
-Before testing these expectations, we must first note a few important caveats.
+Before defining our expectations, though, we must first note a few important caveats.
 As discussed previously, international NGOs have two avenues for legally working in China: (1) formal registration as an RO and (2) ad hoc temporary activity (TA) status.
@@
 not all INGOs have the same goals, missions, or resources).
+
+We use the number of provinces an INGO is authorized to work in as a proxy for organizational flexibility.
+While this is not a perfect measure---geographic scope is only one possible aspect of INGO operational space---it is an element of INGO flexibility that is directly influenced by China's ONGO law.
+Since INGOs are required to seek out separate PSUs for each province they are interested in working in, the count of authorized provinces partially reflects the alignment of INGO services with government preferences.
+Having a larger geographic scope provides concrete forms of INGO flexibility, like being able to more rapidly respond to changing needs in emergency situations such as the COVID-19 pandemic (e.g., a health-focused INGO can redirect staff to a province facing an outbreak), and allowing for a more diversified range of programs to assist with legal risk management when the definition of INGO activities is ambiguous (e.g., an INGO can pull back its work in a province if the relationship with its PSU sours).
+Previous work has shown that INGOs in China often work to maximize their geographic scope, even if they have no current plans to conduct activities nationwide.
+For instance, Oxfam and World Vision went through the cumbersome process to register multiple ROs to cover all the provinces they need to work in, and despite their goal of registering across mainland China, they faced increased bureaucratic hurdles and restriction with each registration [@Li:2020].
+Based on @fig-theory, we posit that the alignment of government preferences and INGO services---represented by to contentiousness of an INGO's main issue area---helps determine INGO operational space.
+We thus expect that the number of provinces an organization is authorized to work in varies by INGO issue area:
+
+> **E~1~**: Because issue areas reflect varied level of contentiousness and government preferences, the number of provinces INGOs are approved to operate in is associated with the contentiousness of their issue areas.
+
+In cases where INGOs have a clear local-oriented focus, such as having a locality name in their registered RO purpose or names.
+Because they do not feel a need to go through the longer process of obtaining national-level registration.
+Accordingly, we temper our issue area expectation with a measure of explicitly local purpose.
+Organizations that have no intention of registering nationally should be registered in fewer provinces:
+
+> **E~2~**: Because they are explicitly focused on local issues, INGOs with explicitly local missions should be registered in fewer provinces.
+
+We also took into account the temporal factor, the time elapsed since the law took effect when the ROs got registered.
+Since there was a *de facto* grace period for INGOs to seek registration even though theoretically all existing INGOs should obtain the legal status right after January 1, 2017, the timing of registration for ROs varies by years.
+More time elapsed since the enforcement of the law can mean INGOs took more efforts to seek an ideal registration results, and they are more rest-assured to maintain a not-yet-legal status because they do not work in contentious issue areas.
+For example, World Animal Protection has been wording in China since 2007, but they did not register their office until two years after the ONGO Law took effect.
+
+> **E~3~**: Because INGOs taking longer time in registration are less eager to gain legal status and having more time to choose a more ideal registration results, they should be registered in more provinces.
+
+Additionally, we introduced province fixed effects in the model to account for socio-economic or institutional differences across provinces, as well as registration year fixed effects to account for any potential administrative processing variance during COVID years.
 
@@
 
-*add the discussion of "significance level, or the interpretation of credible intervals. That is move some of the notes to the figure to the main text?"*
+*add the discussion of "significance level, or the interpretation of credible intervals.
+That is move some of the notes to the figure to the main text?"* - explain credible intervals and how it shows us the whole distribution and is more actionable than confidence intervals and trying to get a single parameter.
+The point of this whole model is to paint a broad picture of the whole situation.
 

### 2024-02-26 manuscript/manuscript.qmd
Update explanation for E2

@@
 Previous work has shown that INGOs in China often work to maximize their geographic scope, even if they have no current plans to conduct activities nationwide.
-For instance, Oxfam and World Vision went through the cumbersome process to register multiple ROs to cover all the provinces they need to work in, and despite their goal of registering across mainland China, they faced increased bureaucratic hurdles and restriction with each registration [@Li:2020].
+For instance, Oxfam and World Vision went through the cumbersome process to register multiple ROs to cover all the provinces they might potentially work in, and despite their goal of registering across mainland China, they faced increased bureaucratic hurdles and restriction with each registration [@Li:2020].
 Based on @fig-theory, we posit that the alignment of government preferences and INGO services---represented by to contentiousness of an INGO's main issue area---helps determine INGO operational space.
@@
 
-In cases where INGOs have a clear local-oriented focus, such as having a locality name in their registered RO purpose or names.
-Because they do not feel a need to go through the longer process of obtaining national-level registration.
-Accordingly, we temper our issue area expectation with a measure of explicitly local purpose.
-Organizations that have no intention of registering nationally should be registered in fewer provinces:
+As shown in @fig-theory, organization-level characteristics like internal preferences and resources are also determinants of INGO operational space.
+Since we measure organizational flexibility with a count of authorized provinces, we temper our expectations in E~1~ by analyzing organizational preferences related to geography.
+Not all INGOs seek to maximize their geographic reach.
+Organizations that explicitly limit their work to specific provinces or that work on issues that naturally lend themselves to a more limited scope (e.g., an INGO that supports educational services in one province) should be registered in fewer provinces:
 

### 2024-02-27 manuscript/manuscript.qmd
More in theory section + some initial modeling caveats

@@
 The nature of an organization's programming also influences its reach and flexibility: a human rights advocacy organization interested in holding a national government accountable for civil liberties abuses will have a much broader geographic and political scope---and thus require greater operational flexibility---than an education organization interested in supporting a handful of primary schools.
-An INGO's available resources also determine its in-country flexibility.
+An INGO's available resources also determine its in-country operational space.
+These organization-level determinants are independent of host government preferences and represent possible resources an INGO can draw on based on the laxity or strictness of the *de facto* enforcement of civil society laws in a country.
 An organization with more funding, more employees, more connections with local regulators or politicians, or other types of resources can benefit from additional flexibility when working in its host country by, for instance, enjoying greater geographic access, more leeway in adherence to regulations, or a wider menu of possible strategies available to accomplish its mission.
 Organizations with fewer resources, on the other hand, will have more limited operational space.
-These organization-level determinants can be seen as independent of government preferences
 
 To test the relationships between government preferences, INGO issue area, INGO characteristics, and operational space, we apply this conceptual model to China's 2017 ONGO law.
-Previous research has looked at *A posteriori* (notes: I don't know if it is a correct use of latin words, I want to say how the INGO sector is like in a timeframe after the law) effects of civil society laws on a global scale [@LianMurdie:2023; @Chaudhry:2022], which naturally blurs the specific policy mechanisms regimes use for controlling and leveraging global civil society.
-By analyzing the population of formally registered INGOs between 2017–2021, we can more precisely explore how a single formal restrictive INGO law has shaped the operational space for foreign organizations working in the country.
-Specifically, we can observe exactly how the Chinese government has used the RO registration process to strategically limit and reshape these organizations' operational space.
-We conducted both a descriptive analysis of the composition of the issue areas of INGOs successfully registered under the INGO law and a regression analysis of the relationship between INGO issue areas and their operational space.
+China provides a unique case for exploring these different mechanisms.
+The implementation and enforcement of the law has been quite strict, and since government data regarding INGOs is complete, we are able to observe the entire population of INGOs granted RO status since 2017.
+By analyzing all formally registered INGOs between 2017--2021, we can more precisely explore how a single formal restrictive civil society law has shaped the operational space for foreign organizations working in the country.
+Government data about each INGO provides each organization's issue area, mission, and scope, and by looking at each organization's geographic reach and registration timeline, we can get a sense of organization-level operational flexibility.
+Importantly, by modeling and exploring the composition of permitted INGOs, we can observe exactly how the Chinese government has used the RO registration process to strategically limit and reshape these organizations' operational space.
 
@@
 
-> **E~2~**: Because they are explicitly focused on local issues, INGOs with explicitly local missions should be registered in fewer provinces.
-
-We also took into account the temporal factor, the time elapsed since the law took effect when the ROs got registered.
+> **E~2~**: Because they are focused on local issues, INGOs with explicitly local missions should be registered in fewer provinces.
+
+Finally, TODO We also took into account the temporal factor, the time elapsed since the law took effect when the ROs got registered.
 Since there was a *de facto* grace period for INGOs to seek registration even though theoretically all existing INGOs should obtain the legal status right after January 1, 2017, the timing of registration for ROs varies by years.
 More time elapsed since the enforcement of the law can mean INGOs took more efforts to seek an ideal registration results, and they are more rest-assured to maintain a not-yet-legal status because they do not work in contentious issue areas.
-For example, World Animal Protection has been wording in China since 2007, but they did not register their office until two years after the ONGO Law took effect.
+For example, World Animal Protection has been working in China since 2007, but they did not register their office until two years after the ONGO Law took effect.
 
 > **E~3~**: Because INGOs taking longer time in registration are less eager to gain legal status and having more time to choose a more ideal registration results, they should be registered in more provinces.
-
-Additionally, we introduced province fixed effects in the model to account for socio-economic or institutional differences across provinces, as well as registration year fixed effects to account for any potential administrative processing variance during COVID years.
 
@@
 
+We are not interested in statistical significance or hypothesis testing.
+Instead, we are interested in the overall registration patterns across our three expectations.
+Accordingly, while we report full model coefficients, care should be taken to not be concerned if those coefficients are statistically different from zero, or if coefficients for one issue area are statistically different from another issue area.
+Instead, we use these model results to generate posterior predictions that illustrate the full range of possible registration patterns.
+
+This is also apparent in our graphical results.
+Rather than display coefficients that demonstrate the marginal effects of one issue area compared to another, we provide posterior predictions of the expected counts and proportions of authorized provinces.
+The model results are thus descriptive explorations of our expectations, not confirmatory hypothesis tests.
+
+Additionally, we introduced province fixed effects in the model to account for socio-economic or institutional differences across provinces, as well as registration year fixed effects to account for any potential administrative processing variance during COVID years.
+
 ```{r fig-province-count-collapsed, fig.width=6, fig.height=3}

### 2024-07-11 notebook/manuscript.qmd
Simplify multi-format outputs

@@
 # Add the manuscript target as a dependency to the overall website
-targets::tar_load(
-  c(manuscript_nice, manuscript_manuscripty)
-)
+targets::tar_load(c(manuscript))
 ```
@@
 
-  <a class="btn btn-warning btn-sm mb-1" href="/manuscript/output-ms/manuscript-ms.pdf" target="manuscript">
+  <a class="btn btn-warning btn-sm mb-1" href="/manuscript/output/manuscript+ms.pdf" target="manuscript">
   <i class="fa-solid fa-file-pdf"></i>&ensp;Manuscripty PDF
@@
 
-  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/manuscript/output-ms/manuscript-ms.pdf">
+  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/manuscript/output/manuscript+ms.pdf">
   <i class="fa-solid fa-file-arrow-down"></i>&ensp;Manuscripty PDF <small>(download)</small>

### 2024-07-11 manuscript/manuscript.qmd
update model
Remove {gt}; switch to {tinytable}

@@
   digits = 3, width = 120,
-  dplyr.summarise.inform = FALSE,
-  knitr.kable.NA = ""
+  dplyr.summarise.inform = FALSE
 )
@@
 library(janitor)
-library(gt)
+library(tinytable)
 library(targets)
@@
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
-invisible(list2env(tar_read(table_functions), .GlobalEnv))
 
@@
 
-::: {#tbl-issues}
-
-\footnotesize
-\renewcommand*{\arraystretch}{1.75}
-
 ```{r}
-#| label: table-issues
+#| label: tbl-issues
+#| tbl-cap: "Possible INGO issue areas and example organizations"
 #| include: true
+
 tribble(
@@
 ) |>
-  gt() |> 
-  tab_footnote(
-    footnote = "Includes poverty alleviation, disaster relief, rural development, etc.",
-    locations = cells_body(columns = Issue, rows = 2)
+  tt(
+    width = c(20, 50),
+    notes = list(
+      "1" = list(i = 2, j = 1, text = "Includes poverty alleviation, disaster relief, rural development, etc."),
+      "2" = list(i = 6, j = 1, text = "Includes grant-making organizations, organizations working on general international communication, and organizations working on multiple non-overlapping issues")
+    )
   ) |>
-  tab_footnote(
-    footnote = "Includes grant-making organizations, organizations working on general international communication, and organizations working on multiple non-overlapping issues",
-    locations = cells_body(columns = Issue, rows = 6)
-  ) |> 
-  cols_width(Issue ~ gt_pct(20), Examples ~ gt_pct(50)) |> 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) |>
-  opts_theme() |> 
-  tab_options(
-    quarto.disable_processing = TRUE
-  )
-```
-
-Possible INGO issue areas and example organizations
-
-:::
+  style_tt(j = 1:2, align = "l") |>
+  style_tt(
+    bootstrap_class = "table table-sm",
+    tabularray_inner = "rowsep=1pt, cells={font=\\footnotesize}"
+  )
+```
 

### 2024-09-19 manuscript/appendix.qmd

--- 2023-12-07 manuscript/appendix.qmd
@@
 library(modelsummary)
-library(gt)
+library(tinytable)
 library(targets)
@@
 
-::: {#tbl-coefs-orig}
-
-\footnotesize
-
 ```{r}
-#| label: table-coefs-orig
+#| label: tbl-coefs-orig
+#| tbl-cap: "Complete model coefficients"
 #| include: true
 
-notes <- c(
+notes <- paste(
   "Estimates are median posterior log odds from ordered Beta regression models;",
@@
 )
+
+if (fmt_out == "latex") {
+  notes <- str_replace_all(notes, "%", r"(\\%)")
+}
+
+inner <- "
+row{odd[3-35]}={abovesep=0pt, belowsep=2pt},
+row{even[4-36]}={rowsep=0pt},
+cells={font=\\footnotesize}, row{1}={valign=b}
+"
 
@@
   coef_map = models_tbl$nice_coefs,
-  output = "gt"
+  notes = c(notes),
+  width = c(50, 25, 25),
+  output = "tinytable"
 ) |>
-  opts_theme() |>
-  tab_footnote(
-    footnote = paste(notes, collapse = " ")
-  ) %>%
-  opts_theme() |>
-  tab_options(
-    quarto.disable_processing = TRUE
+  style_tt(j = 2:3, align = "c") |>
+  style_tt(i = seq(1, 35, 2), j = 1, rowspan = 2, alignv = "t") |>
+  style_tt(
+    bootstrap_class = "table table-sm",
+    tabularray_inner = inner
   )
 ```
-
-Complete model coefficients
-
-:::
 
@@
 
+# Comparison of the cases of TNC and Greenpeace
+
+@tbl-case-study summarizes the cases of TNC and Greenpeace.
+In addition to confirming the correlation between issue area and operational space found in the statistical model, the cases highlight how government preferences exert influence on both the degree of contentious programming INGOs are allowed to undertake and the severity of legal restrictions INGOs can face.
+
+```{r}
+#| label: tbl-case-study
+#| tbl-cap: "Comparison of the work of The Nature Conservancy and Greenpeace in China"
+#| include: true
+
+compare_table <- read_csv(here::here("data", "manual_data", "table-case-study.csv"))
+
+compare_table |>
+  rename(` ` = Characteristic) |>
+  tt(
+    width = c(20, 30, 30)
+  ) |>
+  style_tt(j = 1, bold = TRUE) |>
+  style_tt(j = 1:3, align = "l") |>
+  style_tt(
+    bootstrap_class = "table table-sm",
+    tabularray_inner = "rowsep=1pt, cells={font=\\footnotesize}"
+  )
+```
+
+\newpage
+
 # References
+
+::: {#refs .bibliography}
+:::

### 2024-09-19 manuscript/manuscript.qmd
Add note from Meng

@@
 short-title: "Enforcing Boundaries"
-date: "2024-02-23"
+date: "2024-09-16"
 author:
@@
 We are not interested in statistical significance or hypothesis testing.
+(Meng's note.
+Starting with the negative sentence may be too blunt.
+Suggest to change the order of Sentence 1 and Sentence 2).
 Instead, we are interested in the overall registration patterns across our three expectations.

### 2024-09-19 manuscript/manuscript.qmd
citation and typo correction

@@
 Many INGOs gained legal status by registering as foreign-invested companies [@Sidel:2016], allowing them to hire local employees [@HolbigLang:2022; @Yin:2009].
-However, this legal form is not quite compatible with the non-profit-distributing, social service orientation of civil society [@Ye:2021].
-INGOs registered as foreign-invested companies had to navigate incongruous for-profit regulations, such as rules protecting shareholders' investment returns.
+However, this legal form is not quite compatible with the non-profit-distributing, social service orientation of civil society.
+INGOs registered as foreign-invested companies had to navigate incongruous for-profit regulations, such as rules protecting shareholders' investment returns [@Ye:2021].
 
@@
 By the end of 2021 the probability of national-level registration increases to `r p_timing$x2022.all_32_provinces$prop_ci_nice` while the probability of working in a range of provinces increases to predicted to work in two or more provinces remains around `r p_timing$x2022.between_1_32_provinces$prop_ci_nice`.
-These later INGOs are the least likely to 8be registered in only one province, with a probability of `r p_timing$x2022.only_1_province$prop_ci_nice`.
+These later INGOs are the least likely to be registered in only one province, with a probability of `r p_timing$x2022.only_1_province$prop_ci_nice`.
 @fig-timing-preds(b) demonstrates the expected count of provinces over five years since 2017.
@@
 
-To do: update the discussion according to the new Expectation 3
+To do: update the discussion according to the new Expectation 3.
+Use the Oxfam case as an example to explain later-registered ROs took more efforts to find the PSU and PSB that agree to grand broader province access.
+*Drop* the perspective of local connections (to avoid overlapping and confusion with the variable of local connections.
 
